### 2023-11-10 experiment/stimuli/selection/selection.qmd
update

---
title: "Stimuli Selection"
format:
  html:
    embed-resources: true
editor_options: 
  chunk_output_type: console
---

```{r}
#| include: false
#| code-fold: true
library(tidyverse)
library(easystats)

naps <- readxl::read_excel("13428_2013_379_MOESM1_ESM.xls",  skip = 3,
                           col_names = c("ID", "Category", "Nr", "VerticalHorizontal", "Description",
                                         "Women_Valence", "Women_Valence_SD", "Women_AvAp",
                                         "Women_AvAp_SD", "Women_Arousal", "Women_Arousal_SD",
                                         "Men_Valence", "Men_Valence_SD", "Men_AvAp", "Men_AvAp_SD",
                                         "Men_Arousal", "Men_Arousal_SD", "All_Valence",
                                         "All_Valence_SD", "All_AvAp", "All_AvAp_SD",
                                         "All_Arousal", "All_Arousal_SD", "Width",
                                         "Height", "Luminance", "Contrast",
                                         "JPEG_size80", "LABL", "LABA", "LABB", "Entropy",
                                         "Acronym", "X", "X2")) |>
  select(-X, -X2, -Acronym, -ends_with("_SD")) |>
  mutate(ID = paste0(ID, ".jpg"))

napsero <- readxl::read_excel("Data Sheet 1.XLSX", sheet = "Ratings") |>
  full_join(readxl::read_excel("Data Sheet 1.XLSX", sheet = "Image parameters"), by = join_by("ID", "Category")) |>
  select(-contains("_SD"), -contains("HoF"), -contains("HoM")) |>
  rename(VerticalHorizontal = `V/H`,
         Men_Valence = val_M_HeM,
         Women_Valence = val_M_HeF,
         Men_Arousal = aro_M_HeM,
         Women_Arousal = aro_M_HeF) |>
  mutate(across(c("Luminance", "Contrast", "JPEG_size80", "LABL", "LABA", "LABB", "Entropy"), as.numeric),
         Description = NA)

# Join
naps <- filter(naps, ID %in% filter(napsero, Category == "Non-erotic")$ID)
naps[c("Men_Arousal", "Men_Valence", "Women_Valence", "Women_Arousal", "Nr", "VerticalHorizontal")] <- NA
napsero[napsero$Category== "Non-erotic", "Category"] <- NA

ids <- napsero[is.na(napsero$Category), ]$ID
for(c in c("Category", "Height", "Width", "Luminance", "Contrast",
           "JPEG_size80", "LABL", "LABA", "LABB", "Entropy", "Description")) {
  napsero[napsero$ID == ids, c] <- naps[naps$ID == ids, c]
}

```

## Selection

### Remove couples

```{r}
df <- napsero |>
  filter(Category %in% c("Male", "Female", "Faces", "People")) |>
  mutate(Condition = ifelse(Category %in% c("Female", "Male"), "Erotic", "Non-erotic"))
```

### Select based on norms
```{r}
men <- df |>
  filter(Condition == "Erotic") |>
  group_by(Category) |>
  slice_max(Men_Arousal, n=8, with_ties = FALSE) |>
  pull(ID)

women <- df |>
  filter(Condition == "Erotic", !ID %in% men) |>
  group_by(Category) |>
  slice_max(Women_Arousal, n=8, with_ties = FALSE) |>
  pull(ID)

neutral <- df |>
  filter(Condition == "Non-erotic", !ID %in% c(men, women)) |>
  mutate(Arousal = (Men_Arousal + Women_Arousal) / 2) |>
  slice_min(Arousal, n=16, with_ties = FALSE) |>
  pull(ID)

pos_arousing <- df |>
  filter(Condition == "Non-erotic", !ID %in% c(men, women, neutral)) |>
  mutate(Arousal = (Men_Arousal + Women_Arousal) / 2,
         Valence = (Men_Valence + Women_Valence) / 2) |>
  filter(Valence > 5) |>
  slice_max(Arousal, n=16, with_ties = FALSE) |>
  pull(ID)

selected <- unique(c(men, women, neutral, pos_arousing))

cat(
  paste0("N (men) = ", length(men), "\nN (women) = ", length(women),
       "\nN (neutral) = ", length(neutral),  "\nN (arousing-positive) = ", length(pos_arousing),
       "\nTotal = ", length(selected))
)
```

```{r}
selected
```

### Visualization

```{r}
#| out.width: 1\\textwidth
#| fig.width: 8
#| fig.height: 6
df |>
  mutate(Selected = ifelse(ID %in% selected, TRUE, FALSE)) |>
  pivot_longer(cols = c("Men_Valence", "Men_Arousal", "Women_Valence", "Women_Arousal")) |>
  separate(name, into=c("Target", "Variable")) |>
  pivot_wider(names_from=Variable, values_from=value) |>
  ggplot(aes(x=Valence, y=Arousal, color=Category)) +
  geom_point(aes(shape=Selected), size=6, alpha=0.8) +
  scale_shape_manual(values=c("TRUE"=20, "FALSE"=4)) +
  guides(shape = guide_legend(override.aes = list(color="white"))) +
  facet_wrap(~Target) +
  theme_abyss()
```

### Final Selection

-   ID: picture category and number
-   V/H: vertical / horizontal
-   Av/Ap: avoidance - approach dimension
-   M: mean
-   SD: standard deviation
-   JPEG_size80:index of overall complexity
-   LABL: luminance in CIE L*a*b color space
-   LABA: the amount of red color CIE L*a*b color space
-   LABB: the amount of the green color CIE L*a*b color space

```{r}
#| code-fold: true
df |> 
  filter(ID %in% selected) |> 
  knitr::kable()
```

### 2023-11-10 experiment/stimuli/selection/selection.qmd
rename some stuff

@@
 
-naps <- readxl::read_excel("13428_2013_379_MOESM1_ESM.xls",  skip = 3,
+naps <- readxl::read_excel("norms_naps.xls",  skip = 3,
                            col_names = c("ID", "Category", "Nr", "VerticalHorizontal", "Description",
@@
 
-napsero <- readxl::read_excel("Data Sheet 1.XLSX", sheet = "Ratings") |>
-  full_join(readxl::read_excel("Data Sheet 1.XLSX", sheet = "Image parameters"), by = join_by("ID", "Category")) |>
+napsero <- readxl::read_excel("norms_napsero.XLSX", sheet = "Ratings") |>
+  full_join(readxl::read_excel("norms_napsero.XLSX", sheet = "Image parameters"), by = join_by("ID", "Category")) |>
   select(-contains("_SD"), -contains("HoF"), -contains("HoM")) |>
@@
   filter(Category %in% c("Male", "Female", "Faces", "People")) |>
-  mutate(Condition = ifelse(Category %in% c("Female", "Male"), "Erotic", "Non-erotic"))
+  mutate(Type = ifelse(Category %in% c("Female", "Male"), "Erotic", "Non-erotic"))
 ```
@@
 men <- df |>
-  filter(Condition == "Erotic") |>
+  filter(Type == "Erotic") |>
   group_by(Category) |>
@@
 women <- df |>
-  filter(Condition == "Erotic", !ID %in% men) |>
+  filter(Type == "Erotic", !ID %in% men) |>
   group_by(Category) |>
@@
 neutral <- df |>
-  filter(Condition == "Non-erotic", !ID %in% c(men, women)) |>
+  filter(Type == "Non-erotic", !ID %in% c(men, women)) |>
   mutate(Arousal = (Men_Arousal + Women_Arousal) / 2) |>
@@
 pos_arousing <- df |>
-  filter(Condition == "Non-erotic", !ID %in% c(men, women, neutral)) |>
+  filter(Type == "Non-erotic", !ID %in% c(men, women, neutral)) |>
   mutate(Arousal = (Men_Arousal + Women_Arousal) / 2,
@@
 #| code-fold: true
+write.csv(df, "stimuli.csv", row.names=FALSE)
+
 df |> 

### 2023-11-11 experiment/stimuli_selection/selection.qmd
update

---
title: "Stimuli Selection"
format:
  html:
    embed-resources: true
editor_options: 
  chunk_output_type: console
---

```{r}
#| include: false
#| code-fold: true
library(tidyverse)
library(easystats)
library(ggrepel)

naps <- readxl::read_excel("norms_naps.xls",  skip = 3,
                           col_names = c("ID", "Category", "Nr", "Orientation", "Description",
                                         "Women_Valence", "Women_Valence_SD", "Women_AvAp",
                                         "Women_AvAp_SD", "Women_Arousal", "Women_Arousal_SD",
                                         "Men_Valence", "Men_Valence_SD", "Men_AvAp", "Men_AvAp_SD",
                                         "Men_Arousal", "Men_Arousal_SD", "All_Valence",
                                         "All_Valence_SD", "All_AvAp", "All_AvAp_SD",
                                         "All_Arousal", "All_Arousal_SD", "Width",
                                         "Height", "Luminance", "Contrast",
                                         "JPEG_size80", "LABL", "LABA", "LABB", "Entropy",
                                         "Acronym", "X", "X2")) |>
  select(-X, -X2, -Acronym, -ends_with("_SD")) |>
  mutate(ID = paste0(ID, ".jpg"))

napsero <- readxl::read_excel("norms_napsero.XLSX", sheet = "Ratings") |>
  full_join(readxl::read_excel("norms_napsero.XLSX", sheet = "Image parameters"), by = join_by("ID", "Category")) |>
  select(-contains("_SD"), -contains("HoF"), -contains("HoM")) |>
  rename(Orientation = `V/H`,
         Men_Valence = val_M_HeM,
         Women_Valence = val_M_HeF,
         Men_Arousal = aro_M_HeM,
         Women_Arousal = aro_M_HeF) |>
  mutate(across(c("Luminance", "Contrast", "JPEG_size80", "LABL", "LABA", "LABB", "Entropy"), as.numeric),
         Description = NA)

# Join
naps <- filter(naps, ID %in% filter(napsero, Category == "Non-erotic")$ID)
naps[c("Men_Arousal", "Men_Valence", "Women_Valence", "Women_Arousal", "Nr", "Orientation")] <- NA
napsero[napsero$Category== "Non-erotic", "Category"] <- NA

ids <- napsero[is.na(napsero$Category), ]$ID
for(c in c("Category", "Height", "Width", "Luminance", "Contrast",
           "JPEG_size80", "LABL", "LABA", "LABB", "Entropy", "Description")) {
  napsero[napsero$ID == ids, c] <- naps[naps$ID == ids, c]
}

```

## Selection

### Remove couples

```{r}
df <- napsero |>
  filter(Category %in% c("Male", "Female", "Faces", "People")) |>
  mutate(Type = ifelse(Category %in% c("Female", "Male"), "Erotic", "Non-erotic"))
```

### Select based on norms
```{r}
men <- df |>
  filter(Type == "Erotic") |>
  group_by(Category) |>
  slice_max(Men_Arousal, n=8, with_ties = FALSE) |>
  pull(ID) |> 
  c(
    df |>
      filter(Type == "Erotic") |>
      group_by(Category) |>
      slice_min(Men_Arousal, n=4, with_ties = FALSE) |>
      pull(ID))

women <- df |>
  filter(Type == "Erotic", !ID %in% men) |>
  group_by(Category) |>
  slice_max(Women_Arousal, n=8, with_ties = FALSE) |>
  pull(ID) |> 
  c(
    df |>
      filter(Type == "Erotic", !ID %in% men) |>
      group_by(Category) |>
      slice_min(Women_Arousal, n=4, with_ties = FALSE) |>
      pull(ID)
  )

neutral <- df |>
  filter(Type == "Non-erotic", !ID %in% c(men, women)) |>
  mutate(Arousal = (Men_Arousal + Women_Arousal) / 2) |>
  slice_min(Arousal, n=16, with_ties = FALSE) |>
  pull(ID)

pos_arousing <- df |>
  filter(Type == "Non-erotic", !ID %in% c(men, women, neutral)) |>
  mutate(Arousal = (Men_Arousal + Women_Arousal) / 2,
         Valence = (Men_Valence + Women_Valence) / 2) |>
  filter(Valence > 5) |>
  slice_max(Arousal, n=16, with_ties = FALSE) |>
  pull(ID)

selected <- unique(c(men, women, neutral, pos_arousing))

cat(
  paste0("N (men) = ", length(men), "\nN (women) = ", length(women),
       "\nN (neutral) = ", length(neutral),  "\nN (arousing-positive) = ", length(pos_arousing),
       "\nTotal = ", length(selected))
)
```

```{r}
selected
```

### Visualization

```{r}
#| out.width: 1\\textwidth
#| fig.width: 8
#| fig.height: 6
napsero |>
  mutate(Selected = ifelse(ID %in% selected, TRUE, FALSE),
         label = ifelse(Selected, str_remove(ID, ".jpg"), NA),
         Type = ifelse(Category %in% c("Female", "Male"), "Erotic", "Non-erotic")) |>
  pivot_longer(cols = c("Men_Valence", "Men_Arousal", "Women_Valence", "Women_Arousal")) |>
  separate(name, into=c("Target", "Variable")) |>
  pivot_wider(names_from=Variable, values_from=value) |>
  ggplot(aes(x=Valence, y=Arousal, color=Category)) +
  geom_point(aes(shape=Selected), size=6, alpha=0.8) +
  # ggrepel::geom_label_repel(aes(label = label)) +
  scale_shape_manual(values=c("TRUE"=20, "FALSE"=4)) +
  guides(shape = guide_legend(override.aes = list(color="white"))) +
  facet_grid(~Target) +
  theme_abyss()
```

### Final Selection

-   ID: picture category and number
-   V/H: vertical / horizontal
-   Av/Ap: avoidance - approach dimension
-   M: mean
-   SD: standard deviation
-   JPEG_size80:index of overall complexity
-   LABL: luminance in CIE L*a*b color space
-   LABA: the amount of red color CIE L*a*b color space
-   LABB: the amount of the green color CIE L*a*b color space

```{r}
#| code-fold: true
selection <- df |> 
  filter(ID %in% selected)

write.csv(selection, "stimuli_data.csv", row.names=FALSE)
knitr::kable(selection)
```

```{r}
#| code-fold: true
json <- selection |> 
  select(stimulus=ID, Category, Orientation) |> 
  jsonlite::toJSON()

write(paste("var stimuli_list = ", json), "stimuli_list.js")
```

```{r}
#| code-fold: true
path_ero <- "C:/Dropbox/RECHERCHE/docs/Stimuli/NAPS/NAPS_ERO/"
path_naps <- "C:/Dropbox/RECHERCHE/docs/Stimuli/NAPS/NAPS/"

# Remove all current files
unlink("../stimuli/*")

# Copy each file
for(file in selected) {
  if(str_detect(file, "Male|Female")) {
    file.copy(paste0(path_ero, file), "../stimuli/")
  } else {
    file.copy(paste0(path_naps, file), "../stimuli/")
  }
}
```

### 2023-11-11 experiment/demographics.js

@@ -1,0 +1,134 @@
+// Retrieve and save browser info ========================================================
+var demographics_browser_info = {
+    type: jsPsychBrowserCheck,
+    data: {
+        screen: "browser_info",
+        date: new Date().toLocaleDateString("fr-FR"),
+        time: new Date().toLocaleTimeString("fr-FR"),
+    },
+    on_finish: function () {
+        data = jsPsych.data.get().filter({ screen: "browser_info" }).values()[0]
+        jsPsych.data.addProperties({
+            ["screen_height"]: data["height"],
+            ["screen_width"]: data["width"],
+        })
+        for (var key in data) {
+            if (
+                [
+                    "vsync_rate",
+                    "os",
+                    "mobile",
+                    "browser",
+                    "browser_version",
+                ].includes(key)
+            ) {
+                jsPsych.data.addProperties({
+                    [key]: data[key],
+                })
+            }
+        }
+        jsPsych.data.addProperties()
+    },
+}
+
+// Participant ID ========================================================================
+var demographics_participant_id = {
+    type: jsPsychSurveyText,
+    questions: [
+        {
+            prompt: "Enter participant ID:",
+            placeholder: "001",
+            name: "Participant_ID",
+        },
+    ],
+    data: {
+        screen: "participant_id",
+    },
+    on_finish: function () {
+        // Store `participant_id` so that it can be reused later
+        jsPsych.data.addProperties({
+            participant_id: jsPsych.data.get().last().values()[0]["response"][
+                "Participant_ID"
+            ],
+        })
+    },
+}
+
+// Consent form ========================================================================
+var demographics_consent = {
+    type: jsPsychHtmlButtonResponse,
+    stimulus:
+        // Logo
+        "<img src='https://blogs.brighton.ac.uk/sussexwrites/files/2019/06/University-of-Sussex-logo-transparent.png' width='150px' align='right'/><br><br><br><br><br>" +
+        // Title
+        "<h1>Informed Consent</h1>" +
+        "<p align='left'>This study aims at comparing ....</p>" +
+        "<p align='left'>As you will be shown <b>erotic images</b>, please make sure you find yourself in an private setting for the whole duration of the experiment (~30min).</p>" +
+        "<p align='left'>Your participation in this research will be kept completely confidential. <b>Your responses are entirely anonymous</b>, and no IP address or any identifiers are collected.</p>" +
[…]

### 2023-11-11 experiment/fiction.js

@@ -1,0 +1,175 @@
+// Parameters ======================================================
+var fiction_trialnumber = 1
+
+// instructions ====================================================
+var fiction_instructions = {
+    type: jsPsychHtmlButtonResponse,
+    choices: ["Let's start!"],
+    stimulus:
+        "<h1>Instructions</h1>" +
+        // Left aligned text
+        "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>In this study, we aim at validating our new image-generation algorithm (based on the Generative Adversarial Network - GAN technology) trained to produce high-quality erotic (but also non-erotic content).</p>" +
+        "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>In the following task, you will be presented with images generated by our algorithm (preceded by the word '<b>AI-generated</b>'), intermixed with erotic and non-erotic real photos (preceded by the word '<b>Picture</b>') taken from publicly available picture databases, adjusted to be of similar dimension and aspect as the artificially-generated images.</p>" +
+        "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>After each image, you will have to rate the images on the following scales:</p><ul style='text-align: left; margin-left: 30%; margin-right: 30%;'>" +
+        "<li><b>Sexy</b>: How sexually appealing do you think the image is.</li>" +
+        "<li><b>Arousal</b>: How much you felt your body to react to the image</li>" +
+        "<li><b>Convincing</b>: In case you spot any artifacts or problems with the image that made it look fake (mostly applies to the artificial images)</li>" +
+        "</ul>",
+    data: { screen: "fiction_instructions" },
+}
+
+// Condition assignment ============================================
+function shuffleArray(array) {
+    for (let i = array.length - 1; i > 0; i--) {
+        const j = Math.floor(Math.random() * (i + 1))
+        ;[array[i], array[j]] = [array[j], array[i]]
+    }
+    return array
+}
+
+function assignCondition(stimuli_list) {
+    new_stimuli_list = []
+    // Loop through unique categories
+    for (let cat of [...new Set(stimuli_list.map((a) => a.Category))]) {
+        // Get all stimuli of this category
+        var cat_stimuli = stimuli_list.filter((a) => a.Category == cat)
+
+        // Shuffle cat_stimuli
+        cat_stimuli = shuffleArray(cat_stimuli)
+
[…]

### 2023-11-11 experiment/stimuli_selection/stimuli_list.js

@@ -1,0 +1,1 @@
+var stimuli_list =  [{"stimulus":"Male_001_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_002_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_003_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_004_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_005_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_006_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_007_h.jpg","Category":"Male","Orientation":"h"},{"stimulus":"Male_008_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_009_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_010_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_011_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_012_h.jpg","Category":"Male","Orientation":"h"},{"stimulus":"Male_013_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_014_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_015_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_016_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_017_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_019_h.jpg","Category":"Male","Orientation":"h"},{"stimulus":"Male_020_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_021_h.jpg","Category":"Male","Orientation":"h"},{"stimulus":"Male_022_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_023_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_024_h.jpg","Category":"Male","Orientation":"h"},{"stimulus":"Male_025_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Female_001_h.jpg","Category":"Female","Orientation":"h"},{"stimulus":"Female_002_h.jpg","Category":"Female","Orientation":"h"},{"stimulus":"Female_003_v.jpg","Category":"Female","Orientation":"v"},{"stimulus":"Female_004_v.jpg","Category":"F
[…]

### 2023-11-11 experiment/fiction.js
restore isi

@@ -166,9 +166,9 @@ var fiction_trials = {
     timeline_variables: stimuli_list,
     randomize_order: true,
     timeline: [
-        fiction_fixationcross((isi = 100)),
+        fiction_fixationcross((isi = 1000)),
         fiction_prime,
-        fiction_fixationcross((isi = 50)),
+        fiction_fixationcross((isi = 500)),
         fiction_showimage,
         fiction_ratings,
     ],

### 2023-11-16 experiment/stimuli_selection/selection.qmd
reduce to 54 stims, adjust timings

@@
   group_by(Category) |>
-  slice_max(Men_Arousal, n=8, with_ties = FALSE) |>
+  slice_max(Men_Arousal, n=6, with_ties = FALSE) |>
   pull(ID) |> 
@@
       group_by(Category) |>
-      slice_min(Men_Arousal, n=4, with_ties = FALSE) |>
+      slice_min(Men_Arousal, n=2, with_ties = FALSE) |>
       pull(ID))
@@
   group_by(Category) |>
-  slice_max(Women_Arousal, n=8, with_ties = FALSE) |>
+  slice_max(Women_Arousal, n=6, with_ties = FALSE) |>
   pull(ID) |> 
@@
       group_by(Category) |>
-      slice_min(Women_Arousal, n=4, with_ties = FALSE) |>
+      slice_min(Women_Arousal, n=2, with_ties = FALSE) |>
       pull(ID)
@@
   mutate(Arousal = (Men_Arousal + Women_Arousal) / 2) |>
-  slice_min(Arousal, n=16, with_ties = FALSE) |>
+  slice_min(Arousal, n=12, with_ties = FALSE) |>
   pull(ID)
@@
   filter(Valence > 5) |>
-  slice_max(Arousal, n=16, with_ties = FALSE) |>
+  slice_max(Arousal, n=12, with_ties = FALSE) |>
   pull(ID)

### 2023-11-16 experiment/fiction.js

@@ -2,19 +2,10 @@
 var fiction_trialnumber = 1
 
 // instructions ====================================================
-var fiction_instructions = {
+var fiction_instructions1 = {
     type: jsPsychHtmlButtonResponse,
-    choices: ["Let's start!"],
-    stimulus:
-        "<h1>Instructions</h1>" +
-        // Left aligned text
-        "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>In this study, we aim at validating our new image-generation algorithm (based on the Generative Adversarial Network - GAN technology) trained to produce high-quality erotic (but also non-erotic content).</p>" +
-        "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>In the following task, you will be presented with images generated by our algorithm (preceded by the word '<b>AI-generated</b>'), intermixed with erotic and non-erotic real photos (preceded by the word '<b>Picture</b>') taken from publicly available picture databases, adjusted to be of similar dimension and aspect as the artificially-generated images.</p>" +
-        "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>After each image, you will have to rate the images on the following scales:</p><ul style='text-align: left; margin-left: 30%; margin-right: 30%;'>" +
-        "<li><b>Sexy</b>: How sexually appealing do you think the image is.</li>" +
-        "<li><b>Arousal</b>: How much you felt your body to react to the image</li>" +
-        "<li><b>Convincing</b>: In case you spot any artifacts or problems with the image that made it look fake (mostly applies to the artificial images)</li>" +
-        "</ul>",
+    choices: [text_instructionsbutton_en],
+    stimulus: text_instructions1_en,
     data: { screen: "fiction_instructions" },
 }
 
@@ -72,27 +63,21 @@ function fiction_fixationcross(isi = 500) {
     }
 }
 
-var fiction_prime = {
-    type: jsPsychHtmlKeyboardResponse,
-    stimulus: function () {
-        var cond = jsPsych.timelineVariable("Condition")
-        if (cond == "Reality") {
+function fiction_prime(text_cue) {
+    return {
+        type: jsPsychHtmlKeyboardResponse,
+        stimulus: function () {
+            var cond = jsPsych.timelineVariable("Condition")
             return (
                 "<div style='font-size:400%; position:fixed; text-align: center; top:50%; bottom:50%; right:20%; left:20%'><b>" +
[…]

### 2023-11-16 experiment/instructions.js

@@ -1,0 +1,26 @@
+// =========================================================================================
+// Fiction
+// =========================================================================================
+var text_instructions1_en =
+    "<h1>Instructions</h1>" +
+    // Left aligned text
+    "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>In this study, we aim at validating our new image-generation algorithm (based on the Generative Adversarial Network - GAN technology) trained to produce high-quality erotic (but also non-erotic content).</p>" +
+    "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>In the following task, you will be presented with images generated by our algorithm (preceded by the word '<b>AI-generated</b>'), intermixed with erotic and non-erotic real photos (preceded by the word '<b>Picture</b>') taken from publicly available picture databases, adjusted to be of similar dimension and aspect as the artificially-generated images.</p>" +
+    "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>After each image, you will have to rate the images on the following scales:</p><ul style='text-align: left; margin-left: 30%; margin-right: 30%;'>" +
+    "<li><b>Sexy</b>: How sexy do you think others would find this image, on average? This question is about how sexually appealing you believe this image would in itself be to <b>people similar to you</b> in terms of gender and sexual orientation.</li>" + // "in itself" to suggest "regardless of the condition"
+    "<li><b>Arousal</b>: How much do you find the image sexually arousing. This question is about <b>your own personal reaction</b> to the image.</li>" +
+    // "<li><b>Convincing</b>: In case you spot any artifacts or problems with the image that made it look fake (mostly applies to the artificial images)</li>" +
+    "</ul>"
+
+//-------------------------
+var text_instructionsbutton_en = "Let's start!"
+
+// -------------------------
+
+var text_cue_en = { Reality: "Photo", Fiction: "AI-generated" }
+
+// Ratings ----------------------------------------------------------------
+var text_ticks_en = ["Not at all", "Very much"]
+var text_rating_sexy_en =
+    "How much would you consider this image to be <b>sexy</b> on average?" // Sexual appeal
+var text_rating_arousal_en = "How much did you feel <b>sexually aroused</b>?"

### 2023-11-16 experiment/stimuli_selection/stimuli_list.js

@@ -1,1 +1,58 @@
-var stimuli_list =  [{"stimulus":"Male_001_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_002_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_003_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_004_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_005_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_006_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_007_h.jpg","Category":"Male","Orientation":"h"},{"stimulus":"Male_008_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_009_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_010_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_011_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_012_h.jpg","Category":"Male","Orientation":"h"},{"stimulus":"Male_013_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_014_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_015_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_016_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_017_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_019_h.jpg","Category":"Male","Orientation":"h"},{"stimulus":"Male_020_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_021_h.jpg","Category":"Male","Orientation":"h"},{"stimulus":"Male_022_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_023_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_024_h.jpg","Category":"Male","Orientation":"h"},{"stimulus":"Male_025_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Female_001_h.jpg","Category":"Female","Orientation":"h"},{"stimulus":"Female_002_h.jpg","Category":"Female","Orientation":"h"},{"stimulus":"Female_003_v.jpg","Category":"Female","Orientation":"v"
[…]

### 2023-11-16 experiment/fiction.js
add phase 2

@@ -6,7 +6,14 @@ var fiction_instructions1 = {
     type: jsPsychHtmlButtonResponse,
     choices: [text_instructionsbutton_en],
     stimulus: text_instructions1_en,
-    data: { screen: "fiction_instructions" },
+    data: { screen: "fiction_instructions1" },
+}
+
+var fiction_instructions2 = {
+    type: jsPsychHtmlButtonResponse,
+    choices: [text_instructionsbutton_en],
+    stimulus: text_instructions2_en,
+    data: { screen: "fiction_instructions2" },
 }
 
 // Condition assignment ============================================
@@ -56,7 +63,7 @@ function fiction_fixationcross(isi = 500) {
         },
         stimulus:
             "<div  style='font-size:500%; position:fixed; text-align: center; top:50%; bottom:50%; right:20%; left:20%'>+</div>",
-        choices: "NO_KEYS",
+        choices: ["s"],
         trial_duration: isi,
         save_trial_parameters: { trial_duration: true },
         data: { screen: "fiction_fixationcross" },
@@ -74,42 +81,44 @@ function fiction_prime(text_cue) {
                 "</b></div>"
             )
         },
-        choices: "NO_KEYS",
+        choices: ["s"],
         trial_duration: 1000,
         data: { screen: "fiction_prime" },
     }
 }
 
-var fiction_showimage = {
-    type: jsPsychImageKeyboardResponse,
-    stimulus: function () {
-        return "stimuli/" + jsPsych.timelineVariable("stimulus")
-    },
-    stimulus_height: function () {
-        if (jsPsych.timelineVariable("Orientation") == "h") {
-            return null
-        } else {
-            return Math.round(
-                jsPsych.data.get().last().values()[0]["screen_height"] * 0.9
-            )
-        }
-    },
-    stimulus_width: function () {
-        if (jsPsych.timelineVariable("Orientation") == "v") {
-            return null
-        } else {
-            return Math.round(
-                jsPsych.data.get().last().values()[0]["screen_height"] * 0.9
-            )
-        }
-    },
-    choices: ["s"],
-    trial_duration: 3000,
-    on_finish: function (data) {
-        data.trial_number = fiction_trialnumber
-        fiction_trialnumber += 1
-        data.screen = "fiction_image"
-    },
+function fiction_showimage(duration = 2500) {
+    return {
+        type: jsPsychImageKeyboardResponse,
+        stimulus: function () {
[…]

### 2023-11-16 experiment/instructions.js

@@ -12,6 +12,11 @@ var text_instructions1_en =
     // "<li><b>Convincing</b>: In case you spot any artifacts or problems with the image that made it look fake (mostly applies to the artificial images)</li>" +
     "</ul>"
 
+var text_instructions2_en =
+    "<h1>Done!</h1>" +
+    "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>Thanks a lot. In the next phase, we aim at testing if you found our <b>image generation algorithm convincing</b> and artifacts-free.</p>" +
+    "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>We will briefly present you all the images one last time (our generated ones as well as the photos), and you will have to rate them on how <b>real</b> they are.</p>"
+
 //-------------------------
 var text_instructionsbutton_en = "Let's start!"
 
@@ -24,3 +29,4 @@ var text_ticks_en = ["Not at all", "Very much"]
 var text_rating_sexy_en =
     "How much would you consider this image to be <b>sexy</b> on average?" // Sexual appeal
 var text_rating_arousal_en = "How much did you feel <b>sexually aroused</b>?"
+var text_rating_realness_en = "How <b>realistic</b> is this image?"

### 2023-11-26 experiment/fiction.js
increase cue time + add color priming

@@ -17,13 +17,6 @@ var fiction_instructions2 = {
 }
 
 // Condition assignment ============================================
-function shuffleArray(array) {
-    for (let i = array.length - 1; i > 0; i--) {
-        const j = Math.floor(Math.random() * (i + 1))
-        ;[array[i], array[j]] = [array[j], array[i]]
-    }
-    return array
-}
 
 function assignCondition(stimuli_list) {
     new_stimuli_list = []
@@ -33,7 +26,7 @@ function assignCondition(stimuli_list) {
         var cat_stimuli = stimuli_list.filter((a) => a.Category == cat)
 
         // Shuffle cat_stimuli
-        cat_stimuli = shuffleArray(cat_stimuli)
+        cat_stimuli = shuffleArray(cat_stimuli) // Defined in instructions.js
 
         // Assign half to "Reality" condition and half to "Fiction" condition
         for (let i = 0; i < cat_stimuli.length; i++) {
@@ -70,20 +63,29 @@ function fiction_fixationcross(isi = 500) {
     }
 }
 
-function fiction_prime(text_cue) {
+function fiction_cue(text_cue, duration = 1000) {
     return {
         type: jsPsychHtmlKeyboardResponse,
         stimulus: function () {
             var cond = jsPsych.timelineVariable("Condition")
             return (
-                "<div style='font-size:400%; position:fixed; text-align: center; top:50%; bottom:50%; right:20%; left:20%'><b>" +
+                "<div style='font-size:400%; position:fixed; text-align: center; top:50%; bottom:50%; right:20%; left:20%; color: " +
+                color_cues[cond] +
+                "'><b>" +
                 text_cue[cond] +
                 "</b></div>"
             )
         },
+        data: function () {
+            var cond = jsPsych.timelineVariable("Condition")
+            return {
+                screen: "fiction_cue",
+                color: color_cues[cond],
+                text: cond,
+            }
+        },
         choices: ["s"],
-        trial_duration: 1000,
-        data: { screen: "fiction_prime" },
+        trial_duration: duration,
     }
 }
 
@@ -161,11 +163,11 @@ var fiction_ratings = {
 }
 
 var fiction_trials = {
-    timeline_variables: stimuli_list,
+    timeline_variables: stimuli_list, // .slice(0, 1),
     randomize_order: true,
     timeline: [
         fiction_fixationcross((isi = 1000)),
[…]

### 2023-11-26 experiment/instructions.js

@@ -1,11 +1,28 @@
 // =========================================================================================
+// Parameters
+// =========================================================================================
+function shuffleArray(array) {
+    for (let i = array.length - 1; i > 0; i--) {
+        const j = Math.floor(Math.random() * (i + 1))
+        ;[array[i], array[j]] = [array[j], array[i]]
+    }
+    return array
+}
+
+var color_cues = shuffleArray(["red", "blue", "green"])
+color_cues = { Reality: color_cues[0], Fiction: color_cues[1] }
+// =========================================================================================
 // Fiction
 // =========================================================================================
 var text_instructions1_en =
     "<h1>Instructions</h1>" +
     // Left aligned text
     "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>In this study, we aim at validating our new image-generation algorithm (based on the Generative Adversarial Network - GAN technology) trained to produce high-quality erotic (but also non-erotic content).</p>" +
-    "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>In the following task, you will be presented with images generated by our algorithm (preceded by the word '<b>AI-generated</b>'), intermixed with erotic and non-erotic real photos (preceded by the word '<b>Picture</b>') taken from publicly available picture databases, adjusted to be of similar dimension and aspect as the artificially-generated images.</p>" +
+    "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>In the following task, you will be presented with images generated by our algorithm (preceded by the word '<b style='color:" +
+    color_cues["Fiction"] +
+    "'>AI-generated</b>'), intermixed with erotic and non - erotic real photos (preceded by the word '<b style='color:" +
+    color_cues["Reality"] +
+    "'>Picture</b>') taken from publicly available picture databases, adjusted to be of similar dimension and aspect as the artificially - generated images.</p > " +
     "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>After each image, you will have to rate the images on the following scales:</p><ul style='text-align: left; margin-left: 30%; margin-right: 30%;'>" +
     "<li><b>Sexy</b>: How sexy do you think others would find this image, on average? This question is about how sexually appealing you believe this image would in itself be to <b>people similar to you</b> in terms of gender and sexual orientation.</li>" + // "in itself" to suggest "regardless of the condition"
[…]

### 2023-11-26 experiment/stimuli_selection/selection.qmd
60 stims

@@
   group_by(Category) |>
-  slice_max(Men_Arousal, n=6, with_ties = FALSE) |>
+  slice_max(Men_Arousal, n=8, with_ties = FALSE) |>
   pull(ID) |> 
@@
   group_by(Category) |>
-  slice_max(Women_Arousal, n=6, with_ties = FALSE) |>
+  slice_max(Women_Arousal, n=8, with_ties = FALSE) |>
   pull(ID) |> 
@@
   mutate(Arousal = (Men_Arousal + Women_Arousal) / 2) |>
-  slice_min(Arousal, n=12, with_ties = FALSE) |>
+  slice_min(Arousal, n=10, with_ties = FALSE) |>
   pull(ID)
@@
   filter(Valence > 5) |>
-  slice_max(Arousal, n=12, with_ties = FALSE) |>
+  slice_max(Arousal, n=10, with_ties = FALSE) |>
   pull(ID)
@@
 #| out.width: 1\\textwidth
-#| fig.width: 8
-#| fig.height: 6
-napsero |>
+#| fig.width: 10
+#| fig.height: 8
+#| dpi: 300
+#| message: false
+
+dat <- napsero |>
   mutate(Selected = ifelse(ID %in% selected, TRUE, FALSE),
@@
   separate(name, into=c("Target", "Variable")) |>
-  pivot_wider(names_from=Variable, values_from=value) |>
-  ggplot(aes(x=Valence, y=Arousal, color=Category)) +
-  geom_point(aes(shape=Selected), size=6, alpha=0.8) +
+  pivot_wider(names_from=Variable, values_from=value)
+
+dat |>
+  ggplot(aes(x=Valence, y=Arousal)) +
+  geom_point(aes(shape=Selected, color=Category), size=6, alpha=0.8) +
+  ggside::geom_ysidedensity(data=filter(dat, Selected), aes(color=Category), key_glyph = draw_key_blank) +
+  ggside::geom_xsidedensity(data=filter(dat, Selected), aes(color=Category), key_glyph = draw_key_blank) +
   # ggrepel::geom_label_repel(aes(label = label)) +
   scale_shape_manual(values=c("TRUE"=20, "FALSE"=4)) +
+  scale_color_manual(values = c(
+    "Faces" = "#9E9E9E", "People" = "#795548",
+    "Opposite-sex Couple"="#673AB7", "Male Couple"= "#3F51B5", "Female Couple" = "#9C27B0",
+    "Female" = "#E91E63", "Male"= "#2196F3")) +
   guides(shape = guide_legend(override.aes = list(color="white"))) +
   facet_grid(~Target) +
-  theme_abyss()
+  theme_abyss() +
+  theme(ggside.panel.grid.major = element_blank(), 
+        ggside.axis.text = element_blank(),
+        ggside.axis.line = element_blank())
 ```
 
-### Final Selection
+## Final Selection
 
@@
 #| code-fold: true
+
 selection <- df |> 

### 2023-11-26 experiment/stimuli_selection/stimuli_list.js

@@ -1,58 +1,1 @@
-var stimuli_list = [
-    { stimulus: "Male_003_v.jpg", Category: "Male", Orientation: "v" },
-    { stimulus: "Male_005_v.jpg", Category: "Male", Orientation: "v" },
-    { stimulus: "Male_006_v.jpg", Category: "Male", Orientation: "v" },
-    { stimulus: "Male_007_h.jpg", Category: "Male", Orientation: "h" },
-    { stimulus: "Male_008_v.jpg", Category: "Male", Orientation: "v" },
-    { stimulus: "Male_009_v.jpg", Category: "Male", Orientation: "v" },
-    { stimulus: "Male_012_h.jpg", Category: "Male", Orientation: "h" },
-    { stimulus: "Male_013_v.jpg", Category: "Male", Orientation: "v" },
-    { stimulus: "Male_014_v.jpg", Category: "Male", Orientation: "v" },
-    { stimulus: "Male_015_v.jpg", Category: "Male", Orientation: "v" },
-    { stimulus: "Male_016_v.jpg", Category: "Male", Orientation: "v" },
-    { stimulus: "Male_017_v.jpg", Category: "Male", Orientation: "v" },
-    { stimulus: "Male_022_v.jpg", Category: "Male", Orientation: "v" },
-    { stimulus: "Male_023_v.jpg", Category: "Male", Orientation: "v" },
-    { stimulus: "Male_024_h.jpg", Category: "Male", Orientation: "h" },
-    { stimulus: "Male_025_v.jpg", Category: "Male", Orientation: "v" },
-    { stimulus: "Female_001_h.jpg", Category: "Female", Orientation: "h" },
-    { stimulus: "Female_002_h.jpg", Category: "Female", Orientation: "h" },
-    { stimulus: "Female_003_v.jpg", Category: "Female", Orientation: "v" },
-    { stimulus: "Female_005_v.jpg", Category: "Female", Orientation: "v" },
-    { stimulus: "Female_006_v.jpg", Category: "Female", Orientation: "v" },
-    { stimulus: "Female_008_v.jpg", Category: "Female", Orientation: "v" },
-    { stimulus: "Female_009_h.jpg", Category: "Female", Orientation: "h" },
-    { stimulus: "Female_011_h.jpg", Category: "Female", Orientation: "h" },
-    { stimulus: "Female_013_h.jpg", Category: "Female", Orientation: "h" },
[…]

### 2023-11-30 experiment/questionnaire_selection/BAIT.qmd
add BAIT 2.0 questionnaire

---
title: "Questionnaire Selection"
format:
  html:
    embed-resources: true
editor_options: 
  chunk_output_type: console
---

```{r}
#| include: false
#| code-fold: true
library(tidyverse)
library(easystats)
library(ggrepel)

df <- read.csv("https://raw.githubusercontent.com/RealityBending/FakeFace/main/data/data.csv")
```

This document contains an analysis of the factor structure of the BAIT 1.0 questionnaire (GAAIS + questions about CGI) used in Makowski (Fake Face, 2023).

## Item correlation

```{r}
#| code-fold: true
#| fig.width: 10
#| fig.height: 10

data <- df |> 
  select(starts_with("AI_")) |> 
  rename(
         GAAIS_Neg3_Unethical = AI_2_Unethical,
         GAAIS_Neg10_Dangerous = AI_6_Dangerous,
         GAAIS_Pos7_DailyLife = AI_4_DailyLife,
         GAAIS_Pos12_Exciting = AI_8_Exciting,
         GAAIS_Pos14_Applications = AI_9_Applications,
         # BAIT
         BAIT_1_RealisticImages = AI_1_RealisticImages,
         BAIT_2_VideosReal = AI_3_VideosReal,
         BAIT_3_ImitatingReality = AI_5_ImitatingReality,
         BAIT_4_RealisticVideos = AI_7_RealisticVideos,
         BAIT_5_FaceErrors = AI_10_FaceErrors)

correlation::correlation(data) |> 
  summary() |> 
  plot() +
  theme_bw() +
  theme(axis.text.x = element_text(angle=45, hjust=1)) 
```

## GAAIS

- General Attitudes towards Artificial Intelligence Scale (GAAIS; Schepman et al., 2020, 2022)

```{r}
data_gaais <- select(data, starts_with("GAAIS"))

plot(parameters::n_factors(data_gaais))

parameters::factor_analysis(data_gaais, n = 2, rotation = "varimax", sort=TRUE)
```

## BAIT

- Beliefs about Artificial Imaging Technology - BAIT (Makowski, *preprint*)

```{r}
data_bait <- select(data, starts_with("BAIT"))

plot(parameters::n_factors(data_bait))

parameters::factor_analysis(data_bait, n = 2, rotation = "varimax", sort=TRUE)
```

### 2023-11-30 experiment/demographics.js

@@ -79,7 +79,7 @@ var demographics_multichoice = {
     preamble: "<b>Please answer the following questions:</b>",
     questions: [
         {
-            prompt: "What is your gender?",
+            prompt: "What is your biological sex?",
             options: ["Male", "Female", "Other"],
             name: "gender",
         },
@@ -123,12 +123,75 @@ var demographics_freetext = {
             placeholder: "e.g., Caucasian",
             name: "ethnicity",
         },
+        {
+            prompt: "In which country do you currently live?",
+            placeholder: "e.g., UK, Spain",
+            name: "country",
+        },
     ],
     data: {
         screen: "demographics_2",
     },
 }
 
+var demographics_hormones = {
+    type: jsPsychSurveyMultiChoice,
+    preamble:
+        "<b>The following questions are important to understand the role of potential biological factors in our study.</b><br>Please leave blank if the questions don't apply.",
+    questions: [
+        {
+            prompt: "If you are a female, are you currently using birth control treatment?",
+            options: [
+                "No",
+                "Yes - contraceptive pills",
+                "Yes - intrauterine device (IUD)",
+                "Yes - female condoms",
+                "Yes - condoms for partner",
+                "Yes - other",
+            ],
+            name: "birthcontrol",
+        },
+    ],
+    data: {
+        screen: "demographics_hormones",
+    },
+}
+
+var demographics_sex = {
+    type: jsPsychSurveyText,
+    questions: [
+        {
+            prompt: "When is the last time you engaged in sexual activity (intercourse or masturbation)?",
+            placeholder: "e.g., '2 days ago', '3 years ago'",
+            name: "lastsex",
+        },
+    ],
+    data: {
+        screen: "demographics_sexlast",
+    },
+}
+
 var demographics_info = {
-    timeline: [demographics_multichoice, demographics_freetext],
+    timeline: [
+        demographics_multichoice,
+        demographics_freetext,
+        demographics_hormones,
+        demographics_sex,
+    ],
+}
+
+var demographics_ai = {
+    type: jsPsychSurveyLikert,
+    autocomplete: true,
+    questions: [
+        {
+            prompt: "<b>How knowledgeable do you consider yourself about Artificial Intelligence (AI) technology?</b>",
+            name: "AIknowledge",
+            required: true,
+            labels: ["Not at all - 0", "1", "2", "3", "4", "5", "6 - Expert"],
+        },
+    ],
+    data: {
+        screen: "demographics_AIknowledge",
+    },
 }

### 2023-11-30 experiment/questionnaires.js

@@ -1,0 +1,93 @@
+// Items =================================================
+// General Attitudes towards Artificial Intelligence Scale (GAAIS; Schepman et al., 2020, 2022)
+// We used the most loaded items from Schepman et al. (2023) - loadings from the 2 CFAs are in parentheses
+// We adedd items specifically about CGI and artificial media (BAIT)
+var bait_items = [
+    // Neg3 (0.406, 0.405) - Low loadings
+    // "Organisations use Artificial Intelligence unethically",
+    // Neg9 (0.726, 0.717) - Not used in FakeFace
+    "Artificial Intelligence might take control of people",
+    // Neg10 (0.850, 0.848) - Modified: removed "I think"
+    "Artificial Intelligence is dangerous",
+    // Neg15 (1.014, 0.884) - Not used in FakeFace. Modified: replaced "I shiver with discomfort when I think about" by "I am worried about"
+    "I am worried about future uses of Artificial Intelligence<br>",
+    // Pos7 (0.820, 0.878)
+    "I am interested in using artificially intelligent systems in my daily life",
+    // Pos12 (0.734, 0.554)
+    "Artificial Intelligence is exciting",
+    // Pos14 (0.516, 0.346) - Low loadings
+    // "There are many beneficial applications of Artificial Intelligence",
+    // Pos17 (0.836, 0.656) - Not used in FakeFace
+    "Much of society will benefit from a future full of Artificial Intelligence<br>",
+
+    // New items (Beliefs about Artificial Images Technology - BAIT) ---------------------------
+    // Revised from Makowski et al. (Fake Face study)
+    // Changes from FakeFace: remove "I think"
+    "Current Artificial Intelligence algorithms can generate very realistic images",
+    "Images of faces or people generated by Artificial Intelligence always contain errors and artifacts",
+    "Videos generated by Artificial Intelligence have obvious problems that make them easy to spot as fake",
+    "Current Artificial Intelligence algorithms can generate very realistic videos",
+    "Computer-Generated Images (CGI) are capable of perfectly imitating reality",
+    "Technology allows the creation of environments that seem just as real as reality", // New
+]
+
+var bait_dimensions = [
+    "GAAIS_Negative_9",
+    "GAAIS_Negative_10",
+    "GAAIS_Negative_15",
+    "GAAIS_Positive_7",
+    "GAAIS_Positive_12",
+    "GAAIS_Positive_17",
[…]

### 2024-01-25 analysis/1_cleaning.qmd
preprocessing script

---
title: "FictionEro - Data Cleaning"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: true
    toc: true
---

## Data Preparation

```{r}
#| message: false
#| warning: false

library(tidyverse)
library(easystats)
library(patchwork)
library(ggside)
```

```{r}
df <- read.csv("../data/rawdata_participants.csv")
dftask <- read.csv("../data/rawdata_task.csv")
```

The initial sample consisted of `r report::report_participants(df, age="Age", sex="Sex", education="Education")`.

### Recruitment History

```{r}
#| message: false

# Consecutive count of participants per day (as area)
df |>
  mutate(Date = as.Date(Date, format = "%d/%m/%Y")) |> 
  group_by(Date, Experimenter) |> 
  summarize(N = n()) |> 
  ungroup() |>
  complete(Date, Experimenter, fill = list(N = 0)) |> 
  group_by(Experimenter) |>
  mutate(N = cumsum(N)) |>
  ggplot(aes(x = Date, y = N)) +
  geom_area(aes(fill=Experimenter)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Recruitment History",
    x = "Date",
    y = "Total Number of Participants"
  ) +
  see::theme_modern()
```

### Compute Scores

```{r}
dftask <- full_join(
  dftask, 
  df[c("Participant", "Sex", "SexualOrientation")],
  by = join_by(Participant)
  )

# Sexual relevance
dftask <- dftask |> 
  mutate(Relevance = case_when(
    Type == "Non-erotic" ~ "Non-erotic",
    Sex == "Male" & SexualOrientation == "Heterosexual" & Category == "Female" ~ "Relevant",
    Sex == "Female" & SexualOrientation == "Heterosexual" & Category == "Male" ~ "Relevant",
    Sex == "Male" & SexualOrientation == "Homosexual" & Category == "Male" ~ "Relevant",
    Sex == "Female" & SexualOrientation == "Homosexual" & Category == "Female" ~ "Relevant",
    # TODO: what to do with "Other"? 
    SexualOrientation %in% c("Bisexual", "Other") & Category %in% c("Male", "Female") ~ "Relevant",
    .default = "Irrelevant"
  )) 
```

## Feedback

### Evaluation

```{r}
df |> 
  select(starts_with("Feedback"), -Feedback_Comments) |>
  pivot_longer(everything(), names_to = "Question", values_to = "Answer") |>
  group_by(Question, Answer) |> 
  summarise(prop = n()/nrow(df), .groups = 'drop') |> 
  complete(Question, Answer, fill = list(prop = 0)) |> 
  filter(Answer == "True") |> 
  mutate(Question = str_remove(Question, "Feedback_"),
         Question = str_replace(Question, "AILessArousing", "AI = Less arousing"),
         Question = str_replace(Question, "AIMoreArousing", "AI = More arousing"),
         Question = str_replace(Question, "CouldNotDiscriminate", "Hard to discriminate"),
         Question = str_replace(Question, "LabelsIncorrect", "Labels were incorrect"),
         Question = str_replace(Question, "NoFeels", "Didn't feel anything"),
         Question = str_replace(Question, "CouldDiscriminate", "Easy to discriminate"),
         Question = str_replace(Question, "LabelsReversed", "Labels were reversed"),
         Question = fct_reorder(Question, desc(prop))) |>
  ggplot(aes(x = Question, y = prop)) +
  geom_bar(stat = "identity") +
  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks(), labels=scales::percent) +
  labs(x="Feedback", y = "Participants", title = "Feedback") +
  theme_modern(axis.title.space = 15) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(1.1), angle = 45, hjust = 1),
    axis.title.x = element_blank()
  )
```

### Comments

```{r}
data.frame(Comments = trimws(df$Feedback_Comments[df$Feedback_Comments != ""])) |> 
  filter(!Comments %in% c("No", "Nope", "nope", "None")) |> 
  knitr::kable()
```

## Exclusion

### Mobile

```{r}
df |>
  ggplot(aes(x=Mobile, fill=Mobile)) +
  geom_bar() +
  theme_modern()
```

We removed `r sum(df$Mobile=="True")` participants that participated with a mobile device.

```{r}
df <- filter(df, Mobile == "False")
dftask <- filter(dftask, Participant %in% df$Participant)
```

### Experiment Duration

```{r}
#| echo: true
#| code-fold: false

outliers <- c(
  # "S077", "S094",  # Low RT per item
  # "S107"  # Low BAIT duration
  )
```

```{r}
#| fig-width: 15
#| fig-height: 15

df |>
  mutate(Participant = fct_reorder(Participant, Experiment_Duration),
         Category = ifelse(Experiment_Duration > 60, "extra", "ok"),
         Duration = ifelse(Experiment_Duration > 60, 60, Experiment_Duration),
         Group = ifelse(Participant %in% outliers, "Outlier", "ok")) |>
  ggplot(aes(y = Participant, x = Duration)) +
  geom_point(aes(color = Group, shape = Category)) +
  geom_vline(xintercept = median(df$Experiment_Duration), color = "red", linetype = "dashed") +
  scale_shape_manual(values = c("extra" = 3, ok = 19)) +
  scale_color_manual(values = c("Outlier" = "red", ok = "black"), guide="none") +
  guides(color = "none", shape = "none") +
  ggside::geom_xsidedensity(fill = "#4CAF50", color=NA) +
  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
  labs(
    title = "Experiment Completion Time",
    x = "Duration (in minutes)",
    y = "Participant"
  )  +
  theme_bw() +
  ggside::theme_ggside_void() +
  theme(ggside.panel.scale = .3,
        panel.border = element_blank()) 
```

### Task Duration

```{r}
#| fig-width: 15
#| fig-height: 15

dftask |> 
  mutate(Participant = fct_reorder(Participant, RT1)) |> 
  filter(RT1 < 100) |> 
  ggplot(aes(x=RT1, fill=Participant)) +
  geom_histogram(bins=60) +
  coord_cartesian(xlim = c(0, 15)) +
  scale_fill_metro_d(guide="none") +
  theme_modern() +
  theme(axis.title.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        axis.line.y = element_blank()) +
  labs(title = "Distribution of Response Time for each Participant", x="Response time (for 3 scales) per item (s)") +
  facet_wrap(~Participant, ncol=5, scales="free_y")
```

### BAIT Questionnaire Duration

```{r}
#| fig-width: 15
#| fig-height: 15

df |>
  mutate(Participant = fct_reorder(Participant, BAIT_Duration),
         Category = ifelse(BAIT_Duration > 5, "extra", "ok"),
         Duration = ifelse(BAIT_Duration > 5, 5, BAIT_Duration),
         Group = ifelse(Participant %in% outliers, "Outlier", "ok")) |>
  ggplot(aes(y = Participant, x = Duration)) +
  geom_point(aes(color = Group, shape = Category)) +
  geom_vline(xintercept = median(df$BAIT_Duration), color = "red", linetype = "dashed") +
  scale_shape_manual(values = c("extra" = 3, ok = 19)) +
  scale_color_manual(values = c("Outlier" = "red", ok = "black"), guide="none") +
  guides(color = "none", shape = "none") +
  ggside::geom_xsidedensity(fill = "#9C27B0", color=NA) +
  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
  labs(
    title = "Questionnaire Completion Time",
    x = "Duration (in minutes)",
    y = "Participant"
  )  +
  theme_bw() +
  ggside::theme_ggside_void() +
  theme(ggside.panel.scale = .3,
        panel.border = element_blank()) 
```

### Response to Erotic Stimuli

```{r}
#| fig-width: 15
#| fig-height: 15

dftask |> 
  group_by(Participant, Type) |> 
  summarise(Arousal = mean(Arousal), 
            Valence = mean(Valence),
            Enticement = mean(Enticement),
            .groups = "drop") |>
  pivot_wider(names_from = Type, values_from = all_of(c("Arousal", "Valence", "Enticement"))) |>
  transmute(Participant = Participant,
            d_Arousal = Arousal_Erotic - `Arousal_Non-erotic`,
            d_Valence = Valence_Erotic - `Valence_Non-erotic`,
            d_Enticement = Enticement_Erotic - `Enticement_Non-erotic`) |>
  mutate(Participant = fct_reorder(Participant, d_Arousal)) |> 
  pivot_longer(-Participant) |> 
  mutate(Group = ifelse(Participant %in% outliers, "Outlier", "ok")) |> 
  ggplot(aes(x=value, y=Participant, fill=Group)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = c("Outlier" = "red", ok = "black"), guide="none") +
  theme_bw() +
  labs(title = "Difference between Erotic and Neutral", x="Erotic - Neutral") +
  facet_wrap(~name, ncol=3, scales="free_x")
```

### Sexual Profile

```{r}
df |>
  ggplot(aes(x = Sex)) +
  geom_bar(aes(fill = SexualOrientation)) +
  scale_y_continuous(expand = c(0, 0), breaks = scales::pretty_breaks()) +
  scale_fill_metro_d() +
  labs(x = "Biological Sex", y = "Number of Participants", title = "Sex and Sexual Orientation", fill = "Sexual Orientation") +
  theme_modern(axis.title.space = 15) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(1.1)),
    axis.title.x = element_blank()
  )
```

We removed `r sum(df$Sex=="Other" | df$SexualOrientation=="Other")` participants that were incompatible with further analysis.

```{r}
df <- filter(df, Sex != "Other" & SexualOrientation != "Other")
dftask <- filter(dftask, Participant %in% df$Participant)
```

## Final Sample

```{r}
df <- filter(df, !Participant %in% outliers)
dftask <- filter(dftask, Participant %in% df$Participant)
```

### Country of Origin

```{r p_demographics_country}
p_country <- dplyr::select(df, region = Country) |>
  group_by(region) |>
  summarize(n = n()) |>
  right_join(map_data("world"), by = "region") |>
  ggplot(aes(long, lat, group = group)) +
  geom_polygon(aes(fill = n)) +
  scale_fill_gradientn(colors = c("#FFEB3B", "red", "purple")) +
  labs(fill = "N") +
  theme_void() +
  labs(title = "A Geographically Diverse Sample", subtitle = "Number of participants by country")  +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2))
  )
p_country
```

### Age

```{r p_demographics_age}
p_age <- estimate_density(df$Age) |>
  normalize(select = y) |> 
  mutate(y = y * 86) |>  # To match the binwidth
  ggplot(aes(x = x)) +
  geom_histogram(data=df, aes(x = Age), fill = "#616161", bins=28) +
  # geom_line(aes(y = y), color = "orange", linewidth=2) +
  geom_vline(xintercept = mean(df$Age), color = "red", linewidth=1.5) +
  # geom_label(data = data.frame(x = mean(df$Age) * 1.15, y = 0.95 * 75), aes(y = y), color = "red", label = paste0("Mean = ", format_value(mean(df$Age)))) +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(title = "Age", y = "Number of Participants", color = NULL, subtitle = "Distribution of participants' age") +
  theme_modern(axis.title.space = 10) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(1.1)),
    axis.title.x = element_blank()
  )
p_age
```

<!-- ## Ethnicity -->

<!-- ```{r p_demographics_ethnicity} -->
<!-- plot_waffle <- function(sub, what = "Nationality", title = what, rows = 8, size = 3) { -->
<!--   ggwaffle::waffle_iron(sub, what, rows = rows) |> -->
<!--     ggplot(aes(x, y)) + -->
<!--     geom_point(aes(color = group), shape = "square", size = size) + -->
<!--     coord_equal() + -->
<!--     ggtitle(title) + -->
<!--     labs(fill = "", color = "", subtitle = "N participants per self-declared group") + # (each square represents one participant)" -->
<!--     theme_void() + -->
<!--     theme( -->
<!--       plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0), -->
<!--       plot.subtitle = element_text(size = rel(1.2)), -->
<!--       legend.key.height = unit(1, "mm"), -->
<!--       legend.key.width = unit(1, "mm") -->
<!--     ) -->
<!-- } -->

<!-- p_ethni <- plot_waffle(sub, "Ethnicity", rows = 20, size = 8) + -->
<!--   scale_color_manual(values = c("Hispanic" = "#FF5722", "Caucasian" = "#2196F3", "African" = "#4CAF50", "Asian" = "#FFC107", "Other" = "#795548")) -->
<!-- p_ethni -->
<!-- ``` -->

### Education

```{r p_demographics_education}
p_edu <- df |>
  mutate(Education = fct_relevel(Education, "Other", "High School", "Bachelor", "Master", "Doctorate")) |> 
  ggplot(aes(x = Education)) +
  geom_bar(aes(fill = Education)) +
  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
  scale_fill_viridis_d(guide = "none") +
  labs(title = "Education", y = "Number of Participants", subtitle = "Participants per achieved education level") +
  theme_modern(axis.title.space = 15) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(1.1)),
    axis.title.x = element_blank()
  )
p_edu
```

### Sex

#### Birth Control

```{r p_demographics_sex}
colors <- c(
  "NA" = "#2196F3", "No" = "#E91E63", "Condoms (for partner)" = "#9C27B0",
  "Combined pills" = "#FF9800", "Intrauterine Device (IUD)" = "#FF5722", 
  "Intrauterine System (IUS)" = "#795548"
)
colors <- colors[names(colors) %in% c("NA", df$BirthControl)]

p_sex <- df |>
  mutate(BirthControl = ifelse(Sex == "Male", "NA", BirthControl),
         BirthControl = fct_relevel(BirthControl, names(colors))) |>
  ggplot(aes(x = Sex)) +
  geom_bar(aes(fill = BirthControl)) +
  scale_y_continuous(expand = c(0, 0), breaks = scales::pretty_breaks()) +
  scale_fill_manual(
    values = colors,
    breaks = names(colors)[2:length(colors)]
  ) +
  labs(x = "Biological Sex", y = "Number of Participants", title = "Sex and Birth Control Method", fill = "Birth Control") +
  theme_modern(axis.title.space = 15) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(1.1)),
    axis.title.x = element_blank()
  )
p_sex
```

#### Sexual Orientation and Activity

```{r p_demographics_sexorient}
p_sexorient <- df |>
  ggplot(aes(x = SexualOrientation)) +
  geom_bar() +
  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
  labs(x = "Sexual Orientation", y = "Number of Participants", title = "Sexual Orientation") +
  theme_modern(axis.title.space = 15) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(1.1)),
    axis.title.x = element_blank()
  )
p_sexorient
```

```{r p_demographics_sexactivity}
p_sexactivity <- df |>
  ggplot(aes(x = SexualActivity)) +
  geom_bar() +
  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
  labs(x = "Last Sexual Activity", y = "Number of Participants", title = "Time of Last Sexual Activity") +
  theme_modern(axis.title.space = 15) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(1.1), angle = 45, hjust = 1),
    axis.title.x = element_blank()
  )
p_sexactivity
```

### English and AI-Expertise

```{r p_demographics_expertise}
p_language <- df |>
  ggplot(aes(x = Language_Level)) +
  geom_bar() +
  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
  labs(x = "Level", y = "Number of Participants", title = "Language Level") +
  theme_modern(axis.title.space = 15) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(1.1))
  )

p_expertise <- df |>
  ggplot(aes(x = AI_Knowledge)) +
  geom_bar() +
  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
  labs(x = "Level", y = "Number of Participants", title = "AI-Expertise") +
  theme_modern(axis.title.space = 15) +
  theme(
    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
    axis.text.y = element_text(size = rel(1.1)),
    axis.text.x = element_text(size = rel(1.1))
  )

p_language | p_expertise
```

### Summary

The final sample includes `r report::report_participants(df, age="Age", sex="Sex", education="Education")`.

```{r p_summary}
#| fig-width: 15
#| fig-height: 15

p_country /
  (p_age + p_edu)
```

## Save

```{r}
#| code-fold: false

write.csv(df, "../data/data_participants.csv", row.names = FALSE)
write.csv(dftask, "../data/data.csv", row.names = FALSE)
```

### 2024-01-25 analysis/1_intraindividual.qmd
preprocessing script

---
title: "FictionEro - Analysis (1)"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: true
    toc: true
---

## Data Preparation

```{r}
#| message: false
#| warning: false

library(tidyverse)
library(easystats)
library(patchwork)
library(ggside)
library(glmmTMB)
```

```{r}
dfsub <- read.csv("../data/data_participants.csv")
df <- read.csv("../data/data.csv") |> 
  datawizard::rescale(select=c("Arousal", "Enticement", "Realness"), range=c(0, 1), to=c(0.001, 0.999)) |> 
  datawizard::rescale(select=c("Valence"), range=c(-1, 1), to=c(0.001, 0.999)) |> 
  mutate(Condition = fct_relevel(Condition, "Photograph", "AI-Generated"),
         Relevance =  fct_relevel(Relevance, "Relevant", "Irrelevant", "Non-erotic"))

results_table <- function(model, effects="fixed") {
  display(parameters::parameters(model, effects=effects))
}
```

## Manipulation Check

### Neutral vs. Emotional

```{r}
prior_intercept <- rstanarm::default_prior_intercept(mgcv::betar)
prior_intercept$default <- FALSE
prior_intercept$location <- 0.90
prior_intercept$scale <- 0.30
prior_intercept$autoscale <- FALSE
m <- rstanarm::stan_glmer(Arousal ~ Relevance + (1|Participant) + (1|Item), data=df, family=mgcv::betar, 
                          algorithm = "sampling", 
                          prior_intercept = prior_intercept)
results_table(m)

marginaleffects::predictions(m, by="Relevance", newdata = "marginalmeans") |> 
  as.data.frame()

m <- glmmTMB::glmmTMB(Arousal ~ Relevance + (1|Participant) + (1|Item), data=df, family=beta_family(link = "logit"))
results_table(m)

marginaleffects::predictions(m, 
                             newdata = insight::get_datagrid(m), 
                             vcov=vcov(m)$cond)
```

## Arousal

```{r}
plot_descriptive <- function(df, target="Arousal") {
  # By item
  p1 <- df |> 
    mutate(.average = mean(.data[[target]]), .by="Item") |>
    mutate(Item = fct_reorder(Item, .average)) |>
    ggplot(aes(y = Item, x=.data[[target]])) +
    ggdist::stat_slabinterval(aes(fill=Condition, color=Condition), .width=0.95) +
    scale_color_manual(values=c("AI-Generated"="#F44336", "Photograph"="#2196F3")) +
    scale_fill_manual(values=c("AI-Generated"="#F44336", "Photograph"="#2196F3")) +
    theme_modern() +
    theme(panel.grid.major.y = element_line(color = "grey"),
          panel.border = element_blank(),
          axis.line.x = element_blank(),
          axis.title.y = element_blank()) +
    labs(title = paste0(target, " by Item")) +
    facet_grid(~Sex)

  # By participant
  p2 <- df |> 
    mutate(.average = mean(.data[[target]]), .by="Participant") |>
    mutate(Participant = fct_reorder(Participant, .average)) |>
    ggplot(aes(y = Participant, x=.data[[target]])) +
    ggdist::stat_slabinterval(aes(fill=Condition, color=Condition), 
                              .width=0.95, slab_alpha=0.6, density="histogram", normalize="xy") +
    scale_color_manual(values=c("AI-Generated"="#F44336", "Photograph"="#2196F3")) +
    scale_fill_manual(values=c("AI-Generated"="#F44336", "Photograph"="#2196F3")) +
    theme_modern() +
    theme(panel.grid.major.y = element_line(color = "grey"),
          panel.border = element_blank(),
          axis.line.x = element_blank(),
          axis.title.y = element_blank()) +
    labs(title = paste0(target, " by Participant")) +
    facet_wrap(~Sex, ncol=2, scales="free_y")

  p1 / p2
}

plot_descriptive(df, "Arousal")

m <- glmmTMB::glmmTMB(Arousal ~ Relevance / Condition + (1|Participant) + (1|Item), data=df, family=beta_family(link = "logit"))
results_table(m)
m <- glmmTMB::glmmTMB(Valence ~ Relevance / Condition + (1|Participant) + (1|Item), data=df, family=beta_family(link = "logit"))
results_table(m)
m <- glmmTMB::glmmTMB(Enticement ~ Relevance / Condition + (1|Participant) + (1|Item), data=df, family=beta_family(link = "logit"))
results_table(m)
m <- glmmTMB::glmmTMB(Realness ~ Relevance / Condition + (1|Participant) + (1|Item), data=df, family=beta_family(link = "logit"))
results_table(m)
```

```{r}
ggplot(df, aes(x=Norms_Arousal, y=Arousal, color=Condition)) +
  geom_point() +
  geom_smooth() +
  facet_grid(~Sex)
```

## Realness

```{r}
m <- glmmTMB::glmmTMB(Realness ~ Entropy + Complexity + Contrast + Luminance + (1|Participant) + (1|Item), data=df, family=beta_family(link = "logit"))
m <- glmmTMB::glmmTMB(Realness ~ Entropy + Complexity + Contrast + Luminance + (1|Participant) + (1|Item), data=df)
results_table(m)
```

### 2024-01-25 analysis/0_preprocessing.py

@@ -33,7 +33,7 @@ token = ""  # Paste OSF token here to access private repositories
 files = osf_listfiles(
     token=token,
     data_subproject="sm4jc",  # Data subproject ID
-    after_date="17/01/2024",
+    after_date="19/01/2024",
 )
 
 
@@ -41,6 +41,16 @@ files = osf_listfiles(
 # Initialize empty dataframes
 alldata = pd.DataFrame()
 alldata_subs = pd.DataFrame()
+norm_data = pd.read_csv("../experiment/stimuli_selection/stimuli_data.csv").rename(
+    columns={
+        "ID": "Item",
+        "JPEG_size80": "Complexity",
+        "LABA": "Red",
+        "LABB": "Green",
+        "Luminance": "Luminance2",
+        "LABL": "Luminance",
+    }
+)
 
 for i, file in enumerate(files):
     print(f"File N°{i+1}/{len(files)}")
@@ -53,10 +63,17 @@ for i, file in enumerate(files):
     # Browser info -------------------------------------------------------
     brower = data[data["screen"] == "browser_info"].iloc[0]
 
+    # Experimenter
+    experimenter = brower["researcher"]
+    if experimenter == "TEST":
+        continue
+    if isinstance(experimenter, float):
+        experimenter = "Experimenter" + str(int(experimenter))
+
     df = pd.DataFrame(
         {
             "Participant": file["name"],
-            "Experimenter": str(brower["researcher"]),
+            "Experimenter": experimenter,
             "Experiment_Duration": data["time_elapsed"].max() / 1000 / 60,
             "Language": brower["language"],
             "Date": brower["date"],
@@ -89,14 +106,56 @@ for i, file in enumerate(files):
     edu = "Bachelor" if "bachelor" in edu else edu
     edu = "Master" if "master" in edu else edu
     edu = "Doctorate" if "doctorate" in edu else edu
+    edu = "High School" if "High school" in edu else edu
     df["Education"] = edu
+
+    # Country
+    country = demo2["Country"].title().rstrip()
+    country = "UK" if country in ["Uk", "England"] else country
+    country = "Pakistan" if country in ["Pk"] else country
+    country = (
+        "USA"
+        if country
+        in [
+            "USa",
+            "Usa",
+            "U.S.",
+            "United States",
+            "United States Of America",
+            "Us,Texas",
+            "Us",
+        ]
+        else country
+    )
+    country = np.nan if country in ["", "Na"] else country
[…]

### 2024-01-26 analysis/1_cleaning.qmd
stabilize re-ordering of participants and update data

@@
 ```{r}
+#| code-fold: false
+
 df <- read.csv("../data/rawdata_participants.csv")
@@
 data.frame(Comments = trimws(df$Feedback_Comments[df$Feedback_Comments != ""])) |> 
-  filter(!Comments %in% c("No", "Nope", "nope", "None")) |> 
+  filter(!Comments %in% c("No", "Nope", "nope", "None", "ba")) |> 
   knitr::kable()
@@
 ## Exclusion
+
+```{r}
+#| echo: true
+#| code-fold: false
+
+outliers <- c(
+  # "S077", "S094",  # Low RT per item
+  # "S107"  # Low BAIT duration
+  )
+```
 
@@
 ### Experiment Duration
-
-```{r}
-#| echo: true
-#| code-fold: false
-
-outliers <- c(
-  # "S077", "S094",  # Low RT per item
-  # "S107"  # Low BAIT duration
-  )
-```
 
@@
 dftask |> 
+  filter(Relevance %in% c("Relevant", "Non-erotic")) |> 
   group_by(Participant, Type) |> 
@@
             d_Enticement = Enticement_Erotic - `Enticement_Non-erotic`) |>
+  filter(!is.na(d_Arousal)) |> 
   mutate(Participant = fct_reorder(Participant, d_Arousal)) |> 
@@
 p_sexorient <- df |>
-  ggplot(aes(x = SexualOrientation)) +
+  ggplot(aes(x = SexualOrientation, fill=Sex)) +
   geom_bar() +
   scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
+  scale_fill_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292")) +
   labs(x = "Sexual Orientation", y = "Number of Participants", title = "Sexual Orientation") +
@@
 p_sexactivity <- df |>
-  ggplot(aes(x = SexualActivity)) +
+  ggplot(aes(x = SexualActivity, fill=Sex)) +
   geom_bar() +
   scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
+  scale_fill_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292")) +
   labs(x = "Last Sexual Activity", y = "Number of Participants", title = "Time of Last Sexual Activity") +

### 2024-01-26 analysis/0_preprocessing.py

@@ -36,7 +36,6 @@ files = osf_listfiles(
     after_date="19/01/2024",
 )
 
-
 # Loop through files ======================================================
 # Initialize empty dataframes
 alldata = pd.DataFrame()
@@ -70,6 +69,7 @@ for i, file in enumerate(files):
     if isinstance(experimenter, float):
         experimenter = "Experimenter" + str(int(experimenter))
 
+    file["date"]
     df = pd.DataFrame(
         {
             "Participant": file["name"],
@@ -78,6 +78,7 @@ for i, file in enumerate(files):
             "Language": brower["language"],
             "Date": brower["date"],
             "Time": brower["time"],
+            "Date_OSF": file["date"],
             "Browser": brower["browser"],
             "Mobile": brower["mobile"],
             "Platform": brower["os"],
@@ -134,13 +135,35 @@ for i, file in enumerate(files):
     race = demo2["Ethnicity"].title().rstrip()
     race = (
         "Caucasian"
-        if race in ["White", "Norwegian", "European", "White Australian"]
+        if race
+        in [
+            "White",
+            "Norwegian",
+            "European",
+            "White Australian",
+            "Scandinavian",
+            "Latin White",
+            "White Caucasian",
+            "Causcian",
+            "Mediterranean",
+            "Romanian",
+            "Polish",
+            "Mediterranian Caucasian",
+            "White/European Descent",
+        ]
         else race
     )
     race = "Asian" if race in ["Southeast Asian", "East Asian", "Chinese"] else race
-    race = "Hispanic" if race in ["Latino", "Latin"] else race
-    race = "Black" if race in ["Black African"] else race
-    race = np.nan if race in [""] else race
+    race = "Hispanic" if race in ["Latino", "Latin", "Mexican"] else race
+    race = "South Asian" if race in ["Indian", "Brown"] else race
+    race = "Black" if race in ["Black African", "African American"] else race
+    race = (
+        "Mixed"
+        if race in ["Latin American X Asian", "White, Hispanic", "White/Arabic"]
+        else race
+    )
+    race = "Other" if race in ["Native American"] else race
+    race = np.nan if race in ["", "Na", "Human"] else race
     df["Ethnicity"] = race
 
     # Female questions
@@ -304,10 +327,11 @@ alldata["Item"] = alldata["Item"].str.replace(".jpg", "")
[…]

### 2024-01-31 experiment/instructions_french.js
add French version

@@ -1,0 +1,362 @@
+// =========================================================================================
+// Parameters
+// =========================================================================================
+function shuffleArray(array) {
+    for (let i = array.length - 1; i > 0; i--) {
+        const j = Math.floor(Math.random() * (i + 1))
+        ;[array[i], array[j]] = [array[j], array[i]]
+    }
+    return array
+}
+
+var color_cues = shuffleArray(["red", "blue", "green"])
+color_cues = { Reality: color_cues[0], Fiction: color_cues[1] }
+// =========================================================================================
+// Fiction
+// =========================================================================================
+var text_instructions1 =
+    "<h1>Instructions</h1>" +
+    // Left aligned text
+    "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>Dans cette étude, nous visons à valider notre <b> nouvel algorithme de génération d'images </b> (basé sur une nouvelle forme de technologie Generative Adversarial Network - GAN) entraîné pour produire du contenu érotique (mais aussi non érotique) de haute qualité.</p>" +
+    "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>Dans la tâche suivante, on vous présentera des images érotiques et non érotiques générées par notre algorithme (précédées de l'étiquette '<b style='color:" +
+    color_cues["Fiction"] +
+    "'>generée pa l'IA</b>'), mélangées à des photos réelles (précédées de l'étiquette  '<b style='color:" +
+    color_cues["Reality"] +
+    "'>Photographie</b>') tirées de bases de données d'images publiques.</p > " +
+    "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>Après chaque image, vous devrez l'évaluer sur les échelles suivantes :</p>" +
+    "<ul style='text-align: left; margin-left: 30%; margin-right: 30%;'>" +
+    // Arousal: embodied
+    "<li><b>Excitation</b>: Dans quelle mesure trouvez-vous l'image sexuellement excitante ? Cette question porte sur votre <i> réaction personnelle </i> ressentie dans votre corps à la vue de l'image.</li>" +
+    // Appeal: "objective"
[…]

### 2024-01-31 analysis/1_cleaning.qmd
update cleaning

--- 2024-01-25 analysis/1_cleaning.qmd
@@
 ```{r}
+#| code-fold: false
+
 df <- read.csv("../data/rawdata_participants.csv")
-dftask <- read.csv("../data/rawdata_task.csv")
+dftask <- read.csv("../data/rawdata_task.csv") |> 
+  full_join(
+    df[c("Participant", "Sex", "SexualOrientation")],
+    by = join_by(Participant)
+    )
 ```
@@
 The initial sample consisted of `r report::report_participants(df, age="Age", sex="Sex", education="Education")`.
+
+### Compute Scores
+
+```{r}
+#| code-fold: false
+
+# Create Sexual "relevance" variable (Relevant, irrelevant, non-erotic)
+dftask <- dftask |> 
+  mutate(Relevance = case_when(
+    Type == "Non-erotic" ~ "Non-erotic",
+    Sex == "Male" & SexualOrientation == "Heterosexual" & Category == "Female" ~ "Relevant",
+    Sex == "Female" & SexualOrientation == "Heterosexual" & Category == "Male" ~ "Relevant",
+    Sex == "Male" & SexualOrientation == "Homosexual" & Category == "Male" ~ "Relevant",
+    Sex == "Female" & SexualOrientation == "Homosexual" & Category == "Female" ~ "Relevant",
+    # TODO: what to do with "Other"? 
+    SexualOrientation %in% c("Bisexual", "Other") & Category %in% c("Male", "Female") ~ "Relevant",
+    .default = "Irrelevant"
+  )) 
+```
 
@@
   ungroup() |>
+  # https://bocoup.com/blog/padding-time-series-with-r
   complete(Date, Experimenter, fill = list(N = 0)) |> 
@@
   see::theme_modern()
-```
-
-### Compute Scores
-
-```{r}
-dftask <- full_join(
-  dftask, 
-  df[c("Participant", "Sex", "SexualOrientation")],
-  by = join_by(Participant)
-  )
-
-# Sexual relevance
-dftask <- dftask |> 
-  mutate(Relevance = case_when(
-    Type == "Non-erotic" ~ "Non-erotic",
-    Sex == "Male" & SexualOrientation == "Heterosexual" & Category == "Female" ~ "Relevant",
-    Sex == "Female" & SexualOrientation == "Heterosexual" & Category == "Male" ~ "Relevant",
-    Sex == "Male" & SexualOrientation == "Homosexual" & Category == "Male" ~ "Relevant",
-    Sex == "Female" & SexualOrientation == "Homosexual" & Category == "Female" ~ "Relevant",
-    # TODO: what to do with "Other"? 
-    SexualOrientation %in% c("Bisexual", "Other") & Category %in% c("Male", "Female") ~ "Relevant",
-    .default = "Irrelevant"
-  )) 
 ```
@@
 ```{r}
-data.frame(Comments = trimws(df$Feedback_Comments[df$Feedback_Comments != ""])) |> 
-  filter(!Comments %in% c("No", "Nope", "nope", "None")) |> 
-  knitr::kable()
+data.frame(Source = df$Experimenter,
+           Comments = trimws(df$Feedback_Comments)) |> 
+  filter(!Comments %in% c("", "No", "Nope", "nope", "None", "na")) |> 
+  gt::gt() |> 
+  gt::opt_stylize() |> 
+  gt::opt_interactive(use_compact_mode = TRUE) 
 ```
@@
   transmute(Participant = Participant,
-            d_Arousal = Arousal_Erotic - `Arousal_Non-erotic`,
-            d_Valence = Valence_Erotic - `Valence_Non-erotic`,
-            d_Enticement = Enticement_Erotic - `Enticement_Non-erotic`) |>
-  mutate(Participant = fct_reorder(Participant, d_Arousal)) |> 
+            Arousal = Arousal_Erotic - `Arousal_Non-erotic`,
+            Valence = Valence_Erotic - `Valence_Non-erotic`,
+            Enticement = Enticement_Erotic - `Enticement_Non-erotic`) |>
+  filter(!is.na(Arousal)) |> 
+  mutate(Participant = fct_reorder(Participant, Arousal)) |> 
   pivot_longer(-Participant) |> 
   mutate(Group = ifelse(Participant %in% outliers, "Outlier", "ok")) |> 
-  ggplot(aes(x=value, y=Participant, fill=Group)) +
+  ggplot(aes(x=value, y=Participant, fill=value)) +
   geom_bar(stat = "identity") +
-  scale_fill_manual(values = c("Outlier" = "red", ok = "black"), guide="none") +
+  scale_fill_gradient2(low = "#3F51B5", mid = "#FF9800", high = "#4CAF50", midpoint = 0) +
+  # scale_fill_manual(values = c("Outlier" = "red", ok = "black"), guide="none") +
   theme_bw() +
@@
 ```{r}
+#| code-fold: false
+
 df <- filter(df, Sex != "Other" & SexualOrientation != "Other")
@@
 
-#### Sexual Orientation and Activity
+#### Sexual Profile
 
-```{r p_demographics_sexorient}
-p_sexorient <- df |>
-  ggplot(aes(x = SexualOrientation)) +
+```{r p_demographics_sexprofile}
+#| fig-width: 14
+#| fig-height: 14
+
+p_sexprofile <- df |>
+  select(Participant, Sex, SexualOrientation, SexualActivity, COPS_Duration_1, COPS_Frequency_2) |> 
+  pivot_longer(-all_of(c("Participant", "Sex"))) |> 
+  mutate(name = str_replace_all(name, "SexualOrientation", "Sexual Orientation"),
+         name = str_replace_all(name, "SexualActivity", "Sexual Activity"),
+         name = str_replace_all(name, "COPS_Duration_1", "Pornography Usage (Duration)"),
+         name = str_replace_all(name, "COPS_Frequency_2", "Pornography Usage (Frequency)")) |> 
+  ggplot(aes(x = value, fill=Sex)) +
   geom_bar() +
   scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
-  labs(x = "Sexual Orientation", y = "Number of Participants", title = "Sexual Orientation") +
-  theme_modern(axis.title.space = 15) +
-  theme(
-    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
-    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
-    axis.text.y = element_text(size = rel(1.1)),
-    axis.text.x = element_text(size = rel(1.1)),
-    axis.title.x = element_blank()
-  )
-p_sexorient
-```
-
-```{r p_demographics_sexactivity}
-p_sexactivity <- df |>
-  ggplot(aes(x = SexualActivity)) +
-  geom_bar() +
-  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
-  labs(x = "Last Sexual Activity", y = "Number of Participants", title = "Time of Last Sexual Activity") +
+  scale_fill_manual(values = c("Male"= "#64B5F6", "Female"= "#F06292")) +
+  labs(title = "Sexual Profile of Participants") +
   theme_modern(axis.title.space = 15) +
@@
     axis.text.x = element_text(size = rel(1.1), angle = 45, hjust = 1),
-    axis.title.x = element_blank()
-  )
-p_sexactivity
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()
+  ) +
+  facet_wrap(~name, scales = "free")
+p_sexprofile
 ```

### 2024-02-04 analysis/1_cleaning.qmd
preprocessing

@@
 
-df <- read.csv("../data/rawdata_participants.csv")
+df <- read.csv("../data/rawdata_participants.csv") |> 
+  mutate(across(everything(), ~ifelse(.x == "", NA, .x))) 
 dftask <- read.csv("../data/rawdata_task.csv") |> 
@@
   mutate(Date = as.Date(Date, format = "%d/%m/%Y")) |> 
-  group_by(Date, Experimenter) |> 
+  group_by(Date, Language, Experimenter) |> 
   summarize(N = n()) |> 
@@
   # https://bocoup.com/blog/padding-time-series-with-r
-  complete(Date, Experimenter, fill = list(N = 0)) |> 
-  group_by(Experimenter) |>
+  complete(Date, Language, Experimenter, fill = list(N = 0)) |> 
+  group_by(Language, Experimenter) |>
   mutate(N = cumsum(N)) |>
@@
   ) +
+  facet_wrap(~Language, nrow=2) +
   see::theme_modern()
+
 ```
@@
 ```{r}
-data.frame(Source = df$Experimenter,
+data.frame(Language = df$Language,
+           Source = df$Experimenter,
            Comments = trimws(df$Feedback_Comments)) |> 
   filter(!Comments %in% c("", "No", "Nope", "nope", "None", "na")) |> 
+  arrange(Language, Source) |>
   gt::gt() |> 
@@
   geom_bar() +
+  geom_hline(yintercept=nrow(df)/2, linetype="dashed") +
   theme_modern()
@@
 ### Experiment Duration
+
+The experiment's median duration is `r insight::format_value(median(df$Experiment_Duration))` min (`r print(bayestestR::hdi(df$Experiment_Duration, ci=0.5))`).
 
@@
 ```{r}
-#| fig-width: 15
-#| fig-height: 15
-
-dftask |> 
+plot_hist <- function(dat) {
+  dat |> 
     mutate(Participant = fct_reorder(Participant, RT1)) |> 
@@
     ggplot(aes(x=RT1, fill=Participant)) +
-  geom_histogram(bins=60) +
+    geom_histogram(bins=140) +
     coord_cartesian(xlim = c(0, 15)) +
@@
           axis.line.y = element_blank()) +
-  labs(title = "Distribution of Response Time for each Participant", x="Response time (for 3 scales) per item (s)") +
+    labs(title = "Distribution of Response Time for each Participant", x="Response time (for 3 scales) per stimuli (s)") +
     facet_wrap(~Participant, ncol=5, scales="free_y")
+}
 ```
+
+::: {.panel-tabset}
+
+#### 1-60
+
+```{r}
+#| fig-width: 15
+#| fig-height: 15
+
+plot_hist(dftask[dftask$Participant %in% df$Participant[1:60], ])
+```
+
+#### 61-120
+
+```{r}
+#| fig-width: 15
+#| fig-height: 15
+
+plot_hist(dftask[dftask$Participant %in% df$Participant[61:120], ])
+```
+
+:::
 
@@
   theme_bw() +
+  theme(axis.text.y = element_blank(),
+        axis.ticks.y = element_blank()) +
   labs(title = "Difference between Erotic and Neutral", x="Erotic - Neutral") +
@@
 ### Sexual Profile
+
+#### Sample
 
@@
 
+#### Task Behaviour
+
+```{r}
+#| fig-width: 13
+#| fig-height: 13
+#| warning: false
+
+show_distribution <- function(dftask, target="Arousal") {
+  dftask |> 
+    filter(SexualOrientation %in% c("Heterosexual", "Bisexual", "Homosexual")) |>
+    bayestestR::estimate_density(select=target, 
+                                 at=c("Relevance", "Category", "Sex", "SexualOrientation"), 
+                                 method="KernSmooth") |>
+    ggplot(aes(x = x, y = y)) +
+    geom_line(aes(color = Relevance, linetype = Category)) +
+    facet_grid(SexualOrientation~Sex)  +
+    scale_color_manual(values = c("Relevant" = "red", "Non-erotic" = "blue", "Irrelevant"="orange")) +
+    scale_y_continuous(expand = c(0, 0)) +
+    scale_x_continuous(expand = c(0, 0)) +
+    theme_minimal()  +
+    theme(axis.title.x = element_blank(),
+          axis.title.y = element_blank(),
+          axis.text.y = element_blank(),
+          plot.title = element_text(face="bold")) +
+    labs(title = target) 
+}
+
+(show_distribution(dftask, "Arousal") | show_distribution(dftask, "Valence")) /
+  (show_distribution(dftask, "Enticement") | show_distribution(dftask, "Realness")) +
+  patchwork::plot_layout(guides = "collect") +
+  patchwork::plot_annotation(title = "Distribution of Appraisals depending on the Sexual Profile",
+                             theme = theme(plot.title = element_text(hjust = 0.5, face="bold"))) 
+```
+
+We kept only heterosexual participants (`r insight::format_percent(sum(df$SexualOrientation == "Heterosexual") / nrow(df))`).
+
+```{r}
+#| code-fold: false
+
+df <- filter(df, SexualOrientation == "Heterosexual")
+dftask <- filter(dftask, Participant %in% df$Participant)
+```
+
 ## Final Sample
@@
 
-### Country of Origin
+::: {.panel-tabset}
+
+### Summary
+
+The final sample includes `r report::report_participants(df, age="Age", sex="Sex", education="Education")`.
+
+### Origin
 
@@
 p_country
+```
+
+```{r p_ethnicity}
+ggwaffle::waffle_iron(df, ggwaffle::aes_d(group = Ethnicity), rows=10) |> 
+  ggplot(aes(x, y, fill = group)) + 
+  ggwaffle::geom_waffle() + 
+  coord_equal() + 
+  scale_fill_flat_d() + 
+  ggwaffle::theme_waffle() +
+  labs(title = "Self-reported Ethnicity", subtitle = "Each square represents a participant", fill="")  +
+  theme(
+    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
+    plot.subtitle = element_text(size = rel(1.2)),
+    axis.title.x = element_blank(),
+    axis.title.y = element_blank()
+  )
 ```
@@
 
-### English and AI-Expertise
+### Expertise
 
@@
 
-### Summary
-
-The final sample includes `r report::report_participants(df, age="Age", sex="Sex", education="Education")`.
+:::
 
@@
 
+## Beliefs about Artificial Information Technology (BAIT)
+
+This section pertains to the validation of the BAIT scale measuring beliefs and expectations about artificial creations.
+
+::: {.panel-tabset}
+
+### Structure
+
+#### Exploratory Factor Analysis
+
+```{r}
+bait <- df |> 
+  select(starts_with("BAIT_"), -BAIT_Duration)
+
+cor <- correlation::correlation(bait, redundant = TRUE) |> 
+  correlation::cor_sort() |> 
+  correlation::cor_lower()
+
+clean_labels <- function(x) {
+  x <- str_remove_all(x, "BAIT_") |> 
+    str_replace_all("_", " - ")
+}
+
+cor |> 
+  mutate(val = paste0(insight::format_value(r), format_p(p, stars_only=TRUE))) |>
+  mutate(Parameter2 = fct_rev(Parameter2)) |>
+  mutate(Parameter1 = fct_relabel(Parameter1, clean_labels),
+         Parameter2 = fct_relabel(Parameter2, clean_labels)) |> 
+  ggplot(aes(x=Parameter1, y=Parameter2)) +
+  geom_tile(aes(fill = r), color = "white") +
+  geom_text(aes(label = val), size = 3) +
+  labs(title = "Correlation Matrix",
+       subtitle = "Beliefs about Artificial Information Technology (BAIT)") +
+  scale_fill_gradient2(
+    low = "#2196F3",
+    mid = "white",
+    high = "#F44336",
+    breaks = c(-1, 0, 1),
+    guide = guide_colourbar(ticks=FALSE),
+    midpoint = 0,
+    na.value = "grey85",
+    limit = c(-1, 1))  + 
+  theme_minimal() +
+  theme(legend.title = element_blank(),
+        axis.title.x = element_blank(),
+        axis.title.y = element_blank(),
+        axis.text.x = element_text(angle = 45, hjust = 1))
+```
+
+```{r}
+#| message: false
+
+# n <- parameters::n_factors(bait, type="FA")  
+# plot(n)
+
+efa <- parameters::factor_analysis(bait, cor=cor(bait), n=2, rotation = "oblimin", sort=TRUE, scores="tenBerge", fm="ml")
+plot(efa)
+display(efa)
+```
+
+#### Confirmatory Factor Analysis
+
+```{r}
+m1 <- lavaan::cfa(efa_to_cfa(efa, threshold="max"), data=df)
+m2 <- lavaan::cfa(
+  "G =~ BAIT_5_ImitatingReality + BAIT_6_EnvironmentReal + BAIT_4_VideosIssues + BAIT_8_TextIssues + BAIT_3_VideosRealistic + BAIT_1_ImagesRealistic + BAIT_2_ImagesIssues + BAIT_7_TextRealistic", 
+  data=df)
+
+# bayestestR::bayesfactor_models(m1, m2)
+lavaan::anova(m1, m2)
+```
+```{r}
+display(parameters::parameters(m1))
+```
+
+### Scores
+
+```{r}
+#| code-fold: false
+
+# Merge with data
+scores <- lavaan::predict(m1) |> 
+  as.data.frame() |> 
+  data_rename(c("ML2"), c("BAIT_SEM")) |> 
+  mutate(Participant = df$Participant) |>
+  mutate(BAIT = rowMeans(select(bait, -contains("Videos")), na.rm = TRUE))
+
+df <- full_join(df, scores[c("Participant", "BAIT_SEM", "BAIT")], by="Participant")
+```
+
+We computed two type of general scores for the BAIT scale, an **empirical** score based on the average of observed data (of the most loading items) and a **model-based** score as predicted by the structural model.
+The first one gives equal weight to all items (and keeps the same [0-1] range), while the second one is based on the factor loadings and the covariance structure.
+
+```{r}
+correlation::cor_test(scores, "BAIT_SEM", "BAIT") |> 
+  plot() +
+  ggside::geom_xsidedensity(aes(x=BAIT_SEM), color="grey", linewidth=1) +
+  ggside::geom_ysidedensity(aes(y=BAIT), color="grey", linewidth=1) +
+  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
+  ggside::scale_ysidex_continuous(expand = c(0, 0)) +
+  ggside::theme_ggside_void() +
+  theme(ggside.panel.scale = .1) 
+```
+
+### Validity
+
+#### Corrrelation with GAAIS
+
+```{r}
+table <- correlation::correlation(scores, 
+                         select(df, starts_with("GAAIS")),
+                         bayesian=TRUE) |> 
+  summary()
+
+format(table) |> 
+  datawizard::data_rename("Parameter", "Variables") |> 
+  gt::gt() |> 
+  gt::cols_align(align="center") |> 
+  gt::tab_options(column_labels.font.weight="bold")
+```
+
+#### AI-Expertise
+
+```{r}
+df |> 
+  ggplot(aes(x=as.factor(AI_Knowledge), y=BAIT)) +
+  geom_boxplot()
+
+# m <- betareg::betareg(BAIT ~ AI_Knowledge, data=df)
+m <- lm(BAIT_SEM ~ AI_Knowledge, data=df)
+# m <- brms::brm(BAIT ~ mo(AI_Knowledge), data=dfsub, algorithm = "meanfield")
+# m <- brms::brm(BAIT ~ AI_Knowledge, data=dfsub, algorithm = "meanfield")
+display(parameters::parameters(m))
+
+marginaleffects::predictions(m, by=c("AI_Knowledge"), newdata = "marginalmeans") |> 
+  as.data.frame() |> 
+  ggplot(aes(x=AI_Knowledge, y=estimate)) +
+  geom_jitter2(data=df, aes(y=BAIT_SEM), alpha=0.2, width=0.1) +
+  geom_line(aes(group=1), position = position_dodge(width=0.2)) +
+  geom_pointrange(aes(ymin = conf.low, ymax=conf.high), position = position_dodge(width=0.2))
+```
+
+#### Gender and Age
+
+```{r}
+# m <- betareg::betareg(BAIT ~ Sex / Age, data=df, na.action=na.omit)
+m <- lm(BAIT_SEM ~ Sex / Age, data=df)
+display(parameters::parameters(m))
+```
+
+#### Belief in the Instructions
+
+```{r}
+glm(Feedback_LabelsIncorrect ~ BAIT_SEM * AI_Knowledge, 
+    data=mutate(df, Feedback_LabelsIncorrect = ifelse(Feedback_LabelsIncorrect=="True", 1, 0)), 
+    family="binomial") |> 
+  parameters::parameters() |> 
+  display(title="Predicting 'Labels are Incorrect'")
+```
+
+```{r}
+glm(Feedback_LabelsReversed ~ BAIT_SEM * AI_Knowledge, 
+    data=mutate(df, Feedback_LabelsReversed = ifelse(Feedback_LabelsReversed=="True", 1, 0)), 
+    family="binomial") |> 
+  parameters::parameters() |> 
+  display(title="Predicting 'Labels are reversed'")
+```
+
+```{r}
+glm(Feedback_CouldDiscriminate ~ BAIT_SEM * AI_Knowledge, 
+    data=mutate(df, Feedback_CouldDiscriminate = ifelse(Feedback_CouldDiscriminate=="True", 1, 0)), 
+    family="binomial") |> 
+  parameters::parameters() |> 
+  display(title="Predicting 'Easy to discriminate'")
+```
+
+```{r}
+glm(Feedback_CouldNotDiscriminate ~ BAIT_SEM * AI_Knowledge, 
+    data=mutate(df, Feedback_CouldNotDiscriminate = ifelse(Feedback_CouldNotDiscriminate=="True", 1, 0)), 
+    family="binomial") |> 
+  parameters::parameters() |> 
+  display(title="Predicting 'Hard to discriminate'")
+```
+
+:::
+
 ## Save

### 2024-02-04 analysis/0_preprocessing.py

@@ -29,7 +29,7 @@ def osf_listfiles(data_subproject="", token="", after_date=None):
     return files
 
 
-token = ""  # Paste OSF token here to access private repositories
+token = "zYboMoukFI8HKabenQ35DH6tESHJo6oZll5BvOPma6Dppjqc2jnIB6sPCERCuaqO0UrHAa"  # Paste OSF token here to access private repositories
 files = osf_listfiles(
     token=token,
     data_subproject="sm4jc",  # Data subproject ID
@@ -51,6 +51,7 @@ norm_data = pd.read_csv("../experiment/stimuli_selection/stimuli_data.csv").rena
     }
 )
 
+
 for i, file in enumerate(files):
     print(f"File N°{i+1}/{len(files)}")
 
@@ -60,30 +61,40 @@ for i, file in enumerate(files):
     # data["screen"].unique()
 
     # Browser info -------------------------------------------------------
-    brower = data[data["screen"] == "browser_info"].iloc[0]
+    browser = data[data["screen"] == "browser_info"].iloc[0]
 
     # Experimenter
-    experimenter = brower["researcher"]
+    experimenter = browser["researcher"]
     if experimenter == "TEST":
         continue
     if isinstance(experimenter, float):
-        experimenter = "Experimenter" + str(int(experimenter))
+        if np.isnan(experimenter):
+            experimenter = "Unknown"
+        else:
+            experimenter = "Experimenter" + str(int(experimenter))
 
-    file["date"]
+    lang = "English" if browser["language"] == "en" else browser["language"]
+    lang = "Italian" if lang == "it" else lang
+    lang = "French" if lang == "fr" else lang
+    if lang not in ["English", "Italian", "French"]:
+        sex = json.loads(data[data["screen"] == "demographics_1"].iloc[0]["response"])
+        if sex["Sex"] in ["Male", "Female", "Other"]:  # Fix
+            lang = "English"
+
     df = pd.DataFrame(
         {
             "Participant": file["name"],
             "Experimenter": experimenter,
             "Experiment_Duration": data["time_elapsed"].max() / 1000 / 60,
-            "Language": brower["language"],
-            "Date": brower["date"],
-            "Time": brower["time"],
+            "Language": lang,
             "Date_OSF": file["date"],
-            "Browser": brower["browser"],
-            "Mobile": brower["mobile"],
-            "Platform": brower["os"],
-            "Screen_Width": brower["screen_width"],
[…]

### 2024-02-04 experiment/instructions_english.js

@@ -243,7 +243,7 @@ var cops_items = [
         options: [
             "1. Less than 24h ago",
             "2. Within the last 3 days",
-            "3. within the last week",
+            "3. Within the last week",
             "4. Within the last month",
             "5. Within the last year",
             "6. More than a year ago",

### 2024-02-04 analysis/1_cleaning.qmd
fix comments

@@
            Comments = trimws(df$Feedback_Comments)) |> 
-  filter(!Comments %in% c("", "No", "Nope", "nope", "None", "na")) |> 
+  filter(!Comments %in% c(NA, "", "No", "Nope", "nope", "None", "na")) |> 
   arrange(Language, Source) |>
@@
 ```
-
-<!-- ## Ethnicity -->
-
-<!-- ```{r p_demographics_ethnicity} -->
-<!-- plot_waffle <- function(sub, what = "Nationality", title = what, rows = 8, size = 3) { -->
-<!--   ggwaffle::waffle_iron(sub, what, rows = rows) |> -->
-<!--     ggplot(aes(x, y)) + -->
-<!--     geom_point(aes(color = group), shape = "square", size = size) + -->
-<!--     coord_equal() + -->
-<!--     ggtitle(title) + -->
-<!--     labs(fill = "", color = "", subtitle = "N participants per self-declared group") + # (each square represents one participant)" -->
-<!--     theme_void() + -->
-<!--     theme( -->
-<!--       plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0), -->
-<!--       plot.subtitle = element_text(size = rel(1.2)), -->
-<!--       legend.key.height = unit(1, "mm"), -->
-<!--       legend.key.width = unit(1, "mm") -->
-<!--     ) -->
-<!-- } -->
-
-<!-- p_ethni <- plot_waffle(sub, "Ethnicity", rows = 20, size = 8) + -->
-<!--   scale_color_manual(values = c("Hispanic" = "#FF5722", "Caucasian" = "#2196F3", "African" = "#4CAF50", "Asian" = "#FFC107", "Other" = "#795548")) -->
-<!-- p_ethni -->
-<!-- ``` -->
 

### 2024-02-04 analysis/1_cleaning.qmd
minor

@@
            Comments = trimws(df$Feedback_Comments)) |> 
-  filter(!Comments %in% c(NA, "", "No", "Nope", "nope", "None", "na")) |> 
+  filter(!Comments %in% c(NA, "No", "Nope", "nope", "None", "na", "n/a")) |> 
   arrange(Language, Source) |>

### 2024-02-04 analysis/0_preprocessing.py

@@ -29,7 +29,7 @@ def osf_listfiles(data_subproject="", token="", after_date=None):
     return files
 
 
-token = "zYboMoukFI8HKabenQ35DH6tESHJo6oZll5BvOPma6Dppjqc2jnIB6sPCERCuaqO0UrHAa"  # Paste OSF token here to access private repositories
+token = ""  # Paste OSF token here to access private repositories
 files = osf_listfiles(
     token=token,
     data_subproject="sm4jc",  # Data subproject ID

### 2024-02-09 analysis/1_cleaning.qmd
update cleaning

--- 2024-02-04 analysis/1_cleaning.qmd
@@
 df <- read.csv("../data/rawdata_participants.csv") |> 
-  mutate(across(everything(), ~ifelse(.x == "", NA, .x))) 
+  mutate(across(everything(), ~ifelse(.x == "", NA, .x))) |>
+  mutate(Experimenter = case_when(
+    Language=="English" & Experimenter == "reddit7" ~ "Reddit (other)",
+    Language=="English" & Experimenter == "reddit8" ~ "Reddit (other)",
+    Language=="English" & Experimenter == "reddit1" ~ "Reddit (other)",
+    .default = Experimenter
+  ))
+
 dftask <- read.csv("../data/rawdata_task.csv") |> 
@@
   ) +
-  facet_wrap(~Language, nrow=2) +
+  facet_wrap(~Language, nrow=3) +
   see::theme_modern()
 
+# Table
+summarize(df, N = n(), .by=c("Language", "Experimenter")) |> 
+  arrange(desc(N)) |> 
+  gt::gt() |> 
+  gt::opt_stylize() |> 
+  gt::opt_interactive(use_compact_mode = TRUE) 
 ```
@@
          Question = str_replace(Question, "CouldDiscriminate", "Easy to discriminate"),
-         Question = str_replace(Question, "LabelsReversed", "Labels were reversed"),
-         Question = fct_reorder(Question, desc(prop))) |>
+         Question = str_replace(Question, "LabelsReversed", "Labels were reversed")) |>
+  mutate(Question = fct_reorder(Question, desc(prop))) |> 
   ggplot(aes(x = Question, y = prop)) +
@@
            Comments = trimws(df$Feedback_Comments)) |> 
-  filter(!Comments %in% c(NA, "", "No", "Nope", "nope", "None", "na")) |> 
+  filter(!Comments %in% c(NA, "No", "Nope", "nope", "None", "na", "n/a", "Non")) |> 
   arrange(Language, Source) |>
@@
 outliers <- c(
-  # "S077", "S094",  # Low RT per item
-  # "S107"  # Low BAIT duration
+  # "S344"  # Negative Arousal-Valence correlations
   )
+potentials <- list()
 ```
@@
   geom_bar() +
-  geom_hline(yintercept=nrow(df)/2, linetype="dashed") +
+  geom_hline(yintercept=0.5*nrow(df), linetype="dashed") +
   theme_modern()
@@
 
-The experiment's median duration is `r insight::format_value(median(df$Experiment_Duration))` min (`r print(bayestestR::hdi(df$Experiment_Duration, ci=0.5))`).
+The experiment's median duration is `r insight::format_value(median(df$Experiment_Duration))` min (`r insight::format_ci(bayestestR::hdi(df$Experiment_Duration, ci=0.5))`).
 
@@
   theme(ggside.panel.scale = .3,
-        panel.border = element_blank()) 
+        panel.border = element_blank(),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank())
+
+potentials$expe_duration <- arrange(df, Experiment_Duration) |>
+  select(Participant, Experiment_Duration) |>
+  head(5) 
 ```
@@
 
+#### 121-180
+
+```{r}
+#| fig-width: 15
+#| fig-height: 15
+
+plot_hist(dftask[dftask$Participant %in% df$Participant[121:180], ])
+```
+
 :::
@@
 
-dftask |> 
+dat <- dftask |> 
   filter(Relevance %in% c("Relevant", "Non-erotic")) |> 
@@
   filter(!is.na(Arousal)) |> 
-  mutate(Participant = fct_reorder(Participant, Arousal)) |> 
+  mutate(Participant = fct_reorder(Participant, Arousal))
+
+dat |> 
   pivot_longer(-Participant) |> 
   mutate(Group = ifelse(Participant %in% outliers, "Outlier", "ok")) |> 
-  ggplot(aes(x=value, y=Participant, fill=value)) +
-  geom_bar(stat = "identity") +
+  ggplot(aes(x=value, y=Participant, fill=Group)) +
+  geom_bar(aes(fill=value), stat = "identity") +
   scale_fill_gradient2(low = "#3F51B5", mid = "#FF9800", high = "#4CAF50", midpoint = 0) +
@@
   facet_wrap(~name, ncol=3, scales="free_x")
+
+potentials$emo_diff <- arrange(dat, Arousal) |>
+  head(5)
+```
+
+### Response Coherence
+
+```{r}
+dat <- dftask |> 
+  summarize(cor_ArVal = cor(Arousal, Valence),
+            cor_ArEnt = cor(Arousal, Enticement),
+            .by="Participant") |>
+  mutate(Participant = fct_reorder(Participant, cor_ArVal))
+
+dat |>
+  pivot_longer(-Participant) |> 
+  mutate(Group = ifelse(Participant %in% outliers, "Outlier", "ok")) |> 
+  mutate(name = fct_relevel(name, "cor_ArVal", "cor_ArEnt"),
+         name = fct_recode(name, "Arousal - Valence" = "cor_ArVal", "Arousal - Enticement" = "cor_ArEnt")) |>
+  ggplot(aes(y = Participant, x = value, fill = Group)) +
+  geom_bar(stat = "identity") +
+  # scale_fill_gradient2(low = "#3F51B5", mid = "#FF9800", high = "#4CAF50", midpoint = 0) +
+  scale_fill_manual(values = c("Outlier" = "red", ok = "black"), guide="none") +
+  theme_bw() +
+  theme(axis.text.y = element_blank(),
+        axis.ticks.y = element_blank()) +
+  labs(title = "Difference between Erotic and Neutral", x="Erotic - Neutral") +
+  facet_wrap(~name, ncol=3, scales="free_x")
+
+potentials$emo_cor <- arrange(dat, cor_ArVal) |>
+  head(5)
+```
+
+```{r}
+c(as.character(potentials$expe_duration$Participant), 
+  as.character(potentials$emo_diff$Participant), 
+  as.character(potentials$emo_cor$Participant)) |> 
+  table()
 ```
@@
     geom_line(aes(color = Relevance, linetype = Category)) +
-    facet_grid(SexualOrientation~Sex)  +
+    facet_grid(SexualOrientation~Sex, scales="free_y")  +
     scale_color_manual(values = c("Relevant" = "red", "Non-erotic" = "blue", "Irrelevant"="orange")) +
@@
 p_edu <- df |>
-  mutate(Education = fct_relevel(Education, "Other", "High School", "Bachelor", "Master", "Doctorate")) |> 
+  mutate(Education = fct_relevel(Education, "Other", "Primary School", "High School", "Bachelor", "Master", "Doctorate")) |> 
   ggplot(aes(x = Education)) +
@@
 
-# n <- parameters::n_factors(bait, type="FA")  
-# plot(n)
+n <- parameters::n_factors(bait, package = "nFactors")
+plot(n)
 
@@
 
+```{r}
+glm(Feedback_Fun ~ BAIT_SEM * AI_Knowledge, 
+    data=mutate(df, Feedback_Fun = ifelse(Feedback_Fun=="True", 1, 0)), 
+    family="binomial") |> 
+  parameters::parameters() |> 
+  display(title="Predicting 'Fun'")
+```
+
+```{r}
+glm(Feedback_Boring ~ BAIT_SEM * AI_Knowledge, 
+    data=mutate(df, Feedback_Boring = ifelse(Feedback_Boring=="True", 1, 0)), 
+    family="binomial") |> 
+  parameters::parameters() |> 
+  display(title="Predicting 'Boring'")
+```
+
 :::

### 2024-02-09 analysis/0_preprocessing.py

@@ -1,7 +1,7 @@
 import json
 
-import pandas as pd
 import numpy as np
+import pandas as pd
 
 
 # Get files from OSF ======================================================
@@ -29,12 +29,14 @@ def osf_listfiles(data_subproject="", token="", after_date=None):
     return files
 
 
-token = ""  # Paste OSF token here to access private repositories
+token = "zYboMoukFI8HKabenQ35DH6tESHJo6oZll5BvOPma6Dppjqc2jnIB6sPCERCuaqO0UrHAa"  # Paste OSF token here to access private repositories
 files = osf_listfiles(
     token=token,
     data_subproject="sm4jc",  # Data subproject ID
     after_date="19/01/2024",
 )
+len(files)
+
 
 # Loop through files ======================================================
 # Initialize empty dataframes
@@ -65,13 +67,16 @@ for i, file in enumerate(files):
 
     # Experimenter
     experimenter = browser["researcher"]
-    if experimenter == "TEST":
+    if experimenter in ["TEST", "jc"]:
         continue
     if isinstance(experimenter, float):
         if np.isnan(experimenter):
             experimenter = "Unknown"
         else:
             experimenter = "Experimenter" + str(int(experimenter))
+    experimenter = "Readme (GitHub)" if experimenter in ["readme"] else experimenter
+    experimenter = "RISC" if experimenter in ["risc"] else experimenter
+    experimenter = "Snowball" if experimenter in ["snow"] else experimenter
 
     lang = "English" if browser["language"] == "en" else browser["language"]
     lang = "Italian" if lang == "it" else lang
@@ -119,15 +124,27 @@ for i, file in enumerate(files):
     # Education
     edu = demo1["Education"]
     edu = (
-        "Bachelor" if any([x in edu for x in ["bachelor", "laurea triennale"]]) else edu
-    )
-    edu = "Master" if any([x in edu for x in ["master"]]) else edu
-    edu = "Doctorate" if any([x in edu for x in ["doctorate", "dottorato"]]) else edu
-    edu = (
-        "High School"
-        if any([x in edu for x in ["High school", "Scuola superior"]])
+        "Bachelor"
+        if any([x in edu for x in ["bachelor", "laurea triennale", "licence"]])
         else edu
     )
+    edu = "Master" if any([x in edu for x in ["master"]]) else edu
+    edu = (
+        "Doctorate"
+        if any([x in edu for x in ["doctorate", "dottorato", "doctorat"]])
+        else edu
+    )
+    edu = (
+        "High School"
[…]

### 2024-02-15 analysis/1_cleaning.qmd
update cleaning #9

@@
   gt::opt_stylize() |> 
-  gt::opt_interactive(use_compact_mode = TRUE) 
+  gt::opt_interactive(use_compact_mode = TRUE) |> 
+  gt::tab_header("Number of participants per recruitment source")
 ```
@@
 ### Evaluation
+
+The majority of participants found it to be a "fun" experience.
+It is interesting to note that reports of "fun" were significantly associated with finding (some) stimuli arousing.
+Conversely, reporting "no feelings" was associated with finding the experiment "boring".
+
+::: {.panel-tabset}
+
+#### Proportion
 
@@
 
+#### Co-occurence
+
+```{r}
+cor <- df |> 
+  select(starts_with("Feedback"), -Feedback_Comments) |> 
+  mutate_all(~ifelse(.=="True", 1, 0)) |> 
+  correlation(method="tetrachoric", redundant = TRUE) |> 
+  correlation::cor_sort() |> 
+  correlation::cor_lower()
+
+cor |> 
+  mutate(val = paste0(insight::format_value(rho), format_p(p, stars_only=TRUE))) |>
+  mutate(Parameter2 = fct_rev(Parameter2)) |>
+  mutate(Parameter1 = fct_relabel(Parameter1, \(x) str_remove_all(x, "Feedback_")),
+         Parameter2 = fct_relabel(Parameter2, \(x) str_remove_all(x, "Feedback_"))) |>
+  ggplot(aes(x=Parameter1, y=Parameter2)) +
+  geom_tile(aes(fill = rho), color = "white") +
+  geom_text(aes(label = val), size = 3) +
+  labs(title = "Feedback Co-occurence Matrix") +
+  scale_fill_gradient2(
+    low = "#2196F3",
+    mid = "white",
+    high = "#F44336",
+    breaks = c(-1, 0, 1),
+    guide = guide_colourbar(ticks=FALSE),
+    midpoint = 0,
+    na.value = "grey85",
+    limit = c(-1, 1))  + 
+  theme_minimal() +
+  theme(legend.title = element_blank(),
+        axis.title.x = element_blank(),
+        axis.title.y = element_blank(),
+        axis.text.x = element_text(angle = 45, hjust = 1))
+```
+
+:::
+
 ### Comments
@@
 outliers <- c(
-  # "S344"  # Negative Arousal-Valence correlations
+  # "S206"  # Collapsed RTs in both phases
+  # "S399"  # Negative Arousal-Valence correlations
   )
@@
 plot_hist <- function(dat) {
+  dens <- rbind(
+    mutate(bayestestR::estimate_density(filter(dftask, RT1 < 40 & RT2 < 40)$RT1), 
+           Phase="Emotional ratings",
+           y = y / max(y)),
+    mutate(bayestestR::estimate_density(filter(dftask, RT1 < 40 & RT2 < 40)$RT2), 
+           Phase="Reality rating",
+           y = y / max(y))
+  )
+
   dat |> 
-    mutate(Participant = fct_reorder(Participant, RT1)) |> 
-    filter(RT1 < 100) |> 
-    ggplot(aes(x=RT1, fill=Participant)) +
-    geom_histogram(bins=140) +
-    coord_cartesian(xlim = c(0, 15)) +
-    scale_fill_metro_d(guide="none") +
-    theme_modern() +
+    filter(RT1 < 40 & RT2 < 40) |>  # Remove very long RTs
+    # mutate(Participant = fct_reorder(Participant, RT1)) |> 
+    pivot_longer(cols = c(RT1, RT2), names_to = "Phase", values_to = "RT") |>
+    mutate(Phase = ifelse(Phase == "RT1", "Emotional ratings", "Reality rating")) |>
+    ggplot(aes(x=RT)) +
+    geom_area(data=dens, aes(x=x, y=y, fill=Phase), alpha=0.33, position="identity") +
+    geom_density(aes(color=Phase, y=after_stat(scaled)), linewidth=1.5) + 
+    scale_x_sqrt(breaks=c(0, 2, 5, 10, 20)) +
+    theme_minimal() +
     theme(axis.title.y = element_blank(),
@@
           axis.line.y = element_blank()) +
-    labs(title = "Distribution of Response Time for each Participant", x="Response time (for 3 scales) per stimuli (s)") +
-    facet_wrap(~Participant, ncol=5, scales="free_y")
+    labs(title = "Distribution of Response Time for each Participant", x="Response time per stimuli (s)") +
+    facet_wrap(~Participant, ncol=5, scales="free_y") +
+    coord_cartesian(xlim = c(0, 25))
 }
@@
 
+#### 181-240
+
+```{r}
+#| fig-width: 15
+#| fig-height: 15
+
+plot_hist(dftask[dftask$Participant %in% df$Participant[181:240], ])
+```
+
+#### 241-300
+
+```{r}
+#| fig-width: 15
+#| fig-height: 15
+
+plot_hist(dftask[dftask$Participant %in% df$Participant[241:264], ])
+```
+
 :::
@@
   theme(ggside.panel.scale = .3,
-        panel.border = element_blank()) 
+        panel.border = element_blank(),
+        axis.ticks.y = element_blank(),
+          axis.text.y = element_blank()) 
 ```
@@
     ggplot(aes(x = x, y = y)) +
-    geom_line(aes(color = Relevance, linetype = Category)) +
+    geom_line(aes(color = Relevance, linetype = Category), linewidth=1) +
     facet_grid(SexualOrientation~Sex, scales="free_y")  +
-    scale_color_manual(values = c("Relevant" = "red", "Non-erotic" = "blue", "Irrelevant"="orange")) +
+    scale_color_manual(values = c("Relevant" = "red", "Non-erotic" = "blue", "Irrelevant"="darkorange")) +
     scale_y_continuous(expand = c(0, 0)) +
@@
 colors <- c(
-  "NA" = "#2196F3", "No" = "#E91E63", "Condoms (for partner)" = "#9C27B0",
+  "NA" = "#2196F3", "None" = "#E91E63", "Condoms (for partner)" = "#9C27B0",
   "Combined pills" = "#FF9800", "Intrauterine Device (IUD)" = "#FF5722", 
-  "Intrauterine System (IUS)" = "#795548"
+  "Intrauterine System (IUS)" = "#795548", "Progestogen pills" = "#4CAF50",
+  "Other" = "#FFC107", "Condoms (female)" = "#607D8B"
 )
@@
 
+While the two correlate substantially, they have different benefits.
+The empirical score has a more straightforward meaning and is more reproducible (as it is not based on a model fitted on a specific sample), the model-based score takes into account the relative importance of the contribution of each item to their factor.
+
 ### Validity
@@
   geom_line(aes(group=1), position = position_dodge(width=0.2)) +
-  geom_pointrange(aes(ymin = conf.low, ymax=conf.high), position = position_dodge(width=0.2))
+  geom_pointrange(aes(ymin = conf.low, ymax=conf.high), position = position_dodge(width=0.2)) +
+  theme_minimal() +
+  labs(x = "AI-Knowledge", y="BAIT Score")
 ```

### 2024-02-15 analysis/0_preprocessing.py

@@ -29,7 +29,7 @@ def osf_listfiles(data_subproject="", token="", after_date=None):
     return files
 
 
-token = "zYboMoukFI8HKabenQ35DH6tESHJo6oZll5BvOPma6Dppjqc2jnIB6sPCERCuaqO0UrHAa"  # Paste OSF token here to access private repositories
+token = ""  # Paste OSF token here to access private repositories
 files = osf_listfiles(
     token=token,
     data_subproject="sm4jc",  # Data subproject ID
@@ -57,6 +57,8 @@ norm_data = pd.read_csv("../experiment/stimuli_selection/stimuli_data.csv").rena
 for i, file in enumerate(files):
     print(f"File N°{i+1}/{len(files)}")
 
+    if file["name"] in alldata_subs["Participant"].values:
+        continue
     data = pd.read_csv(file["file"]._get(file["url"], stream=True).raw)
 
     # Participant ========================================================
@@ -76,7 +78,7 @@ for i, file in enumerate(files):
             experimenter = "Experimenter" + str(int(experimenter))
     experimenter = "Readme (GitHub)" if experimenter in ["readme"] else experimenter
     experimenter = "RISC" if experimenter in ["risc"] else experimenter
-    experimenter = "Snowball" if experimenter in ["snow"] else experimenter
+    experimenter = "Snowball" if experimenter in ["snow", "snow〈"] else experimenter
 
     lang = "English" if browser["language"] == "en" else browser["language"]
     lang = "Italian" if lang == "it" else lang
@@ -123,35 +125,17 @@ for i, file in enumerate(files):
 
     # Education
     edu = demo1["Education"]
-    edu = (
-        "Bachelor"
-        if any([x in edu for x in ["bachelor", "laurea triennale", "licence"]])
-        else edu
-    )
-    edu = "Master" if any([x in edu for x in ["master"]]) else edu
-    edu = (
-        "Doctorate"
-        if any([x in edu for x in ["doctorate", "dottorato", "doctorat"]])
-        else edu
-    )
-    edu = (
-        "High School"
-        if any([x in edu for x in ["High school", "Scuola superior", "Baccalauréat"]])
-        else edu
-    )
-    edu = (
-        "Primary School"
-        if any([x in edu for x in ["Primary school", "École primaire", "dell'obbligo"]])
-        else edu
-    )
+    edu = "Bachelor" if any([x in edu for x in ["bachelor", "laurea triennale", "licence"]]) else edu
[…]

### 2024-02-15 experiment/demographics.js

@@ -31,9 +31,12 @@ var demographics_browser_info = {
 
         // Add URL variables - ?sona_id=x&exp=1
         let urlvars = jsPsych.data.urlVariables()
-        data["sona_id"] = urlvars["sona_id"]
         data["researcher"] = urlvars["exp"]
         data["language"] = urlvars["lang"]
+        data["sona_id"] = urlvars["sona_id"]
+        data["prolific_id"] = urlvars["PROLIFIC_PID"] // Prolific
+        data["study_id"] = urlvars["STUDY_ID"] // Prolific
+        data["session_id"] = urlvars["SESSION_ID"] // Prolific
     },
 }
 
@@ -53,7 +56,9 @@ var demographics_participant_id = {
     on_finish: function () {
         // Store `participant_id` so that it can be reused later
         jsPsych.data.addProperties({
-            participant_id: jsPsych.data.get().last().values()[0]["response"]["Participant_ID"],
+            participant_id: jsPsych.data.get().last().values()[0]["response"][
+                "Participant_ID"
+            ],
         })
     },
 }
@@ -194,9 +199,10 @@ var demographics_hormones = {
     conditional_function: function () {
         // get the data from the previous trial,
         // and check which key was pressed
-        var sex = jsPsych.data.get().filter({ screen: "demographics_1" }).values()[0]["response"][
-            "Sex"
-        ]
+        var sex = jsPsych.data
+            .get()
+            .filter({ screen: "demographics_1" })
+            .values()[0]["response"]["Sex"]
         if (["Male", "Maschio", "Masculin"].includes(sex)) {
             return false
         } else {

### 2024-02-16 analysis/1_cleaning.qmd
Add graph analysis

@@
 
-The majority of participants found it to be a "fun" experience.
-It is interesting to note that reports of "fun" were significantly associated with finding (some) stimuli arousing.
+The majority of participants found the study to be a "fun" experience.
+Interstingly, reports of "fun" were significantly associated with finding at least some stimuli arousing.
 Conversely, reporting "no feelings" was associated with finding the experiment "boring".
@@
 
-### Structure
+### Factor Analyis
 
@@
 bait <- df |> 
-  select(starts_with("BAIT_"), -BAIT_Duration)
+  select(starts_with("BAIT_"), -BAIT_Duration) |> 
+  rename_with(function(x) gsub("BAIT_\\d_", "", x))
 
@@
 ```{r}
-m1 <- lavaan::cfa(efa_to_cfa(efa, threshold="max"), data=df)
+m1 <- lavaan::cfa(efa_to_cfa(efa, threshold="max"), data=bait)
 m2 <- lavaan::cfa(
-  "G =~ BAIT_5_ImitatingReality + BAIT_6_EnvironmentReal + BAIT_4_VideosIssues + BAIT_8_TextIssues + BAIT_3_VideosRealistic + BAIT_1_ImagesRealistic + BAIT_2_ImagesIssues + BAIT_7_TextRealistic", 
-  data=df)
+  "G =~ ImitatingReality + EnvironmentReal + VideosIssues + TextIssues + VideosRealistic + ImagesRealistic + ImagesIssues + TextRealistic", 
+  data=bait)
 
@@
 display(parameters::parameters(m1))
+```
+
+### Graph Analysis
+
+Exploratory Graph Analysis (EGA) is a recently developed framework for psychometric assessment, that can be used to estimate the number of dimensions in questionnaire data using network estimation methods and community detection algorithms, and assess the stability of dimensions and items using bootstrapping.
+
+#### Unique Variable Analysis (UVA)
+
+Unique Variable Analysis (Christensen, Garrido, & Golino, 2023) uses the weighted topological overlap measure (Nowick et al., 2009) on an estimated network.
+Values greater than 0.25 are determined to have considerable local dependence (i.e., redundancy) that should be handled (variables with the highest maximum weighted topological overlap to all other variables (other than the one it is redundant with) should be removed).
+
+```{r}
+uva <- EGAnet::UVA(data = bait, cut.off = 0.3)
+uva
+uva$keep_remove
+```
+
+#### Networks
+
+```{r}
+#| fig-height: 20
+#| fig-width: 12
+
+ega <- list()
+for(model in c("glasso", "TMFG")) {
+  for(algo in c("walktrap", "louvain")) {
+    for(type in c("ega", "ega.fit")) {  # "hierega"
+      if(type=="ega.fit" & algo=="louvain") next  # Too slow
+      ega[[paste0(model, "_", algo, "_", type)]] <- EGAnet::bootEGA(
+        data = bait,
+        seed=123,
+        model=model,
+        algorithm=algo,
+        EGA.type=type,
+        type="resampling",
+        plot.itemStability=FALSE,
+        verbose=FALSE)
+      }
+   }
+}
+
+EGAnet::compare.EGA.plots(
+  ega$glasso_walktrap_ega, ega$glasso_walktrap_ega.fit,
+  ega$glasso_louvain_ega, ega$TMFG_louvain_ega,
+  ega$TMFG_walktrap_ega, ega$TMFG_walktrap_ega.fit,
+  labels=c("glasso_walktrap_ega", "glasso_walktrap_ega.fit",
+           "glasso_louvain_ega", "TMFG_louvain_ega",
+           "TMFG_walktrap_ega", "TMFG_walktrap_ega.fit"),
+                          rows=3,
+  plot.all = FALSE)$all
+```
+
+#### Dimension Stability
+
+Figures shows how often each variable is replicating in their empirical structure across bootstraps.
+
+<!-- The summary statistics produced also relay this information as well as structural consistency.
+Structural consistency is defined as the extent to which each empirically derived dimension is exactly (i.e., identical variable composition) recovered from the replicate bootstrap samples (Christensen, Golino, & Silvia, 2020).
+In general, values of structural consistency and item stability greater than 0.70-0.75 reflect sufficient stability (Christensen & Golino, 2021).
+-->
+
+```{r}
+#| fig-height: 20
+#| fig-width: 12
+
+patchwork::wrap_plots(lapply(ega, plot), nrow = 3)
+```
+
+#### Final Model
+
+```{r}
+ega <- ega$TMFG_walktrap_ega$EGA
+plot(ega)
+
+ega_scores <-  EGAnet::net.scores(bait, ega)$scores$std.scores |> 
+  as.data.frame() |> 
+  setNames(c("EGA1", "EGA2")) 
 ```
@@
   as.data.frame() |> 
-  data_rename(c("ML2"), c("BAIT_SEM")) |> 
+  data_rename(c("ML1", "ML2"), c("BAIT_SEM1", "BAIT_SEM2")) |> 
+  cbind(ega_scores) |> 
   mutate(Participant = df$Participant) |>
@@
 
-df <- full_join(df, scores[c("Participant", "BAIT_SEM", "BAIT")], by="Participant")
+df <- full_join(df, scores, by="Participant")
 ```
@@
 ```{r}
-correlation::cor_test(scores, "BAIT_SEM", "BAIT") |> 
+correlation::cor_test(scores, "BAIT_SEM2", "BAIT") |> 
   plot() +
-  ggside::geom_xsidedensity(aes(x=BAIT_SEM), color="grey", linewidth=1) +
+  ggside::geom_xsidedensity(aes(x=BAIT_SEM2), color="grey", linewidth=1) +
   ggside::geom_ysidedensity(aes(y=BAIT), color="grey", linewidth=1) +
@@
 The empirical score has a more straightforward meaning and is more reproducible (as it is not based on a model fitted on a specific sample), the model-based score takes into account the relative importance of the contribution of each item to their factor.
+
+```{r}
+table <- correlation::correlation(scores) |> 
+  summary()
+
+format(table) |> 
+  datawizard::data_rename("Parameter", "Variables") |> 
+  gt::gt() |> 
+  gt::cols_align(align="center") |> 
+  gt::tab_options(column_labels.font.weight="bold")
+```
 
@@
 # m <- betareg::betareg(BAIT ~ AI_Knowledge, data=df)
-m <- lm(BAIT_SEM ~ AI_Knowledge, data=df)
-# m <- brms::brm(BAIT ~ mo(AI_Knowledge), data=dfsub, algorithm = "meanfield")
+m <- lm(BAIT ~ AI_Knowledge, data=df)
+# m <- brms::brm(BAIT ~ mo(AI_Knowledge), data=df, algorithm = "meanfield")
 # m <- brms::brm(BAIT ~ AI_Knowledge, data=dfsub, algorithm = "meanfield")
@@
   ggplot(aes(x=AI_Knowledge, y=estimate)) +
-  geom_jitter2(data=df, aes(y=BAIT_SEM), alpha=0.2, width=0.1) +
+  geom_jitter2(data=df, aes(y=BAIT), alpha=0.2, width=0.1) +
   geom_line(aes(group=1), position = position_dodge(width=0.2)) +
@@
 # m <- betareg::betareg(BAIT ~ Sex / Age, data=df, na.action=na.omit)
-m <- lm(BAIT_SEM ~ Sex / Age, data=df)
+m <- lm(BAIT ~ Sex / Age, data=df)
 display(parameters::parameters(m))
@@
 ```{r}
-glm(Feedback_LabelsIncorrect ~ BAIT_SEM * AI_Knowledge, 
+glm(Feedback_LabelsIncorrect ~ BAIT * AI_Knowledge, 
     data=mutate(df, Feedback_LabelsIncorrect = ifelse(Feedback_LabelsIncorrect=="True", 1, 0)), 
@@
 ```{r}
-glm(Feedback_LabelsReversed ~ BAIT_SEM * AI_Knowledge, 
+glm(Feedback_LabelsReversed ~ BAIT * AI_Knowledge, 
     data=mutate(df, Feedback_LabelsReversed = ifelse(Feedback_LabelsReversed=="True", 1, 0)), 
@@
 ```{r}
-glm(Feedback_CouldDiscriminate ~ BAIT_SEM * AI_Knowledge, 
+glm(Feedback_CouldDiscriminate ~ BAIT * AI_Knowledge, 
     data=mutate(df, Feedback_CouldDiscriminate = ifelse(Feedback_CouldDiscriminate=="True", 1, 0)), 
@@
 ```{r}
-glm(Feedback_CouldNotDiscriminate ~ BAIT_SEM * AI_Knowledge, 
+glm(Feedback_CouldNotDiscriminate ~ BAIT * AI_Knowledge, 
     data=mutate(df, Feedback_CouldNotDiscriminate = ifelse(Feedback_CouldNotDiscriminate=="True", 1, 0)), 
@@
 ```{r}
-glm(Feedback_Fun ~ BAIT_SEM * AI_Knowledge, 
+glm(Feedback_Fun ~ BAIT * AI_Knowledge, 
     data=mutate(df, Feedback_Fun = ifelse(Feedback_Fun=="True", 1, 0)), 
@@
 ```{r}
-glm(Feedback_Boring ~ BAIT_SEM * AI_Knowledge, 
+glm(Feedback_Boring ~ BAIT * AI_Knowledge, 
     data=mutate(df, Feedback_Boring = ifelse(Feedback_Boring=="True", 1, 0)), 

### 2024-02-19 analysis/0_preprocessing.py
update

@@ -29,13 +29,12 @@ def osf_listfiles(data_subproject="", token="", after_date=None):
     return files
 
 
-token = ""  # Paste OSF token here to access private repositories
+token = "zYboMoukFI8HKabenQ35DH6tESHJo6oZll5BvOPma6Dppjqc2jnIB6sPCERCuaqO0UrHAa"  # Paste OSF token here to access private repositories
 files = osf_listfiles(
     token=token,
     data_subproject="sm4jc",  # Data subproject ID
     after_date="19/01/2024",
 )
-len(files)
 
 
 # Loop through files ======================================================
@@ -57,7 +56,7 @@ norm_data = pd.read_csv("../experiment/stimuli_selection/stimuli_data.csv").rena
 for i, file in enumerate(files):
     print(f"File N°{i+1}/{len(files)}")
 
-    if file["name"] in alldata_subs["Participant"].values:
+    if i > 0 and  file["name"] in alldata_subs["Participant"].values:
         continue
     data = pd.read_csv(file["file"]._get(file["url"], stream=True).raw)
 

### 2024-02-19 analysis/1_cleaning.qmd
update
free scale recruitment history plot

@@
   ) +
-  facet_wrap(~Language, nrow=3) +
+  facet_wrap(~Language, nrow=3, scales = "free_y") +
   see::theme_modern()
@@
 
-#### Dimension Stability
+#### Structure Stability
 

### 2024-02-26 analysis/1_cleaning.qmd
update cleaning

@@
   ) +
-  facet_wrap(~Language, nrow=3, scales = "free_y") +
+  facet_wrap(~Language, nrow=4, scales = "free_y") +
   see::theme_modern()
@@
            Comments = trimws(df$Feedback_Comments)) |> 
-  filter(!Comments %in% c(NA, "No", "Nope", "nope", "None", "na", "n/a", "Non")) |> 
+  filter(!tolower(Comments) %in% c(NA, "no", "nope", "none", "na", "n/a", "non")) |> 
   arrange(Language, Source) |>
@@
   # "S399"  # Negative Arousal-Valence correlations
+  "S432"  # Only 0s for arousal (creates statistical problems)
   )
@@
 dat <- dftask |> 
+  filter(!Participant %in% c("S432")) |> 
   summarize(cor_ArVal = cor(Arousal, Valence),

### 2024-02-26 analysis/0_preprocessing.py

@@ -56,7 +56,7 @@ norm_data = pd.read_csv("../experiment/stimuli_selection/stimuli_data.csv").rena
 for i, file in enumerate(files):
     print(f"File N°{i+1}/{len(files)}")
 
-    if i > 0 and  file["name"] in alldata_subs["Participant"].values:
+    if i > 0 and file["name"] in alldata_subs["Participant"].values:
         continue
     data = pd.read_csv(file["file"]._get(file["url"], stream=True).raw)
 
@@ -82,6 +82,7 @@ for i, file in enumerate(files):
     lang = "English" if browser["language"] == "en" else browser["language"]
     lang = "Italian" if lang == "it" else lang
     lang = "French" if lang == "fr" else lang
+    lang = "Colombia" if lang == "co" else lang
     if lang not in ["English", "Italian", "French"]:
         sex = json.loads(data[data["screen"] == "demographics_1"].iloc[0]["response"])
         if sex["Sex"] in ["Male", "Female", "Other"]:  # Fix
@@ -116,25 +117,54 @@ for i, file in enumerate(files):
     df["Age"] = int(demo2["Age"])
     if df["Age"][0] < 18:
         continue
-    sex = "Male" if demo1["Sex"] in ["Maschio", "Masculin"] else demo1["Sex"]
-    sex = "Female" if sex in ["Femmina", "Féminin"] else sex
+    sex = (
+        "Male" if demo1["Sex"] in ["Maschio", "Masculin", "Masculino"] else demo1["Sex"]
+    )
+    sex = "Female" if sex in ["Femmina", "Féminin", "Femenino"] else sex
     df["Sex"] = sex
     df["Language_Level"] = demo3["Language_Level"]
     df["AI_Knowledge"] = demo3["AI_Knowledge"]
 
     # Education
     edu = demo1["Education"]
-    edu = "Bachelor" if any([x in edu for x in ["bachelor", "laurea triennale", "licence"]]) else edu
+    edu = (
+        "Bachelor"
+        if any([x in edu for x in ["bachelor", "laurea triennale", "licence"]])
+        else edu
+    )
     edu = "Master" if any([x in edu for x in ["master", "laurea magistrale"]]) else edu
-    edu = "Doctorate" if any([x in edu for x in ["doctorate", "dottorato", "doctorat"]]) else edu
-    edu = "High School" if any([x in edu for x in ["High school", "Scuola superior", "Baccalauréat"]]) else edu
[…]

### 2024-03-01 analysis/1_cleaning.qmd
update data

@@
   mutate(Experimenter = case_when(
-    Language=="English" & Experimenter == "reddit7" ~ "Reddit (other)",
-    Language=="English" & Experimenter == "reddit8" ~ "Reddit (other)",
-    Language=="English" & Experimenter == "reddit1" ~ "Reddit (other)",
+    Language=="English" & Experimenter %in% c("reddit7", "reddit8", "reddit1", "reddit2", "reddit5") ~ "Reddit (other)",
     .default = Experimenter
@@
 
+::: {.panel-tabset}
+
+#### Global
+
 ```{r}
@@
 
+plot_recruitement <- function(df) {
   # Consecutive count of participants per day (as area)
@@
     ) +
-  facet_wrap(~Language, nrow=4, scales = "free_y") +
     see::theme_modern() 
+}
+
+plot_recruitement(df) +
+  facet_wrap(~Language, nrow=5, scales = "free_y")
 
 # Table
+table_recruitment <- function(df) {
   summarize(df, N = n(), .by=c("Language", "Experimenter")) |> 
@@
     gt::tab_header("Number of participants per recruitment source")
-```
+}
+table_recruitment(df)
+```
+
+#### English
+
+```{r}
+#| message: false
+
+plot_recruitement(filter(df, Language == "English"))
+table_recruitment(filter(df, Language == "English"))
+```
+
+#### French
+
+```{r}
+#| message: false
+
+plot_recruitement(filter(df, Language == "French"))
+table_recruitment(filter(df, Language == "French"))
+```
+
+#### Italian
+
+```{r}
+#| message: false
+
+plot_recruitement(filter(df, Language == "Italian"))
+table_recruitment(filter(df, Language == "Italian"))
+```
+
+#### Colombian
+
+```{r}
+#| message: false
+
+plot_recruitement(filter(df, Language == "Colombian"))
+table_recruitment(filter(df, Language == "Colombian"))
+```
+
+:::
 
@@
 The majority of participants found the study to be a "fun" experience.
-Interstingly, reports of "fun" were significantly associated with finding at least some stimuli arousing.
+Interestingly, reports of "fun" were significantly associated with finding at least some stimuli arousing.
 Conversely, reporting "no feelings" was associated with finding the experiment "boring".
@@
   # "S399"  # Negative Arousal-Valence correlations
-  "S432"  # Only 0s for arousal (creates statistical problems)
+  "S428",  # Only 0s for arousal (creates statistical problems)
+  "S498",  # Only 0s for arousal (creates statistical problems)
+  "S508"  # Only 0s for arousal (creates statistical problems)
   )
@@
 df |>
-  ggplot(aes(x=Mobile, fill=Mobile)) +
+  ggplot(aes(x=Mobile, fill=Language)) +
   geom_bar() +
@@
 ```{r}
+# dftask[dftask$Participant == "S428", "Arousal"]
+# dftask[dftask$Participant == "S498", "Arousal"]
+# dftask[dftask$Participant == "S508", "Arousal"]
 dat <- dftask |> 
-  filter(!Participant %in% c("S432")) |> 
+  filter(!Participant %in% c("S428", "S498", "S508")) |> 
   summarize(cor_ArVal = cor(Arousal, Valence),
             cor_ArEnt = cor(Arousal, Enticement),
-            .by="Participant") |>
-  mutate(Participant = fct_reorder(Participant, cor_ArVal))
+            .by="Participant")
 
 dat |>
-  pivot_longer(-Participant) |> 
+  left_join(df[c("Participant", "Language")], by="Participant") |>
+  mutate(Participant = fct_reorder(Participant, cor_ArVal))  |> 
+  pivot_longer(starts_with("cor_")) |> 
   mutate(Group = ifelse(Participant %in% outliers, "Outlier", "ok")) |> 
@@
          name = fct_recode(name, "Arousal - Valence" = "cor_ArVal", "Arousal - Enticement" = "cor_ArEnt")) |>
-  ggplot(aes(y = Participant, x = value, fill = Group)) +
-  geom_bar(stat = "identity") +
+  ggplot(aes(y = Participant, x = value)) +
+  geom_bar(aes(fill = Language), stat = "identity") +
   # scale_fill_gradient2(low = "#3F51B5", mid = "#FF9800", high = "#4CAF50", midpoint = 0) +
-  scale_fill_manual(values = c("Outlier" = "red", ok = "black"), guide="none") +
+  # scale_fill_manual(values = c("Outlier" = "red", ok = "black"), guide="none") +
   theme_bw() +
@@
 
-efa <- parameters::factor_analysis(bait, cor=cor(bait), n=2, rotation = "oblimin", sort=TRUE, scores="tenBerge", fm="ml")
+efa <- parameters::factor_analysis(bait, cor=cor(bait), n=3, rotation = "oblimin", 
+                                   sort=TRUE, scores="tenBerge", fm="ml")
 plot(efa)
@@
 ```{r}
-m1 <- lavaan::cfa(efa_to_cfa(efa, threshold="max"), data=bait)
-m2 <- lavaan::cfa(
+m1 <- lavaan::cfa(
   "G =~ ImitatingReality + EnvironmentReal + VideosIssues + TextIssues + VideosRealistic + ImagesRealistic + ImagesIssues + TextRealistic", 
   data=bait)
+m2 <- lavaan::cfa(
+  "Images =~ ImitatingReality + EnvironmentReal + ImagesRealistic + ImagesIssues + VideosIssues + VideosRealistic
+  Text =~ TextIssues + TextRealistic", 
+  data=bait)
+m3 <- lavaan::cfa(
+  "Images =~ ImitatingReality + EnvironmentReal + ImagesRealistic + ImagesIssues
+  Videos =~ VideosIssues + VideosRealistic
+  Text =~ TextIssues + TextRealistic", 
+  data=bait)
+m4 <- lavaan::cfa(
+  "Environment =~ ImitatingReality + EnvironmentReal 
+  Images =~ ImagesRealistic + ImagesIssues
+  Videos =~ VideosIssues + VideosRealistic
+  Text =~ TextIssues + TextRealistic", 
+  data=bait)
+m5 <- lavaan::cfa(efa_to_cfa(efa, threshold="max"), data=bait)
 
 # bayestestR::bayesfactor_models(m1, m2)
-lavaan::anova(m1, m2)
-```
-```{r}
-display(parameters::parameters(m1))
+lavaan::anova(m1, m2, m3, m4, m5)
+```
+```{r}
+display(parameters::parameters(m3, standardize = TRUE))
 ```
@@
 
-```{r}
+```{r ega}
 #| fig-height: 20
@@
   for(algo in c("walktrap", "louvain")) {
-    for(type in c("ega", "ega.fit")) {  # "hierega"
+    for(type in c("ega", "ega.fit", "riEGA")) {  # "hierega"
       if(type=="ega.fit" & algo=="louvain") next  # Too slow
@@
   ega$glasso_louvain_ega, ega$TMFG_louvain_ega,
+  ega$glasso_louvain_riEGA, ega$glasso_walktrap_riEGA,
   ega$TMFG_walktrap_ega, ega$TMFG_walktrap_ega.fit,
+  ega$TMFG_louvain_riEGA, ega$TMFG_walktrap_riEGA, 
   labels=c("glasso_walktrap_ega", "glasso_walktrap_ega.fit",
            "glasso_louvain_ega", "TMFG_louvain_ega",
-           "TMFG_walktrap_ega", "TMFG_walktrap_ega.fit"),
-                          rows=3,
+           "glasso_louvain_riEGA", "glasso_walktrap_riEGA",
+           "TMFG_walktrap_ega", "TMFG_walktrap_ega.fit",
+           "TMFG_louvain_riEGA", "TMFG_walktrap_riEGA"),
+  rows=5,
   plot.all = FALSE)$all
@@
 
-patchwork::wrap_plots(lapply(ega, plot), nrow = 3)
+patchwork::wrap_plots(lapply(ega, plot), nrow = 4)
 ```
@@
 ```{r}
-ega <- ega$TMFG_walktrap_ega$EGA
-plot(ega)
-
-ega_scores <-  EGAnet::net.scores(bait, ega)$scores$std.scores |> 
+ega_final <- ega$glasso_walktrap_riEGA$EGA
+plot(ega_final)
+
+ega_scores <-  EGAnet::net.scores(bait, ega_final)$scores$std.scores |> 
   as.data.frame() |> 
-  setNames(c("EGA1", "EGA2")) 
+  setNames(c("EGA_Text", "EGA_Image", "EGA_Videos")) 
 ```
@@
 # Merge with data
-scores <- lavaan::predict(m1) |> 
+scores <- lavaan::predict(m3) |> 
   as.data.frame() |> 
-  data_rename(c("ML1", "ML2"), c("BAIT_SEM1", "BAIT_SEM2")) |> 
+  datawizard::data_addprefix("CFA_") |> 
+  # data_rename(c("ML1", "ML2"), c("BAIT_SEM1", "BAIT_SEM2")) |> 
   cbind(ega_scores) |> 
-  mutate(Participant = df$Participant) |>
-  mutate(BAIT = rowMeans(select(bait, -contains("Videos")), na.rm = TRUE))
+  mutate(Participant = df$Participant)
+
+scores$BAIT_Videos <- (bait$VideosRealistic + (1 - bait$VideosIssues)) / 2
+scores$BAIT_Images <- (bait$ImagesRealistic + (1 - bait$ImagesIssues) + bait$ImitatingReality + bait$EnvironmentReal) / 4
+scores$BAIT_Text <- (bait$TextRealistic + (1 - bait$TextIssues)) / 2
 
@@
 ```{r}
-correlation::cor_test(scores, "BAIT_SEM2", "BAIT") |> 
+correlation::cor_test(scores, "BAIT_Images", "CFA_Images") |> 
   plot() +
-  ggside::geom_xsidedensity(aes(x=BAIT_SEM2), color="grey", linewidth=1) +
-  ggside::geom_ysidedensity(aes(y=BAIT), color="grey", linewidth=1) +
+  ggside::geom_xsidedensity(aes(x=BAIT_Images), color="grey", linewidth=1) +
+  ggside::geom_ysidedensity(aes(y=CFA_Images), color="grey", linewidth=1) +
   ggside::scale_xsidey_continuous(expand = c(0, 0)) +
@@
 ```{r}
-table <- correlation::correlation(scores, 
+table <- correlation::correlation(
+  select(scores, starts_with("BAIT_")), 
   select(df, starts_with("GAAIS")),
@@
 df |> 
-  ggplot(aes(x=as.factor(AI_Knowledge), y=BAIT)) +
+  ggplot(aes(x=as.factor(AI_Knowledge), y=BAIT_Images)) +
   geom_boxplot()
@@
 # m <- betareg::betareg(BAIT ~ AI_Knowledge, data=df)
-m <- lm(BAIT ~ AI_Knowledge, data=df)
+m <- lm(BAIT_Images ~ poly(AI_Knowledge, 2), data=df)
 # m <- brms::brm(BAIT ~ mo(AI_Knowledge), data=df, algorithm = "meanfield")
@@
   ggplot(aes(x=AI_Knowledge, y=estimate)) +
-  geom_jitter2(data=df, aes(y=BAIT), alpha=0.2, width=0.1) +
+  geom_jitter2(data=df, aes(y=BAIT_Images), alpha=0.2, width=0.1) +
   geom_line(aes(group=1), position = position_dodge(width=0.2)) +
@@
 # m <- betareg::betareg(BAIT ~ Sex / Age, data=df, na.action=na.omit)
-m <- lm(BAIT ~ Sex / Age, data=df)
+m <- lm(BAIT_Images ~ Sex / Age, data=df)
 display(parameters::parameters(m))
@@
 ```{r}
-glm(Feedback_LabelsIncorrect ~ BAIT * AI_Knowledge, 
+glm(Feedback_LabelsIncorrect ~ BAIT_Images * AI_Knowledge, 
     data=mutate(df, Feedback_LabelsIncorrect = ifelse(Feedback_LabelsIncorrect=="True", 1, 0)), 
@@
 ```{r}
-glm(Feedback_LabelsReversed ~ BAIT * AI_Knowledge, 
+glm(Feedback_LabelsReversed ~ BAIT_Images * AI_Knowledge, 
     data=mutate(df, Feedback_LabelsReversed = ifelse(Feedback_LabelsReversed=="True", 1, 0)), 
@@
 ```{r}
-glm(Feedback_CouldDiscriminate ~ BAIT * AI_Knowledge, 
+glm(Feedback_CouldDiscriminate ~ BAIT_Images * AI_Knowledge, 
     data=mutate(df, Feedback_CouldDiscriminate = ifelse(Feedback_CouldDiscriminate=="True", 1, 0)), 
@@
 ```{r}
-glm(Feedback_CouldNotDiscriminate ~ BAIT * AI_Knowledge, 
+glm(Feedback_CouldNotDiscriminate ~ BAIT_Images * AI_Knowledge, 
     data=mutate(df, Feedback_CouldNotDiscriminate = ifelse(Feedback_CouldNotDiscriminate=="True", 1, 0)), 
@@
 ```{r}
-glm(Feedback_Fun ~ BAIT * AI_Knowledge, 
+glm(Feedback_Fun ~ BAIT_Images * AI_Knowledge, 
     data=mutate(df, Feedback_Fun = ifelse(Feedback_Fun=="True", 1, 0)), 
@@
 ```{r}
-glm(Feedback_Boring ~ BAIT * AI_Knowledge, 
+glm(Feedback_Boring ~ BAIT_Images * AI_Knowledge, 
     data=mutate(df, Feedback_Boring = ifelse(Feedback_Boring=="True", 1, 0)), 

### 2024-03-01 analysis/0_preprocessing.py

@@ -78,11 +78,13 @@ for i, file in enumerate(files):
     experimenter = "Readme (GitHub)" if experimenter in ["readme"] else experimenter
     experimenter = "RISC" if experimenter in ["risc"] else experimenter
     experimenter = "Snowball" if experimenter in ["snow", "snow〈"] else experimenter
+    experimenter = "SONA" if experimenter in ["sona"] else experimenter
 
     lang = "English" if browser["language"] == "en" else browser["language"]
     lang = "Italian" if lang == "it" else lang
     lang = "French" if lang == "fr" else lang
-    lang = "Colombia" if lang == "co" else lang
+    lang = "Colombian" if lang == "co" else lang
+    lang = "Spanish" if lang == "es" else lang
     if lang not in ["English", "Italian", "French"]:
         sex = json.loads(data[data["screen"] == "demographics_1"].iloc[0]["response"])
         if sex["Sex"] in ["Male", "Female", "Other"]:  # Fix
@@ -105,6 +107,12 @@ for i, file in enumerate(files):
         },
         index=[0],
     )
+
+    df["SONA_ID"] = np.nan
+    if "sona_id" in browser.index:
+        if np.isnan(browser["sona_id"]) == False:
+            id = int(browser["sona_id"])
+            df["SONA_ID"] = id
 
     # Demographics -------------------------------------------------------
     demo1 = data[data["screen"] == "demographics_1"].iloc[0]
@@ -166,6 +174,10 @@ for i, file in enumerate(files):
         "UK" if country in ["Uk", "England", "United Kingdom", "Brighton"] else country
     )
     country = "Netherlands" if country in ["The Netherlands"] else country
+    country = "Spain" if country in ["España"] else country
+    country = "Colombia" if country in ["Medellin"] else country
+    country = "Germany" if country in ["German"] else country
+    country = "Czech Republic" if country in ["Czechia"] else country
     country = "Pakistan" if country in ["Pk"] else country
     country = "Italy" if country in ["Italia"] else country
     country = "Belgium" if country in ["Belgique"] else country
@@ -181,6 +193,7 @@ for i, file in enumerate(files):
             "United States Of America",
             "Us,Texas",
             "Us",
+            "United States Of American",
         ]
         else country
     )
@@ -249,13 +262,26 @@ for i, file in enumerate(files):
             "Indonesian",
             "Asian-American",
             "Asian British",
[…]

### 2024-03-01 experiment/instructions_spanish.js

@@ -73,7 +73,7 @@ var text_feedback1_items = [
     "Sentí que las imágenes generadas por IA fueron más activantes que las fotos",
     " Sentí que las imágenes generadas por IA fueron menos activantes que las fotos",
     "Sentí que las categorías ('Fotografía' y 'Generada por IA') no fueron siempre correctas",
-    " Sentí que las categorías estaban al revés (e.g., 'Fotografía' para imágenes generadas por IA y viceversa)",
+    "Sentí que las categorías estaban al revés (e.g., 'Fotografía' para imágenes generadas por IA y viceversa)",
     "Algunas imágenes fueron realmente activantes",
     "Realmente no sentí nada cuando miraba las imágenes",
 ]

### 2024-03-25 analysis/1_cleaning.qmd
update

@@
 table_recruitment(filter(df, Language == "Colombian"))
+```
+
+#### Spanish
+
+```{r}
+#| message: false
+
+plot_recruitement(filter(df, Language == "Spanish"))
+table_recruitment(filter(df, Language == "Spanish"))
 ```
@@
   # "S399"  # Negative Arousal-Valence correlations
-  "S428",  # Only 0s for arousal (creates statistical problems)
-  "S498",  # Only 0s for arousal (creates statistical problems)
-  "S508"  # Only 0s for arousal (creates statistical problems)
 )
@@
 
-::: {.panel-tabset}
-
-#### 1-60
-
-```{r}
-#| fig-width: 15
-#| fig-height: 15
-
-plot_hist(dftask[dftask$Participant %in% df$Participant[1:60], ])
-```
-
-#### 61-120
-
-```{r}
-#| fig-width: 15
-#| fig-height: 15
-
-plot_hist(dftask[dftask$Participant %in% df$Participant[61:120], ])
-```
-
-#### 121-180
-
-```{r}
-#| fig-width: 15
-#| fig-height: 15
-
-plot_hist(dftask[dftask$Participant %in% df$Participant[121:180], ])
-```
-
-#### 181-240
-
-```{r}
-#| fig-width: 15
-#| fig-height: 15
-
-plot_hist(dftask[dftask$Participant %in% df$Participant[181:240], ])
-```
-
-#### 241-300
-
-```{r}
-#| fig-width: 15
-#| fig-height: 15
-
-plot_hist(dftask[dftask$Participant %in% df$Participant[241:264], ])
-```
-
-:::
+<!-- ::: {.panel-tabset} -->
+
+<!-- #### 1-60 -->
+
+<!-- ```{r} -->
+<!-- #| fig-width: 15 -->
+<!-- #| fig-height: 15 -->
+<!-- #| eval: false -->
+
+<!-- plot_hist(dftask[dftask$Participant %in% df$Participant[1:60], ]) -->
+<!-- ``` -->
+
+<!-- #### 61-120 -->
+
+<!-- ```{r} -->
+<!-- #| fig-width: 15 -->
+<!-- #| fig-height: 15 -->
+<!-- #| eval: false -->
+
+<!-- plot_hist(dftask[dftask$Participant %in% df$Participant[61:120], ]) -->
+<!-- ``` -->
+
+<!-- #### 121-180 -->
+
+<!-- ```{r} -->
+<!-- #| fig-width: 15 -->
+<!-- #| fig-height: 15 -->
+<!-- #| eval: false -->
+
+<!-- plot_hist(dftask[dftask$Participant %in% df$Participant[121:180], ]) -->
+<!-- ``` -->
+
+<!-- #### 181-240 -->
+
+<!-- ```{r} -->
+<!-- #| fig-width: 15 -->
+<!-- #| fig-height: 15 -->
+<!-- #| eval: false -->
+
+<!-- plot_hist(dftask[dftask$Participant %in% df$Participant[181:240], ]) -->
+<!-- ``` -->
+
+<!-- #### 241-300 -->
+
+<!-- ```{r} -->
+<!-- #| fig-width: 15 -->
+<!-- #| fig-height: 15 -->
+<!-- #| eval: false -->
+
+<!-- plot_hist(dftask[dftask$Participant %in% df$Participant[241:264], ]) -->
+<!-- ``` -->
+
+<!-- ::: -->
 
@@
 ```{r}
-# dftask[dftask$Participant == "S428", "Arousal"]
-# dftask[dftask$Participant == "S498", "Arousal"]
-# dftask[dftask$Participant == "S508", "Arousal"]
+# Single arousal response (0)
+outliers <- summarize(dftask, n = length(unique(Arousal)), .by="Participant") |> 
+  filter(n == 1) |> 
+  select(Participant) |> 
+  pull() |> 
+  c(outliers)
+
 dat <- dftask |> 
-  filter(!Participant %in% c("S428", "S498", "S508")) |> 
+  filter(!Participant %in% outliers) |> 
   summarize(cor_ArVal = cor(Arousal, Valence),
@@
 
-```{r}
-c(as.character(potentials$expe_duration$Participant), 
-  as.character(potentials$emo_diff$Participant), 
-  as.character(potentials$emo_cor$Participant)) |> 
-  table()
+We removed `r length(outliers)` that showed no variation in their arousal response.
+
+```{r}
+# c(as.character(potentials$expe_duration$Participant), 
+#   as.character(potentials$emo_diff$Participant), 
+#   as.character(potentials$emo_cor$Participant)) |> 
+#   table()
+#   
+df <- filter(df, !Participant %in% outliers)
+dftask <- filter(dftask, !Participant %in% outliers)
 ```
@@
 df <- filter(df, !Participant %in% outliers)
-dftask <- filter(dftask, Participant %in% df$Participant)
+dftask <- filter(dftask, !Participant %in% outliers)
 ```
@@
 p_language | p_expertise
+```
+
+### System
+
+```{r p_demographics_settings}
+df$Screen_Size <- sqrt(df$Screen_Width * df$Screen_Height)
+
+df |> 
+  ggplot(aes(x = Screen_Size)) +
+  geom_histogram() +
+  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
+  labs(x =  expression("Screen Size ("~sqrt(Number~of~Pixels)~")"), y = "Number of Participants", title = "Screen Size") +
+  theme_modern(axis.title.space = 15) +
+  theme(
+    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
+    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
+    axis.text.y = element_text(size = rel(1.1)),
+    axis.text.x = element_text(size = rel(1.1))
+  )
 ```
@@
         type="resampling",
-        plot.itemStability=FALSE,
+        plot.typicalStructure=FALSE,
         verbose=FALSE)
@@
   as.data.frame() |> 
-  setNames(c("EGA_Text", "EGA_Image", "EGA_Videos")) 
+  setNames(c("EGA_Image", "EGA_Videos", "EGA_Text")) 
 ```
@@
 
-df <- full_join(df, scores, by="Participant")
+df <- merge(df, scores, by="Participant")
 ```

### 2024-03-25 analysis/0_preprocessing.py

@@ -29,6 +29,8 @@ def osf_listfiles(data_subproject="", token="", after_date=None):
     return files
 
 
+
+
 token = "zYboMoukFI8HKabenQ35DH6tESHJo6oZll5BvOPma6Dppjqc2jnIB6sPCERCuaqO0UrHAa"  # Paste OSF token here to access private repositories
 files = osf_listfiles(
     token=token,
@@ -56,7 +58,7 @@ norm_data = pd.read_csv("../experiment/stimuli_selection/stimuli_data.csv").rena
 for i, file in enumerate(files):
     print(f"File N°{i+1}/{len(files)}")
 
-    if i > 0 and file["name"] in alldata_subs["Participant"].values:
+    if "Participant" in alldata_subs.columns and file["name"] in alldata_subs["Participant"].values:
         continue
     data = pd.read_csv(file["file"]._get(file["url"], stream=True).raw)
 
@@ -122,12 +124,13 @@ for i, file in enumerate(files):
     demo3 = data[data["screen"] == "demographics_other"].iloc[0]
     demo3 = json.loads(demo3["response"])
 
-    df["Age"] = int(demo2["Age"])
-    if df["Age"][0] < 18:
+    age = int(demo2["Age"])
+    if age < 18:
         continue
-    sex = (
-        "Male" if demo1["Sex"] in ["Maschio", "Masculin", "Masculino"] else demo1["Sex"]
-    )
+    if age > 100:
+        age = np.nan
+    df["Age"] = age
+    sex = "Male" if demo1["Sex"] in ["Maschio", "Masculin", "Masculino"] else demo1["Sex"]
     sex = "Female" if sex in ["Femmina", "Féminin", "Femenino"] else sex
     df["Sex"] = sex
     df["Language_Level"] = demo3["Language_Level"]
@@ -135,44 +138,21 @@ for i, file in enumerate(files):
 
     # Education
     edu = demo1["Education"]
-    edu = (
-        "Bachelor"
-        if any([x in edu for x in ["bachelor", "laurea triennale", "licence"]])
-        else edu
-    )
+    edu = "Bachelor" if any([x in edu for x in ["bachelor", "laurea triennale", "licence"]]) else edu
     edu = "Master" if any([x in edu for x in ["master", "laurea magistrale"]]) else edu
-    edu = (
-        "Doctorate"
-        if any([x in edu for x in ["doctorate", "dottorato", "doctorat", "Doctorado"]])
-        else edu
-    )
[…]

### 2024-05-24 analysis/1_cleaning.qmd
update data

@@
   mutate(across(everything(), ~ifelse(.x == "", NA, .x))) |>
-  mutate(Experimenter = case_when(
-    Language=="English" & Experimenter %in% c("reddit7", "reddit8", "reddit1", "reddit2", "reddit5") ~ "Reddit (other)",
+  mutate(Sample = case_when(
+    Language=="English" & str_detect(Experimenter, "reddit") ~ "Reddit",
+    Language=="English" & Experimenter %in% c("2discord1", "Experimenter2", "Experimenter1") ~ "Student",
+    Language=="English" & Experimenter %in% c("Unknown", "Readme (GitHub)", "website") ~ "Other",
     .default = Experimenter
@@
 #| message: false
+#| fig-width: 12
+#| fig-height: 12
 
@@
     mutate(Date = as.Date(Date, format = "%d/%m/%Y")) |> 
-    group_by(Date, Language, Experimenter) |> 
+    group_by(Date, Language, Sample) |> 
     summarize(N = n()) |> 
@@
     # https://bocoup.com/blog/padding-time-series-with-r
-    complete(Date, Language, Experimenter, fill = list(N = 0)) |> 
-    group_by(Language, Experimenter) |>
+    complete(Date, Language, Sample, fill = list(N = 0)) |> 
+    group_by(Language, Sample) |>
     mutate(N = cumsum(N)) |>
     ggplot(aes(x = Date, y = N)) +
-    geom_area(aes(fill=Experimenter)) +
+    geom_area(aes(fill=Sample)) +
     scale_y_continuous(expand = c(0, 0)) +
@@
 table_recruitment <- function(df) {
-  summarize(df, N = n(), .by=c("Language", "Experimenter")) |> 
+  summarize(df, N = n(), .by=c("Language", "Sample")) |> 
     arrange(desc(N)) |> 
@@
   labs(x="Feedback", y = "Participants", title = "Feedback") +
-  theme_modern(axis.title.space = 15) +
+  theme_minimal() +
   theme(
@@
            Comments = trimws(df$Feedback_Comments)) |> 
-  filter(!tolower(Comments) %in% c(NA, "no", "nope", "none", "na", "n/a", "non")) |> 
+  filter(!tolower(Comments) %in% c(NA, "no", "nope", "none", "na", "n/a", "non", ".", "..", "ninguno")) |> 
   arrange(Language, Source) |>
@@
 
-outliers <- c(
-  # "S206"  # Collapsed RTs in both phases
-  # "S399"  # Negative Arousal-Valence correlations
-)
-potentials <- list()
+outliers <- list()
 ```
@@
 
-We removed `r sum(df$Mobile=="True")` participants that participated with a mobile device.
-
-```{r}
-df <- filter(df, Mobile == "False")
+There were `r sum(df$Mobile=="True")` participants that used a mobile device.
+
+```{r}
+# df <- filter(df, Mobile == "False")
 dftask <- filter(dftask, Participant %in% df$Participant)
@@
   geom_vline(xintercept = median(df$Experiment_Duration), color = "red", linetype = "dashed") +
+  geom_vline(xintercept = 15, color = "orange", linetype = "dotted") +
   scale_shape_manual(values = c("extra" = 3, ok = 19)) +
@@
     x = "Duration (in minutes)",
-    y = "Participant"
+    y = "Participants"
   )  +
-  theme_bw() +
+  theme_modern() +
   ggside::theme_ggside_void() +
@@
 
-potentials$expe_duration <- arrange(df, Experiment_Duration) |>
-  select(Participant, Experiment_Duration) |>
-  head(5) 
+outliers$expe_duration <- filter(df, Experiment_Duration < 15)$Participant
 ```
@@
   geom_vline(xintercept = median(df$BAIT_Duration), color = "red", linetype = "dashed") +
+  geom_vline(xintercept = 0.5, color = "orange", linetype = "dotted") +
   scale_shape_manual(values = c("extra" = 3, ok = 19)) +
@@
   )  +
-  theme_bw() +
+  theme_modern() +
   ggside::theme_ggside_void() +
@@
           axis.text.y = element_blank())
-```
+
+outliers$bait_duration <- filter(df, BAIT_Duration < 0.5)$Participant
+df[df$Participant %in% outliers$bait_duration, str_detect(names(df), "BAIT_\\d+")] <- NA
+```
+
+We excluded the BAIT data of `r length(outliers$bait_duration)` participants who completed the questionnaire in less than 30 seconds.
 
 ### Response to Erotic Stimuli
+
+```{r}
+# Single arousal response (0)
+outliers$novariability <- summarize(dftask, n = length(unique(Arousal)), .by="Participant") |> 
+  filter(n == 1) |> 
+  select(Participant) |> 
+  pull()
+
+df <- filter(df, !Participant %in% outliers$novariability)
+dftask <- filter(dftask, !Participant %in% outliers$novariability)
+```
+
+We removed `r length(outliers$novariability)` that showed no variation in their arousal response (did not move the scales).
 
@@
 
-potentials$emo_diff <- arrange(dat, Arousal) |>
-  head(5)
+outliers$emo_diff <- sort(as.character(dat[dat$Arousal < 0, ]$Participant))
 ```
@@
 ```{r}
-# Single arousal response (0)
-outliers <- summarize(dftask, n = length(unique(Arousal)), .by="Participant") |> 
-  filter(n == 1) |> 
-  select(Participant) |> 
-  pull() |> 
-  c(outliers)
-
 dat <- dftask |> 
@@
 
-potentials$emo_cor <- arrange(dat, cor_ArVal) |>
-  head(5)
-```
-
-We removed `r length(outliers)` that showed no variation in their arousal response.
-
-```{r}
-# c(as.character(potentials$expe_duration$Participant), 
-#   as.character(potentials$emo_diff$Participant), 
-#   as.character(potentials$emo_cor$Participant)) |> 
-#   table()
-#   
-df <- filter(df, !Participant %in% outliers)
-dftask <- filter(dftask, !Participant %in% outliers)
+outliers$emo_cor <- sort(as.character(dat[dat$cor_ArEnt < 0, ]$Participant))
+
+outliers$arousal <- intersect(outliers$emo_diff, outliers$emo_cor)
+```
+
+We removed `r length(outliers$arousal)` participants that had a negative correlation between arousal and enticement, and had a negative arousal difference between erotic and neutral (suggesting a misunderstanding of the scale direction).
+
+```{r}
+df <- filter(df, !Participant %in% outliers$arousal)
+dftask <- filter(dftask, !Participant %in% outliers$arousal)
 ```
@@
 ## Final Sample
-
-```{r}
-df <- filter(df, !Participant %in% outliers)
-dftask <- filter(dftask, !Participant %in% outliers)
-```
 
@@
 df |> 
-  ggplot(aes(x = Screen_Size)) +
-  geom_histogram() +
+  ggplot(aes(x = Screen_Size, fill=Mobile)) +
+  geom_histogram(bins = 50, color="black") +
   scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
@@
   select(starts_with("BAIT_"), -BAIT_Duration) |> 
-  rename_with(function(x) gsub("BAIT_\\d_", "", x))
+  rename_with(function(x) gsub("BAIT_\\d_", "", x)) |> 
+  filter(!is.na(TextRealistic ))
 
@@
 
-efa <- parameters::factor_analysis(bait, cor=cor(bait), n=3, rotation = "oblimin", 
+efa <- parameters::factor_analysis(bait, cor=cor(bait, use="pairwise.complete.obs"), n=3, rotation = "oblimin", 
                                    sort=TRUE, scores="tenBerge", fm="ml")
@@
 ```{r}
-display(parameters::parameters(m3, standardize = TRUE))
+display(parameters::parameters(m4, standardize = TRUE))
+```
+
+```{r}
+m4b <- lavaan::sem(
+  "Environment =~ ImitatingReality + EnvironmentReal 
+  Images =~ ImagesRealistic + ImagesIssues
+  Videos =~ VideosIssues + VideosRealistic
+  Text =~ TextIssues + TextRealistic
+  G =~ Environment + Images + Videos + Text", 
+  data=bait)
+
+m4c <- lavaan::sem(
+  "Environment =~ ImitatingReality + EnvironmentReal 
+  Images =~ ImagesRealistic + ImagesIssues
+  Videos =~ VideosIssues + VideosRealistic
+  Text =~ TextIssues + TextRealistic
+  Visual =~ Environment + Images", 
+  data=bait)
+
+# bayestestR::bayesfactor_models(m1, m2)
+lavaan::anova(m4, m4b, m4c)
+```
+
+```{r}
+display(parameters::parameters(m4c, standardize = TRUE))
+```
+
+```{r}
+#| message: false
+#| warning: false
+
+library(ggraph)
+library(tidySEM)
+
+edges <- tidySEM::get_edges(m4c) |> 
+  mutate(sign = as.factor(sign(as.numeric(est_std))))
+
+tidygraph::tbl_graph(nodes = tidySEM::get_nodes(m4c), edges = edges) |> 
+  ggraph(layout = 'kk') + 
+  geom_edge_link(aes(filter=op=="=~", label=est_std, color=sign),
+                 angle_calc="along",
+                 label_dodge=unit(-0.015, "npc"),
+                 edge_width=1) + 
+  geom_edge_arc(aes(filter=op=="~~", label=est_std, color=sign), 
+                linetype="dashed", strength=0.1,
+                angle_calc="along",
+                label_dodge=unit(-0.015, "npc"),
+                edge_width=1) + 
+  geom_node_point(aes(shape=shape, color=shape), size=14, alpha=0.3) +
+  geom_node_text(aes(label = name)) + 
+  scale_edge_color_manual(values=c("1"="darkgreen", "-1"="red"), guide="none") +
+  scale_shape_manual(values=c("oval"="circle", "rect"="square"), guide="none") +
+  scale_color_manual(values=c("oval"="orange", "rect"="black"), guide="none") +
+  theme_void()
 ```
@@
 plot(ega_final)
-
+```
+
+### Scores
+
+```{r}
+#| code-fold: false
+
+# Merge with data
 ega_scores <-  EGAnet::net.scores(bait, ega_final)$scores$std.scores |> 
   as.data.frame() |> 
-  setNames(c("EGA_Image", "EGA_Videos", "EGA_Text")) 
-```
-
-### Scores
-
-```{r}
-#| code-fold: false
-
-# Merge with data
-scores <- lavaan::predict(m3) |> 
+  setNames(c("BAIT_Text_EGA", "BAIT_Visual_EGA", "BAIT_Videos_EGA"))
+
+sem_scores <- lavaan::predict(m4c) |> 
   as.data.frame() |> 
-  datawizard::data_addprefix("CFA_") |> 
-  # data_rename(c("ML1", "ML2"), c("BAIT_SEM1", "BAIT_SEM2")) |> 
-  cbind(ega_scores) |> 
-  mutate(Participant = df$Participant)
-
-scores$BAIT_Videos <- (bait$VideosRealistic + (1 - bait$VideosIssues)) / 2
-scores$BAIT_Images <- (bait$ImagesRealistic + (1 - bait$ImagesIssues) + bait$ImitatingReality + bait$EnvironmentReal) / 4
-scores$BAIT_Text <- (bait$TextRealistic + (1 - bait$TextIssues)) / 2
-
-df <- merge(df, scores, by="Participant")
+  datawizard::data_addprefix("BAIT_") |> 
+  datawizard::data_addsuffix("_SEM")
+
+raw_scores <- data.frame(
+  Participant = df[!is.na(df$BAIT_1_ImagesRealistic), ]$Participant,
+  BAIT_Videos = (bait$VideosRealistic + (1 - bait$VideosIssues)) / 2,
+  BAIT_Visual = (bait$ImagesRealistic + (1 - bait$ImagesIssues) + bait$ImitatingReality + bait$EnvironmentReal) / 4,
+  BAIT_Text = (bait$TextRealistic + (1 - bait$TextIssues)) / 2
+  )
+
+scores <- cbind(sem_scores, ega_scores, raw_scores) 
+df <- merge(df, raw_scores, by="Participant")
 ```
@@
 ```{r}
-correlation::cor_test(scores, "BAIT_Images", "CFA_Images") |> 
+correlation::cor_test(scores, "BAIT_Visual", "BAIT_Visual_SEM") |> 
   plot() +
-  ggside::geom_xsidedensity(aes(x=BAIT_Images), color="grey", linewidth=1) +
-  ggside::geom_ysidedensity(aes(y=CFA_Images), color="grey", linewidth=1) +
+  ggside::geom_xsidedensity(aes(x=BAIT_Visual), color="grey", linewidth=1) +
+  ggside::geom_ysidedensity(aes(y=BAIT_Visual_SEM), color="grey", linewidth=1) +
   ggside::scale_xsidey_continuous(expand = c(0, 0)) +
@@
 table <- correlation::correlation(
-  select(scores, starts_with("BAIT_")), 
+  select(df, all_of(names(raw_scores))), 
   select(df, starts_with("GAAIS")),
@@
 df |> 
-  ggplot(aes(x=as.factor(AI_Knowledge), y=BAIT_Images)) +
+  ggplot(aes(x=as.factor(AI_Knowledge), y=BAIT_Visual)) +
   geom_boxplot()
@@
 # m <- betareg::betareg(BAIT ~ AI_Knowledge, data=df)
-m <- lm(BAIT_Images ~ poly(AI_Knowledge, 2), data=df)
+m <- lm(BAIT_Visual ~ poly(AI_Knowledge, 2), data=df)
 # m <- brms::brm(BAIT ~ mo(AI_Knowledge), data=df, algorithm = "meanfield")
@@
   ggplot(aes(x=AI_Knowledge, y=estimate)) +
-  geom_jitter2(data=df, aes(y=BAIT_Images), alpha=0.2, width=0.1) +
+  ggdist::stat_halfeye(data=df, aes(y=BAIT_Visual), geom="slab") +
+  # ggdist::stat_dots(data=df, aes(y=BAIT_Visual), side="left") +
+  # geom_boxplot(data=df, aes(y=BAIT_Visual, group=AI_Knowledge)) +
+  geom_point2(data=df, aes(x=AI_Knowledge-0.08, y=BAIT_Visual), alpha=0.2, position=position_jitter(width=0.06), size=2) +
   geom_line(aes(group=1), position = position_dodge(width=0.2)) +
@@
   theme_minimal() +
-  labs(x = "AI-Knowledge", y="BAIT Score")
+  labs(x = "AI-Knowledge", y="BAIT - Visual")
 ```
@@
 # m <- betareg::betareg(BAIT ~ Sex / Age, data=df, na.action=na.omit)
-m <- lm(BAIT_Images ~ Sex / Age, data=df)
+m <- lm(BAIT_Visual ~ Sex / Age, data=df)
 display(parameters::parameters(m))
@@
 ```{r}
-glm(Feedback_LabelsIncorrect ~ BAIT_Images * AI_Knowledge, 
+glm(Feedback_LabelsIncorrect ~ BAIT_Visual * AI_Knowledge, 
     data=mutate(df, Feedback_LabelsIncorrect = ifelse(Feedback_LabelsIncorrect=="True", 1, 0)), 
@@
 ```{r}
-glm(Feedback_LabelsReversed ~ BAIT_Images * AI_Knowledge, 
+glm(Feedback_LabelsReversed ~ BAIT_Visual * AI_Knowledge, 
     data=mutate(df, Feedback_LabelsReversed = ifelse(Feedback_LabelsReversed=="True", 1, 0)), 
@@
 ```{r}
-glm(Feedback_CouldDiscriminate ~ BAIT_Images * AI_Knowledge, 
+glm(Feedback_CouldDiscriminate ~ BAIT_Visual * AI_Knowledge, 
     data=mutate(df, Feedback_CouldDiscriminate = ifelse(Feedback_CouldDiscriminate=="True", 1, 0)), 
@@
 ```{r}
-glm(Feedback_CouldNotDiscriminate ~ BAIT_Images * AI_Knowledge, 
+m <- glm(Feedback_CouldNotDiscriminate ~ BAIT_Visual * AI_Knowledge, 
     data=mutate(df, Feedback_CouldNotDiscriminate = ifelse(Feedback_CouldNotDiscriminate=="True", 1, 0)), 
-    family="binomial") |> 
-  parameters::parameters() |> 
+    family="binomial")
+
+parameters::parameters(m) |> 
   display(title="Predicting 'Hard to discriminate'")
-```
-
-```{r}
-glm(Feedback_Fun ~ BAIT_Images * AI_Knowledge, 
+
+modelbased::estimate_relation(m, length=6) |> 
+  plot()
+```
+
+```{r}
+glm(Feedback_Fun ~ BAIT_Visual * AI_Knowledge, 
     data=mutate(df, Feedback_Fun = ifelse(Feedback_Fun=="True", 1, 0)), 
@@
 ```{r}
-glm(Feedback_Boring ~ BAIT_Images * AI_Knowledge, 
+glm(Feedback_Boring ~ BAIT_Visual * AI_Knowledge, 
     data=mutate(df, Feedback_Boring = ifelse(Feedback_Boring=="True", 1, 0)), 

### 2024-05-24 analysis/0_preprocessing.py

@@ -29,9 +29,7 @@ def osf_listfiles(data_subproject="", token="", after_date=None):
     return files
 
 
-
-
-token = "zYboMoukFI8HKabenQ35DH6tESHJo6oZll5BvOPma6Dppjqc2jnIB6sPCERCuaqO0UrHAa"  # Paste OSF token here to access private repositories
+token = ""  # Paste OSF token here to access private repositories
 files = osf_listfiles(
     token=token,
     data_subproject="sm4jc",  # Data subproject ID
@@ -58,9 +56,17 @@ norm_data = pd.read_csv("../experiment/stimuli_selection/stimuli_data.csv").rena
 for i, file in enumerate(files):
     print(f"File N°{i+1}/{len(files)}")
 
-    if "Participant" in alldata_subs.columns and file["name"] in alldata_subs["Participant"].values:
+    if (
+        "Participant" in alldata_subs.columns
+        and file["name"] in alldata_subs["Participant"].values
+    ):
         continue
-    data = pd.read_csv(file["file"]._get(file["url"], stream=True).raw)
+
+    download_ok = False
+    while download_ok == False:
+        data = pd.read_csv(file["file"]._get(file["url"], stream=True).raw)
+        if len(data) > 0:
+            download_ok = True
 
     # Participant ========================================================
     # data["screen"].unique()
@@ -130,38 +136,71 @@ for i, file in enumerate(files):
     if age > 100:
         age = np.nan
     df["Age"] = age
-    sex = "Male" if demo1["Sex"] in ["Maschio", "Masculin", "Masculino"] else demo1["Sex"]
+    sex = (
+        "Male" if demo1["Sex"] in ["Maschio", "Masculin", "Masculino"] else demo1["Sex"]
+    )
     sex = "Female" if sex in ["Femmina", "Féminin", "Femenino"] else sex
+    sex = "Other" if sex in ["Autre", "Altro"] else sex
     df["Sex"] = sex
     df["Language_Level"] = demo3["Language_Level"]
     df["AI_Knowledge"] = demo3["AI_Knowledge"]
 
     # Education
     edu = demo1["Education"]
-    edu = "Bachelor" if any([x in edu for x in ["bachelor", "laurea triennale", "licence"]]) else edu
-    edu = "Master" if any([x in edu for x in ["master", "laurea magistrale"]]) else edu
-    edu = "Doctorate" if any([x in edu for x in ["doctorate", "dottorato", "doctorat", "Doctorado"]]) else edu
[…]

### 2024-05-24 analysis/1_models.R
Create 1_models.R

@@ -1,0 +1,37 @@
+# This script is an .R file as it is called from a High Performance Cluster.
+# The models that are generated are then saved locally and used in the analysis.
+# The compiled models are not shared due to repository size constraints.
+
+
+
+# Packages ----------------------------------------------------------------
+library(tidyverse)
+library(datawizard)
+library(brms)
+
+
+options(mc.cores = parallel::detectCores(),
+        brms.backend = "cmdstanr",
+        width = 300)
+
+log <- c("Packages" = TRUE)
+write.csv(as.data.frame(log), '/mnt/lustre/users/psych/dmm56/FictionEro/log.csv')
+
+# Data --------------------------------------------------------------------
+
+dfsub <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/main/data/data_participants.csv")
+df <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/main/data/data.csv") |>
+  dplyr::full_join(
+    dfsub[c("Participant", "Experimenter", "Language", "Feedback_LabelsIncorrect")],
+    by = join_by(Participant)
+  ) |>
+  # datawizard::rescale(select=c("Arousal", "Enticement", "Realness"), range=c(0, 1), to=c(0.001, 0.999)) |>
+  # datawizard::rescale(select=c("Valence"), range=c(-1, 1), to=c(0.001, 0.999)) |>
+  datawizard::rescale(select=c("Valence"), range=c(-1, 1), to=c(0, 1)) |>
+  dplyr::mutate(Condition = forcats::fct_relevel(Condition, "Photograph", "AI-Generated"),
+         Relevance =  forcats::fct_relevel(Relevance, "Relevant", "Irrelevant", "Non-erotic"),
+         Sex =  forcats::fct_relevel(Sex, "Male", "Female"),
+         Feedback_LabelsIncorrect =  forcats::fct_relevel(Feedback_LabelsIncorrect, "False", "True"))
+
+log <- c(log, "Data" = TRUE)
+write.csv(as.data.frame(log), '/mnt/lustre/users/psych/dmm56/FictionEro/log.csv')

### 2024-05-24 analysis/1_models.R
Update 1_models.R

@@ -3,18 +3,25 @@
 # The compiled models are not shared due to repository size constraints.
 
 
+# Options -----------------------------------------------------------------
+
+iter <- 1000
+cores <- parallel::detectCores()
+
+options(mc.cores = cores,
+        brms.backend = "cmdstanr",
+        width = 300)
+
+log <- c("Cores" = cores)
+write.csv(as.data.frame(log), '/mnt/lustre/users/psych/dmm56/FictionEro/log.csv')
+
 
 # Packages ----------------------------------------------------------------
 library(tidyverse)
 library(datawizard)
 library(brms)
 
-
-options(mc.cores = parallel::detectCores(),
-        brms.backend = "cmdstanr",
-        width = 300)
-
-log <- c("Packages" = TRUE)
+log <- c(log, "Packages" = TRUE)
 write.csv(as.data.frame(log), '/mnt/lustre/users/psych/dmm56/FictionEro/log.csv')
 
 # Data --------------------------------------------------------------------
@@ -35,3 +42,27 @@ df <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/main
 
 log <- c(log, "Data" = TRUE)
 write.csv(as.data.frame(log), '/mnt/lustre/users/psych/dmm56/FictionEro/log.csv')
+
+
+
+# Baseline Models --------------------------------------------------------
+
+t0 <- Sys.time()
+
+f <- brms::bf(Arousal ~  0 + Intercept + Sex / Relevance +
+                 (0 + Intercept + Relevance|Participant) +
+                 (0 + Intercept + Relevance|Item))
+
+m_baseline_arousal_linear <- brms::brm(data=df,
+            algorithm="sampling",
+            init = 0,
+            seed=123,
+            refresh=0,
+            iter=200,
+            chains=cores)
+
+t1 <- Sys.time()
+
+log <- c(log, "m1" = TRUE)
+write.csv(as.data.frame(log), '/mnt/lustre/users/psych/dmm56/FictionEro/log.csv')
+save(m_baseline_arousal_linear, file="/mnt/lustre/users/psych/dmm56/FictionEro/m_baseline_arousal_linear.Rdata")

### 2024-06-06 analysis/1_cleaning.qmd
make analysis html not self contained so that we can easily access the figures

@@
     code-fold: true
-    self-contained: true
+    self-contained: false
     toc: true
@@
   mutate(Sample = case_when(
-    Language=="English" & str_detect(Experimenter, "reddit") ~ "Reddit",
-    Language=="English" & Experimenter %in% c("2discord1", "Experimenter2", "Experimenter1") ~ "Student",
-    Language=="English" & Experimenter %in% c("Unknown", "Readme (GitHub)", "website") ~ "Other",
+    Language=="English" & Experimenter %in% c("2discord1", "Experimenter2", "Experimenter1") ~ "Students (Non-incentivized)",
+    Language=="English" & Experimenter %in% c("Unknown", "Readme (GitHub)", "website", "reddit") ~ "General Population",
+    Experimenter %in% c("enter", "macre", "piaca", "unime", "classroom1") ~ "Students (Non-incentivized)",
+    Experimenter %in% c("SONA") ~ "Students (Incentivized)",
+    Experimenter %in% c("gacon", "mafas", "marmar", "mavio", "sobon", "RISC", "Snowball") ~ "General Population",
+    str_detect(Experimenter, "reddit") ~ "General Population",
     .default = Experimenter
@@
 table_recruitment <- function(df) {
-  summarize(df, N = n(), .by=c("Language", "Sample")) |> 
+  summarize(df, N = n(), .by=c("Language", "Experimenter")) |> 
     arrange(desc(N)) |> 
@@
 # df <- filter(df, Mobile == "False")
-dftask <- filter(dftask, Participant %in% df$Participant)
+# dftask <- filter(dftask, Participant %in% df$Participant)
 ```
@@
 
-df <- filter(df, Sex != "Other" & SexualOrientation != "Other")
+df <- filter(df, !(Sex == "Other" | SexualOrientation == "Other"))
 dftask <- filter(dftask, Participant %in% df$Participant)
@@
 p_sexprofile
+```
+
+```{r p_pornfactor}
+#| fig-width: 14
+#| fig-height: 14
+
+dat <- select(df, COPS_Duration_1, COPS_Frequency_2, SexualActivity) |> 
+    mutate(across(where(is.character), as.factor)) |> 
+    mutate(across(where(is.factor), as.numeric))
+
+r <- correlation::correlation(
+  dat) |> 
+  as.matrix()
+
+r <- parameters::factor_analysis(dat, n = 1, rotation = "oblimin", cor = r)
+df$Porn <- get_scores(r)[, 1]
 ```
@@
 ```{r}
+n <- n_factors(select(df, starts_with("GAAIS")))
+n
+parameters::factor_analysis(
+  select(df, starts_with("GAAIS")), 
+  n=2, 
+  rotation="oblimin")
+
+df$GAAIS_Negative <- rowMeans(select(df, starts_with("GAAIS_Negative")))
+df$GAAIS_Positive <- rowMeans(select(df, starts_with("GAAIS_Positive")))
+```
+
+```{r}
 table <- correlation::correlation(
@@
 
+```{r}
+glm(Feedback_AILessArousing ~ BAIT_Visual * AI_Knowledge, 
+    data=mutate(df, Feedback_AILessArousing = ifelse(Feedback_AILessArousing=="True", 1, 0)), 
+    family="binomial") |> 
+  parameters::parameters() |> 
+  display(title="Predicting 'AI was less arousing'")
+```
+
+```{r}
+glm(Feedback_AIMoreArousing ~ BAIT_Visual * AI_Knowledge, 
+    data=mutate(df, Feedback_AIMoreArousing = ifelse(Feedback_AIMoreArousing=="True", 1, 0)), 
+    family="binomial") |> 
+  parameters::parameters() |> 
+  display(title="Predicting 'AI was more arousing'")
+```
+
 :::
@@
 
+setdiff(unique(df$Participant), unique(dftask$Participant))
 write.csv(df, "../data/data_participants.csv", row.names = FALSE)

### 2024-06-06 analysis/2_emotions.qmd
@AnafNeves I pushed the 2_emotions script
you can go through it and make sure you can re-run its chunks

---
title: "FictionEro - Affective Impact of Fiction"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
execute: 
  cache: true
---

## Data Preparation

```{r}
#| message: false
#| warning: false

library(tidyverse)
library(easystats)
library(patchwork)
library(ggside)
library(glmmTMB)

options(mc.cores = parallel::detectCores(),
        brms.backend = "cmdstanr",
        width = 300)
```

```{r}
dfsub <- read.csv("../data/data_participants.csv")
df <- read.csv("../data/data.csv") |> 
  right_join(
    select(dfsub, Participant, Sample, Language, Mobile, starts_with("Feedback_"), 
           BAIT_Visual, BAIT_Text, AI_Knowledge, SexualActivity, 
           GAAIS_Negative, GAAIS_Positive, Porn, COPS_Frequency_2,
           -Feedback_Comments),
    by = "Participant"
    ) |> 
  datawizard::rescale(select=c("Valence"), range=c(-1, 1), to=c(0, 1)) |> 
  mutate(Condition = fct_relevel(Condition, "Photograph", "AI-Generated"),
         Relevance =  fct_relevel(Relevance, "Relevant", "Irrelevant", "Non-erotic"),
         Sex =  fct_relevel(Sex, "Male", "Female"),
         PornFrequency = as.numeric(as.factor(COPS_Frequency_2)),
         SexualActivity_num = as.numeric(as.factor(SexualActivity)),
         ConditionBelief = case_when(
           Condition == "Photograph" & Realness > 0.5 ~ "True",
           Condition == "AI-Generated" & Realness < 0.5 ~ "True",
           .default = "False"
         )) |> 
  mutate(across(starts_with("Feedback_"), function(x) {fct_relevel(x, "False", "True")}))

results_table <- function(model, effects="fixed", filter=NULL) {
  if("marginaleffects" %in% class(model)) {
    model |> 
      parameters::parameters() |> 
      as.data.frame() |> 
      select(-Parameter, -SE, -S, z=Statistic, -Predicted) |> 
      insight::format_table() |> 
      parameters::display()
  } else {
    display(parameters::parameters(model, effects=effects, keep=filter))
  }
}
```

## Manipulation Check

This section is about selecting the best model and performing the **manipulation check**: Neutral vs. Emotional

::: {.panel-tabset}

### Arousal

```{r}
df |> 
  mutate(Arousal_Extreme = ifelse(Arousal %in% c(0, 1), "Extreme", "Not extreme")) |>
  ggplot(aes(x=Arousal, fill=Relevance)) +
  geom_histogram(aes(color=Arousal_Extreme), position = "identity", bins=80) +
  facet_grid(Relevance~Sex, scales="free_y") +
  scale_color_manual(values=c("red", "white"), guide="none") +
  scale_fill_manual(values=c("Relevant"="#E91E63", "Irrelevant"="#FF9800", "Non-erotic"="#03A9F4"), guide="none") +
  scale_y_sqrt(expand = c(0, 0)) +
  labs(title = "Arousal") +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))
```

The *Arousal* data is composed of a mixture of extreme responses (0 and 1) and non-extreme responses between 0 and 1, lending itself to ordered beta model [(Kubinec, 2022)](https://doi.org/10.1017/pan.2022.20), designed explicitly for data with upper and lower bounds, such as survey slider scales. It is a more parsimonious evolution of the zero-and-one inflated beta (ZOIB) regression model (see [this tutorial](https://www.andrewheiss.com/blog/2021/11/08/beta-regression-guide/)) that jointly models the probability of extreme responses, the probability of 1 vs. 0, and the mean and spread of the rest of the responses.

```{r}
#| eval: false

# Get a sense of Random Factors
m1 <- glmmTMB::glmmTMB(Arousal ~ Sex / Relevance + (1|Participant) + (1|Item), data=df)
m2 <- glmmTMB::glmmTMB(Arousal ~ Sex / Relevance + (1+Relevance|Participant) + (1|Item), data=df)
m3 <- glmmTMB::glmmTMB(Arousal ~ Sex / Relevance + (1|Participant) + (1+Sex|Item), data=df)
m4 <- glmmTMB::glmmTMB(Arousal ~ Sex / Relevance + (1|Participant) + (1+Relevance|Item), data=df)
m5 <- glmmTMB::glmmTMB(Arousal ~ Sex / Relevance + (1|Participant) + (1+Sex / Relevance|Item), data=df)
m6 <- glmmTMB::glmmTMB(Arousal ~ Sex / Relevance + (1+Relevance|Participant) + (1+Sex|Item), data=df)
m7 <- glmmTMB::glmmTMB(Arousal ~ Sex / Relevance + (1+Relevance|Participant) + (1+Relevance|Item), data=df)

rbind(
  mutate(performance::icc(m1, by_group=TRUE), Model = "m1"),
  data.frame(Group = "Conditional R2", ICC = performance::r2(m1)$R2_conditional, Model = "m1"),
  mutate(performance::icc(m2, by_group=TRUE), Model = "m2"),
  data.frame(Group = "Conditional R2", ICC = performance::r2(m2)$R2_conditional, Model = "m2"),
  mutate(performance::icc(m3, by_group=TRUE), Model = "m3"),
  data.frame(Group = "Conditional R2", ICC = performance::r2(m3)$R2_conditional, Model = "m3"),
  mutate(performance::icc(m4, by_group=TRUE), Model = "m4"),
  data.frame(Group = "Conditional R2", ICC = performance::r2(m4)$R2_conditional, Model = "m4"),
  mutate(performance::icc(m5, by_group=TRUE), Model = "m5"),
  data.frame(Group = "Conditional R2", ICC = performance::r2(m5)$R2_conditional, Model = "m5"),
  mutate(performance::icc(m6, by_group=TRUE), Model = "m6"),
  data.frame(Group = "Conditional R2", ICC = performance::r2(m6)$R2_conditional, Model = "m6"),
  mutate(performance::icc(m7, by_group=TRUE), Model = "m7"),
  data.frame(Group = "Conditional R2", ICC = performance::r2(m7)$R2_conditional, Model = "m7")
) |>
  ggplot(aes(x = Model, y = ICC, color=Group)) +
  geom_line(aes(group=Group))

test_bf(m6, m1, m2, m3, m4, m5, m7)
compare_performance(m2, m7)

# It seems like the full model, with the effect of relevance on participants and items, is the best.
```

```{r}
m <- glmmTMB::glmmTMB(Arousal ~ Sex / Relevance + (Relevance | Participant) + (1|Item),
                      data=df, family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))
                      # control = glmmTMB::glmmTMBControl(optimizer=stats::optim, # nlminb, optim
                      #                                   optArgs = list(method = "BFGS"),  #Nelder-Mead, BFGS, CG
                      #                                   parallel = 8))
```

```{r}
results_table(m)

estimate_relation(m) |> 
  ggplot(aes(x=Relevance, y=Predicted)) +
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color=Relevance), position=position_dodge(width=0.5)) +
  scale_color_manual(values=c("Relevant"="#E91E63", "Irrelevant"="#FF9800", "Non-erotic"="#03A9F4"), guide="none") +
  labs(y="Arousal") +
  facet_wrap(~Sex) +
  theme_abyss()
```

### Enticement

```{r}
df |> 
  mutate(Enticement_Extreme = ifelse(Enticement %in% c(0, 1), "Extreme", "Not extreme")) |>
  ggplot(aes(x=Enticement, fill=Relevance)) +
  geom_histogram(aes(color=Enticement_Extreme), position = "identity", bins=80) +
  facet_grid(Relevance~Sex, scales="free_y") +
  scale_color_manual(values=c("red", "white"), guide="none") +
  scale_fill_manual(values=c("Relevant"="#E91E63", "Irrelevant"="#FF9800", "Non-erotic"="#03A9F4"), guide="none") +
  scale_y_sqrt(expand = c(0, 0)) +
  labs(title = "Enticement") +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))
```

```{r}
m <- glmmTMB::glmmTMB(Enticement ~ Sex / Relevance + (Relevance | Participant) + (1|Item),
                      data=df, family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))
```

```{r}
results_table(m)

estimate_relation(m) |> 
  ggplot(aes(x=Relevance, y=Predicted)) +
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color=Relevance), position=position_dodge(width=0.5)) +
  scale_color_manual(values=c("Relevant"="#E91E63", "Irrelevant"="#FF9800", "Non-erotic"="#03A9F4"), guide="none") +
  labs(y="Enticement") +
  facet_wrap(~Sex) +
  theme_abyss()
```

### Valence

```{r}
df |> 
  mutate(Valence_Extreme = ifelse(Valence %in% c(0, 1), "Extreme", "Not extreme")) |>
  ggplot(aes(x=Valence, fill=Relevance)) +
  geom_histogram(aes(color=Valence_Extreme), position = "identity", bins=80) +
  facet_grid(Relevance~Sex, scales="free_y") +
  scale_color_manual(values=c("red", "white"), guide="none") +
  scale_fill_manual(values=c("Relevant"="#E91E63", "Irrelevant"="#FF9800", "Non-erotic"="#03A9F4"), guide="none") +
  scale_y_sqrt(expand = c(0, 0)) +
  labs(title = "Valence") +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))
```

```{r}
m <- glmmTMB::glmmTMB(Valence ~ Sex / Relevance + (Relevance | Participant) + (1|Item),
                      data=df, family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))
```

```{r}
results_table(m)

estimate_relation(m) |> 
  ggplot(aes(x=Relevance, y=Predicted)) +
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color=Relevance), position=position_dodge(width=0.5)) +
  scale_color_manual(values=c("Relevant"="#E91E63", "Irrelevant"="#FF9800", "Non-erotic"="#03A9F4"), guide="none") +
  labs(y="Enticement") +
  facet_wrap(~Sex) +
  theme_abyss()
```

:::

## Arousal

```{r}
#| fig-height: 12
#| fig-width: 7

plot_descriptive <- function(df, target="Arousal") {
  # By item
  order <- df |>
    mutate(.Item_Order = paste0(Relevance, "_", Sex, "_", Item)) |>
    summarize(mean = mean(.data[[target]], na.rm=TRUE), .by=c("Condition", ".Item_Order")) |> 
    arrange(.Item_Order, desc(Condition)) |> 
    mutate(diff = sign(mean - lag(mean)),
           Relevance = str_extract(.Item_Order, "^[^_]+"),
           .Item_Order = str_extract(.Item_Order, "(?<=_).+")) |>
    filter(Condition == "Photograph") |> 
    arrange(Relevance, diff, mean)

  p1 <- df |>
    mutate(.Item_Order = paste0(Sex, "_", Item)) |>
    group_by(.Item_Order, Condition) |>
    ggdist::mean_qi(.data[[target]], .width=0.95) |>
    mutate(Sex = fct_rev(str_extract(.Item_Order, "^[^_]+"))) |>
    left_join(order[c(".Item_Order", "diff")], by=".Item_Order") |>
    mutate(.Item_Order = fct_relevel(.Item_Order, order$.Item_Order)) |>
    # mutate(.average = mean(.data[[target]]), .by="Item") |>
    # mutate(Item = fct_reorder(Item, .average)) |>
    ggplot(aes(y = .Item_Order, x=.data[[target]])) +
    geom_line(aes(color=as.factor(diff)), linewidth=1) +
    geom_point(aes(color=Condition), size=2) +

    # ggdist::stat_slabinterval(aes(fill=Condition, color=Condition),
    #                           .width=0.95, normalize="xy", slab_alpha=0.5) +
    # ggdist::stat_histinterval(aes(fill=Condition, color=Condition),
    #                           .width=0.95, normalize="xy", slab_alpha=0.5) +
    scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336", "1"="#F44336", "-1"="#2196F3"),
                       breaks = c('AI-Generated', 'Photograph')) +
    # scale_fill_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
    scale_y_discrete(labels = function(x) str_extract(x, "(?<=_).+")) +
    theme_minimal() +
    theme(panel.grid.minor.x = element_blank(),
          # panel.grid.major.x = element_blank(),
          panel.border = element_blank(),
          axis.line.x = element_blank()) +
    labs(title = paste0(target, " by Item"), color="Condition", y="Items") +
    facet_wrap(~Sex, scales="free_y")

  # By participant
  p2 <- df |>
    summarize(.average = mean(.data[[target]]),
              .by=c("Sex", "Participant", "Condition")) |>
    pivot_wider(names_from = Condition, values_from = .average) |>
    mutate(.diff = Photograph - `AI-Generated`) |>
    mutate(Participant = fct_reorder(Participant, .diff)) |>
    ggplot(aes(x = .diff, y=Participant)) +
    geom_bar(aes(fill=.diff), stat = "identity")  +
    scale_fill_gradient2(guide="none", low="red", high="red", mid="blue") +
    labs(title = paste0(target, " by Participant")) +
    facet_wrap(~Sex, ncol=2, scales="free_y") +
    theme_minimal() +
    theme(panel.grid.major.y = element_blank(),
          panel.border = element_blank(),
          axis.line.x = element_blank(),
          axis.text.y = element_blank()) +
    labs(title = paste0(target, " by Participant"), x="Difference (Photograph - AI-Generated)", y="Participants")

  p1 / p2 + plot_layout(heights = c(2, 1))
}

plot_descriptive(df, "Arousal")
```

### Whole Sample

```{r}
m_arousal <- glmmTMB::glmmTMB(Arousal ~ Sex / Relevance / Condition + 
                                (Relevance | Participant) + (1|Item),
                      data=df, family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

results_table(m_arousal)

marginaleffects::avg_slopes(m_arousal, variables="Condition", by="Sex", re.form=NA) |> 
  results_table()
```

### Subsamples

::: {.panel-tabset}

#### Sample

```{r}
m <- glmmTMB::glmmTMB(Arousal ~ Sample / Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
                      data=df, 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

results_table(m, filter="Condition")
```

#### Mobile

```{r}
m <- glmmTMB::glmmTMB(Arousal ~ Mobile / Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
                      data=df, 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

results_table(m, filter="Condition")
```

:::

### Moderators

```{r}
test_moderator <- function(df, outcome="Arousal", moderator="BAIT_Visual") {
  f <- paste0(outcome, " ~ Sex / (Condition * ", moderator, ") + (Condition | Participant) + (1|Item)")
  r <- glmmTMB::glmmTMB(as.formula(f),
                      data=filter(df, Relevance == "Relevant"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8)) |>
    parameters::parameters() |> 
    as.data.frame() |> 
    select(-df_error, -Effects, -Group, -Component, -SE)
  r$Moderator <- moderator
  r$Outcome <- outcome
  insight::format_table(r[c(7, 8), ])
}

moderator_results <- data.frame()
for(m in c("BAIT_Visual", "BAIT_Text", "AI_Knowledge",
           "GAAIS_Positive", "GAAIS_Negative",
           "Porn", "PornFrequency", "SexualActivity_num")) {
  moderator_results <- rbind(moderator_results,
                             test_moderator(df, "Arousal", m))
}

display(moderator_results)
```

```{r}
feedback_results <- data.frame()
for(m in c("Feedback_CouldDiscriminate", "Feedback_CouldNotDiscriminate",
           "Feedback_AIMoreArousing", "Feedback_AILessArousing", 
           "Feedback_LabelsIncorrect", "Feedback_LabelsReversed")) {
  feedback_results <- rbind(feedback_results,
                            test_moderator(df, "Arousal", m))
}
display(feedback_results)
```

### Believed

```{r}
m <- glmmTMB::glmmTMB(Arousal ~ Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
                      data=filter(df, ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

results_table(m)

moderator_believed <- data.frame()
for(m in c("BAIT_Visual", "BAIT_Text", "AI_Knowledge",
           "GAAIS_Positive", "GAAIS_Negative",
           "Porn", "PornFrequency", "SexualActivity_num", 
           "Feedback_CouldDiscriminate", "Feedback_CouldNotDiscriminate",
           "Feedback_AIMoreArousing", "Feedback_AILessArousing", 
           "Feedback_LabelsIncorrect", "Feedback_LabelsReversed")) {
  moderator_believed <- rbind(moderator_believed,
                             test_moderator(filter(df, ConditionBelief == "True"), "Arousal", m))
}

display(filter(moderator_believed, p < .1))
```

## Enticement

```{r}
#| fig-height: 12
#| fig-width: 7

plot_descriptive(df, "Enticement")
```

### Whole Sample

```{r}
m_enticement <- glmmTMB::glmmTMB(Enticement ~ Sex / Relevance / Condition + 
                                   (Relevance | Participant) + (1|Item),
                      data=df, family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

results_table(m_enticement)

marginaleffects::avg_slopes(m_enticement, variables="Condition", by="Sex", re.form=NA) |> 
  results_table()
```

### Subsamples

::: {.panel-tabset}

#### Sample

```{r}
m <- glmmTMB::glmmTMB(Enticement ~ Sample / Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
                      data=df, 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

results_table(m, filter="Condition")
```

#### Mobile

```{r}
m <- glmmTMB::glmmTMB(Enticement ~ Mobile / Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
                      data=df, 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

results_table(m, filter="Condition")
```

:::

### Moderators

```{r}
for(m in c("BAIT_Visual", "BAIT_Text", "AI_Knowledge",
           "GAAIS_Positive", "GAAIS_Negative",
           "Porn", "PornFrequency", "SexualActivity_num")) {
  moderator_results <- rbind(moderator_results,
                             test_moderator(df, "Enticement", m))
}

display(filter(moderator_results, Outcome == "Enticement"))
```

```{r}
for(m in c("Feedback_CouldDiscriminate", "Feedback_CouldNotDiscriminate",
           "Feedback_AIMoreArousing", "Feedback_AILessArousing", 
           "Feedback_LabelsIncorrect", "Feedback_LabelsReversed")) {
  feedback_results <- rbind(feedback_results,
                            test_moderator(df, "Enticement", m))
}
display(filter(feedback_results, Outcome == "Enticement"))
```

```{r}
m <- glmmTMB::glmmTMB(Arousal ~ Sex / (Condition * SexualActivity_num) + (Condition | Participant) + (1|Item),
                      data=filter(df, ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

results_table(m)

estimate_relation(m, length=20) |> 
  ggplot(aes(x=SexualActivity_num, y=Predicted)) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high, fill=Condition), alpha=0.2) +
  geom_line(aes(color=Condition)) +
  facet_grid(~Sex)
```

### Believed

```{r}
m <- glmmTMB::glmmTMB(Enticement ~ Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
                      data=filter(df, ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

results_table(m)

moderator_believed <- data.frame()
for(m in c("BAIT_Visual", "BAIT_Text", "AI_Knowledge",
           "GAAIS_Positive", "GAAIS_Negative",
           "Porn", "PornFrequency", "SexualActivity_num", 
           "Feedback_CouldDiscriminate", "Feedback_CouldNotDiscriminate",
           "Feedback_AIMoreArousing", "Feedback_AILessArousing", 
           "Feedback_LabelsIncorrect", "Feedback_LabelsReversed")) {
  moderator_believed <- rbind(moderator_believed,
                             test_moderator(filter(df, ConditionBelief == "True"), "Enticement", m))
}

display(filter(moderator_believed, p < .1))
```

## Valence

```{r}
#| fig-height: 12
#| fig-width: 7

plot_descriptive(df, "Valence")
```

### Whole Sample

```{r}
m_valence <- glmmTMB::glmmTMB(Valence ~ Sex / Relevance / Condition + 
                                (Relevance | Participant) + (1|Item),
                      data=df, family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

results_table(m_valence)

marginaleffects::avg_slopes(m_valence, variables="Condition", by="Sex", re.form=NA) |> 
  results_table()
```

### Subsamples

::: {.panel-tabset}

#### Sample

```{r}
m <- glmmTMB::glmmTMB(Valence ~ Sample / Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
                      data=df, 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

results_table(m, filter="Condition")
```

#### Mobile

```{r}
m <- glmmTMB::glmmTMB(Valence ~ Mobile / Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
                      data=df, 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

results_table(m, filter="Condition")
```

:::

### Moderators

```{r}
for(m in c("BAIT_Visual", "BAIT_Text", "AI_Knowledge",
           "GAAIS_Positive", "GAAIS_Negative",
           "Porn", "PornFrequency", "SexualActivity_num")) {
  moderator_results <- rbind(moderator_results,
                             test_moderator(df, "Valence", m))
}

display(filter(moderator_results, Outcome == "Valence"))
```

```{r}
for(m in c("Feedback_CouldDiscriminate", "Feedback_CouldNotDiscriminate",
           "Feedback_AIMoreArousing", "Feedback_AILessArousing", 
           "Feedback_LabelsIncorrect", "Feedback_LabelsReversed")) {
  feedback_results <- rbind(feedback_results,
                            test_moderator(df, "Valence", m))
}
display(filter(feedback_results, Outcome == "Valence"))
```

### Believed

```{r}
m <- glmmTMB::glmmTMB(Valence ~ Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
                      data=filter(df, ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

results_table(m)

moderator_believed <- data.frame()
for(m in c("BAIT_Visual", "BAIT_Text", "AI_Knowledge",
           "GAAIS_Positive", "GAAIS_Negative",
           "Porn", "PornFrequency", "SexualActivity_num", 
           "Feedback_CouldDiscriminate", "Feedback_CouldNotDiscriminate",
           "Feedback_AIMoreArousing", "Feedback_AILessArousing", 
           "Feedback_LabelsIncorrect", "Feedback_LabelsReversed")) {
  moderator_believed <- rbind(moderator_believed,
                             test_moderator(filter(df, ConditionBelief == "True"), "Valence", m))
}

display(filter(moderator_believed, p < .1))
```

## Emotionality (Combined Factor)

```{r}
pca <- principal_components(df[c("Valence", "Arousal", "Enticement")], n = 2)
pca
df$Emotionality <- normalize(predict(pca)$PC1)

df |> 
  mutate(Emotionality_Extreme = ifelse(Emotionality %in% c(0, 1), "Extreme", "Not extreme")) |>
  ggplot(aes(x=Emotionality, fill=Relevance)) +
  geom_histogram(aes(color=Emotionality_Extreme), position = "identity", bins=80) +
  facet_grid(Relevance~Sex, scales="free_y") +
  scale_color_manual(values=c("red", "white"), guide="none") +
  scale_fill_manual(values=c("Relevant"="#E91E63", "Irrelevant"="#FF9800", "Non-erotic"="#03A9F4"), guide="none") +
  scale_y_sqrt(expand = c(0, 0)) +
  labs(title = "Emotionality") +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))
```

```{r}
#| fig-height: 12
#| fig-width: 7

plot_descriptive(df, "Emotionality")
```

### Whole Sample

```{r}
m <- glmmTMB::glmmTMB(Emotionality ~ Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
                      data=df, family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

results_table(m)

marginaleffects::avg_slopes(m, variables="Condition", by="Sex", re.form=NA) |> 
  results_table()
```

### Subsamples

::: {.panel-tabset}

#### Sample

```{r}
m <- glmmTMB::glmmTMB(Emotionality ~ Sample / Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
                      data=df, 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

results_table(m, filter="Condition")
```

#### Mobile

```{r}
m <- glmmTMB::glmmTMB(Emotionality ~ Mobile / Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
                      data=df, 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

results_table(m, filter="Condition")
```

:::

### Moderators

```{r}
for(m in c("BAIT_Visual", "BAIT_Text", "AI_Knowledge",
           "GAAIS_Positive", "GAAIS_Negative",
           "Porn", "PornFrequency", "SexualActivity_num")) {
  moderator_results <- rbind(moderator_results,
                             test_moderator(df, "Emotionality", m))
}

display(filter(moderator_results, Outcome == "Emotionality"))
```

```{r}
for(m in c("Feedback_CouldDiscriminate", "Feedback_CouldNotDiscriminate",
           "Feedback_AIMoreArousing", "Feedback_AILessArousing", 
           "Feedback_LabelsIncorrect", "Feedback_LabelsReversed")) {
  feedback_results <- rbind(feedback_results,
                            test_moderator(df, "Emotionality", m))
}
display(filter(feedback_results, Outcome == "Emotionality"))
```

### Believed

```{r}
m <- glmmTMB::glmmTMB(Emotionality ~ Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
                      data=filter(df, ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

results_table(m)

moderator_believed <- data.frame()
for(m in c("BAIT_Visual", "BAIT_Text", "AI_Knowledge",
           "GAAIS_Positive", "GAAIS_Negative",
           "Porn", "PornFrequency", "SexualActivity_num", 
           "Feedback_CouldDiscriminate", "Feedback_CouldNotDiscriminate",
           "Feedback_AIMoreArousing", "Feedback_AILessArousing", 
           "Feedback_LabelsIncorrect", "Feedback_LabelsReversed")) {
  moderator_believed <- rbind(moderator_believed,
                             test_moderator(filter(df, ConditionBelief == "True"), "Emotionality", m))
}

display(filter(moderator_believed, p < .1))
```

## Figures

```{r}
#| fig-height: 7
#| fig-width: 7

pred1 <- rbind(
  marginaleffects::predictions(m_arousal, by=c("Sex", "Relevance", "Condition"), newdata = "marginalmeans", re.form=NA) |>
  as.data.frame() |> 
  mutate(Outcome="Arousal"),
  marginaleffects::predictions(m_enticement, by=c("Sex", "Relevance", "Condition"), newdata = "marginalmeans", re.form=NA) |>
  as.data.frame() |> 
  mutate(Outcome="Enticement"),
  marginaleffects::predictions(m_valence, by=c("Sex", "Relevance", "Condition"), newdata = "marginalmeans", re.form=NA) |>
  as.data.frame() |> 
  mutate(Outcome="Valence")
)

stars1 <- data.frame(label=c("***", "***", "*", "***"), 
                    Sex=fct_relevel(c("Male", "Male", "Male", "Male"), "Male"), 
                    Relevance=c("Relevant", "Relevant", "Non-erotic", "Relevant"), 
                    Outcome=c("Arousal", "Enticement", "Enticement", "Valence"),
                    y=c(0.75, 0.8, 0.2, 0.8))

p1 <- pred1 |>
  mutate(Sex = fct_relevel(Sex, "Male", "Female")) |> 
  ggplot(aes(x=Relevance, y=estimate)) +
  geom_hline(yintercept=0, color="darkgrey") +
  geom_line(aes(group=Condition, color=Condition), position = position_dodge(width=0.2), alpha=0.8, linewidth=0.2) +
  geom_pointrange(aes(ymin = conf.low, ymax=conf.high, color=Condition), position = position_dodge(width=0.2), size=0.2) +
  geom_text(data=stars1, aes(y=y, label=label), hjust=0.5, size=3) +
  geom_rect(data=data.frame(Type="All trials", estimate=0.1, Sex=as.factor("Male"), Outcome="Arousal", Relevance="Relevant"), 
            aes(xmin=0.8, xmax=1.2, ymin=0.5, ymax=0.80), color="#8BC34A", alpha=0) +
  geom_rect(data=data.frame(Type="All trials", estimate=0.1, Sex=as.factor("Female"), Outcome="Arousal", Relevance="Relevant"), 
            aes(xmin=0.8, xmax=1.2, ymin=0.2, ymax=0.5), color="#8BC34A", alpha=0) +
  facet_grid(Outcome~Sex, switch="y") +
  scale_y_continuous(limits=c(0, 1), labels=scales::percent) +
  scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
  theme_minimal() +
  theme(axis.title.y = element_blank(),
        axis.title.x = element_blank(),
        axis.text.y = element_text(size = 8),
        strip.placement = "outside",
        strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
        strip.text.x = element_text(size = 10),
        strip.text.y = element_text(size = 10),
        axis.text.x = element_text(angle=25, hjust=1, vjust=1.1, size=9, color="black"),
        legend.text = element_text(size = 10),
        legend.position = ) +
  labs(color="Images presented as:",
       tag = "A")
p1
```

```{r}
m1 <- glmmTMB::glmmTMB(Arousal ~ Sex / Condition + (Condition | Participant) + (1|Item),
                      data=filter(df, Relevance=="Relevant"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))
m2 <- glmmTMB::glmmTMB(Arousal ~ Sex / Condition + (Condition | Participant) + (1|Item),
                      data=filter(df, Relevance=="Relevant", ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))
m3 <- glmmTMB::glmmTMB(Arousal ~ Sex / Condition  + (Condition | Participant) + (1|Item),
                      data=filter(df, Relevance=="Relevant", ConditionBelief == "True", Feedback_AILessArousing=="True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

stars2 <- data.frame(label=c("***", "***", "***", "***", "*"), 
                    Sex=fct_relevel(c("Male", "Male", "Male", "Female", "Female"), 
                                    "Male", "Female"), 
                    Type=c("All trials", "Believed trials", "'AI was less arousing'", "Believed trials", "'AI was less arousing'"), 
                    y=c(0.76, 0.76, 0.76, 0.45, 0.45))

pred2 <- rbind(
  estimate_relation(m1) |> 
    mutate(Type = "All trials"),
  estimate_relation(m2) |> 
    mutate(Type = "Believed trials"),
  estimate_relation(m3) |> 
    mutate(Type = "'AI was less arousing'")
)

p2 <- pred2 |> 
  mutate(Type = fct_relevel(Type, "All trials", "Believed trials", "'AI was less arousing'")) |> 
  ggplot(aes(x=Type, y=Predicted)) +
  geom_hline(yintercept=0, color="darkgrey") +
  geom_line(aes(group=Condition, color=Condition), position = position_dodge(width=0.2), alpha=0.8, linewidth=0.1) +
  geom_bar(stat="identity", aes(fill=Condition), position = position_dodge(width=0.2), width=0.2, alpha=0.6) +
  geom_pointrange(aes(ymin = CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.2), size=0.2) +
  geom_rect(data=data.frame(Type="All trials", Predicted=0.1, Sex=as.factor("Male")), 
            aes(xmin=0.7, xmax=1.3, ymin=0.55, ymax=0.7), color="#8BC34A", alpha=0) +
  geom_rect(data=data.frame(Type="All trials", Predicted=0.1, Sex=as.factor("Female")), 
            aes(xmin=0.7, xmax=1.3, ymin=0.25, ymax=0.4), color="#8BC34A", alpha=0) +
  geom_text(data=stars2, aes(y=y, label=label), hjust=0.5, size=3) +
  facet_grid(~Sex) +
  scale_y_continuous(labels=scales::percent) +
  scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
  scale_fill_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
  labs(y="Arousal",
       tag = "B") +
  theme_minimal() +
  theme(axis.title.x = element_blank(),
        axis.text.x = element_text(angle=25, hjust=1, vjust=1.1, size=9),
        axis.text.y = element_text(size = 8),
        axis.title.y = element_text(size = 10),
        strip.placement = "outside",
        strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
        strip.text.x = element_text(size = 10),
        legend.position = "none")

p1 | p2
```

```{r}
#| fig-width: 10
#| fig-height: 8

m6 <- glm(Feedback_AILessArousing ~ Sex / BAIT_Visual, 
    data=mutate(dfsub, Feedback_AILessArousing = ifelse(Feedback_AILessArousing=="True", 1, 0)), 
    family="binomial")

results_table(m6)

pred3 <- estimate_relation(m6, length=50)

p3 <- pred3 |> 
  mutate(Sex = fct_relevel(Sex, "Male", "Female")) |> 
  ggplot(aes(x=BAIT_Visual, y=Predicted)) +
  geom_hline(yintercept=0, color="darkgrey") +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high), alpha=0.3) + 
  geom_line() +
  geom_text(data=data.frame(Sex = as.factor("Male")), aes(x=0.65, y=0.25), label="**") +
  facet_grid(~Sex) +
  scale_y_continuous(labels=scales::percent, expand=c(0, 0)) +
  scale_x_continuous(breaks = c(0.3, 0.5, 0.7, 0.9)) +
  labs(y = "\nProbability of 'AI was less arousing' Feedback\n",
       x = "\nBeliefs about Artificial Information Technology (BAIT)\n'AI algorithms can generate realistic images'",
       tag = "C") +
  theme_minimal() +
  theme(strip.text = element_blank(),
        axis.text.y = element_text(size = 8),
        axis.title.y = element_text(size = 10),
        axis.text.x = element_text(size = 8),
        axis.title.x = element_text(size = 10))

p4 <- patchwork::wrap_plots(p2 / p3 + plot_layout(heights = c(1, 1.6)))
p <- patchwork::wrap_plots(p1 | p4, guides="collect")
p
ggsave("figures/figure1.png", p, width=10, height=8, dpi=300)
```

```{r}
#| eval: false

m4 <- glmmTMB::glmmTMB(Arousal ~ SexualActivity / Sex / Condition + (Condition | Participant) + (1|Item),
                      data=filter(df, Relevance=="Relevant", ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

summary(m4)

pred3 <- estimate_relation(m4) 
pred3 |> 
  mutate(xnum = as.numeric(as.factor(SexualActivity))) |>
  ggplot(aes(x=SexualActivity, y=Predicted)) +
  # geom_ribbon(aes(x=xnum, ymin=CI_low, ymax=CI_high, fill=Condition), alpha=0.5) +
  geom_line(aes(group=Condition, color=Condition), position = position_dodge(width=0.2)) +
  geom_pointrange(aes(ymin = CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.2)) +
  facet_grid(~Sex)

m5 <- glmmTMB::glmmTMB(Arousal ~ Sex / (Condition * GAAIS_Negative) + (Condition | Participant) + (1|Item),
                      data=filter(df, Relevance=="Relevant", ConditionBelief == "True"), 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))
summary(m5)

pred4 <- estimate_relation(m5, length=30) 
pred4 |> 
  ggplot(aes(x=GAAIS_Negative, y=Predicted)) +
  geom_line(aes(group=Condition, color=Condition)) +
  facet_grid(~Sex) 
```

<!-- ## Realness -->

<!-- ### Physical Characteristics -->

<!-- ```{r} -->
<!-- m <- glmmTMB::glmmTMB(Realness ~ Entropy + Complexity + Contrast + Luminance + (1|Participant) + (1|Item), data=df) -->
<!-- results_table(m) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- m <- glmmTMB::glmmTMB(Realness ~ Sex / (Relevance / Condition) + (1|Participant) + (1|Item), data=df, family=beta_family(link = "logit")) -->
<!-- results_table(m) -->
<!-- ``` -->

### 2024-06-06 analysis/old_2_intraindividual.qmd
@AnafNeves I pushed the 2_emotions script
you can go through it and make sure you can re-run its chunks

---
title: "FictionEro - Intraindividual Effects"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: true
    toc: true
---

## Data Preparation

```{r}
#| message: false
#| warning: false

library(tidyverse)
library(easystats)
library(patchwork)
library(ggside)
library(glmmTMB)

options(mc.cores = parallel::detectCores(),
        brms.backend = "cmdstanr",
        width = 300)
```

```{r}
dfsub <- read.csv("../data/data_participants.csv")
df <- read.csv("../data/data.csv") |> 
  right_join(
    dfsub[c("Participant", "Experimenter", "Language", "Mobile", "Feedback_LabelsIncorrect")],
    by = "Participant"
    ) |> 
  # datawizard::rescale(select=c("Arousal", "Enticement", "Realness"), range=c(0, 1), to=c(0.001, 0.999)) |> 
  # datawizard::rescale(select=c("Valence"), range=c(-1, 1), to=c(0.001, 0.999)) |> 
  datawizard::rescale(select=c("Valence"), range=c(-1, 1), to=c(0, 1)) |> 
  mutate(Condition = fct_relevel(Condition, "Photograph", "AI-Generated"),
         Relevance =  fct_relevel(Relevance, "Relevant", "Irrelevant", "Non-erotic"),
         Sex =  fct_relevel(Sex, "Male", "Female"),
         Feedback_LabelsIncorrect =  fct_relevel(Feedback_LabelsIncorrect, "False", "True"))

results_table <- function(model, effects="fixed") {
  display(parameters::parameters(model, effects=effects))
}
```

## Model Selection

This section is about selecting the best model and performing the **manipulation check**: Neutral vs. Emotional

### Arousal

```{r}
df |> 
  mutate(Arousal_Extreme = ifelse(Arousal %in% c(0, 1), "Extreme", "Not extreme")) |>
  ggplot(aes(x=Arousal, fill=Relevance)) +
  geom_histogram(aes(color=Arousal_Extreme), position = "identity", bins=80) +
  facet_grid(Relevance~Sex, scales="free_y") +
  scale_color_manual(values=c("red", "white"), guide="none") +
  scale_fill_manual(values=c("Relevant"="#E91E63", "Irrelevant"="#FF9800", "Non-erotic"="#03A9F4"), guide="none") +
  scale_y_continuous(expand = c(0, 0)) +
  labs(title = "Arousal") +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))
```

The *Arousal* data is composed of a mixture of extreme responses (0 and 1) and non-extreme responses between 0 and 1, lending itself to a zero-and-one inflated beta (ZOIB) regression model (see [this tutorial](https://www.andrewheiss.com/blog/2021/11/08/beta-regression-guide/)). They jointly model the probability of extreme responses, the probability of 1 vs. 0, and the mean and spread of the rest of the responses.

```{r}
#| eval: false

# Get a sense of Random Factors
m1 <- glmmTMB::glmmTMB(Arousal ~ Sex / Relevance + (1|Participant) + (1|Item), data=df)
m2 <- glmmTMB::glmmTMB(Arousal ~ Sex / Relevance + (1+Relevance|Participant) + (1|Item), data=df)
m3 <- glmmTMB::glmmTMB(Arousal ~ Sex / Relevance + (1|Participant) + (1+Sex|Item), data=df)
m4 <- glmmTMB::glmmTMB(Arousal ~ Sex / Relevance + (1|Participant) + (1+Relevance|Item), data=df)
m5 <- glmmTMB::glmmTMB(Arousal ~ Sex / Relevance + (1|Participant) + (1+Sex / Relevance|Item), data=df)
m6 <- glmmTMB::glmmTMB(Arousal ~ Sex / Relevance + (1+Relevance|Participant) + (1+Sex|Item), data=df)
m7 <- glmmTMB::glmmTMB(Arousal ~ Sex / Relevance + (1+Relevance|Participant) + (1+Relevance|Item), data=df)

rbind(
  mutate(performance::icc(m1, by_group=TRUE), Model = "m1"),
  data.frame(Group = "Conditional R2", ICC = performance::r2(m1)$R2_conditional, Model = "m1"),
  mutate(performance::icc(m2, by_group=TRUE), Model = "m2"),
  data.frame(Group = "Conditional R2", ICC = performance::r2(m2)$R2_conditional, Model = "m2"),
  mutate(performance::icc(m3, by_group=TRUE), Model = "m3"),
  data.frame(Group = "Conditional R2", ICC = performance::r2(m3)$R2_conditional, Model = "m3"),
  mutate(performance::icc(m4, by_group=TRUE), Model = "m4"),
  data.frame(Group = "Conditional R2", ICC = performance::r2(m4)$R2_conditional, Model = "m4"),
  mutate(performance::icc(m5, by_group=TRUE), Model = "m5"),
  data.frame(Group = "Conditional R2", ICC = performance::r2(m5)$R2_conditional, Model = "m5"),
  mutate(performance::icc(m6, by_group=TRUE), Model = "m6"),
  data.frame(Group = "Conditional R2", ICC = performance::r2(m6)$R2_conditional, Model = "m6"),
  mutate(performance::icc(m7, by_group=TRUE), Model = "m7"),
  data.frame(Group = "Conditional R2", ICC = performance::r2(m7)$R2_conditional, Model = "m7")
) |>
  ggplot(aes(x = Model, y = ICC, color=Group)) +
  geom_line(aes(group=Group))

test_bf(m6, m1, m2, m3, m4, m5, m7)
compare_performance(m2, m7)

# It seems like the full model, with the effect of relevance on participants and items, is the best.
```

#### Model Comparison

```{r}
#| echo: false

load("models/m_baseline_arousal_linear.RData")
load("models/m_baseline_arousal_beta.RData")
load("models/m_baseline_arousal_zoib.RData")
load("models/m_baseline_arousal_ordbeta.RData")
```

```{r}
pred <- as.data.frame(t(brms::posterior_predict(m_baseline_arousal_linear, ndraws=50))) |>
  datawizard::data_addprefix("m_baseline_arousal_linear") |>
  cbind(
    as.data.frame(t(brms::posterior_predict(m_baseline_arousal_beta, ndraws=50))) |>
      datawizard::data_addprefix("m_baseline_arousal_beta") |>
      select_if(\(x) length(unique(x)) > 2),
    as.data.frame(t(brms::posterior_predict(m_baseline_arousal_zoib, ndraws=50))) |>
      datawizard::data_addprefix("m_baseline_arousal_zoib") |>
      select_if(\(x) length(unique(x)) > 2),
    as.data.frame(t(brms::posterior_predict(m_baseline_arousal_ordbeta, ndraws=50))) |>
      datawizard::data_addprefix("m_baseline_arousal_ordbeta") |>
      select_if(\(x) length(unique(x)) > 2)
  ) |>
  cbind(df)

rbind(
  estimate_density(select(pred, starts_with("m_baseline_arousal_linear"), Sex, Relevance),
                   method="KernSmooth", at=c("Sex", "Relevance")) |>
    mutate(Prediction = "Linear"),
  estimate_density(select(pred, starts_with("m_baseline_arousal_beta"), Sex, Relevance),
                   method="KernSmooth", at=c("Sex", "Relevance")) |>
    mutate(Prediction = "Beta"),
  estimate_density(select(pred, starts_with("m_baseline_arousal_zoib"), Sex, Relevance),
                   method="KernSmooth", at=c("Sex", "Relevance")) |>
    mutate(Prediction = "ZOIB"),
  estimate_density(select(pred, starts_with("m_baseline_arousal_ordbeta"), Sex, Relevance),
                   method="KernSmooth", at=c("Sex", "Relevance")) |>
    mutate(Prediction = "OrdBeta")
) |>
  mutate(Prediction = fct_relevel(Prediction, "Linear", "Beta", "ZOIB", "OrdBeta")) |>
  ggplot(aes(x=x, y=y, color=Relevance)) +
  geom_line(aes(group=interaction(Parameter, Sex, Relevance)),
            linewidth=0.5, alpha=0.3) +
  geom_line(data=estimate_density(df, select="Arousal", method="KernSmooth", at=c("Sex", "Relevance")),
            linewidth=1) +
   scale_color_manual(values=c("Relevant"="#E91E63", "Irrelevant"="#FF9800", "Non-erotic"="#03A9F4")) +
  facet_grid(Prediction~Sex) +
  coord_cartesian(ylim=c(0, 15), xlim=c(0, 1)) +
  theme_minimal()

brms::loo_compare(brms::add_criterion(m_baseline_arousal_linear, "loo"),
                  brms::add_criterion(m_baseline_arousal_beta, "loo"),
                  brms::add_criterion(m_baseline_arousal_zoib, "loo"),
                  brms::add_criterion(m_baseline_arousal_ordbeta, "loo")) |> 
  report()
```

#### Model Description

```{r}
summary(m3, robust=TRUE, priors=TRUE)
# performance::variance_decomposition(m2)
# brms::bayes_R2(m2)
# performance::icc(m1, by_group=TRUE)
```

### Enticement

```{r}
df |> 
  mutate(Enticement_Extreme = ifelse(Enticement %in% c(0, 1), "Extreme", "Not extreme")) |>
  ggplot(aes(x=Enticement, fill=Relevance)) +
  geom_histogram(aes(color=Enticement_Extreme), position = "identity", bins=80) +
  facet_grid(Relevance~Sex, scales="free_y") +
  scale_color_manual(values=c("red", "white")) +
  scale_fill_manual(values=c("Relevant"="#E91E63", "Irrelevant"="#FF9800", "Non-erotic"="#03A9F4")) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(title = "Enticement") +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))
```

## Arousal

### Descriptive

```{r}
plot_descriptive <- function(df, target="Arousal") {
  # By item
  order <- df |>
    mutate(.Item_Order = paste0(Relevance, "_", Sex, "_", Item)) |>
    summarize(mean = mean(.data[[target]], na.rm=TRUE), .by=c("Condition", ".Item_Order")) |> 
    arrange(.Item_Order, desc(Condition)) |> 
    mutate(diff = sign(mean - lag(mean)),
           Relevance = str_extract(.Item_Order, "^[^_]+"),
           .Item_Order = str_extract(.Item_Order, "(?<=_).+")) |>
    filter(Condition == "Photograph") |> 
    arrange(Relevance, diff, mean)

  p1 <- df |>
    mutate(.Item_Order = paste0(Sex, "_", Item)) |>
    group_by(.Item_Order, Condition) |>
    ggdist::mean_qi(.data[[target]], .width=0.95) |>
    mutate(Sex = fct_rev(str_extract(.Item_Order, "^[^_]+"))) |>
    left_join(order[c(".Item_Order", "diff")], by=".Item_Order") |>
    mutate(.Item_Order = fct_relevel(.Item_Order, order$.Item_Order)) |>
    # mutate(.average = mean(.data[[target]]), .by="Item") |>
    # mutate(Item = fct_reorder(Item, .average)) |>
    ggplot(aes(y = .Item_Order, x=.data[[target]])) +
    geom_line(aes(color=as.factor(diff)), linewidth=1) +
    geom_point(aes(color=Condition), size=2) +

    # ggdist::stat_slabinterval(aes(fill=Condition, color=Condition),
    #                           .width=0.95, normalize="xy", slab_alpha=0.5) +
    # ggdist::stat_histinterval(aes(fill=Condition, color=Condition),
    #                           .width=0.95, normalize="xy", slab_alpha=0.5) +
    scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336", "1"="#F44336", "-1"="#2196F3"),
                       breaks = c('AI-Generated', 'Photograph')) +
    # scale_fill_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
    scale_y_discrete(labels = function(x) str_extract(x, "(?<=_).+")) +
    theme_minimal() +
    theme(panel.grid.minor.x = element_blank(),
          # panel.grid.major.x = element_blank(),
          panel.border = element_blank(),
          axis.line.x = element_blank()) +
    labs(title = paste0(target, " by Item"), color="Condition", y="Items") +
    facet_wrap(~Sex, scales="free_y")

  # By participant
  p2 <- df |>
    summarize(.average = mean(.data[[target]]),
              .by=c("Sex", "Participant", "Condition")) |>
    pivot_wider(names_from = Condition, values_from = .average) |>
    mutate(.diff = Photograph - `AI-Generated`) |>
    mutate(Participant = fct_reorder(Participant, .diff)) |>
    ggplot(aes(x = .diff, y=Participant)) +
    geom_bar(aes(fill=.diff), stat = "identity")  +
    scale_fill_gradient2(guide="none", low="red", high="red", mid="blue") +
    labs(title = paste0(target, " by Participant")) +
    facet_wrap(~Sex, ncol=2, scales="free_y") +
    theme_minimal() +
    theme(panel.grid.major.y = element_blank(),
          panel.border = element_blank(),
          axis.line.x = element_blank(),
          axis.text.y = element_blank()) +
    labs(title = paste0(target, " by Participant"), x="Difference (Photograph - AI-Generated)", y="Participants")

  p1 / p2 + plot_layout(heights = c(2, 1))
}

plot_descriptive(df, "Arousal")
```

```{r}
m <- glmmTMB::glmmTMB(Arousal ~ Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
                 data=df, family=glmmTMB::ordbeta())
summary(m)

m <- glmmTMB::glmmTMB(Arousal ~ Sex / Condition + (Condition | Participant) + (1|Item),
                 data=filter(df, Relevance=="Relevant"), 
                 family=glmmTMB::ordbeta())
summary(m)

m <- glmmTMB::glmmTMB(Arousal ~ Mobile / Sex / Condition + (Condition | Participant) + (1|Item),
                 data=filter(df, Relevance=="Relevant"), 
                 family=glmmTMB::ordbeta())
summary(m)

m <- glmmTMB::glmmTMB(Arousal ~ Language / Sex / Condition + (Condition | Participant) + (1|Item),
                 data=filter(df, Relevance=="Relevant", Language != "Spanish"), 
                 family=glmmTMB::ordbeta())
summary(m)

m <- glmmTMB::glmmTMB(Arousal ~ Feedback_LabelsIncorrect / Sex / Condition + (Condition | Participant) + (1|Item),
                 data=filter(df, Relevance=="Relevant", Language != "Spanish"), 
                 family=glmmTMB::ordbeta())
summary(m)
```

### Simple Linear Model

```{r}
m <- brms::brm(Arousal ~  0 + Intercept + Sex / (Relevance / Condition) +
                 (0 + Intercept + (Relevance / Condition)|Participant) +
                 (0 + Intercept + (Relevance / Condition)|Item), 
               data=df,
               algorithm = "meanfield",
               init = 0,
               seed=123,
               iter=30000)

summary(m, robust=TRUE, priors=TRUE)
```

### Model Specification

```{r}
formula <- brms::bf(Arousal ~  0 + Intercept + Sex / (Relevance / Condition) +
                 (0 + Intercept + (Relevance / Condition)|Participant) +
                 (0 + Intercept + (Relevance / Condition)|Item),
               # Precision (spread) of the 0-1 values
               phi ~ 0 + Intercept + Sex / (Relevance) +
                 (0 + Intercept + (Relevance)|Participant) +
                 (0 + Intercept + (Relevance)|Item),
               # Zero and one inflation (probability of extreme response)
               zoi ~ 0 + Intercept + Sex / Relevance +
                 (0 + Intercept|Participant),
               # Conditional one inflation (when extreme, probability of 1)
               coi ~ 0 + Intercept + Sex / Relevance +
                 (0 + Intercept|Item),
               family=brms::zero_one_inflated_beta)

# brms::get_prior(formula, data = df)
priors <- c(
  # Mu
  # brms::set_prior("normal(0, 3)", class = "b", dpar=""),  # qlogis(0.5) plogis(0)
  brms::set_prior("normal(0, 1)", class = "b", dpar="", coef = "Intercept"),  
  brms::set_prior("normal(-0.4, 1)", class = "b", dpar="", coef = "SexFemale"),  
  brms::set_prior("normal(-1.8, 1)", class = "b", coef = c("SexMale:RelevanceIrrelevant")),
  brms::set_prior("normal(-0.3, 1)", class = "b", coef = c("SexFemale:RelevanceIrrelevant")),
  brms::set_prior("normal(-1.7, 1)", class = "b", coef = c("SexMale:RelevanceNonMerotic")),
  brms::set_prior("normal(-1, 1)", class = "b", coef = c("SexFemale:RelevanceNonMerotic")),

  # Fiction
  brms::set_prior("normal(0, 1)", class = "b", coef = c("SexFemale:RelevanceRelevant:ConditionAIMGenerated",
                                                        "SexFemale:RelevanceIrrelevant:ConditionAIMGenerated",
                                                        "SexFemale:RelevanceNonMerotic:ConditionAIMGenerated",
                                                        "SexMale:RelevanceRelevant:ConditionAIMGenerated",
                                                        "SexMale:RelevanceIrrelevant:ConditionAIMGenerated",
                                                        "SexMale:RelevanceNonMerotic:ConditionAIMGenerated")),
  # Phi
  # brms::set_prior("normal(0, 3)", class = "b", dpar="phi"),
  brms::set_prior("normal(1.3, 0.5)", class = "b", dpar="phi", coef = "Intercept"),
  brms::set_prior("normal(-0.02, 0.5)", class = "b", dpar="phi", coef = "SexFemale"),  
  brms::set_prior("normal(0.4, 0.5)", class = "b", dpar="phi", coef = c("SexMale:RelevanceIrrelevant")),
  brms::set_prior("normal(0, 0.5)", class = "b", dpar="phi", coef = c("SexFemale:RelevanceIrrelevant")),
  brms::set_prior("normal(0.1, 0.5)", class = "b", dpar="phi", coef = c("SexMale:RelevanceNonMerotic")),
  brms::set_prior("normal(0.1, 0.5)", class = "b", dpar="phi", coef = c("SexFemale:RelevanceNonMerotic")),

  # ZOI
  # brms::set_prior("normal(0, 2)", class = "b", dpar="zoi"),
  brms::set_prior("normal(-2.3, 2)", class = "b", dpar="zoi", coef = "Intercept"),
  brms::set_prior("normal(1.42, 2)", class = "b", dpar="zoi", coef = "SexFemale"),
  brms::set_prior("normal(2.8, 2)", class = "b", dpar="zoi", coef = c("SexMale:RelevanceIrrelevant")),
  brms::set_prior("normal(0, 2)", class = "b", dpar="zoi", coef = c("SexFemale:RelevanceIrrelevant")),
  brms::set_prior("normal(3.16, 2)", class = "b", dpar="zoi", coef = c("SexMale:RelevanceNonMerotic")),
  brms::set_prior("normal(1.60, 2)", class = "b", dpar="zoi", coef = c("SexFemale:RelevanceNonMerotic")),

  # COI
  # brms::set_prior("normal(0, 5)", class = "b", dpar="coi"),
  brms::set_prior("normal(0.6, 5)", class = "b", dpar="coi", coef = "Intercept"),
  brms::set_prior("normal(-2.7, 5)", class = "b", dpar="coi", coef = "SexFemale"),
  brms::set_prior("normal(-7, 5)", class = "b", dpar="coi", coef = c("SexMale:RelevanceIrrelevant")),
  brms::set_prior("normal(-0.4, 5)", class = "b", dpar="coi", coef = c("SexFemale:RelevanceIrrelevant")),
  brms::set_prior("normal(-7.2, 5)", class = "b", dpar="coi", coef = c("SexMale:RelevanceNonMerotic")),
  brms::set_prior("normal(-3.4, 5)", class = "b", dpar="coi", coef = c("SexFemale:RelevanceNonMerotic")),

  # Random
  brms::set_prior("normal(1.5, 0.5)", class = "sd", dpar="zoi", lb=0),
  brms::set_prior("normal(1, 0.5)", class = "sd", dpar="coi", lb=0),
  brms::set_prior("normal(0.4, 0.5)", class = "sd", dpar="", group ="Participant", lb=0),
  brms::set_prior("normal(0.4, 0.5)", class = "sd", dpar="phi", group ="Participant", lb=0),
  brms::set_prior("normal(0.3, 0.5)", class = "sd", dpar="", group ="Item", lb=0),
  brms::set_prior("normal(0.3, 0.5)", class = "sd", dpar="phi", group ="Item", lb=0)
) |>
  brms::validate_prior(formula, data=df)

m <- brms::brm(formula, 
               data=df,
               prior=priors,
               algorithm = "meanfield",
               init = 0,
               seed=123,
               iter=30000)

summary(m, robust=TRUE, priors=TRUE)
```

### Model Performance

```{r}
m_priors <- update(m, sample_prior = "only", prior=priors)

pred <- as.data.frame(t(brms::posterior_predict(m, ndraws=50))) |>
  datawizard::data_addprefix("post_") |>
  cbind(
    as.data.frame(t(brms::posterior_predict(m_priors, ndraws=50))) |>
      datawizard::data_addprefix("prior_") |>
      select_if(\(x) length(unique(x)) > 2)
  ) |>
  cbind(df)

rbind(
  estimate_density(select(pred, starts_with("post_"), Sex, Relevance, Condition),
                   method="KernSmooth", at=c("Sex", "Relevance", "Condition")) |>
    mutate(Prediction = "Posterior"),
  estimate_density(select(pred, starts_with("prior_"), Sex, Relevance, Condition),
                   method="KernSmooth", at=c("Sex", "Relevance", "Condition")) |>
    mutate(Prediction = "Prior")
) |>
  ggplot(aes(x=x, y=y, color=Relevance, linetype=Condition)) +
  geom_line(aes(group=interaction(Parameter, Sex, Relevance, Condition)),
            linewidth=0.5, alpha=0.3) +
  geom_line(data=estimate_density(df, select="Arousal", method="KernSmooth",
                                  at=c("Sex", "Relevance", "Condition")),
            linewidth=1) +
  facet_grid(Prediction~Sex) +
  coord_cartesian(ylim=c(0, 15), xlim=c(0, 1))
```

### Model Description

Effect size interpretation: consider the coefficient as a fraction of the Erotic vs. Neutral coefficient.

```{r}
# results_table(m)
m
```

<!-- ```{r} -->
<!-- performance::icc(m_arousal_baseline, by_group=TRUE) -->
<!-- performance::variance_decomposition(m_arousal_baseline) -->
<!-- ``` -->

### Model Visualization

```{r}
marg <- marginaleffects::predictions(m, by=c("Sex", "Relevance", "Condition"), newdata = "marginalmeans") |>
  as.data.frame()

marg |>
  ggplot(aes(x=Relevance, y=estimate, color=Condition)) +
  geom_line(aes(group=Condition), position = position_dodge(width=0.2)) +
  geom_pointrange(aes(ymin = conf.low, ymax=conf.high), position = position_dodge(width=0.2)) +
  facet_grid(~Sex)
```

### Sensitivity Analyis

```{r}
#| eval: false

m <- glmmTMB::glmmTMB(Arousal ~ Relevance / Condition + (1|Participant) + (1|Item),
                      data=df)

results <- data.frame()
for(n in seq(20, 80, by=1)) {
  cat(n, " ")
  for(i in 1:20) {
    ppts <- sample(unique(dfsub[dfsub$Sex == "Male", ]$Participant), round(n, 0), replace=TRUE)
    results <- update(m, data=filter(df, Participant %in% ppts)) |>
      parameters::parameters(effects = "fixed") |>
      filter(str_detect(Parameter, "RelevanceRelevant:ConditionAI-Generated")) |>
      mutate(n=n, i=i, Sex="Male") |>
      rbind(results)
  }
}

results |>
  ggplot(aes(x=n, y=p)) +
  geom_hline(yintercept=c(0.05, 0.01, 0.001), linetype="dashed", color="red") +
  geom_point2(size=5, alpha=0.2) +
  geom_smooth() +
  scale_y_sqrt(expand=c(0, 0), breaks=c(0, 0.001, 0.01, 0.05, 0.25, 0.5),
               minor_breaks = NULL) +
  coord_cartesian(ylim=c(0, NA)) +
  labs(title="Sensitivity Analysis by Simulation",
       subtitle = "Effect of 'Fiction' on Arousal (for Males)",
       x = "Number of Participants",
       y = "p-value") +
  theme_bw()
```

### Alternative Analysis

```{r}
#| eval: false

formula <- brms::bf(Arousal ~ s(Norms_Arousal, by=interaction(Sex, Condition)) +
                      (1|Participant) + (1|Item),
                    family = brms::Beta)

mgam <- brms::brm(formula,
               data=df,
               # prior=priors,
               # sample_prior = "only",
               algorithm = "meanfield",
               init = 0,
               seed=123,
               iter=10000)

marginaleffects::predictions(mgam, newdata=insight::get_datagrid(mgam), type="response") |>
  as.data.frame() |>
  ggplot(aes(x=Norms_Arousal, color=Condition)) +
  geom_line(aes(y=estimate)) +
  geom_point(data=df, aes(y=Arousal)) +
  facet_grid(~Sex)

marginaleffects::slopes(mgam,
                        newdata=insight::get_datagrid(mgam, at=c("Sex", "Norms_Arousal"), length=20),
                        variables="Condition")  |>
  as.data.frame() |>
  ggplot(aes(x=Norms_Arousal, y=estimate)) +
  geom_ribbon(aes(ymin=conf.low, ymax=conf.high, fill=Condition), alpha=0.3) +
  geom_line() +
  facet_grid(~Sex)
```

## Enticement

We note that the variability of Enticement scores is larger than that of Arousal.

```{r}
m <- glmmTMB::glmmTMB(Enticement ~ Sex / (Relevance / Condition) + (1+Relevance|Participant) + (1|Item), data=df)
performance::icc(m, by_group=TRUE)
results_table(m)

m <- glmmTMB::glmmTMB(Enticement ~ Sex / (Relevance / Condition) + (1+Relevance|Participant) + (1|Item), data=df, family=beta_family(link = "logit"))
results_table(m)
```

## Valence

```{r}
m <- glmmTMB::glmmTMB(Valence ~ Sex / (Relevance / Condition) + (1|Participant) + (1|Item), data=df)
results_table(m)
m <- mgcv::gamm(Valence ~ Sex / (Relevance / Condition),
                random = list(Participant = ~1, Item = ~1), data=df, family="betar")
results_table(m)
```

## Emotionality (Combined Factor)

```{r}
pca <- principal_components(df[c("Valence", "Arousal", "Enticement")], n = 2)
pca
df$Emotionality <- predict(pca)$PC1
m <- glmmTMB::glmmTMB(Emotionality ~ Sex / (Relevance / Condition) + (1|Participant) + (1|Item), data=df)
results_table(m)
```

## Realness

### Physical Characteristics

```{r}
m <- glmmTMB::glmmTMB(Realness ~ Entropy + Complexity + Contrast + Luminance + (1|Participant) + (1|Item), data=df)
results_table(m)
```

```{r}
m <- glmmTMB::glmmTMB(Realness ~ Sex / (Relevance / Condition) + (1|Participant) + (1|Item), data=df, family=beta_family(link = "logit"))
results_table(m)
```

### 2024-06-06 analysis/old_3_interindividual.qmd
@AnafNeves I pushed the 2_emotions script
you can go through it and make sure you can re-run its chunks

---
title: "FictionEro - Analysis (2)"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: true
    toc: true
---

## Data Preparation

```{r}
#| message: false
#| warning: false

library(tidyverse)
library(easystats)
library(patchwork)
library(ggside)
library(glmmTMB)
library(lavaan)
```

```{r}
dfsub <- read.csv("../data/data_participants.csv")
df <- read.csv("../data/data.csv") |> 
  full_join(
    dfsub[c("Participant", "Experimenter", "Feedback_LabelsIncorrect")],
    by = join_by(Participant)
    ) |> 
  datawizard::rescale(select=c("Arousal", "Enticement", "Realness"), range=c(0, 1), to=c(0.001, 0.999)) |> 
  datawizard::rescale(select=c("Valence"), range=c(-1, 1), to=c(0.001, 0.999)) |> 
  mutate(Condition = fct_relevel(Condition, "Photograph", "AI-Generated"),
         Relevance =  fct_relevel(Relevance, "Relevant", "Irrelevant", "Non-erotic")) 
```

## Belief in the Instructions

```{r}
m <- glmmTMB::glmmTMB(Arousal ~ Sex / (Relevance / (Condition * Feedback_LabelsIncorrect)) + 
                        (1|Participant) + (1|Item), 
                      data=df,
                      family = glmmTMB::beta_family(link = "logit"),
                      )
results_table(m)

m <- lm(Arousal ~ Sex / (Relevance / (Condition * Feedback_LabelsIncorrect)), data=df)

marginal <- marginaleffects::slopes(
  m, 
  newdata=insight::get_datagrid(m, at=c("Sex", "Relevance", "Feedback_LabelsIncorrect")),
  variables="Condition")

marginal |> 
  as.data.frame() |> 
  mutate_at(vars(estimate, conf.low, conf.high), \(x) -1*x) |>
  ggplot(aes(x=Relevance, y=estimate, color=Feedback_LabelsIncorrect)) +
  geom_line(aes(group=Feedback_LabelsIncorrect)) +
  geom_pointrange(aes(ymin = conf.low, ymax=conf.high)) +
  facet_grid(~Sex) +
  labs(y = "Reality - Fiction")
```

## Realness

```{r}
m <- brms::brm(Realness ~ Relevance / (Condition * BAIT) + (1|Participant) + (1|Item), data=df, algorithm = "meanfield")
results_table(m)

pred <- marginaleffects::predictions(m, newdata = insight::get_datagrid(m), re_formula = NULL) |> 
  as.data.frame()

pred |> 
  ggplot(aes(x=BAIT, y=estimate, )) +
  # geom_ribbon(aes(ymin = conf.low, ymax=conf.high, fill=Relevance, group=interaction(Condition, Relevance)), alpha=0.2) +
  geom_line(aes(linetype=Condition, color=Relevance))
```

### 2024-06-06 analysis/old_1_models.R

@@ -6,14 +6,17 @@
 
 # Options -----------------------------------------------------------------
 
+# path <- "/mnt/lustre/users/psych/dmm56/FictionEro/models/"
+path <- "./models/"
 iter <- 1000
-cores <- parallel::detectCores(logical = FALSE)
+# cores <- parallel::detectCores(logical = FALSE)
+cores <- 8
 
 options(mc.cores = cores,
         brms.backend = "cmdstanr")
 
 log <- c("Cores" = cores)
-write.csv(as.data.frame(log), '/mnt/lustre/users/psych/dmm56/FictionEro/log.csv')
+write.csv(as.data.frame(log), paste0(path, "log.csv"))
 
 
 # Packages ----------------------------------------------------------------
@@ -22,7 +25,7 @@ library(datawizard)
 library(brms)
 
 log <- c(log, "Packages" = TRUE)
-write.csv(as.data.frame(log), '/mnt/lustre/users/psych/dmm56/FictionEro/log.csv')
+write.csv(as.data.frame(log), paste0(path, "log.csv"))
 
 # Data --------------------------------------------------------------------
 
@@ -41,7 +44,7 @@ df <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/main
          Feedback_LabelsIncorrect =  forcats::fct_relevel(Feedback_LabelsIncorrect, "False", "True"))
 
 log <- c(log, "Data" = TRUE)
-write.csv(as.data.frame(log), '/mnt/lustre/users/psych/dmm56/FictionEro/log.csv')
+write.csv(as.data.frame(log), paste0(path, "log.csv"))
 
 
 # Baseline Models --------------------------------------------------------
@@ -51,8 +54,8 @@ write.csv(as.data.frame(log), '/mnt/lustre/users/psych/dmm56/FictionEro/log.csv'
 t0 <- Sys.time()
 
 f <- brms::bf(Arousal ~  0 + Intercept + Sex / Relevance +
-                 (0 + Intercept + Relevance|Participant) +
-                 (0 + Intercept + Relevance|Item))
+                 (1|Participant),
+              decomp = "QR")
 
 m_baseline_arousal_linear <- brms::brm(
   f,
@@ -60,15 +63,15 @@ m_baseline_arousal_linear <- brms::brm(
   algorithm="sampling",
   init = 0,
[…]

### 2024-06-06 analysis/3_realness.qmd
part 2/2 of the analysis (@AnafNeves)

---
title: "FictionEro - Determinants of Reality Beliefs"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
execute: 
  cache: true
---

## Data Preparation

```{r}
#| message: false
#| warning: false

library(tidyverse)
library(easystats)
library(patchwork)
library(ggside)
library(glmmTMB)

options(mc.cores = parallel::detectCores(),
        brms.backend = "cmdstanr",
        width = 300)
```

```{r}
dfsub <- read.csv("../data/data_participants.csv")
df <- read.csv("../data/data.csv") |> 
  right_join(
    select(dfsub, Participant, Sample, Language, Mobile, starts_with("Feedback_"), 
           BAIT_Visual, BAIT_Text, AI_Knowledge, SexualActivity, 
           GAAIS_Negative, GAAIS_Positive, Porn, COPS_Frequency_2,
           -Feedback_Comments),
    by = "Participant"
    ) |> 
  datawizard::rescale(select=c("Valence"), range=c(-1, 1), to=c(0, 1)) |> 
  mutate(Condition = fct_relevel(Condition, "Photograph", "AI-Generated"),
         Relevance =  fct_relevel(Relevance, "Relevant", "Irrelevant", "Non-erotic"),
         Sex =  fct_relevel(Sex, "Male", "Female"),
         PornFrequency = as.numeric(as.factor(COPS_Frequency_2)),
         SexualActivity_num = as.numeric(as.factor(SexualActivity)),
         ConditionBelief = case_when(
           Condition == "Photograph" & Realness > 0.5 ~ "True",
           Condition == "AI-Generated" & Realness < 0.5 ~ "True",
           .default = "False"
         ),
         RealnessBelief = ifelse(Realness > 0.5, 1, 0)) |> 
  mutate(across(starts_with("Feedback_"), function(x) {fct_relevel(x, "False", "True")}))

results_table <- function(model, effects="fixed", filter=NULL) {
  if("marginaleffects" %in% class(model)) {
    model |> 
      parameters::parameters() |> 
      as.data.frame() |> 
      select(-Parameter, -SE, -S, z=Statistic, -Predicted) |> 
      insight::format_table() |> 
      parameters::display()
  } else {
    display(parameters::parameters(model, effects=effects, keep=filter))
  }
}
```

### Distribution

```{r}
df |> 
  mutate(Realness_Extreme = ifelse(Realness %in% c(0, 1), "Extreme", "Not extreme")) |>
  ggplot(aes(x=Realness, fill=Relevance)) +
  geom_histogram(aes(color=Realness_Extreme), position = "identity", bins=80) +
  facet_grid(Relevance~Sex, scales="free_y") +
  scale_color_manual(values=c("red", "white"), guide="none") +
  scale_fill_manual(values=c("Relevant"="#E91E63", "Irrelevant"="#FF9800", "Non-erotic"="#03A9F4"), guide="none") +
  scale_y_sqrt(expand = c(0, 0)) +
  labs(title = "Realness") +
  theme_abyss() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))
```

## Physical Characteristics

```{r}
make_model <- function(f, family=glmmTMB::ordbeta()) {
  m <- glmmTMB::glmmTMB(as.formula(f), 
                        data=df, 
                        family=family,
                        control = glmmTMB::glmmTMBControl(parallel = 8))
  print(results_table(m))
  m
}

m <- make_model("Realness ~ Entropy + (1|Participant) + (1|Item)", family=glmmTMB::ordbeta())
m <- make_model("RealnessBelief ~ Entropy + (1|Participant) + (1|Item)", family="binomial")
m <- make_model("Realness ~ Complexity + (1|Participant) + (1|Item)", family=glmmTMB::ordbeta())
m <- make_model("RealnessBelief ~ Complexity + (1|Participant) + (1|Item)", family="binomial")
m <- make_model("Realness ~ Contrast + (1|Participant) + (1|Item)", family=glmmTMB::ordbeta())
m <- make_model("RealnessBelief ~ Contrast + (1|Participant) + (1|Item)", family="binomial")
m <- make_model("Realness ~ Luminance + (1|Participant) + (1|Item)", family=glmmTMB::ordbeta())
m <- make_model("RealnessBelief ~ Luminance + (1|Participant) + (1|Item)", family="binomial")
```

## Manipulation Check

```{r}
m <- make_model("Realness ~ Sex / (Relevance / Condition) + 
                (Relevance|Participant) + (1|Item)",
                family=glmmTMB::ordbeta())

predbeta <- estimate_relation(m, length=20)

m <- make_model("RealnessBelief ~ Sex / (Relevance / Condition) + 
                (Relevance|Participant) + (1|Item)",
                family="binomial")

predbin <- estimate_relation(m, length=20)

predbeta |> 
  ggplot(aes(x=Relevance, y=Predicted)) +
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.2)) +
  facet_grid(~Sex)
```

## Moderators

### AI-Attitutes

```{r}
test_moderator <- function(df, moderator="BAIT_Visual") {
  f <- paste0("Realness ~ Sex / (Relevance / Condition * ", moderator, ") + (Relevance | Participant) + (1|Item)")
  r <- glmmTMB::glmmTMB(as.formula(f),
                      data=df, 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8)) |>
    parameters::parameters() |> 
    as.data.frame() |> 
    select(-df_error, -Effects, -Group, -Component, -SE)
  r$Moderator <- moderator
  insight::format_table(filter(r, str_detect(Parameter, moderator)))
}

moderator <- data.frame()
for(m in c("BAIT_Visual", "BAIT_Text", "AI_Knowledge",
           "GAAIS_Positive", "GAAIS_Negative")) {
  moderator <- rbind(moderator, test_moderator(df, m))
}

display(filter(moderator, p < .05))
```

```{r}
m1 <- glmmTMB::glmmTMB(Realness ~ Sex /
                        (Relevance / Condition *  BAIT_Visual) + 
                        (Relevance | Participant) + (1|Item),
                      data=df, 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

summary(m1)

stars1 <- data.frame(Sex = as.factor(c("Male", "Male", "Female", "Female")), 
                    Condition=c("Photograph", "AI-Generated", "Photograph", "AI-Generated"), 
                    label=c("***", "***", "***", "***"),
                    x=c(0.6, 0.6, 0.65, 0.65),
                    y=c(0.8, 0.6, 0.72, 0.55))

pred1 <- estimate_relation(m1)
p1 <- pred1 |> 
  filter(Relevance == "Relevant") |>
  ggplot(aes(x=BAIT_Visual, y=Predicted)) +
  geom_ribbon(aes(ymin=CI_low, ymax=CI_high, fill=Condition), alpha=0.3) +
  geom_line(aes(color=Condition), linewidth=1, key_glyph = draw_key_rect) +
  geom_text(data=stars1, aes(x=x, y=y, label=label, color=Condition), hjust=0.5, size=3) +
  geom_text(data=data.frame(Sex=as.factor("Female"), x=0.65, y=0.638, label="**"), aes(x=x, y=y, label=label), hjust=0.5, color="#424242", size=3) +
  facet_grid(~Sex) +
  scale_y_continuous(labels=scales::percent) +
  scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
  scale_fill_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336"), guide="none") +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 8),
        strip.placement = "outside",
        strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
        strip.text.x = element_text(size = 10),
        strip.text.y = element_text(size = 10),
        axis.text.x = element_text(size=9, color="black"),
        legend.text = element_text(size = 10)) +
  labs(y="Realness\n", fill="Images presented as:", color="Images presented as:",
       x = "\nBeliefs about Artificial Information Technology (BAIT)\n'AI algorithms can generate realistic images'",
       tag = "A")
p1
```

### Porn Usage

```{r}
moderator <- data.frame()
for(m in c("Porn", "PornFrequency", "SexualActivity_num")) {
  moderator <- rbind(moderator, test_moderator(df, m))
}

display(filter(moderator, p < .05))
```

### Feedback

```{r}
moderator <- data.frame()
for(m in c("Feedback_CouldDiscriminate", "Feedback_CouldNotDiscriminate",
           "Feedback_AIMoreArousing", "Feedback_AILessArousing", 
           "Feedback_LabelsIncorrect", "Feedback_LabelsReversed")) {
  moderator <- rbind(moderator, test_moderator(df, m))
}

display(filter(moderator, p < .05))
```

```{r}
m2 <- glmmTMB::glmmTMB(Realness ~ Sex /
                        (Relevance / Feedback_CouldNotDiscriminate / Condition) + 
                        (Relevance | Participant) + (1|Item),
                      data=df, 
                      family=glmmTMB::ordbeta(),
                      control = glmmTMB::glmmTMBControl(parallel = 8))

summary(m2)

stars2 <- data.frame(Sex = as.factor(c("Male", "Male", "Female", "Female")), 
                    Condition=c("Photograph", "AI-Generated", "Photograph", "AI-Generated"), 
                    label=c("***", "***", "***", "***"),
                    x=c(1.4, 1.6, 1.4, 1.6),
                    y=c(0.79, 0.72, 0.69, 0.63))
stars3 <- data.frame(Sex = as.factor(c("Male", "Male", "Female")), 
                     label=c("***", "***", "***"),
                     x=c(1.1, 1.8, 1.15),
                     y=c(0.71, 0.80, 0.615))

pred2 <- estimate_relation(m2)

p2 <- pred2 |> 
  filter(Relevance == "Relevant") |>
  ggplot(aes(x=Feedback_CouldNotDiscriminate, y=Predicted)) +
  geom_line(aes(color=Condition, group=Condition), linewidth=.3, position = position_dodge(width=0.2), key_glyph = "path") +
  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.2), size=0.8, linewidth=1, key_glyph = "blank") +
  geom_text(data=stars2, aes(x=x, y=y, label=label, color=Condition), hjust=0.5, key_glyph = "blank", size=3) +
  geom_text(data=stars3, aes(x=x, y=y, label=label), hjust=0.5, color="#424242", size=3) +
  guides(color=guide_legend(override.aes = list(linewidth = 1.5))) +
  facet_grid(~Sex) +
  scale_y_continuous(labels=scales::percent) +
  scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
  theme_minimal() +
  theme(axis.text.y = element_text(size = 8),
        strip.placement = "outside",
        strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
        strip.text.x = element_text(size = 10),
        strip.text.y = element_text(size = 10),
        axis.text.x = element_text(size=9, color="black"),
        legend.text = element_text(size = 10)) +
  labs(y="Realness\n", fill="Images presented as:", color="Images presented as:",
       x = "\n'Could not discriminate AI-generated and real' Feedback",
       tag = "B")
p2
```

## Figures

```{r}
p <- (p1 + theme(legend.position = "none")) / p2  + plot_layout(guides = "collect")
ggsave("figures/figure2.png", p, width=8, height=8, dpi=300)
p
```

### 2024-06-11 analysis/2_emotions.qmd
Update 2_emotions.qmd

@@
            GAAIS_Negative, GAAIS_Positive, Porn, COPS_Frequency_2,
+           Screen_Size,
            -Feedback_Comments),
@@
 
-This section is about selecting the best model and performing the **manipulation check**: Neutral vs. Emotional
+This section is about selecting the best model and making a **manipulation check** to make sure that the emotional appraisal were sensitive to the main manipualtion (Neutral vs. Emotional).
 
@@
 ### Arousal
+
+The *Arousal* data is composed of a mixture of extreme responses (0 and 1) and non-extreme responses between 0 and 1, lending itself to ordered beta model [(Kubinec, 2022)](https://doi.org/10.1017/pan.2022.20), designed explicitly for bounded data such as survey slider scales.
+It is a more parsimonious evolution of the zero-and-one inflated beta (ZOIB) regression model (see [this tutorial](https://www.andrewheiss.com/blog/2021/11/08/beta-regression-guide/)) that jointly models the probability of extreme responses, the probability of 1 vs.
+0, and the mean and spread of the rest of the responses.
 
@@
 ```
-
-The *Arousal* data is composed of a mixture of extreme responses (0 and 1) and non-extreme responses between 0 and 1, lending itself to ordered beta model [(Kubinec, 2022)](https://doi.org/10.1017/pan.2022.20), designed explicitly for data with upper and lower bounds, such as survey slider scales.
-It is a more parsimonious evolution of the zero-and-one inflated beta (ZOIB) regression model (see [this tutorial](https://www.andrewheiss.com/blog/2021/11/08/beta-regression-guide/)) that jointly models the probability of extreme responses, the probability of 1 vs.
-0, and the mean and spread of the rest of the responses.
 
@@
 
+The same type of model seems warranted for enticement.
+
 ```{r}
@@
 ### Valence
+
+The same type of model seems warranted for valence.
 
@@
 results_table(m, filter="Condition")
+```
+
+```{r}
+m <- glmmTMB::glmmTMB(Arousal ~ Sex / Relevance / (Condition * Screen_Size) + (Relevance | Participant) + (1|Item),
+                      data=standardize(df, select="Screen_Size"), 
+                      family=glmmTMB::ordbeta(),
+                      control = glmmTMB::glmmTMBControl(parallel = 8))
+
+results_table(m, filter="Screen")
 ```
@@
 
+## Summary
+
+- Believing erotic images to be AI-generated, regardless of its true nature, leads to a less pleasurable experience (i.e., a less intense and less positive emotion).
+While the effect is the most noticeable for men (who experience a stronger arousal when exposed to the images), it appears overall very small in magnitude.
+However, it becomes more pronounced for both genders when controlled for the belief in the images' nature, and is consistent with participants' feedback, suggesting an important meta-cognitive component (in the form of explicitly conscious beliefs).
+- The items developed (BAIT scale) seem to measure a different dimension to AI-expertise.
+
 ## Figures

### 2024-06-23 analysis/3_realness.qmd
realness results
@DominiqueMakowski please check

@@
 ```{r}
+#| warning: false
+
 dfsub <- read.csv("../data/data_participants.csv")
@@
 
+Similar to the arousal data, the realness data contains a mixture of responses ranging from extreme values (0 and 1) to intermediate values between 0 and 1.
+Consequently, an ordered beta model was used for this data, as it is the most suitable for bounded data (e.g., survey sliders).For more information on these models see [(Kubinec, 2022)](https://doi.org/10.1017/pan.2022.20).
+
+This graph highlights gender differences and similarities in the ratings of realness across different types of images, indicating a consistent tendency to rate images as highly real across both genders, particularity at the upper end of the realness scale.
+Both genders exhibit a tendency to rate images as more real as the realness rating increases, with a consistent spike at the highest rating of 1.0 across all image types.
+Males generally show higher counts of high realness ratings compared to females, especially for relevant images.The patterns for irrelevant and non-erotic images are quite similar between genders, with a uniform distribution and a spike at the highest rating.
+
 ```{r}
+#| warning: false
+
 df |> 
@@
 
+Here, we are examining the effect of different physical characteristics of the images to evaluate whether they influence the perceived realness of the images.
+Neither Entropy, Complexity, Contrast, nor Luminance significantly influence the perceived realness of the images, nor the likelihood of realness being above 0.5 ("RealnessBelief"), as indicated by the lack of significant effects.
+
 ```{r}
+#| warning: false
+
 make_model <- function(f, family=glmmTMB::ordbeta()) {
@@
 
+This model examines the influence of sex, relevance, and condition on ratings of realness, incorporating random effects for participants and items.
+
+<!-- Key findings -->
+
+Both genders significantly rate AI-generated images as less real than images labeled as photographs.
+
+For males, this reduction in realness is consistent across all relevance categories.
+Specifically, males rate irrelevant images as significantly less real compared to relevant images.
+Additionally, males rate relevant AI-generated images as significantly less real compared to relevant photographs and rate irrelevant AI-generated images as significantly less real compared to irrelevant photographs.
+
+For females, while they also rate AI-generated images as less real, the reduction is smaller. Females rate irrelevant AI-generated images as significantly less real compared to irrelevant photographs.
+
+Both genders rate non-erotic images as more real than relevant images, with this difference being significant for females.
+For non-erotic images, males rate AI-generated images as significantly less real than photographs, but for females, this difference is not significant.
+
+<!-- All findings -->
+
+<!-- baseline: Male, Relevant, Photograph -->
+
+<!-- 1. **Intercept** - when all predictors are at their baseline images are significantly and positively rated as real -->
+
+<!-- 2. Impact of condition (AI vs Photograph) -->
+<!--     2.1. Both genders significantly rate AI-generated images as less real than images labeled as photographs across all relevance categories. -->
+<!--     2.2. The reduction in realness ratings for AI-generated images is larger for males than for females. -->
+<!--     2.3. For non-erotic images, this difference is significant for males but not for females. -->
+
+<!-- 3. **Impact of Relevance** (Relevant vs. Irrelevant and Non-Erotic) -->
+<!--     3.1. Males significantly rate irrelevant images as less real compared to relevant images. -->
+<!--     3.2. Females also rate irrelevant images as less real than relevant images, but this difference is not significant. -->
+<!--     3.3. Both genders rate non-erotic images as more real than relevant images.This difference is significant for females but not for males. -->
+
+<!-- 4. **Interaction terms** -->
+<!--     4.1. Males rate relevant AI-generated images as significantly less real compared to relevant photographs.  -->
+<!--     4.2. Females rate relevant AI-generated images as less real compared to relevant photographs, but the reduction is smaller than for males -->
+<!--     4.3. Males rate irrelevant AI-generated images as significantly less real compared to irrelevant photographs -->
+<!--     4.4. Females rate irrelevant AI-generated images as significantly less real compared to irrelevant photographs  -->
+<!--     4.5. For non-erotic images, males rate AI-generated images as significantly less real than photographs -->
+<!--     Females rate non-erotic AI-generated images as less real than photographs, but the difference is smaller and not significant.  -->
+
 ```{r}
+#| warning: false
+
 m <- make_model("Realness ~ Sex / (Relevance / Condition) + 
@@
 
+<!-- TODO: Interpret likelihood model of rating images as real ? -->
+
 ## Moderators
+
+Here we look at whether the findings above are moderated by AI-Attitudes, Porn usage, or feedback.
 
@@
 
+This model examines how ratings of realness, predicted by sex, condition, and relevance, are moderated by beliefs about AI's visual and textual capacities, self-reported knowledge of AI, as well as positive and negative attitudes towards AI (note that these results are relative to a baseline of male participants viewing relevant images labelled as photographs).
+Additionally, the model includes relevance and items as random effects.
+
+<!-- Key findings -->
+
+Beliefs about AI's visual capacity played a pivotal role in moderating realness ratings, showing nuanced effects across genders and image contexts.
+Both males and females generally rated images as more real as their beliefs in AI's visual capabilities increased.
+However, this relationship varied significantly depending on the relevance of the images.
+For males, increased beliefs in AI's visual capacity were associated with decreased realness ratings specifically when presented with irrelevant images.
+In contrast, females tended to rate both irrelevant and non-erotic images higher in realness as their beliefs in AI's visual abilities increased.
+Notably, for females viewing irrelevant images labeled as AI-generated, higher beliefs in AI's visual capacity led to decreased realness ratings, indicating a complex interaction.
+
+Beliefs in AI's textual abilities also influenced realness ratings, but the effects differed between genders and image contexts.
+Females showed lower realness ratings for irrelevant images labeled as AI-generated as their beliefs in AI's textual abilities increased.
+Conversely, males demonstrated increased realness ratings only for non-erotic images labeled as AI-generated with higher beliefs in AI's textual capabilities.
+
+Self-reported knowledge of AI had distinct effects on realness ratings as well.
+Males rated non-erotic images lower in realness as their self-reported AI knowledge increased.
+In contrast, females rated irrelevant images labeled as AI-generated as more real with higher self-reported AI knowledge, suggesting divergent perceptions based on their understanding of AI.
+
+Attitudes towards AI, whether positive or negative, further moderated ratings of realness.
+Positive attitudes generally enhanced realness ratings across genders.
+However, this effect was notably diminished for males when viewing irrelevant or non-erotic images labeled as AI-generated.
+Conversely, negative attitudes towards AI tended to decrease realness ratings for females, except when they viewed relevant images labeled as AI-generated, where negative attitudes paradoxically increased perceptions of realness.
+
+<!-- All findings -->
+
+<!-- Baseline: male, relevant, photograph -->
+
+<!-- a) Bait-Visual -->
+
+<!-- 1. For both genders, as beliefs about AI visual capacity increase, realness ratings significantly increase compared to the baseline. -->
+<!-- 2. For males, increased beliefs about AI visual capacity significantly decrease realness ratings of irrelevant images compared to the baseline. -->
+<!-- 3. For females, increased beliefs about AI visual capacity significantly increase realness ratings for irrelevant images and non-erotic images compared to the baseline. -->
+<!-- 4. For females, increased beliefs about AI's visual abilities significantly decrease realness ratings, of irrelevant and AI-generated images, compared to the baseline. -->
+
+<!-- b) Bait-Text -->
+
+<!-- 1. For both genders, increased beliefs in the textual abilities of AI significantly increase realness ratings compared to the baseline. -->
+<!-- 2. For females, increased beliefs in AI textual abilities significantly decrease realness ratings of irrelevant and AI-generated images compared to the baseline. -->
+<!-- 3. For males, this effect occurs when they are presented with non-erotic images labeled as AI-generated compared to the baseline. -->
+
+<!-- c) AI_Knowledge -->
+
+<!-- 1. For males, increased self-reported beliefs about AI knowledge significantly decrease realness ratings only for non-erotic images compared to the baseline. -->
+<!-- 2. For females, increased self-reported beliefs about AI knowledge significantly increase realness ratings only for irrelevant images labeled as AI-generated compared to the baseline. -->
+
+<!-- d) GAIS Positive -->
+
+<!-- 1. Positive attitudes about AI significantly increase realness ratings for both genders compared to the baseline. -->
+<!-- 2. For males, the positive effect of positive attitudes towards AI significantly decreases for irrelevant and non-erotic images compared to the baseline. -->
+<!-- 3. This effect also occurs when males are presented with relevant images that are labelled AI. -->
+
+<!-- e) GAIS Negative -->
+
+<!-- 1. Negative attitudes about AI significantly decrease realness ratings for females compared to the baseline. -->
+<!-- 2. For females, negative attitudes towards AI increase realness ratings for relevant images labeled as AI-generated compared to the baseline. -->
+
 ```{r}
+#| warning: false
+
 test_moderator <- function(df, moderator="BAIT_Visual") {
@@
 
+This graph depicts differences in realness ratings based on beliefs about AI's visual abilities for both genders when presented with images labeled as photographs or AI-generated.
+Notably, images labeled as photographs consistently receive higher realness ratings compared to those labeled as AI-generated, even at lower levels of belief in AI's visual capacity.
+As beliefs in AI's ability to generate realistic images increase, both genders show higher realness scores.
+However, for females with strong beliefs in AI's visual capabilities, the difference in realness ratings between photographs and AI-generated labeled images becomes minimal.
+
 ```{r}
+#| warning: false
+
 m1 <- glmmTMB::glmmTMB(Realness ~ Sex /
@@
 
+This model examines how ratings of realness, predicted by sex, condition, and relevance, are moderated by porn usage.
+
+Porn usage moderates the relationship between sex, relevance, condition, and realness ratings, but for males only.
+As porn usage increases, there is a significant decrease in realness ratings for non-erotic images labelled as AI-generated.
+
 ```{r}
+#| warning: false
+
 moderator <- data.frame()
@@
 
+This model evaluates how ratings of realness, predicted by sex, condition, and relevance, are moderated by participants' feedback.
+
+<!-- Key findings  -->
+
+Self-reported capacity to discriminate or not discriminate AI-generated images moderated realness ratings.
+Females who reported being able to discriminate AI-generated images tended to rate non-erotic images and relevant images labeled as AI-generated as more real.
+
+In contrast, males who reported an inability to discriminate AI-generated images tended to rate images labeled as AI-generated as more real, regardless of the relevance of these images.
+Females who reported an inability to discriminate AI-generated images showed a different pattern, with realness ratings for images labeled as AI-generated decreasing for irrelevant images but increasing for relevant images.
+
+Additionally, arousal ratings of AI-generated images also moderated realness ratings.
+Both genders rated AI-generated images as less real when reporting AI-generated images as being less arousing, with males showing a stronger effect, especially for relevant AI-generated labeled images.
+
+Beliefs about the nature of labels as being reversed or incorrect also moderated realness ratings.
+Males' realness ratings were lower when they believed that the labels were incorrect and lower when they believed the labels were reversed for non-erotic images.
+For females, lower realness ratings for AI-generated images were associated with believing the labels were reversed for relevant images
+
+<!-- All findings -->
+
+<!-- baseline: Male, Relevance, Photographs.  -->
+
+<!-- a) Could discriminate  -->
+
+<!-- 1. Compared to baseline, females self-report capacity to discriminate AI-generated images was associated with a significant increase of realness ratings for non-erotic images.  -->
+<!-- 2.
+Compared to baseline, females self-report capacity to discriminate AI-generated images was associated with a significant increase of realness ratings for relevant images labelled as AI-generated.
+-->
+
+<!-- b) Could not discriminate -->
+<!-- 1. Males and females self-report an inability to discriminate AI-generated images was associated with significantly increased realness ratings compared to the baseline -->
+<!-- 2.
+For males and females, incapacity to discriminate AI-generated images was associated with a significant increase in realness ratings for relevant images when labelled AI-generated, as compared to baseline.
+-->
+<!-- 3. males showed increased realness ratings for irrelevant images labeled as AI-generated, whereas females exhibited decreased realness ratings compared to the baseline.  -->
+<!-- 4. For non-erotic images, reporting an incapacity to discriminate AI-generated images was associated with a increase in realness ratings only for males.  -->
+
+<!-- c) AI images are less arousing -->
+<!-- 1. For both genders, reporting that AI-generated images are less arousing was associated with a significant decrease in realness ratings, as compared to baseline.  -->
+<!-- 2. For males, reporting AI-images as less arousing was further associated with a significant decrease in realness ratings for relevant images labelled as AI-generated, a compared to baseline. -->
+
+<!-- d) Believing labels were not correct -->
+<!-- 1. Reporting that the labels were not always correct was associated with a significant decrease in realness ratings for males only, as compared to baseline.  -->
+<!-- 2. Reporting that the labels were reversed was associated with a significant decrease in realness for non-erotic images for males only, as compared to baseline.  -->
+<!-- 3. Reporting that the labels were reversed was associated with a significant decrease in realness ratings for relevant images labelled AI-generated for females only, as compared to baseline.  -->
+
 ```{r}
+#| warning: false
+
 moderator <- data.frame()
@@
 
+This graph depicts differences in realness ratings based on participants' self-reported capacity to discriminate between AI-generated and real images, for both genders when presented with images labeled as photographs or AI-generated.
+The ability to discriminate AI-generated images is associated with higher realness ratings for both genders.
+However, females generally rate the realness of images lower than males across all conditions.
+The distinction between photographs and AI-generated images remains clear, with photographs being perceived as more real than AI-generated images.
+This difference is less pronounced for females who report an ability to discriminate AI-generated images.
+
 ```{r}
+#| warning: false
+
 m2 <- glmmTMB::glmmTMB(Realness ~ Sex /

### 2024-06-24 analysis/3_realness.qmd
Update 3_realness.qmd

@@
 
-Here, we are examining the effect of different physical characteristics of the images to evaluate whether they influence the perceived realness of the images.
+Here, we are examining the effect of various physical characteristics of the images to evaluate whether they influence the perceived realness of the images.
 Neither Entropy, Complexity, Contrast, nor Luminance significantly influence the perceived realness of the images, nor the likelihood of realness being above 0.5 ("RealnessBelief"), as indicated by the lack of significant effects.

### 2024-06-26 analysis/1_cleaning.qmd
minor

@@
 
+```{r}
+#| warning: false
+
+dat <- df |> 
+  select(starts_with("GAAIS"), starts_with("BAIT")) |> 
+  select(matches("[[:digit:]]"))
+
+ega <- EGAnet::EGA(
+        data = dat,
+        seed=123,
+        model="glasso",
+        algorithm="leiden",
+        plot.EGA=FALSE,
+        verbose=FALSE)
+
+plot(ega)
+
+plot(parameters::factor_analysis(dat, n=6, rotation="oblimin", sort=TRUE))
+```
+
+```{r}
+#| eval: false
+#| echo: false
+
+# Used for feedback screen in the new BAIT implementations
+mean(rowMeans(df[c("GAAIS_Positive_12", "GAAIS_Positive_17")]))
+```
+
 #### AI-Expertise

### 2024-06-26 analysis/0_preprocessing.py

@@ -3,6 +3,9 @@ import json
 import numpy as np
 import pandas as pd
 
+# Note: new data from FakeFace2 got saved in this repo during June 2024.
+# Make sure to use only files before.
+
 
 # Get files from OSF ======================================================
 def osf_listfiles(data_subproject="", token="", after_date=None):

### 2024-06-27 analysis/2_emotions.qmd
95% completed analysis

@@
 
-::: {.panel-tabset}
-
+::: panel-tabset
 ### Arousal
@@
 ```{r}
-df |> 
+arousal <- df |> 
   mutate(Arousal_Extreme = ifelse(Arousal %in% c(0, 1), "Extreme", "Not extreme")) |>
@@
   theme(plot.title = element_text(hjust = 0.5, face="bold"))
+
+arousal
 ```
@@
 
-```{r}
-m <- glmmTMB::glmmTMB(Arousal ~ Sex / Relevance + (Relevance | Participant) + (1|Item),
+This model evaluates the effects of Sex and Relevance on Arousal, accounting for random variability due to participants and items (i.e., random effects).
+
+<!-- Key findings -->
+
+The analysis revealed that on average women rate relevant stimuli lower in arousal compared to men.
+Additionally, both genders tend to rate irrelevant and non-erotic stimuli lower in arousal then relevant stimuli, with males showing a stronger reduction for irrelevant stimuli and a comparable one for non-erotic stimuli.
+Furthermore, females rate irrelevant stimuli higher in arousal than males, whereas both genders rate non-erotic images similarly in terms of arousal.
+
+There is notable variability in arousal ratings across participants, with a greater diversity in responses to irrelevant stimuli compared to relevant ones.There is a strong positive correlation between changes in arousal ratings for irrelevant stimuli and non-erotic stimuli.
+This suggests that participants who exhibit significant increases or decreases in arousal when exposed to irrelevant stimuli tend to exhibit similar changes when exposed to non-erotic stimuli, indicating consistent trends in arousal levels.
+There is significant variability in baseline arousal ratings across different items, indicating that different items elicit varying baseline levels of arousal.
+
+<!-- All findings -->
+
+<!-- a) fixed effects -->
+
+<!-- 1. Intercept: The average arousal ratings for male participants with relevant stimuli. -->
+
+<!-- 2. On average, women rate relevant stimuli lower in arousal compared to males. -->
+
+<!-- 3. On average, males rate irrelevant stimuli lower in arousal than relevant stimuli. -->
+
+<!-- 4. On average, females rate irrelevant stimuli lower in arousal compared to females' arousal ratings of relevant stimuli. -->
+
+<!-- 5. Males rate non-erotic stimuli lower in arousal than relevant stimuli. -->
+
+<!-- 6. Females also rate non-erotic stimuli lower in arousal than relevant stimuli. -->
+
+<!-- b) Variability in the random effects and how they vary together  -->
+
+<!-- 1. Intercept: The variability in baseline arousal ratings across participants for relevant images. -->
+
+<!-- 2.
+The standard deviation for irrelevant stimuli, across participants, is higher compared to the one for relevant stimuli (i.e., arousal ratings vary more widely among participants for irrelevant stimuli than responses for relevant stimuli) -->
+
+<!-- 3.
+The standard deviation for non-erotic stimuli, across participants, is higher compared to the one for relevant stimuli (i.e., arousing ratings vary more widely among participants for non-erotic stimuli than responses for relevant stimuli) -->
+
+<!-- 4.
+Participants who have slightly higher baseline arousal ratings for relevant stimuli tend to have lower changes in arousal ratings for irrelevant stimuli; however, this effect is very small (funder2019 rules).
+-->
+
+<!-- 5. . Participants with higher baseline arousal for relevant stimuli tend to have lower changes in arousal ratings for non-erotic stimuli; this effect is small (funder2019 rules). -->
+
+<!-- 6.Participants who show a strong change in arousal ratings to irrelevant stimuli also tend to show a strong change in arousal ratings to non-erotic stimuli; this effect is very large (funder2019 rules).
+-->
+
+<!-- b.2) Items -->
+
+<!-- Intercept: The variability in baseline arousal ratings across items, indicating that different items have different baseline ratings of arousal. -->
+
+```{r}
+m_a <- glmmTMB::glmmTMB(Arousal ~ Sex / Relevance + (Relevance | Participant) + (1|Item),
                       data=df, family=glmmTMB::ordbeta(),
@@
 ```{r}
-results_table(m)
-
-estimate_relation(m) |> 
+results_table(m_a)
+
+estimate_relation(m_a) |> 
   ggplot(aes(x=Relevance, y=Predicted)) +
@@
 ```{r}
-df |> 
+enticiment <- df |> 
   mutate(Enticement_Extreme = ifelse(Enticement %in% c(0, 1), "Extreme", "Not extreme")) |>
@@
   theme(plot.title = element_text(hjust = 0.5, face="bold"))
-```
-
-```{r}
-m <- glmmTMB::glmmTMB(Enticement ~ Sex / Relevance + (Relevance | Participant) + (1|Item),
+
+enticiment
+```
+
+This model evaluates the effects of Sex and Relevance on Enticement ratings, accounting for random variability due to participants and items (i.e., random effects).
+
+<!-- Key findings -->
+
+In general, women rate relevant images lower in enticement than males.
+Males rate irrelevant images significantly less enticing than relevant ones, while females do not show a significant difference in enticement ratings between irrelevant and relevant images.
+Both males and females rate non-erotic images as the least enticing, with a stronger effect for males.
+
+Random effects show considerable participant-to-participant variation in baseline enticement ratings, especially for irrelevant and non-erotic stimuli, compared to relevant stimuli.Participants with higher initial ratings for relevant stimuli tend to show less change in ratings for irrelevant and non-erotic stimuli, though the effect size varies.A notable correlation exists between changes in enticement ratings for irrelevant and non-erotic stimuli, indicating consistent responsiveness across different stimulus types.
+Lastly, the analysis indicates that different items elicit varying baseline levels of enticement.
+
+<!-- All findings -->
+
+<!-- a) fixed effects -->
+
+<!-- 1. Intercept: The average enticing ratings for male participants with relevant stimuli. -->
+
+<!-- 2. On average, women rate relevant stimuli lower in enticing compared to males. -->
+
+<!-- 3. On average, males rate irrelevant stimuli lower in enticing than relevant stimuli. -->
+
+<!-- 4. On average, females rate irrelevant stimuli higher in enticing compared to females' enticing ratings of relevant stimuli. -->
+
+<!-- 5. Males rate non-erotic stimuli lower in enticing than relevant stimuli. -->
+
+<!-- 6. Females rate non-erotic stimuli lower in enticing than relevant stimuli. -->
+
+<!-- b) Variability in the random effects and how they vary together -->
+
+<!-- 1. Intercept: The variability in baseline enticing ratings across participants for relevant images. -->
+
+<!-- 2.
+The standard deviation for irrelevant stimuli, across participants, is higher compared to the one for relevant stimuli (i.e., enticing ratings vary more widely among participants for irrelevant stimuli than ratings for relevant stimuli) -->
+
+<!-- 3.
+The standard deviation for non-erotic stimuli, across participants, is higher compared to the one for relevant stimuli (i.e., enticing ratings vary more widely among participants for non-erotic stimuli than ratings for relevant stimuli) -->
+
+<!-- 4.Participants who have slightly higher baseline enticing ratings for relevant stimuli tend to have lower changes in enticing ratings for irrelevant stimuli; This effect is very small (funder2019 rules).
+-->
+
+<!-- 5. Participants with higher baseline enticing ratings for relevant stimuli tend to have lower changes in enticing ratings for non-erotic stimuli; this effect is large (funder2019 rules). -->
+
+<!-- 6..Participants who show a strong change in enticing ratings to irrelevant stimuli also tend to show a strong change in enticing ratings to non-erotic stimuli; this effect is very large (funder2019 rules).
+-->
+
+<!-- b.2) Items -->
+
+<!-- Intercept: The variability in baseline enticing ratings across items, indicating that different items have different baseline ratings of enticing. -->
+
+```{r}
+
+m_e <- glmmTMB::glmmTMB(Enticement ~ Sex / Relevance + (Relevance | Participant) + (1|Item),
                       data=df, family=glmmTMB::ordbeta(),
@@
 ```{r}
-results_table(m)
-
-estimate_relation(m) |> 
+results_table(m_e)
+
+estimate_relation(m_e) |> 
   ggplot(aes(x=Relevance, y=Predicted)) +
@@
 ```{r}
-df |> 
+valence <- df |> 
   mutate(Valence_Extreme = ifelse(Valence %in% c(0, 1), "Extreme", "Not extreme")) |>
@@
   theme(plot.title = element_text(hjust = 0.5, face="bold"))
-```
-
-```{r}
-m <- glmmTMB::glmmTMB(Valence ~ Sex / Relevance + (Relevance | Participant) + (1|Item),
+
+valence
+```
+
+This model is evaluating the effects of Sex and Relevance on Valence ratings, accounting for random variability due to participants and items (i.e., random effects).
+
+<!-- Key findings -->
+The analysis reveals that women rate relevant stimuli significantly lower in valence compared to men.
+Male participants consistently rate relevant stimuli higher in valence compared to their ratings of irrelevant stimuli, while females do not show significant differences between these stimuli.
+Both genders rate non-erotic stimuli lower in valence than relevant stimuli and higher than irrelevant ones, with males showing a more pronounced difference.
+
+Participants show diverse baseline valence ratings, especially for irrelevant and non-erotic stimuli, with greater variability observed compared to relevant stimuli.
+Participants who rate relevant stimuli higher in valence exhibit less change in valence ratings for irrelevant and non-erotic stimuli, indicating consistent individual responses across different types of stimuli.There is a significant correlation between changes in valence ratings for irrelevant and non-erotic stimuli, indicating consistent responsiveness across different stimulus types.
+Different items elicit varying baseline levels of valence..
+
+<!-- All findings -->
+
+<!-- a) fixed effects -->
+
+<!-- 1. Intercept: The average valence ratings for male participants with relevant stimuli. -->
+
+<!-- 2. On average, women rate relevant stimuli lower in arousal compared to males. -->
+
+<!-- 3. On average, males rate irrelevant stimuli lower in valence than relevant stimuli. -->
+
+<!-- 4. On average, females rate irrelevant stimuli higher in valence compared to relevant stimuli. -->
+
+<!-- 5. Males rate non-erotic stimuli lower in valence than relevant stimuli, but very slightly -->
+
+<!-- 6. Females rate non-erotic stimuli higher in valence than relevant stimuli, comparably more than irrelevant stimuli -->
+
+<!-- b) Variability in the random effects and how they vary together -->
+
+<!-- 1. Intercept: The variability in baseline valence ratings across participants for relevant images. -->
+
+<!-- 2.
+The standard deviation for irrelevant stimuli, across participants, is higher compared to the one for relevant stimuli (i.e., valence ratings vary more widely among participants for irrelevant stimuli than ratings for relevant stimuli) -->
+
+<!-- 3.
+The standard deviation for non-erotic stimuli, across participants, is higher compared to the one for relevant stimuli, also just slightly (i.e., valence ratings vary more widely among participants for non-erotic stimuli than ratings for relevant stimuli) -->
+
+<!-- 4.Participants who have slightly higher baseline valence ratings for relevant stimuli tend to have lower changes in valence ratings for irrelevant stimuli; This effect is very large (funder2019 rules).
+-->
+
+<!-- 5. Participants with higher baseline valence ratings for relevant stimuli tend to have lower changes in valence ratings for non-erotic stimuli; this effect is very large (funder2019 rules). -->
+
+<!-- 6..Participants who show a strong change in valence ratings to irrelevant stimuli also tend to show a strong change in valence ratings to non-erotic stimuli; this effect is very large (funder2019 rules).
+-->
+
+<!-- b.2) Items -->
+
+<!-- Intercept: The variability in baseline valence ratings across items, indicating that different items have different baseline ratings of valence. -->
+
+```{r}
+m_v <- glmmTMB::glmmTMB(Valence ~ Sex / Relevance + (Relevance | Participant) + (1|Item),
                       data=df, family=glmmTMB::ordbeta(),
@@
 ```{r}
-results_table(m)
-
-estimate_relation(m) |> 
+results_table(m_v)
+
+estimate_relation(m_v) |> 
   ggplot(aes(x=Relevance, y=Predicted)) +
@@
   scale_color_manual(values=c("Relevant"="#E91E63", "Irrelevant"="#FF9800", "Non-erotic"="#03A9F4"), guide="none") +
-  labs(y="Enticement") +
+  labs(y="Valence") +
   facet_wrap(~Sex) +
@@
 
-plot_descriptive(df, "Arousal")
+arousal_desc <- plot_descriptive(df, "Arousal")
+arousal_desc
 ```
@@
 ### Whole Sample
+
+This model examines the effects of Sex, Relevance, and Condition on Arousal, accounting for random variability due to participants and items (i.e., random effects).
+
+<!-- Key findings -->
+<!-- This model differs from the previous one by including an interaction term between Condition (AI-Generated vs.
+Photograph) and Relevance for each sex.
+This allows the model to investigate how the arousal ratings for AI-Generated images versus Photograph images differ based on Relevance and Sex.
+-->
+
+Women rate relevant (photograph) stimuli significantly lower in arousal compared to men.
+Males rate irrelevant (photograph), and non-erotic (photograph), stimuli significantly lower in arousal compared to relevant stimuli.
+Females also rate non-erotic (photograph) stimuli lower in arousal compared to relevant stimuli.
+Lastly, males rate AI-Generated images significantly lower in arousal compared to Photograph images.
+
+The analysis also examined the average marginal effect of the variable "Condition" (comparing AI-Generated to Photograph) separately for males and females.
+For males, the arousal is on average lower for AI-Generated images compared to Photograph images.
+For females, the arousal is on average higher for AI-Generated images compared to Photograph images; however, this effect is not significant.
+
+<!-- All significant findings -->
+
+<!-- 1.The baseline (intercept) is for males with relevant images labeled as photographs. -->
+
+<!-- 2.Females generally have lower arousal levels compared to males for relevant images labeled as photographs. -->
+
+<!-- 3.Males rate irrelevant images significantly lower in arousal compared to relevant images. -->
+
+<!-- 4.Both males and females rate non-erotic images significantly lower in arousal compared to relevant images. -->
+
+<!-- 5.Males rate relevant images labeled as AI-generated significantly lower in arousal compared to relevant images labeled as photographs. -->
+
+<!-- Average marginal effects (or average slopes)  -->
+
+<!-- 1.It is examining the average marginal effect of the variable "Condition" (comparing AI-Generated to Photograph) separately for males and females. -->
+
+<!-- 2. For males, the arousal is on average 0.0066 units lower for AI-Generated images compared to Photograph images. -->
+
+<!-- 3. For woman, the arousal is on average  0.00348 units higher for AI-Generated images compared to Photograph images, however this effect is not significant.  -->
 
@@
 
-::: {.panel-tabset}
-
+::: panel-tabset
 #### Sample
+
+When examining the random slopes, it was observed that only males significantly rated arousal lower for AI-generated images compared to photographs.
+Further analysis of the sample subgroups revealed that this effect was predominantly driven by males from the general population, who significantly contributed to the lower arousal ratings for AI-generated images compared to photographs.
 
@@
 
+We investigated the influence of using a mobile device (mobile = TRUE) versus other devices on arousal ratings, considering the effects of condition and relevance.
+
+<!-- Key Findings -->
+
+Males rated relevant AI-generated images significantly lower in arousal compared to relevant photographs, irrespective of whether they used a mobile device or not.
+However, this effect was more pronounced among male participants who used a mobile device.
+
+We also explored whether the interaction between condition (AI-Generated vs. Photograph) and screen size affected arousal levels. No statistically significant results were found for this interaction.
+
+<!-- All Significant Findings: -->
+
+<!-- 1. Males using mobile devices rated relevant AI-generated images significantly lower in arousal compared to relevant photographs (coefficient = -0.12, p < .001). -->
+
+<!-- 2. Males not using mobile devices also rated relevant AI-generated images lower in arousal compared to relevant photographs, though the effect was smaller (coefficient = -0.05, p = 0.041). -->
+
+<!-- 3. Females' arousal ratings for relevant AI-generated images did not significantly differ from those for relevant photographs, regardless of mobile usage. -->
+
 ```{r}
@@
 ```
-
 :::
@@
 ### Moderators
+
+This model explores whether various factors such as **attitudes towards AI, knowledge about AI, porn usage, frequency of porn consumption, and sexual activity** moderate the relationship between sex, image relevance (specifically AI-generated versus photographs), and arousal ratings.
+
+The analysis revealed a significant interaction effect only for porn usage among females.
+Specifically, females with higher levels of porn usage rated AI-generated images significantly lower in arousal compared to photographs.
+No other moderators showed statistically significant effects on arousal ratings across the interactions of sex, condition (AI-Generated vs.
+Photograph), and the respective moderators.
+
+We also examined whether **feedback** moderates the relationship between sex, condition, and relevance on arousal, we found the following significant effects:
+
+Findings suggest that feedback about the arousal potential of AI-generated images can significantly moderate arousal ratings, with females being more positively influenced by feedback that AI images are more arousing, and males being more negatively influenced by feedback that AI images are less arousing.
+
+<!-- All significant findings for feedback  -->
+
+<!-- 1.For females, giving feedback indicating that AI-generated images were more arousing significantly influenced arousal ratings for images labeled as AI-generated.
+Specifically, females who reported finding AI-generated images more arousing had higher arousal ratings for these images.
+-->
+
+<!-- 2.
+For males, giving feedback indicating that AI-generated images were less arousing significantly influenced arousal ratings for images labeled as AI-generated.
+Specifically, males who reported finding AI-generated images less arousing had lower arousal ratings for these images.
+-->
 
@@
 ### Believed
+
+<!-- TO DO: why believed? -->
 
@@
 
-plot_descriptive(df, "Enticement")
+enticement_desc <- plot_descriptive(df, "Enticement")
+enticement_desc
 ```
@@
 ### Whole Sample
+
+This model examines how Sex, Relevance, and Condition influence Valence ratings, treating relevance within each participant and items as random effects.
+
+<!-- Key Findings: -->
+
+Females consistently rate relevant (photograph) images significantly lower in enticement compared to males.
+Conversely, men rate irrelevant images (photographs) significantly lower in enticement than relevant ones, although this difference is not observed among females.
+Both genders rate non-erotic images (photographs) significantly lower in enticement than relevant ones.
+Interestingly, neither gender shows a significant difference in enticement ratings between AI-generated images and photographs, regardless of relevance.
+
+We also analyzed the average marginal effect of the variable “Condition” (comparing AI-Generated to Photograph) separately for males and females.
+
+For males, enticement ratings are significantly lower on average for AI-Generated images compared to Photograph images.
+For females, enticement ratings are slightly higher on average for AI-Generated images compared to Photograph images, although this difference is not statistically significant.
 
@@
 
-::: {.panel-tabset}
-
+::: panel-tabset
 #### Sample
+
+Here we  examined the interaction between Sample (different participant groups), Sex, Relevance, and Condition (AI-Generated vs. Photograph) on enticement ratings.
+
+These findings indicate that in the General Population and Students (Non-incentivized) samples, males show a preference for relevant Photograph images over relevant AI-Generated images in terms of enticement, while females tend to rate relevant AI-Generated images higher in enticement.
+The differences in enticement ratings between AI-Generated and Photograph images were not significant in other samples or conditions examined.
 
@@
 
+Here, we explored the impact of using a mobile device (mobile = TRUE) versus not using one as a predictor of enticement, alongside condition, sex, and relevance.
+
+We observed that males rated relevant AI-generated images significantly lower in enticement compared to relevant photographs, regardless of whether they used a mobile device or not.
+However, this effect was more pronounced among males using a mobile device.
+Additionally, for males, using a mobile device influenced enticement ratings for non-erotic stimuli, where they rated AI-generated non-erotic stimuli lower in enticement compared to non-erotic photographs.
+
 ```{r}
@@
 ### Moderators
+
+We examined whether **attitudes towards AI, porn usage and frequency, and sexual activity** moderated the relationship between the predictors (sex, relevance, condition) and enticement ratings.
+The results indicated that no moderator was significant.
+
+Looking at **feedback as a moderator**, the results showed that enticement ratings for images labeled AI-generated were moderated by the feedback that AI is more arousing, but this was only significant for women.
+Specifically, women who reported that AI-generated images as more arousing rated these images higher in enticement compared to images labeled as photographs.
+
+Lastly, the interaction between sexual activity and condition on arousal, suggests that for females, the effect of AI-Generated condition on arousal ratings varies with different levels of sexual activity.
 
@@
 
-estimate_relation(m, length=20) |> 
+sex_act_plot<- estimate_relation(m, length=20) |> 
   ggplot(aes(x=SexualActivity_num, y=Predicted)) +
@@
   facet_grid(~Sex)
+
+sex_act_plot
 ```
@@
 
-plot_descriptive(df, "Valence")
+valence_desc <- plot_descriptive(df, "Valence")
+valence_desc
 ```
@@
 ### Whole Sample
+
+This model investigates the effects of Sex, Relevance, and Condition on Valence, accounting for random variability due to participants and items (i.e., random effects).
+
+Females rate relevant images significantly lower in valence than males on average.
+Males rate irrelevant and non-erotic images significantly lower in valence compared to relevant images.
+Females rate both irrelevant and non-erotic images higher in valence compared to relevant ones, but this effect is only significant for non-erotic stimuli.
+Males rate relevant images significantly lower in valence when labeled as AI-generated compared to when labeled as photographs.
+
+Females rate relevant (photograph) images significantly lower in valence compared to males.
+Males rate irrelevant (photograph) and non-erotic (photograph) images significantly lower in valence compared to relevant images.
+Females rate non-erotic (photograph) images higher in valence compared to relevant ones.
+Males rate relevant AI-Generated images significantly lower in valence compared to photographs.
+
+Lastly, we can see that for males, valence ratings are on average significantly lower for AI-Generated images compared to Photograph images. For females, there is no significant effect.
 
@@
 
-::: {.panel-tabset}
-
+::: panel-tabset
 #### Sample
+
+Examining the effect of sample type as a predictor, males consistently rate relevant AI-generated images significantly lower in valence compared to relevant photographs.
+Additionally, among non-incentivized students, this pattern persists for males, while females rate relevant AI-generated images significantly higher in valence compared to relevant photographs
 
@@
 
+When examining the use of mobile devices as a predictor, men consistently rated the valence lower for relevant AI-generated images compared to photographs, regardless of whether they used a mobile or a standard computer.
+However, the effect was more pronounced among those using mobile devices.
+
 ```{r}
@@
 ### Moderators
+
+Here we look at whether the relationship between sex, condition and relevance and valence is moderated by **AI-attitudes, porn frequency and usage, and sexual activity**.
+Females who have more positive attitudes towards AI rated AI-generated images significantly higher in valence compared to images labelled as photographs.
+
+Looking at **feedback** as a moderator we can see that ales who reported that they could not discriminate between AI-generated and photograph images, rated AI-generated images significantly higher in valence compared to images labelled as photographs.
 
@@
 
+Here we combined the data for arousal, valence and enticing into an emotionality factor.
+
 ```{r}
@@
 
-df |> 
+emotionality <- df |> 
   mutate(Emotionality_Extreme = ifelse(Emotionality %in% c(0, 1), "Extreme", "Not extreme")) |>
@@
   theme(plot.title = element_text(hjust = 0.5, face="bold"))
+
+emotionality
 ```
@@
 
-plot_descriptive(df, "Emotionality")
+emotionality_desc <- plot_descriptive(df, "Emotionality")
+emotionality_desc
 ```
@@
 ### Whole Sample
+
+This model looks at the effect of sex, relevance and condition on emotionality, accounting for random variability due to participants and items (i.e., random effects).
+
+<!-- Intercept: male, relevance, photograph -->
+
+These findings suggest that females consistently rate relevant (photograph) images lower in emotionality compared to males.
+Additionally, males specifically rate irrelevant (photograph) images lower in emotionality, and both genders rate non-erotic (photgraph) images lower in emotionality compared to relevant images.
+Furthermore, males rate AI-generated relevant images lower in emotionality compared to those labelled as photographs.
+
+For males, emotionality ratings are on average significantly lower for AI-Generated images compared to Photograph images.
+This indicates that males generally rate AI-Generated images lower in emotionality compared to photographs.
+For females, there is no significant difference between the mean ratings of AI-Generated and Photograph images in terms of emotionality.
+This suggests that females do not show a significant preference or difference in emotionality ratings between AI-Generated and Photograph images.
 
@@
 
-::: {.panel-tabset}
-
+::: panel-tabset
 #### Sample
+
+This model investigates the influence of sample type (General Population, Incentivized Students, Non-incentivized Students), Sex, Relevance, and Condition (AI-Generated vs.
+Photograph) on emotionality ratings.
+Males from the General Population consistently rated AI-Generated images lower in emotionality compared to photographs across relevant conditions.
+Females from the Non-incentivized Students group showed a significant preference for AI-Generated images in terms of emotionality compared to photographs.
+
+These findings suggest that the perception of emotionality in AI-Generated images varies significantly based on sample type (general population vs.
+students) and the relevance of the images, particularly for males and non-incentivized female students.
 
@@
 
+This analysis explores the influence of using a mobile device to complete the experiment on emotionality ratings, focusing on differences between males and females across relevant and irrelevant conditions of AI-Generated and photograph images.
+
+Males consistently rate emotionality significantly lower for relevant AI-Generated images compared to photograph images, irrespective of whether they use a mobile device or not.
+They also rate emotionality significantly lower for irrelevant AI-Generated images compared to photograph images when not using a mobile device.
+For females, there are no significant differences in how they rate emotionality for AI-Generated images based on whether they use a mobile device or not, regardless of relevance.
+
+These findings highlight that the perception of emotionality in AI-Generated images among males is notably affected by the use of mobile devices during the experiment, whereas females show no significant variation in their ratings based on device usage.
+
 ```{r}
@@
 ### Moderators
+
+Looking at **AI-attitudes, porn frequency and usage, sexual activity, and feedback** as moderators, the analysis showed that for females, having a positive attitude towards AI significantly increased their emotionality ratings for AI-generated images compared to those who did not have such positive attitudes.
+Additionally, for females reporting finding AI more arousing lowered their emotionality ratings for AI-generated images compared to those that did not.
+This effect was significantly reversed for males.
 
@@
 ```
+
+For females reporting finding AI more arousing lowered their emotionality ratings for AI-generated images compared to those that did not. This effect was significantly reversed for males.
 
@@
 <!-- ```{r} -->
+
 <!-- m <- glmmTMB::glmmTMB(Realness ~ Entropy + Complexity + Contrast + Luminance + (1|Participant) + (1|Item), data=df) -->
+
 <!-- results_table(m) -->
+
 <!-- ``` -->
@@
 <!-- ```{r} -->
+
 <!-- m <- glmmTMB::glmmTMB(Realness ~ Sex / (Relevance / Condition) + (1|Participant) + (1|Item), data=df, family=beta_family(link = "logit")) -->
+
 <!-- results_table(m) -->
+
 <!-- ``` -->

### 2024-06-27 analysis/3_realness.qmd
95% completed analysis

@@
 
-This graph highlights gender differences and similarities in the ratings of realness across different types of images, indicating a consistent tendency to rate images as highly real across both genders, particularity at the upper end of the realness scale.
+<!-- This graph highlights gender differences and similarities in the ratings of realness across different types of images, indicating a consistent tendency to rate images as highly real across both genders, particularity at the upper end of the realness scale.
 Both genders exhibit a tendency to rate images as more real as the realness rating increases, with a consistent spike at the highest rating of 1.0 across all image types.
 Males generally show higher counts of high realness ratings compared to females, especially for relevant images.The patterns for irrelevant and non-erotic images are quite similar between genders, with a uniform distribution and a spike at the highest rating.
+-->
 
@@
 <!-- 2. Impact of condition (AI vs Photograph) -->
+
 <!--     2.1. Both genders significantly rate AI-generated images as less real than images labeled as photographs across all relevance categories. -->
+
 <!--     2.2. The reduction in realness ratings for AI-generated images is larger for males than for females. -->
+
 <!--     2.3. For non-erotic images, this difference is significant for males but not for females. -->
@@
 <!-- 3. **Impact of Relevance** (Relevant vs. Irrelevant and Non-Erotic) -->
+
 <!--     3.1. Males significantly rate irrelevant images as less real compared to relevant images. -->
+
 <!--     3.2. Females also rate irrelevant images as less real than relevant images, but this difference is not significant. -->
+
 <!--     3.3. Both genders rate non-erotic images as more real than relevant images.This difference is significant for females but not for males. -->
@@
 <!-- 4. **Interaction terms** -->
+
 <!--     4.1. Males rate relevant AI-generated images as significantly less real compared to relevant photographs.  -->
+
 <!--     4.2. Females rate relevant AI-generated images as less real compared to relevant photographs, but the reduction is smaller than for males -->
+
 <!--     4.3. Males rate irrelevant AI-generated images as significantly less real compared to irrelevant photographs -->
+
 <!--     4.4. Females rate irrelevant AI-generated images as significantly less real compared to irrelevant photographs  -->
+
 <!--     4.5. For non-erotic images, males rate AI-generated images as significantly less real than photographs -->
+
 <!--     Females rate non-erotic AI-generated images as less real than photographs, but the difference is smaller and not significant.  -->
@@
 <!-- 1. For both genders, as beliefs about AI visual capacity increase, realness ratings significantly increase compared to the baseline. -->
+
 <!-- 2. For males, increased beliefs about AI visual capacity significantly decrease realness ratings of irrelevant images compared to the baseline. -->
+
 <!-- 3. For females, increased beliefs about AI visual capacity significantly increase realness ratings for irrelevant images and non-erotic images compared to the baseline. -->
+
 <!-- 4. For females, increased beliefs about AI's visual abilities significantly decrease realness ratings, of irrelevant and AI-generated images, compared to the baseline. -->
@@
 <!-- 1. For both genders, increased beliefs in the textual abilities of AI significantly increase realness ratings compared to the baseline. -->
+
 <!-- 2. For females, increased beliefs in AI textual abilities significantly decrease realness ratings of irrelevant and AI-generated images compared to the baseline. -->
+
 <!-- 3. For males, this effect occurs when they are presented with non-erotic images labeled as AI-generated compared to the baseline. -->
@@
 <!-- 1. For males, increased self-reported beliefs about AI knowledge significantly decrease realness ratings only for non-erotic images compared to the baseline. -->
+
 <!-- 2. For females, increased self-reported beliefs about AI knowledge significantly increase realness ratings only for irrelevant images labeled as AI-generated compared to the baseline. -->
@@
 <!-- 1. Positive attitudes about AI significantly increase realness ratings for both genders compared to the baseline. -->
+
 <!-- 2. For males, the positive effect of positive attitudes towards AI significantly decreases for irrelevant and non-erotic images compared to the baseline. -->
+
 <!-- 3. This effect also occurs when males are presented with relevant images that are labelled AI. -->
@@
 <!-- 1. Negative attitudes about AI significantly decrease realness ratings for females compared to the baseline. -->
+
 <!-- 2. For females, negative attitudes towards AI increase realness ratings for relevant images labeled as AI-generated compared to the baseline. -->
@@
 <!-- 1. Compared to baseline, females self-report capacity to discriminate AI-generated images was associated with a significant increase of realness ratings for non-erotic images.  -->
+
 <!-- 2.
@@
 <!-- b) Could not discriminate -->
+
 <!-- 1. Males and females self-report an inability to discriminate AI-generated images was associated with significantly increased realness ratings compared to the baseline -->
+
 <!-- 2.
@@
 -->
+
 <!-- 3. males showed increased realness ratings for irrelevant images labeled as AI-generated, whereas females exhibited decreased realness ratings compared to the baseline.  -->
+
 <!-- 4. For non-erotic images, reporting an incapacity to discriminate AI-generated images was associated with a increase in realness ratings only for males.  -->
@@
 <!-- c) AI images are less arousing -->
+
 <!-- 1. For both genders, reporting that AI-generated images are less arousing was associated with a significant decrease in realness ratings, as compared to baseline.  -->
+
 <!-- 2. For males, reporting AI-images as less arousing was further associated with a significant decrease in realness ratings for relevant images labelled as AI-generated, a compared to baseline. -->
@@
 <!-- d) Believing labels were not correct -->
+
 <!-- 1. Reporting that the labels were not always correct was associated with a significant decrease in realness ratings for males only, as compared to baseline.  -->
+
 <!-- 2. Reporting that the labels were reversed was associated with a significant decrease in realness for non-erotic images for males only, as compared to baseline.  -->
+
 <!-- 3. Reporting that the labels were reversed was associated with a significant decrease in realness ratings for relevant images labelled AI-generated for females only, as compared to baseline.  -->
@@
 
+## Summary
+
+-   Findings indicate a consistent perception across both genders that AI-generated images are perceived as less realistic compared to photographs.
+Interestingly, both genders rated non-erotic images as more realistic than relevant and irrelevant images.
+
+-   As beliefs in AI's ability to generate realistic images increases, both genders show higher realness scores.
+
+-   Porn usage moderated realness ratings, only for men presented with AI-generated non-erotic images.
+
+-   Males who reported an inability to discriminate AI-generated images perceived both relevant and irrelevant AI-generated images as more real, whereas females who reported this inability showed increased realness ratings only for relevant AI-generated images.
+
 ## Figures

### 2024-09-28 study1/stimuli_selection/selection.qmd
changes to files
changed experiment1 to study1 and its corresponding URLS, HTMLs, links...
Added study2 folder, changed selection.qmd for study2

--- 2023-11-26 experiment/stimuli_selection/selection.qmd
@@
 - SD: standard deviation
--   JPEG_size80:index of overall complexity
+- JPEG_size80: index of overall complexity
 - LABL: luminance in CIE L*a*b color space
@@
 - LABB: the amount of the green color CIE L*a*b color space
+- Entropy: the amount of complexity in gray scale. Images with high entropy are images that are more "noisy" and have a high degree of contrast.
 

### 2024-09-28 study2/stimuli_selection2/selection2.qmd
changes to files
changed experiment1 to study1 and its corresponding URLS, HTMLs, links...
Added study2 folder, changed selection.qmd for study2

---
title: "Stimuli Selection 2"
format:
  html:
    embed-resources: true
editor_options: 
  chunk_output_type: console
---

```{r}
#| include: false
#| code-fold: true
library(tidyverse)
library(easystats)
library(ggrepel)

napsero2 <- readxl::read_excel("norms_napsero.XLSX", sheet = "Ratings") |>
  full_join(readxl::read_excel("norms_napsero.XLSX", sheet = "Image parameters"), by = join_by("ID", "Category")) |>
  select(-contains("_SD")) |>
  rename(Orientation = `V/H`,
         Hetero_Men_Valence = val_M_HeM,
         Hetero_Women_Valence = val_M_HeF,
         Homo_Men_Valence = val_M_HoM,
         Homo_Women_Valence = val_M_HoF,
         Hetero_Men_Arousal = aro_M_HeM,
         Hetero_Women_Arousal = aro_M_HeF,
         Homo_Men_Arousal = aro_M_HoM,
         Homo_Women_Arousal = aro_M_HoF) |>
  mutate(across(c("Luminance", "Contrast", "JPEG_size80", "LABL", "LABA", "LABB", "Entropy"), as.numeric),
         Description = NA)

# # Join
# naps <- filter(naps, ID %in% filter(napsero, Category == "Non-erotic")$ID)
# naps[c("Men_Arousal", "Men_Valence", "Women_Valence", "Women_Arousal", "Nr", "Orientation")] <- NA
# napsero[napsero$Category== "Non-erotic", "Category"] <- NA
# 
# ids <- napsero[is.na(napsero$Category), ]$ID
# for(c in c("Category", "Height", "Width", "Luminance", "Contrast",
#            "JPEG_size80", "LABL", "LABA", "LABB", "Entropy", "Description")) {
#   napsero[napsero$ID == ids, c] <- naps[naps$ID == ids, c]
# }

```

## Selection

### Select based on norms
```{r}
men <- napsero2 |>
  filter( Category != "Non-erotic") |>
  group_by(Category) |>
  slice_max(Hetero_Men_Arousal, n=8, with_ties = FALSE) |>
  pull(ID) |> 
  c(
    napsero2 |>
      filter( Category != "Non-erotic") |>
      group_by(Category) |>
      slice_min(Hetero_Men_Arousal, n=2, with_ties = FALSE) |>
      pull(ID))

homo_men <- napsero2 |>
  filter( Category != "Non-erotic") |>
  group_by(Category) |>
  slice_max(Homo_Men_Arousal, n=8, with_ties = FALSE) |>
  pull(ID) |> 
  c(
    napsero2 |>
      filter( Category != "Non-erotic") |>
      group_by(Category) |>
      slice_min(Homo_Men_Arousal, n=2, with_ties = FALSE) |>
      pull(ID))

women <- napsero2 |>
  filter(Category != "Non-erotic", !ID %in% men) |>
  group_by(Category) |>
  slice_max(Hetero_Women_Arousal, n=8, with_ties = FALSE) |>
  pull(ID) |> 
  c(
    napsero2 |>
      filter(Category != "Non-erotic", !ID %in% men) |>
      group_by(Category) |>
      slice_min(Hetero_Women_Arousal, n=2, with_ties = FALSE) |>
      pull(ID)
  )

homo_women <- napsero2 |>
  filter(Category != "Non-erotic", !ID %in% men) |>
  group_by(Category) |>
  slice_max(Homo_Women_Arousal, n=8, with_ties = FALSE) |>
  pull(ID) |> 
  c(
    napsero2 |>
      filter(Category != "Non-erotic", !ID %in% men) |>
      group_by(Category) |>
      slice_min(Homo_Women_Arousal, n=2, with_ties = FALSE) |>
      pull(ID)
  )

neutral <-  napsero2|>
  filter(Category == "Non-erotic", !ID %in% c(men, women)) |>
  mutate(Arousal = (Hetero_Men_Arousal + Hetero_Women_Arousal + Homo_Men_Arousal + Homo_Women_Arousal ) / 4) |>
  slice_min(Arousal, n=10, with_ties = FALSE) |>
  pull(ID)

pos_arousing <-  napsero2 |>
  filter(Category == "Non-erotic", !ID %in% c(men, women, neutral)) |>
  mutate(Arousal = (Hetero_Men_Arousal + Hetero_Women_Arousal + Homo_Men_Arousal + Homo_Women_Arousal) / 4,
         Valence = (Hetero_Men_Valence + Hetero_Women_Valence + Homo_Men_Valence + Homo_Women_Valence) / 4) |>
  filter(Valence > 5) |>
  slice_max(Arousal, n=10, with_ties = FALSE) |>
  pull(ID)

selected2 <- unique(c(men, homo_men, women, homo_women, neutral, pos_arousing))
selected_erotic_2 <- unique(c(men, homo_men, women, homo_women))

cat(
  paste0("N (men) = ", length(men), "\nN (homo_men) = ", length(homo_men),  "\nN (women) = ", length(women), "N (homo_women) = ", length(homo_women), "\nN (neutral) = ", length(neutral),  "\nN (arousing-positive) = ", length(pos_arousing),
       "\nTotal = ", length(selected2))
)
```

```{r}
selected_erotic_2

```

### Visualization

```{r}
#| out.width: 1\\textwidth
#| fig.width: 10
#| fig.height: 8
#| dpi: 300
#| message: false

dat2 <- napsero2 |>
  mutate(Selected = ifelse(ID %in% selected_erotic_2, TRUE, FALSE),
         label = ifelse(Selected, str_remove(ID, ".jpg"), NA)) |>
  pivot_longer(cols = c("Hetero_Men_Valence", "Hetero_Men_Arousal", "Hetero_Women_Valence", "Hetero_Women_Arousal", "Homo_Men_Valence", "Homo_Men_Arousal", "Homo_Women_Valence", "Homo_Women_Arousal")) |>
  separate(name, into=c("Sexual_Orientation", "Target", "Variable")) |>
  pivot_wider(names_from=Variable, values_from=value)

dat2 |>
  filter(Category != "Non-erotic") |>
  ggplot(aes(x=Valence, y=Arousal)) +
  geom_point(aes(shape=Selected, color=Category), size=6, alpha=0.8) +
  ggside::geom_ysidedensity(data=filter(dat2, Selected), aes(color=Category), key_glyph = draw_key_blank) +
  ggside::geom_xsidedensity(data=filter(dat2, Selected), aes(color=Category), key_glyph = draw_key_blank) +
  # ggrepel::geom_label_repel(aes(label = label)) +
  scale_shape_manual(values=c("TRUE"=20, "FALSE"=4)) +
  scale_color_manual(values = c(
    "Opposite-sex Couple"="#673AB7", "Male Couple"= "#3F51B5", "Female Couple" = "#9C27B0",
    "Female" = "#E91E63", "Male"= "#2196F3")) +
  guides(shape = guide_legend(override.aes = list(color="white"))) +
  facet_grid(~Sexual_Orientation*Target) +
  theme_abyss() +
  theme(ggside.panel.grid.major = element_blank(), 
        ggside.axis.text = element_blank(),
        ggside.axis.line = element_blank())

```

## Final Selection

- ID: picture category and number
- V/H: vertical / horizontal
- Av/Ap: avoidance - approach dimension
- M: mean
- SD: standard deviation
- JPEG_size80: index of overall complexity
- LABL: luminance in CIE L*a*b color space
- LABA: the amount of red color CIE L*a*b color space
- LABB: the amount of the green color CIE L*a*b color space
- Entropy: the amount of complexity in gray scale. Images with high entropy are images that are more "noisy" and have a high degree of contrast.

```{r}
#| code-fold: true

selection_erotic2 <- napsero2 |> 
  filter(ID %in% selected_erotic_2)

write.csv(selection_erotic2, "stimuli_data_erotic2.csv", row.names=FALSE)
knitr::kable(selection_erotic2)
```

```{r}
#| code-fold: true
json <- selection2 |> 
  select(stimulus=ID, Category, Orientation) |> 
  jsonlite::toJSON()

write(paste("var stimuli_list2 = ", json), "stimuli_list2.js")
```

```{r}
#| code-fold: true
path_ero <- "C:/Dropbox/RECHERCHE/docs/Stimuli/NAPS/NAPS_ERO/"
path_naps <- "C:/Dropbox/RECHERCHE/docs/Stimuli/NAPS/NAPS/"

# Remove all current files
unlink("../stimuli/*")

# Copy each file
for(file in selected) {
  if(str_detect(file, "Male|Female")) {
    file.copy(paste0(path_ero, file), "../stimuli/")
  } else {
    file.copy(paste0(path_naps, file), "../stimuli/")
  }
}
```

### 2024-09-28 analysis/0_preprocessing.py

@@ -44,7 +44,7 @@ files = osf_listfiles(
 # Initialize empty dataframes
 alldata = pd.DataFrame()
 alldata_subs = pd.DataFrame()
-norm_data = pd.read_csv("../experiment/stimuli_selection/stimuli_data.csv").rename(
+norm_data = pd.read_csv("../study1/stimuli_selection/stimuli_data.csv").rename(
     columns={
         "ID": "Item",
         "JPEG_size80": "Complexity",

### 2024-09-28 study1/demographics.js

@@ -82,7 +82,7 @@ var demographics_debriefing = {
 }
 
 var demographics_endscreen = function (
-    link = "https://realitybending.github.io/FictionEro/experiment/english.html"
+    link = "https://realitybending.github.io/FictionEro/study1/english.html"
 ) {
     return {
         type: jsPsychHtmlButtonResponse,

### 2024-09-28 study1/fiction.js

@@ -30,7 +30,8 @@ function assignCondition(stimuli_list) {
 
         // Assign half to "Reality" condition and half to "Fiction" condition
         for (let i = 0; i < cat_stimuli.length; i++) {
-            cat_stimuli[i].Condition = i < cat_stimuli.length / 2 ? "Reality" : "Fiction"
+            cat_stimuli[i].Condition =
+                i < cat_stimuli.length / 2 ? "Reality" : "Fiction"
         }
 
         // Add to new_stimuli_list
@@ -175,9 +176,15 @@ var fiction_trials = {
     timeline_variables: stimuli_list,
     randomize_order: true,
     timeline: [
-        fiction_fixationcross((duration = 750), (screen = "fiction_fixationcross1a")),
+        fiction_fixationcross(
+            (duration = 750),
+            (screen = "fiction_fixationcross1a")
+        ),
         fiction_cue((text_cue = text_cue), (duration = 1250)),
-        fiction_fixationcross((isi = 500), (screen = "fiction_fixationcross1b")),
+        fiction_fixationcross(
+            (isi = 500),
+            (screen = "fiction_fixationcross1b")
+        ),
         fiction_showimage((duration = 2500), (screen = "fiction_image1")),
         fiction_ratings,
     ],

### 2024-09-28 study1/instructions_english.js

@@ -92,7 +92,7 @@ var text_debriefing =
     "<p>To complete your participation in this study, click on 'Continue' and <b>wait until your responses have been successfully saved</b> before closing the tab.</p> "
 
 var text_endscreen = function (
-    link = "https://realitybending.github.io/FictionEro/experiment/english?exp=snow&lang=en"
+    link = "https://realitybending.github.io/FictionEro/study1/english?exp=snow&lang=en"
 ) {
     return (
         "<h1>Thank you for participating</h1>" +
@@ -290,7 +290,8 @@ var consent_text = // Logo and title
     // "<p>Please note that various checks will be performed to ensure the validity of the data.<br>We reserve the right to return your participation or prorate reimbursement should we detect non-valid responses (e.g., random pattern of answers, instructions not read, ...).</p>"
     "<p align='left'>For further information about this research, or if you have any concerns, please contact Dr Dominique Makowski (D.Makowski@sussex.ac.uk). This research has been approved (ER/MHHE20/2) by the School of Psychology. The University of Sussex has insurance in place to cover its legal liabilities in respect of this study.</p>"
 
-var consent_button = "I am more than 18 years old, and I read, understood, and consent to the above"
+var consent_button =
+    "I am more than 18 years old, and I read, understood, and consent to the above"
 
 var fullscreen_text =
     "<p>The experiment will switch to full screen mode when you press the button below</p>"
@@ -319,10 +320,26 @@ var demographics_p_eth = "e.g., Caucasian"
 var demographics_q_cou = "In which country do you currently live?"
 var demographics_p_cou = "e.g., UK, Spain"
 var demographics_q_lang = "<b>How would you rate your level of English?</b>"
-var demographics_c_lang = ["Beginner - 0", "1", "2", "3", "4", "5", "6 - Native"]
+var demographics_c_lang = [
+    "Beginner - 0",
+    "1",
+    "2",
+    "3",
+    "4",
+    "5",
+    "6 - Native",
+]
 var demographics_q_ai =
     "<b>How knowledgeable do you consider yourself about Artificial Intelligence (AI) technology?</b>"
-var demographics_c_ai = ["Not at all - 0", "1", "2", "3", "4", "5", "6 - Expert"]
+var demographics_c_ai = [
+    "Not at all - 0",
+    "1",
+    "2",
+    "3",
+    "4",
+    "5",
+    "6 - Expert",
+]
 var demographics_hormones_preamble =
[…]

### 2024-09-28 study1/instructions_french.js

@@ -56,11 +56,13 @@ var text_instructions_questionnaires =
 // Ratings ----------------------------------------------------------------
 var text_ticks = ["Pas du tout", "Beaucoup"]
 var text_ticks_valence = ["Désagréable", "Agréable"]
-var text_rating_appeal = "Dans quelle mesure cette image vous semble-t-elle <b>attrayante</b> ?"
+var text_rating_appeal =
+    "Dans quelle mesure cette image vous semble-t-elle <b>attrayante</b> ?"
 var text_rating_arousal =
     "Dans quelle mesure vous êtes-vous senti(e) <b>sexuellement excité(e)</b> ?"
 var text_rating_valence = "Le <b>ressenti</b> évoqué par l'image était..."
-var text_rating_realness = "Dans quelle mesure cette image est-elle <b>réaliste</b> ?"
+var text_rating_realness =
+    "Dans quelle mesure cette image est-elle <b>réaliste</b> ?"
 
 // -------------------------
 var text_feedback1 =
@@ -93,7 +95,7 @@ var text_debriefing =
     '<p>Pour terminer votre participation à cette étude, cliquez sur "Continuer" et <b>attendez que vos réponses aient été sauvegardées</b> avant de fermer l\'onglet.</p>'
 
 var text_endscreen = function (
-    link = "https://realitybending.github.io/FictionEro/experiment/french?exp=snow&lang=fr"
+    link = "https://realitybending.github.io/FictionEro/study1/french?exp=snow&lang=fr"
 ) {
     return (
         "<h1>Merci de votre participation</h1>" +
@@ -291,7 +293,8 @@ var consent_text = // Logo and title
     // "<p>Veuillez noter que divers contrôles seront effectués pour garantir la validité des données. <br>Nous nous réservons le droit d'exclure vos données si nous détectons des réponses non valides</br> (par exemple, des réponses aléatoires, des instructions non lues, ...).</p>"
[…]

### 2024-09-28 study1/instructions_italian.js

@@ -93,7 +93,7 @@ var text_debriefing =
     "<p>Per completare la tua partecipazione a questo studio, clicca su 'Continua' e <b>attendi finché le tue risposte sono state salvate</b> prima di chiudere la scheda.</p> "
 
 var text_endscreen = function (
-    link = "https://realitybending.github.io/FictionEro/experiment/english?exp=snow&lang=it" //*** OR NOT???
+    link = "https://realitybending.github.io/FictionEro/study1/english?exp=snow&lang=it" //*** OR NOT???
 ) {
     return (
         "<h1>Grazie per la tua partecipazione</h1>" +
@@ -288,7 +288,8 @@ var consent_text = // Logo and title
     "</ul></p>" +
     "<p align='left'>Per ulteriori informazioni su questa ricerca o se hai domande, contatta il Dr. Dominique Makowski (D.Makowski@sussex.ac.uk) e/o il Dr. Marco Viola dell'Università di Roma Tre (marco.viola@uniroma3.it). Questa ricerca è stata approvata (ER/MHHE20/2) dalla School of Psychology dell'Università del Sussex. L'Università di Sussex ha un'assicurazione in vigore per coprire le responsabilità legali relative a questo studio.</p>"
 
-var consent_button = "Ho più di 18 anni, ho letto, compreso e acconsento a quanto sopra"
+var consent_button =
+    "Ho più di 18 anni, ho letto, compreso e acconsento a quanto sopra"
 
 var fullscreen_text =
     "<p>L'esperimento passerà alla modalità a schermo intero appena premerai il pulsante qui sotto</p>"
@@ -298,10 +299,12 @@ var fullscreen_button = "Continua"
 var button_continue = "Continua"
 var button_end = "Fine"
 
-var demographics1_preamble = "<b>Per favore, rispondi alle seguenti domande:</b>"
+var demographics1_preamble =
+    "<b>Per favore, rispondi alle seguenti domande:</b>"
 var demographics_q_sex = "Qual è il tuo sesso biologico?"
 var demographics_c_sex = ["Maschio", "Femmina", "Altro"]
-var demographics_q_edu = "Qual è il titolo di studio più alto che hai conseguito?"
+var demographics_q_edu =
+    "Qual è il titolo di studio più alto che hai conseguito?"
 var demographics_c_edu = [
     "Università (dottorato)",
[…]

### 2024-09-28 study1/instructions_spanish.js

@@ -56,7 +56,8 @@ var text_instructions_questionnaires =
 // Ratings ----------------------------------------------------------------
 var text_ticks = ["En absoluto", "Mucho"]
 var text_ticks_valence = ["Desagradable", "Agradable"]
-var text_rating_appeal = "Que tan <b>atractiva/apetecible</b> consideras que es esta imagen?"
+var text_rating_appeal =
+    "Que tan <b>atractiva/apetecible</b> consideras que es esta imagen?"
 var text_rating_arousal = "En qué medida experimentas <b>activación sexual</b>?"
 var text_rating_valence = "La<b>sensación</b> generada por la imagen fue..."
 var text_rating_realness = "¿Que tan <b>realista</b> fue la imagen?"
@@ -91,7 +92,7 @@ var text_debriefing =
     "<p>Para completar tu participación en este estudio, haz clic en 'Continuar' y <b>espera hasta que tus respuestas hayan sido guardadas exitosamente</b> antes de cerrar la pestaña.</p> "
 
 var text_endscreen = function (
-    link = "https://realitybending.github.io/FictionEro/experiment/english?exp=snow&lang=en"
+    link = "https://realitybending.github.io/FictionEro/study1/english?exp=snow&lang=en"
 ) {
     return (
         "<h1>Gracias por participar</h1>" +
@@ -289,7 +290,8 @@ var consent_text = // Logo and title
     // "<p> Tenga en cuenta que se realizarán varias comprobaciones para garantizar la validez de los datos.<br>Nos reservamos el derecho de devolverle su participación o un reembolso prorrateado si detectamos respuestas no válidas (por ejemplo, patrón aleatorio de respuestas, instrucciones no leídas, . ..).</p>"
     "<p align='left'>Para obtener más información sobre esta investigación, o si tiene alguna inquietud, comuníquese con el Dr Antonio Olivera-La Rosa (antonio.oliverade@amigo.edu.co). Esta investigación ha sido aprobada (ER/MHHE20/2) por el consejo de ética. La Universidad de Sussex cuenta con un seguro para cubrir sus responsabilidades legales con respecto a este estudio.</p>"
 
-var consent_button = " Tengo más de 18 años y leo, entiendo y doy mi consentimiento a lo anterior."
+var consent_button =
[…]

### 2024-09-28 study1/questionnaires.js

@@ -19,7 +19,11 @@ var bait_dimensions = [
 
 // Questionnaires =================================================
 
-function format_questions_analog(items, dimensions, ticks = ["Inaccurate", "Accurate"]) {
+function format_questions_analog(
+    items,
+    dimensions,
+    ticks = ["Inaccurate", "Accurate"]
+) {
     var questions = []
     for (const [index, element] of items.entries()) {
         questions.push({

### 2024-09-28 study2/stimuli_selection2/stimuli_list2.js

@@ -1,0 +1,1 @@
+var stimuli_list2 =  [{"stimulus":"Male_001_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_002_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_003_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_005_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_006_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_007_h.jpg","Category":"Male","Orientation":"h"},{"stimulus":"Male_008_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_009_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_011_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_012_h.jpg","Category":"Male","Orientation":"h"},{"stimulus":"Male_013_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_014_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_015_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_016_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_017_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_020_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_022_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_023_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_024_h.jpg","Category":"Male","Orientation":"h"},{"stimulus":"Male_025_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Female_001_h.jpg","Category":"Female","Orientation":"h"},{"stimulus":"Female_002_h.jpg","Category":"Female","Orientation":"h"},{"stimulus":"Female_003_v.jpg","Category":"Female","Orientation":"v"},{"stimulus":"Female_004_v.jpg","Category":"Female","Orientation":"v"},{"stimulus":"Female_005_v.jpg","Category":"Female","Orientation":"v"},{"stimulus":"Female_006_v.jpg","Category":"Female","Orientation":"v"},{"stimulus":"Female_008_v.jpg","Category":"Female","Orientation":"v"},{"stimulus":"Female_009_h.jpg","Cat
[…]

### 2024-10-02 study2/stimuli_selection2/selection2.qmd
study 2 qmd small changes

@@
 men <- napsero2 |>
-  filter( Category != "Non-erotic") |>
+  filter(!Category %in% c("Non-erotic", "Male Couple", "Female Couple", "Male")) |>
   group_by(Category) |>
   slice_max(Hetero_Men_Arousal, n=8, with_ties = FALSE) |>
-  pull(ID) |> 
-  c(
-    napsero2 |>
-      filter( Category != "Non-erotic") |>
-      group_by(Category) |>
-      slice_min(Hetero_Men_Arousal, n=2, with_ties = FALSE) |>
-      pull(ID))
+  pull(ID)
 
 homo_men <- napsero2 |>
-  filter( Category != "Non-erotic") |>
+  filter(!Category %in% c("Non-erotic", "Female Couple", "Female", "Opposite-sex Couple")) |>
   group_by(Category) |>
   slice_max(Homo_Men_Arousal, n=8, with_ties = FALSE) |>
-  pull(ID) |> 
-  c(
-    napsero2 |>
-      filter( Category != "Non-erotic") |>
-      group_by(Category) |>
-      slice_min(Homo_Men_Arousal, n=2, with_ties = FALSE) |>
-      pull(ID))
+  pull(ID)
 
 women <- napsero2 |>
-  filter(Category != "Non-erotic", !ID %in% men) |>
+  filter(!Category %in% c("Non-erotic", "Female Couple", "Male Couple", "Female"), !ID %in% men) |>
   group_by(Category) |>
   slice_max(Hetero_Women_Arousal, n=8, with_ties = FALSE) |>
-  pull(ID) |> 
-  c(
-    napsero2 |>
-      filter(Category != "Non-erotic", !ID %in% men) |>
+  pull(ID)
+
+homo_women <- napsero2 |>
+  filter(!Category %in% c("Non-erotic", "Male Couple", "Male", "Opposite-sex Couple"), !ID %in% men) |>
   group_by(Category) |>
-      slice_min(Hetero_Women_Arousal, n=2, with_ties = FALSE) |>
+  slice_max(Homo_Women_Arousal, n=8, with_ties = FALSE) |>
   pull(ID) 
+# 
+# neutral <-  napsero2|>
+#   filter(Category == "Non-erotic", !ID %in% c(men, women)) |>
+#   mutate(Arousal = (Hetero_Men_Arousal + Hetero_Women_Arousal + Homo_Men_Arousal + Homo_Women_Arousal ) / 4) |>
+#   slice_min(Arousal, n=10, with_ties = FALSE) |>
+#   pull(ID)
+# 
+# pos_arousing <-  napsero2 |>
+#   filter(Category == "Non-erotic", !ID %in% c(men, women, neutral)) |>
+#   mutate(Arousal = (Hetero_Men_Arousal + Hetero_Women_Arousal + Homo_Men_Arousal + Homo_Women_Arousal) / 4,
+#          Valence = (Hetero_Men_Valence + Hetero_Women_Valence + Homo_Men_Valence + Homo_Women_Valence) / 4) |>
+#   filter(Valence > 5) |>
+#   slice_max(Arousal, n=10, with_ties = FALSE) |>
+#   pull(ID)
+
+# selected2 <- unique(c(men, homo_men, women, homo_women, neutral, pos_arousing))
+
+#only has unique images 
+selected_erotic_2 <- c(men, women, homo_men,homo_women)
+
+cat(
+  paste0("N (men) = ", length(men), "\nN (homo_men) = ", length(homo_men),  "\nN (women) = ", length(women), "\nN (homo_women) = ", length(homo_women),
+       "\nTotal = ", length(selected_erotic_2))
 )
 
-homo_women <- napsero2 |>
-  filter(Category != "Non-erotic", !ID %in% men) |>
-  group_by(Category) |>
-  slice_max(Homo_Women_Arousal, n=8, with_ties = FALSE) |>
-  pull(ID) |> 
-  c(
-    napsero2 |>
-      filter(Category != "Non-erotic", !ID %in% men) |>
-      group_by(Category) |>
-      slice_min(Homo_Women_Arousal, n=2, with_ties = FALSE) |>
-      pull(ID)
-  )
-
-neutral <-  napsero2|>
-  filter(Category == "Non-erotic", !ID %in% c(men, women)) |>
-  mutate(Arousal = (Hetero_Men_Arousal + Hetero_Women_Arousal + Homo_Men_Arousal + Homo_Women_Arousal ) / 4) |>
-  slice_min(Arousal, n=10, with_ties = FALSE) |>
-  pull(ID)
-
-pos_arousing <-  napsero2 |>
-  filter(Category == "Non-erotic", !ID %in% c(men, women, neutral)) |>
-  mutate(Arousal = (Hetero_Men_Arousal + Hetero_Women_Arousal + Homo_Men_Arousal + Homo_Women_Arousal) / 4,
-         Valence = (Hetero_Men_Valence + Hetero_Women_Valence + Homo_Men_Valence + Homo_Women_Valence) / 4) |>
-  filter(Valence > 5) |>
-  slice_max(Arousal, n=10, with_ties = FALSE) |>
-  pull(ID)
-
-selected2 <- unique(c(men, homo_men, women, homo_women, neutral, pos_arousing))
-selected_erotic_2 <- unique(c(men, homo_men, women, homo_women))
-
-cat(
-  paste0("N (men) = ", length(men), "\nN (homo_men) = ", length(homo_men),  "\nN (women) = ", length(women), "N (homo_women) = ", length(homo_women), "\nN (neutral) = ", length(neutral),  "\nN (arousing-positive) = ", length(pos_arousing),
-       "\nTotal = ", length(selected2))
-)
 ```
@@
 
+# dat2 |>
+#   filter(Category != "Non-erotic") |>
+#   ggplot(aes(x=Valence, y=Arousal)) +
+#   geom_point(aes(shape=Selected, color=Category), size=6, alpha=0.8) +
+#   ggside::geom_ysidedensity(data=filter(dat2, Selected), aes(color=Category), key_glyph = draw_key_blank) +
+#   ggside::geom_xsidedensity(data=filter(dat2, Selected), aes(color=Category), key_glyph = draw_key_blank) +
+#   # ggrepel::geom_label_repel(aes(label = label)) +
+#   scale_shape_manual(values=c("TRUE"=20, "FALSE"=4)) +
+#   scale_color_manual(values = c(
+#     "Opposite-sex Couple"="#673AB7", "Male Couple"= "#3F51B5", "Female Couple" = "#9C27B0",
+#     "Female" = "#E91E63", "Male"= "#2196F3")) +
+#   guides(shape = guide_legend(override.aes = list(color="white"))) +
+#   facet_grid(~Sexual_Orientation*Target) +
+#   theme_abyss() +
+#   theme(ggside.panel.grid.major = element_blank(), 
+#         ggside.axis.text = element_blank(),
+#         ggside.axis.line = element_blank())
+
 dat2 |>
   filter(Category != "Non-erotic") |>
-  ggplot(aes(x=Valence, y=Arousal)) +
-  geom_point(aes(shape=Selected, color=Category), size=6, alpha=0.8) +
-  ggside::geom_ysidedensity(data=filter(dat2, Selected), aes(color=Category), key_glyph = draw_key_blank) +
-  ggside::geom_xsidedensity(data=filter(dat2, Selected), aes(color=Category), key_glyph = draw_key_blank) +
-  # ggrepel::geom_label_repel(aes(label = label)) +
-  scale_shape_manual(values=c("TRUE"=20, "FALSE"=4)) +
+  ggplot(aes(x = Valence, y = Arousal)) +
+  geom_point(data = filter(dat2, Selected == FALSE),
+             aes(shape = Selected, color = Category), size = 4, alpha = 0.3) +
+  geom_point(data = filter(dat2, Sexual_Orientation == "Hetero", Target == "Men",
+                           Category %in% c("Opposite-sex Couple", "Female"), 
+                           ID %in% men | Selected == FALSE),
+             aes(shape = Selected, color = Category), size = 6, alpha = 0.8) +
+  geom_point(data = filter(dat2, Sexual_Orientation == "Hetero", Target == "Women",
+                           Category %in% c("Opposite-sex Couple", "Male"),
+                           ID %in% women | Selected == FALSE),
+             aes(shape = Selected, color = Category), size = 6, alpha = 0.8) +
+  geom_point(data = filter(dat2, Sexual_Orientation == "Homo", Target == "Men",
+                           Category %in% c("Male Couple", "Male"), 
+                           ID %in% homo_men | Selected == FALSE),
+             aes(shape = Selected, color = Category), size = 6, alpha = 0.8) +
+  geom_point(data = filter(dat2, Sexual_Orientation == "Homo", Target == "Women", 
+                           Category %in% c("Female Couple", "Female"), 
+                           ID %in% homo_women | Selected == FALSE),
+             aes(shape = Selected, color = Category), size = 6, alpha = 0.8) +
+  ggside::geom_ysidedensity(data = filter(dat2, Sexual_Orientation == "Hetero", Target == "Men",
+                           Category %in% c("Opposite-sex Couple", "Female")),
+                            aes(color = Category), key_glyph = draw_key_blank, alpha = 0.6) +
+  ggside::geom_xsidedensity(data = filter(dat2, Sexual_Orientation == "Hetero", Target == "Men",
+                           Category %in% c("Opposite-sex Couple", "Female")),
+                            aes(color = Category), key_glyph = draw_key_blank, alpha = 0.6) +
+  ggside::geom_ysidedensity(data = filter(dat2, Selected, Sexual_Orientation == "Hetero", Target == "Women", 
+                           Category %in% c("Opposite-sex Couple", "Male")),
+                            aes(color = Category), key_glyph = draw_key_blank, alpha = 0.6) +
+  ggside::geom_xsidedensity(data = filter(dat2, Selected, Sexual_Orientation == "Hetero", Target == "Women", 
+                           Category %in% c("Opposite-sex Couple", "Male")),
+                            aes(color = Category), key_glyph = draw_key_blank, alpha = 0.6) +
+  ggside::geom_ysidedensity(data = filter(dat2, Sexual_Orientation == "Homo", Target == "Men",
+                           Category %in% c("Male Couple", "Male")),
+                            aes(color = Category), key_glyph = draw_key_blank, alpha = 0.6) +
+  ggside::geom_xsidedensity(data = filter(dat2, Sexual_Orientation == "Homo", Target == "Men",
+                           Category %in% c("Male Couple", "Male")),
+                            aes(color = Category), key_glyph = draw_key_blank, alpha = 0.6) +
+  ggside::geom_ysidedensity(data = filter(dat2, Selected, Sexual_Orientation == "Homo", Target == "Women", 
+                           Category %in% c("Female Couple", "Female")),
+                            aes(color = Category), key_glyph = draw_key_blank, alpha = 0.6) +
+  ggside::geom_xsidedensity(data = filter(dat2, Selected, Sexual_Orientation == "Homo", Target == "Women", 
+                           Category %in% c("Female Couple", "Female")),
+                            aes(color = Category), key_glyph = draw_key_blank, alpha = 0.6) +
+  scale_shape_manual(values = c("TRUE" = 20, "FALSE" = 4)) +
   scale_color_manual(values = c(
-    "Opposite-sex Couple"="#673AB7", "Male Couple"= "#3F51B5", "Female Couple" = "#9C27B0",
-    "Female" = "#E91E63", "Male"= "#2196F3")) +
-  guides(shape = guide_legend(override.aes = list(color="white"))) +
-  facet_grid(~Sexual_Orientation*Target) +
+    "Opposite-sex Couple" = "#673AB7", "Male Couple" = "#3F51B5", "Female Couple" = "#9C27B0",
+    "Female" = "#E91E63", "Male" = "#2196F3")) +
+  guides(shape = guide_legend(override.aes = list(color = "white"))) +
+  facet_grid(~Sexual_Orientation * Target) +
   theme_abyss() +
@@
 
-write.csv(selection_erotic2, "stimuli_data_erotic2.csv", row.names=FALSE)
+write.csv(selection_erotic2, "stimuli_data2.csv", row.names=FALSE)
 knitr::kable(selection_erotic2)

### 2024-10-02 study1/analysis/3_realness.qmd
push

--- 2024-06-27 analysis/3_realness.qmd
@@
         legend.text = element_text(size = 10)) +
-  labs(y="Realness\n", fill="Images presented as:", color="Images presented as:",
+  labs(y="Realness\n", fill="Erotic images presented as:", color="Erotic images presented as:",
        x = "\n'Could not discriminate AI-generated and real' Feedback",

### 2024-10-02 study1/experiment/stimuli_selection/selection.qmd
push

--- 2024-09-28 study1/stimuli_selection/selection.qmd
@@
         ggside.axis.line = element_blank())
+
 ```

### 2024-10-02 study2/experiment/stimuli_selection/selection.qmd
push

---
title: "Stimuli Selection"
format:
  html:
    embed-resources: true
editor_options: 
  chunk_output_type: console
---

```{r}
#| include: false
#| code-fold: true

library(tidyverse)
library(easystats)
library(ggrepel)

napsero <- readxl::read_excel("norms_napsero.XLSX", sheet = "Ratings") |>
  full_join(readxl::read_excel("norms_napsero.XLSX", sheet = "Image parameters"), by = join_by("ID", "Category")) |>
  select(-contains("_SD")) |>
  rename(Orientation = `V/H`,
         Hetero_Men_Valence = val_M_HeM,
         Hetero_Women_Valence = val_M_HeF,
         Homo_Men_Valence = val_M_HoM,
         Homo_Women_Valence = val_M_HoF,
         Hetero_Men_Arousal = aro_M_HeM,
         Hetero_Women_Arousal = aro_M_HeF,
         Homo_Men_Arousal = aro_M_HoM,
         Homo_Women_Arousal = aro_M_HoF) |>
  mutate(across(c("Luminance", "Contrast", "JPEG_size80", "LABL", "LABA", "LABB", "Entropy"), as.numeric),
         Description = NA)
```

## Selection

### Select based on norms
```{r}
men <- napsero |>
  filter(Category %in% c("Female", "Opposite-sex Couple")) |>
  group_by(Category) |>
  slice_max(Hetero_Men_Arousal, n=25, with_ties = FALSE) |>
  pull(ID)

homo_men <- napsero |>
  filter(Category %in% c("Male", "Male Couple")) |>
  group_by(Category) |>
  slice_max(Homo_Men_Arousal, n=25, with_ties = FALSE) |>
  pull(ID)

women <- napsero |>
  filter(Category %in% c("Male", "Opposite-sex Couple")) |> 
  group_by(Category) |> 
  slice_max(Hetero_Women_Arousal, n=25, with_ties = FALSE) |>
  pull(ID)

homo_women <- napsero |>
  filter(Category %in% c("Female", "Female Couple")) |>
  group_by(Category) |>
  slice_max(Homo_Women_Arousal, n=25, with_ties = FALSE) |>
  pull(ID)

selected_erotic <- c(men, women, homo_men,homo_women)

cat(
  paste0("N (men) = ", length(men), "\nN (homo_men) = ", length(homo_men),  "\nN (women) = ", length(women), "\nN (homo_women) = ", length(homo_women))
)
```

### Visualization

```{r}
#| fig.width: 10
#| fig.height: 8
#| dpi: 300
#| message: false

dat <- napsero |>
  select(ID, Category, ends_with("_Arousal"), ends_with("_Valence")) |> 
  pivot_longer(cols = c("Hetero_Men_Valence", "Hetero_Men_Arousal", "Hetero_Women_Valence", "Hetero_Women_Arousal", "Homo_Men_Valence", "Homo_Men_Arousal", "Homo_Women_Valence", "Homo_Women_Arousal")) |>
  separate(name, into=c("Participant1", "Participant2", "Variable")) |>
  mutate("Target" = paste0(Participant1, "_", Participant2)) |> 
  select(-Participant1, -Participant2) |> 
  pivot_wider(names_from=Variable, values_from=value) |> 
  mutate(Selected = case_when(
    Target == "Hetero_Men" & ID %in% men ~ TRUE,
    Target == "Homo_Men" & ID %in% homo_men ~ TRUE,
    Target == "Hetero_Women" & ID %in% women ~ TRUE,
    Target == "Homo_Women" & ID %in% homo_women ~ TRUE,
    .default = FALSE
  ))

dat |> 
  ggplot(aes(x = Valence, y = Arousal)) +
  geom_point(data=filter(dat, Selected==FALSE),
             aes(shape = Selected, color = Category), size = 4, alpha = 0.3) +
  geom_point(data=filter(dat, Selected==TRUE),
             aes(shape = Selected, color = Category), size = 4, alpha = 0.8) +
  facet_wrap(~Target) +
  ggside::geom_ysidedensity(data=filter(dat, Selected==TRUE), 
                            aes(color = Category),
                            key_glyph = draw_key_blank, alpha = 0.0) +
  ggside::geom_xsidedensity(data=filter(dat, Selected==TRUE), 
                            aes(color = Category), 
                            key_glyph = draw_key_blank, alpha = 0.0)  +
  scale_shape_manual(values = c("TRUE" = 20, "FALSE" = 4)) +
  scale_color_manual(values = c(
    "Opposite-sex Couple" = "#673AB7", "Male Couple" = "#3F51B5", "Female Couple" = "#9C27B0",
    "Female" = "#E91E63", "Male" = "#2196F3", "Non-erotic"="grey")) +
  guides(shape = guide_legend(override.aes = list(color = "white"))) +
  theme_abyss() +
  theme(ggside.panel.grid.major = element_blank(), 
        ggside.axis.text = element_blank(),
        ggside.axis.line = element_blank())
```

## Final Selection

- ID: picture category and number
- V/H: vertical / horizontal
- Av/Ap: avoidance - approach dimension
- M: mean
- SD: standard deviation
- JPEG_size80: index of overall complexity
- LABL: luminance in CIE L*a*b color space
- LABA: the amount of red color CIE L*a*b color space
- LABB: the amount of the green color CIE L*a*b color space
- Entropy: the amount of complexity in gray scale. Images with high entropy are images that are more "noisy" and have a high degree of contrast.

```{r}
#| code-fold: true

selection_erotic2 <- napsero2 |> 
  filter(ID %in% selected_erotic_2)

write.csv(selection_erotic2, "stimuli_data2.csv", row.names=FALSE)
knitr::kable(selection_erotic2)
```

```{r}
#| code-fold: true
json <- selection2 |> 
  select(stimulus=ID, Category, Orientation) |> 
  jsonlite::toJSON()

write(paste("var stimuli_list2 = ", json), "stimuli_list2.js")
```

```{r}
#| code-fold: true
path_ero <- "C:/Dropbox/RECHERCHE/docs/Stimuli/NAPS/NAPS_ERO/"
path_naps <- "C:/Dropbox/RECHERCHE/docs/Stimuli/NAPS/NAPS/"

# Remove all current files
unlink("../stimuli/*")

# Copy each file
for(file in selected) {
  if(str_detect(file, "Male|Female")) {
    file.copy(paste0(path_ero, file), "../stimuli/")
  } else {
    file.copy(paste0(path_naps, file), "../stimuli/")
  }
}
```

### 2024-10-02 analysis/0_preprocessing.py

@@ -1,830 +1,0 @@
-import json
-
-import numpy as np
-import pandas as pd
-
-# Note: new data from FakeFace2 got saved in this repo during June 2024.
-# Make sure to use only files before.
-
-
-# Get files from OSF ======================================================
-def osf_listfiles(data_subproject="", token="", after_date=None):
-    try:
-        import osfclient
-    except ImportError:
-        raise ImportError("Please install 'osfclient' (`pip install osfclient`)")
-    osf = osfclient.OSF(token=token).project(data_subproject)  # Connect to project
-    storage = [s for s in osf.storages][0]  # Access storage component
-    files = [
-        {
-            "name": file.name.replace(".csv", ""),
-            "date": pd.to_datetime(file.date_created),
-            "url": file._download_url,
-            "size": file.size,
-            "file": file,
-        }
-        for file in storage.files
-    ]
-
-    if after_date is not None:
-        date = pd.to_datetime(after_date, format="%d/%m/%Y", utc=True)
-        files = [f for f, d in zip(files, [f["date"] > date for f in files]) if d]
-    return files
-
-
-token = ""  # Paste OSF token here to access private repositories
-files = osf_listfiles(
-    token=token,
-    data_subproject="sm4jc",  # Data subproject ID
-    after_date="19/01/2024",
-)
-
-
-# Loop through files ======================================================
-# Initialize empty dataframes
-alldata = pd.DataFrame()
-alldata_subs = pd.DataFrame()
-norm_data = pd.read_csv("../study1/stimuli_selection/stimuli_data.csv").rename(
-    columns={
-        "ID": "Item",
-        "JPEG_size80": "Complexity",
-        "LABA": "Red",
-        "LABB": "Green",
-        "Luminance": "Luminance2",
-        "LABL": "Luminance",
-    }
-)
-
-
-for i, file in enumerate(files):
-    print(f"File N°{i+1}/{len(files)}")
-
-    if (
-        "Participant" in alldata_subs.columns
-        and file["name"] in alldata_subs["Participant"].values
-    ):
-        continue
-
-    download_ok = False
-    while download_ok == False:
-        data = pd.read_csv(file["file"]._get(file["url"], stream=True).raw)
-        if len(data) > 0:
-            download_ok = True
-
-    # Participant ========================================================
-    # data["screen"].unique()
-
-    # Browser info -------------------------------------------------------
-    browser = data[data["screen"] == "browser_info"].iloc[0]
-
[…]

### 2024-10-02 analysis/old_1_models.R

@@ -1,226 +1,0 @@
-# This script is an .R file as it is called from a High Performance Cluster.
-# The models that are generated are then saved locally and used in the analysis.
-# The compiled models are not shared due to repository size constraints.
-
-# qsub -jc test.long /mnt/lustre/users/psych/dmm56/FictionEro/run.sh
-
-# Options -----------------------------------------------------------------
-
-# path <- "/mnt/lustre/users/psych/dmm56/FictionEro/models/"
-path <- "./models/"
-iter <- 1000
-# cores <- parallel::detectCores(logical = FALSE)
-cores <- 8
-
-options(mc.cores = cores,
-        brms.backend = "cmdstanr")
-
-log <- c("Cores" = cores)
-write.csv(as.data.frame(log), paste0(path, "log.csv"))
-
-
-# Packages ----------------------------------------------------------------
-library(tidyverse)
-library(datawizard)
-library(brms)
-
-log <- c(log, "Packages" = TRUE)
-write.csv(as.data.frame(log), paste0(path, "log.csv"))
-
-# Data --------------------------------------------------------------------
-
-dfsub <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/main/data/data_participants.csv")
-df <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/main/data/data.csv") |>
-  dplyr::full_join(
-    dfsub[c("Participant", "Experimenter", "Language", "Feedback_LabelsIncorrect")],
-    by = dplyr::join_by(Participant)
-  ) |>
-  # datawizard::rescale(select=c("Arousal", "Enticement", "Realness"), range=c(0, 1), to=c(0.001, 0.999)) |>
-  # datawizard::rescale(select=c("Valence"), range=c(-1, 1), to=c(0.001, 0.999)) |>
-  datawizard::rescale(select=c("Valence"), range=c(-1, 1), to=c(0, 1)) |>
-  dplyr::mutate(Condition = forcats::fct_relevel(Condition, "Photograph", "AI-Generated"),
-         Relevance =  forcats::fct_relevel(Relevance, "Relevant", "Irrelevant", "Non-erotic"),
-         Sex =  forcats::fct_relevel(Sex, "Male", "Female"),
-         Feedback_LabelsIncorrect =  forcats::fct_relevel(Feedback_LabelsIncorrect, "False", "True"))
-
-log <- c(log, "Data" = TRUE)
-write.csv(as.data.frame(log), paste0(path, "log.csv"))
-
-
[…]

### 2024-10-02 study1/analysis/0_preprocessing.py

@@ -1,0 +1,830 @@
+import json
+
+import numpy as np
+import pandas as pd
+
+# Note: new data from FakeFace2 got saved in this repo during June 2024.
+# Make sure to use only files before.
+
+
+# Get files from OSF ======================================================
+def osf_listfiles(data_subproject="", token="", after_date=None):
+    try:
+        import osfclient
+    except ImportError:
+        raise ImportError("Please install 'osfclient' (`pip install osfclient`)")
+    osf = osfclient.OSF(token=token).project(data_subproject)  # Connect to project
+    storage = [s for s in osf.storages][0]  # Access storage component
+    files = [
+        {
+            "name": file.name.replace(".csv", ""),
+            "date": pd.to_datetime(file.date_created),
+            "url": file._download_url,
+            "size": file.size,
+            "file": file,
+        }
+        for file in storage.files
+    ]
+
+    if after_date is not None:
+        date = pd.to_datetime(after_date, format="%d/%m/%Y", utc=True)
+        files = [f for f, d in zip(files, [f["date"] > date for f in files]) if d]
+    return files
+
+
+token = ""  # Paste OSF token here to access private repositories
+files = osf_listfiles(
+    token=token,
+    data_subproject="sm4jc",  # Data subproject ID
+    after_date="19/01/2024",
+)
+
+
+# Loop through files ======================================================
+# Initialize empty dataframes
+alldata = pd.DataFrame()
+alldata_subs = pd.DataFrame()
+norm_data = pd.read_csv("../study1/stimuli_selection/stimuli_data.csv").rename(
+    columns={
+        "ID": "Item",
+        "JPEG_size80": "Complexity",
+        "LABA": "Red",
+        "LABB": "Green",
+        "Luminance": "Luminance2",
+        "LABL": "Luminance",
+    }
+)
+
+
+for i, file in enumerate(files):
+    print(f"File N°{i+1}/{len(files)}")
+
+    if (
+        "Participant" in alldata_subs.columns
+        and file["name"] in alldata_subs["Participant"].values
+    ):
+        continue
+
+    download_ok = False
+    while download_ok == False:
+        data = pd.read_csv(file["file"]._get(file["url"], stream=True).raw)
+        if len(data) > 0:
+            download_ok = True
+
+    # Participant ========================================================
+    # data["screen"].unique()
+
+    # Browser info -------------------------------------------------------
+    browser = data[data["screen"] == "browser_info"].iloc[0]
+
[…]

### 2024-10-02 study1/analysis/old_1_models.R

@@ -1,0 +1,226 @@
+# This script is an .R file as it is called from a High Performance Cluster.
+# The models that are generated are then saved locally and used in the analysis.
+# The compiled models are not shared due to repository size constraints.
+
+# qsub -jc test.long /mnt/lustre/users/psych/dmm56/FictionEro/run.sh
+
+# Options -----------------------------------------------------------------
+
+# path <- "/mnt/lustre/users/psych/dmm56/FictionEro/models/"
+path <- "./models/"
+iter <- 1000
+# cores <- parallel::detectCores(logical = FALSE)
+cores <- 8
+
+options(mc.cores = cores,
+        brms.backend = "cmdstanr")
+
+log <- c("Cores" = cores)
+write.csv(as.data.frame(log), paste0(path, "log.csv"))
+
+
+# Packages ----------------------------------------------------------------
+library(tidyverse)
+library(datawizard)
+library(brms)
+
+log <- c(log, "Packages" = TRUE)
+write.csv(as.data.frame(log), paste0(path, "log.csv"))
+
+# Data --------------------------------------------------------------------
+
+dfsub <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/main/data/data_participants.csv")
+df <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/main/data/data.csv") |>
+  dplyr::full_join(
+    dfsub[c("Participant", "Experimenter", "Language", "Feedback_LabelsIncorrect")],
+    by = dplyr::join_by(Participant)
+  ) |>
+  # datawizard::rescale(select=c("Arousal", "Enticement", "Realness"), range=c(0, 1), to=c(0.001, 0.999)) |>
+  # datawizard::rescale(select=c("Valence"), range=c(-1, 1), to=c(0.001, 0.999)) |>
+  datawizard::rescale(select=c("Valence"), range=c(-1, 1), to=c(0, 1)) |>
+  dplyr::mutate(Condition = forcats::fct_relevel(Condition, "Photograph", "AI-Generated"),
+         Relevance =  forcats::fct_relevel(Relevance, "Relevant", "Irrelevant", "Non-erotic"),
+         Sex =  forcats::fct_relevel(Sex, "Male", "Female"),
+         Feedback_LabelsIncorrect =  forcats::fct_relevel(Feedback_LabelsIncorrect, "False", "True"))
+
+log <- c(log, "Data" = TRUE)
+write.csv(as.data.frame(log), paste0(path, "log.csv"))
+
+
[…]

### 2024-10-02 study1/demographics.js

@@ -1,212 +1,0 @@
-// Full screen
-var fullscreen_on = {
-    type: jsPsychFullscreen,
-    message: fullscreen_text,
-    button_label: fullscreen_button,
-    fullscreen_mode: true,
-    delay_after: 0,
-}
-
-var fullscreen_off = {
-    type: jsPsychFullscreen,
-    message: fullscreen_text,
-    button_label: fullscreen_button,
-    fullscreen_mode: false,
-}
-
-// Retrieve and save browser info ========================================================
-var demographics_browser_info = {
-    type: jsPsychBrowserCheck,
-    data: {
-        screen: "browser_info",
-        date: new Date().toLocaleDateString("fr-FR"),
-        time: new Date().toLocaleTimeString("fr-FR"),
-    },
-    on_finish: function (data) {
-        dat = jsPsych.data.get().filter({ screen: "browser_info" }).values()[0]
-
-        // Rename
-        data["screen_height"] = dat["height"]
-        data["screen_width"] = dat["width"]
-
-        // Add URL variables - ?sona_id=x&exp=1
-        let urlvars = jsPsych.data.urlVariables()
-        data["researcher"] = urlvars["exp"]
-        data["language"] = urlvars["lang"]
-        data["sona_id"] = urlvars["sona_id"]
-        data["prolific_id"] = urlvars["PROLIFIC_PID"] // Prolific
-        data["study_id"] = urlvars["STUDY_ID"] // Prolific
-        data["session_id"] = urlvars["SESSION_ID"] // Prolific
-    },
-}
-
-// Participant ID ========================================================================
-var demographics_participant_id = {
-    type: jsPsychSurveyText,
-    questions: [
-        {
-            prompt: "Enter participant ID:",
-            placeholder: "001",
-            name: "Participant_ID",
-        },
-    ],
-    data: {
-        screen: "participant_id",
-    },
-    on_finish: function () {
-        // Store `participant_id` so that it can be reused later
-        jsPsych.data.addProperties({
-            participant_id: jsPsych.data.get().last().values()[0]["response"][
-                "Participant_ID"
-            ],
-        })
-    },
-}
-
-// Consent form ========================================================================
-var demographics_consent = {
-    type: jsPsychHtmlButtonResponse,
-    css_classes: ["narrow-text"],
-    stimulus: consent_text,
-    choices: [consent_button],
-    data: { screen: "consent" },
-}
-
-// Thank you ========================================================================
-var demographics_debriefing = {
-    type: jsPsychHtmlButtonResponse,
[…]

### 2024-10-02 study1/experiment/demographics.js

@@ -1,0 +1,212 @@
+// Full screen
+var fullscreen_on = {
+    type: jsPsychFullscreen,
+    message: fullscreen_text,
+    button_label: fullscreen_button,
+    fullscreen_mode: true,
+    delay_after: 0,
+}
+
+var fullscreen_off = {
+    type: jsPsychFullscreen,
+    message: fullscreen_text,
+    button_label: fullscreen_button,
+    fullscreen_mode: false,
+}
+
+// Retrieve and save browser info ========================================================
+var demographics_browser_info = {
+    type: jsPsychBrowserCheck,
+    data: {
+        screen: "browser_info",
+        date: new Date().toLocaleDateString("fr-FR"),
+        time: new Date().toLocaleTimeString("fr-FR"),
+    },
+    on_finish: function (data) {
+        dat = jsPsych.data.get().filter({ screen: "browser_info" }).values()[0]
+
+        // Rename
+        data["screen_height"] = dat["height"]
+        data["screen_width"] = dat["width"]
+
+        // Add URL variables - ?sona_id=x&exp=1
+        let urlvars = jsPsych.data.urlVariables()
+        data["researcher"] = urlvars["exp"]
+        data["language"] = urlvars["lang"]
+        data["sona_id"] = urlvars["sona_id"]
+        data["prolific_id"] = urlvars["PROLIFIC_PID"] // Prolific
+        data["study_id"] = urlvars["STUDY_ID"] // Prolific
+        data["session_id"] = urlvars["SESSION_ID"] // Prolific
+    },
+}
+
+// Participant ID ========================================================================
+var demographics_participant_id = {
+    type: jsPsychSurveyText,
+    questions: [
+        {
+            prompt: "Enter participant ID:",
+            placeholder: "001",
+            name: "Participant_ID",
+        },
+    ],
+    data: {
+        screen: "participant_id",
+    },
+    on_finish: function () {
+        // Store `participant_id` so that it can be reused later
+        jsPsych.data.addProperties({
+            participant_id: jsPsych.data.get().last().values()[0]["response"][
+                "Participant_ID"
+            ],
+        })
+    },
+}
+
+// Consent form ========================================================================
+var demographics_consent = {
+    type: jsPsychHtmlButtonResponse,
+    css_classes: ["narrow-text"],
+    stimulus: consent_text,
+    choices: [consent_button],
+    data: { screen: "consent" },
+}
+
+// Thank you ========================================================================
+var demographics_debriefing = {
+    type: jsPsychHtmlButtonResponse,
[…]

### 2024-10-02 study1/experiment/fiction.js

@@ -1,0 +1,270 @@
+// Parameters ======================================================
+var fiction_trialnumber = 1
+
+// instructions ====================================================
+var fiction_instructions1 = {
+    type: jsPsychHtmlButtonResponse,
+    choices: [text_instructionsbutton],
+    stimulus: text_instructions1,
+    data: { screen: "fiction_instructions1" },
+}
+
+var fiction_instructions2 = {
+    type: jsPsychHtmlButtonResponse,
+    choices: [text_instructionsbutton],
+    stimulus: text_instructions2,
+    data: { screen: "fiction_instructions2" },
+}
+
+// Condition assignment ============================================
+
+function assignCondition(stimuli_list) {
+    new_stimuli_list = []
+    // Loop through unique categories
+    for (let cat of [...new Set(stimuli_list.map((a) => a.Category))]) {
+        // Get all stimuli of this category
+        var cat_stimuli = stimuli_list.filter((a) => a.Category == cat)
+
+        // Shuffle cat_stimuli
+        cat_stimuli = shuffleArray(cat_stimuli) // Defined in instructions.js
+
+        // Assign half to "Reality" condition and half to "Fiction" condition
+        for (let i = 0; i < cat_stimuli.length; i++) {
+            cat_stimuli[i].Condition =
+                i < cat_stimuli.length / 2 ? "Reality" : "Fiction"
+        }
+
+        // Add to new_stimuli_list
+        new_stimuli_list.push(...cat_stimuli)
+    }
+    return new_stimuli_list
+}
+
+stimuli_list = assignCondition(stimuli_list)
+
+// Trials ==========================================================
+var fiction_preloadstims = {
+    type: jsPsychPreload,
+    images: stimuli_list.map((a) => "stimuli/" + a.stimulus),
+}
+
+function fiction_fixationcross(isi = 500, screen = "fiction_fixationcross") {
+    return {
+        type: jsPsychHtmlKeyboardResponse,
+        on_start: function () {
+            document.body.style.cursor = "none"
+        },
+        stimulus:
+            "<div  style='font-size:500%; position:fixed; text-align: center; top:50%; bottom:50%; right:20%; left:20%'>+</div>",
+        choices: ["s"],
+        trial_duration: isi,
+        save_trial_parameters: { trial_duration: true },
+        data: { screen: screen },
+    }
+}
+
+function fiction_cue(text_cue, duration = 1000) {
+    return {
[…]

### 2024-10-02 study1/experiment/instructions_english.js

@@ -1,0 +1,356 @@
+// =========================================================================================
+// Parameters
+// =========================================================================================
+function shuffleArray(array) {
+    for (let i = array.length - 1; i > 0; i--) {
+        const j = Math.floor(Math.random() * (i + 1))
+        ;[array[i], array[j]] = [array[j], array[i]]
+    }
+    return array
+}
+
+var color_cues = shuffleArray(["red", "blue", "green"])
+color_cues = { Reality: color_cues[0], Fiction: color_cues[1] }
+// =========================================================================================
+// Fiction
+// =========================================================================================
+var text_instructions1 =
+    "<h1>Instructions</h1>" +
+    // Left aligned text
+    "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>In this study, we aim at validating our <b>new image-generation algorithm</b> (based on a new form of Generative Adversarial Network - GAN - technology) trained to produce high-quality erotic (but also non-erotic content).</p>" +
+    "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>In the following task, you will be presented with erotic and non-erotic images generated by our algorithm (preceded by the word '<b style='color:" +
+    color_cues["Fiction"] +
+    "'>AI-generated</b>'), intermixed with real photos (preceded by the word '<b style='color:" +
+    color_cues["Reality"] +
+    "'>Photograph</b>') taken from public picture databases.</p > " +
+    "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>After each image, you will have to rate the images on the following scales:</p>" +
+    "<ul style='text-align: left; margin-left: 30%; margin-right: 30%;'>" +
+    // Arousal: embodied
+    "<li><b>Arousing</b>: How much do you find the image sexually arousing. This question is about your own <i>personal reaction</i> felt in your body when seeing the image.</li>" +
+    // Appeal: "objective"
+    "<li><b>Enticing</b>: How enticing and sexually appealing would you rate this image to be. Think of how much, in general, people similar to you in terms of gender and sexual orientation would like it.</li>" +
+    // Emotional Valence
+    "<li><b>Valence</b>: Did the image evoke a positive and pleasant (not necessarily sexual) feeling in you, or could it better characterized as negative and unpleasant? Think of how much you did enjoy (or not) looking at the image</li></ul>" +
+    // Contrasting explanation
[…]

### 2024-10-02 study1/experiment/instructions_french.js

@@ -1,0 +1,362 @@
+// =========================================================================================
+// Parameters
+// =========================================================================================
+function shuffleArray(array) {
+    for (let i = array.length - 1; i > 0; i--) {
+        const j = Math.floor(Math.random() * (i + 1))
+        ;[array[i], array[j]] = [array[j], array[i]]
+    }
+    return array
+}
+
+var color_cues = shuffleArray(["red", "blue", "green"])
+color_cues = { Reality: color_cues[0], Fiction: color_cues[1] }
+// =========================================================================================
+// Fiction
+// =========================================================================================
+var text_instructions1 =
+    "<h1>Instructions</h1>" +
+    // Left aligned text
+    "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>Dans cette étude, nous visons à valider notre <b>nouvel algorithme de génération d'images</b> (basé sur une nouvelle forme de technologie Generative Adversarial Network - GAN) entraîné pour produire du contenu érotique (mais aussi non-érotique) de haute qualité.</p>" +
+    "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>Dans la tâche suivante, on vous présentera des images érotiques et non-érotiques générées par notre algorithme (précédées de l'étiquette '<b style='color:" +
+    color_cues["Fiction"] +
+    "'>Générée par l'IA</b>'), mélangées à des photos réelles (précédées de l'étiquette  '<b style='color:" +
+    color_cues["Reality"] +
+    "'>Photographie</b>') tirées de bases de données d'images publiques.</p > " +
+    "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>Après chaque image, vous devrez l'évaluer sur les échelles suivantes:</p>" +
+    "<ul style='text-align: left; margin-left: 30%; margin-right: 30%;'>" +
+    // Arousal: embodied
+    "<li><b>Excitation</b>: Dans quelle mesure trouvez-vous l'image sexuellement excitante ? Cette question porte sur votre <i>réaction personnelle</i> ressentie dans votre corps à la vue de l'image.</li>" +
+    // Appeal: "objective"
[…]

### 2024-10-02 study1/experiment/instructions_italian.js

@@ -1,0 +1,349 @@
+// =========================================================================================
+// Parameters
+// =========================================================================================
+function shuffleArray(array) {
+    for (let i = array.length - 1; i > 0; i--) {
+        const j = Math.floor(Math.random() * (i + 1))
+        ;[array[i], array[j]] = [array[j], array[i]]
+    }
+    return array
+}
+
+var color_cues = shuffleArray(["red", "blue", "green"])
+color_cues = { Reality: color_cues[0], Fiction: color_cues[1] }
+// =========================================================================================
+// Fiction
+// =========================================================================================
+var text_instructions1 =
+    "<h1>Istruzioni</h1>" +
+    // Left aligned text
+    "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'> In questo studio, vogliamo validare il nostro nuovo <b>algoritmo di generazione di immagini</b> (basato su un nuovo tipo di Generative Adversarial Network - GAN) addestrato a produrre contenuti erotici (ma anche non erotici) di alta qualità.</p>" +
+    "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>Nel compito che svolgerai, ti saranno presentate delle immagini sia erotiche che non erotiche generate dal nostro algoritmo (precedute dalla parola '<b style='color:" +
+    color_cues["Fiction"] +
+    "'>Generata dal IA </b>'), inframmezzate da fotografie reali (precedute dalla parola '<b style='color:" +
+    color_cues["Reality"] +
+    "'>Fotografia</b>') provenienti da database di immagini pubblici.</p > " +
+    "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'> Dopo ogni immagine, ti sarà chiesto di esprimere un giudizio sulla scala seguente:</p>" +
+    "<ul style='text-align: left; margin-left: 30%; margin-right: 30%;'>" +
+    // Arousal: embodied
+    "<li><b>Eccitante</b>: Quanto trovi l'immagine sessualmente eccitante. Questa domanda riguarda la <i>reazione soggettiva</i> che percepisci nel tuo corpo quando vedi l'immagine.</li>" +
+    // Appeal: "objective"
[…]

### 2024-10-02 study1/experiment/instructions_spanish.js

@@ -1,0 +1,349 @@
+// =========================================================================================
+// Parameters
+// =========================================================================================
+function shuffleArray(array) {
+    for (let i = array.length - 1; i > 0; i--) {
+        const j = Math.floor(Math.random() * (i + 1))
+        ;[array[i], array[j]] = [array[j], array[i]]
+    }
+    return array
+}
+
+var color_cues = shuffleArray(["red", "blue", "green"])
+color_cues = { Reality: color_cues[0], Fiction: color_cues[1] }
+// =========================================================================================
+// Fiction
+// =========================================================================================
+var text_instructions1 =
+    "<h1>Instrucciones</h1>" +
+    // Left aligned text
+    "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>En este estudio buscamos validar nuestro <b> nuevo algoritmo de generación de imágenes </b> (basado en una nueva forma de Generative Adversarial Network - GAN - tecnología) diseñado para producir contenido erótico de alta calidad (pero también contenido no erótico).</p>" +
+    "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>En la siguiente tarea, se te presentarán imágenes eróticas y no eróticas generadas por nuestro algoritmo (precedidas por la palabra '<b style='color:" +
+    color_cues["Fiction"] +
+    "'>Generadas por IA (Inteligencia Artificial)</b>'), entremezcladas con fotos reales (precedidas por la palabra '<b style='color:" +
+    color_cues["Reality"] +
+    "'>Fotografías</b>') tomada de bases de datos públicas.</p > " +
+    "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>Después de cada imagen, deberás de evaluarla a través de las siguientes escalas:</p>" +
+    "<ul style='text-align: left; margin-left: 30%; margin-right: 30%;'>" +
+    // Arousal: embodied
+    "<li><b>Activante</b>: En qué medida encuentras la imagen sexualmente activante. Esta pregunta es acerca de tu <i>reacción personal</i> experimentada en tu cuerpo cuando ves la imagen.</li>" +
+    // Appeal: "objective"
[…]

### 2024-10-02 study1/experiment/questionnaires.js

@@ -1,0 +1,72 @@
+// Items =================================================
+
+var bait_dimensions = [
+    "GAAIS_Negative_9",
+    "GAAIS_Negative_10",
+    "GAAIS_Negative_15",
+    "GAAIS_Positive_7",
+    "GAAIS_Positive_12",
+    "GAAIS_Positive_17",
+    "BAIT_1_ImagesRealistic",
+    "BAIT_2_ImagesIssues",
+    "BAIT_3_VideosRealistic",
+    "BAIT_4_VideosIssues",
+    "BAIT_5_ImitatingReality",
+    "BAIT_6_EnvironmentReal",
+    "BAIT_7_TextRealistic",
+    "BAIT_8_TextIssues",
+]
+
+// Questionnaires =================================================
+
+function format_questions_analog(
+    items,
+    dimensions,
+    ticks = ["Inaccurate", "Accurate"]
+) {
+    var questions = []
+    for (const [index, element] of items.entries()) {
+        questions.push({
+            prompt: "<b>" + element + "</b>",
+            name: dimensions[index],
+            ticks: ticks,
+            required: false,
+            min: 0,
+            max: 1,
+            step: 0.01,
+            slider_start: 0.5,
+        })
+    }
+    return questions
+}
+
+// BAIT 2.0
+var questionnaire_bait = {
+    type: jsPsychMultipleSlider,
+    questions: format_questions_analog(
+        bait_items,
+        bait_dimensions,
+        // In Schepman et al. (2022) they removed 'Strongly'
+        (ticks = bait_ticks)
+    ),
+    randomize_question_order: true,
+    preamble: bait_instructions,
+    require_movement: false,
+    slider_width: 600,
+    data: {
+        screen: "questionnaire_bait",
+    },
+}
+
+// COPS ========================================================================
+// Consumption of Pornography Scale – General (COPS – G)
+// Hatchet al. (2023)
+var questionnaire_cops = {
+    type: jsPsychSurveyMultiChoice,
+    css_classes: ["narrow-text"],
+    preamble: cops_instructions,
+    questions: cops_items,
+    data: {
+        screen: "questionnaire_cops",
+    },
+}

### 2024-10-02 study1/experiment/stimuli_selection/stimuli_list.js

@@ -1,0 +1,1 @@
+var stimuli_list =  [{"stimulus":"Male_001_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_002_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_003_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_005_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_006_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_007_h.jpg","Category":"Male","Orientation":"h"},{"stimulus":"Male_008_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_009_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_011_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_012_h.jpg","Category":"Male","Orientation":"h"},{"stimulus":"Male_013_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_014_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_015_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_016_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_017_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_020_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_022_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_023_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_024_h.jpg","Category":"Male","Orientation":"h"},{"stimulus":"Male_025_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Female_001_h.jpg","Category":"Female","Orientation":"h"},{"stimulus":"Female_002_h.jpg","Category":"Female","Orientation":"h"},{"stimulus":"Female_003_v.jpg","Category":"Female","Orientation":"v"},{"stimulus":"Female_004_v.jpg","Category":"Female","Orientation":"v"},{"stimulus":"Female_005_v.jpg","Category":"Female","Orientation":"v"},{"stimulus":"Female_006_v.jpg","Category":"Female","Orientation":"v"},{"stimulus":"Female_008_v.jpg","Category":"Female","Orientation":"v"},{"stimulus":"Female_009_h.jpg","Catego
[…]

### 2024-10-02 study1/fiction.js

@@ -1,270 +1,0 @@
-// Parameters ======================================================
-var fiction_trialnumber = 1
-
-// instructions ====================================================
-var fiction_instructions1 = {
-    type: jsPsychHtmlButtonResponse,
-    choices: [text_instructionsbutton],
-    stimulus: text_instructions1,
-    data: { screen: "fiction_instructions1" },
-}
-
-var fiction_instructions2 = {
-    type: jsPsychHtmlButtonResponse,
-    choices: [text_instructionsbutton],
-    stimulus: text_instructions2,
-    data: { screen: "fiction_instructions2" },
-}
-
-// Condition assignment ============================================
-
-function assignCondition(stimuli_list) {
-    new_stimuli_list = []
-    // Loop through unique categories
-    for (let cat of [...new Set(stimuli_list.map((a) => a.Category))]) {
-        // Get all stimuli of this category
-        var cat_stimuli = stimuli_list.filter((a) => a.Category == cat)
-
-        // Shuffle cat_stimuli
-        cat_stimuli = shuffleArray(cat_stimuli) // Defined in instructions.js
-
-        // Assign half to "Reality" condition and half to "Fiction" condition
-        for (let i = 0; i < cat_stimuli.length; i++) {
-            cat_stimuli[i].Condition =
-                i < cat_stimuli.length / 2 ? "Reality" : "Fiction"
-        }
-
-        // Add to new_stimuli_list
-        new_stimuli_list.push(...cat_stimuli)
-    }
-    return new_stimuli_list
-}
-
-stimuli_list = assignCondition(stimuli_list)
-
-// Trials ==========================================================
-var fiction_preloadstims = {
-    type: jsPsychPreload,
-    images: stimuli_list.map((a) => "stimuli/" + a.stimulus),
-}
-
-function fiction_fixationcross(isi = 500, screen = "fiction_fixationcross") {
-    return {
-        type: jsPsychHtmlKeyboardResponse,
-        on_start: function () {
-            document.body.style.cursor = "none"
-        },
-        stimulus:
-            "<div  style='font-size:500%; position:fixed; text-align: center; top:50%; bottom:50%; right:20%; left:20%'>+</div>",
-        choices: ["s"],
-        trial_duration: isi,
-        save_trial_parameters: { trial_duration: true },
-        data: { screen: screen },
-    }
-}
-
-function fiction_cue(text_cue, duration = 1000) {
-    return {
[…]

### 2024-10-02 study1/instructions_english.js

@@ -1,356 +1,0 @@
-// =========================================================================================
-// Parameters
-// =========================================================================================
-function shuffleArray(array) {
-    for (let i = array.length - 1; i > 0; i--) {
-        const j = Math.floor(Math.random() * (i + 1))
-        ;[array[i], array[j]] = [array[j], array[i]]
-    }
-    return array
-}
-
-var color_cues = shuffleArray(["red", "blue", "green"])
-color_cues = { Reality: color_cues[0], Fiction: color_cues[1] }
-// =========================================================================================
-// Fiction
-// =========================================================================================
-var text_instructions1 =
-    "<h1>Instructions</h1>" +
-    // Left aligned text
-    "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>In this study, we aim at validating our <b>new image-generation algorithm</b> (based on a new form of Generative Adversarial Network - GAN - technology) trained to produce high-quality erotic (but also non-erotic content).</p>" +
-    "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>In the following task, you will be presented with erotic and non-erotic images generated by our algorithm (preceded by the word '<b style='color:" +
-    color_cues["Fiction"] +
-    "'>AI-generated</b>'), intermixed with real photos (preceded by the word '<b style='color:" +
-    color_cues["Reality"] +
-    "'>Photograph</b>') taken from public picture databases.</p > " +
-    "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>After each image, you will have to rate the images on the following scales:</p>" +
-    "<ul style='text-align: left; margin-left: 30%; margin-right: 30%;'>" +
-    // Arousal: embodied
-    "<li><b>Arousing</b>: How much do you find the image sexually arousing. This question is about your own <i>personal reaction</i> felt in your body when seeing the image.</li>" +
-    // Appeal: "objective"
-    "<li><b>Enticing</b>: How enticing and sexually appealing would you rate this image to be. Think of how much, in general, people similar to you in terms of gender and sexual orientation would like it.</li>" +
-    // Emotional Valence
-    "<li><b>Valence</b>: Did the image evoke a positive and pleasant (not necessarily sexual) feeling in you, or could it better characterized as negative and unpleasant? Think of how much you did enjoy (or not) looking at the image</li></ul>" +
-    // Contrasting explanation
[…]

### 2024-10-02 study1/instructions_french.js

@@ -1,362 +1,0 @@
-// =========================================================================================
-// Parameters
-// =========================================================================================
-function shuffleArray(array) {
-    for (let i = array.length - 1; i > 0; i--) {
-        const j = Math.floor(Math.random() * (i + 1))
-        ;[array[i], array[j]] = [array[j], array[i]]
-    }
-    return array
-}
-
-var color_cues = shuffleArray(["red", "blue", "green"])
-color_cues = { Reality: color_cues[0], Fiction: color_cues[1] }
-// =========================================================================================
-// Fiction
-// =========================================================================================
-var text_instructions1 =
-    "<h1>Instructions</h1>" +
-    // Left aligned text
-    "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>Dans cette étude, nous visons à valider notre <b>nouvel algorithme de génération d'images</b> (basé sur une nouvelle forme de technologie Generative Adversarial Network - GAN) entraîné pour produire du contenu érotique (mais aussi non-érotique) de haute qualité.</p>" +
-    "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>Dans la tâche suivante, on vous présentera des images érotiques et non-érotiques générées par notre algorithme (précédées de l'étiquette '<b style='color:" +
-    color_cues["Fiction"] +
-    "'>Générée par l'IA</b>'), mélangées à des photos réelles (précédées de l'étiquette  '<b style='color:" +
-    color_cues["Reality"] +
-    "'>Photographie</b>') tirées de bases de données d'images publiques.</p > " +
-    "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>Après chaque image, vous devrez l'évaluer sur les échelles suivantes:</p>" +
-    "<ul style='text-align: left; margin-left: 30%; margin-right: 30%;'>" +
-    // Arousal: embodied
-    "<li><b>Excitation</b>: Dans quelle mesure trouvez-vous l'image sexuellement excitante ? Cette question porte sur votre <i>réaction personnelle</i> ressentie dans votre corps à la vue de l'image.</li>" +
-    // Appeal: "objective"
[…]

### 2024-10-02 study1/instructions_italian.js

@@ -1,349 +1,0 @@
-// =========================================================================================
-// Parameters
-// =========================================================================================
-function shuffleArray(array) {
-    for (let i = array.length - 1; i > 0; i--) {
-        const j = Math.floor(Math.random() * (i + 1))
-        ;[array[i], array[j]] = [array[j], array[i]]
-    }
-    return array
-}
-
-var color_cues = shuffleArray(["red", "blue", "green"])
-color_cues = { Reality: color_cues[0], Fiction: color_cues[1] }
-// =========================================================================================
-// Fiction
-// =========================================================================================
-var text_instructions1 =
-    "<h1>Istruzioni</h1>" +
-    // Left aligned text
-    "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'> In questo studio, vogliamo validare il nostro nuovo <b>algoritmo di generazione di immagini</b> (basato su un nuovo tipo di Generative Adversarial Network - GAN) addestrato a produrre contenuti erotici (ma anche non erotici) di alta qualità.</p>" +
-    "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>Nel compito che svolgerai, ti saranno presentate delle immagini sia erotiche che non erotiche generate dal nostro algoritmo (precedute dalla parola '<b style='color:" +
-    color_cues["Fiction"] +
-    "'>Generata dal IA </b>'), inframmezzate da fotografie reali (precedute dalla parola '<b style='color:" +
-    color_cues["Reality"] +
-    "'>Fotografia</b>') provenienti da database di immagini pubblici.</p > " +
-    "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'> Dopo ogni immagine, ti sarà chiesto di esprimere un giudizio sulla scala seguente:</p>" +
-    "<ul style='text-align: left; margin-left: 30%; margin-right: 30%;'>" +
-    // Arousal: embodied
-    "<li><b>Eccitante</b>: Quanto trovi l'immagine sessualmente eccitante. Questa domanda riguarda la <i>reazione soggettiva</i> che percepisci nel tuo corpo quando vedi l'immagine.</li>" +
-    // Appeal: "objective"
[…]

### 2024-10-02 study1/instructions_spanish.js

@@ -1,349 +1,0 @@
-// =========================================================================================
-// Parameters
-// =========================================================================================
-function shuffleArray(array) {
-    for (let i = array.length - 1; i > 0; i--) {
-        const j = Math.floor(Math.random() * (i + 1))
-        ;[array[i], array[j]] = [array[j], array[i]]
-    }
-    return array
-}
-
-var color_cues = shuffleArray(["red", "blue", "green"])
-color_cues = { Reality: color_cues[0], Fiction: color_cues[1] }
-// =========================================================================================
-// Fiction
-// =========================================================================================
-var text_instructions1 =
-    "<h1>Instrucciones</h1>" +
-    // Left aligned text
-    "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>En este estudio buscamos validar nuestro <b> nuevo algoritmo de generación de imágenes </b> (basado en una nueva forma de Generative Adversarial Network - GAN - tecnología) diseñado para producir contenido erótico de alta calidad (pero también contenido no erótico).</p>" +
-    "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>En la siguiente tarea, se te presentarán imágenes eróticas y no eróticas generadas por nuestro algoritmo (precedidas por la palabra '<b style='color:" +
-    color_cues["Fiction"] +
-    "'>Generadas por IA (Inteligencia Artificial)</b>'), entremezcladas con fotos reales (precedidas por la palabra '<b style='color:" +
-    color_cues["Reality"] +
-    "'>Fotografías</b>') tomada de bases de datos públicas.</p > " +
-    "<p style='text-align: left; margin-left: 30%; margin-right: 30%;'>Después de cada imagen, deberás de evaluarla a través de las siguientes escalas:</p>" +
-    "<ul style='text-align: left; margin-left: 30%; margin-right: 30%;'>" +
-    // Arousal: embodied
-    "<li><b>Activante</b>: En qué medida encuentras la imagen sexualmente activante. Esta pregunta es acerca de tu <i>reacción personal</i> experimentada en tu cuerpo cuando ves la imagen.</li>" +
-    // Appeal: "objective"
[…]

### 2024-10-02 study1/questionnaires.js

@@ -1,72 +1,0 @@
-// Items =================================================
-
-var bait_dimensions = [
-    "GAAIS_Negative_9",
-    "GAAIS_Negative_10",
-    "GAAIS_Negative_15",
-    "GAAIS_Positive_7",
-    "GAAIS_Positive_12",
-    "GAAIS_Positive_17",
-    "BAIT_1_ImagesRealistic",
-    "BAIT_2_ImagesIssues",
-    "BAIT_3_VideosRealistic",
-    "BAIT_4_VideosIssues",
-    "BAIT_5_ImitatingReality",
-    "BAIT_6_EnvironmentReal",
-    "BAIT_7_TextRealistic",
-    "BAIT_8_TextIssues",
-]
-
-// Questionnaires =================================================
-
-function format_questions_analog(
-    items,
-    dimensions,
-    ticks = ["Inaccurate", "Accurate"]
-) {
-    var questions = []
-    for (const [index, element] of items.entries()) {
-        questions.push({
-            prompt: "<b>" + element + "</b>",
-            name: dimensions[index],
-            ticks: ticks,
-            required: false,
-            min: 0,
-            max: 1,
-            step: 0.01,
-            slider_start: 0.5,
-        })
-    }
-    return questions
-}
-
-// BAIT 2.0
-var questionnaire_bait = {
-    type: jsPsychMultipleSlider,
-    questions: format_questions_analog(
-        bait_items,
-        bait_dimensions,
-        // In Schepman et al. (2022) they removed 'Strongly'
-        (ticks = bait_ticks)
-    ),
-    randomize_question_order: true,
-    preamble: bait_instructions,
-    require_movement: false,
-    slider_width: 600,
-    data: {
-        screen: "questionnaire_bait",
-    },
-}
-
-// COPS ========================================================================
-// Consumption of Pornography Scale – General (COPS – G)
-// Hatchet al. (2023)
-var questionnaire_cops = {
-    type: jsPsychSurveyMultiChoice,
-    css_classes: ["narrow-text"],
-    preamble: cops_instructions,
-    questions: cops_items,
-    data: {
-        screen: "questionnaire_cops",
-    },
-}

### 2024-10-02 study1/stimuli_selection/stimuli_list.js

@@ -1,1 +1,0 @@
-var stimuli_list =  [{"stimulus":"Male_001_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_002_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_003_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_005_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_006_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_007_h.jpg","Category":"Male","Orientation":"h"},{"stimulus":"Male_008_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_009_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_011_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_012_h.jpg","Category":"Male","Orientation":"h"},{"stimulus":"Male_013_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_014_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_015_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_016_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_017_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_020_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_022_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_023_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_024_h.jpg","Category":"Male","Orientation":"h"},{"stimulus":"Male_025_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Female_001_h.jpg","Category":"Female","Orientation":"h"},{"stimulus":"Female_002_h.jpg","Category":"Female","Orientation":"h"},{"stimulus":"Female_003_v.jpg","Category":"Female","Orientation":"v"},{"stimulus":"Female_004_v.jpg","Category":"Female","Orientation":"v"},{"stimulus":"Female_005_v.jpg","Category":"Female","Orientation":"v"},{"stimulus":"Female_006_v.jpg","Category":"Female","Orientation":"v"},{"stimulus":"Female_008_v.jpg","Category":"Female","Orientation":"v"},{"stimulus":"Female_009_h.jpg","Catego
[…]

### 2024-10-02 study2/experiment/stimuli_selection/stimuli_list.js

@@ -1,0 +1,452 @@
+var stimuli_list = [
+    {
+        stimulus: "Opposite-sex_couple_001_v.jpg",
+        Category: "Opposite-sex Couple",
+        Orientation: "v",
+    },
+    {
+        stimulus: "Opposite-sex_couple_002_h.jpg",
+        Category: "Opposite-sex Couple",
+        Orientation: "h",
+    },
+    {
+        stimulus: "Opposite-sex_couple_003_v.jpg",
+        Category: "Opposite-sex Couple",
+        Orientation: "v",
+    },
+    {
+        stimulus: "Opposite-sex_couple_005_h.jpg",
+        Category: "Opposite-sex Couple",
+        Orientation: "h",
+    },
+    {
+        stimulus: "Opposite-sex_couple_007_h.jpg",
+        Category: "Opposite-sex Couple",
+        Orientation: "h",
+    },
+    {
+        stimulus: "Opposite-sex_couple_008_h.jpg",
+        Category: "Opposite-sex Couple",
+        Orientation: "h",
+    },
+    {
+        stimulus: "Opposite-sex_couple_009_h.jpg",
+        Category: "Opposite-sex Couple",
+        Orientation: "h",
+    },
+    {
+        stimulus: "Opposite-sex_couple_010_h.jpg",
+        Category: "Opposite-sex Couple",
+        Orientation: "h",
+    },
+    {
+        stimulus: "Opposite-sex_couple_011_h.jpg",
+        Category: "Opposite-sex Couple",
+        Orientation: "h",
+    },
+    {
+        stimulus: "Opposite-sex_couple_012_h.jpg",
+        Category: "Opposite-sex Couple",
+        Orientation: "h",
+    },
+    {
+        stimulus: "Opposite-sex_couple_013_h.jpg",
+        Category: "Opposite-sex Couple",
+        Orientation: "h",
+    },
+    {
+        stimulus: "Opposite-sex_couple_014_h.jpg",
+        Category: "Opposite-sex Couple",
+        Orientation: "h",
+    },
+    {
+        stimulus: "Opposite-sex_couple_015_h.jpg",
+        Category: "Opposite-sex Couple",
+        Orientation: "h",
+    },
+    {
+        stimulus: "Opposite-sex_couple_016_v.jpg",
+        Category: "Opposite-sex Couple",
+        Orientation: "v",
+    },
+    {
+        stimulus: "Opposite-sex_couple_017_v.jpg",
+        Category: "Opposite-sex Couple",
[…]

### 2024-10-02 study2/stimuli_selection2/stimuli_list2.js

@@ -1,1 +1,0 @@
-var stimuli_list2 =  [{"stimulus":"Male_001_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_002_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_003_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_005_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_006_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_007_h.jpg","Category":"Male","Orientation":"h"},{"stimulus":"Male_008_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_009_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_011_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_012_h.jpg","Category":"Male","Orientation":"h"},{"stimulus":"Male_013_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_014_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_015_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_016_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_017_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_020_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_022_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_023_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Male_024_h.jpg","Category":"Male","Orientation":"h"},{"stimulus":"Male_025_v.jpg","Category":"Male","Orientation":"v"},{"stimulus":"Female_001_h.jpg","Category":"Female","Orientation":"h"},{"stimulus":"Female_002_h.jpg","Category":"Female","Orientation":"h"},{"stimulus":"Female_003_v.jpg","Category":"Female","Orientation":"v"},{"stimulus":"Female_004_v.jpg","Category":"Female","Orientation":"v"},{"stimulus":"Female_005_v.jpg","Category":"Female","Orientation":"v"},{"stimulus":"Female_006_v.jpg","Category":"Female","Orientation":"v"},{"stimulus":"Female_008_v.jpg","Category":"Female","Orientation":"v"},{"stimulus":"Female_009_h.jpg","Cat
[…]

### 2024-10-03 study2/experiment/stimuli_selection/selection.qmd
stimuli 2

@@
 ---
-title: "Stimuli Selection"
+title: "Stimuli Selection "
 format:
@@
 ### Select based on norms
+
+In this study, we select only the 25 most arousing items that align with the participants' sexual orientation.
+For example, homosexual men will be shown the 25 most arousing images of males and male couples.
+While this approach reduces variability in arousal levels, it is more appropriate for our categorical analysis to focus exclusively on high-arousal stimuli.
+
+Additionally, insights from our previous study suggest that introducing neutral images between arousing ones diminishes participants' ability to maintain arousal, given that arousal tends to build over time.
+Images that evoke aversion can further disrupt arousal, undermining participants' ability to remain aroused immediately afterward.
+
 ```{r}
@@
 
-selection_erotic2 <- napsero2 |> 
-  filter(ID %in% selected_erotic_2)
+selection <- napsero |> 
+  filter(ID %in% selected_erotic)
 
-write.csv(selection_erotic2, "stimuli_data2.csv", row.names=FALSE)
-knitr::kable(selection_erotic2)
+write.csv(selection, "stimuli_data.csv", row.names=FALSE)
+knitr::kable(selection)
 ```
@@
 #| code-fold: true
-json <- selection2 |> 
+json <- selection |> 
   select(stimulus=ID, Category, Orientation) |> 
@@
 
-write(paste("var stimuli_list2 = ", json), "stimuli_list2.js")
+write(paste("var stimuli_list = ", json), "stimuli_list.js")
 ```
 
-```{r}
-#| code-fold: true
-path_ero <- "C:/Dropbox/RECHERCHE/docs/Stimuli/NAPS/NAPS_ERO/"
-path_naps <- "C:/Dropbox/RECHERCHE/docs/Stimuli/NAPS/NAPS/"
+<!-- ```{r} -->
+<!-- #| code-fold: true -->
+<!-- path_ero <- "C:/Dropbox/RECHERCHE/docs/Stimuli/NAPS/NAPS_ERO/" -->
+<!-- path_naps <- "C:/Dropbox/RECHERCHE/docs/Stimuli/NAPS/NAPS/" -->
 
-# Remove all current files
-unlink("../stimuli/*")
+<!-- # Remove all current files -->
+<!-- unlink("../stimuli/*") -->
 
-# Copy each file
-for(file in selected) {
-  if(str_detect(file, "Male|Female")) {
-    file.copy(paste0(path_ero, file), "../stimuli/")
-  } else {
-    file.copy(paste0(path_naps, file), "../stimuli/")
-  }
-}
-```
+<!-- # Copy each file -->
+<!-- for(file in selected) { -->
+<!--   if(str_detect(file, "Male|Female")) { -->
+<!--     file.copy(paste0(path_ero, file), "../stimuli/") -->
+<!--   } else { -->
+<!--     file.copy(paste0(path_naps, file), "../stimuli/") -->
+<!--   } -->
+<!-- } -->
+<!-- ``` -->

### 2024-10-03 study2/experiment/stimuli_selection/selection.qmd
Revert "stimuli 2"
This reverts commit a7dac3b662598a95344793d4146ca44d1df9cd63.

--- 2024-10-02 study2/experiment/stimuli_selection/selection.qmd
@@
 
-write(paste("var stimuli_list2 = ", json), "stimuli_list2.js")
+write(paste("var stimuli_list = ", json), "stimuli_list.js")
 ```

### 2024-10-03 study2/experiment/stimuli_selection/stimuli_list.js

@@ -1,1 +1,452 @@
-var stimuli_list =  [{"stimulus":"Opposite-sex_couple_001_v.jpg","Category":"Opposite-sex Couple","Orientation":"v"},{"stimulus":"Opposite-sex_couple_002_h.jpg","Category":"Opposite-sex Couple","Orientation":"h"},{"stimulus":"Opposite-sex_couple_003_v.jpg","Category":"Opposite-sex Couple","Orientation":"v"},{"stimulus":"Opposite-sex_couple_005_h.jpg","Category":"Opposite-sex Couple","Orientation":"h"},{"stimulus":"Opposite-sex_couple_007_h.jpg","Category":"Opposite-sex Couple","Orientation":"h"},{"stimulus":"Opposite-sex_couple_008_h.jpg","Category":"Opposite-sex Couple","Orientation":"h"},{"stimulus":"Opposite-sex_couple_009_h.jpg","Category":"Opposite-sex Couple","Orientation":"h"},{"stimulus":"Opposite-sex_couple_010_h.jpg","Category":"Opposite-sex Couple","Orientation":"h"},{"stimulus":"Opposite-sex_couple_011_h.jpg","Category":"Opposite-sex Couple","Orientation":"h"},{"stimulus":"Opposite-sex_couple_012_h.jpg","Category":"Opposite-sex Couple","Orientation":"h"},{"stimulus":"Opposite-sex_couple_013_h.jpg","Category":"Opposite-sex Couple","Orientation":"h"},{"stimulus":"Opposite-sex_couple_014_h.jpg","Category":"Opposite-sex Couple","Orientation":"h"},{"stimulus":"Opposite-sex_couple_015_h.jpg","Category":"Opposite-sex Couple","Orientation":"h"},{"stimulus":"Opposite-sex_couple_016_v.jpg","Category":"Opposite-sex Couple","Orientation":"v"},{"stimulus":"Opposite-sex_couple_017_v.jpg","Category":"Opposite-sex Couple","Orientation":"v"},{"stimulus":"Opposite-sex_couple_018_h.jpg","Category":"Opposite-sex Couple","Orientation":"h"},{"stimulus":"Opposite-sex_couple_019_v.jpg","Category":"Opposite-sex Couple","Orientation":"v"},{"stimulus":"Opposite-sex_couple_020_h.jpg","Category":"Opposite-sex Couple","Orientation":"h"},{"stimulus":"Opposite-sex_couple_022_v.jpg",
[…]

### 2024-10-03 study2/experiment/demographics.js
Study2 eperiment implementation
not finished

@@ -1,0 +1,341 @@
+// Full screen
+var fullscreen_text =
+    "<p>The experiment will switch to full screen mode when you press the button below</p>"
+var fullscreen_button = "Continue"
+
+var fullscreen_on = {
+    type: jsPsuchFullscreen,
+    message: fullscreen_text,
+    button_label: fullscreen_button,
+    fullscreen_mode: true,
+    delay_after: 0,
+}
+
+var fullscreen_off = {
+    type: jsPsuchFullscreen,
+    message: fullscreen_text,
+    button_label: fullscreen_button,
+    fullscreen_mode: false,
+}
+
+// Retrieve and save browser info ========================================================
+var demographics_browser_info = {
+    type: jsPsychBrowserCheck,
+    data: {
+        screen: "browser_info",
+        date: new Date().toLocaleDateString("fr-FR"),
+        time: new Date().toLocaleTimeString("fr-FR"),
+    },
+    on_finish: function (data) {
+        dat = jsPsych.data.get().filter({ screen: "browser_info" }).values()[0]
+
+        // Rename
+        data["screen_height"] = dat["height"]
+        data["screen_width"] = dat["width"]
+
+        // Add URL variables - ?sona_id=x&exp=1
+        let urlvars = jsPsych.data.urlVariables()
+        data["researcher"] = urlvars["exp"]
+        data["sona_id"] = urlvars["sona_id"]
+        data["prolific_id"] = urlvars["PROLIFIC_PID"] // Prolific
+        data["study_id"] = urlvars["STUDY_ID"] // Prolific
+        data["session_id"] = urlvars["SESSION_ID"] // Prolific
+    },
+}
+
+// Consent form ========================================================
+var demographics_consent = {
+    type: jsPsychHtmlButtonResponse,
+    css_classes: ["narrow-text"],
+    stimulus: function () {
+        // Logo and title
+        let text =
+            "<img src='https://blogs.brighton.ac.uk/sussexwrites/files/2019/06/University-of-Sussex-logo-transparent.png' width='150px' align='right'/><br><br><br><br><br>" +
+            "<h1>Informed Consent</h1>"
+
+        if (jsPsych.data.urlVariables()["exp"] == "surveyswap") {
+            text +=
+                "<p style='color:green;' align='left'><b>Note: You will receive a <i style='color:purple;'>SurveySwap.io</i> completion code at the end of the experiment.</b></p>"
+        }
+
+        // Consent Form
+        text +=
[…]

### 2024-10-03 study2/experiment/eye_tracking.js

@@ -1,0 +1,171 @@
+var eyetracking_consent = {
+    type: jsPsychHtmlButtonResponse,
+    stimulus:
+        "<h2>Eye movements</h2>" +
+        "<p>As the next phase of the experiment involves the presentation of visual stimuli, we are interested in what parts of the image people look at, and we would like to use your webcam to record your gaze.</p>" +
+        "<p><b style='color: red'>Important: The experiment does <i>not</i> record your face or any images from the camera.</b> It only extracts the estimated gaze pattern on the screen. <b>Your participation remains completely anonymous</b>.</p>" +
+        "<img src='media/eyetracker.gif' height='300' align='center'></img>" +
+        "<p>After you pressed <b>'I agree'</b>, a pop-up will appear asking you to enable your webcam. It may take a couple of seconds for the camera to initialize.</p>",
+    choices: ["I agree", "I don't have a webcam"],
+    data: {
+        screen: "eyetracking_consent",
+    },
+}
+
+// Calibration ====================================================================
+const calibration_points = [
+    [20, 20],
+    [50, 20],
+    [80, 20],
+    [20, 50],
+    [50, 50],
+    [50, 50],
+    [80, 50],
+    [20, 80],
+    [50, 80],
+    [80, 80],
+]
+
+var eyetracking_webcam = {
+    type: jsPsychWebgazerInitCamera,
+    instructions:
+        "<h2>Setup</h2>" +
+        "<p style='text-align: left;'><b>1.</b> Make sure you are in a well-lit room, that your face is well lit, and clean your glasses if need be.</p>" +
+        "<p style='text-align: left;'><b>2.</b> Center your face in the box.</p>" +
+        "<p style='text-align: left;'><b>3.</b> Make sure you are seated comfortably, as it is important that you keep this head position throughout the experiment.</p>" +
+        "<p style='text-align: left;'><b>4.</b> When your face is centered in the box and the box is green, you can click to continue.</p>",
+}
+
+var eyetracking_calibration_instructions = {
+    type: jsPsychHtmlButtonResponse,
+    stimulus:
+        "<h2>Gaze Calibration (1/2)</h2>" +
+        "<p>You will now see a series of <b>black dots</b> appear on the screen. Look at each dot and <b>click on it</b> without moving your head too much.</p>",
+    choices: ["Ready"],
+    data: {
+        screen: "eyetracking_calibration_instructions",
+    },
+}
+
+var eyetracking_calibration_run = {
+    type: jsPsychWebgazerCalibrate,
[…]

### 2024-10-03 study2/experiment/fiction.js

@@ -1,0 +1,512 @@
+// Condition assignment ============================================
+function shuffleArray(array) {
+    for (let i = array.length - 1; i > 0; i--) {
+        const j = Math.floor(Math.random() * (i + 1))
+        ;[array[i], array[j]] = [array[j], array[i]]
+    }
+    return array
+}
+
+function assignCondition(stimuli) {
+    new_stimuli_list = []
+    // Loop through unique categories
+    for (let cat of [...new Set(stimuli.map((a) => a.Category))]) {
+        // Get all stimuli of this category
+        var cat_stimuli = stimuli.filter((a) => a.Category == cat)
+
+        // Shuffle cat_stimuli
+        cat_stimuli = shuffleArray(cat_stimuli) // Custom funciton defined above
+
+        // Assign half to "Reality" condition and half to "Fiction" condition
+        for (let i = 0; i < cat_stimuli.length; i++) {
+            cat_stimuli[i].Condition =
+                i < cat_stimuli.length / 2 ? "Reality" : "Fiction"
+        }
+
+        // Add to new_stimuli_list
+        new_stimuli_list.push(...cat_stimuli)
+    }
+    return shuffleArray(new_stimuli_list)
+}
+
+// Variables ===================================================================
+var fiction_trialnumber = 1
+var color_cues = shuffleArray(["red", "blue", "green"])
+color_cues = { Reality: color_cues[0], Fiction: color_cues[1] }
+var text_cue = { Reality: "Photograph", Fiction: "AI-generated" }
+stimuli = assignCondition(stimuli)
+
+// Screens =====================================================================
+var fiction_instructions1 = {
+    type: jsPsychHtmlButtonResponse,
+    css_classes: ["narrow-text"],
+    stimulus:
+        "<h1>Part 3/4</h1>" +
+        "<div style='text-align: left'>" +
+        "<p>This study stems out of an exciting new partnership between researchers from the <b>University of Sussex</b> and a young <b>AI startup</b> based in Brighton, UK, that specializes in making AI technology more ethical.</p>" +
+        "<p>Our goal is to better understand how various people react to different faces. For this, we will be using a new <b>image-generation algorithm</b> (based on a modified <i>Generative Adversarial Network</i>) trained on a carefully refined material to produce realistic high-quality images. " +
+        "This allows us to manipulate the generation parameters and understand how they impact face perception.</p>" +
+        "<div style='text-align: center;'><img src='media/gan.gif' height='200'></img></div>" +
[…]

### 2024-10-21 study2/experiment/stimuli_selection/selection.qmd
changes made to scripts

@@
 
-selected_erotic <- c(men, women, homo_men,homo_women)
+selected<- c(men, women, homo_men,homo_women)
 
@@
 #| code-fold: true
-path_ero <- "C:/Dropbox/RECHERCHE/docs/Stimuli/NAPS/NAPS_ERO/"
-path_naps <- "C:/Dropbox/RECHERCHE/docs/Stimuli/NAPS/NAPS/"
+path_ero <- "C:/Users/asf25/OneDrive - University of Sussex/phd/data_base/naps/NAPS_ERO/"
 
@@
 unlink("../stimuli/*")
+# 
+# Copy each file
+for (file in selected) {
+  file.copy(paste0(path_ero, file), "../stimuli/")
+}
 
-# Copy each file
-for(file in selected) {
-  if(str_detect(file, "Male|Female")) {
-    file.copy(paste0(path_ero, file), "../stimuli/")
-  } else {
-    file.copy(paste0(path_naps, file), "../stimuli/")
-  }
-}
 ```

### 2024-10-21 study2/experiment/demographics.js

@@ -4,7 +4,7 @@ var fullscreen_text =
 var fullscreen_button = "Continue"
 
 var fullscreen_on = {
-    type: jsPsuchFullscreen,
+    type: jsPsychFullscreen,
     message: fullscreen_text,
     button_label: fullscreen_button,
     fullscreen_mode: true,
@@ -12,7 +12,7 @@ var fullscreen_on = {
 }
 
 var fullscreen_off = {
-    type: jsPsuchFullscreen,
+    type: jsPsychFullscreen,
     message: fullscreen_text,
     button_label: fullscreen_button,
     fullscreen_mode: false,

### 2024-10-21 study2/experiment/fiction.js

@@ -7,12 +7,12 @@ function shuffleArray(array) {
     return array
 }
 
-function assignCondition(stimuli) {
+function assignCondition(stimuli_list) {
     new_stimuli_list = []
     // Loop through unique categories
-    for (let cat of [...new Set(stimuli.map((a) => a.Category))]) {
+    for (let cat of [...new Set(stimuli_list.map((a) => a.Category))]) {
         // Get all stimuli of this category
-        var cat_stimuli = stimuli.filter((a) => a.Category == cat)
+        var cat_stimuli = stimuli_list.filter((a) => a.Category == cat)
 
         // Shuffle cat_stimuli
         cat_stimuli = shuffleArray(cat_stimuli) // Custom funciton defined above
@@ -34,24 +34,23 @@ var fiction_trialnumber = 1
 var color_cues = shuffleArray(["red", "blue", "green"])
 color_cues = { Reality: color_cues[0], Fiction: color_cues[1] }
 var text_cue = { Reality: "Photograph", Fiction: "AI-generated" }
-stimuli = assignCondition(stimuli)
+stimuli_list = assignCondition(stimuli_list)
 
 // Screens =====================================================================
 var fiction_instructions1 = {
     type: jsPsychHtmlButtonResponse,
     css_classes: ["narrow-text"],
     stimulus:
-        "<h1>Part 3/4</h1>" +
-        "<div style='text-align: left'>" +
         "<p>This study stems out of an exciting new partnership between researchers from the <b>University of Sussex</b> and a young <b>AI startup</b> based in Brighton, UK, that specializes in making AI technology more ethical.</p>" +
-        "<p>Our goal is to better understand how various people react to different faces. For this, we will be using a new <b>image-generation algorithm</b> (based on a modified <i>Generative Adversarial Network</i>) trained on a carefully refined material to produce realistic high-quality images. " +
+        "<p>Our goal is to better understand how various people react to different images. For this, we will be using a new <b>image-generation algorithm</b> (based on a modified <i>Generative Adversarial Network</i>) trained on a carefully refined material to produce realistic high-quality images. " +
         "This allows us to manipulate the generation parameters and understand how they impact face perception.</p>" +
         "<div style='text-align: center;'><img src='media/gan.gif' height='200'></img></div>" +
-        "<p>In the next part, you will be presented with faces generated by our algorithm (preceded by the word '<b style='color:" +
[…]

### 2024-10-21 study2/experiment/questionnaires.js

@@ -1,0 +1,173 @@
+// Questionnaires
+var questionnaires_instructions0 = {
+    type: jsPsychHtmlButtonResponse,
+    stimulus:
+        "<p>We will continue with a series of questionnaires about your personality.<br>It is important that you answer truthfully. Please read the statements carefully and answer according to what describe you the best.</p>",
+    choices: ["Continue"],
+    data: { screen: "part2_instructions" },
+}
+
+// Questionnaires =================================================
+
+/* Attitudes towards AI *==========================*/
+// Beliefs about Artificial Images Technology (BAIT)
+// History:
+// - BAIT-Original: Items specifically about CGI and artificial media originally in Makowski et al. (FakeFace study)
+// - BAIT-14: Validated in FictionEro (with new items + removal of "I think"), where it was mixed with the 6 most
+//   loading items of the positive and negative attitutes dimensions from the General Attitudes towards
+//   Artificial Intelligence Scale (GAAIS; Schepman et al., 2020, 2022)
+// - BAIT-14: Used in FakeNewsValidation
+// - BAIT-12 (Current version): Used in FakeFace2.
+//   - Removed 2 GAAIS items (GAAIS_Negative_9, GAAIS_Positive_7)
+//   - Replaced "Artificial Intelligence" with "AI
+//   - Change display (Analog scale -> Likert scale)
+
+const bait_items = [
+    // BAIT items
+    "Current AI algorithms can generate very realistic images",
+    "Images of faces or people generated by AI always contain errors and artifacts",
+    "Videos generated by AI have obvious problems that make them easy to spot as fake",
+    "Current AI algorithms can generate very realistic videos",
+    "Computer-Generated Images (CGI) are capable of perfectly imitating reality",
+    "Technology allows the creation of environments that seem just as real as reality",
+    "AI assistants can write texts that are indistinguishable from those written by humans",
+    "Documents and paragraphs written by AI usually read differently compared to Human productions",
+
+    // Expectations
+    // "Current AI algorithms can already create content that is indistinguishable from reality",
+
+    // Discrimination skills
+    // "I can easily distinguish between real and AI-generated images",
+    // "I can easily distinguish between real and AI-generated text",
+
+    // Attitutes (adapted from GAAIS; Schepman et al., 2023)
[…]

### 2024-10-21 study2/experiment/stimuli_selection/stimuli_list.js

@@ -1,452 +1,1 @@
-var stimuli_list = [
-    {
-        stimulus: "Opposite-sex_couple_001_v.jpg",
-        Category: "Opposite-sex Couple",
-        Orientation: "v",
-    },
-    {
-        stimulus: "Opposite-sex_couple_002_h.jpg",
-        Category: "Opposite-sex Couple",
-        Orientation: "h",
-    },
-    {
-        stimulus: "Opposite-sex_couple_003_v.jpg",
-        Category: "Opposite-sex Couple",
-        Orientation: "v",
-    },
-    {
-        stimulus: "Opposite-sex_couple_005_h.jpg",
-        Category: "Opposite-sex Couple",
-        Orientation: "h",
-    },
-    {
-        stimulus: "Opposite-sex_couple_007_h.jpg",
-        Category: "Opposite-sex Couple",
-        Orientation: "h",
-    },
-    {
-        stimulus: "Opposite-sex_couple_008_h.jpg",
-        Category: "Opposite-sex Couple",
-        Orientation: "h",
-    },
-    {
-        stimulus: "Opposite-sex_couple_009_h.jpg",
-        Category: "Opposite-sex Couple",
-        Orientation: "h",
-    },
-    {
-        stimulus: "Opposite-sex_couple_010_h.jpg",
-        Category: "Opposite-sex Couple",
-        Orientation: "h",
-    },
-    {
-        stimulus: "Opposite-sex_couple_011_h.jpg",
-        Category: "Opposite-sex Couple",
-        Orientation: "h",
-    },
-    {
-        stimulus: "Opposite-sex_couple_012_h.jpg",
-        Category: "Opposite-sex Couple",
-        Orientation: "h",
-    },
-    {
-        stimulus: "Opposite-sex_couple_013_h.jpg",
-        Category: "Opposite-sex Couple",
-        Orientation: "h",
-    },
-    {
-        stimulus: "Opposite-sex_couple_014_h.jpg",
-        Category: "Opposite-sex Couple",
-        Orientation: "h",
-    },
-    {
-        stimulus: "Opposite-sex_couple_015_h.jpg",
-        Category: "Opposite-sex Couple",
-        Orientation: "h",
-    },
-    {
-        stimulus: "Opposite-sex_couple_016_v.jpg",
-        Category: "Opposite-sex Couple",
-        Orientation: "v",
-    },
-    {
-        stimulus: "Opposite-sex_couple_017_v.jpg",
-        Category: "Opposite-sex Couple",
[…]

### 2024-12-09 study1/analysis/2_emotions.qmd
push
formatting

--- 2024-06-27 analysis/2_emotions.qmd
@@
 
-This section is about selecting the best model and making a **manipulation check** to make sure that the emotional appraisal were sensitive to the main manipualtion (Neutral vs. Emotional).
+This section is about selecting the best model and making a **manipulation check** to make sure that the emotional appraisal were sensitive to the main manipulation (Neutral vs. Emotional).
 
@@
 ### Believed
+
+<!-- Effect becomes larger, more significant and goes in both directions for both genders -->
 

### 2024-12-09 study2/experiment/fiction.js

@@ -21,11 +21,7 @@ function assignCondition(stimuli_list) {
 
     // Define the stimuli categories based on Gender and Sexuality
     let stimuliCategory = []
-    if (
-        sexuality === "Heterosexual" ||
-        sexuality === "Bisexual" ||
-        sexuality === "Other"
-    ) {
+    if (sexuality === "Heterosexual" || sexuality === "Bisexual" || sexuality === "Other") {
         if (gender === "Male" || gender === "Other") {
             stimuliCategory = ["Female", "Opposite-sex Couple"]
         } else if (gender === "Female") {
@@ -52,14 +48,11 @@ function assignCondition(stimuli_list) {
 
         // Assign half to "Reality" condition and half to "Fiction" condition
         for (let i = 0; i < cat_stimuli.length; i++) {
-            cat_stimuli[i].Condition =
-                i < cat_stimuli.length / 2 ? "Reality" : "Fiction"
+            cat_stimuli[i].Condition = i < cat_stimuli.length / 2 ? "Reality" : "Fiction"
         }
 
         // Filter cat_stimuli based on the determined stimuli categories
-        cat_stimuli = cat_stimuli.filter((stimulus) =>
-            stimuliCategory.includes(stimulus.Category)
-        )
+        cat_stimuli = cat_stimuli.filter((stimulus) => stimuliCategory.includes(stimulus.Category))
 
         // Add to new_stimuli_list
         new_stimuli_list.push(...cat_stimuli)
@@ -127,8 +120,7 @@ var fiction_instructions2 = {
 
 var fiction_preloadstims = {
     type: jsPsychPreload,
-    message:
-        "Please wait while the experiment is being loaded (it can take a few seconds)",
+    message: "Please wait while the experiment is being loaded (it can take a few seconds)",
     images: stimuli_list.map((a) => "stimuli/" + a.stimulus),
     on_load: function () {
         stimuli = assignCondition(stimuli_list)
@@ -251,9 +243,7 @@ var fiction_ratings1 = {
         showNavigationButtons: false,
         title: function () {
             return (
-                "Rating - " +
-                Math.round(((fiction_trialnumber - 1) / stimuli.length) * 100) +
-                "%"
+                "Rating - " + Math.round(((fiction_trialnumber - 1) / stimuli.length) * 100) + "%"
             )
         },
         description: "Think of the person that you just saw.",
[…]

### 2024-12-09 study2/experiment/fiction.js
update to JsPsych 8
@AnafNeves

@@ -140,7 +140,7 @@ var fiction_fixation1a = {
     data: function () {
         return {
             screen: "fiction_fixation1a",
-            item: jsPsych.timelineVariable("stimulus"),
+            item: jsPsych.evaluateTimelineVariable("stimulus"),
         }
     },
 }
@@ -148,7 +148,7 @@ var fiction_fixation1a = {
 var fiction_cue = {
     type: jsPsychHtmlKeyboardResponse,
     stimulus: function () {
-        var cond = jsPsych.timelineVariable("Condition")
+        var cond = jsPsych.evaluateTimelineVariable("Condition")
         return (
             "<div style='font-size:450%; position:fixed; text-align: center; top:50%; bottom:50%; right:20%; left:20%; color: " +
             color_cues[cond] +
@@ -158,12 +158,12 @@ var fiction_cue = {
         )
     },
     data: function () {
-        var cond = jsPsych.timelineVariable("Condition")
+        var cond = jsPsych.evaluateTimelineVariable("Condition")
         return {
             screen: "fiction_cue",
             color: color_cues[cond],
             condition: cond,
-            item: jsPsych.timelineVariable("stimulus"),
+            item: jsPsych.evaluateTimelineVariable("stimulus"),
         }
     },
     choices: ["s"],
@@ -181,7 +181,7 @@ var fiction_fixation1b = {
     data: function () {
         return {
             screen: "fiction_fixation1b",
-            item: jsPsych.timelineVariable("stimulus"),
+            item: jsPsych.evaluateTimelineVariable("stimulus"),
         }
     },
     extensions: [
@@ -195,7 +195,7 @@ var fiction_fixation1b = {
 var fiction_showimage1 = {
     type: jsPsychImageKeyboardResponse,
     stimulus: function () {
-        return "stimuli/" + jsPsych.timelineVariable("stimulus")
+        return "stimuli/" + jsPsych.evaluateTimelineVariable("stimulus")
     },
     stimulus_height: function () {
         if (window.innerHeight < window.innerWidth) {
@@ -361,7 +361,7 @@ var fiction_fixation2 = {
 var fiction_showimage2 = {
     type: jsPsychImageKeyboardResponse,
     stimulus: function () {
-        return "stimuli/" + jsPsych.timelineVariable("stimulus")
+        return "stimuli/" + jsPsych.evaluateTimelineVariable("stimulus")
     },
     stimulus_height: function () {
         if (window.innerHeight < window.innerWidth) {

### 2025-01-27 study2/experiment/stimuli_selection/selection.qmd
updated stimuli selection
now only 25 images of opposite-sex couples (rather than 30)

@@
 
-write.csv(selection, "stimuli_data.csv", row.names=FALSE)
+# Sum the arousal scores 
+selection <- selection |>
+  mutate(total_arousal = selection$Hetero_Men_Arousal + selection$Hetero_Women_Arousal,
+         total_valence = selection$Hetero_Men_Valence + selection$Hetero_Women_Valence)
+
+# arrange by the 25 highest scores of arousal and calculate the lowest arousal score
+selection |>
+  filter(Category == "Opposite-sex Couple") |>
+  arrange(desc(total_arousal)) |>
+  head(25) |>
+  summarize(min_arousal = min(total_arousal)) # 8.8
+
+#check how many images have a score of 8.8 and the ID of the one with the lowest valance
+remove_image <- selection |> 
+  filter(total_arousal == 8.8) |> # 3 
+  filter(total_valence == min(total_valence)) |> 
+  select(ID)
+
+# last selection 
+last_selection <- selection |>
+  filter(!(Category == "Opposite-sex Couple" & total_arousal < 8.8)) |>
+  filter(!(ID %in% remove_image))
+
+write.csv(last_selection, "stimuli_data.csv", row.names=FALSE)
 knitr::kable(selection)
@@
 #| code-fold: true
-json <- selection |> 
+json <- last_selection |> 
   select(stimulus=ID, Category, Orientation) |> 

### 2025-01-27 study2/experiment/stimuli_selection/stimuli_list.js

@@ -1,1 +1,1 @@
-var stimuli_list =  [{"stimulus":"Opposite-sex_couple_001_v.jpg","Category":"Opposite-sex Couple","Orientation":"v"},{"stimulus":"Opposite-sex_couple_002_h.jpg","Category":"Opposite-sex Couple","Orientation":"h"},{"stimulus":"Opposite-sex_couple_003_v.jpg","Category":"Opposite-sex Couple","Orientation":"v"},{"stimulus":"Opposite-sex_couple_005_h.jpg","Category":"Opposite-sex Couple","Orientation":"h"},{"stimulus":"Opposite-sex_couple_007_h.jpg","Category":"Opposite-sex Couple","Orientation":"h"},{"stimulus":"Opposite-sex_couple_008_h.jpg","Category":"Opposite-sex Couple","Orientation":"h"},{"stimulus":"Opposite-sex_couple_009_h.jpg","Category":"Opposite-sex Couple","Orientation":"h"},{"stimulus":"Opposite-sex_couple_010_h.jpg","Category":"Opposite-sex Couple","Orientation":"h"},{"stimulus":"Opposite-sex_couple_011_h.jpg","Category":"Opposite-sex Couple","Orientation":"h"},{"stimulus":"Opposite-sex_couple_012_h.jpg","Category":"Opposite-sex Couple","Orientation":"h"},{"stimulus":"Opposite-sex_couple_013_h.jpg","Category":"Opposite-sex Couple","Orientation":"h"},{"stimulus":"Opposite-sex_couple_014_h.jpg","Category":"Opposite-sex Couple","Orientation":"h"},{"stimulus":"Opposite-sex_couple_015_h.jpg","Category":"Opposite-sex Couple","Orientation":"h"},{"stimulus":"Opposite-sex_couple_016_v.jpg","Category":"Opposite-sex Couple","Orientation":"v"},{"stimulus":"Opposite-sex_couple_017_v.jpg","Category":"Opposite-sex Couple","Orientation":"v"},{"stimulus":"Opposite-sex_couple_018_h.jpg","Category":"Opposite-sex Couple","Orientation":"h"},{"stimulus":"Opposite-sex_couple_019_v.jpg","Category":"Opposite-sex Couple","Orientation":"v"},{"stimulus":"Opposite-sex_couple_020_h.jpg","Category":"Opposite-sex Couple","Orientation":"h"},{"stimulus":"Opposite-sex_couple_022_v.jpg","
[…]

### 2025-01-27 study2/experiment/stimuli_selection/selection.qmd
Update selection.qmd

@@
 # last selection 
-last_selection <- selection |>
+selection <- selection |>
   filter(!(Category == "Opposite-sex Couple" & total_arousal < 8.8)) |>
@@
 
-write.csv(last_selection, "stimuli_data.csv", row.names=FALSE)
+write.csv(selection, "stimuli_data.csv", row.names=FALSE)
 knitr::kable(selection)
@@
 #| code-fold: true
-json <- last_selection |> 
+json <- selection |> 
   select(stimulus=ID, Category, Orientation) |> 
@@
 #| code-fold: true
-path_ero <- "C:/Users/asf25/OneDrive - University of Sussex/phd/data_base/naps/NAPS_ERO/"
+path_ero <- "C:/Users/asf25/Desktop/PhD/data_base/NAPS_ERO/"
 

### 2025-02-19 study2/analysis/1_cleaning.qmd
started cleaning file

---
title: "FictionEro-2 - Data Cleaning"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
---

### 2025-02-19 study2/analysis/0_preprocessing.py

@@ -388,7 +388,7 @@ data_demo = replace_value(data_demo, "Discipline", "Other_Marketing and Research
 data_demo = replace_value(data_demo, "Discipline", "Other_Information Technology", "Other")
 data_demo = replace_value(data_demo, "Discipline", "Other_Finance", "Business, Economics")
 data_demo = replace_value(data_demo, "Discipline", "Other_Data analyst", "Engineering, Computer Science")
-
+data_demo = replace_value(data_demo, "Discipline", "Other_Human Genetics", "Other")
 
 # data_demo["SexualOrientation"][data_demo["SexualOrientation"].str.contains("Other_").values].values
 data_demo = replace_value(data_demo, "SexualOrientation", "Other_Straight", "Heterosexual")
@@ -402,10 +402,12 @@ data_demo = replace_value(data_demo, "SexualStatus", "Other_Married", "In a rela
 # data_demo["Country"][data_demo["Country"].str.contains("Other_").values].values
 
 # data_demo["Education"][data_demo["Education"].str.contains("Other_").values].values
-# data_demo[data_demo["Education"].str.contains("Other_")]["Country"] --> south africa college?
+# data_demo[data_demo["Education"].str.contains("Other_")]["Country"] //--> south africa college?
 data_demo = replace_value(data_demo, "Education", "Other_College", "Other")
 data_demo = replace_value(data_demo, "Education", "Other_some college, short courses(not diploma nor degree)", "High school")
 data_demo = replace_value(data_demo, "Education", "Other_COLLEGE", "Other")
+data_demo = replace_value(data_demo, "Education", "Other_College.", "Other")
+data_demo = replace_value(data_demo, "Education", "Other_College (diploma)", "Other")
 
 # Compute the correlation for each participant for arousal and valence 
 correlations = {}

### 2025-02-19 study2/analysis/1_cleaning.qmd
minor

@@
 ---
+
+## Data Preparation
+
+```{r}
+#| message: false
+#| warning: false
+
+library(tidyverse)
+library(easystats)
+library(patchwork)
+library(ggside)
+library(ggdist)
+
+```
+
+```{r}
+#| code-fold: false
+
+df <- read.csv("../data/rawdata_participants.csv")
+
+dftask <- read.csv("../data/rawdata_task.csv") |>
+  full_join(
+    df[c("Participant", "Gender", "SexualOrientation")], # add Gneder and sexual orientation to this dataset
+    by = join_by(Participant)
+    )
+```
+
+The initial sample consisted of `r report::report_participants(df, age="Age", sex="Sex", education="Education")`.
+
+## Feedback
+
+### Evaluation
+
+::: {.panel-tabset}
+
+### Experiment Enjoyment
+
+```{r}
+df |> 
+  summarise(n = n(), .by=c("Feedback_Enjoyment")) |>
+  filter(!is.na(Feedback_Enjoyment)) |> 
+  mutate(n = n / sum(n),
+         Feedback_Enjoyment = fct_rev(as.factor(Feedback_Enjoyment))) |>
+  ggplot(aes(y = n, x = 1, fill = Feedback_Enjoyment)) +
+  geom_bar(stat="identity", position="stack") +
+  scale_fill_manual(values=c("darkgreen", "yellowgreen",  "yellow", "orange", "red")) +
+  coord_flip() +
+  scale_x_continuous(expand=c(0, 0))  +
+  scale_y_continuous(labels = scales::percent)  +
+  labs(title="Experiment Enjoyment",
+       subtitle="Proportion of participants by condition") + 
+  guides(fill = guide_legend(reverse=TRUE)) +
+  theme_minimal() +
+  theme(
+    axis.title = element_blank(),
+    axis.text.y = element_blank(),
+    panel.grid.major.y = element_blank(),
+    panel.grid.minor.y = element_blank(),
+    legend.position = "top",
+    legend.title = element_blank()) 
+```
+
+### Comments
+
+<!-- eventually create table with selected comments -->
+
+```{r}
+
+data.frame(Comments = df$Feedback_Text) |>
+  filter(!tolower(Comments) %in% c(NA, "no", "no comments", "nothing", "none", "")) |> 
+  gt::gt() |> 
+  gt::opt_stylize() |> 
+  gt::opt_interactive(use_compact_mode = TRUE)
+
+```
+
+## Exclusion
+
+```{r}
+#| echo: true
+#| code-fold: false
+
+outliers <- list()
+```
+
+### Experiment Duration
+
+The experiment's median duration is `r insight::format_value(median(df$Experiment_Duration))` min (`r insight::format_ci(bayestestR::hdi(df$Experiment_Duration, ci=0.5))`).
+
+```{r}
+df |>
+  mutate(Participant = fct_reorder(Participant, Experiment_Duration),
+         Category = ifelse(Experiment_Duration > 60, "extra", "ok"),
+         Duration = ifelse(Experiment_Duration > 60, 60, Experiment_Duration),
+         Group = ifelse(Participant %in% outliers, "Outlier", "ok")) |>
+  ggplot(aes(y = Participant, x = Duration)) +
+  geom_point(aes(color = Group, shape = Category)) +
+  geom_vline(xintercept = median(df$Experiment_Duration), color = "red", linetype = "dashed") +
+  geom_vline(xintercept = 15, color = "orange", linetype = "dotted") +
+  scale_shape_manual(values = c("extra" = 3, ok = 20)) +
+  scale_color_manual(values = c("Outlier" = "red", ok = "black"), guide="none") +
+  guides(color = "none", shape = "none") +
+  ggside::geom_xsidedensity(fill = "#4CAF50", color=NA) +
+  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
+  labs(
+    title = "Experiment Completion Time",
+    x = "Duration (in minutes)",
+    y = "Participants"
+  )  +
+  theme_modern() +
+  ggside::theme_ggside_void() +
+  theme(ggside.panel.scale = .3,
+        panel.border = element_blank(),
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank())
+
+```
+### BAIT Questionnaire Duration
+
+```{r}
+#| fig-width: 15
+#| fig-height: 15
+
+df |>
+  mutate(Participant = fct_reorder(Participant, Bait_Duration),
+         Category = ifelse(Bait_Duration > 5, "extra", "ok"),
+         Duration = ifelse(Bait_Duration > 5, 5, Bait_Duration),
+         Group = ifelse(Participant %in% outliers, "Outlier", "ok")) |>
+  ggplot(aes(y = Participant, x = Duration)) +
+  geom_point(aes(color = Group, shape = Category)) +
+  geom_vline(xintercept = median(df$Bait_Duration), color = "red", linetype = "dashed") +
+  geom_vline(xintercept = 0.5, color = "orange", linetype = "dotted") +
+  scale_shape_manual(values = c("extra" = 3, ok = 19)) +
+  scale_color_manual(values = c("Outlier" = "red", ok = "black"), guide="none") +
+  guides(color = "none", shape = "none") +
+  ggside::geom_xsidedensity(fill = "#9C27B0", color=NA) +
+  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
+  labs(
+    title = "Questionnaire Completion Time",
+    x = "Duration (in minutes)",
+    y = "Participant"
+  )  +
+  theme_modern() +
+  ggside::theme_ggside_void() +
+  theme(ggside.panel.scale = .3,
+        panel.border = element_blank(),
+        axis.ticks.y = element_blank(),
+          axis.text.y = element_blank())
+
+# min(df$Bait_Duration) 0.8084833
+# max(df$Bait_Duration) 20.37072
+```
+
+### Response to Erotic Stimuli
+
+```{r}
+# Single arousal response (0)
+outliers$novariability <- summarize(dftask, n = length(unique(Arousal)), .by="Participant") |> 
+  filter(n == 1) |> 
+  select(Participant) |> 
+  pull()
+```
+### Response Coherence
+
+```{r}
+dat <- dftask |> 
+  filter(!Participant %in% outliers) |> 
+  summarize(cor_ArVal = cor(Arousal, Valence),
+            cor_ArEnt = cor(Arousal, Enticing),
+            .by="Participant")
+
+dat |>
+  mutate(Participant = fct_reorder(Participant, cor_ArVal)) |>
+  pivot_longer(starts_with("cor_")) |>
+  mutate(Group = ifelse(Participant %in% outliers, "Outlier", "ok")) |> 
+  mutate(name = fct_relevel(name, "cor_ArVal", "cor_ArEnt"),
+         name = fct_recode(name, "Arousal - Valence" = "cor_ArVal", "Arousal - Enticement" = "cor_ArEnt")) |>
+  ggplot(aes(y = Participant, x = value)) +
+  geom_bar(stat =  "identity") +
+  # scale_fill_gradient2(low = "#3F51B5", mid = "#FF9800", high = "#4CAF50", midpoint = 0) +
+  # scale_fill_manual(values = c("Outlier" = "red", ok = "black"), guide="none") +
+  theme_bw() +
+  theme(axis.text.y = element_blank(),
+        axis.ticks.y = element_blank()) +
+  facet_wrap(~name, ncol=3, scales="free_x")
+
+outliers$emo_cor <- sort(as.character(dat[dat$cor_ArEnt < 0, ]$Participant))
+outliers$emo_aro <- sort(as.character(dat[dat$cor_ArVal < 0, ]$Participant))
+
+outliers$arousal <- intersect(outliers$emo_aro, outliers$emo_cor)
+
+```
+`r length(outliers$arousal)` participant has a negative correlation between arousal and enticement, and has a negative correlation between arousal and valance.
+
+```{r}
+# df <- filter(df, !Participant %in% outliers$arousal)
+# dftask <- filter(dftask, !Participant %in% outliers$arousal)
+```
+
+### Sexual Profile
+
+```{r}
+df |>
+  ggplot(aes(x = Gender)) +
+  geom_bar(aes(fill = SexualOrientation)) +
+  scale_y_continuous(expand = c(0, 0), breaks = scales::pretty_breaks()) +
+  labs(x = "Biological Sex", y = "Number of Participants", title = "Sex and Sexual Orientation", fill = "Sexual Orientation") +
+  theme_modern(axis.title.space = 15) +
+  theme(
+    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
+    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
+    axis.text.y = element_text(size = rel(1.1)),
+    axis.text.x = element_text(size = rel(1.1)),
+    axis.title.x = element_blank()
+  )
+```
+
+#### Stimuli Choice
+
+```{r}
+
+df |>
+
+```

### 2025-02-20 study2/analysis/1_cleaning.qmd
changes to cleaning script

@@
 ```
-`r length(outliers$arousal)` participant has a negative correlation between arousal and enticement, and has a negative correlation between arousal and valance.
+
+`r length(outliers$arousal)` participant had a negative correlation between arousal and enticement, and had a negative correlation between arousal and valance.
+
+**NOTE**: Remove?
 
@@
 
-### Sexual Profile
+## Final Sample
+
+::: {.panel-tabset}
+
+### Summary
+
+The final sample includes `r report::report_participants(df, age="Age", sex="Sex", education="Education")`.
+
+### Age and Gender
+
+```{r}
+p_age <- df |>
+  ggplot(aes(x = Age, fill = Gender)) + 
+  geom_histogram(data=df, aes(x = Age, fill=Gender), binwidth = 2) +
+  geom_vline(xintercept = mean(df$Age), color = "red", linewidth=1.5, linetype="dashed") +
+  scale_fill_viridis_d() +
+  scale_x_continuous(expand = c(0, 0), breaks = seq(10, max(df$Age), by = 10)) +
+  scale_y_continuous(expand = c(0, 0)) +
+  labs(title = "Age", y = "Number of Participants", color = NULL, subtitle = "Distribution of participants' age") +
+  theme_modern(axis.title.space = 10) +
+  theme(
+    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
+    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
+    axis.text.y = element_text(size = rel(1.1)),
+    axis.text.x = element_text(size = rel(1.1)),
+    axis.title.x = element_blank()
+  )
+
+p_age
+```
+
+### Sexuality
 
@@
 df |> 
+  filter(SexualOrientation == "Bisexual") |>
+  ggplot(aes(x=Gender)) +
+  geom_bar(aes(fill = StimuliChoice)) +
+   labs(x = "Gender", y = "Number of Participants", title = "Bisexuals' Choice of Stimuli", fill = "Stimuli Choice") +
+  theme_modern(axis.title.space = 15) +
+  theme(
+    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
+    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
+    axis.text.y = element_text(size = rel(1.1)),
+    axis.text.x = element_text(size = rel(1.1)),
+    axis.title.x = element_blank()
+  )
 
 ```
+
+### Origin
+
+```{r p_demographics_country}
+p_map <- df |>
+  mutate(Country = case_when(
+    Country=="United States"~ "USA",
+    Country=="United Kingdom" ~ "UK",
+    TRUE ~ Country
+  ))|>
+  dplyr::select(region = Country) |>
+  group_by(region) |>
+  summarize(n = n()) |>
+  right_join(map_data("world"), by = "region") |>
+  # mutate(n = replace_na(n, 0)) |>
+  ggplot(aes(long, lat, group = group)) +
+  geom_polygon(aes(fill = n)) +
+  scale_fill_gradientn(colors = c("#E66101", "#ca0020", "#cc66cc")) +
+  labs(fill = "N") +
+  theme_void() +
+  labs(title = "Country of Residence", subtitle = "Number of participants by country")  +
+  theme(
+    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
+    plot.subtitle = element_text(size = rel(1.2))
+  )
+
+p_map
+```
+
+### Education
+
+```{r}
+p_edu <- df |>
+  mutate(Education = fct_relevel(Education, "Other", "High School", "Bachelor", "Master", "Doctorate")) |> 
+  ggplot(aes(x = Education)) +
+  geom_bar(aes(fill = Education)) +
+  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
+  scale_fill_viridis_d(guide = "none") +
+  labs(title = "Education", y = "Number of Participants", subtitle = "Participants per achieved education level") +
+  theme_modern(axis.title.space = 15) +
+  theme(
+    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
+    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
+    axis.text.y = element_text(size = rel(1.1)),
+    axis.text.x = element_text(size = rel(1.1)),
+    axis.title.x = element_blank()
+  )
+p_edu
+```
+
+### Ethnicity
+
+```{r}
+p_eth <- df |>
+  filter(!is.na(Ethnicity)) |> 
+  ggplot(aes(x = "", fill = Ethnicity)) +
+  geom_bar() +
+  coord_polar("y") +
+  theme_minimal() +
+  theme(
+    axis.text.x = element_blank(),
+    axis.title.x = element_blank(),
+    axis.text.y = element_blank(),
+    axis.title.y = element_blank()
+  )
+
+p_eth
+```
+
+:::
+
+### Expertise
+
+```{r p_demographics_expertise}
+p_language <- df |>
+  ggplot(aes(x = Language_Level)) +
+  geom_bar() +
+  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
+  labs(x = "Level", y = "Number of Participants", title = "Language Level") +
+  theme_modern(axis.title.space = 15) +
+  theme(
+    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
+    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
+    axis.text.y = element_text(size = rel(1.1)),
+    axis.text.x = element_text(size = rel(1.1))
+  )
+
+p_expertise <- df |>
+  ggplot(aes(x = AI_Knowledge)) +
+  geom_bar() +
+  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
+  labs(x = "Level", y = "Number of Participants", title = "AI-Expertise") +
+  theme_modern(axis.title.space = 15) +
+  theme(
+    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
+    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
+    axis.text.y = element_text(size = rel(1.1)),
+    axis.text.x = element_text(size = rel(1.1))
+  )
+
+p_language | p_expertise
+```
+
+### System
+
+```{r p_demographics_settings}
+df$Screen_Size <- sqrt(df$Screen_Width * df$Screen_Height)
+
+df |> 
+  ggplot(aes(x = Screen_Size, fill=Mobile)) +
+  geom_histogram(bins = 50, color="black") +
+  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
+  labs(x =  expression("Screen Size ("~sqrt(Number~of~Pixels)~")"), y = "Number of Participants", title = "Screen Size") +
+  theme_modern(axis.title.space = 15) +
+  theme(
+    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
+    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
+    axis.text.y = element_text(size = rel(1.1)),
+    axis.text.x = element_text(size = rel(1.1))
+  )
+```
+
+:::
+
+```{r p_summary}
+#| fig-width: 15
+#| fig-height: 15
+
+p_country / 
+  (p_age + p_edu)
+```
+
+## Beliefs about Artificial Information Technology (BAIT)
+
+This section pertains to the validation of the BAIT scale measuring beliefs and expectations about artificial creations.
+
+::: {.panel-tabset}
+
+### Factor Analyis
+
+#### Exploratory Factor Analysis
+
+```{r}
+bait <- df |> 
+  select(starts_with("BAIT_"), -Bait_Duration) |> 
+  rename_with(function(x) gsub("BAIT_\\d_", "", x)) |> 
+  filter(!is.na(TextRealistic ))
+
+cor <- correlation::correlation(bait, redundant = TRUE) |> 
+  correlation::cor_sort() |> 
+  correlation::cor_lower()
+
+clean_labels <- function(x) {
+  x <- str_remove_all(x, "BAIT_") |> 
+    str_replace_all("_", " - ")
+}
+
+cor |> 
+  mutate(val = paste0(insight::format_value(r), format_p(p, stars_only=TRUE))) |>
+  mutate(Parameter2 = fct_rev(Parameter2)) |>
+  mutate(Parameter1 = fct_relabel(Parameter1, clean_labels),
+         Parameter2 = fct_relabel(Parameter2, clean_labels)) |> 
+  ggplot(aes(x=Parameter1, y=Parameter2)) +
+  geom_tile(aes(fill = r), color = "white") +
+  geom_text(aes(label = val), size = 3) +
+  labs(title = "Correlation Matrix",
+       subtitle = "Beliefs about Artificial Information Technology (BAIT)") +
+  scale_fill_gradient2(
+    low = "#2196F3",
+    mid = "white",
+    high = "#F44336",
+    breaks = c(-1, 0, 1),
+    guide = guide_colourbar(ticks=FALSE),
+    midpoint = 0,
+    na.value = "grey85",
+    limit = c(-1, 1))  + 
+  theme_minimal() +
+  theme(legend.title = element_blank(),
+        axis.title.x = element_blank(),
+        axis.title.y = element_blank(),
+        axis.text.x = element_text(angle = 45, hjust = 1))
+```
+
+```{r}
+#| message: false
+
+n <- parameters::n_factors(bait, package = "nFactors")
+plot(n)
+
+efa <- parameters::factor_analysis(bait, cor=cor(bait, use="pairwise.complete.obs"), n=3, rotation = "oblimin", 
+                                   sort=TRUE, scores="tenBerge", fm="ml")
+plot(efa)
+display(efa)
+```
+
+#### Confirmatory Factor Analysis
+
+```{r}
+m1 <- lavaan::cfa(
+  "G =~ ImitatingReality + EnvironmentReal + VideosIssues + TextIssues + VideosRealistic + ImagesRealistic + ImagesIssues + TextRealistic", 
+  data=bait)
+m2 <- lavaan::cfa(
+  "Images =~ ImitatingReality + EnvironmentReal + ImagesRealistic + ImagesIssues + VideosIssues + VideosRealistic
+  Text =~ TextIssues + TextRealistic", 
+  data=bait)
+m3 <- lavaan::cfa(
+  "Images =~ ImitatingReality + EnvironmentReal + ImagesRealistic + ImagesIssues
+  Videos =~ VideosIssues + VideosRealistic
+  Text =~ TextIssues + TextRealistic", 
+  data=bait)
+m4 <- lavaan::cfa(
+  "Environment =~ ImitatingReality + EnvironmentReal 
+  Images =~ ImagesRealistic + ImagesIssues
+  Videos =~ VideosIssues + VideosRealistic
+  Text =~ TextIssues + TextRealistic", 
+  data=bait)
+m5 <- lavaan::cfa(efa_to_cfa(efa, threshold="max"), data=bait)
+
+# bayestestR::bayesfactor_models(m1, m2)
+lavaan::anova(m1, m2, m3, m4, m5)
+```
+```{r}
+display(parameters::parameters(m4, standardize = TRUE))
+```
+
+```{r}
+m4b <- lavaan::sem(
+  "Environment =~ ImitatingReality + EnvironmentReal 
+  Images =~ ImagesRealistic + ImagesIssues
+  Videos =~ VideosIssues + VideosRealistic
+  Text =~ TextIssues + TextRealistic
+  G =~ Environment + Images + Videos + Text", 
+  data=bait)
+
+m4c <- lavaan::sem(
+  "Environment =~ ImitatingReality + EnvironmentReal 
+  Images =~ ImagesRealistic + ImagesIssues
+  Videos =~ VideosIssues + VideosRealistic
+  Text =~ TextIssues + TextRealistic
+  Visual =~ Environment + Images", 
+  data=bait)
+
+# bayestestR::bayesfactor_models(m1, m2)
+lavaan::anova(m4, m4b, m4c)
+```
+
+```{r}
+display(parameters::parameters(m4c, standardize = TRUE))
+```
+
+```{r}
+#| message: false
+#| warning: false
+
+library(ggraph)
+library(tidySEM)
+
+edges <- tidySEM::get_edges(m4c) |> 
+  mutate(sign = as.factor(sign(as.numeric(est_std))))
+
+tidygraph::tbl_graph(nodes = tidySEM::get_nodes(m4c), edges = edges) |> 
+  ggraph(layout = 'kk') + 
+  geom_edge_link(aes(filter=op=="=~", label=est_std, color=sign),
+                 angle_calc="along",
+                 label_dodge=unit(-0.015, "npc"),
+                 edge_width=1) + 
+  geom_edge_arc(aes(filter=op=="~~", label=est_std, color=sign), 
+                linetype="dashed", strength=0.1,
+                angle_calc="along",
+                label_dodge=unit(-0.015, "npc"),
+                edge_width=1) + 
+  geom_node_point(aes(shape=shape, color=shape), size=14, alpha=0.3) +
+  geom_node_text(aes(label = name)) + 
+  scale_edge_color_manual(values=c("1"="darkgreen", "-1"="red"), guide="none") +
+  scale_shape_manual(values=c("oval"="circle", "rect"="square"), guide="none") +
+  scale_color_manual(values=c("oval"="orange", "rect"="black"), guide="none") +
+  theme_void()
+```
+
+### Graph Analysis
+
+Exploratory Graph Analysis (EGA) is a recently developed framework for psychometric assessment, that can be used to estimate the number of dimensions in questionnaire data using network estimation methods and community detection algorithms, and assess the stability of dimensions and items using bootstrapping.
+
+#### Unique Variable Analysis (UVA)
+
+Unique Variable Analysis (Christensen, Garrido, & Golino, 2023) uses the weighted topological overlap measure (Nowick et al., 2009) on an estimated network.
+Values greater than 0.25 are determined to have considerable local dependence (i.e., redundancy) that should be handled (variables with the highest maximum weighted topological overlap to all other variables (other than the one it is redundant with) should be removed).
+
+```{r}
+uva <- EGAnet::UVA(data = bait, cut.off = 0.3)
+uva
+uva$keep_remove
+```
+
+#### Networks
+
+```{r ega}
+#| fig-height: 20
+#| fig-width: 12
+
+ega <- list()
+for(model in c("glasso", "TMFG")) {
+  for(algo in c("walktrap", "louvain")) {
+    for(type in c("ega", "ega.fit", "riEGA")) {  # "hierega"
+      if(type=="ega.fit" & algo=="louvain") next  # Too slow
+      ega[[paste0(model, "_", algo, "_", type)]] <- EGAnet::bootEGA(
+        data = bait,
+        seed=123,
+        model=model,
+        algorithm=algo,
+        EGA.type=type,
+        type="resampling",
+        plot.typicalStructure=FALSE,
+        verbose=FALSE)
+      }
+   }
+}
+
+EGAnet::compare.EGA.plots(
+  ega$glasso_walktrap_ega, ega$glasso_walktrap_ega.fit,
+  ega$glasso_louvain_ega, ega$TMFG_louvain_ega,
+  ega$glasso_louvain_riEGA, ega$glasso_walktrap_riEGA,
+  ega$TMFG_walktrap_ega, ega$TMFG_walktrap_ega.fit,
+  ega$TMFG_louvain_riEGA, ega$TMFG_walktrap_riEGA, 
+  labels=c("glasso_walktrap_ega", "glasso_walktrap_ega.fit",
+           "glasso_louvain_ega", "TMFG_louvain_ega",
+           "glasso_louvain_riEGA", "glasso_walktrap_riEGA",
+           "TMFG_walktrap_ega", "TMFG_walktrap_ega.fit",
+           "TMFG_louvain_riEGA", "TMFG_walktrap_riEGA"),
+  rows=5,
+  plot.all = FALSE)$all
+```
+
+#### Structure Stability
+
+Figures shows how often each variable is replicating in their empirical structure across bootstraps.
+
+<!-- The summary statistics produced also relay this information as well as structural consistency.
+Structural consistency is defined as the extent to which each empirically derived dimension is exactly (i.e., identical variable composition) recovered from the replicate bootstrap samples (Christensen, Golino, & Silvia, 2020).
+In general, values of structural consistency and item stability greater than 0.70-0.75 reflect sufficient stability (Christensen & Golino, 2021).
+-->
+
+```{r}
+#| fig-height: 20
+#| fig-width: 12
+
+patchwork::wrap_plots(lapply(ega, plot), nrow = 4)
+```
+
+#### Final Model
+
+```{r}
+ega_final <- ega$glasso_walktrap_riEGA$EGA
+plot(ega_final)
+```
+
+### Scores
+
+```{r}
+#| code-fold: false
+
+# Merge with data
+ega_scores <-  EGAnet::net.scores(bait, ega_final)$scores$std.scores |> 
+  as.data.frame() |> 
+  setNames(c("BAIT_Text_EGA", "BAIT_Visual_EGA", "BAIT_Videos_EGA"))
+
+sem_scores <- lavaan::predict(m4c) |> 
+  as.data.frame() |> 
+  datawizard::data_addprefix("BAIT_") |> 
+  datawizard::data_addsuffix("_SEM")
+
+raw_scores <- data.frame(
+  Participant = df[!is.na(df$BAIT_1_ImagesRealistic), ]$Participant,
+  BAIT_Videos = (bait$VideosRealistic + (1 - bait$VideosIssues)) / 2,
+  BAIT_Visual = (bait$ImagesRealistic + (1 - bait$ImagesIssues) + bait$ImitatingReality + bait$EnvironmentReal) / 4,
+  BAIT_Text = (bait$TextRealistic + (1 - bait$TextIssues)) / 2
+  )
+
+scores <- cbind(sem_scores, ega_scores, raw_scores) 
+df <- merge(df, raw_scores, by="Participant")
+```
+
+We computed two type of general scores for the BAIT scale, an **empirical** score based on the average of observed data (of the most loading items) and a **model-based** score as predicted by the structural model.
+The first one gives equal weight to all items (and keeps the same [0-1] range), while the second one is based on the factor loadings and the covariance structure.
+
+```{r}
+correlation::cor_test(scores, "BAIT_Visual", "BAIT_Visual_SEM") |> 
+  plot() +
+  ggside::geom_xsidedensity(aes(x=BAIT_Visual), color="grey", linewidth=1) +
+  ggside::geom_ysidedensity(aes(y=BAIT_Visual_SEM), color="grey", linewidth=1) +
+  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
+  ggside::scale_ysidex_continuous(expand = c(0, 0)) +
+  ggside::theme_ggside_void() +
+  theme(ggside.panel.scale = .1) 
+```
+
+While the two correlate substantially, they have different benefits.
+The empirical score has a more straightforward meaning and is more reproducible (as it is not based on a model fitted on a specific sample), the model-based score takes into account the relative importance of the contribution of each item to their factor.
+
+```{r}
+table <- correlation::correlation(scores) |> 
+  summary()
+
+format(table) |> 
+  datawizard::data_rename("Parameter", "Variables") |> 
+  gt::gt() |> 
+  gt::cols_align(align="center") |> 
+  gt::tab_options(column_labels.font.weight="bold")
+```
+
+### Validity
+
+#### Corrrelation with GAAIS
+
+```{r}
+n <- n_factors(select(df, starts_with("GAAIS")))
+n
+parameters::factor_analysis(
+  select(df, starts_with("GAAIS")), 
+  n=2, 
+  rotation="oblimin")
+
+df$GAAIS_Negative <- rowMeans(select(df, starts_with("GAAIS_Negative")))
+df$GAAIS_Positive <- rowMeans(select(df, starts_with("GAAIS_Positive")))
+```
+
+```{r}
+table <- correlation::correlation(
+  select(df, all_of(names(raw_scores))), 
+  select(df, starts_with("GAAIS")),
+  bayesian=TRUE) |> 
+  summary()
+
+format(table) |> 
+  datawizard::data_rename("Parameter", "Variables") |> 
+  gt::gt() |> 
+  gt::cols_align(align="center") |> 
+  gt::tab_options(column_labels.font.weight="bold")
+```
+
+```{r}
+#| warning: false
+
+dat <- df |> 
+  select(starts_with("GAAIS"), starts_with("BAIT")) |> 
+  select(matches("[[:digit:]]"))
+
+ega <- EGAnet::EGA(
+        data = dat,
+        seed=123,
+        model="glasso",
+        algorithm="leiden",
+        plot.EGA=FALSE,
+        verbose=FALSE)
+
+plot(ega)
+
+plot(parameters::factor_analysis(dat, n=6, rotation="oblimin", sort=TRUE))
+```
+
+```{r}
+#| eval: false
+#| echo: false
+
+# Used for feedback screen in the new BAIT implementations
+mean(rowMeans(df[c("GAAIS_Positive_12", "GAAIS_Positive_17")])) * 6
+```
+
+#### AI-Expertise
+
+```{r}
+df |> 
+  ggplot(aes(x=as.factor(AI_Knowledge), y=BAIT_Visual)) +
+  geom_boxplot()
+
+# m <- betareg::betareg(BAIT ~ AI_Knowledge, data=df)
+m <- lm(BAIT_Visual ~ poly(AI_Knowledge, 2), data=df)
+# m <- brms::brm(BAIT ~ mo(AI_Knowledge), data=df, algorithm = "meanfield")
+# m <- brms::brm(BAIT ~ AI_Knowledge, data=dfsub, algorithm = "meanfield")
+display(parameters::parameters(m))
+
+marginaleffects::predictions(m, by=c("AI_Knowledge"), newdata = "marginalmeans") |> 
+  as.data.frame() |> 
+  ggplot(aes(x=AI_Knowledge, y=estimate)) +
+  ggdist::stat_halfeye(data=df, aes(y=BAIT_Visual), geom="slab") +
+  # ggdist::stat_dots(data=df, aes(y=BAIT_Visual), side="left") +
+  # geom_boxplot(data=df, aes(y=BAIT_Visual, group=AI_Knowledge)) +
+  geom_point2(data=df, aes(x=AI_Knowledge-0.08, y=BAIT_Visual), alpha=0.2, position=position_jitter(width=0.06), size=2) +
+  geom_line(aes(group=1), position = position_dodge(width=0.2)) +
+  geom_pointrange(aes(ymin = conf.low, ymax=conf.high), position = position_dodge(width=0.2)) +
+  theme_minimal() +
+  labs(x = "AI-Knowledge", y="BAIT - Visual")
+```
+
+#### Gender and Age
+
+```{r}
+# m <- betareg::betareg(BAIT ~ Sex / Age, data=df, na.action=na.omit)
+m <- lm(BAIT_Visual ~ Sex / Age, data=df)
+display(parameters::parameters(m))
+```
+
+#### Belief in the Instructions
+
+```{r}
+glm(Feedback_LabelsIncorrect ~ BAIT_Visual * AI_Knowledge, 
+    data=mutate(df, Feedback_LabelsIncorrect = ifelse(Feedback_LabelsIncorrect=="True", 1, 0)), 
+    family="binomial") |> 
+  parameters::parameters() |> 
+  display(title="Predicting 'Labels are Incorrect'")
+```
+
+```{r}
+glm(Feedback_LabelsReversed ~ BAIT_Visual * AI_Knowledge, 
+    data=mutate(df, Feedback_LabelsReversed = ifelse(Feedback_LabelsReversed=="True", 1, 0)), 
+    family="binomial") |> 
+  parameters::parameters() |> 
+  display(title="Predicting 'Labels are reversed'")
+```
+
+```{r}
+glm(Feedback_CouldDiscriminate ~ BAIT_Visual * AI_Knowledge, 
+    data=mutate(df, Feedback_CouldDiscriminate = ifelse(Feedback_CouldDiscriminate=="True", 1, 0)), 
+    family="binomial") |> 
+  parameters::parameters() |> 
+  display(title="Predicting 'Easy to discriminate'")
+```
+
+```{r}
+m <- glm(Feedback_CouldNotDiscriminate ~ BAIT_Visual * AI_Knowledge, 
+    data=mutate(df, Feedback_CouldNotDiscriminate = ifelse(Feedback_CouldNotDiscriminate=="True", 1, 0)), 
+    family="binomial")
+
+parameters::parameters(m) |> 
+  display(title="Predicting 'Hard to discriminate'")
+
+modelbased::estimate_relation(m, length=6) |> 
+  plot()
+```
+
+```{r}
+glm(Feedback_Fun ~ BAIT_Visual * AI_Knowledge, 
+    data=mutate(df, Feedback_Fun = ifelse(Feedback_Fun=="True", 1, 0)), 
+    family="binomial") |> 
+  parameters::parameters() |> 
+  display(title="Predicting 'Fun'")
+```
+
+```{r}
+glm(Feedback_Boring ~ BAIT_Visual * AI_Knowledge, 
+    data=mutate(df, Feedback_Boring = ifelse(Feedback_Boring=="True", 1, 0)), 
+    family="binomial") |> 
+  parameters::parameters() |> 
+  display(title="Predicting 'Boring'")
+```
+
+```{r}
+glm(Feedback_AILessArousing ~ BAIT_Visual * AI_Knowledge, 
+    data=mutate(df, Feedback_AILessArousing = ifelse(Feedback_AILessArousing=="True", 1, 0)), 
+    family="binomial") |> 
+  parameters::parameters() |> 
+  display(title="Predicting 'AI was less arousing'")
+```
+
+```{r}
+glm(Feedback_AIMoreArousing ~ BAIT_Visual * AI_Knowledge, 
+    data=mutate(df, Feedback_AIMoreArousing = ifelse(Feedback_AIMoreArousing=="True", 1, 0)), 
+    family="binomial") |> 
+  parameters::parameters() |> 
+  display(title="Predicting 'AI was more arousing'")
+```
+
+:::

### 2025-02-21 study2/analysis/1_cleaning.qmd
updated data

--- 2025-02-19 study2/analysis/1_cleaning.qmd
@@
 ```{r}
-#| code-fold: false
 
@@
 ## Feedback
-
-### Evaluation
 
@@
 data.frame(Comments = df$Feedback_Text) |>
-  filter(!tolower(Comments) %in% c(NA, "no", "no comments", "nothing", "none", "")) |> 
+  filter(!tolower(Comments) %in% c(NA, "no", "no comments", "nothing", "none", "", "no.")) |> 
   gt::gt() |> 
@@
 
-### Response to Erotic Stimuli
-
-```{r}
-# Single arousal response (0)
-outliers$novariability <- summarize(dftask, n = length(unique(Arousal)), .by="Participant") |> 
-  filter(n == 1) |> 
-  select(Participant) |> 
-  pull()
-```
 ### Response Coherence
@@
 
-### Sexual Profile
+:::
+
+## Final Sample
+
+### Summary
+
+The final sample includes `r report::report_participants(df, age="Age", sex="Sex", education="Education")`.
+
+::: {.panel-tabset}
+
+### Age and Gender
+
+```{r}
+p_age <- df |>
+  ggplot(aes(x = Age, fill = Gender)) + 
+  geom_histogram(data=df, aes(x = Age, fill=Gender), binwidth = 2) +
+  geom_vline(xintercept = mean(df$Age), color = "red", linewidth=1.5, linetype="dashed") +
+  scale_fill_viridis_d() +
+  scale_x_continuous(expand = c(0, 0), breaks = seq(10, max(df$Age), by = 10)) +
+  scale_y_continuous(expand = c(0, 0)) +
+  labs(title = "Age", y = "Number of Participants", color = NULL, subtitle = "Distribution of participants' age") +
+  theme_modern(axis.title.space = 10) +
+  theme(
+    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
+    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
+    axis.text.y = element_text(size = rel(1.1)),
+    axis.text.x = element_text(size = rel(1.1)),
+    axis.title.x = element_blank()
+  )
+
+p_age
+```
+
+### Sexuality
 
@@
 df |> 
+  filter(SexualOrientation == "Bisexual") |>
+  ggplot(aes(x=Gender)) +
+  geom_bar(aes(fill = StimuliChoice)) +
+   labs(x = "Gender", y = "Number of Participants", title = "Bisexuals' Choice of Stimuli", fill = "Stimuli Choice") +
+  theme_modern(axis.title.space = 15) +
+  theme(
+    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
+    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
+    axis.text.y = element_text(size = rel(1.1)),
+    axis.text.x = element_text(size = rel(1.1)),
+    axis.title.x = element_blank()
+  )
 
 ```
+
+### Origin
+
+```{r p_demographics_country}
+p_map <- df |>
+  mutate(Country = case_when(
+    Country=="United States"~ "USA",
+    Country=="United Kingdom" ~ "UK",
+    TRUE ~ Country
+  ))|>
+  dplyr::select(region = Country) |>
+  group_by(region) |>
+  summarize(n = n()) |>
+  right_join(map_data("world"), by = "region") |>
+  # mutate(n = replace_na(n, 0)) |>
+  ggplot(aes(long, lat, group = group)) +
+  geom_polygon(aes(fill = n)) +
+  scale_fill_gradientn(colors = c("#E66101", "#ca0020", "#cc66cc")) +
+  labs(fill = "N") +
+  theme_void() +
+  labs(title = "Country of Residence", subtitle = "Number of participants by country")  +
+  theme(
+    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
+    plot.subtitle = element_text(size = rel(1.2))
+  )
+
+p_map
+```
+
+### Education
+
+```{r}
+p_edu <- df |>
+  mutate(Education = fct_relevel(Education, "Other", "High School", "Bachelor", "Master", "Doctorate")) |> 
+  ggplot(aes(x = Education)) +
+  geom_bar(aes(fill = Education)) +
+  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
+  scale_fill_viridis_d(guide = "none") +
+  labs(title = "Education", y = "Number of Participants", subtitle = "Participants per achieved education level") +
+  theme_modern(axis.title.space = 15) +
+  theme(
+    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
+    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
+    axis.text.y = element_text(size = rel(1.1)),
+    axis.text.x = element_text(size = rel(1.1)),
+    axis.title.x = element_blank()
+  )
+p_edu
+```
+
+### Ethnicity
+
+```{r}
+p_eth <- df |>
+  filter(!is.na(Ethnicity)) |> 
+  ggplot(aes(x = "", fill = Ethnicity)) +
+  geom_bar() +
+  coord_polar("y") +
+  theme_minimal() +
+  theme(
+    axis.text.x = element_blank(),
+    axis.title.x = element_blank(),
+    axis.text.y = element_blank(),
+    axis.title.y = element_blank()
+  )
+
+p_eth
+
+```
+
+### System
+
+```{r p_demographics_settings}
+df$Screen_Size <- sqrt(df$Screen_Width * df$Screen_Height)
+
+df |> 
+  ggplot(aes(x = Screen_Size, fill=Mobile)) +
+  geom_histogram(bins = 50, color="black") +
+  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
+  labs(x =  expression("Screen Size ("~sqrt(Number~of~Pixels)~")"), y = "Number of Participants", title = "Screen Size") +
+  theme_modern(axis.title.space = 15) +
+  theme(
+    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
+    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
+    axis.text.y = element_text(size = rel(1.1)),
+    axis.text.x = element_text(size = rel(1.1))
+  )
+```
+
+:::

### 2025-02-21 study2/analysis/2_emotion.qmd
updated data

---
title: "FictionEro2 - Affective Impact of Fiction"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
---

### 2025-02-26 study2/analysis/1_cleaning.qmd
started analysis + updated data

@@
 
-```
-
-```{r}
-
 df <- read.csv("../data/rawdata_participants.csv")
@@
 ::: {.panel-tabset}
+
+### Proportion
+
+```{r}
+df |> 
+  select(starts_with("Feedback"), -Feedback_Text, -Feedback_AllRealConfidence, -Feedback_AllFakeConfidence, -Feedback_DiffSubtle, -Feedback_Enjoyment) |>
+  pivot_longer(everything(), names_to = "Question", values_to = "Answer") |>
+  group_by(Question, Answer) |> 
+  summarise(prop = n()/nrow(df), .groups = 'drop') |> 
+  complete(Question, Answer, fill = list(prop = 0)) |> 
+  filter(Answer == "True") |> 
+  mutate(Question = str_remove(Question, "Feedback_"),
+         Question = str_replace(Question, "SomeFacesAttractive", "Some faces were attractive"),
+         Question = str_replace(Question, "NoFacesAttractive", "No faces were attractive"),
+         Question = str_replace(Question, "AILessAttractive", "AI = Less attractive"),
+         Question = str_replace(Question, "AIMoreAttractive", "AI = More attractive"),
+         # Question = str_replace(Question, "DiffSubtle", "Subtle differences between AI images and photos"),
+         Question = str_replace(Question, "DiffNone", "No difference between AI images and photos"),
+         Question = str_replace(Question, "LabelsIncorrect", "Labels were incorrect"),
+         Question = str_replace(Question, "AllReal", "All images were real"),
+         Question = str_replace(Question, "AllFake", "All images were AI-generated"),
+         Question = str_replace(Question, "DiffObvious", "Obvious differences between AI images and photos"),
+         Question = str_replace(Question, "LabelsReversed", "Labels were reversed")) |>
+  mutate(Question = fct_reorder(Question, desc(prop))) |> 
+  ggplot(aes(x = Question, y = prop)) +
+  geom_bar(stat = "identity") +
+  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks(), labels=scales::percent) +
+  labs(x="Feedback", y = "Participants", title = "Feedback") +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
+    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
+    axis.text.y = element_text(size = rel(1.1)),
+    axis.text.x = element_text(size = rel(1.1), angle = 55, hjust = 1),
+    axis.title.x = element_blank()
+  )
+```
+
+### Confidence
+
+```{r}
+
+df |>
+  select(Feedback_AllRealConfidence, Feedback_AllFakeConfidence) |>
+  pivot_longer(everything(), names_to = "Authenticity", values_to = "Confidence") |>
+  drop_na() |>
+  mutate(Authenticity = str_remove(Authenticity, "Feedback_"),
+         Authenticity = str_replace(Authenticity, "AllRealConfidence", "All images were real"),
+         Authenticity = str_replace(Authenticity, "AllFakeConfidence", "All images were fake")) |>
+  ggplot(aes(x = Confidence, fill= Authenticity)) +
+  geom_bar() +
+  labs(x="Confidence (0-5)", y = "Number of Participants", title = "Confidence on the authenticity of the images") +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(size = rel(1.2), face = "bold", hjust = 0),
+    plot.subtitle = element_text(size = rel(1.2), vjust = 7),
+    axis.text.y = element_text(size = rel(1.1)),
+    axis.title.x = element_blank())
+```
 
@@
 
+:::
+
 ## Exclusion
+
+::: {.panel-tabset}
 
@@
 ```
+
+### Mobile
+
+```{r}
+mobile <- table(df$Mobile)
+
+# outliers$Mobile <- sum(df$Mobile=="True")
+```
+
+There were `r sum(df$Mobile=="True")` participants that used a mobile device.
 
@@
 ```
-### BAIT Questionnaire Duration
-
-```{r}
-#| fig-width: 15
-#| fig-height: 15
-
-df |>
-  mutate(Participant = fct_reorder(Participant, Bait_Duration),
-         Category = ifelse(Bait_Duration > 5, "extra", "ok"),
-         Duration = ifelse(Bait_Duration > 5, 5, Bait_Duration),
-         Group = ifelse(Participant %in% outliers, "Outlier", "ok")) |>
-  ggplot(aes(y = Participant, x = Duration)) +
-  geom_point(aes(color = Group, shape = Category)) +
-  geom_vline(xintercept = median(df$Bait_Duration), color = "red", linetype = "dashed") +
-  geom_vline(xintercept = 0.5, color = "orange", linetype = "dotted") +
-  scale_shape_manual(values = c("extra" = 3, ok = 19)) +
-  scale_color_manual(values = c("Outlier" = "red", ok = "black"), guide="none") +
-  guides(color = "none", shape = "none") +
-  ggside::geom_xsidedensity(fill = "#9C27B0", color=NA) +
-  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
-  labs(
-    title = "Questionnaire Completion Time",
-    x = "Duration (in minutes)",
-    y = "Participant"
-  )  +
-  theme_modern() +
-  ggside::theme_ggside_void() +
-  theme(ggside.panel.scale = .3,
-        panel.border = element_blank(),
-        axis.ticks.y = element_blank(),
-          axis.text.y = element_blank())
-
-# min(df$Bait_Duration) 0.8084833
-# max(df$Bait_Duration) 20.37072
-```
 
@@
 
-outliers$emo_cor <- sort(as.character(dat[dat$cor_ArEnt < 0, ]$Participant))
+outliers$emo_ent <- sort(as.character(dat[dat$cor_ArEnt < 0, ]$Participant))
 outliers$emo_aro <- sort(as.character(dat[dat$cor_ArVal < 0, ]$Participant))
-
-outliers$arousal <- intersect(outliers$emo_aro, outliers$emo_cor)
+outliers$arousal <- intersect(outliers$emo_aro, outliers$emo_ent)
 
@@
 
-**NOTE**: Remove?
+```{r}
 
-```{r}
-# df <- filter(df, !Participant %in% outliers$arousal)
-# dftask <- filter(dftask, !Participant %in% outliers$arousal)
 ```
@@
   scale_y_continuous(expand = c(0, 0), breaks = scales::pretty_breaks()) +
-  labs(x = "Biological Sex", y = "Number of Participants", title = "Sex and Sexual Orientation", fill = "Sexual Orientation") +
+  labs(x = "Biological Sex", y = "Number of Participants", title = "Gender and Sexual Orientation", fill = "Sexual Orientation") +
   theme_modern(axis.title.space = 15) +
@@
 df |> 
+  group_by(Gender) |>
   filter(SexualOrientation == "Bisexual") |>
@@
     axis.text.y = element_text(size = rel(1.1)),
-    axis.text.x = element_text(size = rel(1.1)),
+    axis.text.x = element_text(size = rel(1.1), angle = 45, hjust = 1),
     axis.title.x = element_blank()

### 2025-02-26 study2/analysis/2_emotion.qmd
started analysis + updated data

@@
 ---
+
+## Data Preparation
+
+```{r}
+#| message: false
+#| warning: false
+
+library(tidyverse)
+library(easystats)
+library(patchwork)
+library(ggside)
+library(glmmTMB)
+
+options(mc.cores = parallel::detectCores(),
+        brms.backend = "cmdstanr",
+        width = 300)
+```
+
+**notes**: How about confidence on all AI and all photos
+
+```{r}
+dfsub <- read.csv("../data/data_participants.csv")
+df <- read.csv("../data/data.csv") |> 
+  right_join(
+    select(dfsub, Participant, Mobile, starts_with(c("Feedback_","BAIT")), COPS_Frequency_2, SexualActivity,
+           -Feedback_Text),
+    by = "Participant"
+    ) |> 
+  mutate(Condition = fct_relevel(Condition, "Reality", "Fiction"),
+         Gender =  fct_relevel(Gender, "Male", "Female", "Other"),
+         PornFrequency = as.numeric(as.factor(COPS_Frequency_2)),
+         GenderualActivity_num = as.numeric(as.factor(SexualActivity)),
+         ConditionBelief = case_when(
+           Condition == "Reality" & Realness > 0.5 ~ "True",
+           Condition == "AI-Fiction" & Realness < 0.5 ~ "True",
+           .default = "False",
+         )) |> 
+  mutate(across(starts_with("Feedback_")& !matches("Feedback_AllRealConfidence|Feedback_AllFakeConfidence|Feedback_Enjoyment"), function(x) {fct_relevel(x, "False", "True")}))
+
+results_table <- function(model, effects="fixed", filter=NULL) {
+  if("marginaleffects" %in% class(model)) {
+    model |> 
+      parameters::parameters() |> 
+      as.data.frame() |> 
+      select(-Parameter, -SE, -S, z=Statistic, -Predicted) |> 
+      insight::format_table() |> 
+      parameters::display()
+  } else {
+    display(parameters::parameters(model, effects=effects, keep=filter))
+  }
+}
+```
+
+## Manipulation Check
+
+This section is about selecting the best model. Notably, all the stimuli presented are of an erotic nature.
+
+**Note to dom** beta model does not make sense anymore, what else should we do?
+
+::: panel-tabset
+
+### Arousal
+
+```{r}
+arousal <- df |> 
+  ggplot(aes(x=Arousal)) +
+  geom_histogram(fill="grey", position = "identity", binwidth = 0.5) +
+  scale_y_sqrt(expand = c(0, 0)) +
+  scale_x_continuous(breaks = (0:6), labels = c("Not at all", "1", "2", "3", "4", "5", "Very much")) +
+  labs(title = "Arousal") +
+  theme_abyss() +
+  theme(plot.title = element_text(hjust = 0.5, face="bold"))
+
+arousal
+```
+
+**Note**:  Model m3, which includes random intercepts and random slopes for Gender at the stimulus level, exhibits relatively high correlations between the random intercepts and slopes.
+This suggests that the random effects are strongly correlated, which could indicate overfitting.
+
+```{r}
+#| eval: false
+
+# Get a sense of Random Factors
+m1 <- glmmTMB::glmmTMB(Arousal ~ Gender + (1|Participant), data=df)
+m2 <- glmmTMB::glmmTMB(Arousal ~ Gender + (1|Participant) + (1|Stimulus ), data=df)
+m3 <- glmmTMB::glmmTMB(Arousal ~ Gender + (1|Participant) + (1+Gender|Stimulus ), data=df)
+
+test_bf(m1,m2)
+compare_performance(m1, m2)
+
+# the model with participants and stimuli as random effecs seems to be the best
+```
+
+This model evaluate ths the effects of Gender on Arousal, accounting for random variability due to participants and the stimuli (i.e., random effects).
+
+The analysis revealed that on average **women rate erotic stimuli significantly lower in arousal than men**, while participants identifying as 'other' rate on average erotic stimuli higher than men, however this is not significant.
+
+```{r}
+m_a <- glmmTMB::glmmTMB(Arousal ~ Gender + (1|Participant) + (1|Stimulus ),
+                      data=df,
+                      control = glmmTMB::glmmTMBControl(parallel = 8))
+                      # control = glmmTMB::glmmTMBControl(optimizer=stats::optim, # nlminb, optim
+                      #                                   optArgs = list(method = "BFGS"),  #Nelder-Mead, BFGS, CG
+                      #                                   parallel = 8))
+
+results_table(m_a)
+
+```
+
+```{r}
+estimate_relation(m_a) |> 
+  ggplot(aes(x=Gender, y=Predicted)) +
+  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color = Gender), position=position_dodge(width=0.5)) +
+ scale_color_manual(values=c("Male"="#E91E63", "Female"="#FF9800","Other"="#03A9F4"), guide="none") +  labs(y="Arousal") +
+  theme_abyss()
+```
+
+### Enticement
+
+```{r}
+valence <- df |> 
+  ggplot(aes(x=Enticing)) +
+  geom_histogram(fill="grey", position = "identity", binwidth = 0.5) +
+  scale_y_sqrt(expand = c(0, 0)) +
+  scale_x_continuous(breaks = (0:6), labels = c("Not at all", "1", "2", "3", "4", "5", "Very much")) +
+  labs(title = "Valence") +
+  theme_abyss() +
+  theme(plot.title = element_text(hjust = 0.5, face="bold"),
+        legend.position = "none")
+
+valence
+```
+
+This model evaluate ths the effects of Gender on Enticement, accounting for random variability due to participants and the stimuli (i.e., random effects). Notably, all the stimuli is erotic.
+
+The analysis revealed that on average **women rate erotic stimuli significantly lower in enticiment than men**, while participants identifying as 'other' rate on average erotic stimuli higher than men.
+However, these differences were not statistically significant.
+
+```{r}
+m_e <- glmmTMB::glmmTMB(Enticing ~ Gender + (1|Participant) + (1|Stimulus ),
+                      data=df,
+                      control = glmmTMB::glmmTMBControl(parallel = 8))
+                      # control = glmmTMB::glmmTMBControl(optimizer=stats::optim, # nlminb, optim
+                      #                                   optArgs = list(method = "BFGS"),  #Nelder-Mead, BFGS, CG
+                      #                                   parallel = 8))
+
+results_table(m_e)
+
+```
+
+```{r}
+estimate_relation(m_e) |> 
+  ggplot(aes(x=Gender, y=Predicted)) +
+  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color = Gender), position=position_dodge(width=0.5)) +
+ scale_color_manual(values=c("Male"="#E91E63", "Female"="#FF9800","Other"="#03A9F4"), guide="none") +  labs(y="Arousal") +
+  theme_abyss()
+```
+
+### Valence
+
+```{r}
+valence <- df |> 
+  ggplot(aes(x=Valence)) +
+  geom_histogram(fill="grey", position = "identity", binwidth = 0.5) +
+  scale_y_sqrt(expand = c(0, 0)) +
+  scale_x_continuous(breaks = (0:6), labels = c("Unpleasant", "1", "2", "3", "4", "5", "Pleasa")) +
+  labs(title = "Valence") +
+  theme_abyss() +
+  theme(plot.title = element_text(hjust = 0.5, face="bold"),
+        legend.position = "none")
+
+valence
+```
+
+This model evaluate ths the effects of Gender on valence, accounting for random variability due to participants and the stimuli (i.e., random effects). Notably, all the stimuli is erotic.
+
+<!-- Key Findings -->
+
+The analysis revealed that on average **women rate erotic stimuli significantly lower in arousal than men**, while participants identifying as 'other' rate on average erotic stimuli higher than men,.
+None of these differences were statistically significant.
+
+```{r}
+m_v <- glmmTMB::glmmTMB(Valence ~ Gender + (1|Participant) + (1|Stimulus ),
+                      data=df,
+                      control = glmmTMB::glmmTMBControl(parallel = 8))
+                      # control = glmmTMB::glmmTMBControl(optimizer=stats::optim, # nlminb, optim
+                      #                                   optArgs = list(method = "BFGS"),  #Nelder-Mead, BFGS, CG
+                      #                                   parallel = 8))
+
+results_table(m_v)
+
+```
+
+```{r}
+estimate_relation(m_e) |> 
+  ggplot(aes(x=Gender, y=Predicted)) +
+  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color = Gender), position=position_dodge(width=0.5)) +
+ scale_color_manual(values=c("Male"="#E91E63", "Female"="#FF9800","Other"="#03A9F4"), guide="none") +  labs(y="Arousal") +
+  theme_abyss()
+```

### 2025-02-28 study2/analysis/2_emotion.qmd
added dapipe to save only demo_data

@@
 
-**notes**: How about confidence on all AI and all photos
+**notes**: How about confidence on all AI and all photos.
 
@@
   right_join(
-    select(dfsub, Participant, Mobile, starts_with(c("Feedback_","BAIT")), COPS_Frequency_2, SexualActivity,
+    select(dfsub, Participant, Mobile, starts_with(c("Feedback_","BAIT")), COPS_Frequency_2, GenderualActivity,
            -Feedback_Text),
@@
          PornFrequency = as.numeric(as.factor(COPS_Frequency_2)),
-         GenderualActivity_num = as.numeric(as.factor(SexualActivity)),
+         GenderualActivity_num = as.numeric(as.factor(GenderualActivity)),
          ConditionBelief = case_when(
@@
            .default = "False",
+         )) |> 
+  mutate(Condition = case_when(
+    Condition == "Fiction" ~ "AI-Generated",
+    Condition == "Reality" ~ "Photograph"
   )) |>
@@
 arousal
+```
+
+```{r}
+
+df |> 
+  mutate(ConditionBelief = as.factor(ConditionBelief)) |> 
+  mutate(ConditionBelief = case_when(
+    ConditionBelief == "False" ~ "Not Believed",
+    ConditionBelief == "True" ~ "Believed",)) |>
+  ggplot(aes(x=Arousal, fill=Gender)) +
+  geom_histogram(position = "identity", binwidth = 0.5) +
+  facet_grid(Gender~ConditionBelief, scales="free_y") +
+  scale_color_manual(values=c("red", "white"), guide="none") +
+  scale_fill_manual(values=c("Female"="#E91E63", "Male"="#FF9800", "Other" = "#03A9F4"), guide="none") +
+  # scale_y_sqrt(expand = c(0, 0)) +
+  labs(title = "Arousal to images believed or not to be AI-Gnerated") +
+  theme_abyss() +
+  theme(plot.title = element_text(hjust = 0.5, face="bold"))
 ```
@@
 
+```{r}
+
+df |> 
+  mutate(ConditionBelief = as.factor(ConditionBelief)) |> 
+  mutate(ConditionBelief = case_when(
+    ConditionBelief == "False" ~ "Not Believed",
+    ConditionBelief == "True" ~ "Believed",)) |>
+  ggplot(aes(x=Enticing, fill=Gender)) +
+  geom_histogram(position = "identity", binwidth = 0.5) +
+  facet_grid(Gender~ConditionBelief, scales="free_y") +
+  scale_color_manual(values=c("red", "white"), guide="none") +
+  scale_fill_manual(values=c("Female"="#E91E63", "Male"="#FF9800", "Other" = "#03A9F4"), guide="none") +
+  # scale_y_sqrt(expand = c(0, 0)) +
+  labs(title = "Enticiment to images believed or not to be AI-Gnerated") +
+  theme_abyss() +
+  theme(plot.title = element_text(hjust = 0.5, face="bold"))
+```
+
 This model evaluate ths the effects of Gender on Enticement, accounting for random variability due to participants and the stimuli (i.e., random effects). Notably, all the stimuli is erotic.
@@
   scale_y_sqrt(expand = c(0, 0)) +
-  scale_x_continuous(breaks = (0:6), labels = c("Unpleasant", "1", "2", "3", "4", "5", "Pleasa")) +
+  scale_x_continuous(breaks = (0:6), labels = c("Unpleasant", "1", "2", "3", "4", "5", "Pleasant")) +
   labs(title = "Valence") +
@@
 valence
+```
+
+```{r}
+
+df |> 
+  mutate(ConditionBelief = as.factor(ConditionBelief)) |> 
+  mutate(ConditionBelief = case_when(
+    ConditionBelief == "False" ~ "Not Believed",
+    ConditionBelief == "True" ~ "Believed",)) |>
+  ggplot(aes(x=Valence, fill=Gender)) +
+  geom_histogram(position = "identity", binwidth = 0.5) +
+  facet_grid(Gender~ConditionBelief, scales="free_y") +
+  scale_color_manual(values=c("red", "white"), guide="none") +
+  scale_fill_manual(values=c("Female"="#E91E63", "Male"="#FF9800", "Other" = "#03A9F4"), guide="none") +
+  # scale_y_sqrt(expand = c(0, 0)) +
+  labs(title = "Valence to images believed or not to be AI-Gnerated") +
+  theme_abyss() +
+  theme(plot.title = element_text(hjust = 0.5, face="bold"))
 ```
@@
 ```
+
+:::
+
+## Arousal
+
+```{r}
+#| fig-height: 12
+#| fig-width: 7
+
+plot_descriptive <- function(df, target="Arousal") {
+  # By item
+  order <- df |>
+    mutate(.Item_Order = paste0(Gender, "_", Stimulus)) |>
+    summarize(mean = mean(.data[[target]], na.rm=TRUE), .by=c("Condition", ".Item_Order")) |> 
+    arrange(.Item_Order, desc(Condition)) |> 
+    mutate(diff = sign(mean - lag(mean)),
+           Relevance = str_extract(.Item_Order, "^[^_]+"),
+           .Item_Order = str_extract(.Item_Order, "(?<=_).+")) |>
+    filter(Condition == "Photograph") |> 
+    arrange(Relevance, diff, mean)
+
+  p1 <- df |>
+    mutate(.Item_Order = paste0(Gender, "_", Stimulus)) |>
+    group_by(.Item_Order, Condition) |>
+    ggdist::mean_qi(.data[[target]], .width=0.95) |>
+    mutate(Gender = fct_rev(str_extract(.Item_Order, "^[^_]+"))) |>
+    left_join(order[c(".Item_Order", "diff")], by=".Item_Order") |>
+    mutate(.Item_Order = fct_relevel(.Item_Order, order$.Item_Order)) |>
+    # mutate(.average = mean(.data[[target]]), .by="Item") |>
+    # mutate(Item = fct_reorder(Item, .average)) |>
+    ggplot(aes(y = .Item_Order, x=.data[[target]])) +
+    geom_line(aes(color=as.factor(diff)), linewidth=1) +
+    geom_point(aes(color=Condition), size=2) +
+
+    # ggdist::stat_slabinterval(aes(fill=Condition, color=Condition),
+    #                           .width=0.95, normalize="xy", slab_alpha=0.5) +
+    # ggdist::stat_histinterval(aes(fill=Condition, color=Condition),
+    #                           .width=0.95, normalize="xy", slab_alpha=0.5) +
+    scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336", "1"="#F44336", "-1"="#2196F3"),
+                       breaks = c('AI-Generated', 'Photograph')) +
+    # scale_fill_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
+    scale_y_discrete(labels = function(x) str_extract(x, "(?<=_).+")) +
+    theme_minimal() +
+    theme(panel.grid.minor.x = element_blank(),
+          # panel.grid.major.x = element_blank(),
+          panel.border = element_blank(),
+          axis.line.x = element_blank()) +
+    labs(title = paste0(target, " by Item"), color="Condition", y="Items") +
+    facet_wrap(~Gender, scales="free_y")
+
+  # By participant
+  p2 <- df |>
+    summarize(.average = mean(.data[[target]]),
+              .by=c("Gender", "Participant", "Condition")) |>
+    pivot_wider(names_from = Condition, values_from = .average) |>
+    mutate(.diff = Photograph - `AI-Generated`) |>
+    mutate(Participant = fct_reorder(Participant, .diff)) |>
+    ggplot(aes(x = .diff, y=Participant)) +
+    geom_bar(aes(fill=.diff), stat = "identity")  +
+    scale_fill_gradient2(guide="none", low="red", high="red", mid="blue") +
+    labs(title = paste0(target, " by Participant")) +
+    facet_wrap(~Gender, ncol=2, scales="free_y") +
+    theme_minimal() +
+    theme(panel.grid.major.y = element_blank(),
+          panel.border = element_blank(),
+          axis.line.x = element_blank(),
+          axis.text.y = element_blank()) +
+    labs(title = paste0(target, " by Participant"), x="Difference (Photograph - AI-Generated)", y="Participants")
+
+  p1 / p2 + plot_layout(heights = c(2, 1))
+}
+
+# remove other 
+arousal_desc <- df |> 
+  filter(Gender != "Other") |> 
+  plot_descriptive("Arousal")
+
+arousal_desc
+```
+
+### Whole Sample
+
+```{r}
+
+```

### 2025-03-14 paper/manuscript.qmd
data + paper folder

---
title: ""
shorttitle: "FicitionEro"
author:
  - name: Dominique Makowski
    corresponding: true
    orcid: 0000-0001-5375-9967
    email: D.Makowski@sussex.ac.uk
    url: https://realitybending.github.io/
    roles:
    affiliations:
      - ref: "id1"
      - name: "University of Sussex"
        department:  "Sussex Centre for Consciousness Science"
  - name: Ana Neves
    orcid: 0009-0006-0020-7599
    roles:
      - Project administration
      - Data curation
      - Formal Analysis
      - Investigation
      - Visualization
      - Writing – original draft
      - Writing – review & editing
    affiliations:
      - id: "id1"
        name: "University of Sussex"
        department: "School of Psychology"
        city: "Brighton"
        country: "UK"
        postal-code: "BN1 9RH"
# author-note:
#   status-changes: 
#     affiliation-change: null
#     deceased: null
#   disclosures:
#     study-registration: null
#     data-sharing: null
#     related-report: null
#     conflict-of-interest: null
#     financial-support: null
#     gratitude: null
#     authorship-agreements: null
    #   # - Project administration
    #   # - Data curation
    #   # - Formal Analysis
    #   # - Investigation
    #   # - Visualization
    #   # - Writing – original draft
    #   # - Writing – review & editing
    # Roles are optional. 
    # conceptualization, data curation, formal Analysis, funding acquisition, investigation, 
    # methodology, project administration, resources, software, supervision, validation, 
    # visualization, writing, editing
    #   - Conceptualization
    #   - Data curation
    #   - formal Analysis
    #   - Funding acquisition
    #   - Investigation
    #   - Methodology
    #   - Project administration
    #   - Resources
    #   - Software
    #   - Supervision
    #   - Validation
    #   - Visualization
    #   - Writing – original draft
author-note:
  disclosures:
    gratitude: |
      ::: {.callout-note icon=false appearance="simple"}
      :::
      This preprint is a non-peer-reviewed work from the [**Reality Bending Lab**](https://realitybending.github.io/).
      ![](https://realitybending.github.io/media/ReBeL_LogoOnly_hu11484441381606756729.png){width=20% fig-align="center"}
abstract: |
  Blabla the abstract blabla.
keywords: [keyword1, keyword2, keyword3]
floatsintext: true
numbered-lines: true
bibliography: bibliography.bib
suppress-title-page: false
mask: false
# Language options. See https://quarto.org/docs/authoring/language.html
lang: en
language:
  citation-last-author-separator: "and"
  citation-masked-author: "Masked Citation"
  citation-masked-date: "n.d."
  citation-masked-title: "Masked Title"
  title-block-author-note: "Author Note"
  title-block-correspondence-note: "Correspondence concerning this article should be addressed to"
  title-block-role-introduction: "Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows:"
  references-meta-analysis:
format:
  apaquarto-pdf:
    # Can be jou (journal), man (manuscript), stu (student), or doc (document)
    documentmode: man
    include-in-header:
      - text: |
          \usepackage{lscape}
  apaquarto-docx: default
  apaquarto-html: default
editor: 
  markdown: 
    wrap: sentence
editor_options: 
  chunk_output_type: console
---

<!-- Study 1  -->

<!-- Study 2 -->

### 2025-03-14 study2/analysis/0_preprocessing.py

@@ -230,35 +230,26 @@ for i, file in enumerate(files):
     sexactivity = "6. More than a year ago" if "6." in sexactivity else sexactivity
     sexactivity = np.nan if sexactivity in [""] else sexactivity
     df["SexualActivity"] = sexactivity
+    
+    copsfreq = cops.get("COPS_Frequency") or ""  # Ensures None is converted to ""
+    copsfreq = copsfreq.rstrip()  
 
-   copsfreq = cops["COPS_Frequency"]
-copsfreq = copsfreq.rstrip() if isinstance(copsfreq, str) else np.nan
-    copsfreq = (
-        "0. I haven't viewed pornography in the past 30 days"
-        if "0." in copsfreq
-        else copsfreq
-    )
-    copsfreq = (
-        "1. I viewed pornography once in the past 30 days"
-        if "1." in copsfreq
-        else copsfreq
-    )
-    copsfreq = (
-        "2. I viewed pornography twice in the past 30 days"
-        if "2." in copsfreq
-        else copsfreq
-    )
-    copsfreq = "3. I viewed pornography weekly" if "3." in copsfreq else copsfreq
-    copsfreq = (
-        "4. I viewed pornography multiple times a week"
-        if "4." in copsfreq
-        else copsfreq
-    )
-    copsfreq = "5. I viewed pornography daily" if "5." in copsfreq else copsfreq
-    copsfreq = (
-        "6. I viewed pornography multiple times a day" if "6." in copsfreq else copsfreq
-    )
-    copsfreq = np.nan if not copsfreq else copsfreq
+    if "0." in copsfreq:
+        copsfreq = "0. I haven't viewed pornography in the past 30 days"
+    elif "1." in copsfreq:
+        copsfreq = "1. I viewed pornography once in the past 30 days"
+    elif "2." in copsfreq:
+        copsfreq = "2. I viewed pornography twice in the past 30 days"
+    elif "3." in copsfreq:
+        copsfreq = "3. I viewed pornography weekly"
+    elif "4." in copsfreq:
+        copsfreq = "4. I viewed pornography multiple times a week"
+    elif "5." in copsfreq:
+        copsfreq = "5. I viewed pornography daily"
+    elif "6." in copsfreq:
+        copsfreq = "6. I viewed pornography multiple times a day"
+
+    copsfreq = np.nan if copsfreq == "" else copsfreq
     df["COPS_Frequency_2"] = copsfreq
 
[…]

### 2025-03-14 study2/analysis/0_preprocessing.py
updated cleaning data

@@ -381,17 +381,19 @@ for i, file in enumerate(files):
         df["Eyetracking_Validation1_Min"] = np.min(calib[-2])
         # The average x and y distance from each validation point, plus the median
         # distance r of the points from this average offset.
-        df["Eyetracking_Validation1_Distance"] = np.mean([g["r"] for g in dist[-2]])
-
-        df["Eyetracking_Validation2_Mean"] = np.mean(calib[-1])
-        df["Eyetracking_Validation2_Max"] = np.max(calib[-1])
-        df["Eyetracking_Validation2_Min"] = np.min(calib[-1])
-
+        
         ## Convert None to NaN 
         dist = [
             [{k: (np.nan if v is None else v) for k, v in d.items()} for d in row]
             for row in dist
             ]
+        #dist = [[np.nan if x is None else x for x in row] for row in dist]
+
+        df["Eyetracking_Validation1_Distance"] = np.mean([g["r"] for g in dist[-2]])
+
+        df["Eyetracking_Validation2_Mean"] = np.mean(calib[-1])
+        df["Eyetracking_Validation2_Max"] = np.max(calib[-1])
+        df["Eyetracking_Validation2_Min"] = np.min(calib[-1])
         
         df["Eyetracking_Validation2_Distance"] = np.mean([g["r"] for g in dist[-1]])
 
@@ -498,7 +500,10 @@ data_demo = replace_value(data_demo, "Discipline", "Other_Geography and Primary 
 data_demo = replace_value(data_demo, "Discipline", "Other_Communications", "Other")
 data_demo = replace_value(data_demo, "Discipline", "Other_education", "Other")
 data_demo = replace_value(data_demo, "Discipline", "Other_Veterinary medicine (behavioural)", "Other")
-
+data_demo = replace_value(data_demo, "Discipline", "Other_policing", "Other")
+data_demo = replace_value(data_demo, "Discipline", "Other_Health and Life Sciences", "Other")
+data_demo = replace_value(data_demo, "Discipline", "Other_cognitive behavioural psychotherapy", "Psychology, Neuroscience")
+data_demo = replace_value(data_demo, "Discipline", "Other_Design", "Other")
 
 # data_demo["SexualOrientation"][data_demo["SexualOrientation"].str.contains("Other_").values].values
 data_demo = replace_value(data_demo, "SexualOrientation", "Other_Straight", "Heterosexual")
[…]

### 2025-03-18 paper/manuscript.qmd
added paradigm ppt

@@
 
-<!-- Study 1  -->
+```{r}
+#| label: setup
+#| include: false
+library(conflicted)
+library(tidyverse)
+library(flextable)
+library(ftExtra)
+library(officer)
+library(knitr)
 
-<!-- Study 2 -->
+conflicts_prefer(dplyr::filter, .quiet = TRUE)
+conflicts_prefer(flextable::separate_header, .quiet = TRUE)
+```
+
+```{r, echo = FALSE, warning=FALSE, message=FALSE}
+# options and parameters
+options(digits = 3)
+
+knitr::opts_chunk$set(
+    collapse = TRUE,
+    dpi = 450,
+    fig.width = see::golden_ratio(9),
+    fig.height = 9,
+    fig.path = "images/"
+)
+
+cache <- TRUE
+```
+
+# Study 1
+
+## Methods
+
+**Participants**
+
+**Materials**
+
+**Procedure**
+
+```{r}
+#| message: false
+#| warning: false
+
+knitr::include_graphics("images/Paradigm.png")
+```
+
+**Ethics**
+
+**Data Analysis**
+
+# Study 2
+
+## Methods
+
+**Participants**
+
+**Materials**
+
+**Procedure**
+
+**Ethics**
+
+**Data Analysis**

### 2025-03-18 study2/analysis/1_cleaning.qmd
minor
analysis scripts updated

@@
   geom_bar() +
+  scale_x_continuous(n.breaks = 6) +
   labs(x="Confidence (0-5)", y = "Number of Participants", title = "Confidence on the authenticity of the images") +
@@
 data.frame(Comments = df$Feedback_Text) |>
-  filter(!tolower(Comments) %in% c(NA, "no", "no comments", "nothing", "none", "", "no.")) |> 
+  filter(!tolower(Comments) %in% c(NA, "no", "no comments", "nothing", "none", "", "no.", "no. ", "n/a", "n/a - thanks", "thanks")) |> 
   gt::gt() |> 
@@
 
-::: {.panel-tabset}
-
 ```{r}
 #| echo: true
-#| code-fold: false
+#| code-fold: true
 
@@
 
+### BAIT Questionnaire Duration
+#
+```{r}
+#| fig-width: 15
+#| fig-height: 15
+
+df |>
+  mutate(Participant = fct_reorder(Participant, Bait_Duration),
+         Category = ifelse(Bait_Duration > 5, "extra", "ok"),
+         Duration = ifelse(Bait_Duration > 5, 5, Bait_Duration),
+         Group = ifelse(Participant %in% outliers, "Outlier", "ok")) |>
+  ggplot(aes(y = Participant, x = Duration)) +
+  geom_point(aes(color = Group, shape = Category)) +
+  geom_vline(xintercept = median(df$Bait_Duration), color = "red", linetype = "dashed") +
+  geom_vline(xintercept = 0.5, color = "orange", linetype = "dotted") +
+  scale_shape_manual(values = c("extra" = 3, ok = 19)) +
+  scale_color_manual(values = c("Outlier" = "red", ok = "black"), guide="none") +
+  guides(color = "none", shape = "none") +
+  ggside::geom_xsidedensity(fill = "#9C27B0", color=NA) +
+  ggside::scale_xsidey_continuous(expand = c(0, 0)) +
+  labs(
+    title = "Questionnaire Completion Time",
+    x = "Duration (in minutes)",
+    y = "Participant"
+  )  +
+  theme_modern() +
+  ggside::theme_ggside_void() +
+  theme(ggside.panel.scale = .3,
+        panel.border = element_blank(),
+        axis.ticks.y = element_blank(),
+          axis.text.y = element_blank())
+
+outliers$bait_duration <- filter(df, Bait_Duration < 0.5)$Participant
+df[df$Participant %in% outliers$bait_duration, str_detect(names(df), "BAIT_\\d+")] <- NA
+```
+
+`r length(outliers$bait_duration)` participants completed the questionnaire in less than 30 seconds.
+
+### Response to Erotic Stimuli
+
+```{r}
+# Single arousal response (0)
+outliers$novariability <- summarize(dftask, n = length(unique(Arousal)), .by="Participant") |> 
+  filter(n == 1) |> 
+  select(Participant) |> 
+  pull()
+
+df <- filter(df, !Participant %in% outliers$novariability)
+dftask <- filter(dftask, !Participant %in% outliers$novariability)
+```
+
+`r length(outliers$novariability)` participants showed no variation in their arousal response (did not move the scales).
+
 ### Response Coherence
@@
 
-`r length(outliers$arousal)` participant had a negative correlation between arousal and enticement, and had a negative correlation between arousal and valance.
+`r length(outliers$arousal)` participant had a negative correlation between arousal and enticement, AND had a negative correlation between arousal and valance.
 
 ```{r}
-
+df <- filter(df, !Participant %in% outliers$arousal)
+dftask <- filter(dftask, !Participant %in% outliers$arousal)
 ```
-
-:::
 
@@
 p_edu <- df |>
-  mutate(Education = fct_relevel(Education, "Other", "High School", "Bachelor", "Master", "Doctorate")) |> 
+  mutate(Education = fct_relevel(Education, "High school", "Bachelor", "Master", "Doctorate", "Other"))|> 
   ggplot(aes(x = Education)) +
@@
 :::
+
+## Save
+
+```{r}
+#| code-fold: false
+
+# setdiff(unique(df$Participant), unique(dftask$Participant))
+write.csv(df, "../data/data_participants.csv", row.names = FALSE)
+write.csv(dftask, "../data/data.csv", row.names = FALSE)
+```

### 2025-03-18 study2/analysis/2_emotion.qmd
analysis scripts updated

@@
 dfsub <- read.csv("../data/data_participants.csv")
+
 df <- read.csv("../data/data.csv") |> 
   right_join(
-    select(dfsub, Participant, Mobile, starts_with(c("Feedback_","BAIT")), COPS_Frequency_2, GenderualActivity,
+    select(dfsub, Participant, Mobile, starts_with(c("Feedback_","BAIT")), COPS_Frequency_2, SexualActivity,
            -Feedback_Text),
@@
     ) |> 
-  mutate(Condition = fct_relevel(Condition, "Reality", "Fiction"),
-         Gender =  fct_relevel(Gender, "Male", "Female", "Other"),
-         PornFrequency = as.numeric(as.factor(COPS_Frequency_2)),
-         GenderualActivity_num = as.numeric(as.factor(GenderualActivity)),
-         ConditionBelief = case_when(
-           Condition == "Reality" & Realness > 0.5 ~ "True",
-           Condition == "AI-Fiction" & Realness < 0.5 ~ "True",
-           .default = "False",
-         )) |> 
   mutate(Condition = case_when(
@@
     Condition == "Reality" ~ "Photograph"
+  )) |>
+  mutate(Condition = fct_relevel(Condition, "Photograph", "AI-Generated"),
+         Gender =  fct_relevel(Gender, "Male", "Female", "Other"),
+         PornFrequency = as.numeric(as.factor(COPS_Frequency_2)),
+         GenderualActivity_num = as.numeric(as.factor(SexualActivity)),
+         ConditionBelief = case_when(
+           Condition == "Photograph" & Realness > 0 ~ "True",
+           Condition == "AI-Generated" & Realness < 0 ~ "True",
+           .default = "False",
          )) |>
@@
 
-**Note to dom** beta model does not make sense anymore, what else should we do?
-
 ::: panel-tabset
@@
 ### Arousal
+
+Arousal ratings were relatively well-distributed across the scale, with the highest frequency for "Not at all" and a gradual decrease across higher ratings.
+
+The pattern of arousal ratings was similar regardless of whether participants believed the images were AI-generated or real.
+Among male participants, arousal ratings were relatively evenly distributed but tended to cluster around the middle of the scale, independent of their belief about the images' origin.
+Female participants, on the other hand, showed a pronounced peak at the lowest arousal rating, irrespective of their perception of the images as AI-generated.
+Participants with other gender identities provided fewer responses overall, but their arousal ratings generally leaned toward moderate levels, particularly in the "Not Believed" condition.
 
@@
 
-# the model with participants and stimuli as random effecs seems to be the best
+# the model with participants only as random effecs seems to be the best
 ```
 
-This model evaluate ths the effects of Gender on Arousal, accounting for random variability due to participants and the stimuli (i.e., random effects).
-
+This model evaluate ths the effects of Gender on Arousal, accounting for random variability due to participants (i.e., random effects).
 The analysis revealed that on average **women rate erotic stimuli significantly lower in arousal than men**, while participants identifying as 'other' rate on average erotic stimuli higher than men, however this is not significant.
@@
 ```{r}
-m_a <- glmmTMB::glmmTMB(Arousal ~ Gender + (1|Participant) + (1|Stimulus ),
-                      data=df,
+m_a <- glmmTMB::glmmTMB(Arousal ~ Gender + (1|Participant),
+                      data=df, family=glmmTMB::ordbeta(),
                       control = glmmTMB::glmmTMBControl(parallel = 8))
@@
 
+Enticement ratings were relatively well-distributed across the scale.
+
+Male participants predominantly provided responses in the mid-to-high enticement range across both conditions.
+Female participants showed a pronounced peak at the lowest enticement rating when they did not believe the image was AI-generated, with a similar but less pronounced pattern in the believed condition.
+Participants identifying as 'Other' responses were more concentrated around the middle of the scale.
+
 ```{r}
-valence <- df |> 
+enticement <- df |> 
   ggplot(aes(x=Enticing)) +
@@
   scale_x_continuous(breaks = (0:6), labels = c("Not at all", "1", "2", "3", "4", "5", "Very much")) +
-  labs(title = "Valence") +
+  labs(title = "Enticement") +
   theme_abyss() +
@@
 
-valence
+enticement
 ```
@@
 ```{r}
-m_e <- glmmTMB::glmmTMB(Enticing ~ Gender + (1|Participant) + (1|Stimulus ),
+m_e <- glmmTMB::glmmTMB(Enticing ~ Gender + (1|Participant),
                       data=df,
@@
 ### Valence
+
+Valence ratings were concetrated more around the mid-to-high valence.
+
+Participants showed the same pattern of results regardless of whether they believed the images to be Ai-generated or not. 
+Males tended to to have the majority of their responses concentrated in the mid-to-high valence range. Female majoity valence ratings were on on the lower (0) and midle end of the scale (3/4).
 
@@
 
-The analysis revealed that on average **women rate erotic stimuli significantly lower in arousal than men**, while participants identifying as 'other' rate on average erotic stimuli higher than men,.
-None of these differences were statistically significant.
+The analysis revealed that on average **women rate erotic stimuli significantly lower in valence than men**, while participants identifying as 'other' rate on average erotic stimuli higher in valence than men but these was not statistically significant.
 
 ```{r}
-m_v <- glmmTMB::glmmTMB(Valence ~ Gender + (1|Participant) + (1|Stimulus ),
+m_v <- glmmTMB::glmmTMB(Valence ~ Gender + (1|Participant),
                       data=df,
@@
 ## Arousal
+
+In contrast to [study1](https://realitybending.github.io/FictionEro/study1/analysis/2_emotions.html) arousal ratings differ by whether the images were preceeded by 'photograph' or by 'ai-generated'.
 
@@
 
+This model examines the effect of Gender and condition on Arousal, accounting for random variability due to participants and items (i.e., random effects).
+
+<!-- The intercept is Male and photograph.  -->
+Women rated 'photographs' significantly lower in arousal than men.
+Men rated 'photographs' significantly higher in arousal than 'AI-generated' images.
+
 ```{r}
 
+m_arousal <- glmmTMB::glmmTMB(Arousal ~ Gender/ Condition + 
+                                (1| Participant) + (1|Stimulus), data=df, control = glmmTMB::glmmTMBControl(parallel = 8))
+
+results_table(m_arousal)
+
+# marginaleffects::avg_slopes(m_arousal, variables="Condition", by="Gender", re.form=NA) |> 
+#   results_table()
+
 ```

### 2025-03-21 study2/analysis/1_cleaning.qmd
removed other + minor changes to scripts

@@
 
+Only `r sum(df$Gender=="Other")` participants self-reported as neither female nor male, hence they were excluded from further analysis.
+
 ```{r}
+df<- filter(df, !Gender=="Other")
 df <- filter(df, !Participant %in% outliers$arousal)

### 2025-03-21 study2/analysis/2_emotion.qmd
removed other + minor changes to scripts

@@
 ```{r}
+#| warning: false
+#| 
 dfsub <- read.csv("../data/data_participants.csv")
@@
 }
+
+## re-scaled variables
+scale_values <- function(x){(x-min(x))/(max(x)-min(x))}
+
+df$Arousal <- scale_values(df$Arousal)
+df$Enticing <- scale_values(df$Enticing)
+df$Valence <- scale_values(df$Valence)
 ```
@@
 This section is about selecting the best model. Notably, all the stimuli presented are of an erotic nature.
+Note that variables were rescaled to [0,1] when fitting the models and that the stimuli presented to participants was assigned according to their self-rated sexuality, making all stimuli relevant to participants.
+
+To summarise, women rate stimuli on average significantly lower in arousal, enticiment and valence than men.
 
@@
   ggplot(aes(x=Arousal)) +
-  geom_histogram(fill="grey", position = "identity", binwidth = 0.5) +
+  geom_bar(fill="#03A9F4") +
   scale_y_sqrt(expand = c(0, 0)) +
-  scale_x_continuous(breaks = (0:6), labels = c("Not at all", "1", "2", "3", "4", "5", "Very much")) +
-  labs(title = "Arousal") +
+  labs(title = "Arousal", ) +
   theme_abyss() +
@@
   ggplot(aes(x=Arousal, fill=Gender)) +
-  geom_histogram(position = "identity", binwidth = 0.5) +
+  geom_bar(position = "identity") +
   facet_grid(Gender~ConditionBelief, scales="free_y") +
   scale_color_manual(values=c("red", "white"), guide="none") +
-  scale_fill_manual(values=c("Female"="#E91E63", "Male"="#FF9800", "Other" = "#03A9F4"), guide="none") +
+  scale_fill_manual(values=c("Female"="#E91E63", "Male"="#FF9800"), guide="none") +
   # scale_y_sqrt(expand = c(0, 0)) +
@@
 
-test_bf(m1,m2)
+test_bf(m1,m2, m3)
 compare_performance(m1, m2)
@@
 This model evaluate ths the effects of Gender on Arousal, accounting for random variability due to participants (i.e., random effects).
-The analysis revealed that on average **women rate erotic stimuli significantly lower in arousal than men**, while participants identifying as 'other' rate on average erotic stimuli higher than men, however this is not significant.
+The analysis revealed that on average **women rate erotic stimuli significantly lower in arousal than men**.
 
 ```{r}
+
 m_a <- glmmTMB::glmmTMB(Arousal ~ Gender + (1|Participant),
@@
   geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color = Gender), position=position_dodge(width=0.5)) +
- scale_color_manual(values=c("Male"="#E91E63", "Female"="#FF9800","Other"="#03A9F4"), guide="none") +  labs(y="Arousal") +
+ scale_color_manual(values=c("Male"="#E91E63", "Female"="#FF9800"), guide="none") +  labs(y="Arousal") +
   theme_abyss()
@@
 ```{r}
-enticement <- df |> 
+enticiment <- df |> 
   ggplot(aes(x=Enticing)) +
-  geom_histogram(fill="grey", position = "identity", binwidth = 0.5) +
+  geom_bar(fill="#03A9F4") +
   scale_y_sqrt(expand = c(0, 0)) +
-  scale_x_continuous(breaks = (0:6), labels = c("Not at all", "1", "2", "3", "4", "5", "Very much")) +
-  labs(title = "Enticement") +
+  labs(title = "Enticement", ) +
   theme_abyss() +
-  theme(plot.title = element_text(hjust = 0.5, face="bold"),
-        legend.position = "none")
+  theme(plot.title = element_text(hjust = 0.5, face="bold"))
 
-enticement
+enticiment
 ```
@@
   ggplot(aes(x=Enticing, fill=Gender)) +
-  geom_histogram(position = "identity", binwidth = 0.5) +
+  geom_bar(position = "identity", binwidth = 0.5) +
   facet_grid(Gender~ConditionBelief, scales="free_y") +
   scale_color_manual(values=c("red", "white"), guide="none") +
-  scale_fill_manual(values=c("Female"="#E91E63", "Male"="#FF9800", "Other" = "#03A9F4"), guide="none") +
+  scale_fill_manual(values=c("Female"="#E91E63", "Male"="#FF9800"), guide="none") +
   # scale_y_sqrt(expand = c(0, 0)) +
@@
 
-The analysis revealed that on average **women rate erotic stimuli significantly lower in enticiment than men**, while participants identifying as 'other' rate on average erotic stimuli higher than men.
-However, these differences were not statistically significant.
+The analysis revealed that on average **women rate erotic stimuli significantly lower in enticiment than men**.
 
@@
 m_e <- glmmTMB::glmmTMB(Enticing ~ Gender + (1|Participant),
-                      data=df,
+                      data=df,family=glmmTMB::ordbeta(),
                       control = glmmTMB::glmmTMBControl(parallel = 8))
@@
   ggplot(aes(x=Valence)) +
-  geom_histogram(fill="grey", position = "identity", binwidth = 0.5) +
+  geom_bar(fill="#03A9F4") +
   scale_y_sqrt(expand = c(0, 0)) +
-  scale_x_continuous(breaks = (0:6), labels = c("Unpleasant", "1", "2", "3", "4", "5", "Pleasant")) +
-  labs(title = "Valence") +
+  labs(title = "Valence", ) +
   theme_abyss() +
-  theme(plot.title = element_text(hjust = 0.5, face="bold"),
-        legend.position = "none")
+  theme(plot.title = element_text(hjust = 0.5, face="bold"))
 
@@
   ggplot(aes(x=Valence, fill=Gender)) +
-  geom_histogram(position = "identity", binwidth = 0.5) +
+  geom_bar(position = "identity", binwidth = 0.5) +
   facet_grid(Gender~ConditionBelief, scales="free_y") +
   scale_color_manual(values=c("red", "white"), guide="none") +
-  scale_fill_manual(values=c("Female"="#E91E63", "Male"="#FF9800", "Other" = "#03A9F4"), guide="none") +
+  scale_fill_manual(values=c("Female"="#E91E63", "Male"="#FF9800"), guide="none") +
   # scale_y_sqrt(expand = c(0, 0)) +
@@
 
-The analysis revealed that on average **women rate erotic stimuli significantly lower in valence than men**, while participants identifying as 'other' rate on average erotic stimuli higher in valence than men but these was not statistically significant.
+The analysis revealed that on average **women rate erotic stimuli significantly lower in valence than men**.
 
 ```{r}
-m_v <- glmmTMB::glmmTMB(Valence ~ Gender + (1|Participant),
+m_v <- glmmTMB::glmmTMB(Valence ~ Gender + (1|Participant), family=glmmTMB::ordbeta(),
                       data=df,
@@
 m_arousal <- glmmTMB::glmmTMB(Arousal ~ Gender/ Condition + 
-                                (1| Participant) + (1|Stimulus), data=df, control = glmmTMB::glmmTMBControl(parallel = 8))
+                                (1| Participant) + (1|Stimulus), family=glmmTMB::ordbeta(),
+                              data=df, control = glmmTMB::glmmTMBControl(parallel = 8))
 
@@
 
-# marginaleffects::avg_slopes(m_arousal, variables="Condition", by="Gender", re.form=NA) |> 
+# marginaleffects::avg_slopes(m_arousal, variables="Condition", by="Gender") |>
 #   results_table()
@@
 ```
+
+### Moderators
+
+This model explores whether various factors such as **attitudes towards AI, knowledge about AI, frequency of porn consumption, and sexual activity** moderate the relationship between gender, image relevance (specifically AI-generated versus photographs), and arousal ratings.
+
+```{r}
+test_moderator <- function(df, outcome="Arousal", moderator="Bait_Visual") {
+  f <- paste0(outcome, " ~ Gender / (Condition * ", moderator, ") + (Condition | Participant) + (1|Stimulus)")
+  r <- glmmTMB::glmmTMB(as.formula(f),
+                      data = df,
+                      family=glmmTMB::ordbeta(),
+                      control = glmmTMB::glmmTMBControl(parallel = 8)) |>
+    parameters::parameters() |> 
+    as.data.frame() |> 
+    select(-df_error, -Effects, -Group, -Component, -SE)
+  r$Moderator <- moderator
+  r$Outcome <- outcome
+  insight::format_table(r[c(7, 8), ])
+}
+
+moderator_results <- data.frame()
+for(m in c("BAIT_VideosRealistic", "BAIT_TextRealistic", "BAIT_ExpertAI", "PornFrequency", "SexualActivity")) {
+  moderator_results <- rbind(moderator_results,
+                             test_moderator(df, "Arousal", m))
+}
+
+display(moderator_results)
+```
+
+```{r}
+feedback_results <- data.frame()
+for(m in c("Feedback_NoFacesAttractive", "Feedback_SomeFacesAttractive", "Feedback_AIMoreAttractive", 
+           "Feedback_AILessAttractive", "Feedback_DiffObvious", "Feedback_DiffSubtle", "Feedback_DiffNone" ,
+           "Feedback_LabelsIncorrect", "Feedback_LabelsReversed", "Feedback_AllReal", "Feedback_AllFake",
+           "Feedback_AllRealConfidence", "Feedback_AllFakeConfidence" ,  "Feedback_Enjoyment")){ 
+  feedback_results <- rbind(feedback_results,
+                            test_moderator(df, "Arousal", m))
+}
+display(feedback_results)
+```

### 2025-04-30 study2/analysis/2_emotion.qmd
updated script

@@
   right_join(
-    select(dfsub, Participant, Mobile, starts_with(c("Feedback_","BAIT")), COPS_Frequency_2, SexualActivity,
+    select(dfsub, Participant, Mobile, starts_with(c("Feedback_","BAIT")), COPS_Frequency, SexualActivity, BAIT_Worry, BAIT_Dangerous, 
            -Feedback_Text),
@@
   mutate(Condition = fct_relevel(Condition, "Photograph", "AI-Generated"),
-         Gender =  fct_relevel(Gender, "Male", "Female", "Other"),
-         PornFrequency = as.numeric(as.factor(COPS_Frequency_2)),
-         GenderualActivity_num = as.numeric(as.factor(SexualActivity)),
+         Gender =  fct_relevel(Gender, "Male", "Female"),
+         PornFrequency = as.numeric(as.factor(COPS_Frequency)),
+         SexurualActivity_num = as.numeric(as.factor(SexualActivity)),
          ConditionBelief = case_when(
@@
 df$Valence <- scale_values(df$Valence)
+```
+
+**Note**: [These calculations are based on the validation of the BAIT scale](https://realitybending.github.io/FictionEro/study1/analysis/1_cleaning.html)
+
+```{r}
+
+bait <- df |> 
+  select(starts_with("BAIT_"), -Bait_Duration) |> 
+  rename_with(function(x) gsub("BAIT_\\d_", "", x)) |> 
+  filter(!is.na(BAIT_TextRealistic ))
+
+raw_scores <- data.frame(
+  Participant = df[!is.na(df$BAIT_ImagesRealistic), ]$Participant,
+  BAIT_Videos = (bait$BAIT_VideosRealistic + (1 - bait$BAIT_VideosIssues)) / 2,
+  BAIT_Visual = (bait$BAIT_ImagesRealistic + (1 - bait$BAIT_ImagesIssues) + bait$BAIT_ImitatingReality + bait$BAIT_EnvironmentReal) / 4,
+  BAIT_Text = (bait$BAIT_TextRealistic + (1 - bait$BAIT_TextIssues)) / 2
+  )
+
+df <- merge(df, raw_scores, by="Participant")
 ```
@@
 ```{r}
-estimate_relation(m_e) |> 
+estimate_relation(m_v) |> 
   ggplot(aes(x=Gender, y=Predicted)) +
@@
 ```{r}
-test_moderator <- function(df, outcome="Arousal", moderator="Bait_Visual") {
+test_moderator <- function(df, outcome="Arousal", moderator="BAIT_Visual") {
   f <- paste0(outcome, " ~ Gender / (Condition * ", moderator, ") + (Condition | Participant) + (1|Stimulus)")
@@
 moderator_results <- data.frame()
-for(m in c("BAIT_VideosRealistic", "BAIT_TextRealistic", "BAIT_ExpertAI", "PornFrequency", "SexualActivity")) {
+for(m in c("BAIT_Visual", "BAIT_Text", "BAIT_ExpertAI", "PornFrequency", "SexualActivity")) {
   moderator_results <- rbind(moderator_results,
@@
 ```
+
+### Believed
+
+```{r}
+  m <- glmmTMB::glmmTMB(Arousal ~ Sex / Condition + (1|Participant) + (1|Item),
+                        data=filter(df, ConditionBelief == "True"), 
+                        family=glmmTMB::ordbeta(),
+                        control = glmmTMB::glmmTMBControl(parallel = 8))
+
+  results_table(m)
+```
+
+```{r}
+
+ moderator_believed <- data.frame()
+  for(m in c("BAIT_Visual", "BAIT_Text", "AI_Knowledge",
+             "GAAIS_Positive", "GAAIS_Negative",
+             "Porn", "PornFrequency", "SexualActivity_num", 
+             "Feedback_CouldDiscriminate", "Feedback_CouldNotDiscriminate",
+             "Feedback_AIMoreArousing", "Feedback_AILessArousing", 
+             "Feedback_LabelsIncorrect", "Feedback_LabelsReversed")) {
+    moderator_believed <- rbind(moderator_believed,
+                               test_moderator(filter(df, ConditionBelief == "True"), "Arousal", m))
+  }
+
+  display(filter(moderator_believed, p < .1))
+
+```

### 2025-05-02 study1/analysis/2_emotions.qmd
updated analysis scripts and data

@@
 
-This model examines how Sex, Relevance, and Condition influence Valence ratings, treating relevance within each participant and items as random effects.
+This model examines how Sex, Relevance, and Condition influence Enticement ratings, treating relevance within each participant and items as random effects.
 

### 2025-05-02 study2/analysis/1_cleaning.qmd
updated analysis scripts and data

@@
 
+### Old vs New feedback
+
+Due to a mistake in the study's implementation, some of the feedback was incorrect, e.g., "Some faces were attractive" and "AI-generated faces were less attractive" rather than "Some images were arousing" and "AI-generated images were less arousing".
+
+```{r}
+
+table(df$version)
+
+```
+
 ### Proportion
@@
          Question = str_replace(Question, "AIMoreAttractive", "AI = More attractive"),
+         Question = str_replace(Question, "SomeImagesArousing", "Some images were arousing"),
+         Question = str_replace(Question, "NoImagesArousing", "No images were arousing"),
+         Question = str_replace(Question, "AILessArousing", "AI = Less arousing"),
+         Question = str_replace(Question, "AIMoreArousing", "AI = More arousing"),
          # Question = str_replace(Question, "DiffSubtle", "Subtle differences between AI images and photos"),

### 2025-05-02 study2/analysis/2_emotion.qmd
updated analysis scripts and data

@@
   right_join(
-    select(dfsub, Participant, Mobile, starts_with(c("Feedback_","BAIT")), COPS_Frequency, SexualActivity, BAIT_Worry, BAIT_Dangerous, 
-           -Feedback_Text),
+    select(dfsub, Participant, Mobile, starts_with(c("Feedback_","BAIT")), COPS_Frequency, SexualActivity,- Feedback_Text),
     by = "Participant"
@@
          )) |>
-  mutate(across(starts_with("Feedback_")& !matches("Feedback_AllRealConfidence|Feedback_AllFakeConfidence|Feedback_Enjoyment"), function(x) {fct_relevel(x, "False", "True")}))
+  rename(AllRealConfidence = "Feedback_AllRealConfidence",
+         AllFakeConfidence = "Feedback_AllFakeConfidence",
+         Enjoyment = "Feedback_Enjoyment"
+         )|>
+  mutate(across(starts_with("Feedback_"), as.factor))
 
@@
 
-bait <- df |> 
-  select(starts_with("BAIT_"), -Bait_Duration) |> 
-  rename_with(function(x) gsub("BAIT_\\d_", "", x)) |> 
-  filter(!is.na(BAIT_TextRealistic ))
+df$BAIT_Videos <- (df$BAIT_VideosRealistic + (1 - df$BAIT_VideosIssues)) / 2
 
-raw_scores <- data.frame(
-  Participant = df[!is.na(df$BAIT_ImagesRealistic), ]$Participant,
-  BAIT_Videos = (bait$BAIT_VideosRealistic + (1 - bait$BAIT_VideosIssues)) / 2,
-  BAIT_Visual = (bait$BAIT_ImagesRealistic + (1 - bait$BAIT_ImagesIssues) + bait$BAIT_ImitatingReality + bait$BAIT_EnvironmentReal) / 4,
-  BAIT_Text = (bait$BAIT_TextRealistic + (1 - bait$BAIT_TextIssues)) / 2
-  )
+df$BAIT_Visual = (df$BAIT_ImagesRealistic + (1 - df$BAIT_ImagesIssues) + df$BAIT_ImitatingReality + df$BAIT_EnvironmentReal) / 4
 
-df <- merge(df, raw_scores, by="Participant")
+df$BAIT_Text = (df$BAIT_TextRealistic + (1 - df$BAIT_TextIssues)) / 2
+
+df$BAIT_Negative <- (df$BAIT_Worry + df$BAIT_Dangerous)/2
+
+df$BAIT_Positive <- (df$BAIT_Exciting + df$BAIT_Benefit)/2
 ```
@@
 
+The analysis also examined the average marginal effect of the variable "Condition" (comparing AI-Generated to Photograph) separately for males and females.
+For males, the arousal is on average significantly lower (althoug only slighly) for AI-Generated images compared to Photograph images.
+For females, the arousal is on average slightly lower for AI-Generated images compared to Photograph images; however, this effect is not significant.
+
 ```{r}
@@
 
-# marginaleffects::avg_slopes(m_arousal, variables="Condition", by="Gender") |>
+marginaleffects::avg_slopes(m_arousal, variables="Condition", by="Gender") 
 #   results_table()
@@
 This model explores whether various factors such as **attitudes towards AI, knowledge about AI, frequency of porn consumption, and sexual activity** moderate the relationship between gender, image relevance (specifically AI-generated versus photographs), and arousal ratings.
+
+The analysis revealed a significant interaction effect only for **positive attitudes towards AI** among females.
+Specifically, females with higher positive attitudes towards AI rated AI-generated images as more arousing, relative to when they viewed photographs
+
+No other moderators showed statistically significant effects on arousal across the interactions of gender, condition (Ai-generated vs Photograph), and the respective moderators.
+
+We also examined whether **feedback** moderates the relationship between gender and condition on arousal.
+Findings suggest that feedback moderates this relationship only for men.
+Specifically, males who reported finding AI-generated images as less and more arousing had lower and higher, respectively, arousal ratings for those images.
+
+<!-- All significant findings for feedback  -->
+
+<!-- 1.For Males, giving feedback indicating that AI-generated images were less attractive, influenced arousal ratings for images labeled as AI-generated.
+Specifically, males who reported finding AI-generated images as less arousing had lower arousal ratings for those images.
+
+<!-- 2.
+For Males, giving feedback indicating that AI-generated images were more attractive significantly influenced arousal ratings for images labeled as AI-generated.
+Specifically, males who reported finding AI-generated images more attractive had higher arousal ratings for these images.
+-->
+
+<!-- Note: The feedback that the difference between the conditions was subtle only had one value - i.e., False.
+The feedback that some AI images were arousing and that no AI images were arousing also only had one value - i.e., False -->
 
@@
 moderator_results <- data.frame()
-for(m in c("BAIT_Visual", "BAIT_Text", "BAIT_ExpertAI", "PornFrequency", "SexualActivity")) {
+for(m in c("BAIT_Visual", "BAIT_Text", "BAIT_ExpertAI", "BAIT_Positive", "BAIT_Negative", "PornFrequency", "SexualActivity")) {
   moderator_results <- rbind(moderator_results,
@@
 feedback_results <- data.frame()
-for(m in c("Feedback_NoFacesAttractive", "Feedback_SomeFacesAttractive", "Feedback_AIMoreAttractive", 
-           "Feedback_AILessAttractive", "Feedback_DiffObvious", "Feedback_DiffSubtle", "Feedback_DiffNone" ,
-           "Feedback_LabelsIncorrect", "Feedback_LabelsReversed", "Feedback_AllReal", "Feedback_AllFake",
-           "Feedback_AllRealConfidence", "Feedback_AllFakeConfidence" ,  "Feedback_Enjoyment")){ 
+for(m in c("Feedback_NoFacesAttractive", "Feedback_SomeFacesAttractive", "Feedback_AIMoreAttractive", "Feedback_AILessAttractive", "Feedback_DiffObvious", "Feedback_DiffNone" ,
+           "Feedback_LabelsIncorrect", "Feedback_LabelsReversed", "Feedback_AllReal", "Feedback_AllFake", "AllRealConfidence", "AllFakeConfidence" ,  "Enjoyment",
+
+           ## New feedback
+           "Feedback_AIMoreArousing", "Feedback_AILessArousing"
+
+           )){ 
   feedback_results <- rbind(feedback_results,
@@
 
+<!-- To DO -->
+
 ```{r}
-  m <- glmmTMB::glmmTMB(Arousal ~ Sex / Condition + (1|Participant) + (1|Item),
+  m <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition + (1|Participant) + (1|Stimulus),
                         data=filter(df, ConditionBelief == "True"), 
@@
  moderator_believed <- data.frame()
-  for(m in c("BAIT_Visual", "BAIT_Text", "AI_Knowledge",
-             "GAAIS_Positive", "GAAIS_Negative",
-             "Porn", "PornFrequency", "SexualActivity_num", 
+  for(m in c("BAIT_Visual", "BAIT_Text", "BAIT_ExpertAI",
+             "BAIT_Positive", "BAIT_Negative",
+             "PornFrequency", "SexualActivity", 
              "Feedback_CouldDiscriminate", "Feedback_CouldNotDiscriminate",
              "Feedback_AIMoreArousing", "Feedback_AILessArousing", 
+             "Feedback_AIMoreAttractive", "Feedback_AILessAttractive",
              "Feedback_LabelsIncorrect", "Feedback_LabelsReversed")) {
@@
 ```
+
+## Enticement
+
+Enticment ratings differ by whether the images were preceeded by 'photograph' or by 'ai-generated'.
+
+```{r}
+#| fig-height: 12
+#| fig-width: 7
+
+enticement_desc <- plot_descriptive(df, "Enticing")
+enticement_desc
+```
+
+### Whole Sample
+
+This model examines how Gender and Condition influence enticement ratings, treating participant and items as random effects.
+
+<!-- Key Findings: -->
+
+There was a significant interaction between gender and image condition, whereby men were less enticed by AI-generated images, whereas women showed no significant difference in enticement based on image condition.
+Across both conditions, women rated the images as less enticing overall than men.
+
+We also analyzed the average marginal effect of the variable “Condition” (comparing AI-Generated to Photograph) separately for males and females.
+
+For males, enticement ratings are significantly lower on average for AI-Generated images compared to Photograph images.
+For females, enticement ratings are slightly lower on average for AI-Generated images compared to Photograph images, although this difference is not statistically significant.
+
+**Note**. 'Other' was removed due to the very small percentage of individuals identifying as such.
+
+```{r}
+m_enticement <- glmmTMB::glmmTMB(Enticing ~ Gender / Condition + 
+                                   (1 | Participant) + (1|Stimulus),
+                      data=df, family=glmmTMB::ordbeta(),
+                      control = glmmTMB::glmmTMBControl(parallel = 8))
+
+results_table(m_enticement)
+
+marginaleffects::avg_slopes(m_enticement, variables="Condition", by="Gender", re.form=NA)
+```
+
+### Moderators
+
+We examined whether **attitudes towards AI, porn frequency, and sexual activity** moderated the relationship between the predictors (sex, relevance, condition) and enticement ratings.
+
+Looking at **feedback as a moderator**, the results showed that enticement ratings for images labeled AI-generated were moderated by the feedback reporting attitudes towards AI, but this was only significant for women.
+Specifically, women who reported that having more positive and negative attitudes towards AI, rated these images higher, and lower, in enticement compared to images labeled as photographs.
+
+```{r}
+for(m in c("BAIT_Visual", "BAIT_Text", "BAIT_ExpertAI",
+           "BAIT_Positive", "BAIT_Negative",
+           "PornFrequency", "SexualActivity")) {
+  moderator_results <- rbind(moderator_results,
+                             test_moderator(df, "Enticing", m))
+}
+
+display(filter(moderator_results, Outcome == "Enticing"))
+```
+
+```{r}
+for(m in c("Feedback_CouldDiscriminate", "Feedback_CouldNotDiscriminate",
+           "Feedback_AIMoreArousing", "Feedback_AILessArousing",
+           "Feedback_AIMoreAttractive", "Feedback_LessArousing",
+           "Feedback_LabelsIncorrect", "Feedback_LabelsReversed")) {
+  feedback_results <- rbind(feedback_results,
+                            test_moderator(df, "Enticing", m))
+}
+display(filter(feedback_results, Outcome == "Enticing"))
+```
+
+```{r}
+m <- glmmTMB::glmmTMB(Enticing ~ Gender / (Condition * SexualActivity) + (Condition | Participant) + (1|Stimulus),
+                      data=filter(df, ConditionBelief == "True"), 
+                      family=glmmTMB::ordbeta(),
+                      control = glmmTMB::glmmTMBControl(parallel = 8))
+
+results_table(m)
+
+sex_act_plot<- estimate_relation(m, length=20) |> 
+  ggplot(aes(x=SexualActivity_num, y=Predicted)) +
+  geom_ribbon(aes(ymin=CI_low, ymax=CI_high, fill=Condition), alpha=0.2) +
+  geom_line(aes(color=Condition)) +
+  facet_grid(~Sex)
+
+sex_act_plot
+```

### 2025-05-02 study2/analysis/0_preprocessing.py

@@ -108,6 +108,8 @@ demo_break_df = pd.DataFrame(all_phase1_data)
 data_demo = pd.DataFrame()
 data_task = pd.DataFrame()
 data_eye = pd.DataFrame()
+all_feedback = []  # to collect all feedback given that some participants had the wrong instructions
+
 
 #All other files
 break_files = [file for file in files if file.endswith("_break.csv")] # only files ending in break
@@ -231,7 +233,7 @@ for i, file in enumerate(files):
     sexactivity = np.nan if sexactivity in [""] else sexactivity
     df["SexualActivity"] = sexactivity
     
-    copsfreq = cops.get("COPS_Frequency") or ""  # Ensures None is converted to ""
+    copsfreq = cops.get("COPS_Frequency_2") or ""  # Ensures None is converted to ""
     copsfreq = copsfreq.rstrip()  
 
     if "0." in copsfreq:
@@ -250,7 +252,33 @@ for i, file in enumerate(files):
         copsfreq = "6. I viewed pornography multiple times a day"
 
     copsfreq = np.nan if copsfreq == "" else copsfreq
-    df["COPS_Frequency_2"] = copsfreq
+    df["COPS_Frequency"] = copsfreq
+
+    # check feedback version
+    feedback_df = data[data["screen"] == "fiction_feedback1"].copy()
+
+    def detect_version(response):
+        try:
+            parsed = json.loads(response)
+            response_text = json.dumps(parsed).lower()
+            if "attractive" in response_text:
+                return "old"
+            elif "arousing" in response_text:
+                return "new"
+            else:
+                return "unknown"
+        except Exception:
+            return "error"
+
+    if not feedback_df.empty:
+        feedback_df["Participant"] = filename
+        feedback_df["version"] = feedback_df["response"].apply(detect_version)
+        feedback_df["Datetime"] = df["Datetime"].values[0]  # Add timestamp to each feedback
+        all_feedback.append(feedback_df) 
+
+    # Count how many participants had each version
+    version_counts = feedback_df["version"].value_counts()
+    print(version_counts)
 
     # Feedback -------------------------------------------------------------
     f1 = data[data["screen"] == "fiction_feedback1"].iloc[0]
@@ -260,6 +288,10 @@ for i, file in enumerate(files):
     df["Feedback_SomeFacesAttractive"] = False
     df["Feedback_AIMoreAttractive"] = False
     df["Feedback_AILessAttractive"] = False
[…]

### 2025-05-06 study1/analysis/2_emotions.qmd
finish* 2_emotions qmd
* missing interpretation of believed, a summary and figures

@@
 
-Lastly, the interaction between sexual activity and condition on arousal, suggests that for females, the effect of AI-Generated condition on arousal ratings varies with different levels of sexual activity.
+Lastly, the interaction between sexual activity and condition on enticement, suggests that for females, the effect of AI-Generated condition on enticing ratings varies with different levels of sexual activity.
 

### 2025-05-06 study2/analysis/2_emotion.qmd
finish* 2_emotions qmd
* missing interpretation of believed, a summary and figures

@@
     Condition == "Fiction" ~ "AI-Generated",
-    Condition == "Reality" ~ "Photograph"
+    Condition == "Reality
+    " ~ "Photograph"
   )) |>
@@
          PornFrequency = as.numeric(as.factor(COPS_Frequency)),
-         SexurualActivity_num = as.numeric(as.factor(SexualActivity)),
+         SexualActivity_num = as.numeric(as.factor(SexualActivity)),
          ConditionBelief = case_when(
@@
 
-This model examines the effect of Gender and condition on Arousal, accounting for random variability due to participants and items (i.e., random effects).
+This model examines the effect of **gender and condition on Arousal**, accounting for random variability due to participants and items (i.e., random intercepts).
 
 <!-- The intercept is Male and photograph.  -->
-Women rated 'photographs' significantly lower in arousal than men.
-Men rated 'photographs' significantly higher in arousal than 'AI-generated' images.
+Women rated 'photographs' significantly lower in arousal than men. Men rated 'photographs' significantly higher in arousal than 'AI-generated' images.
 
@@
 
+Lastly, the interaction between sexual activity and condition on Arousal levels.
+The three-way interaction between gender, condition (AI-Generated), and sexual activity did not reach statistical significance for either males or females, suggesting that the relationship between the AI-Generated condition and arousal ratings does not significantly vary with sexual activity levels for either gender.
+
 <!-- All significant findings for feedback  -->
@@
 moderator_results <- data.frame()
-for(m in c("BAIT_Visual", "BAIT_Text", "BAIT_ExpertAI", "BAIT_Positive", "BAIT_Negative", "PornFrequency", "SexualActivity")) {
+for(m in c("BAIT_Visual", "BAIT_Text", "BAIT_ExpertAI", "BAIT_Positive", "BAIT_Negative", "PornFrequency", "SexualActivity_num")) {
   moderator_results <- rbind(moderator_results,
@@
 feedback_results <- data.frame()
-for(m in c("Feedback_NoFacesAttractive", "Feedback_SomeFacesAttractive", "Feedback_AIMoreAttractive", "Feedback_AILessAttractive", "Feedback_DiffObvious", "Feedback_DiffNone" ,
-           "Feedback_LabelsIncorrect", "Feedback_LabelsReversed", "Feedback_AllReal", "Feedback_AllFake", "AllRealConfidence", "AllFakeConfidence" ,  "Enjoyment",
+for(m in c("Feedback_NoFacesAttractive", "Feedback_SomeFacesAttractive",
+           "Feedback_AIMoreAttractive", "Feedback_AILessAttractive",
+           "Feedback_AIMoreArousing", "Feedback_AILessArousing",
 
-           ## New feedback
-           "Feedback_AIMoreArousing", "Feedback_AILessArousing"
+           "Feedback_DiffObvious", "Feedback_DiffNone",
 
-           )){ 
+           "Feedback_LabelsIncorrect", "Feedback_LabelsReversed",
+           "Feedback_AllReal", "Feedback_AllFake",
+
+           "AllRealConfidence","AllFakeConfidence" ,
+           "Enjoyment")) {
   feedback_results <- rbind(feedback_results,
@@
 display(feedback_results)
+
+```
+
+```{r}
+m <- glmmTMB::glmmTMB(Arousal ~ Gender / (Condition * SexualActivity_num) + (Condition | Participant) + (1|Stimulus),
+                      data=filter(df, ConditionBelief == "True"), 
+                      family=glmmTMB::ordbeta(),
+                      control = glmmTMB::glmmTMBControl(parallel = 8))
+
+results_table(m)
+
+sex_act_plot<- estimate_relation(m, length=20) |> 
+  ggplot(aes(x=SexualActivity_num, y=Predicted)) +
+  geom_ribbon(aes(ymin=CI_low, ymax=CI_high, fill=Condition), alpha=0.2) +
+  geom_line(aes(color=Condition)) +
+  facet_grid(~Gender)
+
+sex_act_plot
 ```
@@
 ### Believed
-
-<!-- To DO -->
 
@@
              "PornFrequency", "SexualActivity", 
-             "Feedback_CouldDiscriminate", "Feedback_CouldNotDiscriminate",
+             "Feedback_DiffObvious", "Feedback_DiffNone",
              "Feedback_AIMoreArousing", "Feedback_AILessArousing", 
@@
 
-This model examines how Gender and Condition influence enticement ratings, treating participant and items as random effects.
+This model examines how Gender and Condition influence enticement ratings, treating participant and items as random intercepts.
 
@@
 We examined whether **attitudes towards AI, porn frequency, and sexual activity** moderated the relationship between the predictors (sex, relevance, condition) and enticement ratings.
+The results showed that enticing ratings for images labeled AI-generated were moderated by the feedback reporting attitudes towards AI, but this was only significant for women.
+Specifically, women who reported having more positive attitudes towards AI, rated these images higher in arousal compared to images labeled as photographs.
 
-Looking at **feedback as a moderator**, the results showed that enticement ratings for images labeled AI-generated were moderated by the feedback reporting attitudes towards AI, but this was only significant for women.
-Specifically, women who reported that having more positive and negative attitudes towards AI, rated these images higher, and lower, in enticement compared to images labeled as photographs.
+Looking at **feedback as a moderator**, the results showed that enticement ratings for images labelled as AI-Generated were moderated by the feedback that AI is less Attractive for males, and that difference between the AI-Generated images and real photos is obvious for females.
 
+Lastly, the interaction between sexual activity and condition on enticement, suggests that enticement ratings do not significantly differ with sexual activity levels for either gender.
+
+<!-- Note: Feedback that 'No Images were Arousing' , 'Some Images were Arousing' and the 'difference between real and photos was Subtle' only had 1 level, hence were excluded from the following analysis -->
 ```{r}
@@
 ```{r}
-for(m in c("Feedback_CouldDiscriminate", "Feedback_CouldNotDiscriminate",
+for(m in c("Feedback_NoFacesAttractive", "Feedback_SomeFacesAttractive",
+           "Feedback_AIMoreAttractive", "Feedback_AILessAttractive",
            "Feedback_AIMoreArousing", "Feedback_AILessArousing",
-           "Feedback_AIMoreAttractive", "Feedback_LessArousing",
-           "Feedback_LabelsIncorrect", "Feedback_LabelsReversed")) {
+
+           "Feedback_DiffObvious", "Feedback_DiffNone",
+
+           "Feedback_LabelsIncorrect", "Feedback_LabelsReversed",
+           "Feedback_AllReal", "Feedback_AllFake")) {
   feedback_results <- rbind(feedback_results,
@@
 }
+
 display(filter(feedback_results, Outcome == "Enticing"))
@@
 ```{r}
-m <- glmmTMB::glmmTMB(Enticing ~ Gender / (Condition * SexualActivity) + (Condition | Participant) + (1|Stimulus),
+m <- glmmTMB::glmmTMB(Enticing ~ Gender / (Condition * SexualActivity_num) + (Condition | Participant) + (1|Stimulus),
                       data=filter(df, ConditionBelief == "True"), 
@@
   geom_line(aes(color=Condition)) +
-  facet_grid(~Sex)
+  facet_grid(~Gender)
 
@@
 ```
+
+### Believed
+
+<!-- Effect becomes larger, more significant and goes in both directions for both genders -->
+
+```{r}
+m <- glmmTMB::glmmTMB(Enticing ~ Gender / Condition + (1 | Participant) + (1|Stimulus),
+                      data=filter(df, ConditionBelief == "True"), 
+                      family=glmmTMB::ordbeta(),
+                      control = glmmTMB::glmmTMBControl(parallel = 8))
+
+results_table(m)
+```
+
+```{r}
+
+moderator_believed <- data.frame()
+for(m in c("BAIT_Visual", "BAIT_Text", "BAIT_ExpertAI",
+           "BAIT_Positive", "BAIT_Negative", "PornFrequency", "SexualActivity",
+
+           "Feedback_DiffObvious", "Feedback_DiffNone",
+           "Feedback_AIMoreArousing", "Feedback_AILessArousing",
+           "Feedback_AIMoreAttractive", "Feedback_LessArousing",
+           "Feedback_LabelsIncorrect", "Feedback_LabelsReversed")) {
+  moderator_believed <- rbind(moderator_believed,
+                             test_moderator(filter(df, ConditionBelief == "True"), "Enticing", m))
+}
+
+display(filter(moderator_believed, p < .1))
+```
+
+## Valence
+
+```{r}
+#| fig-height: 12
+#| fig-width: 7
+
+valence_desc <- plot_descriptive(df, "Valence")
+valence_desc
+```
+
+### Whole Sample
+
+This model examines the effect of Gender and Condition on Valence ratings, while accounting for random variability due to participants and items (i.e., random intercepts).
+
+<!-- The intercept is Male and photograph.  -->
+Male participants rated images labelled as AI-Generated significantly lower in valence than Real images. For females, there is no significant effect.
+
+```{r}
+m_valence <- glmmTMB::glmmTMB(Valence ~ Gender / Condition + 
+                                (1| Participant) + (1|Stimulus),
+                      data=df, family=glmmTMB::ordbeta(),
+                      control = glmmTMB::glmmTMBControl(parallel = 8))
+
+results_table(m_valence)
+
+marginaleffects::avg_slopes(m_valence, variables="Condition", by="Gender", re.form=NA)
+```
+
+### Moderators
+
+Here we look at whether the relationship between gender and condition and valence is moderated by **AI-attitudes, porn frequency, and sexual activity**.
+The results showed that enticing ratings for images labeled AI-generated were moderated by the feedback reporting attitudes towards AI, but this was only significant for women.
+More specifically, females who have more positive and negative attitudes towards AI rated images labelled as AI-Generated significantly higher and lower in valence compared to images labelled as photographs
+
+Looking at **feedback** as a moderator, the results show that valence ratings for images labelled AI-Generated were moderted by the feedback that the difference between AI and Photos was obvious, but only for females.
+
+```{r}
+for(m in c("BAIT_Visual", "BAIT_Text", "BAIT_ExpertAI",
+           "BAIT_Positive", "BAIT_Negative", "PornFrequency", "SexualActivity_num")) {
+  moderator_results <- rbind(moderator_results,
+                             test_moderator(df, "Valence", m))
+}
+
+display(filter(moderator_results, Outcome == "Valence"))
+```
+
+```{r}
+feedback_results <- data.frame()
+for(m in c("Feedback_NoFacesAttractive", "Feedback_SomeFacesAttractive",
+           "Feedback_AIMoreAttractive", "Feedback_AILessAttractive",
+           "Feedback_AIMoreArousing", "Feedback_AILessArousing",
+
+           "Feedback_DiffObvious", "Feedback_DiffNone",
+
+           "Feedback_LabelsIncorrect", "Feedback_LabelsReversed",
+           "Feedback_AllReal", "Feedback_AllFake",
+
+           "AllRealConfidence","AllFakeConfidence" ,
+           "Enjoyment")) {
+  feedback_results <- rbind(feedback_results,
+                            test_moderator(df, "Valence", m))
+}
+display(filter(feedback_results, Outcome == "Valence"))
+```
+
+### Believed
+
+```{r}
+m <- glmmTMB::glmmTMB(Valence ~ Gender /Condition + (1| Participant) + (1|Stimulus),
+                      data=filter(df, ConditionBelief == "True"), 
+                      family=glmmTMB::ordbeta(),
+                      control = glmmTMB::glmmTMBControl(parallel = 8))
+
+results_table(m)
+
+```
+
+```{r}
+for(m in c("Feedback_DiffObvious", "Feedback_DiffNone","Feedback_DiffSubtle",
+
+           "Feedback_AIMoreArousing", "Feedback_AILessArousing",
+           "Feedback_AIMoreAttractive", "Feedback_LessArousing",
+
+           "Feedback_LabelsIncorrect", "Feedback_LabelsReversed",
+           "Feedback_AllReal", "Feedback_AllFake")) {
+  moderator_believed <- rbind(moderator_believed,
+                             test_moderator(filter(df, ConditionBelief == "True"), "Valence", m))
+}
+
+display(filter(moderator_believed, p < .1))
+```
+
+## Emotionality (combined factor)
+
+Here we combined the data for arousal, valence and enticing into an emotionality factor.
+
+```{r}
+pca <- principal_components(df[c("Valence", "Arousal", "Enticing")], n = 2)
+pca
+```
+
+```{r}
+df$Emotionality <- normalize(predict(pca)$PC1)
+
+emotionality <- df |> 
+  mutate(Emotionality_Extreme = ifelse(Emotionality %in% c(0, 1), "Extreme", "Not extreme")) |>
+  ggplot(aes(x=Emotionality, fill = Gender)) +
+  geom_histogram(aes(color=Emotionality_Extreme), position = "identity", bins=80) +
+  facet_grid(~Gender, scales="free_y") +
+  scale_color_manual(values=c("red", "white"), guide="none") +
+  scale_fill_manual(values=c("Female"="#48c9b0", "Male"="#FF9800"), guide="none") +
+  scale_y_sqrt(expand = c(0, 0)) +
+  labs(title = "Emotionality") +
+  theme_abyss() +
+  theme(plot.title = element_text(hjust = 0.5, face="bold"))
+
+emotionality
+```
+
+```{r}
+emotionality_desc <- plot_descriptive(df, "Emotionality")
+emotionality_desc
+```
+
+### Whole Sample
+
+This model looks at the effect of gender and condition on emotionality, accounting for random variability due to participants and items (i.e., random intercepts).
+
+The results show that females consistently rate photographs as higher in emotionality compared to males. Additonally, males rate AI-Generated images higher in emotionality compared to photographs.
+
+```{r}
+m <- glmmTMB::glmmTMB(Emotionality ~ Gender /Condition + (1| Participant) + (1|Stimulus),
+                      data=df, family=glmmTMB::ordbeta(),
+                      control = glmmTMB::glmmTMBControl(parallel = 8))
+
+results_table(m)
+```
+
+```{r}
+marginaleffects::avg_slopes(m, variables="Condition", by="Gender", re.form=NA)
+```
+
+### Moderators
+
+Looking at **AI-attitudes, porn frequency and sexual activity**, and feedback as moderators, we can see that for females, emotionality ratings for AI-generated images are negatively moderated by positive attitudes towards AI, meaning that females with more positive AI attitudes rate the images as less emotional.
+For males, emotionality ratings are positively moderated by negative attitudes towards AI, meaning that males with more negative AI attitudes rate the images as more emotional.
+
+Looking at **feedback** as a moderator, the results show that for males, emotionality ratings for AI-Generated images were negatively moderated by the feedback that AI images were more attractive.
+
+```{r}
+for(m in c("BAIT_Visual", "BAIT_Text", "BAIT_ExpertAI",
+           "BAIT_Positive", "BAIT_Negative", "PornFrequency", "SexualActivity_num")) {
+  moderator_results <- rbind(moderator_results,
+                             test_moderator(df, "Emotionality", m))
+}
+
+display(filter(moderator_results, Outcome == "Emotionality"))
+```
+
+```{r}
+feedback_results <- data.frame()
+for(m in c("Feedback_NoFacesAttractive", "Feedback_SomeFacesAttractive",
+           "Feedback_AIMoreAttractive", "Feedback_AILessAttractive",
+           "Feedback_AIMoreArousing", "Feedback_AILessArousing",
+
+           "Feedback_DiffObvious", "Feedback_DiffNone",
+
+           "Feedback_LabelsIncorrect", "Feedback_LabelsReversed",
+           "Feedback_AllReal", "Feedback_AllFake",
+
+           "AllRealConfidence","AllFakeConfidence" ,
+           "Enjoyment")) {
+  feedback_results <- rbind(feedback_results,
+                            test_moderator(df, "Emotionality", m))
+}
+display(filter(feedback_results, Outcome == "Emotionality"))
+```
+
+### Believed
+
+```{r}
+m <- glmmTMB::glmmTMB(Emotionality ~ Gender / Condition + (1 | Participant) + (1|Stimulus),
+                      data=filter(df, ConditionBelief == "True"), 
+                      family=glmmTMB::ordbeta(),
+                      control = glmmTMB::glmmTMBControl(parallel = 8))
+
+results_table(m)
+
+```
+
+```{r}
+for(m in c("Feedback_DiffObvious", "Feedback_DiffNone","Feedback_DiffSubtle",
+
+           "Feedback_AIMoreArousing", "Feedback_AILessArousing",
+           "Feedback_AIMoreAttractive", "Feedback_LessArousing",
+
+           "Feedback_LabelsIncorrect", "Feedback_LabelsReversed",
+           "Feedback_AllReal", "Feedback_AllFake")) {
+  moderator_believed <- rbind(moderator_believed,
+                             test_moderator(filter(df, ConditionBelief == "True"), "Emotionality", m))
+}
+
+display(filter(moderator_believed, p < .1))
+```
+
+## Summary
+
+-
+
+## Figures

### 2025-05-06 study2/analysis/3_realness.qmd
finish* 2_emotions qmd
* missing interpretation of believed, a summary and figures

---
title: "FictionEro2 - Determinants of Reality Beliefs"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
execute: 
  cache: true
---

### 2025-05-06 study2/analysis/0_preprocessing.py

@@ -233,25 +233,25 @@ for i, file in enumerate(files):
     sexactivity = np.nan if sexactivity in [""] else sexactivity
     df["SexualActivity"] = sexactivity
     
-    copsfreq = cops.get("COPS_Frequency_2") or ""  # Ensures None is converted to ""
-    copsfreq = copsfreq.rstrip()  
+    copsfreq = (cops.get("COPS_Frequency") or "").rstrip()
 
-    if "0." in copsfreq:
+    if copsfreq == "I haven't watched pornography in the past 30 days":
         copsfreq = "0. I haven't viewed pornography in the past 30 days"
-    elif "1." in copsfreq:
+    elif copsfreq == "I watched pornography once in the past 30 days":
         copsfreq = "1. I viewed pornography once in the past 30 days"
-    elif "2." in copsfreq:
+    elif copsfreq == "I watched pornography twice in the past 30 days":
         copsfreq = "2. I viewed pornography twice in the past 30 days"
-    elif "3." in copsfreq:
+    elif copsfreq == "I watched pornography weekly":
         copsfreq = "3. I viewed pornography weekly"
-    elif "4." in copsfreq:
+    elif copsfreq == "I watched pornography multiple times a week":
         copsfreq = "4. I viewed pornography multiple times a week"
-    elif "5." in copsfreq:
+    elif copsfreq == "I watched pornography daily":
         copsfreq = "5. I viewed pornography daily"
-    elif "6." in copsfreq:
+    elif copsfreq == "I watched pornography multiple times a day":
         copsfreq = "6. I viewed pornography multiple times a day"
+    elif copsfreq == "":
+        copsfreq = np.nan
 
-    copsfreq = np.nan if copsfreq == "" else copsfreq
     df["COPS_Frequency"] = copsfreq
 
     # check feedback version
@@ -288,7 +288,7 @@ for i, file in enumerate(files):
     df["Feedback_SomeFacesAttractive"] = False
     df["Feedback_AIMoreAttractive"] = False
     df["Feedback_AILessAttractive"] = False
-    df["Feeback_NoImagesArousing"] = False
+    df["Feedback_NoImagesArousing"] = False
     df["Feedback_SomeImagesArousing"] = False
     df["Feedback_AIMoreArousing"] = False
     df["Feedback_AILessArousing"] = False
@@ -302,8 +302,8 @@ for i, file in enumerate(files):
                 df["Feedback_AIMoreAttractive"] = True
             if "less attractive" in f:
[…]

### 2025-05-07 study2/analysis/2_emotion.qmd
updated analysis

@@
   right_join(
-    select(dfsub, Participant, Mobile, starts_with(c("Feedback_","BAIT")), COPS_Frequency, SexualActivity,- Feedback_Text),
+    select(dfsub, Participant, Mobile, starts_with(c("Feedback_","BAIT")), COPS_Frequency, SexualActivity,-Feedback_Text),
     by = "Participant"
     ) |> 
+  datawizard::rescale(select= c("Arousal", "Enticing", "Valence"), range=c(0, 6), to=c(0,1)) |>
   mutate(Condition = case_when(
     Condition == "Fiction" ~ "AI-Generated",
-    Condition == "Reality
-    " ~ "Photograph"
+    Condition == "Reality" ~ "Photograph"
   )) |>
@@
 }
-
-## re-scaled variables
-scale_values <- function(x){(x-min(x))/(max(x)-min(x))}
-
-df$Arousal <- scale_values(df$Arousal)
-df$Enticing <- scale_values(df$Enticing)
-df$Valence <- scale_values(df$Valence)
 ```
@@
 for(m in c("BAIT_Visual", "BAIT_Text", "BAIT_ExpertAI",
-           "BAIT_Positive", "BAIT_Negative", "PornFrequency", "SexualActivity",
-
+           "BAIT_Positive", "BAIT_Negative", "PornFrequency",
+           "SexualActivity",
            "Feedback_DiffObvious", "Feedback_DiffNone",
            "Feedback_AIMoreArousing", "Feedback_AILessArousing",
-           "Feedback_AIMoreAttractive", "Feedback_LessArousing",
+           "Feedback_AIMoreAttractive", "Feedback_AILessArousing",
            "Feedback_LabelsIncorrect", "Feedback_LabelsReversed")) {
@@
 ```{r}
-for(m in c("Feedback_DiffObvious", "Feedback_DiffNone","Feedback_DiffSubtle",
-
+moderator_believed <- data.frame()
+for(m in c("BAIT_Visual", "BAIT_Text", "BAIT_ExpertAI",
+           "BAIT_Positive", "BAIT_Negative", "PornFrequency",
+           "SexualActivity", 
+           "Feedback_DiffObvious", "Feedback_DiffNone",
            "Feedback_AIMoreArousing", "Feedback_AILessArousing",
-           "Feedback_AIMoreAttractive", "Feedback_LessArousing",
-
-           "Feedback_LabelsIncorrect", "Feedback_LabelsReversed",
-           "Feedback_AllReal", "Feedback_AllFake")) {
+           "Feedback_AIMoreAttractive", "Feedback_AILessArousing",
+           "Feedback_LabelsIncorrect", "Feedback_LabelsReversed")) {
   moderator_believed <- rbind(moderator_believed,

### 2025-05-07 study2/analysis/3_realness.qmd
updated analysis

@@
 ---
+
+## Data Preparation
+
+```{r}
+#| message: false
+#| warning: false
+
+library(tidyverse)
+library(easystats)
+library(patchwork)
+library(ggside)
+library(glmmTMB)
+
+options(mc.cores = parallel::detectCores(),
+        brms.backend = "cmdstanr",
+        width = 300)
+```
+
+```{r}
+
+dfsub <- read.csv("../data/data_participants.csv")
+
+df <- read.csv("../data/data.csv") |> 
+  right_join(
+    select(dfsub, Participant, Mobile, starts_with(c("Feedback_", "BAIT_")), COPS_Frequency, SexualActivity,-Feedback_Text),
+    by = "Participant"
+    ) |> 
+  datawizard::rescale(select= c("Arousal", "Enticing", "Valence"), range=c(0, 6), to=c(0,1)) |> 
+  datawizard::rescale(select= c("Realness"), range=c(-3,3), to=c(0,1)) |>
+  mutate(Condition = case_when(
+    Condition == "Fiction" ~ "AI-Generated",
+    Condition == "Reality" ~ "Photograph"
+  )) |>
+  mutate(Condition = fct_relevel(Condition, "Photograph", "AI-Generated"),
+         Gender =  fct_relevel(Gender, "Male", "Female"),
+         PornFrequency = as.numeric(as.factor(COPS_Frequency)),
+         SexualActivity_num = as.numeric(as.factor(SexualActivity)),
+         ConditionBelief = case_when(
+           Condition == "Photograph" & Realness > 0.5 ~ "True",
+           Condition == "AI-Generated" & Realness < 0.5 ~ "True",
+           .default = "False"),
+         RealnessBelief = ifelse(Realness > 0.5, 1, 0)) |>
+  rename(AllRealConfidence = "Feedback_AllRealConfidence",
+         AllFakeConfidence = "Feedback_AllFakeConfidence",
+         Enjoyment = "Feedback_Enjoyment"
+         )|>
+  mutate(across(starts_with("Feedback_"), as.factor))
+
+results_table <- function(model, effects="fixed", filter=NULL) {
+  if("marginaleffects" %in% class(model)) {
+    model |> 
+      parameters::parameters() |> 
+      as.data.frame() |> 
+      select(-Parameter, -SE, -S, z=Statistic, -Predicted) |> 
+      insight::format_table() |> 
+      parameters::display()
+  } else {
+    display(parameters::parameters(model, effects=effects, keep=filter))
+  }
+}
+
+```
+
+**Note**: [These calculations are based on the validation of the BAIT scale](https://realitybending.github.io/FictionEro/study1/analysis/1_cleaning.html)
+
+```{r}
+
+df$BAIT_Videos <- (df$BAIT_VideosRealistic + (1 - df$BAIT_VideosIssues)) / 2
+
+df$BAIT_Visual = (df$BAIT_ImagesRealistic + (1 - df$BAIT_ImagesIssues) + df$BAIT_ImitatingReality + df$BAIT_EnvironmentReal) / 4
+
+df$BAIT_Text = (df$BAIT_TextRealistic + (1 - df$BAIT_TextIssues)) / 2
+
+df$BAIT_Negative <- (df$BAIT_Worry + df$BAIT_Dangerous)/2
+
+df$BAIT_Positive <- (df$BAIT_Exciting + df$BAIT_Benefit)/2
+```
+
+### Distribution
+
+The Realness variable captures a distribution of responses ranging from extreme values (0 and 1) to more ambivalent ratings in between.
+Given the bounded an ordered beta regression model was employed, as recommended for such data structures [(Kubinec, 2022)](https://doi.org/10.1017/pan.2022.20).
+
+Notably, participants’ confidence in their judgments varied depending on whether they believed the image label (e.g., "AI-generated" or "Photograph").
+When the label was believed, participants tended to give more extreme realness ratings, suggesting greater confidence in their evaluations.
+In contrast, non-belief in the label was associated with a higher frequency of intermediate responses, indicating more uncertainty or ambivalence in perceived realness.
+
+```{r}
+#| warning: false
+
+df |> 
+  mutate(ConditionBelief = as.factor(ConditionBelief)) |> 
+  mutate(ConditionBelief = case_when(
+    ConditionBelief == "False" ~ "Not Believed",
+    ConditionBelief == "True" ~ "Believed",)) |>
+  mutate(Realness_Extreme = ifelse(Realness %in% c(0, 1), "Extreme", "Not extreme")) |>
+  ggplot(aes(x=Realness, fill = Gender)) +
+  geom_histogram(aes(color=Realness_Extreme), position = "identity", bins=15) +
+  facet_grid(Gender ~ ConditionBelief, scales="free_y") +
+  scale_color_manual(values=c("red", "white"), guide="none") +
+  scale_fill_manual(values=c("Female"="#FF9800", "Male"="#03A9F4"), guide="none") +
+  scale_y_sqrt(expand = c(0, 0)) +
+  labs(title = "Realness") +
+  theme_abyss() +
+  theme(plot.title = element_text(hjust = 0.5, face="bold"))
+```
+
+## Physical Characteristics
+
+## Manipulation Check
+
+This model examines the influence gender and condition on ratings of realness, incorporating random intercepts for participants and items.
+
+<!-- Intercept: Male and Photograph -->
+
+For males the realness ratings were lower for images labelled AI-Generated compared to real photographs.
+For females they also rated images labelled as AI-Generated as less Real, altough this effect was not significant.
+
+```{r}
+#| warning: false
+
+m <- make_model("Realness ~ Gender / Condition + 
+                (1|Participant) + (1|Stimulus)",
+                family=glmmTMB::ordbeta())
+
+predbeta <- estimate_relation(m, length=20)
+
+m <- make_model("RealnessBelief ~ Gender / Condition + 
+                (1|Participant) + (1|Stimulus)",
+                family="binomial")
+
+predbin <- estimate_relation(m, length=20)
+
+predbeta |> 
+  ggplot(aes(x=Condition, y=Predicted)) +
+  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.2)) +
+  scale_color_manual(values=c("red", "blue"), guide="none") +
+  facet_grid(~Gender)
+```
+
+## Moderators
+
+Here we look at whether the findings above are moderated by **AI-Generated, Porn frequency and sexual activity or feedback**
+
+### AI-Attitudes
+
+Attitudes towards AI did not significantly moderate the influence of Gender and Condition on Realness ratings
+
+```{r}
+#| warning: false
+
+test_moderator <- function(df, moderator="BAIT_Visual") {
+  f <- paste0("Realness ~ Gender / (Condition * ", moderator, ") + (1| Participant) + (1|Stimulus)")
+  r <- glmmTMB::glmmTMB(as.formula(f),
+                      data=df, 
+                      family=glmmTMB::ordbeta(),
+                      control = glmmTMB::glmmTMBControl(parallel = 8)) |>
+    parameters::parameters() |> 
+    as.data.frame() |> 
+    select(-df_error, -Effects, -Group, -Component, -SE)
+  r$Moderator <- moderator
+  insight::format_table(filter(r, str_detect(Parameter, moderator)))
+}
+
+moderator <- data.frame()
+for(m in c("BAIT_Visual", "BAIT_Text", "BAIT_ExpertAI",
+           "BAIT_Positive", "BAIT_Negative")) {
+  moderator <- rbind(moderator, test_moderator(df, m))
+}
+
+display(filter(moderator, p < .05))
+```
+
+<!-- This graph depicts differences in realness ratings based on beliefs about AI's visual abilities for both genders when presented with images labeled as photographs or AI-generated.
+Notably, images labeled as photographs consistently received higher ratings of realness than those labelled as AI-Generated, even at lower levels of belief in AI's visual capacity.
+-->
+
+<!-- As beliefs in AI's ability to generate realistic images increase, both genders show higher realness scores.
+However, for females with strong beliefs in AI's visual capabilities, realness ratings are higher for images labelled as AI-Generated compared to images labelled as photographs.
+-->
+
+<!-- **Notably NONE of these results were significant.** -->
+
+<!-- ```{r} -->
+<!-- #| warning: false -->
+
+<!-- m1 <- glmmTMB::glmmTMB(Realness ~ Gender / -->
+<!--                         (Condition *  BAIT_Visual) +  -->
+<!--                         (1| Participant) + (1|Stimulus), -->
+<!--                       data=df,  -->
+<!--                       family=glmmTMB::ordbeta(), -->
+<!--                       control = glmmTMB::glmmTMBControl(parallel = 8)) -->
+
+<!-- summary(m1) -->
+
+<!-- # stars1 <- data.frame(Gender = as.factor(c("Male", "Male", "Female", "Female")),  -->
+<!-- #                     Condition=c("Photograph", "AI-Generated", "Photograph", "AI-Generated"),  -->
+<!-- #                     label=c("***", "***", "***", "***"), -->
+<!-- #                     x=c(0.6, 0.6, 0.65, 0.65), -->
+<!-- #                     y=c(0.8, 0.6, 0.72, 0.55)) -->
+
+<!-- pred1 <- estimate_relation(m1) -->
+<!-- p1 <- pred1 |> -->
+<!--   ggplot(aes(x=BAIT_Visual, y=Predicted)) + -->
+<!--   geom_ribbon(aes(ymin=CI_low, ymax=CI_high, fill=Condition), alpha=0.3) + -->
+<!--   geom_line(aes(color=Condition), linewidth=1, key_glyph = draw_key_rect) + -->
+<!--   # geom_text(data=stars1, aes(x=x, y=y, label=label, color=Condition), hjust=0.5, size=3) + -->
+<!--   # geom_text(data=data.frame(Gender=as.factor("Female"), x=0.65, y=0.638, label="**"), aes(x=x, y=y, label=label), hjust=0.5, color="#424242", size=3) + -->
+<!--   facet_grid(~Gender) + -->
+<!--   scale_y_continuous(labels=scales::percent) + -->
+<!--   scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) + -->
+<!--   scale_fill_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336"), guide="none") + -->
+<!--   theme_minimal() + -->
+<!--   theme(axis.text.y = element_text(size = 8), -->
+<!--         strip.placement = "outside", -->
+<!--         strip.background.x = element_rect(fill=c("lightgrey"), color=NA), -->
+<!--         strip.text.x = element_text(size = 10), -->
+<!--         strip.text.y = element_text(size = 10), -->
+<!--         axis.text.x = element_text(size=9, color="black"), -->
+<!--         legend.text = element_text(size = 10)) + -->
+<!--   labs(y="Realness\n", fill="Images presented as:", color="Images presented as:", -->
+<!--        x = "\nBeliefs about Artificial Information Technology (BAIT)\n'AI algorithms can generate realistic images'", -->
+<!--        tag = "A") -->
+<!-- p1 -->
+<!-- ``` -->
+
+### Porn + Sexual Activity
+
+This model evaluates how ratings of realness, predicted by sex, condition, and relevance, are moderated by participants' report of how often they engaged in sexual activity and how often they view pornography.
+
+Looking at porn frequency and sexual activity, the influence of Gender and Condition on Realness scores was not moderated by these variables.
+
+```{r}
+#| warning: false
+
+moderator <- data.frame()
+for(m in c("PornFrequency", "SexualActivity_num")) {
+  moderator <- rbind(moderator, test_moderator(df, m))
+}
+
+display(filter(moderator, p < .05))
+```
+
+### Feedback
+
+This model evaluates how ratings of realness, predicted by sex, condition, and relevance, are moderated by participants' feedback.
+
+For males, the belief that AI-generated images were less arousing significantly increased realness ratings for images labeled as AI-generated (compared to photos).
+
+For male participants, the belief that all images were real also significantly increased realness ratings for photos.
+
+For female participants, the belief that no faces were attractive was associated with significantly higher realness ratings for photographs.
+
+```{r}
+#| warning: false
+
+moderator <- data.frame()
+for(m in c("Feedback_DiffObvious", "Feedback_DiffNone",
+           "Feedback_AIMoreArousing", "Feedback_AILessArousing", 
+           "Feedback_NoFacesAttractive", "Feedback_SomeFacesAttractive", 
+           "Feedback_LabelsIncorrect", "Feedback_LabelsReversed",
+           "Feedback_AllReal",
+           "Feedback_AllFake")) {
+  moderator <- rbind(moderator, test_moderator(df, m))
+}
+
+display(filter(moderator, p < .05))
+```
+
+```{r}
+#| warning: false
+
+m2 <- glmmTMB::glmmTMB(Realness ~ Gender /
+                         (Feedback_AILessArousing / Condition) + 
+                        (1 | Participant) + (1|Stimulus),
+                      data=df, 
+                      family=glmmTMB::ordbeta(),
+                      control = glmmTMB::glmmTMBControl(parallel = 8))
+
+summary(m2)
+
+stars1 <- data.frame(Gender = as.factor("Male"),
+                     Condition = "AI-Generated",
+                     label = "***",
+                     x = 1.5, 
+                     y = 0.55)
+
+pred1 <- estimate_relation(m2)
+
+p1 <- pred1 |> 
+  ggplot(aes(x=Feedback_AILessArousing, y=Predicted)) +
+  geom_line(aes(color=Condition, group=Condition), linewidth=.3, position = position_dodge(width=0.2), key_glyph = "path") +
+  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.2), size=0.8, linewidth=1, key_glyph = "blank") +
+  # geom_text(data=stars2, aes(x=x, y=y, label=label, color=Condition), hjust=0.5, key_glyph = "blank", size=3) +
+  geom_text(data=stars2, aes(x=x, y=y, label=label), hjust=0.5, color="#424242", size=3) +
+  guides(color=guide_legend(override.aes = list(linewidth = 1.5))) +
+  facet_grid(~Gender) +
+  scale_y_continuous(labels=scales::percent) +
+  scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
+  theme_minimal() +
+  theme(axis.text.y = element_text(size = 8),
+        strip.placement = "outside",
+        strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
+        strip.text.x = element_text(size = 10),
+        strip.text.y = element_text(size = 10),
+        axis.text.x = element_text(size=9, color="black"),
+        legend.text = element_text(size = 10)) +
+  labs(y="Realness\n", fill="Images presented as:", color="Images presented as:",
+       x = "\n'AI-Images were less arousing' Feedback",
+       tag = "B")
+
+```
+
+```{r}
+#| warning: false
+
+m2 <- glmmTMB::glmmTMB(Realness ~ Gender /
+                         (Feedback_NoFacesAttractive / Condition) + 
+                        (1 | Participant) + (1|Stimulus),
+                      data=df, 
+                      family=glmmTMB::ordbeta(),
+                      control = glmmTMB::glmmTMBControl(parallel = 8))
+
+summary(m2)
+
+# stars2 <- data.frame(
+#   Gender = as.factor("Male"),
+#   Condition = "AI-Generated",
+#   label = "***",
+#   x = 1.5,
+#   y = 0.5)
+
+pred2 <- estimate_relation(m2)
+
+p2 <- pred2 |> 
+  ggplot(aes(x=Feedback_NoFacesAttractive, y=Predicted)) +
+  geom_line(aes(color=Condition, group=Condition), linewidth=.3, position = position_dodge(width=0.2), key_glyph = "path") +
+  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.2), size=0.8, linewidth=1, key_glyph = "blank") +
+  # geom_text(data=stars2, aes(x=x, y=y, label=label, color=Condition), hjust=0.5, key_glyph = "blank", size=3) +
+  # geom_text(data=stars2, aes(x=x, y=y, label=label), hjust=0.5, color="#424242", size=3) +
+  guides(color=guide_legend(override.aes = list(linewidth = 1.5))) +
+  facet_grid(~Gender) +
+  scale_y_continuous(labels=scales::percent) +
+  scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
+  theme_minimal() +
+  theme(axis.text.y = element_text(size = 8),
+        strip.placement = "outside",
+        strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
+        strip.text.x = element_text(size = 10),
+        strip.text.y = element_text(size = 10),
+        axis.text.x = element_text(size=9, color="black"),
+        legend.text = element_text(size = 10)) +
+  labs(y="Realness\n", fill="Images presented as:", color="Images presented as:",
+       x = "\n'AI-Faces were less attractive' Feedback",
+       tag = "B")
+
+p2
+```
+
+## Summary

### 2025-05-08 study2/analysis/2_emotion.qmd
data analysis
lacking final figures and rendering emotions analysis script

--- 2025-05-06 study2/analysis/2_emotion.qmd
@@
 
-**notes**: How about confidence on all AI and all photos.
-
 ```{r}
@@
     ) |> 
+    datawizard::rescale(select= c("Arousal", "Enticing", "Valence"), range=c(0, 6), to=c(0,1)) |> 
+  datawizard::rescale(select= c("Realness"), range=c(-3,3), to=c(0,1)) |>
   mutate(Condition = case_when(
     Condition == "Fiction" ~ "AI-Generated",
-    Condition == "Reality
-    " ~ "Photograph"
+    Condition == "Reality" ~ "Photograph"
   )) |>
@@
          ConditionBelief = case_when(
-           Condition == "Photograph" & Realness > 0 ~ "True",
-           Condition == "AI-Generated" & Realness < 0 ~ "True",
+           Condition == "Photograph" & Realness > 0.5 ~ "True",
+           Condition == "AI-Generated" & Realness < 0.5 ~ "True",
            .default = "False",
@@
 
-## re-scaled variables
-scale_values <- function(x){(x-min(x))/(max(x)-min(x))}
-
-df$Arousal <- scale_values(df$Arousal)
-df$Enticing <- scale_values(df$Enticing)
-df$Valence <- scale_values(df$Valence)
 ```
@@
 
-## Manipulation Check
+## Visualisation of Key Variables
 
@@
 
-To summarise, women rate stimuli on average significantly lower in arousal, enticiment and valence than men.
+To summarise, **women** rate stimuli on average **significantly lower** in arousal, enticiment and valence than **men**.
 
@@
 
-Arousal ratings were relatively well-distributed across the scale, with the highest frequency for "Not at all" and a gradual decrease across higher ratings.
+In general, males exhibited greater variability in their arousal ratings, while females tended to provide more lower arousal ratings.
 
-The pattern of arousal ratings was similar regardless of whether participants believed the images were AI-generated or real.
-Among male participants, arousal ratings were relatively evenly distributed but tended to cluster around the middle of the scale, independent of their belief about the images' origin.
-Female participants, on the other hand, showed a pronounced peak at the lowest arousal rating, irrespective of their perception of the images as AI-generated.
-Participants with other gender identities provided fewer responses overall, but their arousal ratings generally leaned toward moderate levels, particularly in the "Not Believed" condition.
+The pattern of arousal ratings for images that participants believed to be either AI-generated or photos (i.e., initially labeled as photos and later rated as photos, or initially labeled as AI and later rated as AI), as well as for images where participants disagreed with the original labels, was generally similar across genders.
 
@@
 arousal <- df |> 
-  ggplot(aes(x=Arousal)) +
-  geom_bar(fill="#03A9F4") +
+  ggplot(aes(x=Arousal, fill = Gender)) +
+  geom_bar() +
   scale_y_sqrt(expand = c(0, 0)) +
+  scale_x_continuous(
+    breaks = c(0, 1),
+    labels = c("Not at all","Very much")) +
   labs(title = "Arousal", ) +
+  facet_wrap(~Gender) +
+   scale_fill_manual(values=c("Male"="#E91E63", "Female"="#FF9800"), guide="none") +
   theme_abyss() +
@@
   geom_bar(position = "identity") +
+   scale_x_continuous(
+    breaks = c(0, 1),
+    labels = c("Not at all","Very much")) +
   facet_grid(Gender~ConditionBelief, scales="free_y") +
   scale_color_manual(values=c("red", "white"), guide="none") +
-  scale_fill_manual(values=c("Female"="#E91E63", "Male"="#FF9800"), guide="none") +
+  scale_fill_manual(values=c("Male"="#E91E63", "Female"="#FF9800"), guide="none") +
   # scale_y_sqrt(expand = c(0, 0)) +
-  labs(title = "Arousal to images believed or not to be AI-Gnerated") +
+  labs(title = "Arousal Ratings for Images Based on Belief in Original Labels") +
   theme_abyss() +
@@
 ```
-
-**Note**:  Model m3, which includes random intercepts and random slopes for Gender at the stimulus level, exhibits relatively high correlations between the random intercepts and slopes.
-This suggests that the random effects are strongly correlated, which could indicate overfitting.
 
@@
 test_bf(m1,m2, m3)
-compare_performance(m1, m2)
+compare_performance(m1, m2, m3)
 
-# the model with participants only as random effecs seems to be the best
+# Model m3, which includes random intercepts for Participants and both random intercepts and slopes for Gender at the Stimulus level, seems to be the best
 ```
@@
 
-Enticement ratings were relatively well-distributed across the scale.
+In general, males tended to rate images higher in enticement more often than females.
 
-Male participants predominantly provided responses in the mid-to-high enticement range across both conditions.
-Female participants showed a pronounced peak at the lowest enticement rating when they did not believe the image was AI-generated, with a similar but less pronounced pattern in the believed condition.
-Participants identifying as 'Other' responses were more concentrated around the middle of the scale.
+Enticing ratings for images where participants believed in the original labels, as well as for those where they disagreed with the labels, were similar for males.
+
+For females, although a similar pattern was observed, they tended to provide more lower enticement ratings, particularly for images where they believed in the original labels.
 
@@
 enticiment <- df |> 
-  ggplot(aes(x=Enticing)) +
-  geom_bar(fill="#03A9F4") +
+  ggplot(aes(x=Enticing, fill = Gender)) +
+  geom_bar() +
   scale_y_sqrt(expand = c(0, 0)) +
+  scale_x_continuous(
+    breaks = c(0, 1),
+    labels = c("Not at all","Very much")) +
   labs(title = "Enticement", ) +
+  facet_wrap(~Gender) +
+   scale_fill_manual(values=c("Male"="#E91E63", "Female"="#FF9800"), guide="none") +
   theme_abyss() +
@@
   geom_bar(position = "identity", binwidth = 0.5) +
+  scale_x_continuous(
+    breaks = c(0, 1),
+    labels = c("Not at all","Very much")) +
   facet_grid(Gender~ConditionBelief, scales="free_y") +
-  scale_color_manual(values=c("red", "white"), guide="none") +
   scale_fill_manual(values=c("Female"="#E91E63", "Male"="#FF9800"), guide="none") +
   # scale_y_sqrt(expand = c(0, 0)) +
-  labs(title = "Enticiment to images believed or not to be AI-Gnerated") +
+  labs(title = "Enticement Ratings for Images Based on Belief in Original Labels") +
   theme_abyss() +
@@
   geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color = Gender), position=position_dodge(width=0.5)) +
- scale_color_manual(values=c("Male"="#E91E63", "Female"="#FF9800"), guide="none") +  labs(y="Arousal") +
+ scale_color_manual(values=c("Male"="#E91E63", "Female"="#FF9800"), guide="none") +  labs(y="Enticement") +
   theme_abyss()
@@
 
-Valence ratings were concetrated more around the mid-to-high valence.
+In general, males tended to assign higher valence ratings to images more frequently.
+Females, on the other hand, showed higher frequencies of ratings in the middle and lower ranges of the valence scale.
 
-Participants showed the same pattern of results regardless of whether they believed the images to be Ai-generated or not. 
-Males tended to to have the majority of their responses concentrated in the mid-to-high valence range. Female majoity valence ratings were on on the lower (0) and midle end of the scale (3/4).
+The pattern of valence ratings for images, whether believed or not believed, was similar for both genders, with ratings for believed images closely resembling those for non-believed images.
 
@@
 valence <- df |> 
-  ggplot(aes(x=Valence)) +
-  geom_bar(fill="#03A9F4") +
+  ggplot(aes(x=Valence, fill = Gender)) +
+  geom_bar() +
   scale_y_sqrt(expand = c(0, 0)) +
+   scale_x_continuous(
+    breaks = c(0, 1),
+    labels = c("Not at all","Very much")) +
+  scale_fill_manual(values=c("Female"="#E91E63", "Male"="#FF9800"), guide="none") +
   labs(title = "Valence", ) +
+    facet_wrap(~Gender) +
   theme_abyss() +
@@
   facet_grid(Gender~ConditionBelief, scales="free_y") +
-  scale_color_manual(values=c("red", "white"), guide="none") +
   scale_fill_manual(values=c("Female"="#E91E63", "Male"="#FF9800"), guide="none") +
   # scale_y_sqrt(expand = c(0, 0)) +
-  labs(title = "Valence to images believed or not to be AI-Gnerated") +
+  labs(title = "Valence to Ratings for Images Based on Belief in Original Labels") +
   theme_abyss() +
@@
 This model evaluate ths the effects of Gender on valence, accounting for random variability due to participants and the stimuli (i.e., random effects). Notably, all the stimuli is erotic.
-
-<!-- Key Findings -->
 
@@
   geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color = Gender), position=position_dodge(width=0.5)) +
- scale_color_manual(values=c("Male"="#E91E63", "Female"="#FF9800"), guide="none") +  labs(y="Arousal") +
+ scale_color_manual(values=c("Male"="#E91E63", "Female"="#FF9800"), guide="none") +  labs(y="Valence") +
   theme_abyss()
@@
 marginaleffects::avg_slopes(m_arousal, variables="Condition", by="Gender") 
-#   results_table()
+# > results_table()
 
@@
 The analysis revealed a significant interaction effect only for **positive attitudes towards AI** among females.
-Specifically, females with higher positive attitudes towards AI rated AI-generated images as more arousing, relative to when they viewed photographs
+Specifically, females with higher positive attitudes towards AI rated AI-generated images as more arousing, relative to when they viewed images labelled as photographs.
 
@@
 ```{r}
+
 m <- glmmTMB::glmmTMB(Arousal ~ Gender / (Condition * SexualActivity_num) + (Condition | Participant) + (1|Stimulus),
@@
 
-This model examines how Gender and Condition influence enticement ratings, treating participant and items as random intercepts.
+This model examines how **Gender and Condition influence enticement** ratings, treating participant and items as random intercepts.
 
@@
 For females, enticement ratings are slightly lower on average for AI-Generated images compared to Photograph images, although this difference is not statistically significant.
-
-**Note**. 'Other' was removed due to the very small percentage of individuals identifying as such.
 
@@
 
-Looking at **feedback as a moderator**, the results showed that enticement ratings for images labelled as AI-Generated were moderated by the feedback that AI is less Attractive for males, and that difference between the AI-Generated images and real photos is obvious for females.
+Looking at **feedback as a moderator**, the results showed that enticement ratings for images labelled as AI-Generated were moderated by the feedback that AI is less attractive for males, and that difference between the AI-Generated images and real photos is obvious for females.
 
@@
            "Feedback_AIMoreArousing", "Feedback_AILessArousing",
-           "Feedback_AIMoreAttractive", "Feedback_LessArousing",
+           "Feedback_AIMoreAttractive", "Feedback_AILessArousing",
            "Feedback_LabelsIncorrect", "Feedback_LabelsReversed")) {
@@
 
-This model examines the effect of Gender and Condition on Valence ratings, while accounting for random variability due to participants and items (i.e., random intercepts).
+This model examines the effect of **Gender and Condition on Valence** ratings, while accounting for random variability due to participants and items (i.e., random intercepts).
 
@@
 ```{r}
-for(m in c("Feedback_DiffObvious", "Feedback_DiffNone","Feedback_DiffSubtle",
+moderator_believed <- data.frame()
+for(m in c("BAIT_Visual", "BAIT_Text", "BAIT_ExpertAI",
+           "BAIT_Positive", "BAIT_Negative", "PornFrequency", "SexualActivity",
 
+           "Feedback_DiffObvious", "Feedback_DiffNone",
            "Feedback_AIMoreArousing", "Feedback_AILessArousing",
-           "Feedback_AIMoreAttractive", "Feedback_LessArousing",
-
-           "Feedback_LabelsIncorrect", "Feedback_LabelsReversed",
-           "Feedback_AllReal", "Feedback_AllFake")) {
+           "Feedback_AIMoreAttractive", "Feedback_AILessArousing",
+           "Feedback_LabelsIncorrect", "Feedback_LabelsReversed")) {
   moderator_believed <- rbind(moderator_believed,
@@
 
-display(filter(moderator_believed, p < .1))
+(filter(moderator_believed, p < .1))
 ```
@@
 ```{r}
-df$Emotionality <- normalize(predict(pca)$PC1)
+df$Emotionality <- as.numeric(normalize(predict(pca)$PC1))
 
@@
   ggplot(aes(x=Emotionality, fill = Gender)) +
-  geom_histogram(aes(color=Emotionality_Extreme), position = "identity", bins=80) +
+  geom_histogram(aes(color=Emotionality_Extreme), position = "identity", bins=20) +
   facet_grid(~Gender, scales="free_y") +
   scale_color_manual(values=c("red", "white"), guide="none") +
-  scale_fill_manual(values=c("Female"="#48c9b0", "Male"="#FF9800"), guide="none") +
+  scale_fill_manual(values=c("Male"="#E91E63", "Female"="#FF9800"), guide="none") +
   scale_y_sqrt(expand = c(0, 0)) +
@@
 
-This model looks at the effect of gender and condition on emotionality, accounting for random variability due to participants and items (i.e., random intercepts).
+This model looks at the effect of **Gender and Condition on Emotionality**, accounting for random variability due to participants and items (i.e., random intercepts).
 
@@
 ```{r}
-m <- glmmTMB::glmmTMB(Emotionality ~ Gender /Condition + (1| Participant) + (1|Stimulus),
+m <- glmmTMB::glmmTMB(Emotionality ~ Gender / Condition + (1| Participant) + (1|Stimulus),
                       data=df, family=glmmTMB::ordbeta(),
@@
 
-Looking at **feedback** as a moderator, the results show that for males, emotionality ratings for AI-Generated images were negatively moderated by the feedback that AI images were more attractive.
+Looking at **feedback** as a moderator,  the results show that emotionality ratings for AI-generated images were significantly moderated only by positive attitudes toward AI in females and negative attitudes toward AI in males.
+
+Interestingly, for females, higher positive attitudes (BAIT Positive) were associated with lower emotionality ratings of AI-generated images.
+For males, higher negative attitudes (BAIT Negative) were associated with higher emotionality ratings.
 
@@
 
--
+**Gender Differences**
+- Women rate stimuli on average significantly lower in arousal, enticiment and valence than men, however this difference was not significant for valence.
+
+-Males rated AI-generated images significantly lower than photographs in arousal, valence, and enticement.
+Females showed no significant difference in ratings between AI-generated and photographic images across all outcomes.
+
+**Moderators**
+- For women, **positive attitudes towards AI** moderated arousal, enticement, and valence ratings, resulting in **more favorable evaluations of AI-generated images**.
+Negative attitudes moderated valence ratings, leading to less favorable evaluations.
+
+- For men, negative attitudes towards AI moderated only enticement ratings, with more negative views leading to less enticing ratings of AI-generated images.
+
+- Men’s **perceptions of the attractiveness of AI-generated images** moderated both arousal and enticement ratings.
+More attractive AI images were rated as more arousing and enticing, while less attractive AI images were rated as less arousing.
+
+- Women’s feedback about the differences between AI and real images being obvious moderated both enticement and valence ratings, with AI-generated images rated as less enticing and less valent.
 
 ## Figures
+
+## Notes/ Questions
+
+1. 'Other' was removed due to the very small percentage of individuals identifying as such.
+2. 'Porn' factor was not computed, instead sexual activity and frequency of watching porn were treated seperate.

### 2025-05-08 study2/analysis/3_realness.qmd
data analysis
lacking final figures and rendering emotions analysis script

@@
 ---
-
 ## Data Preparation
@@
 
+Here, we are examining the effect of various physical characteristics of the images to evaluate whether they influence the perceived realness of the images.
+Neither Entropy, Complexity, Contrast, nor Luminance significantly influence the perceived realness of the images, nor the likelihood of realness being above 0.5 ("RealnessBelief"), as indicated by the lack of significant effects.
+
+```{r}
+#| warning: false
+
+make_model <- function(f, family=glmmTMB::ordbeta()) {
+  m <- glmmTMB::glmmTMB(as.formula(f), 
+                        data=df, 
+                        family=family,
+                        control = glmmTMB::glmmTMBControl(parallel = 8))
+  print(results_table(m))
+  m
+}
+
+m <- make_model("Realness ~ Entropy + (1|Participant) + (1|Stimulus)", family=glmmTMB::ordbeta())
+m <- make_model("RealnessBelief ~ Entropy + (1|Participant) + (1|Stimulus)", family="binomial")
+m <- make_model("Realness ~ Complexity + (1|Participant) + (1|Stimulus)", family=glmmTMB::ordbeta())
+m <- make_model("RealnessBelief ~ Complexity + (1|Participant) + (1|Stimulus)", family="binomial")
+m <- make_model("Realness ~ Contrast + (1|Participant) + (1|Stimulus)", family=glmmTMB::ordbeta())
+m <- make_model("RealnessBelief ~ Contrast + (1|Participant) + (1|Stimulus)", family="binomial")
+m <- make_model("Realness ~ Luminance + (1|Participant) + (1|Stimulus)", family=glmmTMB::ordbeta())
+m <- make_model("RealnessBelief ~ Luminance + (1|Participant) + (1|Stimulus)", family="binomial")
+```
+
 ## Manipulation Check
@@
 
-Attitudes towards AI did not significantly moderate the influence of Gender and Condition on Realness ratings
+This model looks at whether realness ratings are moderated by attitudes towards AI.
+
+Looking at the results, the influence of Gender and Condition on Realness scores was not moderated by attidues towards AI.
 
@@
 
-<!-- This graph depicts differences in realness ratings based on beliefs about AI's visual abilities for both genders when presented with images labeled as photographs or AI-generated.
-Notably, images labeled as photographs consistently received higher ratings of realness than those labelled as AI-Generated, even at lower levels of belief in AI's visual capacity.
--->
-
-<!-- As beliefs in AI's ability to generate realistic images increase, both genders show higher realness scores.
-However, for females with strong beliefs in AI's visual capabilities, realness ratings are higher for images labelled as AI-Generated compared to images labelled as photographs.
--->
-
-<!-- **Notably NONE of these results were significant.** -->
-
-<!-- ```{r} -->
-<!-- #| warning: false -->
-
-<!-- m1 <- glmmTMB::glmmTMB(Realness ~ Gender / -->
-<!--                         (Condition *  BAIT_Visual) +  -->
-<!--                         (1| Participant) + (1|Stimulus), -->
-<!--                       data=df,  -->
-<!--                       family=glmmTMB::ordbeta(), -->
-<!--                       control = glmmTMB::glmmTMBControl(parallel = 8)) -->
-
-<!-- summary(m1) -->
-
-<!-- # stars1 <- data.frame(Gender = as.factor(c("Male", "Male", "Female", "Female")),  -->
-<!-- #                     Condition=c("Photograph", "AI-Generated", "Photograph", "AI-Generated"),  -->
-<!-- #                     label=c("***", "***", "***", "***"), -->
-<!-- #                     x=c(0.6, 0.6, 0.65, 0.65), -->
-<!-- #                     y=c(0.8, 0.6, 0.72, 0.55)) -->
-
-<!-- pred1 <- estimate_relation(m1) -->
-<!-- p1 <- pred1 |> -->
-<!--   ggplot(aes(x=BAIT_Visual, y=Predicted)) + -->
-<!--   geom_ribbon(aes(ymin=CI_low, ymax=CI_high, fill=Condition), alpha=0.3) + -->
-<!--   geom_line(aes(color=Condition), linewidth=1, key_glyph = draw_key_rect) + -->
-<!--   # geom_text(data=stars1, aes(x=x, y=y, label=label, color=Condition), hjust=0.5, size=3) + -->
-<!--   # geom_text(data=data.frame(Gender=as.factor("Female"), x=0.65, y=0.638, label="**"), aes(x=x, y=y, label=label), hjust=0.5, color="#424242", size=3) + -->
-<!--   facet_grid(~Gender) + -->
-<!--   scale_y_continuous(labels=scales::percent) + -->
-<!--   scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) + -->
-<!--   scale_fill_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336"), guide="none") + -->
-<!--   theme_minimal() + -->
-<!--   theme(axis.text.y = element_text(size = 8), -->
-<!--         strip.placement = "outside", -->
-<!--         strip.background.x = element_rect(fill=c("lightgrey"), color=NA), -->
-<!--         strip.text.x = element_text(size = 10), -->
-<!--         strip.text.y = element_text(size = 10), -->
-<!--         axis.text.x = element_text(size=9, color="black"), -->
-<!--         legend.text = element_text(size = 10)) + -->
-<!--   labs(y="Realness\n", fill="Images presented as:", color="Images presented as:", -->
-<!--        x = "\nBeliefs about Artificial Information Technology (BAIT)\n'AI algorithms can generate realistic images'", -->
-<!--        tag = "A") -->
-<!-- p1 -->
-<!-- ``` -->
-
 ### Porn + Sexual Activity
 
-This model evaluates how ratings of realness, predicted by sex, condition, and relevance, are moderated by participants' report of how often they engaged in sexual activity and how often they view pornography.
+This model evaluates how ratings of realness, predicted by Gender and Condition, are moderated by participants' report of how often they engaged in sexual activity and how often they view pornography.
 
@@
 
-For males, the belief that AI-generated images were less arousing significantly increased realness ratings for images labeled as AI-generated (compared to photos).
+For males, the feedback that AI-generated images were less arousing significantly moderated realness ratings for images labeled as AI-generated, with higher realness ratings for those images when participants thought they were less arousing.
 
-For male participants, the belief that all images were real also significantly increased realness ratings for photos.
+For males, the belief that all images were real significantly increased realness ratings for all images, regardless of their actual content.
 
-For female participants, the belief that no faces were attractive was associated with significantly higher realness ratings for photographs.
+For females, the belief that no faces were attractive significantly increased realness ratings for the images, suggesting that lower attractiveness perceptions made the images seem more real.
 
@@
 
-stars1 <- data.frame(Gender = as.factor("Male"),
-                     Condition = "AI-Generated",
-                     label = "***",
-                     x = 1.5, 
-                     y = 0.55)
+# stars1 <- data.frame(Gender = as.factor("Male"),
+#                      Condition = "AI-Generated",
+#                      label = "***",
+#                      x = 1.5, 
+#                      y = 0.55)
+#
 
@@
   # geom_text(data=stars2, aes(x=x, y=y, label=label, color=Condition), hjust=0.5, key_glyph = "blank", size=3) +
-  geom_text(data=stars2, aes(x=x, y=y, label=label), hjust=0.5, color="#424242", size=3) +
+  # geom_text(data=stars1, aes(x=x, y=y, label=label), hjust=0.5, color="#424242", size=3) +
   guides(color=guide_legend(override.aes = list(linewidth = 1.5))) +
@@
        tag = "B")
+
+p1
 
@@
 ## Summary
+
+- For males the realness ratings were lower for images labelled AI-Generated compared to real photographs.
+For females they also rated images labelled as AI-Generated as less Real, altough this effect was not significant.
+- Looking at moderators, attitudes towards AI, participants reports of how often they engaged in sexual activity and how often they view pornography, did not moderate realness ratings
+- Looking at the feedback as a moderator for realness ratings, for males, feedback that AI-generated images were less arousing increased realness ratings for those images, and believing all images were real raised realness ratings across all images.
+For females, the belief that no faces were attractive raised realness ratings for the images.
+
+## Figures
+
+## Notes/ Questions
+
+1. 'Other' was removed due to the very small percentage of individuals identifying as such.
+2. 'Porn' factor was not computed, instead sexual activity and frequency of watching porn were treated seperate. 
+3. Missing significance starts on figures.

### 2025-05-09 study2/analysis/2_emotion.qmd
updated scripts

@@
 
-```{r}
+```{r data preparation}
 #| warning: false
@@
 
-```{r}
+```{r Bait Dimensions}
 
@@
 
-This section is about selecting the best model. Notably, all the stimuli presented are of an erotic nature.
-Note that variables were rescaled to [0,1] when fitting the models and that the stimuli presented to participants was assigned according to their self-rated sexuality, making all stimuli relevant to participants.
+This section is about selecting the best model. Notably, **all the stimuli presented are of an erotic nature**.
+Note that variables were rescaled to [0,1] when fitting the models and that the stimuli presented to participants was assigned according to their self-rated sexuality, making **all stimuli relevant** to participants.
 
@@
 
-The pattern of arousal ratings for images that participants believed to be either AI-generated or photos (i.e., initially labeled as photos and later rated as photos, or initially labeled as AI and later rated as AI), as well as for images where participants disagreed with the original labels, was generally similar across genders.
+The pattern of arousal ratings for images that participants believed to be either AI-generated or photos (i.e., initially labeled as photos and later rated as photos, or initially labeled as AI and later rated as AI), as well as for images where participants disagreed with the original labels, was generally similar within genders.
+However, between genders, women tended to provide more low arousal ratings than men.
 
-```{r}
+```{r Arousal1}
 arousal <- df |> 
@@
 
-```{r}
+```{r Arousal2}
 
@@
 
-```{r}
+```{r Arousal Model selection}
 #| eval: false
@@
 
-```{r}
+```{r Arousal3}
 
@@
 
-```{r}
+```{r Arousal Plot}
 estimate_relation(m_a) |> 
@@
 
-Enticing ratings for images where participants believed in the original labels, as well as for those where they disagreed with the labels, were similar for males.
+Enticing ratings for images where participants believed in the original labels, as well as for those where they disagreed with the labels, were similar for within genders, with males providing higher ratings of enticement.
 
-For females, although a similar pattern was observed, they tended to provide more lower enticement ratings, particularly for images where they believed in the original labels.
+For females, although a similar pattern was observed, they tended to provide more lower enticement ratings, particularly for images where they disagreed with the original labels.
 
-```{r}
+```{r Enticement1}
 enticiment <- df |> 
@@
 
-```{r}
+```{r Enticement2}
 
@@
 
-This model evaluate ths the effects of Gender on Enticement, accounting for random variability due to participants and the stimuli (i.e., random effects). Notably, all the stimuli is erotic.
-
+This model evaluate ths the effects of Gender on Enticement, accounting for random variability due to participants (i.e., random effects).
 The analysis revealed that on average **women rate erotic stimuli significantly lower in enticiment than men**.
 
-```{r}
+```{r Enticicement3}
 m_e <- glmmTMB::glmmTMB(Enticing ~ Gender + (1|Participant),
@@
 
-```{r}
+```{r Enticement plot}
 estimate_relation(m_e) |> 
@@
 
-The pattern of valence ratings for images, whether believed or not believed, was similar for both genders, with ratings for believed images closely resembling those for non-believed images.
+The pattern of valence ratings for images, whether believed or not believed, was similar within genders, with ratings for believed images closely resembling those for non-believed images.
 
-```{r}
+```{r Valence1}
 valence <- df |> 
@@
 
-```{r}
+```{r Valence2}
 
@@
   geom_bar(position = "identity", binwidth = 0.5) +
+  scale_x_continuous(
+    breaks = c(0, 1),
+    labels = c("Not at all","Very much")) +
   facet_grid(Gender~ConditionBelief, scales="free_y") +
@@
 
-This model evaluate ths the effects of Gender on valence, accounting for random variability due to participants and the stimuli (i.e., random effects). Notably, all the stimuli is erotic.
-
+This model evaluate ths the effects of Gender on valence, accounting for random variability due to participants.
 The analysis revealed that on average **women rate erotic stimuli significantly lower in valence than men**.
 
-```{r}
+```{r Valence3}
 m_v <- glmmTMB::glmmTMB(Valence ~ Gender + (1|Participant), family=glmmTMB::ordbeta(),
@@
 
-```{r}
+```{r Valence plot}
 estimate_relation(m_v) |> 
@@
 
-In contrast to [study1](https://realitybending.github.io/FictionEro/study1/analysis/2_emotions.html) arousal ratings differ by whether the images were preceeded by 'photograph' or by 'ai-generated'.
+In contrast to [study1](https://realitybending.github.io/FictionEro/study1/analysis/2_emotions.html) arousal ratings for some images differ by whether the images were preceeded by 'photograph' or by 'AI-generated'.
 
-```{r}
+```{r Arousal Desc}
 #| fig-height: 12
@@
 
-This model examines the effect of **gender and condition on Arousal**, accounting for random variability due to participants and items (i.e., random intercepts).
+This model examines the effect of **Gender and Condition on Arousal**, accounting for random variability due to participants and items (i.e., random intercepts).
 
@@
 
-```{r}
+```{r Arousal Model}
 
@@
 
-No other moderators showed statistically significant effects on arousal across the interactions of gender, condition (Ai-generated vs Photograph), and the respective moderators.
+No other moderators showed statistically significant effects on arousal across the interactions of gender, condition (AI-generated vs Photograph), and the respective moderators.
 
@@
 
-```{r}
+```{r Arousal Moderator}
 test_moderator <- function(df, outcome="Arousal", moderator="BAIT_Visual") {
@@
 
-```{r}
+```{r Arousal Moderator Feedback}
 feedback_results <- data.frame()
@@
 
-```{r}
+```{r Arousal Sexual Activity}
 
@@
 
-```{r}
+```{r Arousal Believed}
   m <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition + (1|Participant) + (1|Stimulus),
@@
 
-```{r}
+```{r Arousal Believed2}
 
@@
 
-Enticment ratings differ by whether the images were preceeded by 'photograph' or by 'ai-generated'.
+Enticment ratings, for some images, differ by whether the images were preceeded by 'photograph' or by 'AI-generated'.
 
-```{r}
+```{r Enticement Desc}
 #| fig-height: 12
@@
 
+Across both conditions, women rated the images as less enticing overall than men.
 There was a significant interaction between gender and image condition, whereby men were less enticed by AI-generated images, whereas women showed no significant difference in enticement based on image condition.
-Across both conditions, women rated the images as less enticing overall than men.
 
 We also analyzed the average marginal effect of the variable “Condition” (comparing AI-Generated to Photograph) separately for males and females.
-
 For males, enticement ratings are significantly lower on average for AI-Generated images compared to Photograph  images.
@@
 
-```{r}
+```{r Enticement Model}
 m_enticement <- glmmTMB::glmmTMB(Enticing ~ Gender / Condition + 
@@
 Looking at **feedback as a moderator**, the results showed that enticement ratings for images labelled as AI-Generated were moderated by the feedback that AI is less attractive for males, and that difference between the AI-Generated images and real photos is obvious for females.
+Specifically,
 
@@
 <!-- Note: Feedback that 'No Images were Arousing' , 'Some Images were Arousing' and the 'difference between real and photos was Subtle' only had 1 level, hence were excluded from the following analysis -->
-```{r}
+```{r Enticement Moderator}
 for(m in c("BAIT_Visual", "BAIT_Text", "BAIT_ExpertAI",
@@
 
-```{r}
+```{r Enticement Moderator Feedback}
+feedback_results <- data.frame()
 for(m in c("Feedback_NoFacesAttractive", "Feedback_SomeFacesAttractive",
@@
 
-```{r}
+```{r Enticement Sexual Activity}
 m <- glmmTMB::glmmTMB(Enticing ~ Gender / (Condition * SexualActivity_num) + (Condition | Participant) + (1|Stimulus),
@@
 
-```{r}
+```{r Enticement Believed1}
 m <- glmmTMB::glmmTMB(Enticing ~ Gender / Condition + (1 | Participant) + (1|Stimulus),
@@
 
-```{r}
+```{r Enticement Believed2}
 
@@
 
-```{r}
+```{r Valence Desc}
 #| fig-height: 12
@@
 
-```{r}
+```{r Valence Model}
 m_valence <- glmmTMB::glmmTMB(Valence ~ Gender / Condition + 
@@
 The results showed that enticing ratings for images labeled AI-generated were moderated by the feedback reporting attitudes towards AI, but this was only significant for women.
-More specifically, females who have more positive and negative attitudes towards AI rated images labelled as AI-Generated significantly higher and lower in valence compared to images labelled as photographs
+More specifically, females who have more positive and negative attitudes towards AI rated images labelled as AI-Generated significantly higher and lower in valence compared to images labelled as photographs.
 
@@
 
-```{r}
+```{r Valence Moderator}
 for(m in c("BAIT_Visual", "BAIT_Text", "BAIT_ExpertAI",
@@
 
-```{r}
+```{r Valence Moderator Feedback}
 feedback_results <- data.frame()
@@
 
-```{r}
+```{r Valence Believed1}
 m <- glmmTMB::glmmTMB(Valence ~ Gender /Condition + (1| Participant) + (1|Stimulus),
@@
 
-```{r}
+```{r Valence Beleived2}
 moderator_believed <- data.frame()
@@
 
-```{r}
+```{r Emotionality Factor}
 pca <- principal_components(df[c("Valence", "Arousal", "Enticing")], n = 2)
@@
 
-```{r}
+```{r EMotionality Plot}
 df$Emotionality <- as.numeric(normalize(predict(pca)$PC1))
@@
 
-```{r}
+```{r Emotionality Desc}
 emotionality_desc <- plot_descriptive(df, "Emotionality")
@@
 
-```{r}
+```{r Emotionality Model}
 m <- glmmTMB::glmmTMB(Emotionality ~ Gender / Condition + (1| Participant) + (1|Stimulus),
@@
 results_table(m)
-```
 
-```{r}
 marginaleffects::avg_slopes(m, variables="Condition", by="Gender", re.form=NA)
@@
 
-```{r}
+```{r Emotionality Moderator}
 for(m in c("BAIT_Visual", "BAIT_Text", "BAIT_ExpertAI",
@@
 
-```{r}
+```{r Emotionality Moderator Feedback}
 feedback_results <- data.frame()
@@
 
-```{r}
+```{r EMotionality Believed1}
 m <- glmmTMB::glmmTMB(Emotionality ~ Gender / Condition + (1 | Participant) + (1|Stimulus),
@@
 
-```{r}
+```{r Emotionality2}
 moderator_believed <- data.frame()
@@
 2. 'Porn' factor was not computed, instead sexual activity and frequency of watching porn were treated seperate. 
+3. Missing final figures and interpretation of belief as influencing emotional ratings of images

### 2025-05-09 study2/analysis/3_realness.qmd
updated scripts

@@
   geom_histogram(aes(color=Realness_Extreme), position = "identity", bins=15) +
+  scale_x_continuous(
+    breaks = c(0, 1),
+    labels = c("AI","Real")) +
   facet_grid(Gender ~ ConditionBelief, scales="free_y") +
@@
 
-Here, we are examining the effect of various physical characteristics of the images to evaluate whether they influence the perceived realness of the images.
+Here, we are examining the effect of various **physical characteristics** of the images to evaluate whether they influence the perceived realness of the images.
 Neither Entropy, Complexity, Contrast, nor Luminance significantly influence the perceived realness of the images, nor the likelihood of realness being above 0.5 ("RealnessBelief"), as indicated by the lack of significant effects.
@@
 
-This model examines the influence gender and condition on ratings of realness, incorporating random intercepts for participants and items.
-
-<!-- Intercept: Male and Photograph -->
+This model examines the influence **Gender and Condition** on ratings of realness, incorporating random intercepts for participants and items.
 
@@
 This model looks at whether realness ratings are moderated by attitudes towards AI.
-
 Looking at the results, the influence of Gender and Condition on Realness scores was not moderated by attidues towards AI.
@@
 This model evaluates how ratings of realness, predicted by Gender and Condition, are moderated by participants' report of how often they engaged in sexual activity and how often they view pornography.
-
 Looking at porn frequency and sexual activity, the influence of Gender and Condition on Realness scores was not moderated by these variables.
@@
 
-- For males the realness ratings were lower for images labelled AI-Generated compared to real photographs.
+- For **males** the **realness ratings were lower for images labelled AI-Generated** compared to real photographs.
 For females they also rated images labelled as AI-Generated as less Real, altough this effect was not significant.
-- Looking at moderators, attitudes towards AI, participants reports of how often they engaged in sexual activity and how often they view pornography, did not moderate realness ratings
-- Looking at the feedback as a moderator for realness ratings, for males, feedback that AI-generated images were less arousing increased realness ratings for those images, and believing all images were real raised realness ratings across all images.
-For females, the belief that no faces were attractive raised realness ratings for the images.
+- Looking at moderators, **attitudes towards AI**, participants reports of **how often they engaged in sexual activity** and **how often they view pornography**, did **not moderate realness ratings**
+- Looking at the **feedback as a moderator** for realness ratings, for **males**, feedback that **AI-generated images were less arousing increased realness ratings for those images**, and believing all images were real raised realness ratings across all images.
+For females, the **reporting that no faces were attractive increased realness ratings** for the images.
 

### 2025-05-12 study2/analysis/2_emotion.qmd
emotions html

@@
 **Gender Differences**
-- Women rate stimuli on average significantly lower in arousal, enticiment and valence than men, however this difference was not significant for valence.
 
--Males rated AI-generated images significantly lower than photographs in arousal, valence, and enticement.
+- Main manipulation worked for men only - i.e., reality manipulation on the nature of the stimuli on subjective ratings
+
+- Males rated AI-generated images significantly lower than photographs in arousal, valence, and enticement.
 Females showed no significant difference in ratings between AI-generated and photographic images across all outcomes.
 
+- Women rate stimuli on average significantly lower in arousal, enticement and valence than men, however this difference was not significant for valence.
+
 **Moderators**
+
 - For women, **positive attitudes towards AI** moderated arousal, enticement, and valence ratings, resulting in **more favorable evaluations of AI-generated images**.

### 2025-05-13 study2/analysis/1_cleaning.qmd
data analysis
lacking final figures and rendering emotions analysis script
updated analysis

@@
 ::: {.panel-tabset}
-
-### Old vs New feedback
-
-Due to a mistake in the study's implementation, some of the feedback was incorrect, e.g., "Some faces were attractive" and "AI-generated faces were less attractive" rather than "Some images were arousing" and "AI-generated images were less arousing".
-
-```{r}
-
-table(df$version)
-
-```
 
@@
 
-# outliers$Mobile <- sum(df$Mobile=="True")
+outliers$Mobile <- sum(df$Mobile=="True")
+
+df <- filter(df, Mobile == "False")
+dftask <- filter(dftask, Participant %in% df$Participant)
 ```
@@
 ### BAIT Questionnaire Duration
-#
+
 ```{r}
@@
 The final sample includes `r report::report_participants(df, age="Age", sex="Sex", education="Education")`.
+
+**NOTE** that due to a mistake in the study's implementation, some of the feedback was incorrect, e.g., "Some faces were attractive" and "AI-generated faces were less attractive" rather than "Some images were arousing" and "AI-generated images were less arousing".
+
+`r sum(df$version=="old")` participants had the old version of the feedback and `r sum(df$version=="new")` had the newer version.
 

### 2025-05-13 study2/analysis/2_emotion.qmd
updated analysis

@@
     breaks = c(0, 1),
-    labels = c("Not at all","Very much")) +
-  scale_fill_manual(values=c("Female"="#E91E63", "Male"="#FF9800"), guide="none") +
+    labels = c("Unplesant","Pleasant")) +
+  scale_fill_manual(values=c("Male"="#E91E63", "Female"="#FF9800"), guide="none") +
   labs(title = "Valence", ) +
@@
     breaks = c(0, 1),
-    labels = c("Not at all","Very much")) +
+    labels = c("Unplesant","Pleasant")) +
   facet_grid(Gender~ConditionBelief, scales="free_y") +

### 2025-05-20 study2/analysis/1_cleaning.qmd
updated htmls

@@
     axis.text.y = element_text(size = rel(1.1)),
-    axis.text.x = element_text(size = rel(1.1), angle = 55, hjust = 1),
+    axis.text.x = element_text(size = rel(1.1), angle = 75, hjust = 1),
     axis.title.x = element_blank()
@@
   scale_y_continuous(labels = scales::percent)  +
-  labs(title="Experiment Enjoyment",
-       subtitle="Proportion of participants by condition") + 
+  labs(title="Experiment Enjoyment")+
   guides(fill = guide_legend(reverse=TRUE)) +
@@
 
+### Innapropriate Stimuli
+
+```{r}
+
+femalehetero_malecouple <- dftask |> 
+  filter(Gender == "Female" & SexualOrientation == "Heterosexual", str_detect(Stimulus, "^Male_couple")) |> 
+  select(Participant, Gender, SexualOrientation, Stimulus) |> 
+  distinct()
+
+malehetero_femalecouple <- dftask |> 
+  filter(Gender == "Male" & SexualOrientation == "Heterosexual", str_detect(Stimulus, "^Female_couple")) |> 
+  select(Participant, Gender, SexualOrientation, Stimulus) |> 
+  distinct()
+
+femalehomo_male <- dftask |> 
+  filter(Gender == "Female" & SexualOrientation == "Homosexual", str_detect(Stimulus, "^Male")) |> 
+  select(Participant, Gender, SexualOrientation, Stimulus) |> 
+  distinct()
+
+malehomo_female <- dftask |> 
+  filter(Gender == "Male" & SexualOrientation == "Homosexual", str_detect(Stimulus, "^Female")) |> 
+  select(Participant, Gender, SexualOrientation, Stimulus) |> 
+  distinct()
+
+outliers$IrrStimuli <- unique(filter(femalehetero_malecouple)$Participant)
+
+```
+
+We removed `r sum(df$Participant=="S030")` from the rest of the analysis considering their stimuli choice was not relevant to their sexual orientation - i.e., self-assigned as Heterosexual and choosing male-couples as stimuli.
+
+```{r}
+df<- filter(df, !Participant=="S030")
+df <- filter(df, !Participant %in% outliers$IrrStimuli)
+dftask <- filter(dftask, !Participant %in% outliers$IrrStimuli)
+
+```
+
 ## Final Sample

### 2025-05-20 study2/analysis/2_emotion.qmd
updated htmls

@@
          )|>
-  mutate(across(starts_with("Feedback_"), as.factor))
+  mutate(across(starts_with("Feedback_"), as.factor)) |>
+  mutate(ConditionBelief = as.factor(ConditionBelief))
 
@@
     filter(Condition == "Photograph") |> 
-    arrange(Relevance, diff, mean)
+    arrange(diff, mean)
 
@@
     left_join(order[c(".Item_Order", "diff")], by=".Item_Order") |>
-    mutate(.Item_Order = fct_relevel(.Item_Order, order$.Item_Order)) |>
+mutate(.Item_Order = fct_relevel(.Item_Order, intersect(order$.Item_Order, unique(.Item_Order)))) |>
     # mutate(.average = mean(.data[[target]]), .by="Item") |>
@@
 ```{r Enticement Moderator Feedback}
-feedback_results <- data.frame()
 for(m in c("Feedback_NoFacesAttractive", "Feedback_SomeFacesAttractive",
@@
 
-sex_act_plot<- estimate_relation(m, length=20) |> 
+sex_act_plot_ent<- estimate_relation(m, length=20) |> 
   ggplot(aes(x=SexualActivity_num, y=Predicted)) +
@@
 
-sex_act_plot
+sex_act_plot_ent
 ```
@@
 ```{r Enticement Believed2}
-
-moderator_believed <- data.frame()
 for(m in c("BAIT_Visual", "BAIT_Text", "BAIT_ExpertAI",
@@
 ```{r Valence Moderator Feedback}
-feedback_results <- data.frame()
 for(m in c("Feedback_NoFacesAttractive", "Feedback_SomeFacesAttractive",
@@
 ```{r Valence Beleived2}
-moderator_believed <- data.frame()
 for(m in c("BAIT_Visual", "BAIT_Text", "BAIT_ExpertAI",
@@
 ```{r Emotionality Moderator Feedback}
-feedback_results <- data.frame()
 for(m in c("Feedback_NoFacesAttractive", "Feedback_SomeFacesAttractive",
@@
 ```{r Emotionality2}
-moderator_believed <- data.frame()
 for(m in c("BAIT_Visual", "BAIT_Text", "BAIT_ExpertAI",

### 2025-05-20 study2/analysis/0_preprocessing.py

@@ -610,7 +610,7 @@ data_demo = replace_value(data_demo, "Discipline", "Other_Health and Life Scienc
 data_demo = replace_value(data_demo, "Discipline", "Other_cognitive behavioural psychotherapy", "Psychology, Neuroscience")
 data_demo = replace_value(data_demo, "Discipline", "Other_Design", "Other")
 
-# data_demo["SexualOrientation"][data_demo["SexualOrientation"].str.contains("Other_").values].values
+data_demo["SexualOrientation"][data_demo["SexualOrientation"].str.contains("Other_").values].values
 data_demo = replace_value(data_demo, "SexualOrientation", "Other_Straight", "Heterosexual")
 
 # data_demo["SexualStatus"][data_demo["SexualStatus"].str.contains("Other_").values].values

### 2025-05-21 study2/analysis/2_emotion.qmd
Update 2_emotion.qmd

@@
 
+<!-- predictions(): unit-level (conditional) estimates. -->
+
+<!-- avg_predictions(): average (marginal) estimates. -->
+
+```{r}
+
+pred1 <- rbind(
+  marginaleffects::avg_predictions(m_arousal, by=c("Gender", "Condition"), newdata = "mean", re.form=NA) |>
+  as.data.frame() |> 
+  mutate(Outcome="Arousal"),
+  marginaleffects::avg_predictions(m_enticement, by=c("Gender", "Condition"), newdata = "mean", re.form=NA) |>
+  as.data.frame() |> 
+  mutate(Outcome="Enticement"),
+  marginaleffects::avg_predictions(m_valence, by=c("Gender", "Condition"), newdata = "mean", re.form=NA) |>
+  as.data.frame() |> 
+  mutate(Outcome="Valence")
+)
+
+stars1 <- data.frame(label=c("**", "***", "***", "*"),
+                    Gender=fct_relevel(c("Male", "Male", "Male", "Female"), "Male"),
+                    Outcome=c("Arousal", "Enticement", "Valence", "Valence"),
+                    y=c(0.55, 0.58, 0.62, 0.6))
+
+p1 <- pred1 |>
+  mutate(Gender = fct_relevel(Gender, "Male", "Female")) |> 
+  ggplot(aes(x=Outcome, y=estimate)) +
+  geom_hline(yintercept=0, color="darkgrey") +
+  geom_line(aes(group=Condition, color=Condition), position = position_dodge(width=0.2), alpha=0.8, linewidth=0.2) +
+  geom_pointrange(aes(ymin = conf.low, ymax=conf.high, color=Condition), position = position_dodge(width=0.2), size=0.2) +
+  geom_text(data=stars1, aes(y=y, label=label), hjust=0.5, size=3) +
+  geom_rect(data=data.frame(Type="All trials", estimate=0.1, Gender=as.factor("Male"), Outcome="Arousal"),
+            aes(xmin=0.8, xmax=1.2, ymin=0.35, ymax=0.6), color="#8BC34A", alpha=0) +
+  geom_rect(data=data.frame(Type="All trials", estimate=0.1, Gender=as.factor("Female"), Outcome="Arousal"),
+            aes(xmin=0.8, xmax=1.2, ymin=0.3, ymax=0.5), color="#8BC34A", alpha=0) +
+  facet_grid(~Gender, switch="y") +
+  scale_y_continuous(limits=c(0, 1), labels=scales::percent) +
+  scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
+  theme_minimal() +
+  theme(axis.title.y = element_blank(),
+        axis.title.x = element_blank(),
+        axis.text.y = element_text(size = 8),
+        strip.placement = "outside",
+        strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
+        strip.text.x = element_text(size = 10),
+        strip.text.y = element_text(size = 10),
+        axis.text.x = element_text(angle=25, hjust=1, vjust=1.1, size=9, color="black"),
+        legend.text = element_text(size = 10),
+        legend.position = ) +
+  labs(color="Images presented as:",
+       tag = "A")
+
+p1
+
+```
+
 ## Notes/ Questions

### 2025-05-21 study2/analysis/2_emotion.qmd
2_emotions update

@@
 
+```{r}
+m1 <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition + (Condition | Participant) + (1|Stimulus),data = df, 
+                      family=glmmTMB::ordbeta(),
+                      control = glmmTMB::glmmTMBControl(parallel = 8))
+m2 <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition + (Condition | Participant) + (1|Stimulus),
+                      data=filter(df, ConditionBelief == "True"), 
+                      family=glmmTMB::ordbeta(),
+                      control = glmmTMB::glmmTMBControl(parallel = 8))
+m3 <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition  + (Condition | Participant) + (1|Stimulus),
+                      data=filter(df, ConditionBelief == "True", Feedback_AILessAttractive=="True"), 
+                      family=glmmTMB::ordbeta(),
+                      control = glmmTMB::glmmTMBControl(parallel = 8))
+m4 <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition  + (Condition | Participant) + (1|Stimulus),
+                      data=filter(df, ConditionBelief == "True", Feedback_AIMoreAttractive=="True"), 
+                      family=glmmTMB::ordbeta(),
+                      control = glmmTMB::glmmTMBControl(parallel = 8))
+
+stars2 <- data.frame(label=c("**", "***", "*", "*", "**"), 
+                    Gender=fct_relevel(c("Male", "Male", "Male", "Female"), 
+                                    "Male", "Female"), 
+                    Type=c("All trials", "Believed trials", "'AI was less attractive'", "'AI was more attractive",
+                           "Believed trials", "'AI was less arousing'"), 
+                    y=c(0.65, 0.65, 0.65, 0, 0.65))
+
+pred2 <- rbind(
+  estimate_relation(m1) |> 
+    mutate(Type = "All trials"),
+  estimate_relation(m2) |> 
+    mutate(Type = "Believed trials"),
+  estimate_relation(m3) |> 
+    mutate(Type = "'AI was less attractive'"),
+  estimate_relation(m4) |> 
+    mutate(Type = "'AI was more attractive'"))
+
+p2 <- pred2 |> 
+  mutate(Type = fct_relevel(Type, "All trials", "Believed trials", "'AI was less attractive'", "'AI was more attractive'")) |> 
+  ggplot(aes(x=Type, y=Predicted)) +
+  geom_hline(yintercept=0, color="darkgrey") +
+  geom_line(aes(group=Condition, color=Condition), position = position_dodge(width=0.2), alpha=0.8, linewidth=0.1) +
+  geom_bar(stat="identity", aes(fill=Condition), position = position_dodge(width=0.2), width=0.2, alpha=0.6) +
+  geom_pointrange(aes(ymin = CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.2), size=0.2) +
+  geom_rect(data=data.frame(Type="All trials", Predicted=0.1, Gender=as.factor("Male")),
+            aes(xmin=0.7, xmax=1.3, ymin=0.35, ymax=0.55), color="#8BC34A", alpha=0) +
+  geom_rect(data=data.frame(Type="All trials", Predicted=0.1, Gender=as.factor("Female")),
+            aes(xmin=0.7, xmax=1.3, ymin=0.30, ymax=0.48), color="#8BC34A", alpha=0) +
+  # geom_text(data=stars2, aes(y=y, label=label), hjust=0.5, size=3) +
+  facet_grid(~Gender) +
+  scale_y_continuous(labels=scales::percent) +
+  scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
+  scale_fill_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
+  labs(y="Arousal",
+       tag = "B") +
+  theme_minimal() +
+  theme(axis.title.x = element_blank(),
+        axis.text.x = element_text(angle=25, hjust=1, vjust=1.1, size=9),
+        axis.text.y = element_text(size = 8),
+        axis.title.y = element_text(size = 10),
+        strip.placement = "outside",
+        strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
+        strip.text.x = element_text(size = 10),
+        legend.position = "none")
+
+p2
+
+```
+
 ## Notes/ Questions

### 2025-05-23 study2/analysis/2_emotion.qmd
updated analysis

--- 2025-05-21 study2/analysis/2_emotion.qmd
@@
          Gender =  fct_relevel(Gender, "Male", "Female"),
+         SexualOrientation = fct_relevel(SexualOrientation, "Heterosexual", "Homosexual", "Bisexual"),
          PornFrequency = as.numeric(as.factor(COPS_Frequency)),
@@
 
-**Note**: [These calculations are based on the validation of the BAIT scale](https://realitybending.github.io/FictionEro/study1/analysis/1_cleaning.html)
-
 ```{r Bait Dimensions}
@@
 ```
+**Note**: [The calculations for the BAIt/GAAIS dimensions were based on the validation of the BAIT scale](https://realitybending.github.io/FictionEro/study1/analysis/1_cleaning.html)
+
+**BAIT_Videos** was calculated by averaging participants’ agreement with the statement that current AI algorithms can generate very realistic videos and the inverse of their agreement with the statement that videos generated by AI have obvious problems that make them easy to spot as fake.
+**Higher scores** reflect **stronger beliefs in the visual realism and technical reliability of AI-generated videos**.
+
+**BAIT_Visual** was computed as the average of four items: belief that AI algorithms can generate very realistic images, the inverse of belief that AI-generated images always contain errors and artifacts, agreement that CGI can perfectly imitate reality, and belief that technology allows the creation of environments that seem just as real as reality.
+**Higher scores capture stronger beliefs in the visual realism and immersive quality of AI-generated and computer-generated content**.
+
+**BAIT_Text** was calculated by averaging agreement with the belief that AI assistants can write texts indistinguishable from those written by humans and the inverse of the belief that AI-written documents usually read differently than human-written ones.
+**Higher scores indicate stronger beliefs in the linguistic realism of AI-generated text.**
+
+**BAIT_Negative** was computed by averaging levels of agreement with the statements “AI is dangerous” and “I am worried about future uses of AI”.**This composite reflects participants’ negative attitudes toward AI.**
+
+**BAIT_Positive** was calculated by averaging agreement with the statements “AI is exciting” and “Much of society will benefit from a future full of AI”.
+**This score represents positive attitudes towards AI.**
 
@@
   labs(title = "Arousal", ) +
-  facet_wrap(~Gender) +
+  facet_wrap(Gender~SexualOrientation) +
    scale_fill_manual(values=c("Male"="#E91E63", "Female"="#FF9800"), guide="none") +
@@
 m3 <- glmmTMB::glmmTMB(Arousal ~ Gender + (1|Participant) + (1+Gender|Stimulus ), data=df)
-
-test_bf(m1,m2, m3)
-compare_performance(m1, m2, m3)
+m4 <- glmmTMB::glmmTMB(Arousal ~ Gender/SexualOrientation + (1|Participant), data=df)
+m5 <- glmmTMB::glmmTMB(Arousal ~ Gender/SexualOrientation + (1|Participant) + (1|Stimulus ), data=df)
+m6 <- glmmTMB::glmmTMB(Arousal ~ Gender/SexualOrientation + (1|Participant) + (1+Gender|Stimulus ), data=df)
+
+test_bf(m1,m2, m3, m4, m5,)
+compare_performance(m1, m2, m3, m4, m5, m6)
 
@@
 
-This model evaluate ths the effects of Gender on Arousal, accounting for random variability due to participants (i.e., random effects).
+This model evaluate ths the effects of Gender and Sexual Orientation on Arousal, accounting for random variability due to participants (i.e., random effects).
 The analysis revealed that on average **women rate erotic stimuli significantly lower in arousal than men**.
 
+There was no difference between heterosexual, homosexual, and bisexual individuals within each gender on arousal ratings.
+
 ```{r Arousal3}
 
-m_a <- glmmTMB::glmmTMB(Arousal ~ Gender + (1|Participant),
+m_a <- glmmTMB::glmmTMB(Arousal ~ Gender/ SexualOrientation + (1|Participant),
                       data=df, family=glmmTMB::ordbeta(),
@@
 estimate_relation(m_a) |> 
-  ggplot(aes(x=Gender, y=Predicted)) +
+  ggplot(aes(x=SexualOrientation, y=Predicted)) +
   geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color = Gender), position=position_dodge(width=0.5)) +
  scale_color_manual(values=c("Male"="#E91E63", "Female"="#FF9800"), guide="none") +  labs(y="Arousal") +
+  facet_wrap(~Gender) +
   theme_abyss()
@@
   labs(title = "Enticement", ) +
-  facet_wrap(~Gender) +
+  facet_wrap(Gender~SexualOrientation) +
   scale_fill_manual(values=c("Male"="#E91E63", "Female"="#FF9800"), guide="none") +
@@
 
+There was no difference between heterosexual, homosexual, and bisexual individuals within each gender on arousal ratings.
+
 ```{r Enticicement3}
-m_e <- glmmTMB::glmmTMB(Enticing ~ Gender + (1|Participant),
+m_e <- glmmTMB::glmmTMB(Enticing ~ Gender/SexualOrientation + (1|Participant),
                       data=df,family=glmmTMB::ordbeta(),
@@
   geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color = Gender), position=position_dodge(width=0.5)) +
- scale_color_manual(values=c("Male"="#E91E63", "Female"="#FF9800"), guide="none") +  labs(y="Enticement") +
+ scale_color_manual(values=c("Male"="#E91E63", "Female"="#FF9800"), guide="none") + 
+  facet_wrap(~SexualOrientation) +
+  labs(y="Enticement") +
   theme_abyss()
@@
   labs(title = "Valence", ) +
-    facet_wrap(~Gender) +
+    facet_wrap(Gender~SexualOrientation) +
   theme_abyss() +
@@
 
+There was no difference between heterosexual, homosexual, and bisexual individuals within each gender on arousal ratings.
+
 ```{r Valence3}
-m_v <- glmmTMB::glmmTMB(Valence ~ Gender + (1|Participant), family=glmmTMB::ordbeta(),
+m_v <- glmmTMB::glmmTMB(Valence ~ Gender/SexualOrientation+ (1|Participant), family=glmmTMB::ordbeta(),
                       data=df,
@@
  scale_color_manual(values=c("Male"="#E91E63", "Female"="#FF9800"), guide="none") +  labs(y="Valence") +
+  facet_wrap(~SexualOrientation) +
   theme_abyss()
@@
 
+```{r}
+
+df <- df |>
+  filter(SexualOrientation == "Heterosexual")
+
+```
+
+Due to the low number of participants self-described as Bisexual (N= `r sum(dfsub$SexualOrientation=="Bisexual")`) and Homosexual  (N= `r sum(dfsub$SexualOrientation=="Homosexual")`) the main analysis will focus solely on Heterosexual individuals.
+
+Exploratory analysis will then evaluate the effect of sexual orientation on ratings.
+
 ## Arousal
@@
 In contrast to [study1](https://realitybending.github.io/FictionEro/study1/analysis/2_emotions.html) arousal ratings for some images differ by whether the images were preceeded by 'photograph' or by 'AI-generated'.
+A possible explanation might be due to the lower number of participants compared to study1.
 
@@
 
-This model examines the effect of **Gender and Condition on Arousal**, accounting for random variability due to participants and items (i.e., random intercepts).
+This model examines the effect of **Gender Sexual Orientation and Condition on Arousal**, accounting for random variability due to participants and items (i.e., random intercepts).
 
@@
            "Feedback_LabelsIncorrect", "Feedback_LabelsReversed",
-           "Feedback_AllReal", "Feedback_AllFake")) {
+           "Feedback_AllReal", "Feedback_AllFake",
+
+           "AllRealConfidence","AllFakeConfidence" ,
+           "Enjoyment")) {
   feedback_results <- rbind(feedback_results,
@@
 
-- Women rate stimuli on average significantly lower in arousal, enticement and valence than men, however this difference was not significant for valence.
+- Women rate stimuli on average lower in arousal, enticement and valence than men, however this difference was not significant.
 
@@
 
-- For women, **positive attitudes towards AI** moderated arousal, enticement, and valence ratings, resulting in **more favorable evaluations of AI-generated images**.
+- For women, **positive attitudes towards AI** moderated arousal and enticement, resulting in **more favorable evaluations of AI-generated images**.
 Negative attitudes moderated valence ratings, leading to less favorable evaluations.
 
-- For men, negative attitudes towards AI moderated only enticement ratings, with more negative views leading to less enticing ratings of AI-generated images.
-
-- Men’s **perceptions of the attractiveness of AI-generated images** moderated both arousal and enticement ratings.
-More attractive AI images were rated as more arousing and enticing, while less attractive AI images were rated as less arousing.
-
-- Women’s feedback about the differences between AI and real images being obvious moderated both enticement and valence ratings, with AI-generated images rated as less enticing and less valent.
+- **negative attitudes towards AI** moderated valence ratings for both genders
+
+- Reporting having **higher knowledge about AI** moderated valence ratings for men
+
+- **Sexual activity** moderated enticement ratings for females. Specifically, females who reported having sexual activity within the 3 previous days tended to rate AI images higher in enticement.
+
+- Men’s **perceptions of the attractiveness of AI-generated images** moderated both arousal and valence ratings. More attractive AI images were rated as more arousing and valent.
+
+- Female's feedback that **no images were attractive** moderated arousal ratings.
 
@@
 
-stars1 <- data.frame(label=c("**", "***", "***", "*"),
-                    Gender=fct_relevel(c("Male", "Male", "Male", "Female"), "Male"),
-                    Outcome=c("Arousal", "Enticement", "Valence", "Valence"),
-                    y=c(0.55, 0.58, 0.62, 0.6))
+stars1 <- data.frame(label=c("**", "***", "**"),
+                    Gender=fct_relevel(c("Male", "Male", "Male"), "Male"),
+                    Outcome=c("Arousal", "Enticement", "Valence"),
+                    y=c(0.55, 0.58, 0.62))
 
@@
 
+```{r}
+m1 <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition + (Condition | Participant) + (1|Stimulus),data = df, 
+                      family=glmmTMB::ordbeta(),
+                      control = glmmTMB::glmmTMBControl(parallel = 8))
+m2 <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition + (Condition | Participant) + (1|Stimulus),
+                      data=filter(df, ConditionBelief == "True"), 
+                      family=glmmTMB::ordbeta(),
+                      control = glmmTMB::glmmTMBControl(parallel = 8))
+m3 <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition  + (Condition | Participant) + (1|Stimulus),
+                      data=filter(df, ConditionBelief == "True", Feedback_AILessAttractive=="True"), 
+                      family=glmmTMB::ordbeta(),
+                      control = glmmTMB::glmmTMBControl(parallel = 8))
+m4 <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition  + (Condition | Participant) + (1|Stimulus),
+                      data=filter(df, ConditionBelief == "True", Feedback_AIMoreAttractive=="True"), 
+                      family=glmmTMB::ordbeta(),
+                      control = glmmTMB::glmmTMBControl(parallel = 8))
+
+stars2 <- data.frame(label=c("**", "*"),
+                    Gender=fct_relevel(c("Male", "Male")),
+                    Type=c("All trials", "'AI was more attractive'"),
+                    y=c(0.52, 0.65))
+
+pred2 <- rbind(
+  estimate_relation(m1) |> 
+    mutate(Type = "All trials"),
+  estimate_relation(m2) |> 
+    mutate(Type = "Believed trials"),
+  estimate_relation(m3) |> 
+    mutate(Type = "'AI was less attractive'"),
+  estimate_relation(m4) |> 
+    mutate(Type = "'AI was more attractive'"))
+
+p2 <- pred2 |> 
+  mutate(Type = fct_relevel(Type, "All trials", "Believed trials", "'AI was less attractive'", "'AI was more attractive'")) |> 
+  ggplot(aes(x=Type, y=Predicted)) +
+  geom_hline(yintercept=0, color="darkgrey") +
+  geom_line(aes(group=Condition, color=Condition), position = position_dodge(width=0.2), alpha=0.8, linewidth=0.1) +
+  geom_bar(stat="identity", aes(fill=Condition), position = position_dodge(width=0.2), width=0.2, alpha=0.6) +
+  geom_pointrange(aes(ymin = CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.2), size=0.2) +
+  geom_rect(data=data.frame(Type="All trials", Predicted=0.1, Gender=as.factor("Male")),
+            aes(xmin=0.7, xmax=1.3, ymin=0.35, ymax=0.55), color="#8BC34A", alpha=0) +
+  geom_rect(data=data.frame(Type="All trials", Predicted=0.1, Gender=as.factor("Female")),
+            aes(xmin=0.7, xmax=1.3, ymin=0.30, ymax=0.48), color="#8BC34A", alpha=0) +
+  geom_text(data=stars2, aes(y=y, label=label), hjust=0.5, size=3) +
+  facet_grid(~Gender) +
+  scale_y_continuous(labels=scales::percent) +
+  scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
+  scale_fill_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
+  labs(y="Arousal",
+       tag = "B") +
+  theme_minimal() +
+  theme(axis.title.x = element_blank(),
+        axis.text.x = element_text(angle=25, hjust=1, vjust=1.1, size=9),
+        axis.text.y = element_text(size = 8),
+        axis.title.y = element_text(size = 10),
+        strip.placement = "outside",
+        strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
+        strip.text.x = element_text(size = 10),
+        legend.position = "none")
+
+p2
+
+```
+
+```{r}
+
+dfsub$Gender <- as.factor(dfsub$Gender)
+dfsub$Gender <- fct_relevel(dfsub$Gender, "Male", "Female")
+dfsub$BAIT_Visual = (dfsub$BAIT_ImagesRealistic + (1 - dfsub$BAIT_ImagesIssues) + dfsub$BAIT_ImitatingReality + dfsub$BAIT_EnvironmentReal) / 4
+
+m6 <- glm(Feedback_NoFacesAttractive ~ Gender / BAIT_Visual, 
+    data=mutate(dfsub, Feedback_NoFacesAttractive = ifelse(Feedback_NoFacesAttractive =="True", 1, 0)), 
+    family="binomial")
+
+results_table(m6)
+```
+
 ## Notes/ Questions

### 2025-05-23 study2/analysis/3_realness.qmd
updated analysis

@@
   mutate(Condition = fct_relevel(Condition, "Photograph", "AI-Generated"),
+         SexualOrientation = fct_relevel(SexualOrientation,"Heterosexual", "Homosexual", "Bisexual"),
          Gender =  fct_relevel(Gender, "Male", "Female"),
@@
   scale_y_sqrt(expand = c(0, 0)) +
+  facet_wrap(Gender~SexualOrientation) +
   labs(title = "Realness") +
@@
 
+```{r}
+
+df <- df|>
+  filter(SexualOrientation == "Heterosexual")
+```
 ## Physical Characteristics
@@
 
-Here we look at whether the findings above are moderated by **AI-Generated, Porn frequency and sexual activity or feedback**
+Here we look at whether the findings above are moderated by **AI-Generated, Porn frequency and sexual activity or feedback**.
+Note that the focus solely on heterosexaul individuals (N = `r sum(dfsub$SexualOrientation == "Heterosexual")`)
 
@@
            "Feedback_LabelsIncorrect", "Feedback_LabelsReversed",
-           "Feedback_AllReal",
-           "Feedback_AllFake")) {
+           "Feedback_AllReal", "Feedback_AllFake",
+           "AllRealConfidence","AllFakeConfidence" ,
+           "Enjoyment")) {
   moderator <- rbind(moderator, test_moderator(df, m))
@@
                          (Feedback_AILessArousing / Condition) + 
-                        (1 | Participant) + (1|Stimulus),
+                        (1|Participant) + (1|Stimulus),
                       data=df, 
@@
 
-# stars1 <- data.frame(Gender = as.factor("Male"),
-#                      Condition = "AI-Generated",
-#                      label = "***",
-#                      x = 1.5, 
-#                      y = 0.55)
-#
+stars2 <- data.frame(Gender = as.factor(c("Male")),
+                     feedback = as.factor("Feedback_AILessArousing"),
+                    label=c("***"),
+                    x=c(1.03),
+                    y=c(0.58))
+# stars3 <- data.frame(Sex = as.factor(c("Male", "Male", "Female")), 
+#                      label=c("***", "***", "***"),
+#                      x=c(1.1, 1.8, 1.15),
+#                      y=c(0.71, 0.80, 0.615))
 
@@
   # geom_text(data=stars2, aes(x=x, y=y, label=label, color=Condition), hjust=0.5, key_glyph = "blank", size=3) +
-  # geom_text(data=stars1, aes(x=x, y=y, label=label), hjust=0.5, color="#424242", size=3) +
+  geom_text(data=stars2, aes(x=x, y=y, label=label), hjust=0.5, color="#424242", size=3) +
   guides(color=guide_legend(override.aes = list(linewidth = 1.5))) +

### 2025-05-27 study2/analysis/2_emotion.qmd
updated scripts/analysis

@@
 
-stars2 <- data.frame(label=c("**", "*"),
-                    Gender=fct_relevel(c("Male", "Male")),
-                    Type=c("All trials", "'AI was more attractive'"),
-                    y=c(0.52, 0.65))
+stars2 <- data.frame(label=c("**", "***", "*"),
+                    Gender=fct_relevel(c("Male", "Male", "Male")),
+                    Type=c("All trials", "Believed trials" ,"'AI was more attractive'"),
+                    y=c(0.52, 0.56, 0.66))
 

### 2025-05-27 study2/analysis/3_realness.qmd
updated scripts/analysis

@@
                     label=c("***"),
-                    x=c(1.03),
-                    y=c(0.58))
+                    x=c(1.0),
+                    y=c(0.545))
 # stars3 <- data.frame(Sex = as.factor(c("Male", "Male", "Female")), 
@@
   ggplot(aes(x=Feedback_AILessArousing, y=Predicted)) +
-  geom_line(aes(color=Condition, group=Condition), linewidth=.3, position = position_dodge(width=0.2), key_glyph = "path") +
-  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.2), size=0.8, linewidth=1, key_glyph = "blank") +
+  geom_line(aes(color=Condition, group=Condition), linewidth=.3, position = position_dodge(width=0.3), key_glyph = "path") +
+  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.3), size=0.8, linewidth=1, key_glyph = "blank") +
   # geom_text(data=stars2, aes(x=x, y=y, label=label, color=Condition), hjust=0.5, key_glyph = "blank", size=3) +
@@
        x = "\n'AI-Images were less arousing' Feedback",
-       tag = "B")
+       tag = "A")
 
@@
 
-# stars2 <- data.frame(
-#   Gender = as.factor("Male"),
-#   Condition = "AI-Generated",
-#   label = "***",
-#   x = 1.5,
-#   y = 0.5)
+stars3 <- data.frame(Gender = as.factor(c("Female", "Female")), 
+                    Condition=c("Photograph", "AI-Generated"), 
+                    label=c("**", "**"),
+                    x=c(1.3, 1.7),
+                    y=c(0.6, 0.6))
+
+stars4 <- data.frame(Gender = as.factor("Male"), 
+                    Condition="AI-Generated", 
+                    label="***",
+                    x=c(1),
+                    y=c(0.545))
 
@@
   ggplot(aes(x=Feedback_NoFacesAttractive, y=Predicted)) +
-  geom_line(aes(color=Condition, group=Condition), linewidth=.3, position = position_dodge(width=0.2), key_glyph = "path") +
-  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.2), size=0.8, linewidth=1, key_glyph = "blank") +
-  # geom_text(data=stars2, aes(x=x, y=y, label=label, color=Condition), hjust=0.5, key_glyph = "blank", size=3) +
-  # geom_text(data=stars2, aes(x=x, y=y, label=label), hjust=0.5, color="#424242", size=3) +
+  geom_line(aes(color=Condition, group=Condition), linewidth=.3, position = position_dodge(width=0.4), key_glyph = "path") +
+  geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.4), size=0.8, linewidth=1, key_glyph = "blank") +
+  geom_text(data=stars3, aes(x=x, y=y, label=label, color=Condition), hjust=0.5, key_glyph = "blank", size=3) +
+  geom_text(data=stars4, aes(x=x, y=y, label=label), hjust=0.5, color="#424242", size=3) +
   guides(color=guide_legend(override.aes = list(linewidth = 1.5))) +
@@
   labs(y="Realness\n", fill="Images presented as:", color="Images presented as:",
-       x = "\n'AI-Faces were less attractive' Feedback",
+       x = "\n'No faces attractive' Feedback",
        tag = "B")
@@
 
+```{r}
+
+p <- (p1 + theme(legend.position = "none")) / p2  + plot_layout(guides = "collect")
+p
+```
+
 ## Notes/ Questions

### 2025-05-29 study2/analysis/2_emotion.qmd
updated study1 rawdata
@DominiqueMakowski could you check whether the logic is alright, if so I will then re-run the analysis for study 1

@@
 
-test_bf(m1,m2, m3, m4, m5,)
+test_bf(m1,m2, m3, m4, m5,m6)
 compare_performance(m1, m2, m3, m4, m5, m6)
@@
 ```{r EMotionality Plot}
-df$Emotionality <- as.numeric(normalize(predict(pca)$PC1))
+df$Emotionality <- as.numeric(normalize(-predict(pca)$PC1))
 
@@
 
-The results show that females consistently rate photographs as higher in emotionality compared to males. Additonally, males rate AI-Generated images higher in emotionality compared to photographs.
+The results show males rate AI-Generated images lower in emotionality compared to photographs.
 
@@
 
-Looking at **AI-attitudes, porn frequency and sexual activity**, and feedback as moderators, we can see that for females, emotionality ratings for AI-generated images are negatively moderated by positive attitudes towards AI, meaning that females with more positive AI attitudes rate the images as less emotional.
-For males, emotionality ratings are positively moderated by negative attitudes towards AI, meaning that males with more negative AI attitudes rate the images as more emotional.
-
-Looking at **feedback** as a moderator, the results show that emotionality ratings for AI-generated images were significantly moderated only by positive attitudes toward AI in females and negative attitudes toward AI in males.
-
-Interestingly, for females, higher positive attitudes (BAIT Positive) were associated with lower emotionality ratings of AI-generated images.
-For males, higher negative attitudes (BAIT Negative) were associated with higher emotionality ratings.
+Looking at **AI-attitudes, porn frequency and sexual activity**, and feedback as moderators, we can see that for males reporting higher expertise in AI led to an increase of emotionality ratings for images labelled as AI-Generated.
+Additionally, males who reported having more negative attitiudes towards AI, rated AI-Generated images lower in emotionality compared to fotographs.
+While for feamles, those with more positive AI attitudes rate AI-generated images higher in emotionality.
+
+Looking at **feedback** as a moderator, the results show that for males who reported finidng AI-generated images as more attractive rated these images higher in emotionality.Conversely, males who reported finding AI-generated images as less attractive rated these images lower in emotionality.
 

### 2025-05-29 study2/analysis/3_realness.qmd
updated study1 rawdata
@DominiqueMakowski could you check whether the logic is alright, if so I will then re-run the analysis for study 1

@@
 ```
+
 ## Physical Characteristics
@@
 
+### Association betwen Emotional responses and Realness Ratings
+
+**Realness** ratings were positively correlated with **Arousal**, **Enticement**, and **Valence.**
+
+To examine the unique role of **Arousal** in predicting **perceived realness**, a model was tested including both linear and quadratic effects of Arousal, along with its interactions with Gender and Condition (AI-generated vs.
+real images), modeling participants and images as random intercepts.
+To assess whether a non-linear (quadratic) component improved the model, a comparison was conducted between a model including a quadratic term for Arousal and one without.
+The model excluding the quadratic term was decisively favored, with Bayes Factors indicating that the data were over 1000 times more likely under the simpler linear model.
+This strongly supports the adequacy of a linear relationship between Arousal and Realness in this context.
+The following findings were seen in the simpler model:
+
+- **Arousal** had a strong positive linear effect on Realness, indicating that higher arousal was **associated** with **increased perceptions of realness**.
+
+- For **female** participants, the positive **effect of Arousal on Realness** is significantly **weaker** than for **males**.
+This suggests that women are less influenced by Arousal when making realness judgments.
+
+- Among **males**, the effect of **Arousal, on realness ratings**, is significantly **weaker** when judging images previous labelled as **AI-generated** compared to real ones.
+
+These results suggest a gender-specific modulation in how emotional arousal shapes beliefs about what is real, particularly when distinguishing between real and synthetic faces.
+
+```{r}
+df |>
+  select(Gender, Arousal, Enticing, Valence, RealnessBelief, Realness) |>
+  group_by(Gender) |>
+  correlation::correlation()
+
+p_a <- plot(cor_test(df, "Arousal", "Realness")) +
+  ggplot2::facet_wrap(~Gender) +
+  ggplot2::theme_bw()
+
+p_e <- plot(cor_test(df, "Enticing", "Realness")) +
+  ggplot2::facet_wrap(~Gender) +
+  ggplot2::theme_bw()
+
+p_v <- plot(cor_test(df, "Valence", "Realness")) +
+  ggplot2::facet_wrap(~Gender) +
+  ggplot2::theme_bw()
+
+p_sub <- p_a/ p_e/ p_v
+
+m1_dir <- make_model("Realness ~ Arousal / Gender/ Condition + (1 | Participant) + (1|Stimulus)", family=glmmTMB::ordbeta())
+m2_dir <- make_model("Realness ~ poly(Arousal, 2) / Gender/ Condition + (1 | Participant) + (1|Stimulus)", family=glmmTMB::ordbeta())
+
+compare_performance(m1_dir, m2_dir)
+test_performance(m1_dir, m2_dir)
+
+```
+
 ## Summary

### 2025-05-29 study1/analysis/0_preprocessing.py

@@ -1,4 +1,5 @@
 import json
+import os
 
 import numpy as np
 import pandas as pd
@@ -6,45 +7,43 @@ import pandas as pd
 # Note: new data from FakeFace2 got saved in this repo during June 2024.
 # Make sure to use only files before.
 
+# # Get files from OSF ======================================================
+# def osf_listfiles(data_subproject="", token="", after_date=None):
+#     try:
+#         import osfclient
+#     except ImportError:
+#         raise ImportError("Please install 'osfclient' (`pip install osfclient`)")
+#     osf = osfclient.OSF(token=token).project(data_subproject)  # Connect to project
+#     storage = [s for s in osf.storages][0]  # Access storage component
+#     files = [
+#         {
+#             "name": file.name.replace(".csv", ""),
+#             "date": pd.to_datetime(file.date_created),
+#             "url": file._download_url,
+#             "size": file.size,
+#             "file": file,
+#         }
+#         for file in storage.files
+#     ]
 
-# Get files from OSF ======================================================
-def osf_listfiles(data_subproject="", token="", after_date=None):
-    try:
-        import osfclient
-    except ImportError:
-        raise ImportError("Please install 'osfclient' (`pip install osfclient`)")
-    osf = osfclient.OSF(token=token).project(data_subproject)  # Connect to project
-    storage = [s for s in osf.storages][0]  # Access storage component
-    files = [
-        {
-            "name": file.name.replace(".csv", ""),
-            "date": pd.to_datetime(file.date_created),
-            "url": file._download_url,
-            "size": file.size,
-            "file": file,
-        }
-        for file in storage.files
-    ]
-
-    if after_date is not None:
-        date = pd.to_datetime(after_date, format="%d/%m/%Y", utc=True)
-        files = [f for f, d in zip(files, [f["date"] > date for f in files]) if d]
-    return files
+#     if after_date is not None:
+#         date = pd.to_datetime(after_date, format="%d/%m/%Y", utc=True)
+#         files = [f for f, d in zip(files, [f["date"] > date for f in files]) if d]
+#     return files
 
 
-token = ""  # Paste OSF token here to access private repositories
-files = osf_listfiles(
-    token=token,
-    data_subproject="sm4jc",  # Data subproject ID
-    after_date="19/01/2024",
-)
[…]

### 2025-06-04 study1/analysis/0_preprocessing.py
updated data
removed all participants without the language column

@@ -4,41 +4,6 @@ import os
 import numpy as np
 import pandas as pd
 
-# Note: new data from FakeFace2 got saved in this repo during June 2024.
-# Make sure to use only files before.
-
-# # Get files from OSF ======================================================
-# def osf_listfiles(data_subproject="", token="", after_date=None):
-#     try:
-#         import osfclient
-#     except ImportError:
-#         raise ImportError("Please install 'osfclient' (`pip install osfclient`)")
-#     osf = osfclient.OSF(token=token).project(data_subproject)  # Connect to project
-#     storage = [s for s in osf.storages][0]  # Access storage component
-#     files = [
-#         {
-#             "name": file.name.replace(".csv", ""),
-#             "date": pd.to_datetime(file.date_created),
-#             "url": file._download_url,
-#             "size": file.size,
-#             "file": file,
-#         }
-#         for file in storage.files
-#     ]
-
-#     if after_date is not None:
-#         date = pd.to_datetime(after_date, format="%d/%m/%Y", utc=True)
-#         files = [f for f, d in zip(files, [f["date"] > date for f in files]) if d]
-#     return files
-
-
-# token = "zYboMoukFI8HKabenQ35DH6tESHJo6oZll5BvOPma6Dppjqc2jnIB6sPCERCuaqO0UrHAa"  # Paste OSF token here to access private repositories
-# files = osf_listfiles(
-#     token=token,
-#     data_subproject="sm4jc",  # Data subproject ID
-#     after_date="19/01/2024",
-# )
-
 # Loop through files ======================================================
 # Initialize empty dataframes
 alldata = pd.DataFrame()
@@ -59,51 +24,27 @@ path = "C:/Users/asf25/Box/FictionEro1/"
 files = os.listdir(path)
 after_date = pd.to_datetime("2024-01-19")  # Date after which files were added
 cutoff_date = pd.to_datetime("2024-06-01")  
-skipped_files_date = []
-skipped_files_debriefing = []
-wrong_data_files = []
+skipped_files = []
 
+# Convert list of dicts into a DataFrame
+new_data = pd.DataFrame()
 for i, file in enumerate(files):
     print(f"File N°{i+1}/{len(files)}, file: {file}") 
 
     data = pd.read_csv(path + file)
     filename = file.replace(".csv", "")
 
-    # Extract the date from the rows where screen == browser_info
-    date_series = data.loc[data["screen"] == "browser_info", "date"] 
[…]

### 2025-06-04 study1/analysis/1_cleaning.qmd
push
cleaning_script incomplete
script is not rendering due to the addition of the new 60 participants

--- 2024-06-26 analysis/1_cleaning.qmd
@@
 # Used for feedback screen in the new BAIT implementations
-mean(rowMeans(df[c("GAAIS_Positive_12", "GAAIS_Positive_17")]))
+mean(rowMeans(df[c("GAAIS_Positive_12", "GAAIS_Positive_17")])) * 6
 ```
@@
 
-marginaleffects::predictions(m, by=c("AI_Knowledge"), newdata = "marginalmeans") |> 
+marginaleffects::predictions(m, by=c("AI_Knowledge"), newdata = "means") |> 
   as.data.frame() |> 

### 2025-06-10 study1/analysis/1_cleaning.qmd
updated data scripts and data

@@
 
-marginaleffects::predictions(m, by=c("AI_Knowledge"), newdata = "means") |> 
+  modelbased::estimate_means(m, by=c("AI_Knowledge")) |>
   as.data.frame() |> 
-  ggplot(aes(x=AI_Knowledge, y=estimate)) +
+  ggplot(aes(x=AI_Knowledge, y=Mean)) +
   ggdist::stat_halfeye(data=df, aes(y=BAIT_Visual), geom="slab") +
@@
   geom_line(aes(group=1), position = position_dodge(width=0.2)) +
-  geom_pointrange(aes(ymin = conf.low, ymax=conf.high), position = position_dodge(width=0.2)) +
+  geom_pointrange(aes(ymin = CI_low, ymax=CI_high), position = position_dodge(width=0.2)) +
   theme_minimal() +

### 2025-06-10 study1/analysis/2_emotions.qmd
updated data scripts and data

@@
       as.data.frame() |> 
-      select(-Parameter, -SE, -S, z=Statistic, -Predicted) |> 
+      select(-Parameter, -SE, -S, z=Statistic) |> 
       insight::format_table() |> 
@@
 
+<!-- Note: The model did not converge when adding Relevance and Condition as random slopes for Item. -->
+
 ```{r}
@@
 
-```{r}
-m <- glmmTMB::glmmTMB(Arousal ~ Sample / Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
+*Note.* Model converged when adding Relevance and Condition as random slopes of each stimuli.
+
+```{r}
+m <- glmmTMB::glmmTMB(Arousal ~ Sample / Sex / Relevance / Condition + (Relevance | Participant) + ((Relevance / Condition)|Item),
                       data=df, 
@@
 
-```{r}
-m <- glmmTMB::glmmTMB(Arousal ~ Mobile / Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
+*Note.* Model converged when adding Relevance and Condition as random slopes of each stimuli.
+
+```{r}
+m <- glmmTMB::glmmTMB(Arousal ~ Mobile / Sex / Relevance / Condition + (Relevance | Participant) + ((Relevance / Condition)|Item),
                       data=df, 
@@
 
-```{r}
-m <- glmmTMB::glmmTMB(Arousal ~ Sex / Relevance / (Condition * Screen_Size) + (Relevance | Participant) + (1|Item),
+<!-- *Note.* Model converged when adding Relevance and Condition as random slopes of each stimuli. -->
+
+```{r}
+m <- glmmTMB::glmmTMB(Arousal ~ Sex / Relevance / (Condition * Screen_Size) + (Relevance | Participant) + ((Relevance/Condition)|Item),
                       data=standardize(df, select="Screen_Size"), 
@@
 
+<!-- Note. Not enough contrasts to add relevance and condition as random slopes for items -->
 ```{r}
@@
 
-```{r}
-  m <- glmmTMB::glmmTMB(Arousal ~ Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
+<!-- *Note.* Model converged when adding Relevance and Condition as random slopes of each stimuli. -->
+
+```{r}
+  m <- glmmTMB::glmmTMB(Arousal ~ Sex / Relevance / Condition + (Relevance | Participant) + ((Relevance/Condition)|Item),
                         data=filter(df, ConditionBelief == "True"), 
@@
 
+*Note*. Model adding Relevance and Condition as random slopes for each stimuli converged
+
 ```{r}
 m_enticement <- glmmTMB::glmmTMB(Enticement ~ Sex / Relevance / Condition + 
-                                   (Relevance | Participant) + (1|Item),
+                                   (Relevance | Participant) + ((Relevance/Condition)|Item),
                       data=df, family=glmmTMB::ordbeta(),
@@
 
-```{r}
-m <- glmmTMB::glmmTMB(Enticement ~ Sample / Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
+*Note.* Model adding Relevance and Condition as random slopes for each stimuli converged.
+
+```{r}
+m <- glmmTMB::glmmTMB(Enticement ~ Sample / Sex / Relevance / Condition + (Relevance | Participant) + ((Relevance/Condition)|Item),
                       data=df, 
@@
 
-```{r}
-m <- glmmTMB::glmmTMB(Enticement ~ Mobile / Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
+*Note.* Model adding Relevance and Condition as random slopes for each stimuli converged.
+```{r}
+m <- glmmTMB::glmmTMB(Enticement ~ Mobile / Sex / Relevance / Condition + (Relevance | Participant) + ((Relevance/Condition)|Item),
                       data=df, 
@@
 ```{r}
-m <- glmmTMB::glmmTMB(Arousal ~ Sex / (Condition * SexualActivity_num) + (Condition | Participant) + (1|Item),
+m <- glmmTMB::glmmTMB(Arousal ~ Sex / (Condition * SexualActivity_num) + (Condition | Participant) + ((Relevance/Condition)|Item),
                       data=filter(df, ConditionBelief == "True"), 
@@
 <!-- Effect becomes larger, more significant and goes in both directions for both genders -->
-
-```{r}
-m <- glmmTMB::glmmTMB(Enticement ~ Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
+*Note.* Model adding Relevance and Condition as random slopes for each stimuli converged.
+```{r}
+m <- glmmTMB::glmmTMB(Enticement ~ Sex / Relevance / Condition + (Relevance | Participant) + ((Relevance/Condition)|Item),
                       data=filter(df, ConditionBelief == "True"), 
@@
 
+*Note.* Model adding Relevance and Condition as random slopes for each stimuli converged.
 ```{r}
 m_valence <- glmmTMB::glmmTMB(Valence ~ Sex / Relevance / Condition + 
-                                (Relevance | Participant) + (1|Item),
+                                (Relevance | Participant) + ((Relevance/Condition)|Item),
                       data=df, family=glmmTMB::ordbeta(),
@@
 
-```{r}
-m <- glmmTMB::glmmTMB(Valence ~ Sample / Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
+*Note.* Model adding Relevance and Condition as random slopes for each stimuli converged.
+```{r}
+m <- glmmTMB::glmmTMB(Valence ~ Sample / Sex / Relevance / Condition + (Relevance | Participant) + ((Relevance/Condition)|Item),
                       data=df, 
@@
 ```{r}
-m <- glmmTMB::glmmTMB(Valence ~ Mobile / Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
+m <- glmmTMB::glmmTMB(Valence ~ Mobile / Sex / Relevance / Condition + (Relevance | Participant) + ((Relevance/Condition)|Item),
                       data=df, 
@@
 ```{r}
-m <- glmmTMB::glmmTMB(Valence ~ Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
+m <- glmmTMB::glmmTMB(Valence ~ Sex / Relevance / Condition + (Relevance | Participant) + ((Relevance/Condition)|Item),
                       data=filter(df, ConditionBelief == "True"), 
@@
 ```{r}
-m <- glmmTMB::glmmTMB(Emotionality ~ Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
+m <- glmmTMB::glmmTMB(Emotionality ~ Sex / Relevance / Condition + (Relevance | Participant) + ((Relevance/Condition)|Item),
                       data=df, family=glmmTMB::ordbeta(),
@@
 ```{r}
-m <- glmmTMB::glmmTMB(Emotionality ~ Sample / Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
+m <- glmmTMB::glmmTMB(Emotionality ~ Sample / Sex / Relevance / Condition + (Relevance | Participant) + ((Relevance/Condition)|Item),
                       data=df, 
@@
 ```{r}
-m <- glmmTMB::glmmTMB(Emotionality ~ Mobile / Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
+m <- glmmTMB::glmmTMB(Emotionality ~ Mobile / Sex / Relevance / Condition + (Relevance | Participant) + ((Relevance/Condition)|Item),
                       data=df, 
@@
 ```{r}
-m <- glmmTMB::glmmTMB(Emotionality ~ Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
+m <- glmmTMB::glmmTMB(Emotionality ~ Sex / Relevance / Condition + (Relevance | Participant) + ((Relevance/Condition)|Item),
                       data=filter(df, ConditionBelief == "True"), 
@@
 
-pred1 <- rbind(
-  marginaleffects::predictions(m_arousal, by=c("Sex", "Relevance", "Condition"), newdata = "marginalmeans", re.form=NA) |>
+pred1 <- 
+  rbind(
+  modelbased::estimate_means(m_Arousal, by=c("Sex", "Relevance", "Condition")) |>
   as.data.frame() |> 
   mutate(Outcome="Arousal"),
-  marginaleffects::predictions(m_enticement, by=c("Sex", "Relevance", "Condition"), newdata = "marginalmeans", re.form=NA) |>
+  modelbased::estimate_means(m_enticement, by=c("Sex", "Relevance", "Condition") |>
   as.data.frame() |> 
   mutate(Outcome="Enticement"),
-  marginaleffects::predictions(m_valence, by=c("Sex", "Relevance", "Condition"), newdata = "marginalmeans", re.form=NA) |>
+  modelbased::estimate_means(m_valence, by=c("Sex", "Relevance", "Condition")) |>
   as.data.frame() |> 

### 2025-06-10 study1/analysis/0_preprocessing.py

@@ -40,12 +40,12 @@ for i, file in enumerate(files):
     # Browser info -------------------------------------------------------
     browser = data[data["screen"] == "browser_info"].iloc[0]
 
-    # skip participants without the language column 
+    # Skip participants with no language column 
     if "language" not in browser.index:
-        print(f"Skipping {filename}: no language information")
+        print(f"Skipping {filename}: no language column")
         skipped_files.append({"filename": filename, "date": browser["date"]})
         continue
-    
+
     # Experimenter
     experimenter = browser["researcher"]
     if experimenter in ["TEST", "jc"]:

### 2025-06-11 study1/analysis/2_emotions.qmd
minor

@@
 
-marginaleffects::avg_slopes(m, variables="Condition", by="Sex", re.form=NA) |> 
+marginaleffects::avg_slopes(m, variables="Condition", by="Sex", re.form=NA, backend ="emmeans") |> 
   results_table()
@@
   rbind(
-  modelbased::estimate_means(m_Arousal, by=c("Sex", "Relevance", "Condition")) |>
+  modelbased::estimate_means(m_arousal, by=c("Sex", "Relevance", "Condition")) |>
   as.data.frame() |> 
   mutate(Outcome="Arousal"),
-  modelbased::estimate_means(m_enticement, by=c("Sex", "Relevance", "Condition") |>
+  modelbased::estimate_means(m_enticement, by=c("Sex", "Relevance", "Condition")) |>
   as.data.frame() |> 
@@
         legend.text = element_text(size = 10),
-        legend.position = ) +
+        legend.position = "bottom") +
   labs(color="Images presented as:",

### 2025-06-11 study2/analysis/2_emotion.qmd
minor

@@
 editor_options: 
-  chunk_output_type: console
+  chunk_output_type: inline
 format:
@@
 ```{r Arousal1}
+#| fig-width: 12
 arousal <- df |> 
@@
 estimate_relation(m_a) |> 
-  ggplot(aes(x=SexualOrientation, y=Predicted)) +
+  ggplot(aes(x=Gender, y=Predicted)) +
   geom_pointrange(aes(ymin=CI_low, ymax=CI_high, color = Gender), position=position_dodge(width=0.5)) +
  scale_color_manual(values=c("Male"="#E91E63", "Female"="#FF9800"), guide="none") +  labs(y="Arousal") +
-  facet_wrap(~Gender) +
+  facet_wrap(~SexualOrientation) +
   theme_abyss()
@@
 ```{r Enticement1}
+#| fig-width: 12
 enticiment <- df |> 
@@
 ```{r Valence1}
+#| fig-width: 12
+
 valence <- df |> 
@@
 
-In contrast to [study1](https://realitybending.github.io/FictionEro/study1/analysis/2_emotions.html) arousal ratings for some images differ by whether the images were preceeded by 'photograph' or by 'AI-generated'.
-A possible explanation might be due to the lower number of participants compared to study1.
+Similar to [study1](https://realitybending.github.io/FictionEro/study1/analysis/2_emotions.html) arousal ratings for some "AI-generated" are lower then when they are presented as real photos.
 

### 2025-06-11 study2/analysis/3_realness.qmd
minor

@@
 
-p_a <- plot(cor_test(df, "Arousal", "Realness")) +
-  ggplot2::facet_wrap(~Gender) +
-  ggplot2::theme_bw()
+p_a <- ggplot(df, aes(x = Arousal, y = Realness, color = Condition, fill = Condition)) +
+  geom_smooth(method = "lm", se = TRUE) +
+  facet_wrap(~Gender) +
+  scale_color_manual(values = c("AI-Generated" = "#2196F3", "Photograph" = "#F44336")) +
+  scale_fill_manual(values = c("AI-Generated" = "#2196F3", "Photograph" = "#F44336")) +
+  smplot2::sm_statCorr() +
+  theme_minimal() +
+  theme(
+    axis.text.y = element_text(size = 8),
+    strip.placement = "outside",
+    strip.background.x = element_rect(fill = "lightgrey", color = NA),
+    strip.text.x = element_text(size = 10),
+    strip.text.y = element_text(size = 10),
+    axis.text.x = element_text(size = 9, color = "black"),
+    legend.text = element_text(size = 10)) +
+   labs(y="Realness\n", fill="Images presented as:", color="Images presented as:",
+       x = "Arousal")
 
-p_e <- plot(cor_test(df, "Enticing", "Realness")) +
-  ggplot2::facet_wrap(~Gender) +
-  ggplot2::theme_bw()
+p_e <- ggplot(df, aes(x = Enticing, y = Realness, color = Condition, fill = Condition)) +
+  geom_smooth(method = "lm", se = TRUE) +
+  facet_wrap(~Gender) +
+  scale_color_manual(values = c("AI-Generated" = "#2196F3", "Photograph" = "#F44336")) +
+  scale_fill_manual(values = c("AI-Generated" = "#2196F3", "Photograph" = "#F44336")) +
+  smplot2::sm_statCorr() +
+  theme_minimal() +
+  theme(
+    axis.text.y = element_text(size = 8),
+    strip.placement = "outside",
+    axis.title.y = element_blank(),
+    strip.background.x = element_rect(fill = "lightgrey", color = NA),
+    strip.text.x = element_text(size = 10),
+    axis.text.x = element_text(size = 9, color = "black"),
+    legend.text = element_text(size = 10)) +
+   labs(y="Realness\n", fill="Images presented as:", color="Images presented as:",
+       x = "Enticement")
 
-p_v <- plot(cor_test(df, "Valence", "Realness")) +
-  ggplot2::facet_wrap(~Gender) +
-  ggplot2::theme_bw()
+p_v <- ggplot(df, aes(x = Valence, y = Realness, color = Condition, fill = Condition)) +
+  geom_smooth(method = "lm", se = TRUE) +
+  facet_wrap(~Gender) +
+  scale_color_manual(values = c("AI-Generated" = "#2196F3", "Photograph" = "#F44336")) +
+  scale_fill_manual(values = c("AI-Generated" = "#2196F3", "Photograph" = "#F44336")) +
+  smplot2::sm_statCorr() +
+  theme_minimal() +
+  theme(
+    axis.text.y = element_text(size = 8),
+    strip.placement = "outside",
+    axis.title.y = element_blank(),
+    strip.background.x = element_rect(fill = "lightgrey", color = NA),
+    strip.text.x = element_text(size = 10),
+    axis.text.x = element_text(size = 9, color = "black"),
+    legend.text = element_text(size = 10)) +
+   labs(y="Realness\n", fill="Images presented as:", color="Images presented as:",
+       x = "Valence")
 
-p_sub <- p_a/ p_e/ p_v
+p_sub <- (p_a + theme(legend.position = "none"))| (p_e + theme(legend.position = "none"))| p_v + plot_layout(guides = "collect")
 

### 2025-06-17 study2/analysis/2_emotion.qmd
minor

@@
 editor_options: 
-  chunk_output_type: inline
+  chunk_output_type: console
 format:
@@
   mutate(across(starts_with("Feedback_"), as.factor)) |>
-  mutate(ConditionBelief = as.factor(ConditionBelief))
+  mutate(ConditionBelief = as.factor(ConditionBelief)) |>
+  mutate(StimuliType = case_when(
+    grepl("couple", Stimulus, ignore.case = TRUE) ~ "Couple",
+    TRUE ~ "Individual")) |>
+  mutate(StimuliType = fct_relevel(StimuliType, "Individual", "Couple"))
 
@@
 ```
-**Note**: [The calculations for the BAIt/GAAIS dimensions were based on the validation of the BAIT scale](https://realitybending.github.io/FictionEro/study1/analysis/1_cleaning.html)
-
-**BAIT_Videos** was calculated by averaging participants’ agreement with the statement that current AI algorithms can generate very realistic videos and the inverse of their agreement with the statement that videos generated by AI have obvious problems that make them easy to spot as fake.
-**Higher scores** reflect **stronger beliefs in the visual realism and technical reliability of AI-generated videos**.
-
-**BAIT_Visual** was computed as the average of four items: belief that AI algorithms can generate very realistic images, the inverse of belief that AI-generated images always contain errors and artifacts, agreement that CGI can perfectly imitate reality, and belief that technology allows the creation of environments that seem just as real as reality.
-**Higher scores capture stronger beliefs in the visual realism and immersive quality of AI-generated and computer-generated content**.
-
-**BAIT_Text** was calculated by averaging agreement with the belief that AI assistants can write texts indistinguishable from those written by humans and the inverse of the belief that AI-written documents usually read differently than human-written ones.
-**Higher scores indicate stronger beliefs in the linguistic realism of AI-generated text.**
-
-**BAIT_Negative** was computed by averaging levels of agreement with the statements “AI is dangerous” and “I am worried about future uses of AI”.**This composite reflects participants’ negative attitudes toward AI.**
-
-**BAIT_Positive** was calculated by averaging agreement with the statements “AI is exciting” and “Much of society will benefit from a future full of AI”.
-**This score represents positive attitudes towards AI.**
 
@@
 To summarise, **women** rate stimuli on average **significantly lower** in arousal, enticiment and valence than **men**.
+There was no difference between heterosexual, homosexual, and bisexual individuals within each gender on subjective ratings.
 
@@
 The analysis revealed that on average **women rate erotic stimuli significantly lower in arousal than men**.
-
 There was no difference between heterosexual, homosexual, and bisexual individuals within each gender on arousal ratings.
@@
 The analysis revealed that on average **women rate erotic stimuli significantly lower in enticiment than men**.
-
-There was no difference between heterosexual, homosexual, and bisexual individuals within each gender on arousal ratings.
+There was no difference between heterosexual, homosexual, and bisexual individuals within each gender on enticement ratings.
 
@@
 The analysis revealed that on average **women rate erotic stimuli significantly lower in valence than men**.
-
 There was no difference between heterosexual, homosexual, and bisexual individuals within each gender on arousal ratings.
@@
 
-This model examines the effect of **Gender Sexual Orientation and Condition on Arousal**, accounting for random variability due to participants and items (i.e., random intercepts).
-
-<!-- The intercept is Male and photograph.  -->
-Women rated 'photographs' significantly lower in arousal than men. Men rated 'photographs' significantly higher in arousal than 'AI-generated' images.
-
-The analysis also examined the average marginal effect of the variable "Condition" (comparing AI-Generated to Photograph) separately for males and females.
-For males, the arousal is on average significantly lower (althoug only slighly) for AI-Generated images compared to Photograph images.
-For females, the arousal is on average slightly lower for AI-Generated images compared to Photograph images; however, this effect is not significant.
-
-```{r Arousal Model}
-
-m_arousal <- glmmTMB::glmmTMB(Arousal ~ Gender/ Condition + 
-                                (1| Participant) + (1|Stimulus), family=glmmTMB::ordbeta(),
+This model examines the effect of **Gender Sexual Orientation, stimuli type, and Condition on Arousal**, accounting for random variability due to participants and items (i.e., random intercepts) and condition as random slope for participants.
+
+<!-- The intercept is Male, photograph, individuals  -->
+
+Women rate photograph of individuals lower than males.
+Men show less arousal toward couple images (vs individual ones), regardless of condition.
+Women show greater arousal toward couple images than individual ones.
+Men show less arousal for AI-generated individual images compared to photographic individual images.
+
+Looking at average slopes:
+1. Males rate AI-generated images ~0.014 lower in arousal (on average) than photos — significant.
+2. Females also rate AI images lower, but not significantly.
+3. Males rate couple images significantly lower in arousal than individual ones.
+4. Females rate couple images significantly higher in arousal than individual ones.
+
+```{r Arousal with Stimuli Type}
+
+m_arousal <- glmmTMB::glmmTMB(Arousal ~ Gender/ StimuliType/ Condition + 
+                                (Condition| Participant) + (1|Stimulus), family=glmmTMB::ordbeta(),
                               data=df, control = glmmTMB::glmmTMBControl(parallel = 8))
@@
 results_table(m_arousal)
-
-marginaleffects::avg_slopes(m_arousal, variables="Condition", by="Gender") 
-# > results_table()
+marginaleffects::avg_slopes(m_arousal, variables=c("Condition", "StimuliType"), by="Gender") |>
+  results_table()
 
@@
 ```{r Arousal Believed}
-m <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition + (1|Participant) + (1|Stimulus),
+m_a_b <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition + (Condition|Participant) + (Condition|Stimulus),
                         data=filter(df, ConditionBelief == "True"), 
@@
 
-results_table(m)
+results_table(m_a_b)
 ```
@@
 
-This model examines how **Gender and Condition influence enticement** ratings, treating participant and items as random intercepts.
+This model examines how **Gender, Stimuli Type and Condition influence enticement** ratings, treating participant and items as random intercepts.
 
@@
 
-Across both conditions, women rated the images as less enticing overall than men.
-There was a significant interaction between gender and image condition, whereby men were less enticed by AI-generated images, whereas women showed no significant difference in enticement based on image condition.
-
-We also analyzed the average marginal effect of the variable “Condition” (comparing AI-Generated to Photograph) separately for males and females.
-For males, enticement ratings are significantly lower on average for AI-Generated images compared to Photograph  images.
-For females, enticement ratings are slightly lower on average for AI-Generated images compared to Photograph images, although this difference is not statistically significant.
-
+Women rated images as less enticing than men overall.
+They rated couple images as more enticing than individual images.
+Men, on the other hand, rated couple images as less enticing.
+Men also rated AI-generated images as significantly less enticing than photographs, both for images of individual and couple stimuli.
+In contrast, women did not significantly differentiate between AI and photographic images in terms of enticement.
+
+Looking at the average slopes, both genders rate Ai-generated conditions lower in enticement, although this effect is only significant for men. 
 ```{r Enticement Model}
-m_enticement <- glmmTMB::glmmTMB(Enticing ~ Gender / Condition + 
-                                   (1 | Participant) + (1|Stimulus),
+m_enticement <- glmmTMB::glmmTMB(Enticing ~ Gender / StimuliType/ Condition + 
+                                   (Condition | Participant) + (1|Stimulus),
                       data=df, family=glmmTMB::ordbeta(),
@@
 
-marginaleffects::avg_slopes(m_enticement, variables="Condition", by="Gender", re.form=NA)
+marginaleffects::avg_slopes(m_enticement, variables="Condition", by="Gender") |>
+  results_table()
+
 ```
@@
 
+<!-- Note. Adding condition as random slope for participant did not converge -->
+
 ```{r Enticement Believed1}
-m <- glmmTMB::glmmTMB(Enticing ~ Gender / Condition + (1 | Participant) + (1|Stimulus),
+m_e_b <- glmmTMB::glmmTMB(Enticing ~ Gender / Condition + (Condition| Participant) + (1|Stimulus),
                       data=filter(df, ConditionBelief == "True"), 
@@
 
-This model examines the effect of **Gender and Condition on Valence** ratings, while accounting for random variability due to participants and items (i.e., random intercepts).
+This model examines the effect of **Gender, Stimuli Type and Condition on Valence** ratings, while accounting for random variability due to participants and items (i.e., random intercepts).
 
 <!-- The intercept is Male and photograph.  -->
-Male participants rated images labelled as AI-Generated significantly lower in valence than Real images. For females, there is no significant effect.
+Women rated images overall as lower in valence than men did.
+They rated couple images as higher in valence than individual ones.
+Additionally, women rated AI-generated couple images as significantly lower in valence than photographic couple images.
+Men rated images of couples lower in valence and AI-images of individuals lower in valence comapred to real photos of individuals.
+
+Looking at avergae slopes, both genders rate AI-generated images lower in valence, but this effect is only significant for males.
 
 ```{r Valence Model}
-m_valence <- glmmTMB::glmmTMB(Valence ~ Gender / Condition + 
-                                (1| Participant) + (1|Stimulus),
+m_valence <- glmmTMB::glmmTMB(Valence ~ Gender / StimuliType/ Condition + 
+                                (Condition| Participant) + (1|Stimulus),
                       data=df, family=glmmTMB::ordbeta(),
@@
 
-marginaleffects::avg_slopes(m_valence, variables="Condition", by="Gender", re.form=NA)
+marginaleffects::avg_slopes(m_valence, variables="Condition", by="Gender") |>
+  results_table()
+
 ```
@@
 ```{r Valence Believed1}
-m <- glmmTMB::glmmTMB(Valence ~ Gender /Condition + (1| Participant) + (1|Stimulus),
+m_v_b <- glmmTMB::glmmTMB(Valence ~ Gender /Condition + (Condition| Participant) + (1|Stimulus),
                       data=filter(df, ConditionBelief == "True"), 
@@
 
-results_table(m)
+results_table(m_v_b)
 
@@
 
-This model looks at the effect of **Gender and Condition on Emotionality**, accounting for random variability due to participants and items (i.e., random intercepts).
-
-The results show males rate AI-Generated images lower in emotionality compared to photographs.
+This model looks at the effect of **Gender, StimuliType and Condition on Emotionality**, accounting for random variability due to participants and items (i.e., random intercepts).
+
+Females, compared to males, report significantly lower emotionality ratings for fotographs.
+Among males, couple stimuli are rated lower than individual stimuli.Among females, couple stimuli are rated higher than individual stimuli.
+For males, AI-generated individual stimuli are rated lower than human-generated ones.
+Females have lower ratings for AI-generated couple stimuli compared to AI-generated stimuli of individuals.
 
 ```{r Emotionality Model}
-m <- glmmTMB::glmmTMB(Emotionality ~ Gender / Condition + (1| Participant) + (1|Stimulus),
+m_em <- glmmTMB::glmmTMB(Emotionality ~ Gender /StimuliType/ Condition + (Condition| Participant) + (1|Stimulus),
                       data=df, family=glmmTMB::ordbeta(),
@@
 
-results_table(m)
-
-marginaleffects::avg_slopes(m, variables="Condition", by="Gender", re.form=NA)
+results_table(m_em)
+
+marginaleffects::avg_slopes(m_em, variables="Condition", by="Gender", re.form=NA) |>
+  results_table()
 ```
@@
 ```{r EMotionality Believed1}
-m <- glmmTMB::glmmTMB(Emotionality ~ Gender / Condition + (1 | Participant) + (1|Stimulus),
+m <- glmmTMB::glmmTMB(Emotionality ~ Gender / Condition + (Condition| Participant) + (1|Stimulus),
                       data=filter(df, ConditionBelief == "True"), 
@@
 
-**Gender Differences**
-
-- Main manipulation worked for men only - i.e., reality manipulation on the nature of the stimuli on subjective ratings
-
-- Males rated AI-generated images significantly lower than photographs in arousal, valence, and enticement.
-Females showed no significant difference in ratings between AI-generated and photographic images across all outcomes.
-
-- Women rate stimuli on average lower in arousal, enticement and valence than men, however this difference was not significant.
+- Gender is a major predictor of arousal, enticement and valence, with females generally reporting lower ratings than males overall.
+- Women prefer couple images (i.e.,significantly higher arousal, enticement and valence ratings); men prefer individual images (i.e.,significantly lower arousal, enticement and valence ratings). 
+- AI-generation reduces arousal for men, especially for individual images. AI-generation has no significant effect on arousal for women, whether images are of individuals or couples.
 
@@
 
-- For women, **positive attitudes towards AI** moderated arousal and enticement, resulting in **more favorable evaluations of AI-generated images**.
+- For women, positive attitudes towards AI moderated arousal and enticement, resulting in more favorable evaluations of AI-generated images.
 Negative attitudes moderated valence ratings, leading to less favorable evaluations.
-
-- **negative attitudes towards AI** moderated valence ratings for both genders
-
-- Reporting having **higher knowledge about AI** moderated valence ratings for men
-
-- **Sexual activity** moderated enticement ratings for females. Specifically, females who reported having sexual activity within the 3 previous days tended to rate AI images higher in enticement.
-
-- Men’s **perceptions of the attractiveness of AI-generated images** moderated both arousal and valence ratings. More attractive AI images were rated as more arousing and valent.
-
-- Female's feedback that **no images were attractive** moderated arousal ratings.
+- Negative attitudes towards AI moderated valence ratings for both genders
+- Reporting having higher knowledge about AI moderated valence ratings for men
+- Sexual activity moderated enticement ratings for females. Specifically, females who reported having sexual activity within the 3 previous days tended to rate AI images higher in enticement.
+- Men’s perceptions of the attractiveness of AI-generated images moderated both arousal and valence ratings. More attractive AI images were rated as more arousing and valent. 
+- Female's feedback that no images were attractive moderated arousal ratings.
 
@@
 pred1 <- rbind(
-  marginaleffects::avg_predictions(m_arousal, by=c("Gender", "Condition"), newdata = "mean", re.form=NA) |>
+  marginaleffects::avg_predictions(m_arousal, by=c("Gender", "StimuliType", "Condition"), newdata = "mean", re.form=NA) |>
   as.data.frame() |> 
   mutate(Outcome="Arousal"),
-  marginaleffects::avg_predictions(m_enticement, by=c("Gender", "Condition"), newdata = "mean", re.form=NA) |>
+  marginaleffects::avg_predictions(m_enticement, by=c("Gender","StimuliType",  "Condition"), newdata = "mean", re.form=NA) |>
   as.data.frame() |> 
   mutate(Outcome="Enticement"),
-  marginaleffects::avg_predictions(m_valence, by=c("Gender", "Condition"), newdata = "mean", re.form=NA) |>
+  marginaleffects::avg_predictions(m_valence, by=c("Gender", "StimuliType", "Condition"), newdata = "mean", re.form=NA) |>
   as.data.frame() |> 
@@
 
-stars1 <- data.frame(label=c("**", "***", "**"),
-                    Gender=fct_relevel(c("Male", "Male", "Male"), "Male"),
-                    Outcome=c("Arousal", "Enticement", "Valence"),
-                    y=c(0.55, 0.58, 0.62))
+stars1a <- data.frame(label=c("**","***", "**", "***", "***"),
+                    Gender=fct_relevel(c("Male", "Female", "Male", "Female", "Female"), "Male"),
+                    Outcome=c("Arousal","Arousal", "Enticement", "Enticement", "Valence"),
+                    Condition=c("Photograph", "Photograph", "Photograph", "Photograph", "Photograph"), 
+                    x=c(1.5, 1.5, 1.5, 1.5, 1.5), 
+                    y = c(0.52, 0.40, 0.57, 0.51, 0.6))
+
+stars1b <- data.frame(label=c("*","**", "*","*"),
+                    Gender=fct_relevel(c("Male", "Male", "Male","Female"), "Male"),
+                    Outcome=c("Arousal", "Enticement", "Enticement","Valence"),
+                    x=c(1, 1, 2, 2),
+                    y=c(0.58, 0.63, 0.54, 0.6))
 
@@
   mutate(Gender = fct_relevel(Gender, "Male", "Female")) |> 
-  ggplot(aes(x=Outcome, y=estimate)) +
+  ggplot(aes(x=StimuliType, y=estimate)) +
   geom_hline(yintercept=0, color="darkgrey") +
-  geom_line(aes(group=Condition, color=Condition), position = position_dodge(width=0.2), alpha=0.8, linewidth=0.2) +
-  geom_pointrange(aes(ymin = conf.low, ymax=conf.high, color=Condition), position = position_dodge(width=0.2), size=0.2) +
-  geom_text(data=stars1, aes(y=y, label=label), hjust=0.5, size=3) +
-  geom_rect(data=data.frame(Type="All trials", estimate=0.1, Gender=as.factor("Male"), Outcome="Arousal"),
-            aes(xmin=0.8, xmax=1.2, ymin=0.35, ymax=0.6), color="#8BC34A", alpha=0) +
-  geom_rect(data=data.frame(Type="All trials", estimate=0.1, Gender=as.factor("Female"), Outcome="Arousal"),
-            aes(xmin=0.8, xmax=1.2, ymin=0.3, ymax=0.5), color="#8BC34A", alpha=0) +
-  facet_grid(~Gender, switch="y") +
+  geom_line(aes(group=Condition, color=Condition), position = position_dodge(width=0.2), alpha=0.8, linewidth=0.2, key_glyph = "path") +
+  geom_pointrange(aes(ymin = conf.low, ymax=conf.high, color=Condition), position = position_dodge(width=0.2), size=0.3) +
+  geom_text(data=stars1a, aes(x=x, y=y, label=label, color=Condition), hjust=0.5, key_glyph = "blank", size=3) +
+  geom_text(data=stars1b, aes(x=x, y=y, label=label), hjust=0.5, color="#424242", size=3) +
+  # geom_rect(data=data.frame(Type="All trials", estimate=0.1, Gender=as.factor("Male"), Outcome="Arousal"),
+  #           aes(xmin=0.8, xmax=1.2, ymin=0.35, ymax=0.6), color="#8BC34A", alpha=0) +
+  # geom_rect(data=data.frame(Type="All trials", estimate=0.1, Gender=as.factor("Female"), Outcome="Arousal"),
+  #           aes(xmin=0.8, xmax=1.2, ymin=0.3, ymax=0.5), color="#8BC34A", alpha=0) +
+  facet_grid(Outcome~Gender, switch="y", scales ="free") +
   scale_y_continuous(limits=c(0, 1), labels=scales::percent) +
@@
         legend.position = ) +
-  labs(color="Images presented as:",
-       tag = "A")
+  labs(color="Images presented as:")
 
@@
 
-1. 'Other' was removed due to the very small percentage of individuals identifying as such.
-2. 'Porn' factor was not computed, instead sexual activity and frequency of watching porn were treated seperate. 
-3. Missing final figures and interpretation of belief as influencing emotional ratings of images
+1. Models for arousal, enticement, and valence had singularity issues when also adding condition as random slope for stimuli
+2. 'Other' was removed due to the very small percentage of individuals identifying as such.
+3. 'Porn' factor was not computed, instead sexual activity and frequency of watching porn were treated seperate. 
+4. Missing final figures and interpretation of belief as influencing emotional ratings of images
+5.[The calculations for the BAIt/GAAIS dimensions were based on the validation of the BAIT scale](https://realitybending.github.io/FictionEro/study1/analysis/1_cleaning.html)
+
+**BAIT_Videos** was calculated by averaging participants’ agreement with the statement that current AI algorithms can generate very realistic videos and the inverse of their agreement with the statement that videos generated by AI have obvious problems that make them easy to spot as fake.
+**Higher scores** reflect **stronger beliefs in the visual realism and technical reliability of AI-generated videos**.
+
+**BAIT_Visual** was computed as the average of four items: belief that AI algorithms can generate very realistic images, the inverse of belief that AI-generated images always contain errors and artifacts, agreement that CGI can perfectly imitate reality, and belief that technology allows the creation of environments that seem just as real as reality.
+**Higher scores capture stronger beliefs in the visual realism and immersive quality of AI-generated and computer-generated content**.
+
+**BAIT_Text** was calculated by averaging agreement with the belief that AI assistants can write texts indistinguishable from those written by humans and the inverse of the belief that AI-written documents usually read differently than human-written ones.
+**Higher scores indicate stronger beliefs in the linguistic realism of AI-generated text.**
+
+**BAIT_Negative** was computed by averaging levels of agreement with the statements “AI is dangerous” and “I am worried about future uses of AI”.**This composite reflects participants’ negative attitudes toward AI.**
+
+**BAIT_Positive** was calculated by averaging agreement with the statements “AI is exciting” and “Much of society will benefit from a future full of AI”.
+**This score represents positive attitudes towards AI.**

### 2025-06-17 study2/analysis/3_realness.qmd
minor

@@
          )|>
-  mutate(across(starts_with("Feedback_"), as.factor))
+  mutate(across(starts_with("Feedback_"), as.factor)) |>
+  mutate(StimuliType = case_when(
+    grepl("couple", Stimulus, ignore.case = TRUE) ~ "Couple",
+    TRUE ~ "Individual")) |>
+  mutate(StimuliType = fct_relevel(StimuliType, "Individual", "Couple"))
 
@@
 
+**Note**. Adding StimuliType as a predictor did not change the pattern - Condition was still only a significant predictor for men.
+
 ```{r}
@@
 
-m <- make_model("Realness ~ Gender / Condition + 
+m <- make_model("Realness ~ Gender /Condition + 
                 (1|Participant) + (1|Stimulus)",
@@
 
-m <- make_model("RealnessBelief ~ Gender / Condition + 
+m <- make_model("RealnessBelief ~ Gender /Condition + 
                 (1|Participant) + (1|Stimulus)",
@@
   scale_color_manual(values=c("red", "blue"), guide="none") +
-  facet_grid(~Gender)
+  facet_grid(StimuliType~Gender)
 ```

### 2025-06-17 study2/analysis/2_emotion.qmd
updated analysis

@@
 Looking at average slopes:
+
 1. Males rate AI-generated images ~0.014 lower in arousal (on average) than photos — significant.
@@
 results_table(m_arousal)
+
 marginaleffects::avg_slopes(m_arousal, variables=c("Condition", "StimuliType"), by="Gender") |>
   results_table()
-
 ```
@@
 Looking at the average slopes, both genders rate Ai-generated conditions lower in enticement, although this effect is only significant for men.
+
 ```{r Enticement Model}
@@
 
-Looking at avergae slopes, both genders rate AI-generated images lower in valence, but this effect is only significant for males.
+Looking at avergae slopes, both genders rate AI-generated images lower in valence, but this effect is only significant for males as well.
 
@@
 ```{r Emotionality Desc}
+#| fig-height: 12
+#| fig-width: 7
+
 emotionality_desc <- plot_descriptive(df, "Emotionality")
@@
 ```{r}
+#| fig-height: 12
+#| fig-width: 7
 
@@
                     x=c(1.5, 1.5, 1.5, 1.5, 1.5), 
-                    y = c(0.52, 0.40, 0.57, 0.51, 0.6))
+                    y = c(0.53, 0.40, 0.6, 0.51, 0.6))
 
@@
                     x=c(1, 1, 2, 2),
-                    y=c(0.58, 0.63, 0.54, 0.6))
+                    y=c(0.60, 0.65, 0.56, 0.6))
 

### 2025-06-17 study2/analysis/3_realness.qmd
updated analysis

@@
 
+## Probability of Beliefs
+
+This logistic regression model predicts the probability that a participant believed the condition (i.e., ratings on the nature of the stimuli matched that of the riginal labels), based on their gender, the condition they were shown (AI-generated vs.
+Photo), and their interaction.
+
+- Female participants have 18% lower odds of believing the condition is real compared to males, when presented with an image labelled as photo.
+- Male participants had 60% lower odds of believing the label was accurate when the image was labeled as AI-generated compared to when it was labeled as a photo.
+- The interaction between gender and condition suggests that the effect of the AI-generated label was slightly attenuated in females compared to males, although this did not reach statistical significance.
+
+```{r}
+
+df <- df |> 
+  mutate(ConditionBelieved = case_when(
+    ConditionBelief == "True" ~ 1, 
+    ConditionBelief == "False" ~ 0 
+  ))
+
+m <- glm(ConditionBelieved ~ Gender*Condition, data = df, family = binomial())
+model_parameters(m, exponentiate = TRUE)
+predictions <- modelbased::estimate_means(m, c("Gender", "Condition"))
+contrasts <- modelbased::estimate_contrasts(m, "Gender", by = "Condition")
+
+plot(predictions) +
+  theme_minimal() +
+  labs(y= "Probability of Believing in the Original Labels") +
+  theme(
+        axis.title.x = element_blank(),
+        axis.text.y = element_text(size = 8),
+        strip.placement = "outside",
+        strip.background.x = element_rect(fill=c("lightgrey", "blue"), color=NA),
+        strip.text.x = element_text(size = 10),
+        strip.text.y = element_text(size = 10),
+        axis.text.x = element_text(size=9, color="black"),
+        legend.text = element_text(size = 10),
+        legend.position = ) +
+  labs(color="Images presented as:")
+
+```
+
 ## Physical Characteristics
@@
   scale_color_manual(values=c("red", "blue"), guide="none") +
-  facet_grid(StimuliType~Gender)
+  facet_grid(~Gender)
 ```
@@
 
-To examine the unique role of **Arousal** in predicting **perceived realness**, a model was tested including both linear and quadratic effects of Arousal, along with its interactions with Gender and Condition (AI-generated vs.
+To examine the role of **Arousal** in predicting **perceived realness**, a model was tested including both linear and quadratic effects of Arousal, along with its interactions with Gender and Condition (AI-generated vs.
 real images), modeling participants and images as random intercepts.
+
 To assess whether a non-linear (quadratic) component improved the model, a comparison was conducted between a model including a quadratic term for Arousal and one without.

### 2025-06-20 study2/analysis/2_emotion.qmd
push

@@
 #| warning: false
-#| 
+
 dfsub <- read.csv("../data/data_participants.csv")
@@
 
-stars1a <- data.frame(label=c("**","***", "**", "***", "***"),
-                    Gender=fct_relevel(c("Male", "Female", "Male", "Female", "Female"), "Male"),
-                    Outcome=c("Arousal","Arousal", "Enticement", "Enticement", "Valence"),
-                    Condition=c("Photograph", "Photograph", "Photograph", "Photograph", "Photograph"), 
-                    x=c(1.5, 1.5, 1.5, 1.5, 1.5), 
-                    y = c(0.53, 0.40, 0.6, 0.51, 0.6))
+stars1a <- data.frame(label=c("**","***", "**", "***", "***", "***"),
+                    Gender=fct_relevel(c("Male", "Female", "Male", "Female", "Male", "Female"), "Male"),
+                    Outcome=c("Arousal","Arousal", "Enticement", "Enticement", "Valence", "Valence"),
+                    Condition=c("Photograph", "Photograph", "Photograph", "Photograph", "Photograph", "Photograph"), 
+                    x=c(1.5, 1.5, 1.5, 1.5, 1.5, 1.5), 
+                    y = c(0.53, 0.40, 0.6, 0.51, 0.62, 0.58))
 
@@
   geom_hline(yintercept=0, color="darkgrey") +
-  geom_line(aes(group=Condition, color=Condition), position = position_dodge(width=0.2), alpha=0.8, linewidth=0.2, key_glyph = "path") +
+  geom_line(aes(group=Condition, color=Condition), position = position_dodge(width=0.2), alpha=0.8, linewidth=0.4, key_glyph = "path") +
   geom_pointrange(aes(ymin = conf.low, ymax=conf.high, color=Condition), position = position_dodge(width=0.2), size=0.3) +
@@
   facet_grid(Outcome~Gender, switch="y", scales ="free") +
-  scale_y_continuous(limits=c(0, 1), labels=scales::percent) +
+  scale_y_continuous(limits=c(0.20, 0.8), labels=scales::percent) +
   scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
-  theme_minimal() +
+  theme_bw() +
   theme(axis.title.y = element_blank(),

### 2025-06-23 study1/analysis/1_cleaning.qmd
html cleaning updatee

@@
                                  at=c("Relevance", "Category", "Sex", "SexualOrientation"), 
+                                       by = c("Relevance", "Category", "Sex", "SexualOrientation"),
+
                                  method="KernSmooth") |>

### 2025-06-24 study1/analysis/1_cleaning.qmd
updated cleaning script study1

@@
 ```{r}
+
 # df <- filter(df, Mobile == "False")
@@
 
+`r length(outliers$expe_duration)` participants completed the experiment in less than 15 minutes.
+
 ### Task Duration
@@
 
-We excluded the BAIT data of `r length(outliers$bait_duration)` participants who completed the questionnaire in less than 30 seconds.
+`r length(outliers$bait_duration)` participants completed the BAIT questionnaire in less than 30 seconds.
 

### 2025-06-24 study1/analysis/2_emotions.qmd
updated cleaning script study1

@@
   scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
-  theme_minimal() +
+  theme_bw() +
   theme(axis.title.y = element_blank(),

### 2025-06-24 study1/analysis/2_emotions.qmd
Update 2_emotions.qmd

@@
 m_enticement <- glmmTMB::glmmTMB(Enticement ~ Sex / Relevance / Condition + 
-                                   (Relevance | Participant) + ((Relevance/Condition)|Item),
+                                   (Relevance | Participant) + (1|Item),
                       data=df, family=glmmTMB::ordbeta(),
@@
 m_valence <- glmmTMB::glmmTMB(Valence ~ Sex / Relevance / Condition + 
-                                (Relevance | Participant) + ((Relevance/Condition)|Item),
+                                (Relevance | Participant) + (1|Item),
                       data=df, family=glmmTMB::ordbeta(),
@@
 ```{r}
-m <- glmmTMB::glmmTMB(Emotionality ~ Sex / Relevance / Condition + (Relevance | Participant) + ((Relevance/Condition)|Item),
+m <- glmmTMB::glmmTMB(Emotionality ~ Sex / Relevance / Condition + (Relevance | Participant) + (1|Item),
                       data=df, family=glmmTMB::ordbeta(),
@@
   rbind(
-  modelbased::estimate_means(m_arousal, by=c("Sex", "Relevance", "Condition")) |>
+  modelbased::estimate_means(m_arousal, by=c("Sex", "Relevance", "Condition"), backend = "emmeans") |>
   as.data.frame() |> 
   mutate(Outcome="Arousal"),
-  modelbased::estimate_means(m_enticement, by=c("Sex", "Relevance", "Condition")) |>
+  modelbased::estimate_means(m_enticement, by=c("Sex", "Relevance", "Condition"),backend = "emmeans") |>
   as.data.frame() |> 
   mutate(Outcome="Enticement"),
-  modelbased::estimate_means(m_valence, by=c("Sex", "Relevance", "Condition")) |>
+  modelbased::estimate_means(m_valence, by=c("Sex", "Relevance", "Condition"),backend = "emmeans") |>
   as.data.frame() |> 
-  mutate(Outcome="Valence")
-)
+  mutate(Outcome="Valence"))
 
@@
   mutate(Sex = fct_relevel(Sex, "Male", "Female")) |> 
-  ggplot(aes(x=Relevance, y=estimate)) +
+  ggplot(aes(x=Relevance, y=Proportion)) +
   geom_hline(yintercept=0, color="darkgrey") +
   geom_line(aes(group=Condition, color=Condition), position = position_dodge(width=0.2), alpha=0.8, linewidth=0.2) +
-  geom_pointrange(aes(ymin = conf.low, ymax=conf.high, color=Condition), position = position_dodge(width=0.2), size=0.2) +
+  geom_pointrange(aes(ymin = CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.2), size=0.2) +
   geom_text(data=stars1, aes(y=y, label=label), hjust=0.5, size=3) +
-  geom_rect(data=data.frame(Type="All trials", estimate=0.1, Sex=as.factor("Male"), Outcome="Arousal", Relevance="Relevant"), 
+  geom_rect(data=data.frame(Type="All trials", Proportion=0.1, Sex=as.factor("Male"), Outcome="Arousal", Relevance="Relevant"), 
             aes(xmin=0.8, xmax=1.2, ymin=0.5, ymax=0.80), color="#8BC34A", alpha=0) +
-  geom_rect(data=data.frame(Type="All trials", estimate=0.1, Sex=as.factor("Female"), Outcome="Arousal", Relevance="Relevant"), 
+  geom_rect(data=data.frame(Type="All trials", Proportion=0.1, Sex=as.factor("Female"), Outcome="Arousal", Relevance="Relevant"), 
             aes(xmin=0.8, xmax=1.2, ymin=0.2, ymax=0.5), color="#8BC34A", alpha=0) +
@@
 ```
-
-<!-- ## Realness -->
-
-<!-- ### Physical Characteristics -->
-
-<!-- ```{r} -->
-
-<!-- m <- glmmTMB::glmmTMB(Realness ~ Entropy + Complexity + Contrast + Luminance + (1|Participant) + (1|Item), data=df) -->
-
-<!-- results_table(m) -->
-
-<!-- ``` -->
-
-<!-- ```{r} -->
-
-<!-- m <- glmmTMB::glmmTMB(Realness ~ Sex / (Relevance / Condition) + (1|Participant) + (1|Item), data=df, family=beta_family(link = "logit")) -->
-
-<!-- results_table(m) -->
-
-<!-- ``` -->

### 2025-06-25 study1/analysis/2_emotions.qmd
minor

@@
   scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
-  theme_bw() +
+  theme_minimal() +
   theme(axis.title.y = element_blank(),

### 2025-06-25 study2/analysis/2_emotion.qmd
minor

@@
 ```{r Arousal Believed}
-m_a_b <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition + (Condition|Participant) + (Condition|Stimulus),
+m <- glmmTMB::glmmTMB(Arousal ~ Gender / StimuliType/Condition + (Condition|Participant) + (Condition|Stimulus),
                         data=filter(df, ConditionBelief == "True"), 
@@
 
-results_table(m_a_b)
+results_table(m)
 ```
@@
 ```{r Enticement Believed1}
-m_e_b <- glmmTMB::glmmTMB(Enticing ~ Gender / Condition + (Condition| Participant) + (1|Stimulus),
+m <- glmmTMB::glmmTMB(Enticing ~ Gender / Condition + (Condition| Participant) + (1|Stimulus),
                       data=filter(df, ConditionBelief == "True"), 
@@
 ```{r Valence Believed1}
-m_v_b <- glmmTMB::glmmTMB(Valence ~ Gender /Condition + (Condition| Participant) + (1|Stimulus),
+m <- glmmTMB::glmmTMB(Valence ~ Gender /Condition + (Condition| Participant) + (1|Stimulus),
                       data=filter(df, ConditionBelief == "True"), 
@@
 
-results_table(m_v_b)
+results_table(m)
 
@@
 ```{r Emotionality Model}
-m_em <- glmmTMB::glmmTMB(Emotionality ~ Gender /StimuliType/ Condition + (Condition| Participant) + (1|Stimulus),
+m_emotionality <- glmmTMB::glmmTMB(Emotionality ~ Gender /StimuliType/ Condition + (Condition| Participant) + (1|Stimulus),
                       data=df, family=glmmTMB::ordbeta(),
@@
 
-results_table(m_em)
-
-marginaleffects::avg_slopes(m_em, variables="Condition", by="Gender", re.form=NA) |>
+results_table(m_emotionality)
+
+marginaleffects::avg_slopes(m_emotionality, variables="Condition", by="Gender", re.form=NA) |>
   results_table()
@@
 ```{r}
-#| fig-height: 12
+#| fig-height: 7
 #| fig-width: 7
@@
 pred1 <- rbind(
-  marginaleffects::avg_predictions(m_arousal, by=c("Gender", "StimuliType", "Condition"), newdata = "mean", re.form=NA) |>
+  modelbased::estimate_means(m_arousal, by=c("Gender", "StimuliType", "Condition"), backend = "emmeans") |>
   as.data.frame() |> 
   mutate(Outcome="Arousal"),
-  marginaleffects::avg_predictions(m_enticement, by=c("Gender","StimuliType",  "Condition"), newdata = "mean", re.form=NA) |>
+  modelbased::estimate_means(m_enticement, by=c("Gender","StimuliType",  "Condition"), backend = "emmeans") |>
   as.data.frame() |> 
   mutate(Outcome="Enticement"),
-  marginaleffects::avg_predictions(m_valence, by=c("Gender", "StimuliType", "Condition"), newdata = "mean", re.form=NA) |>
+  modelbased::estimate_means(m_valence, by=c("Gender", "StimuliType", "Condition"), backend = "emmeans") |>
   as.data.frame() |> 
@@
 
-stars1a <- data.frame(label=c("**","***", "**", "***", "***", "***"),
-                    Gender=fct_relevel(c("Male", "Female", "Male", "Female", "Male", "Female"), "Male"),
-                    Outcome=c("Arousal","Arousal", "Enticement", "Enticement", "Valence", "Valence"),
-                    Condition=c("Photograph", "Photograph", "Photograph", "Photograph", "Photograph", "Photograph"), 
-                    x=c(1.5, 1.5, 1.5, 1.5, 1.5, 1.5), 
-                    y = c(0.53, 0.40, 0.6, 0.51, 0.62, 0.58))
+# stars1a <- data.frame(label=c("**","***", "**", "***", "***", "***"),
+#                     Gender=fct_relevel(c("Male", "Female", "Male", "Female", "Male", "Female"), "Male"),
+#                     Outcome=c("Arousal","Arousal", "Enticement", "Enticement", "Valence", "Valence"),
+#                     Condition=c("Photograph", "Photograph", "Photograph", "Photograph", "Photograph", "Photograph"), 
+#                     x=c(1.5, 1.5, 1.5, 1.5, 1.5, 1.5), 
+#                     y = c(0.53, 0.40, 0.6, 0.51, 0.62, 0.58))
+
+stars1b <- data.frame(label=c("*"),
+                    Gender=fct_relevel(c("Male"), "Male"),
+                    Outcome=c("Arousal"),
+                    x=1,
+                    y=0.60)
 
 stars1b <- data.frame(label=c("*","**", "*","*"),
-                    Gender=fct_relevel(c("Male", "Male", "Male","Female"), "Male"),
+                    Gender=fct_relevel(c("Male", "Male", "Male","Male"), "Male"),
                     Outcome=c("Arousal", "Enticement", "Enticement","Valence"),
-                    x=c(1, 1, 2, 2),
-                    y=c(0.60, 0.65, 0.56, 0.6))
+                    x=c(1, 1, 2, 1),
+                    y=c(0.60, 0.65, 0.56, 0.68))
 
@@
   mutate(Gender = fct_relevel(Gender, "Male", "Female")) |> 
-  ggplot(aes(x=StimuliType, y=estimate)) +
+  ggplot(aes(x=StimuliType, y=Proportion)) +
   geom_hline(yintercept=0, color="darkgrey") +
   geom_line(aes(group=Condition, color=Condition), position = position_dodge(width=0.2), alpha=0.8, linewidth=0.4, key_glyph = "path") +
-  geom_pointrange(aes(ymin = conf.low, ymax=conf.high, color=Condition), position = position_dodge(width=0.2), size=0.3) +
-  geom_text(data=stars1a, aes(x=x, y=y, label=label, color=Condition), hjust=0.5, key_glyph = "blank", size=3) +
-  geom_text(data=stars1b, aes(x=x, y=y, label=label), hjust=0.5, color="#424242", size=3) +
-  # geom_rect(data=data.frame(Type="All trials", estimate=0.1, Gender=as.factor("Male"), Outcome="Arousal"),
-  #           aes(xmin=0.8, xmax=1.2, ymin=0.35, ymax=0.6), color="#8BC34A", alpha=0) +
-  # geom_rect(data=data.frame(Type="All trials", estimate=0.1, Gender=as.factor("Female"), Outcome="Arousal"),
-  #           aes(xmin=0.8, xmax=1.2, ymin=0.3, ymax=0.5), color="#8BC34A", alpha=0) +
+  geom_pointrange(aes(ymin = CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.2), size=0.3) +
+  geom_text(data=stars1b, aes(x=x, y=y, label=label), hjust=0.5, color="#424242", size=6) +
+  geom_rect(data=data.frame(StimuliType = "Individual", Proportion=0.1, Gender=as.factor("Male"), Outcome="Arousal"),
+            aes(xmin=0.8, xmax=1.2, ymin=0.35, ymax=0.7), color="#8BC34A", alpha=0, ) +
+  geom_rect(data=data.frame(StimuliType = "Individual",Proportion=0.1, Gender=as.factor("Female"), Outcome="Arousal"),
+            aes(xmin=0.8, xmax=1.2, ymin=0.2, ymax=0.5), color="#8BC34A", alpha=0) +
   facet_grid(Outcome~Gender, switch="y", scales ="free") +
-  scale_y_continuous(limits=c(0.20, 0.8), labels=scales::percent) +
+  scale_y_continuous(limits=c(0, 1), labels=scales::percent) +
   scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
-  theme_bw() +
+  theme_minimal() +
   theme(axis.title.y = element_blank(),
@@
 m3 <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition  + (Condition | Participant) + (1|Stimulus),
-                      data=filter(df, ConditionBelief == "True", Feedback_AILessAttractive=="True"), 
+                      data=filter(df, ConditionBelief == "True", Feedback_NoFacesAttractive=="True"), 
                       family=glmmTMB::ordbeta(),
@@
 
-stars2 <- data.frame(label=c("**", "***", "*"),
-                    Gender=fct_relevel(c("Male", "Male", "Male")),
-                    Type=c("All trials", "Believed trials" ,"'AI was more attractive'"),
-                    y=c(0.52, 0.56, 0.66))
+stars2 <- data.frame(label=c("**", "***", "*", "*", "*"),
+                    Gender=fct_relevel(c("Male", "Male", "Male", "Female", "Female")),
+                    Type=c("All trials", "Believed trials" ,"'AI was more attractive'", "Believed trials", "'No faces were attractive'"),
+                    y=c(0.52, 0.56, 0.66, 0.47, 0.39))
 
@@
   estimate_relation(m3) |> 
-    mutate(Type = "'AI was less attractive'"),
+    mutate(Type = "'No faces were attractive'"),
   estimate_relation(m4) |> 
@@
 p2 <- pred2 |> 
-  mutate(Type = fct_relevel(Type, "All trials", "Believed trials", "'AI was less attractive'", "'AI was more attractive'")) |> 
+  mutate(Type = fct_relevel(Type, "All trials", "Believed trials", "'No faces were attractive'", "'AI was more attractive'")) |> 
   ggplot(aes(x=Type, y=Predicted)) +
@@
 4. Missing final figures and interpretation of belief as influencing emotional ratings of images
-5.[The calculations for the BAIt/GAAIS dimensions were based on the validation of the BAIT scale](https://realitybending.github.io/FictionEro/study1/analysis/1_cleaning.html)
+5. [The calculations for the BAIt/GAAIS dimensions were based on the validation of the BAIT scale](https://realitybending.github.io/FictionEro/study1/analysis/1_cleaning.html)
 

### 2025-06-30 study2/analysis/2_emotion.qmd
minor

@@
 
-stars1b <- data.frame(label=c("*"),
-                    Gender=fct_relevel(c("Male"), "Male"),
-                    Outcome=c("Arousal"),
-                    x=1,
-                    y=0.60)
-
 stars1b <- data.frame(label=c("*","**", "*","*"),
@@
 p1
+
+```
+
+```{r}
+#| fig-height: 7
+#| fig-width: 7
+
+pred1 <- modelbased::estimate_means(m_arousal, by=c("Gender", "StimuliType", "Condition"), backend = "emmeans") |>
+  as.data.frame() |> 
+  mutate(Outcome="Arousal")
+
+# stars1a <- data.frame(label=c("**","***", "**", "***", "***", "***"),
+#                     Gender=fct_relevel(c("Male", "Female", "Male", "Female", "Male", "Female"), "Male"),
+#                     Outcome=c("Arousal","Arousal", "Enticement", "Enticement", "Valence", "Valence"),
+#                     Condition=c("Photograph", "Photograph", "Photograph", "Photograph", "Photograph", "Photograph"), 
+#                     x=c(1.5, 1.5, 1.5, 1.5, 1.5, 1.5), 
+#                     y = c(0.53, 0.40, 0.6, 0.51, 0.62, 0.58))
+
+stars1b <- data.frame(label=c("*"),
+                    Gender=fct_relevel(c("Male")),
+                    Outcome=c("Arousal"),
+                    x=1,
+                    y=0.60)
+
+pred1 |>
+  mutate(Gender = fct_relevel(Gender, "Male", "Female")) |> 
+  ggplot(aes(x=StimuliType, y=Proportion)) +
+  geom_hline(yintercept=0, color="darkgrey") +
+  geom_line(aes(group=Condition, color=Condition), position = position_dodge(width=0.3), alpha=0.8, linewidth=1, key_glyph = "path") +
+  geom_pointrange(aes(ymin = CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.3), size=0.6) +
+  geom_text(data=stars1b, aes(x=x, y=y, label=label), hjust=0.5, color="#424242", size=6) +
+  # geom_rect(data=data.frame(StimuliType = "Individual", Proportion=0.1, Gender=as.factor("Male"), Outcome="Arousal"),
+  #           aes(xmin=0.8, xmax=1.2, ymin=0.35, ymax=0.7), color="#8BC34A", alpha=0, linewidth = 1) +
+  # geom_rect(data=data.frame(StimuliType = "Individual",Proportion=0.1, Gender=as.factor("Female"), Outcome="Arousal"),
+  #           aes(xmin=0.8, xmax=1.2, ymin=0.2, ymax=0.5), color="#8BC34A", alpha=0, linewidth = 1) +
+  facet_grid(Outcome~Gender, switch="y", scales ="free") +
+  scale_y_continuous(limits=c(0, 1), labels=scales::percent, expand = c(0,0)) +
+  scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
+  theme_bw() +
+  theme(axis.title.y = element_blank(),
+        axis.title.x = element_blank(),
+        axis.text.y = element_text(size = 8),
+        strip.placement = "outside",
+        strip.background.x = element_rect(fill=c("#1C2133"), color=NA),
+        strip.text.x = element_text(size = 12, color = "White", face = "bold"),
+        strip.text.y = element_blank(),
+        axis.text.x = element_text(size=12, color="black", face = "bold"),
+        legend.text = element_text(size = 12),
+        legend.position = "bottom") +
+  labs(color="Images presented as:")
 

### 2025-07-17 study1/analysis/2_emotions.qmd
updated script

@@
 m_arousal <- glmmTMB::glmmTMB(Arousal ~ Sex / Relevance / Condition + 
-                                (Relevance | Participant) + (1|Item),
+                                (Relevance | Participant) + ((Relevance / Condition)|Item),
                       data=df, family=glmmTMB::ordbeta(),

### 2025-08-01 study2/analysis/2_emotion.qmd
Update 2_emotion.qmd
cleaning script data updated

--- 2025-06-25 study2/analysis/2_emotion.qmd
@@
 
-This section is about selecting the best model. Notably, **all the stimuli presented are of an erotic nature**.
-Note that variables were rescaled to [0,1] when fitting the models and that the stimuli presented to participants was assigned according to their self-rated sexuality, making **all stimuli relevant** to participants.
+This section is about selecting the best model.
+Notably, **all the stimuli presented are of an erotic nature**.
+Note that variables were rescaled to \[0,1\] when fitting the models and that the stimuli presented to participants was assigned according to their self-rated sexuality, making **all stimuli relevant** to participants.
 
@@
 ::: panel-tabset
-
 ### Arousal
@@
 
-1. Males rate AI-generated images ~0.014 lower in arousal (on average) than photos — significant.
+1.  Males rate AI-generated images \~0.014 lower in arousal (on average) than photos — significant.
 2.  Females also rate AI images lower, but not significantly.
@@
 
-```{r Arousal with Stimuli Type}
-
-m_arousal <- glmmTMB::glmmTMB(Arousal ~ Gender/ StimuliType/ Condition + 
+```{r Arousal}
+
+m_arousal <- glmmTMB::glmmTMB(Arousal ~ Gender/ Condition + 
                                 (Condition| Participant) + (1|Stimulus), family=glmmTMB::ordbeta(),
@@
 marginaleffects::avg_slopes(m_arousal, variables=c("Condition", "StimuliType"), by="Gender") |>
+  results_table()
+```
+
+```{r Arousal with Stimuli Type}
+
+m_arousal_st <- glmmTMB::glmmTMB(Arousal ~ Gender/ StimuliType/ Condition + 
+                                (Condition| Participant) + (1|Stimulus), family=glmmTMB::ordbeta(),
+                              data=df, control = glmmTMB::glmmTMBControl(parallel = 8))
+
+results_table(m_arousal_st)
+
+marginaleffects::avg_slopes(m_arousal_st, variables=c("Condition", "StimuliType"), by="Gender") |>
   results_table()
@@
 
+```{=html}
 <!-- 1.For Males, giving feedback indicating that AI-generated images were less attractive, influenced arousal ratings for images labeled as AI-generated.
@@
 -->
+```
 
@@
 
-```{r Arousal Believed}
+```{r Arousal Believed with stimuli type}
 m <- glmmTMB::glmmTMB(Arousal ~ Gender / StimuliType/Condition + (Condition|Participant) + (Condition|Stimulus),
+                        data=filter(df, ConditionBelief == "True"), 
+                        family=glmmTMB::ordbeta(),
+                        control = glmmTMB::glmmTMBControl(parallel = 8))
+
+results_table(m)
+```
+
+```{r Arousal Believed without stimuli type}
+m <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition + (Condition|Participant) + (Condition|Stimulus),
                         data=filter(df, ConditionBelief == "True"), 
@@
 
+```{r Enticement Model with stimuly type}
+m_enticement_st <- glmmTMB::glmmTMB(Enticing ~ Gender / StimuliType/ Condition + 
+                                   (Condition | Participant) + (1|Stimulus),
+                      data=df, family=glmmTMB::ordbeta(),
+                      control = glmmTMB::glmmTMBControl(parallel = 8))
+
+results_table(m_enticement_st)
+
+marginaleffects::avg_slopes(m_enticement_st, variables="Condition", by="Gender") |>
+  results_table()
+
+```
+
 ### Moderators
@@
 <!-- Note: Feedback that 'No Images were Arousing' , 'Some Images were Arousing' and the 'difference between real and photos was Subtle' only had 1 level, hence were excluded from the following analysis -->
+
 ```{r Enticement Moderator}
@@
 
-```{r Enticement Believed1}
+```{r Enticement Believed1 with stimuli type}
+m <- glmmTMB::glmmTMB(Enticing ~ Gender/ StimuliType/ Condition + (Condition| Participant) + (1|Stimulus),
+                      data=filter(df, ConditionBelief == "True"), 
+                      family=glmmTMB::ordbeta(),
+                      control = glmmTMB::glmmTMBControl(parallel = 8))
+
+results_table(m)
+```
+
+```{r Enticement Believed1 wihtout stimuli type}
 m <- glmmTMB::glmmTMB(Enticing ~ Gender / Condition + (Condition| Participant) + (1|Stimulus),
@@
 <!-- The intercept is Male and photograph.  -->
+
 Women rated images overall as lower in valence than men did.
@@
 ```{r Valence Model}
-m_valence <- glmmTMB::glmmTMB(Valence ~ Gender / StimuliType/ Condition + 
+m_valence <- glmmTMB::glmmTMB(Valence ~ Gender/ Condition + 
                                 (Condition| Participant) + (1|Stimulus),
@@
 marginaleffects::avg_slopes(m_valence, variables="Condition", by="Gender") |>
+  results_table()
+
+```
+
+```{r Valence Model with stimuli type}
+m_valence_st <- glmmTMB::glmmTMB(Valence ~ Gender / StimuliType/ Condition + 
+                                (Condition| Participant) + (1|Stimulus),
+                      data=df, family=glmmTMB::ordbeta(),
+                      control = glmmTMB::glmmTMBControl(parallel = 8))
+
+results_table(m_valence_st)
+
+marginaleffects::avg_slopes(m_valence_st, variables="Condition", by="Gender") |>
   results_table()
@@
 
-```{r Valence Believed1}
+```{r Valence Believed1 with stimuli type}
+m <- glmmTMB::glmmTMB(Valence ~ Gender / StimuliType/ Condition + (Condition| Participant) + (1|Stimulus),
+                      data=filter(df, ConditionBelief == "True"), 
+                      family=glmmTMB::ordbeta(),
+                      control = glmmTMB::glmmTMBControl(parallel = 8))
+
+results_table(m)
+
+```
+
+```{r Valence Believed1 without stimuli type}
 m <- glmmTMB::glmmTMB(Valence ~ Gender /Condition + (Condition| Participant) + (1|Stimulus),
@@
 ```{r Emotionality Model}
-m_emotionality <- glmmTMB::glmmTMB(Emotionality ~ Gender /StimuliType/ Condition + (Condition| Participant) + (1|Stimulus),
+m_emotionality <- glmmTMB::glmmTMB(Emotionality ~ Gender/ Condition + (Condition| Participant) + (1|Stimulus),
                       data=df, family=glmmTMB::ordbeta(),
@@
 marginaleffects::avg_slopes(m_emotionality, variables="Condition", by="Gender", re.form=NA) |>
+  results_table()
+```
+
+```{r Emotionality Model with stimuli type}
+m_emotionality_st <- glmmTMB::glmmTMB(Emotionality ~ Gender /StimuliType/ Condition + (Condition| Participant) + (1|Stimulus),
+                      data=df, family=glmmTMB::ordbeta(),
+                      control = glmmTMB::glmmTMBControl(parallel = 8))
+
+results_table(m_emotionality_st)
+
+marginaleffects::avg_slopes(m_emotionality_st, variables="Condition", by="Gender", re.form=NA) |>
   results_table()
@@
 
-```{r EMotionality Believed1}
+```{r EMotionality Believed1 with stimuli type}
+m <- glmmTMB::glmmTMB(Emotionality ~ Gender/StimuliType/ Condition + (Condition| Participant) + (1|Stimulus),
+                      data=filter(df, ConditionBelief == "True"), 
+                      family=glmmTMB::ordbeta(),
+                      control = glmmTMB::glmmTMBControl(parallel = 8))
+
+results_table(m)
+
+```
+
+```{r EMotionality Believed1 without stimuli type}
 m <- glmmTMB::glmmTMB(Emotionality ~ Gender / Condition + (Condition| Participant) + (1|Stimulus),
@@
 #                     y = c(0.53, 0.40, 0.6, 0.51, 0.62, 0.58))
-
-stars1b <- data.frame(label=c("*"),
-                    Gender=fct_relevel(c("Male"), "Male"),
-                    Outcome=c("Arousal"),
-                    x=1,
-                    y=0.60)
 

### 2025-08-04 study2/analysis/0_preprocessing.py
updated dataset

@@ -125,9 +125,6 @@ break_files = [file for file in files if file.endswith("_break.csv")] # only fil
 phase1_files = [file for file in files if file.endswith("_phase1.csv")] # only files ending in break
 full_files = {f.replace("_Full.csv", "") for f in files if f.endswith("_Full.csv")}
 
-
-# files =["fchewatykz_Full.csv", "e77b658j0u_Full.csv", "lfo5rrdu9j_Full.csv","2c7w3enlwf_Full.csv", "7xqzrwrgv2_Full.csv", "qfu1gsb248_Full.csv", "n66clkllgv_Full.csv", "5lfwsyc1td_Full.csv", "9b9uo9mzd9_Full.csv", "z9vmjhw9en_Full.csv"]
-
 for i, file in enumerate(files):
     #skip demo files
     if file in demo_files:
@@ -650,6 +647,7 @@ correlations_df = pd.DataFrame(list(correlations.items()), columns=["Participant
 # Compute distirbution based on correlations 
 correlations_df['Correlation'].hist()
 
+
 # data_task[data_task["Participant"] == 'S002']
 
 
@@ -675,11 +673,14 @@ data_demo["Experiment_Duration"].median()
 # Look for duplicates in the data in the column prolific_id
 duplicates = data_demo[data_demo.duplicated(subset=["Prolific_ID"], keep=False)]
 
-# # Save data ==============================================================
-# data_demo = data_demo.drop(columns=["Prolific_ID"])
+# Remove participant based on prolific_id (duplicate)
+data_demo = data_demo[data_demo["Participant"] != "S278"] # remove participant with no data
 
-# data_demo.to_csv("../data/rawdata_participants.csv", index=False)
-# data_task.to_csv("../data/rawdata_task.csv", index=False)
-# data_eye.to_csv("../data/rawdata_eyetracking.csv", index=False)
+# # Save data ==============================================================
+data_demo = data_demo.drop(columns=["Prolific_ID"])
+
+data_demo.to_csv("../data/rawdata_participants.csv", index=False)
+data_task.to_csv("../data/rawdata_task.csv", index=False)
+data_eye.to_csv("../data/rawdata_eyetracking.csv", index=False)
 
 

### 2025-08-04 study2/analysis/2_emotion.qmd
updated analysis script

@@
 
-```{r Enticement Model with stimuly type}
+```{r Enticement Model with stimuli type}
 m_enticement_st <- glmmTMB::glmmTMB(Enticing ~ Gender / StimuliType/ Condition + 
@@
 pred1 <- rbind(
-  modelbased::estimate_means(m_arousal, by=c("Gender", "StimuliType", "Condition"), backend = "emmeans") |>
+  modelbased::estimate_means(m_arousal, by=c("Gender", "Condition"), backend = "emmeans") |>
   as.data.frame() |> 
   mutate(Outcome="Arousal"),
-  modelbased::estimate_means(m_enticement, by=c("Gender","StimuliType",  "Condition"), backend = "emmeans") |>
+  modelbased::estimate_means(m_enticement, by=c("Gender", "Condition"), backend = "emmeans") |>
   as.data.frame() |> 
   mutate(Outcome="Enticement"),
-  modelbased::estimate_means(m_valence, by=c("Gender", "StimuliType", "Condition"), backend = "emmeans") |>
+  modelbased::estimate_means(m_valence, by=c("Gender","Condition"), backend = "emmeans") |>
   as.data.frame() |> 

### 2025-08-04 study2/analysis/2_emotion.qmd
Update 2_emotion.qmd

@@
 
-marginaleffects::avg_slopes(m_arousal, variables=c("Condition", "StimuliType"), by="Gender") |>
+marginaleffects::avg_slopes(m_arousal, variables="Condition", by="Gender") |>
   results_table()
@@
 
-```{=html}
 <!-- 1.For Males, giving feedback indicating that AI-generated images were less attractive, influenced arousal ratings for images labeled as AI-generated.
@@
 -->
-```
 
@@
 display(moderator_results)
+
 ```
@@
 ```{r Enticement Model}
-m_enticement <- glmmTMB::glmmTMB(Enticing ~ Gender / StimuliType/ Condition + 
+m_enticement <- glmmTMB::glmmTMB(Enticing ~ Gender / Condition + 
                                    (Condition | Participant) + (1|Stimulus),
@@
 
-marginaleffects::avg_slopes(m_enticement_st, variables="Condition", by="Gender") |>
+marginaleffects::avg_slopes(m_enticement_st, variables=c("Condition", "StimuliType"), by="Gender") |>
   results_table()
@@
 
-marginaleffects::avg_slopes(m_valence_st, variables="Condition", by="Gender") |>
+marginaleffects::avg_slopes(m_valence_st, variables=c("Condition", "StimuliType"), by="Gender") |>
   results_table()
@@
 
-marginaleffects::avg_slopes(m_emotionality_st, variables="Condition", by="Gender", re.form=NA) |>
+marginaleffects::avg_slopes(m_emotionality_st, variables=c("Condition", "StimuliType"), by="Gender", re.form=NA) |>
   results_table()
@@
 
--   Gender is a major predictor of arousal, enticement and valence, with females generally reporting lower ratings than males overall.
+-   Gender is a major predictor of arousal, enticement and valence, with females generally reporting lower ratings than males overall but not significantly.
+- Men significantly rate AI images as less arousing, enticing and valent than images presented as real photos.
+- Women rate images presented as AI-generated lower in valence than images presented as real photos.
+
 -  Women prefer couple images (i.e.,significantly higher arousal, enticement and valence ratings); men prefer individual images (i.e.,significantly lower arousal, enticement and valence ratings).
@@
 
--   For women, positive attitudes towards AI moderated arousal and enticement, resulting in more favorable evaluations of AI-generated images.
+<!-- -   For women, positive attitudes towards AI moderated arousal and enticement, resulting in more favorable evaluations of AI-generated images.
 Negative attitudes moderated valence ratings, leading to less favorable evaluations.
--   Negative attitudes towards AI moderated valence ratings for both genders
--   Reporting having higher knowledge about AI moderated valence ratings for men
--   Sexual activity moderated enticement ratings for females. Specifically, females who reported having sexual activity within the 3 previous days tended to rate AI images higher in enticement.
--   Men’s perceptions of the attractiveness of AI-generated images moderated both arousal and valence ratings. More attractive AI images were rated as more arousing and valent.
--   Female's feedback that no images were attractive moderated arousal ratings.
+-->
+<!-- -   Negative attitudes towards AI moderated arousal, valence ratings for both genders -->
+<!-- -   Reporting having higher knowledge about AI moderated arousal, valence ratings for men -->
+<!-- <!-- -   Sexual activity moderated enticement ratings for females.
+Specifically, females who reported having sexual activity within the 3 previous days tended to rate AI images higher in enticement.
+--> -->
+<!-- -   Men’s perceptions of the attractiveness of AI-generated images moderated both arousal and valence ratings.
+More attractive AI images were rated as more arousing and valent, less attractive.
+-->
+<!-- -   Female's feedback that no images were attractive moderated arousal ratings. -->
 
@@
 
-stars1b <- data.frame(label=c("*","**", "*","*"),
-                    Gender=fct_relevel(c("Male", "Male", "Male","Male"), "Male"),
-                    Outcome=c("Arousal", "Enticement", "Enticement","Valence"),
-                    x=c(1, 1, 2, 1),
-                    y=c(0.60, 0.65, 0.56, 0.68))
+# stars1b <- data.frame(label=c("*","**", "*","*"),
+#                     Gender=fct_relevel(c("Male", "Male", "Male","Male"), "Male"),
+#                     Outcome=c("Arousal", "Enticement", "Enticement","Valence"),
+#                     x=c(1, 1, 2, 1),
+#                     y=c(0.60, 0.65, 0.56, 0.68))
 
@@
   mutate(Gender = fct_relevel(Gender, "Male", "Female")) |> 
-  ggplot(aes(x=StimuliType, y=Proportion)) +
+  ggplot(aes(x=Outcome, y=Proportion)) +
   geom_hline(yintercept=0, color="darkgrey") +
@@
   geom_pointrange(aes(ymin = CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.2), size=0.3) +
-  geom_text(data=stars1b, aes(x=x, y=y, label=label), hjust=0.5, color="#424242", size=6) +
-  geom_rect(data=data.frame(StimuliType = "Individual", Proportion=0.1, Gender=as.factor("Male"), Outcome="Arousal"),
-            aes(xmin=0.8, xmax=1.2, ymin=0.35, ymax=0.7), color="#8BC34A", alpha=0, ) +
-  geom_rect(data=data.frame(StimuliType = "Individual",Proportion=0.1, Gender=as.factor("Female"), Outcome="Arousal"),
-            aes(xmin=0.8, xmax=1.2, ymin=0.2, ymax=0.5), color="#8BC34A", alpha=0) +
-  facet_grid(Outcome~Gender, switch="y", scales ="free") +
+  # geom_text(data=stars1a, aes(x=x, y=y, label=label), hjust=0.5, color="#424242", size=6) +
+  # geom_rect(data=data.frame(StimuliType = "Individual", Proportion=0.1, Gender=as.factor("Male"), Outcome="Arousal"),
+  #           aes(xmin=0.8, xmax=1.2, ymin=0.35, ymax=0.7), color="#8BC34A", alpha=0, ) +
+  # geom_rect(data=data.frame(StimuliType = "Individual",Proportion=0.1, Gender=as.factor("Female"), Outcome="Arousal"),
+            # aes(xmin=0.8, xmax=1.2, ymin=0.2, ymax=0.5), color="#8BC34A", alpha=0) +
+  facet_grid(~Gender, switch="y", scales ="free") +
   scale_y_continuous(limits=c(0, 1), labels=scales::percent) +
@@
 m3 <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition  + (Condition | Participant) + (1|Stimulus),
-                      data=filter(df, ConditionBelief == "True", Feedback_NoFacesAttractive=="True"), 
+                      data=filter(df, ConditionBelief == "True", Feedback_AILessAttractive=="True"), 
                       family=glmmTMB::ordbeta(),
@@
 
-stars2 <- data.frame(label=c("**", "***", "*", "*", "*"),
-                    Gender=fct_relevel(c("Male", "Male", "Male", "Female", "Female")),
-                    Type=c("All trials", "Believed trials" ,"'AI was more attractive'", "Believed trials", "'No faces were attractive'"),
-                    y=c(0.52, 0.56, 0.66, 0.47, 0.39))
+stars2 <- data.frame(label=c("**", "***", "*", "***", "*", "*"),
+                    Gender=fct_relevel(c("Male", "Male", "Male", "Female", "Male", "Male")),
+                    Type=c("All trials", "Believed trials" ,"'AI was more attractive'", "Believed trials", "'AI was less attractive'", "'AI was less attractive'"),
+                    y=c(0.52, 0.56, 0.66, 0.47, 0.39, 0.6))
 
@@
   estimate_relation(m3) |> 
-    mutate(Type = "'No faces were attractive'"),
+    mutate(Type = "'AI was less attractive'"),
   estimate_relation(m4) |> 
@@
 p2 <- pred2 |> 
-  mutate(Type = fct_relevel(Type, "All trials", "Believed trials", "'No faces were attractive'", "'AI was more attractive'")) |> 
+  mutate(Type = fct_relevel(Type, "All trials", "Believed trials", "'AI was less attractive'", "'AI was more attractive'")) |> 
   ggplot(aes(x=Type, y=Predicted)) +

### 2025-08-05 study2/analysis/1_cleaning.qmd
updated data and html cleaning

@@
 
+Only `r sum(df$SexualOrientation == "Other")` participants self-reported as not being heterosexual, homosexual, nor bisexual, hence they were removed from further analysis.
+
 ```{r}
 df<- filter(df, !Gender=="Other")
+df<- filter(df, !SexualOrientation=="Other")
+
 df <- filter(df, !Participant %in% outliers$arousal)

### 2025-08-05 study2/analysis/2_emotion.qmd
Update 2_emotion.qmd
need to render this version

@@
 
+df$SexualOrientation <- droplevels(df$SexualOrientation)
+
 ```
@@
 ## Arousal
-
-Similar to [study1](https://realitybending.github.io/FictionEro/study1/analysis/2_emotions.html) arousal ratings for some "AI-generated" are lower then when they are presented as real photos.
+<!-- Similar to [study1](https://realitybending.github.io/FictionEro/study1/analysis/2_emotions.html) arousal ratings for some "AI-generated" are lower then when they are presented as real photos. -->
 
@@
 
-### Whole Sample
+### Sample
+
+This model examines the effect of **Gender Sexual Orientation and Condition on Arousal**, accounting for random variability due to participants and items (i.e., random intercepts) and condition as random slope for participants.
+
+<!-- The intercept is Male, photograph, individuals  -->
+
+Men rate images labelled as AI-generated as less arousing than images labelled as real.  Women also rate AI-generated images lower in arousal but not significantly.
+
+```{r Arousal}
+
+m_arousal <- glmmTMB::glmmTMB(Arousal ~ Gender/ Condition + 
+                                (Condition| Participant) + (1|Stimulus), family=glmmTMB::ordbeta(),
+                              data=df, control = glmmTMB::glmmTMBControl(parallel = 8))
+
+results_table(m_arousal)
+
+marginaleffects::avg_slopes(m_arousal, variables="Condition", by="Gender") |>
+  results_table()
+```
+
+#### Sample with Stimili Type
 
 This model examines the effect of **Gender Sexual Orientation, stimuli type, and Condition on Arousal**, accounting for random variability due to participants and items (i.e., random intercepts) and condition as random slope for participants.
-
-<!-- The intercept is Male, photograph, individuals  -->
 
@@
 Women show greater arousal toward couple images than individual ones.
-Men show less arousal for AI-generated individual images compared to photographic individual images.
-
-Looking at average slopes:
-
-1.  Males rate AI-generated images \~0.014 lower in arousal (on average) than photos — significant.
-2.  Females also rate AI images lower, but not significantly.
-3.  Males rate couple images significantly lower in arousal than individual ones.
-4.  Females rate couple images significantly higher in arousal than individual ones.
-
-```{r Arousal}
-
-m_arousal <- glmmTMB::glmmTMB(Arousal ~ Gender/ Condition + 
-                                (Condition| Participant) + (1|Stimulus), family=glmmTMB::ordbeta(),
-                              data=df, control = glmmTMB::glmmTMBControl(parallel = 8))
-
-results_table(m_arousal)
-
-marginaleffects::avg_slopes(m_arousal, variables="Condition", by="Gender") |>
-  results_table()
-```
+Men show less arousal for AI-generated individual and couple images compared to photographic images.
 
@@
 
+#### Questionnaires
+
 This model explores whether various factors such as **attitudes towards AI, knowledge about AI, frequency of porn consumption, and sexual activity** moderate the relationship between gender, image relevance (specifically AI-generated versus photographs), and arousal ratings.
 
-The analysis revealed a significant interaction effect only for **positive attitudes towards AI** among females.
+The analysis revealed a significant interaction effect for **positive, and negative, attitudes towards AI** among females and males respectively.
 Specifically, females with higher positive attitudes towards AI rated AI-generated images as more arousing, relative to when they viewed images labelled as photographs.
+Additionally, males with higher **negative attitudes towards AI** rated AI-generated labelled images as less arousing.
+
+Females self-report on their expertise on AI was also a moderator of arousal ratings. In particular, females with higher ratings of AI-knowledge rated images labelled as AI-generated as more arousing.
 
 No other moderators showed statistically significant effects on arousal across the interactions of gender, condition (AI-generated vs Photograph), and the respective moderators.
-
-We also examined whether **feedback** moderates the relationship between gender and condition on arousal.
-Findings suggest that feedback moderates this relationship only for men.
-Specifically, males who reported finding AI-generated images as less and more arousing had lower and higher, respectively, arousal ratings for those images.
-
-Lastly, the interaction between sexual activity and condition on Arousal levels.
-The three-way interaction between gender, condition (AI-Generated), and sexual activity did not reach statistical significance for either males or females, suggesting that the relationship between the AI-Generated condition and arousal ratings does not significantly vary with sexual activity levels for either gender.
-
-<!-- All significant findings for feedback  -->
-
-<!-- 1.For Males, giving feedback indicating that AI-generated images were less attractive, influenced arousal ratings for images labeled as AI-generated.
-Specifically, males who reported finding AI-generated images as less arousing had lower arousal ratings for those images.
-
-<!-- 2.
-For Males, giving feedback indicating that AI-generated images were more attractive significantly influenced arousal ratings for images labeled as AI-generated.
-Specifically, males who reported finding AI-generated images more attractive had higher arousal ratings for these images.
--->
-
-<!-- Note: The feedback that the difference between the conditions was subtle only had one value - i.e., False.
-The feedback that some AI images were arousing and that no AI images were arousing also only had one value - i.e., False -->
 
@@
 
+#### Feedback
+
+We also examined whether **feedback** moderates the relationship between gender and condition on arousal.
+
+Findings suggest that feedback moderates this relationship only for men.
+Specifically, males who reported finding AI-generated images as less and more arousing had lower and higher, respectively, arousal ratings for those images.
+
 ```{r Arousal Moderator Feedback}
@@
 
+#### Sexual Activity
+
+Lastly, the interaction between sexual activity and condition on Arousal levels.
+The three-way interaction between gender, condition (AI-Generated), and sexual activity did not reach statistical significance for either males or females, suggesting that the relationship between the AI-Generated condition and arousal ratings does not significantly vary with sexual activity levels for either gender.
+
 ```{r Arousal Sexual Activity}
@@
 ### Believed
-
+#### With Stimuli Type
 ```{r Arousal Believed with stimuli type}
@@
 ```
+
+#### Without Stimuli Type
+
+For trials believed to be true (i.e., labelled in phase 2 matches label presented in phase 1), both males and females rated AI-generated images lower in Arousal then images labelled as real photos.
 
@@
 
-Enticment ratings, for some images, differ by whether the images were preceeded by 'photograph' or by 'AI-generated'.
-
 ```{r Enticement Desc}
@@
 
-### Whole Sample
+### Sample
+This model examines how **Gender and Condition influence enticement** ratings, treating participant and items as random intercepts.
+
+Men rate images presented as AI-generated significantly lower in enticement than images presented as real photos.
+
+```{r Enticement Model}
+m_enticement <- glmmTMB::glmmTMB(Enticing ~ Gender / Condition + 
+                                   (Condition | Participant) + (1|Stimulus),
+                      data=df, family=glmmTMB::ordbeta(),
+                      control = glmmTMB::glmmTMBControl(parallel = 8))
+
+results_table(m_enticement)
+
+marginaleffects::avg_slopes(m_enticement, variables="Condition", by="Gender") |>
+  results_table()
+
+```
+
+#### Sample with Stimuli Type
 
@@
 
-Looking at the average slopes, both genders rate Ai-generated conditions lower in enticement, although this effect is only significant for men.
-
-```{r Enticement Model}
-m_enticement <- glmmTMB::glmmTMB(Enticing ~ Gender / Condition + 
-                                   (Condition | Participant) + (1|Stimulus),
-                      data=df, family=glmmTMB::ordbeta(),
-                      control = glmmTMB::glmmTMBControl(parallel = 8))
-
-results_table(m_enticement)
-
-marginaleffects::avg_slopes(m_enticement, variables="Condition", by="Gender") |>
-  results_table()
-
-```
-
 ```{r Enticement Model with stimuli type}
@@
 
+#### Questionnaires
+
 We examined whether **attitudes towards AI, porn frequency, and sexual activity** moderated the relationship between the predictors (sex, relevance, condition) and enticement ratings.
-The results showed that enticing ratings for images labeled AI-generated were moderated by the feedback reporting attitudes towards AI, but this was only significant for women.
+
+The results showed that enticing ratings for images labeled AI-generated were moderated by the feedback reporting attitudes towards AI.
 Specifically, women who reported having more positive attitudes towards AI, rated these images higher in arousal compared to images labeled as photographs.
-
-Looking at **feedback as a moderator**, the results showed that enticement ratings for images labelled as AI-Generated were moderated by the feedback that AI is less attractive for males, and that difference between the AI-Generated images and real photos is obvious for females.
-Specifically,
-
-Lastly, the interaction between sexual activity and condition on enticement, suggests that enticement ratings do not significantly differ with sexual activity levels for either gender.
+While, men reporting having more negative attitudes towards AI reported these images as less enticing.
+
+Sexual activity was a significant moderator for females ratings of enticement, specifically those that reported having has sexual acitvity in the three days prior to the survey rated images as more enticing.
 
@@
 
+#### Feedback
+
+Looking at **feedback as a moderator**, the results showed that enticement ratings for images labelled as AI-Generated were moderated by the feedback that AI is less attractive for males, where they rated these images as less enticing.
+Additionally, women who reported believing all labels were incorrect rated AI-generated images as less enticing.
+
 ```{r Enticement Moderator Feedback}
@@
 ```
+
+#### Sexual Activity
+Lastly, the interaction between sexual activity and condition on enticement, suggests that enticement ratings do not significantly differ with sexual activity levels for either gender.
 
@@
 
-<!-- Effect becomes larger, more significant and goes in both directions for both genders -->
-
+#### With Stimuli Type
 <!-- Note. Adding condition as random slope for participant did not converge -->
-
 ```{r Enticement Believed1 with stimuli type}
@@
 ```
+
+#### Without Stimuli Type
+
+For trials where the original labels where believed to be true both genders rated AI-generated images as less enticing.
 
@@
 
-### Whole Sample
+### Sample
+This model examines the effect of **Gender, and Condition on Valence** ratings, while accounting for random variability due to participants and items (i.e., random intercepts).
+
+Both genders rate AI-generated images as less valent than images labelled as real photos.
+
+```{r Valence Model}
+m_valence <- glmmTMB::glmmTMB(Valence ~ Gender/ Condition + 
+                                (Condition| Participant) + (1|Stimulus),
+                      data=df, family=glmmTMB::ordbeta(),
+                      control = glmmTMB::glmmTMBControl(parallel = 8))
+
+results_table(m_valence)
+
+marginaleffects::avg_slopes(m_valence, variables="Condition", by="Gender") |>
+  results_table()
+
+```
+
+#### With Stimuli Type
 
@@
 
-```{r Valence Model}
-m_valence <- glmmTMB::glmmTMB(Valence ~ Gender/ Condition + 
-                                (Condition| Participant) + (1|Stimulus),
-                      data=df, family=glmmTMB::ordbeta(),
-                      control = glmmTMB::glmmTMBControl(parallel = 8))
-
-results_table(m_valence)
-
-marginaleffects::avg_slopes(m_valence, variables="Condition", by="Gender") |>
-  results_table()
-
-```
-
 ```{r Valence Model with stimuli type}
@@
 
+#### Questionnaires
+
 Here we look at whether the relationship between gender and condition and valence is moderated by **AI-attitudes, porn frequency, and sexual activity**.
-The results showed that enticing ratings for images labeled AI-generated were moderated by the feedback reporting attitudes towards AI, but this was only significant for women.
-More specifically, females who have more positive and negative attitudes towards AI rated images labelled as AI-Generated significantly higher and lower in valence compared to images labelled as photographs.
-
-Looking at **feedback** as a moderator, the results show that valence ratings for images labelled AI-Generated were moderted by the feedback that the difference between AI and Photos was obvious, but only for females.
+
+The results showed that enticing ratings for images labeled AI-generated were moderated by the feedback reporting attitudes towards AI only for males.
+More specifically, males reporting more negative attitudes towards AI, rated these images as less valent.
+Additionally, males reporting higher AI experitise, rated AI images as more valent.
 
@@
 
+#### Feedback
+
+Looking at **feedback** as a moderator, the results show that valence ratings for images labelled AI-Generated were moderated by the feedback that AI images were more attractive for males.
+
+Additionally, both feedback that there were no difference between AI and real photos and that the difference between AI and photos was obvious where both moderators for females ratings of valence - with females reporting these feedbacks rating AI images as less valent.
+
+Males feedback that labels were incorrect was also a moderator for valent ratings of AI-generated images, with these images being rated as more valent for those reporting this feedback.
 ```{r Valence Moderator Feedback}
@@
 
+#### With Stimuli Type
 ```{r Valence Believed1 with stimuli type}
@@
 ```
+
+#### Without Stimuli Type
+
+Both genders rate images labelled as AI-generated as less valent for trials where they believed the original labels to be true.
 
@@
 
-### Whole Sample
-
-This model looks at the effect of **Gender, StimuliType and Condition on Emotionality**, accounting for random variability due to participants and items (i.e., random intercepts).
-
-Females, compared to males, report significantly lower emotionality ratings for fotographs.
-Among males, couple stimuli are rated lower than individual stimuli.Among females, couple stimuli are rated higher than individual stimuli.
-For males, AI-generated individual stimuli are rated lower than human-generated ones.
-Females have lower ratings for AI-generated couple stimuli compared to AI-generated stimuli of individuals.
+### Sample
+This model looks at the effect of **Gender and Condition on Emotionality**, accounting for random variability due to participants and items (i.e., random intercepts).
+
+Both genders rate AI-generated images as less emotional than images labelled as photographs.
 
@@
 
+#### With Stimuli Type
+
+This model looks at the effect of **Gender, StimuliType and Condition on Emotionality**, accounting for random variability due to participants and items (i.e., random intercepts).
+
+Females, compared to males, report significantly lower emotionality ratings for fotographs.
+Among males, couple stimuli are rated lower than individual stimuli.
+Among females, couple stimuli are rated higher than individual stimuli.
+For males, AI-generated individual, and couple, stimuli are rated lower than human-generated ones.
+
 ```{r Emotionality Model with stimuli type}
@@
 
-Looking at **AI-attitudes, porn frequency and sexual activity**, and feedback as moderators, we can see that for males reporting higher expertise in AI led to an increase of emotionality ratings for images labelled as AI-Generated.
-Additionally, males who reported having more negative attitiudes towards AI, rated AI-Generated images lower in emotionality compared to fotographs.
-While for feamles, those with more positive AI attitudes rate AI-generated images higher in emotionality.
-
-Looking at **feedback** as a moderator, the results show that for males who reported finidng AI-generated images as more attractive rated these images higher in emotionality.Conversely, males who reported finding AI-generated images as less attractive rated these images lower in emotionality.
+Looking at **AI-attitudes, porn frequency and sexual activity** as moderators, we can see that for males and females reporting higher expertise in AI led to an increase of emotionality ratings for images labelled as AI-Generated.
+
+Additionally, males and females who reported having more positive attitiudes towards AI, rated AI-Generated images higher in emotionality compared to fotographs.
+Additionally, for males, those with more negative AI attitudes rate AI-generated images lower in emotionality.
 
@@
 
+#### Feedback
+
+Looking at **feedback** as a moderator, the results show that for males who reported finidng AI-generated images as more attractive rated these images higher in emotionality.
+Conversely, males who reported finding AI-generated images as less attractive rated these images lower in emotionality.
+
+For females, who reproted believing the difference between AI and photos was none, rated AI images higher in emotionality.
+
 ```{r Emotionality Moderator Feedback}
@@
 
+#### With Stimuli Type
 ```{r EMotionality Believed1 with stimuli type}
@@
 ```
+
+#### Without Stimuli Type
+
+Both genders rated AI-generated images lower in emotionality than images presented as real photos.
 
@@
 -   Gender is a major predictor of arousal, enticement and valence, with females generally reporting lower ratings than males overall but not significantly.
-- Men significantly rate AI images as less arousing, enticing and valent than images presented as real photos.
-- Women rate images presented as AI-generated lower in valence than images presented as real photos.
-
--  Women prefer couple images (i.e.,significantly higher arousal, enticement and valence ratings); men prefer individual images (i.e.,significantly lower arousal, enticement and valence ratings).
-- AI-generation reduces arousal for men, especially for individual images. AI-generation has no significant effect on arousal for women, whether images are of individuals or couples.
+-   Condition is a major predictor of arousal, enticement and valence for males, with images presented as AI-generated being rated lower than images presented as real photos.
+For females, condition was only a significant predictor for valence scores.
+-   However when taking into account only the trials in which the original labels were believed to be true, both genders rated AI-generated images as less arousing, enticing and valent. 
+-  Women prefer couple images while men prefer individual images.
 
 **Moderators**
-
-<!-- -   For women, positive attitudes towards AI moderated arousal and enticement, resulting in more favorable evaluations of AI-generated images.
-Negative attitudes moderated valence ratings, leading to less favorable evaluations.
--->
-<!-- -   Negative attitudes towards AI moderated arousal, valence ratings for both genders -->
-<!-- -   Reporting having higher knowledge about AI moderated arousal, valence ratings for men -->
-<!-- <!-- -   Sexual activity moderated enticement ratings for females.
-Specifically, females who reported having sexual activity within the 3 previous days tended to rate AI images higher in enticement.
---> -->
-<!-- -   Men’s perceptions of the attractiveness of AI-generated images moderated both arousal and valence ratings.
-More attractive AI images were rated as more arousing and valent, less attractive.
--->
-<!-- -   Female's feedback that no images were attractive moderated arousal ratings. -->
+AI Attitudes:
+  - Females with positive attitudes rated AI images as more arousing and enticing.
+  - Males with negative attitudes rated AI images as less arousing, enticing, and valent.
+
+AI Expertise:
+  - Females with higher expertise rated AI images as more arousing.
+  - Males with higher expertise rated AI images as more valent.
+
+Feedback Effects:
+  - Males: Feedback that AI images were more arousing, attractive, or mislabelled increased ratings.
+  - Females: Feedback suggesting no/obvious difference reduced valence ratings.
 
@@
 
-# stars1a <- data.frame(label=c("**","***", "**", "***", "***", "***"),
-#                    Gender=fct_relevel(c("Male", "Female", "Male", "Female", "Male", "Female"), "Male"),
-#                     Outcome=c("Arousal","Arousal", "Enticement", "Enticement", "Valence", "Valence"),
-#                     Condition=c("Photograph", "Photograph", "Photograph", "Photograph", "Photograph", "Photograph"),
-#                     x=c(1.5, 1.5, 1.5, 1.5, 1.5, 1.5),
-#                     y = c(0.53, 0.40, 0.6, 0.51, 0.62, 0.58))
-
-# stars1b <- data.frame(label=c("*","**", "*","*"),
-#                     Gender=fct_relevel(c("Male", "Male", "Male","Male"), "Male"),
-#                     Outcome=c("Arousal", "Enticement", "Enticement","Valence"),
-#                     x=c(1, 1, 2, 1),
-#                     y=c(0.60, 0.65, 0.56, 0.68))
+stars1a <- data.frame(label=c("**","***", "**", "*"),
+                   Gender=fct_relevel(c("Male", "Male", "Male", "Female"), "Male"),
+                    Outcome=c("Arousal","Enticement","Valence", "Valence"),
+                    y = c(0.5, 0.57, 0.60, 0.60))
 
@@
   geom_pointrange(aes(ymin = CI_low, ymax=CI_high, color=Condition), position = position_dodge(width=0.2), size=0.3) +
-  # geom_text(data=stars1a, aes(x=x, y=y, label=label), hjust=0.5, color="#424242", size=6) +
-  # geom_rect(data=data.frame(StimuliType = "Individual", Proportion=0.1, Gender=as.factor("Male"), Outcome="Arousal"),
-  #           aes(xmin=0.8, xmax=1.2, ymin=0.35, ymax=0.7), color="#8BC34A", alpha=0, ) +
-  # geom_rect(data=data.frame(StimuliType = "Individual",Proportion=0.1, Gender=as.factor("Female"), Outcome="Arousal"),
-            # aes(xmin=0.8, xmax=1.2, ymin=0.2, ymax=0.5), color="#8BC34A", alpha=0) +
+  geom_text(data=stars1a, aes(y=y, label=label), hjust=0.5, color="#424242", size=6) +
+  geom_rect(data=data.frame(Outcome = "Arousal", Proportion=0.1, Gender=as.factor("Male")),
+            aes(xmin=0.8, xmax=1.2, ymin=0.35, ymax=0.53), color="#8BC34A", alpha=0, ) +
+  geom_rect(data=data.frame(StimuliType = "Individual",Proportion=0.1, Gender=as.factor("Female"), Outcome="Arousal"),
+            aes(xmin=0.8, xmax=1.2, ymin=0.33, ymax=0.48), color="#8BC34A", alpha=0) +
   facet_grid(~Gender, switch="y", scales ="free") +
-  scale_y_continuous(limits=c(0, 1), labels=scales::percent) +
+  scale_y_continuous(limits=c(0.2, 0.7), labels=scales::percent) +
   scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
@@
   labs(color="Images presented as:")
-
 p1

### 2025-08-06 study2/analysis/1_cleaning.qmd
updated cleaning file and html

@@
     full_join(
-    df[c("Participant", "Gender", "SexualOrientation")], # add Gneder and sexual orientation to this dataset
+        df[c("Participant", "Gender", "SexualOrientation")], # add Gender and sexual orientation to this dataset
         by = join_by(Participant)
     )
+
 ```
@@
     group_by(Question, Answer) |>
-  summarise(prop = n()/nrow(df), .groups = 'drop') |> 
+    summarise(prop = n() / nrow(df), .groups = "drop") |>
     complete(Question, Answer, fill = list(prop = 0)) |>
     filter(Answer == "True") |>
-  mutate(Question = str_remove(Question, "Feedback_"),
+    mutate(
+        Question = str_remove(Question, "Feedback_"),
         Question = str_replace(Question, "SomeFacesAttractive", "Some faces were attractive"),
@@
         Question = str_replace(Question, "DiffObvious", "Obvious differences between AI images and photos"),
-         Question = str_replace(Question, "LabelsReversed", "Labels were reversed")) |>
+        Question = str_replace(Question, "LabelsReversed", "Labels were reversed")
+    ) |>
     mutate(Question = fct_reorder(Question, desc(prop))) |>
@@
     geom_bar(stat = "identity") +
-  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks(), labels=scales::percent) +
-  labs(x="Feedback", y = "Participants", title = "Feedback") +
+    scale_y_continuous(expand = c(0, 0), breaks = scales::pretty_breaks(), labels = scales::percent) +
+    labs(x = "Feedback", y = "Participants", title = "Feedback") +
     theme_minimal() +
@@
     drop_na() |>
-  mutate(Authenticity = str_remove(Authenticity, "Feedback_"),
+    mutate(
+        Authenticity = str_remove(Authenticity, "Feedback_"),
         Authenticity = str_replace(Authenticity, "AllRealConfidence", "All images were real"),
-         Authenticity = str_replace(Authenticity, "AllFakeConfidence", "All images were fake")) |>
-  ggplot(aes(x = Confidence, fill= Authenticity)) +
+        Authenticity = str_replace(Authenticity, "AllFakeConfidence", "All images were fake")
+    ) |>
+    ggplot(aes(x = Confidence, fill = Authenticity)) +
     geom_bar() +
     scale_x_continuous(n.breaks = 6) +
-  labs(x="Confidence (0-5)", y = "Number of Participants", title = "Confidence on the authenticity of the images") +
+    labs(x = "Confidence (0-5)", y = "Number of Participants", title = "Confidence on the authenticity of the images") +
     theme_minimal() +
@@
         axis.text.y = element_text(size = rel(1.1)),
-    axis.title.x = element_blank())
+        axis.title.x = element_blank()
+    )
 ```
@@
 df |>
-  summarise(n = n(), .by=c("Feedback_Enjoyment")) |>
+    summarise(n = n(), .by = c("Feedback_Enjoyment")) |>
     filter(!is.na(Feedback_Enjoyment)) |>
-  mutate(n = n / sum(n),
-         Feedback_Enjoyment = fct_rev(as.factor(Feedback_Enjoyment))) |>
+    mutate(
+        n = n / sum(n),
+        Feedback_Enjoyment = fct_rev(as.factor(Feedback_Enjoyment))
+    ) |>
     ggplot(aes(y = n, x = 1, fill = Feedback_Enjoyment)) +
-  geom_bar(stat="identity", position="stack") +
-  scale_fill_manual(values=c("darkgreen", "yellowgreen",  "yellow", "orange", "red")) +
+    geom_bar(stat = "identity", position = "stack") +
+    scale_fill_manual(values = c("darkgreen", "yellowgreen", "yellow", "orange", "red")) +
     coord_flip() +
-  scale_x_continuous(expand=c(0, 0))  +
+    scale_x_continuous(expand = c(0, 0)) +
     scale_y_continuous(labels = scales::percent) +
-  labs(title="Experiment Enjoyment")+
-  guides(fill = guide_legend(reverse=TRUE)) +
+    labs(title = "Experiment Enjoyment") +
+    guides(fill = guide_legend(reverse = TRUE)) +
     theme_minimal() +
@@
         legend.position = "top",
-    legend.title = element_blank()) 
+        legend.title = element_blank()
+    )
 ```
@@
 
-outliers$Mobile <- sum(df$Mobile=="True")
+outliers$Mobile <- sum(df$Mobile == "True")
 
@@
 
-There were `r sum(df$Mobile=="True")` participants that used a mobile device.
+There were `r  length(outliers$Mobile)` participants that used a mobile device.
 
@@
 df |>
-  mutate(Participant = fct_reorder(Participant, Experiment_Duration),
+    mutate(
+        Participant = fct_reorder(Participant, Experiment_Duration),
         Category = ifelse(Experiment_Duration > 60, "extra", "ok"),
         Duration = ifelse(Experiment_Duration > 60, 60, Experiment_Duration),
-         Group = ifelse(Participant %in% outliers, "Outlier", "ok")) |>
+        Group = ifelse(Participant %in% outliers, "Outlier", "ok")
+    ) |>
     ggplot(aes(y = Participant, x = Duration)) +
@@
     scale_shape_manual(values = c("extra" = 3, ok = 20)) +
-  scale_color_manual(values = c("Outlier" = "red", ok = "black"), guide="none") +
+    scale_color_manual(values = c("Outlier" = "red", ok = "black"), guide = "none") +
     guides(color = "none", shape = "none") +
-  ggside::geom_xsidedensity(fill = "#4CAF50", color=NA) +
+    ggside::geom_xsidedensity(fill = "#4CAF50", color = NA) +
     ggside::scale_xsidey_continuous(expand = c(0, 0)) +
@@
     ggside::theme_ggside_void() +
-  theme(ggside.panel.scale = .3,
+    theme(
+        ggside.panel.scale = .3,
         panel.border = element_blank(),
         axis.text.y = element_blank(),
-        axis.ticks.y = element_blank())
+        axis.ticks.y = element_blank()
+    )
 
@@
 df |>
-  mutate(Participant = fct_reorder(Participant, Bait_Duration),
+    mutate(
+        Participant = fct_reorder(Participant, Bait_Duration),
         Category = ifelse(Bait_Duration > 5, "extra", "ok"),
         Duration = ifelse(Bait_Duration > 5, 5, Bait_Duration),
-         Group = ifelse(Participant %in% outliers, "Outlier", "ok")) |>
+        Group = ifelse(Participant %in% outliers, "Outlier", "ok")
+    ) |>
     ggplot(aes(y = Participant, x = Duration)) +
@@
     scale_shape_manual(values = c("extra" = 3, ok = 19)) +
-  scale_color_manual(values = c("Outlier" = "red", ok = "black"), guide="none") +
+    scale_color_manual(values = c("Outlier" = "red", ok = "black"), guide = "none") +
     guides(color = "none", shape = "none") +
-  ggside::geom_xsidedensity(fill = "#9C27B0", color=NA) +
+    ggside::geom_xsidedensity(fill = "#9C27B0", color = NA) +
     ggside::scale_xsidey_continuous(expand = c(0, 0)) +
@@
     ggside::theme_ggside_void() +
-  theme(ggside.panel.scale = .3,
+    theme(
+        ggside.panel.scale = .3,
         panel.border = element_blank(),
         axis.ticks.y = element_blank(),
-          axis.text.y = element_blank())
+        axis.text.y = element_blank()
+    )
 
@@
 # Single arousal response (0)
-outliers$novariability <- summarize(dftask, n = length(unique(Arousal)), .by="Participant") |> 
+outliers$novariability <- summarize(dftask, n = length(unique(Arousal)), .by = "Participant") |>
     filter(n == 1) |>
@@
     filter(!Participant %in% outliers) |>
-  summarize(cor_ArVal = cor(Arousal, Valence),
+    summarize(
+        cor_ArVal = cor(Arousal, Valence),
         cor_ArEnt = cor(Arousal, Enticing),
-            .by="Participant")
+        .by = "Participant"
+    )
 
@@
     mutate(Group = ifelse(Participant %in% outliers, "Outlier", "ok")) |>
-  mutate(name = fct_relevel(name, "cor_ArVal", "cor_ArEnt"),
-         name = fct_recode(name, "Arousal - Valence" = "cor_ArVal", "Arousal - Enticement" = "cor_ArEnt")) |>
+    mutate(
+        name = fct_relevel(name, "cor_ArVal", "cor_ArEnt"),
+        name = fct_recode(name, "Arousal - Valence" = "cor_ArVal", "Arousal - Enticement" = "cor_ArEnt")
+    ) |>
     ggplot(aes(y = Participant, x = value)) +
@@
     theme_bw() +
-  theme(axis.text.y = element_blank(),
-        axis.ticks.y = element_blank()) +
-  facet_wrap(~name, ncol=3, scales="free_x")
+    theme(
+        axis.text.y = element_blank(),
+        axis.ticks.y = element_blank()
+    ) +
+    facet_wrap(~name, ncol = 3, scales = "free_x")
 
@@
 ```{r}
-df<- filter(df, !Gender=="Other")
-df<- filter(df, !SexualOrientation=="Other")
+df <- filter(df, !Gender == "Other")
+df <- filter(df, !SexualOrientation == "Other")
 
@@
 ```{r}
-df<- filter(df, !Participant=="S030")
+df <- filter(df, !Participant == "S030")
 df <- filter(df, !Participant %in% outliers$IrrStimuli)
@@
     ggplot(aes(x = Age, fill = Gender)) +
-  geom_histogram(data=df, aes(x = Age, fill=Gender), binwidth = 2) +
-  geom_vline(xintercept = mean(df$Age), color = "red", linewidth=1.5, linetype="dashed") +
+    geom_histogram(data = df, aes(x = Age, fill = Gender), binwidth = 2) +
+    geom_vline(xintercept = mean(df$Age), color = "red", linewidth = 1.5, linetype = "dashed") +
     scale_fill_viridis_d() +
@@
     filter(SexualOrientation == "Bisexual") |>
-  ggplot(aes(x=Gender)) +
+    ggplot(aes(x = Gender)) +
     geom_bar(aes(fill = StimuliChoice)) +
@@
     mutate(Country = case_when(
-    Country=="United States"~ "USA",
-    Country=="United Kingdom" ~ "UK",
+        Country == "United States" ~ "USA",
+        Country == "United Kingdom" ~ "UK",
         TRUE ~ Country
-  ))|>
+    )) |>
     dplyr::select(region = Country) |>
@@
 p_edu <- df |>
-  mutate(Education = fct_relevel(Education, "High school", "Bachelor", "Master", "Doctorate", "Other"))|> 
+    mutate(Education = fct_relevel(Education, "High school", "Bachelor", "Master", "Doctorate", "Other")) |>
     ggplot(aes(x = Education)) +
     geom_bar(aes(fill = Education)) +
-  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
+    scale_y_continuous(expand = c(0, 0), breaks = scales::pretty_breaks()) +
     scale_fill_viridis_d(guide = "none") +
@@
 df |>
-  ggplot(aes(x = Screen_Size, fill=Mobile)) +
-  geom_histogram(bins = 50, color="black") +
-  scale_y_continuous(expand = c(0, 0), breaks= scales::pretty_breaks()) +
-  labs(x =  expression("Screen Size ("~sqrt(Number~of~Pixels)~")"), y = "Number of Participants", title = "Screen Size") +
+    ggplot(aes(x = Screen_Size, fill = Mobile)) +
+    geom_histogram(bins = 50, color = "black") +
+    scale_y_continuous(expand = c(0, 0), breaks = scales::pretty_breaks()) +
+    labs(x = expression("Screen Size (" ~ sqrt(Number ~ of ~ Pixels) ~ ")"), y = "Number of Participants", title = "Screen Size") +
     theme_modern(axis.title.space = 15) +

### 2025-08-06 analysis/server/make_model.R
added models script

@@ -1,0 +1,157 @@
+# Fit models
+
+library(tidyverse)
+library(easystats)
+library(patchwork)
+library(ggside)
+library(glmmTMB)
+
+options(mc.cores = parallel::detectCores(),
+        brms.backend = "cmdstanr",
+        width = 300)
+
+results_table <- function(model, effects="fixed", filter=NULL) {
+  if("marginaleffects" %in% class(model)) {
+    model |> 
+      parameters::parameters() |> 
+      as.data.frame() |> 
+      select(-Parameter, -SE, -S, z=Statistic) |> 
+      insight::format_table() |> 
+      parameters::display()
+  } else {
+    display(parameters::parameters(model, effects=effects, keep=filter))
+  }
+}
+
+# Study 1 ===================================================================================================================================
+
+dfsub <- dfsub <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/refs/heads/main/study1/data/data_participants.csv")
+df <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/refs/heads/main/study1/data/data.csv") |> 
+  right_join(
+    select(dfsub, Participant, Sample, Language, Mobile, starts_with("Feedback_"), 
+           BAIT_Visual, BAIT_Text, AI_Knowledge, SexualActivity, 
+           GAAIS_Negative, GAAIS_Positive, Porn, COPS_Frequency_2,
+           Screen_Size,
+           -Feedback_Comments),
+    by = "Participant"
+  ) |> 
+  datawizard::rescale(select=c("Valence"), range=c(-1, 1), to=c(0, 1)) |> 
+  mutate(Condition = fct_relevel(Condition, "Photograph", "AI-Generated"),
+         Relevance =  fct_relevel(Relevance, "Relevant", "Irrelevant", "Non-erotic"),
+         Sex =  fct_relevel(Sex, "Male", "Female"),
+         PornFrequency = as.numeric(as.factor(COPS_Frequency_2)),
+         SexualActivity_num = as.numeric(as.factor(SexualActivity)),
+         ConditionBelief = case_when(
+           Condition == "Photograph" & Realness > 0.5 ~ "True",
+           Condition == "AI-Generated" & Realness < 0.5 ~ "True",
+           .default = "False"
+         ),
[…]

### 2025-08-07 analysis/server/make_model.R
Update make_model.R

@@ -10,23 +10,10 @@ options(mc.cores = parallel::detectCores(),
         brms.backend = "cmdstanr",
         width = 300)
 
-results_table <- function(model, effects="fixed", filter=NULL) {
-  if("marginaleffects" %in% class(model)) {
-    model |> 
-      parameters::parameters() |> 
-      as.data.frame() |> 
-      select(-Parameter, -SE, -S, z=Statistic) |> 
-      insight::format_table() |> 
-      parameters::display()
-  } else {
-    display(parameters::parameters(model, effects=effects, keep=filter))
-  }
-}
-
 # Study 1 ===================================================================================================================================
 
-dfsub <- dfsub <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/refs/heads/main/study1/data/data_participants.csv")
-df <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/refs/heads/main/study1/data/data.csv") |> 
+dfsub1 <- dfsub <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/refs/heads/main/study1/data/data_participants.csv")
+df1 <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/refs/heads/main/study1/data/data.csv") |> 
   right_join(
     select(dfsub, Participant, Sample, Language, Mobile, starts_with("Feedback_"), 
            BAIT_Visual, BAIT_Text, AI_Knowledge, SexualActivity, 
@@ -54,42 +41,36 @@ df <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/refs
 # MODELS --------
 
 # Arousal
-m_a1 <-  glmmTMB::glmmTMB(Arousal ~ Sex / Relevance / Condition*ConditionBelief + (1|Participant) + (1|Item),
-                         data=df,
-                         family=glmmTMB::ordbeta(),
-                         control = glmmTMB::glmmTMBControl(parallel = 8))
-
-
-results_table(m_a1)
-saveRDS(m_a1, file = "../models/ModelArousal_1")
+m_a1 <-  glmmTMB::glmmTMB(Arousal ~ Sex / Relevance/ Condition*ConditionBelief + (1|Participant) + (1|Item),
+                          data=df1,
+                          family=glmmTMB::ordbeta(),
[…]

### 2025-08-07 analysis/analysis.qmd
started analysis script

---
title: "FictionEro - Affective Impact of Fiction"
editor: source
editor_options: 
  chunk_output_type: console
format:
  html:
    code-fold: true
    self-contained: false
    toc: true
execute: 
  cache: true
---

## Data Preparation

```{r}
#| message: false
#| warning: false

library(tidyverse)
library(easystats)
library(patchwork)
library(ggside)
library(glmmTMB)

options(mc.cores = parallel::detectCores(),
        brms.backend = "cmdstanr",
        width = 300)

results_table <- function(model, effects="fixed", filter=NULL) {
  if("marginaleffects" %in% class(model)) {
    model |> 
      parameters::parameters() |> 
      as.data.frame() |> 
      select(-Parameter, -SE, -S, z=Statistic) |> 
      insight::format_table() |> 
      parameters::display()
  } else {
    display(parameters::parameters(model, effects=effects, keep=filter))
  }
}

```

```{r data study1}
#| warning: false

dfsub1 <- dfsub <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/refs/heads/main/study1/data/data_participants.csv")
df1 <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/refs/heads/main/study1/data/data.csv") |> 
  right_join(
    select(dfsub, Participant, Sample, Language, Mobile, starts_with("Feedback_"), 
           BAIT_Visual, BAIT_Text, AI_Knowledge, SexualActivity, 
           GAAIS_Negative, GAAIS_Positive, Porn, COPS_Frequency_2,
           Screen_Size,
           -Feedback_Comments),
    by = "Participant"
    ) |> 
  datawizard::rescale(select=c("Valence"), range=c(-1, 1), to=c(0, 1)) |> 
  mutate(Condition = fct_relevel(Condition, "Photograph", "AI-Generated"),
         Relevance =  fct_relevel(Relevance, "Relevant", "Irrelevant", "Non-erotic"),
         Sex =  fct_relevel(Sex, "Male", "Female"),
         PornFrequency = as.numeric(as.factor(COPS_Frequency_2)),
         SexualActivity_num = as.numeric(as.factor(SexualActivity)),
         ConditionBelief = case_when(
           Condition == "Photograph" & Realness > 0.5 ~ "True",
           Condition == "AI-Generated" & Realness < 0.5 ~ "True",
           .default = "False"
         )) |> 
  mutate(across(starts_with("Feedback_"), function(x) {fct_relevel(x, "False", "True")}))
```

```{r data study2}
#| warning: false

dfsub2 <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/refs/heads/main/study2/data/data_participants.csv")
df2 <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/refs/heads/main/study2/data/data.csv") |> 
  right_join(
    select(dfsub2, Participant, Mobile, starts_with(c("Feedback_","BAIT")), COPS_Frequency, SexualActivity,- Feedback_Text),
    by = "Participant"
    ) |> 
    datawizard::rescale(select= c("Arousal", "Enticing", "Valence"), range=c(0, 6), to=c(0,1)) |> 
  datawizard::rescale(select= c("Realness"), range=c(-3,3), to=c(0,1)) |>
  mutate(Condition = case_when(
    Condition == "Fiction" ~ "AI-Generated",
    Condition == "Reality" ~ "Photograph"
  )) |>
  mutate(Condition = fct_relevel(Condition, "Photograph", "AI-Generated"),
         Gender =  fct_relevel(Gender, "Male", "Female"),
         SexualOrientation = fct_relevel(SexualOrientation, "Heterosexual", "Homosexual", "Bisexual"),
         PornFrequency = as.numeric(as.factor(COPS_Frequency)),
         SexualActivity_num = as.numeric(as.factor(SexualActivity)),
         ConditionBelief = case_when(
           Condition == "Photograph" & Realness > 0.5 ~ "True",
           Condition == "AI-Generated" & Realness < 0.5 ~ "True",
           .default = "False",
         )) |>
  rename(AllRealConfidence = "Feedback_AllRealConfidence",
         AllFakeConfidence = "Feedback_AllFakeConfidence",
         Enjoyment = "Feedback_Enjoyment"
         )|>
  mutate(across(starts_with("Feedback_"), as.factor)) |>
  mutate(ConditionBelief = as.factor(ConditionBelief)) |>
  mutate(StimuliType = case_when(
    grepl("couple", Stimulus, ignore.case = TRUE) ~ "Couple",
    TRUE ~ "Individual")) |>
  mutate(StimuliType = fct_relevel(StimuliType, "Individual", "Couple"))
```

## Manipulation Checks

### Distributions

```{r Arousal1}
#| fig-width: 12
arousal_dist1 <- df1 |>
  ggplot(aes(x=Arousal, fill = Condition)) +
  geom_histogram(position = "identity", alpha = 0.4, colour = "black", bins = 20) +
  scale_x_continuous(breaks = c(0, 1)) +
  labs(title = "Arousal Study 1", ) +
  facet_wrap(~Sex) +
   scale_fill_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))

arousal_dist1
```

```{r Arousal2}
#| fig-width: 12
arousal_dist2 <- df2 |>
  ggplot(aes(x=Arousal, fill = Condition)) +
  geom_bar(position = "identity", alpha = 0.5, line = "black") +
  scale_y_sqrt(expand = c(0, 0)) +
  scale_x_continuous(breaks = c(0, 1)) +
  labs(title = "Arousal Study 2", ) +
  facet_wrap(~Gender) +
   scale_fill_manual(values=c("Photograph"="#F44336", "AI-Generated"="#2196F3")) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face="bold"))

arousal_dist2
```

### Rate Belief

```{r ratebelief}

rate1 <- table(df1$Feedback_LabelsIncorrect)["True"] / sum(table(df1$Feedback_LabelsIncorrect))
rate2 <- table(df2$Feedback_AllReal)["True"] / sum(table(df2$Feedback_AllReal))

```

The rate of people that did not believe the instructions in study 1 (i.e., gave feedback that the labels were incorrect) was `r round(mean(rate1) * 100, 1)`% while in study 2 (i.e., gave feedback that all images were real images) was `r round(mean(rate2) * 100, 1)`%.

### Average Arousal

#### Study 1

```{r meanarousal 1}
#| message: false

dfsub1 <- dfsub1 |>
  right_join(
    df1 |>
      group_by(Participant, Condition) |>
      summarise(mean_arousal = mean(Arousal, na.rm = TRUE), .groups = "drop") |>
      pivot_wider(
        names_from = Condition,
        names_prefix = "mean_Arousal_",
        values_from = mean_arousal
      ) |>
      mutate(diff_arousal = `mean_Arousal_AI-Generated` - mean_Arousal_Photograph)
  )

ttest1 <- stats::t.test(diff_arousal ~ Feedback_AILessArousing, data = dfsub1)
```

```{r}
diff_plot1 <- dfsub1 |> 
  ggplot(aes(x = Feedback_AILessArousing, y = diff_arousal, fill = Feedback_AILessArousing)) +
  geom_boxplot(width = 0.4,alpha = 0.6) +
  geom_jitter(width = 0.2, alpha = 0.1, size = 1) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, fill = "black") +
  labs(
    title = "Study 1",
    x = "Participant said AI is less arousing",
    y = "Arousal Difference (AI - Photo)"
  ) +
  scale_fill_manual(values = c("True" = "#FF9800", "False" = "#E91E63")) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    legend.position = "none"
  )

diff_plot1
```

`r report(ttest1, data = dfsub1)`

#### Study 2 
```{r meanarousal 2}
#| message: false

dfsub2 <- dfsub2 |>
  right_join(
    df2|>
      group_by(Participant, Condition)|>
      summarise(mean_arousal = mean(Arousal, na.rm = TRUE), .groups = "drop") |>
      pivot_wider(names_from = Condition, 
                  names_prefix = "mean_Arousal_", 
                  values_from = mean_arousal) |>
      mutate(diff_arousal = `mean_Arousal_AI-Generated` - mean_Arousal_Photograph)
    )

ttest2 <- stats::t.test(diff_arousal ~ Feedback_AILessArousing, data = dfsub2)
```

```{r}
diff_plot2 <- dfsub2 |> 
  ggplot(aes(x = Feedback_AILessArousing, y = diff_arousal, fill = Feedback_AILessArousing)) +
  geom_boxplot(width = 0.4, alpha = 0.6) +
  geom_jitter(width = 0.2, alpha = 0.1, size = 1) +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 2, fill = "black") +
  labs(
    title = "Study 2",
    x = "Participant said AI is less arousing",
    y = "Arousal Difference (AI - Photo)"
  ) +
  scale_fill_manual(values = c("True" = "#FF9800", "False" = "#E91E63")) +
  theme_minimal() +
  theme(
    plot.title = element_text(hjust = 0.5, face = "bold"),
    legend.position = "none"
  )

diff_plot2
```

`r report(ttest2, data = dfsub1)`

## Effect of Manipulation

*Note*. Models for study 1 only include the conditions which were relevant to the participants secual orientation (e.g., seeing images of men as a heterosexual woman).

### Arousal

```{r}
arousal1 <- readRDS("models/ModelArousal_1.rds")
results_table(arousal1)

pred_a1 <- estimate_means(arousal1, by = c("Sex", "Relevance", "Condition", "ConditionBelief"), backend = "emmeans")  |>
  as.data.frame()

pred_a1|>
  mutate(Sex = fct_relevel(Sex, "Male", "Female")) |>
  ggplot(aes(x = Arousal, y= Proportion ))

```

```{r}
arousal2 <- readRDS("models/ModelArousal_2.rds")
results_table(arousal2)

pred_a2 <- estimate_means(arousal2, by = c("Gender","Condition", "ConditionBelief"), backend = "emmeans") |>
  as.data.frame()
```

## Interindividual Variability and Moderators

```{r}

```

### 2025-08-08 analysis/analysis.qmd
attempt at making graph

@@
   right_join(
-    select(dfsub, Participant, Sample, Language, Mobile, starts_with("Feedback_"), 
+    select(dfsub1, Participant, Sample, Language, Mobile, starts_with("Feedback_"), 
            BAIT_Visual, BAIT_Text, AI_Knowledge, SexualActivity, 
@@
            -Feedback_Comments),
-    by = "Participant"
-    ) |> 
+    by = "Participant") |> 
   datawizard::rescale(select=c("Valence"), range=c(-1, 1), to=c(0, 1)) |> 
@@
 arousal1 <- readRDS("models/ModelArousal_1.rds")
-results_table(arousal1)
-
-pred_a1 <- estimate_means(arousal1, by = c("Sex", "Relevance", "Condition", "ConditionBelief"), backend = "emmeans")  |>
-  as.data.frame()
-
-pred_a1|>
-  mutate(Sex = fct_relevel(Sex, "Male", "Female")) |>
-  ggplot(aes(x = Arousal, y= Proportion ))
-
+arousal2 <- readRDS("models/ModelArousal_2.rds")
 ```
@@
 ```{r}
-arousal2 <- readRDS("models/ModelArousal_2.rds")
-results_table(arousal2)
 
-pred_a2 <- estimate_means(arousal2, by = c("Gender","Condition", "ConditionBelief"), backend = "emmeans") |>
-  as.data.frame()
+pred_a <- rbind(
+  modelbased::estimate_means(arousal1, by = c("Sex", "Relevance", "Condition", "ConditionBelief"), backend = "emmeans")  |>
+    filter(Relevance == "Relevant") |>
+    select(-Relevance) |>
+    rename(Gender = "Sex") |>
+    mutate(Sample = "Study 1")|>
+  as.data.frame(), 
+  modelbased::estimate_means(arousal2, by = c("Gender","Condition", "ConditionBelief"), backend = "emmeans")|>
+    mutate(Sample = "Study 2") |>
+    as.data.frame())
+
+pred_a |>
+  ggplot(aes(x = ConditionBelief,y = Proportion, color = Condition,linetype = Sample, group = interaction(Sample, Condition))) +
+  geom_line(size = 1) +
+  geom_point(size = 2) +
+  geom_errorbar(aes(ymin = CI_low, ymax = CI_high),width = 0.1) +
+  facet_wrap(~ Gender) +
+  scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
+  theme_minimal(base_size = 14) +
+  theme(
+        axis.text.y = element_text(size = 8),
+        strip.placement = "outside",
+        strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
+        strip.text.x = element_text(size = 10),
+        strip.text.y = element_text(size = 10),
+        axis.text.x = element_text(face = "bold", size=9, color="black"),
+        legend.text = element_text(size = 10),
+        legend.position =  ) +
+  labs(x = "Whether the original labels were believed to be true",y = "Estimated Proportion",color = "Images presented as:",linetype = "Sample")
+```
+
+### Enticement
+
+```{r}
+enticement1 <- readRDS("models/ModelEnticement_1.rds")
+enticement2 <- readRDS("models/ModelEnticement_2.rds")
+```
+
+### Valence
+
+```{r}
+valence1 <- readRDS("models/ModelValence_1.rds")
+valence2 <- readRDS("models/ModelValence_2.rds")
 ```

### 2025-09-01 analysis/analysis.qmd
updated analysis

--- 2025-08-07 analysis/analysis.qmd
@@
 library(glmmTMB)
+library(gt)
 
@@
            -Feedback_Comments),
-    by = "Participant"
-    ) |> 
+    by = "Participant") |> 
+  rename(Gender = Sex) |>
   datawizard::rescale(select=c("Valence"), range=c(-1, 1), to=c(0, 1)) |> 
@@
          Relevance =  fct_relevel(Relevance, "Relevant", "Irrelevant", "Non-erotic"),
-         Sex =  fct_relevel(Sex, "Male", "Female"),
+         Gender =  fct_relevel(Gender, "Male", "Female"),
          PornFrequency = as.numeric(as.factor(COPS_Frequency_2)),
@@
   labs(title = "Arousal Study 1", ) +
-  facet_wrap(~Sex) +
+  facet_wrap(~Gender) +
    scale_fill_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
@@
 
+```{r}
+
+tbl_results <-   function(model1,                                         title_table = "Fixed Effects: Study 1"){
+
+  # ---- Fixed effects table ----
+  tbl <- parameters::parameters(model1) |>
+    as.data.frame() |>
+    select(-Effects, -Group, -Component, -df_error, -CI) |>
+    gt() |>
+    # tab_header(title = title_table, subtitle = subtitle_table) |>
+    fmt_number(columns = c("Coefficient", "SE", "CI_low", "CI_high", "z", "p"), decimals = 2) |>
+    cols_label(
+      Parameter = "Predictor",
+      Coefficient = "β",
+      SE = "SE",
+      CI_low = "CI (lower)",
+      CI_high = "CI (upper)",
+      z = "z-value",
+      p = "p"
+    ) |>
+    cols_merge(columns = c("CI_low", "CI_high"), pattern = "{1}, {2}") |>
+    cols_label(`CI_low` = "95% CI") |>
+    tab_style(
+      style = cell_text(weight = "bold"),
+      locations = cells_column_labels(everything())
+    ) |>
+    opt_table_lines()
+
+    return(tbl)
+}
+
+```
+
+```{r}
+make_model_plot <- function(model1, model2 = NULL, 
+                            title = "Estimated Marginal Means") {
+
+    pred_df <- rbind(
+      modelbased::estimate_means(model1, by = c("Gender", "Relevance", "Condition", "ConditionBelief"), backend = "emmeans")  |>
+        filter(Relevance == "Relevant") |>
+        select(-Relevance) |>
+        mutate(Sample = "Study 1")|>
+      as.data.frame(), 
+      modelbased::estimate_means(model2, by = c("Gender","Condition", "ConditionBelief"), backend = "emmeans")|>
+        mutate(Sample = "Study 2") |>
+        as.data.frame())
+
+    plt <- pred_df |>
+      ggplot(aes(x = ConditionBelief,y = Proportion, color = Condition,linetype = Sample, group = interaction(Sample, Condition))) +
+      geom_line(size = 1) +
+      geom_point(size = 2) +
+      geom_errorbar(aes(ymin = CI_low, ymax = CI_high),width = 0.1) +
+      facet_wrap(~ Gender) +
+      scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
+      theme_minimal(base_size = 14) +
+        labs(x = "Whether the original labels were believed to be true",y = "Estimated Proportion",color = "Images presented as:",linetype = "Sample", title = "Enticement") +
+      theme(
+            axis.text.y = element_text(size = 8),
+            strip.placement = "outside",
+            strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
+            strip.text.x = element_text(size = 10),
+            strip.text.y = element_text(size = 10),
+            axis.text.x = element_text(face = "bold", size=9, color="black"),
+            legend.text = element_text(size = 10),
+            legend.position =  )
+
+    return(plt)
+}
+
+```
+
 ### Arousal
@@
 arousal1 <- readRDS("models/ModelArousal_1.rds")
-results_table(arousal1)
+arousal2 <- readRDS("models/ModelArousal_2.rds")
+```
 
-pred_a1 <- estimate_means(arousal1, by = c("Sex", "Relevance", "Condition", "ConditionBelief"), backend = "emmeans")  |>
-  as.data.frame()
+```{r}
 
-pred_a1|>
-  mutate(Sex = fct_relevel(Sex, "Male", "Female")) |>
-  ggplot(aes(x = Arousal, y= Proportion ))
+tbl_a1 <- tbl_results(arousal1, title = "Fixed Effects: Arousal Study 1")
+tbl_a2 <- tbl_results(arousal2, title = "Fixed Effects: Arousal Study 2")
 
@@
 ```{r}
-arousal2 <- readRDS("models/ModelArousal_2.rds")
-results_table(arousal2)
 
-pred_a2 <- estimate_means(arousal2, by = c("Gender","Condition", "ConditionBelief"), backend = "emmeans") |>
-  as.data.frame()
+plt_a <- make_model_plot(arousal1, arousal2,
+                title = "Arousal for Relevant Stimuli")
+```
+
+### Enticement
+
+```{r}
+enticement1 <- readRDS("models/ModelEnticement_1.rds")
+enticement2 <- readRDS("models/ModelEnticement_2.rds")
+```
+
+```{r}
+
+tbl_e1 <- tbl_results(enticement1, title = "Fixed Effects: Enticement Study 1")
+tbl_e2 <- tbl_results(enticement2, title = "Fixed Effects: Enticement Study 2")
+
+```
+
+```{r}
+
+plt_e <- make_model_plot(enticement1, enticement2,
+                title = "Enticement for Relevant Stimuli")
+```
+
+### Valence
+
+```{r}
+valence1 <- readRDS("models/ModelValence_1.rds")
+valence2 <- readRDS("models/ModelValence_2.rds")
+```
+
+```{r}
+
+tbl_v1 <- tbl_results(valence1, title = "Fixed Effects: Valence Study 1")
+tbl_v2 <- tbl_results(valence2, title = "Fixed Effects: Valence Study 2")
+
+```
+
+```{r}
+
+plt_v <- make_model_plot(valence1, valence2,
+                title = "Valence for Relevant Stimuli")
 ```
@@
 
+1. extract random effects
+2. make plot of participant effects
+3. effect of condition believed + relevant 
+4. correlation matrix/ matrix of scatter plots
+
 ```{r}

### 2025-09-01 paper/manuscript.qmd
Update manuscript.qmd

@@
 
-**Materials**
+The initial sample comprised 1,067 participants recruited via multiple channels, including Prolific (ref), Sona (ref), social media platforms, university classrooms, and snowball sampling.
+This strategy yielded a heterogeneous pool of both incentivised and non-incentivised individuals, including students and members of the general population from England, France, Italy, Colombia, and Spain.
+
+To ensure data quality, several exclusion criteria were applied.
+Participants were removed if they (a) showed no variation in arousal ratings across trials (N = 8), (b) displayed a negative correlation between arousal and enticement alongside lower arousal ratings for erotic compared to neutral stimuli, suggesting a possible misunderstanding of scale direction (N = 4), or (c) self-identified with a gender or sexual orientation incompatible with the aims of the analysis (N = 350).
+For the latter, only self-reported heterosexual individuals were retained.
+
+The final sample consisted of 705 participants (Mean = 30.2 years $\pm$ 11.8, 35.7% Female).
+Participants were primarily from the United Kingdom (28.23%), Italy (18.72%), the United States (14.33%), and Colombia (11.06%), with the remaining 27.66% distributed across other countries.
+
+Ethical approval for this study was obtained from the School of Psychology Ethics Committee at the University of Sussex (ER/MHHE20/1).
+
+### Materials
+
+All written materials in this study were translated into the participants native tongue languages: English, Italian, French, Spanish.
+
+#### Questionnaires
+
+The Beliefs about Artificial Image Technology (BAIT) assesses general attitudes toward artificial intelligence (AI) and beliefs about AI-generated media.
+It includes six items adapted from the General Attitudes towards Artificial Intelligence Scale [GAAIS, @schepman2020initial; @schepman2023general] comprising three positively valenced (e.g., “Artificial Intelligence is exciting”) and three negatively valenced items (e.g., “Artificial Intelligence might take control of people”).
+In addition, several items were developed to evaluate beliefs about computer-generated imagery, such as “Current Artificial Intelligence algorithms can generate very realistic images” and “Images of faces or people generated by Artificial Intelligence always contain errors and artifacts.” All items were rated on a continuous scale from strongly disagree (0) to strongly agree (1).
+One item was included to assess self-reported AI knowledge, with anchors ranging from Not at all (0) to Expert (6).
+
+Consumption of Pornography Scale – General [COPS; @hatch2023consumption] is a 34-item measure of pornography use across four dimensions: frequency, duration, accidental exposure, and deliberate exposure.
+In the current study, a subset of items from the frequency and duration subscales was used.
+Participants reported how often they had viewed pornography in the past 30 days (e.g., not at all, once or twice, weekly, daily, multiple times per day), and the typical duration of viewing sessions (less than 5 minutes to 46+ minutes).
+An additional item assessed the recency of any sexual activity, with response options ranging from within the past 24 hours to more than a year ago.
+
+#### Affective Measures
+
+**Arousal**.
+Subjective sexual arousal was assessed following each image with the question, “How much did you feel sexually aroused?” Responses were recorded on a continuous scale from Not at all (0) to Very much (1).
+
+**Enticement**. Perceived enticement was measured after each image using the question, “How enticing would you rate this image to be?” with the same scale ranging from Not at all (0) to Very much (1).
+
+**Valence**. Emotional valence was evaluated by asking, “The feeling evoked by the image was...” rated on a scale from Unpleasant (-1) to Pleasant (1).
+
+**Perceived Realism**.
+In a final stage of the experiment, each image was shown again, and participants rated its perceived realism with the question, “How realistic was this image?” using a continuous scale anchored at AI-generated (0) and Photograph (1).
 
@@
 
-knitr::include_graphics("images/Paradigm.png")
+knitr::include_graphics("images/Paradigm1.png")
 ```
 
-**Ethics**
+The study was conducted in line with the born-open principle [@de2024datapipe], ensuring transparency and reproducibility at every stage.
+The experiment was implemented entirely in jsPsych [@de2015jspsych], with the full code hosted publicly on GitHub, which also served as the platform for running the online study.
+Raw data were automatically stored in a private Open Science Framework (OSF) repository.
+Anonymized data, together with all preprocessing and analysis scripts, will be openly released on GitHub to facilitate complete reproducibility.
+
+Participants first provided informed consent before completing a short demographic questionnaire covering gender, age, ethnicity, country of residence, education, and English proficiency.
+Optional questions on birth control use were also included.
+They then proceeded to the experimental tasks.
+
+In the first phase, participants were told that the study aimed to validate a new image-generation algorithm.
+They were informed that they would see images allegedly produced by this algorithm intermixed with real photographs, each preceded by a cue indicating whether the upcoming image was of an “AI-generated” or “Photograph" origin.
+Their task was to rate each image on arousal, enticement, and valence.
+
+Each participant viewed 60 images in total: 40 erotic images (20 male and 20 female) from the Erotic subset of the Nencki Affective Picture System [NAPS ERO; @wierzba2015erotic], and 20 additional images (10 neutral, 10 positively arousing) from the original NAPS database [@marchewka2014nencki].
+Each trial followed a fixed timing sequence: a fixation cross (750 ms), a color-coded textual cue (1,250 ms), another fixation cross (500 ms), then the image (2,500 ms).
+Cues were presented in red, green, or blue, with colors randomly assigned across participants.
+
+Following each image, participants rated their emotional response using three continuous sliders assessing sexual arousal, enticement, and valence.
+This phase was self-paced, with responses required before continuing.
+
+After completing the image-rating phase, participants filled out two self-report questionnaires: first the BAIT scale, followed by the COPS questionnaire.
+
+<!-- Thanks a lot. In the next phase, we would like to see if you found our <b>image generation algorithm convincing</b> and error-free. -->
+
+<!-- We will briefly present you <b>all the images</b> one last time (the AI-generated ones, as well as the photos), and you will have to rate them on how <b>real</b> (how realistic, photography-like) the image is.
+-->
+
+In the final phase, participants viewed the same 60 images, presented in a new randomized order.
+Each was preceded by a 500 ms fixation cross and displayed for 1,000 ms.
+This time, participants rated each image on perceived realism—how photographic or lifelike it appeared.
+
+At the end of the experiment, participants completed a feedback form.
+They were asked whether they could distinguish AI-generated from real images, whether AI images appeared more or less arousing, whether cue labels seemed accurate or reversed, and whether specific images stood out as particularly arousing or unarousing.
+
+Finally, participants were debriefed on the true purpose of the study: to examine how image labels (AI-generated vs.
+real photograph) influence emotional responses.
+Importantly, they were informed that all images were real photographs, and that the “AI-generated” label was used solely to test the effect of belief on affective reactions.
+A shareable link to the experiment was also provided.
 

### 2025-09-01 paper/manuscript.qmd
updated manuscript

@@
 
-The initial sample comprised 1,067 participants recruited via multiple channels, including Prolific (ref), Sona (ref), social media platforms, university classrooms, and snowball sampling.
+The initial sample comprised 1,067 participants recruited via multiple channels, including Prolific\textcopyright, Sona (ref), social media platforms, university classrooms, and snowball sampling.
 This strategy yielded a heterogeneous pool of both incentivised and non-incentivised individuals, including students and members of the general population from England, France, Italy, Colombia, and Spain.
@@
 
-**Participants**
+### Participants
 
-**Materials**
+The initial sample comprised of 279 participants recruited via Prolific\textcopyright.
+Participant exclusions were applied as follows: five participants were removed for showing no variability in arousal ratings (i.e., they did not move the response scales).
+An additional five participants were excluded for completing the study on a mobile device.
+One participant was excluded due to displaying negative correlations between arousal and both enticement and valence.
+Furthermore, five participants who self-identified as neither female nor male, and two participants who reported a sexual orientation other than heterosexual, homosexual, or bisexual, were excluded from further analyses.
+Finally, one participant was removed because the stimuli presented were not relevant to their gender and sexual orientation.
 
-**Procedure**
+The final sample consisted of 261 participants (Mean = 37.4 $\pm$ 12.7, 48.7% Female).
+%4.12% of participants were from the United Kingdom, 26.52% from South Africa, 11.47% from the United States and the remaining 7.89% distributed across other countries.
 
-**Ethics**
+Ethical approval for this study was obtained from the School of Psychology Ethics Committee at the University of Sussex (ER/EB672/2).
 
-**Data Analysis**
+### Materials
+
+### Procedure
+```{r}
+#| message: false
+#| warning: false
+
+knitr::include_graphics("images/Paradigm1.png")
+```
+
+### Data Analysis

### 2025-09-01 analysis/analysis.qmd
updated analysis script
analysis not completed, just a draft

@@
          AllFakeConfidence = "Feedback_AllFakeConfidence",
-         Enjoyment = "Feedback_Enjoyment"
+         Enjoyment = "Feedback_Enjoyment",
+         Item = Stimulus
          )|>
@@
   mutate(StimuliType = case_when(
-    grepl("couple", Stimulus, ignore.case = TRUE) ~ "Couple",
+    grepl("couple", Item, ignore.case = TRUE) ~ "Couple",
     TRUE ~ "Individual")) |>
@@
 
-*Note*. Models for study 1 only include the conditions which were relevant to the participants secual orientation (e.g., seeing images of men as a heterosexual woman).
+*Note*. Models for study 1 only include the conditions which were relevant to the participants sexual orientation (e.g., seeing images of men as a heterosexual woman).
 
@@
   # ---- Fixed effects table ----
-  tbl <- parameters::parameters(model1) |>
+  tbl <- parameters::parameters(model1, effects = "fixed") |>
     as.data.frame() |>
-    select(-Effects, -Group, -Component, -df_error, -CI) |>
+    select(-Effects, -df_error, -CI) |>
     gt() |>
@@
 
+### Random Effects
+
+#### Arousal
 ```{r}
+table_dvour <- function(g) {
+  performance::performance_dvour(g) |> 
+    arrange(desc(D_vour)) |> 
+    gt::gt() |> 
+    gt::data_color("D_vour", palette = c("red", "red", "orange", "yellow", "green"), domain = c(0, 1)) |> 
+    gt::fmt_auto()
+}
+
+a1 <- modelbased::estimate_grouplevel(arousal1)
+table_dvour(a1)
+
+a2 <- modelbased::estimate_grouplevel(arousal2)
+table_dvour(a2)
 
 ```
+
+### Participant effects
+
+```{r}
+plot_grouplevel_effects <- function(model, outcome_name = NULL) {
+
+  # Colors
+  colors <- c("Participant" = "#9C27B0", "Item" = "#FF9800")
+
+  # Plot
+  p <- ggplot(model, aes(x = Median, y = Level)) +
+    geom_pointrange(aes(xmin = CI_low, xmax = CI_high, color = Group), size = 0.3) +
+    ggside::geom_xsidedensity(aes(group = Group, fill = Group), color = NA, alpha = 0.3) +
+    scale_color_manual(values = colors) +
+    scale_fill_manual(values = colors) +
+    theme_minimal() +
+    theme(
+      axis.text.y = element_blank(),
+      axis.ticks.y = element_blank(),
+      axis.title.x = element_text(size = 12),
+      axis.title.y = element_blank(),
+      panel.grid.minor = element_blank(),
+      panel.grid.major.y = element_blank(),
+      legend.position = "bottom"
+    ) +
+    labs(
+      x = ifelse(is.null(outcome_name), "Random intercept (participant/item)", paste0(outcome_name, " random intercept")),
+      y = "",
+      color = "Group",
+      fill = "Group"
+    )
+
+  return(p)
+}
+
+plot_grouplevel_effects(a1, outcome_name = "Arousal")
+
+```

### 2025-09-01 analysis/server/make_model.R

@@ -22,10 +22,11 @@ df1 <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/ref
            -Feedback_Comments),
     by = "Participant"
   ) |> 
+  rename(Gender = Sex) |>
   datawizard::rescale(select=c("Valence"), range=c(-1, 1), to=c(0, 1)) |> 
   mutate(Condition = fct_relevel(Condition, "Photograph", "AI-Generated"),
          Relevance =  fct_relevel(Relevance, "Relevant", "Irrelevant", "Non-erotic"),
-         Sex =  fct_relevel(Sex, "Male", "Female"),
+         Gender =  fct_relevel(Gender, "Male", "Female"),
          PornFrequency = as.numeric(as.factor(COPS_Frequency_2)),
          SexualActivity_num = as.numeric(as.factor(SexualActivity)),
          ConditionBelief = case_when(
@@ -41,20 +42,20 @@ df1 <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/ref
 # MODELS --------
 
 # Arousal
-m_a1 <-  glmmTMB::glmmTMB(Arousal ~ Sex / Relevance/ Condition*ConditionBelief + (1|Participant) + (1|Item),
+m_a1 <-  glmmTMB::glmmTMB(Arousal ~ Gender / Relevance/ Condition*ConditionBelief + (1|Participant) + (1|Item),
                           data=df1,
                           family=glmmTMB::ordbeta(),
                           control = glmmTMB::glmmTMBControl(parallel = 8))
 
 # Enticement
-m_e1 <-  glmmTMB::glmmTMB(Enticement ~ Sex /Relevance/Condition*ConditionBelief + (1|Participant) + (1|Item),
+m_e1 <-  glmmTMB::glmmTMB(Enticement ~ Gender /Relevance/Condition*ConditionBelief + (1|Participant) + (1|Item),
                           data=df1,
                           family=glmmTMB::ordbeta(),
                           control = glmmTMB::glmmTMBControl(parallel = 8))
 
 
 # Valence
-m_v1 <-  glmmTMB::glmmTMB(Valence ~ Sex / Relevance/ Condition*ConditionBelief + (1|Participant) + (1|Item),
+m_v1 <-  glmmTMB::glmmTMB(Valence ~ Gender / Relevance/ Condition*ConditionBelief + (1|Participant) + (1|Item),
                           data=df1,
[…]

### 2025-09-02 analysis/analysis.qmd
updated analysis

@@
   html:
+    toc: true
     code-fold: true
     self-contained: false
-    toc: true
 execute: 
@@
         width = 300)
-
-results_table <- function(model, effects="fixed", filter=NULL) {
-  if("marginaleffects" %in% class(model)) {
-    model |> 
-      parameters::parameters() |> 
-      as.data.frame() |> 
-      select(-Parameter, -SE, -S, z=Statistic) |> 
-      insight::format_table() |> 
-      parameters::display()
-  } else {
-    display(parameters::parameters(model, effects=effects, keep=filter))
-  }
-}
 
@@
 
+```{r}
+
+tbl_results <-   function(model1, title_table = "Fixed Effects: Study 1"){
+
+  # ---- Fixed effects table ----
+  tbl <- parameters::parameters(model1, effects = "fixed") |>
+    as.data.frame() |>
+    select(-Effects, -df_error, -CI) |>
+    gt() |>
+    # tab_header(title = title_table, subtitle = subtitle_table) |>
+    fmt_number(columns = c("Coefficient", "SE", "CI_low", "CI_high", "z", "p"), decimals = 2) |>
+    cols_label(
+      Parameter = "Predictor",
+      Coefficient = "β",
+      SE = "SE",
+      CI_low = "CI (lower)",
+      CI_high = "CI (upper)",
+      z = "z-value",
+      p = "p"
+    ) |>
+    cols_merge(columns = c("CI_low", "CI_high"), pattern = "{1}, {2}") |>
+    cols_label(`CI_low` = "95% CI") |>
+    tab_style(
+      style = cell_text(weight = "bold"),
+      locations = cells_column_labels(everything())
+    ) |>
+    opt_table_lines()
+
+    return(tbl)
+}
+
+make_combined_plot <- function(model1, model2 = NULL, 
+                               title = "Estimated Marginal Means") {
+
+  df1 <- modelbased::estimate_means(
+    model1, by = c("Gender", "Relevance", "Condition", "ConditionBelief"),backend = "emmeans") |>
+    dplyr::mutate(Sample = "Study 1") |>
+    as.data.frame()
+
+  # Study 2: only Relevant
+  if (!is.null(model2)) {
+    df2 <- modelbased::estimate_means(
+      model2, by = c("Gender", "Condition", "ConditionBelief"), backend = "emmeans") |>
+      dplyr::mutate(Relevance = "Relevant", Sample = "Study 2") |>
+      as.data.frame()
+    pred_df <- rbind(df1, df2)
+  } else {
+    pred_df <- df1
+  }
+
+  plt <- pred_df |>
+    ggplot(aes(x = ConditionBelief, y = Proportion,color = Condition, linetype = Sample, group = interaction(Sample, Condition)
+    )) +
+    geom_hline(yintercept = 0, color = "darkgrey") +
+    geom_line(size = 1) +
+    geom_point(size = 2) +
+    geom_errorbar(aes(ymin = CI_low, ymax = CI_high), width = 0.1) +
+    facet_grid(Relevance ~ Gender, switch = "y") +
+    scale_color_manual(values = c("AI-Generated" = "#2196F3","Photograph" = "#F44336")) +
+    theme_minimal(base_size = 14) +
+    labs(title = title, x= "Whether the original labels were believed to be true",color = "Images presented as:", linetype = "Sample"
+    ) +
+    theme(
+      axis.title.y = element_blank(),
+      axis.text.y = element_text(size = 8),
+      strip.placement = "outside",
+      strip.background.x = element_rect(fill = "lightgrey", color = NA),
+      strip.text.x = element_text(size = 10),
+      strip.text.y = element_text(size = 10),
+      axis.text.x = element_text(face = "bold", size = 9, color = "black"),
+      legend.text = element_text(size = 10),
+      legend.position = "bottom"
+    )
+
+  plt
+}
+
+```
+
 ## Manipulation Checks
 
-### Distributions
+::: {.panel-tabset}
+
+### Rate Belief
+
+```{r ratebelief}
+
+rate1 <- table(df1$Feedback_LabelsIncorrect)["True"] / sum(table(df1$Feedback_LabelsIncorrect))
+rate2 <- table(df2$Feedback_AllReal)["True"] / sum(table(df2$Feedback_AllReal))
+
+```
+
+The rate of people that did not believe the instructions in study 1 (i.e., gave feedback that the labels were incorrect) was `r round(mean(rate1) * 100, 1)`% while in study 2 (i.e., gave feedback that all images were real images) was `r round(mean(rate2) * 100, 1)`%.
+
+### Arousal Distributions
 
@@
 
-### Rate Belief
-
-```{r ratebelief}
-
-rate1 <- table(df1$Feedback_LabelsIncorrect)["True"] / sum(table(df1$Feedback_LabelsIncorrect))
-rate2 <- table(df2$Feedback_AllReal)["True"] / sum(table(df2$Feedback_AllReal))
-
-```
-
-The rate of people that did not believe the instructions in study 1 (i.e., gave feedback that the labels were incorrect) was `r round(mean(rate1) * 100, 1)`% while in study 2 (i.e., gave feedback that all images were real images) was `r round(mean(rate2) * 100, 1)`%.
-
 ### Average Arousal
-
-#### Study 1
 
@@
 
-`r report(ttest1, data = dfsub1)`
-
-#### Study 2 
 ```{r meanarousal 2}
@@
 
-`r report(ttest2, data = dfsub1)`
+**Study 1**: `r report::report(ttest1, data = dfsub1)`
+
+**Study 2**: `r report::report(ttest2, data = dfsub2)`
+
+:::
 
@@
 
-*Note*. Models for study 1 only include the conditions which were relevant to the participants sexual orientation (e.g., seeing images of men as a heterosexual woman).
-
-```{r}
-
-tbl_results <-   function(model1, title_table = "Fixed Effects: Study 1"){
-
-  # ---- Fixed effects table ----
-  tbl <- parameters::parameters(model1, effects = "fixed") |>
-    as.data.frame() |>
-    select(-Effects, -df_error, -CI) |>
-    gt() |>
-    # tab_header(title = title_table, subtitle = subtitle_table) |>
-    fmt_number(columns = c("Coefficient", "SE", "CI_low", "CI_high", "z", "p"), decimals = 2) |>
-    cols_label(
-      Parameter = "Predictor",
-      Coefficient = "β",
-      SE = "SE",
-      CI_low = "CI (lower)",
-      CI_high = "CI (upper)",
-      z = "z-value",
-      p = "p"
-    ) |>
-    cols_merge(columns = c("CI_low", "CI_high"), pattern = "{1}, {2}") |>
-    cols_label(`CI_low` = "95% CI") |>
-    tab_style(
-      style = cell_text(weight = "bold"),
-      locations = cells_column_labels(everything())
-    ) |>
-    opt_table_lines()
-
-    return(tbl)
-}
-
-```
-
-```{r}
-make_model_plot <- function(model1, model2 = NULL, 
-                            title = "Estimated Marginal Means") {
-
-    pred_df <- rbind(
-      modelbased::estimate_means(model1, by = c("Gender", "Relevance", "Condition", "ConditionBelief"), backend = "emmeans")  |>
-        filter(Relevance == "Relevant") |>
-        select(-Relevance) |>
-        mutate(Sample = "Study 1")|>
-      as.data.frame(), 
-      modelbased::estimate_means(model2, by = c("Gender","Condition", "ConditionBelief"), backend = "emmeans")|>
-        mutate(Sample = "Study 2") |>
-        as.data.frame())
-
-    plt <- pred_df |>
-      ggplot(aes(x = ConditionBelief,y = Proportion, color = Condition,linetype = Sample, group = interaction(Sample, Condition))) +
-      geom_line(size = 1) +
-      geom_point(size = 2) +
-      geom_errorbar(aes(ymin = CI_low, ymax = CI_high),width = 0.1) +
-      facet_wrap(~ Gender) +
-      scale_color_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
-      theme_minimal(base_size = 14) +
-        labs(x = "Whether the original labels were believed to be true",y = "Estimated Proportion",color = "Images presented as:",linetype = "Sample", title = "Enticement") +
-      theme(
-            axis.text.y = element_text(size = 8),
-            strip.placement = "outside",
-            strip.background.x = element_rect(fill=c("lightgrey"), color=NA),
-            strip.text.x = element_text(size = 10),
-            strip.text.y = element_text(size = 10),
-            axis.text.x = element_text(face = "bold", size=9, color="black"),
-            legend.text = element_text(size = 10),
-            legend.position =  )
-
-    return(plt)
-}
-
-```
+::: {.panel-tabset}
 
@@
 arousal2 <- readRDS("models/ModelArousal_2.rds")
+
+tbl_a1 <- tbl_results(arousal1, title = "Fixed Effects: Arousal Study 1")
+tbl_a1
 ```
@@
 ```{r}
-
-tbl_a1 <- tbl_results(arousal1, title = "Fixed Effects: Arousal Study 1")
 tbl_a2 <- tbl_results(arousal2, title = "Fixed Effects: Arousal Study 2")
-
+tbl_a2
 ```
@@
 ```{r}
-
-plt_a <- make_model_plot(arousal1, arousal2,
-                title = "Arousal for Relevant Stimuli")
+plta <- make_combined_plot(arousal1, arousal2, title = "Arousal Estimates for All Stimuli")
 ```
@@
 enticement2 <- readRDS("models/ModelEnticement_2.rds")
+
+tbl_e1 <- tbl_results(enticement1, title = "Fixed Effects: Enticement Study 1")
+tbl_e1
 ```
@@
 ```{r}
-
-tbl_e1 <- tbl_results(enticement1, title = "Fixed Effects: Enticement Study 1")
 tbl_e2 <- tbl_results(enticement2, title = "Fixed Effects: Enticement Study 2")
-
+tbl_e2
 ```
@@
 ```{r}
-
-plt_e <- make_model_plot(enticement1, enticement2,
-                title = "Enticement for Relevant Stimuli")
+plt_e <- make_combined_plot(enticement1, enticement2, title = "Enticement Estimates for All Stimuli")
+plt_e
 ```
@@
 valence2 <- readRDS("models/ModelValence_2.rds")
+
+tbl_v1 <- tbl_results(valence1, title = "Fixed Effects: Valence Study 1")
+tbl_v1
 ```
@@
 ```{r}
-
-tbl_v1 <- tbl_results(valence1, title = "Fixed Effects: Valence Study 1")
 tbl_v2 <- tbl_results(valence2, title = "Fixed Effects: Valence Study 2")
-
+tbl_v2
 ```
@@
 ```{r}
+plt_v <- make_combined_plot(valence1, valence2, title = "Valence Estimates for All Stimuli")
+plt_v
+```
 
-plt_v <- make_model_plot(valence1, valence2,
-                title = "Valence for Relevant Stimuli")
-```
+:::
 
@@
 
-#### Arousal
-```{r}
-table_dvour <- function(g) {
-  performance::performance_dvour(g) |> 
-    arrange(desc(D_vour)) |> 
-    gt::gt() |> 
-    gt::data_color("D_vour", palette = c("red", "red", "orange", "yellow", "green"), domain = c(0, 1)) |> 
-    gt::fmt_auto()
-}
-
-a1 <- modelbased::estimate_grouplevel(arousal1)
-table_dvour(a1)
-
-a2 <- modelbased::estimate_grouplevel(arousal2)
-table_dvour(a2)
-
-```
-
 ### Participant effects
-
-```{r}
-plot_grouplevel_effects <- function(model, outcome_name = NULL) {
-
-  # Colors
-  colors <- c("Participant" = "#9C27B0", "Item" = "#FF9800")
-
-  # Plot
-  p <- ggplot(model, aes(x = Median, y = Level)) +
-    geom_pointrange(aes(xmin = CI_low, xmax = CI_high, color = Group), size = 0.3) +
-    ggside::geom_xsidedensity(aes(group = Group, fill = Group), color = NA, alpha = 0.3) +
-    scale_color_manual(values = colors) +
-    scale_fill_manual(values = colors) +
-    theme_minimal() +
-    theme(
-      axis.text.y = element_blank(),
-      axis.ticks.y = element_blank(),
-      axis.title.x = element_text(size = 12),
-      axis.title.y = element_blank(),
-      panel.grid.minor = element_blank(),
-      panel.grid.major.y = element_blank(),
-      legend.position = "bottom"
-    ) +
-    labs(
-      x = ifelse(is.null(outcome_name), "Random intercept (participant/item)", paste0(outcome_name, " random intercept")),
-      y = "",
-      color = "Group",
-      fill = "Group"
-    )
-
-  return(p)
-}
-
-plot_grouplevel_effects(a1, outcome_name = "Arousal")
-
-```

### 2025-09-02 analysis/analysis.qmd
updated script

@@
         width = 300)
+
+results_table <- function(model, effects="fixed", filter=NULL) {
+  if("marginaleffects" %in% class(model)) {
+    model |> 
+      parameters::parameters() |> 
+      as.data.frame() |> 
+      select(-Parameter, -SE, -S, z=Statistic) |> 
+      insight::format_table() |> 
+      parameters::display()
+  } else {
+    display(parameters::parameters(model, effects=effects, keep=filter))
+  }
+}
 
@@
   mutate(StimuliType = fct_relevel(StimuliType, "Individual", "Couple"))
-```
-
-```{r}
-
-tbl_results <-   function(model1, title_table = "Fixed Effects: Study 1"){
-
-  # ---- Fixed effects table ----
-  tbl <- parameters::parameters(model1, effects = "fixed") |>
-    as.data.frame() |>
-    select(-Effects, -df_error, -CI) |>
-    gt() |>
-    # tab_header(title = title_table, subtitle = subtitle_table) |>
-    fmt_number(columns = c("Coefficient", "SE", "CI_low", "CI_high", "z", "p"), decimals = 2) |>
-    cols_label(
-      Parameter = "Predictor",
-      Coefficient = "β",
-      SE = "SE",
-      CI_low = "CI (lower)",
-      CI_high = "CI (upper)",
-      z = "z-value",
-      p = "p"
-    ) |>
-    cols_merge(columns = c("CI_low", "CI_high"), pattern = "{1}, {2}") |>
-    cols_label(`CI_low` = "95% CI") |>
-    tab_style(
-      style = cell_text(weight = "bold"),
-      locations = cells_column_labels(everything())
-    ) |>
-    opt_table_lines()
-
-    return(tbl)
-}
-
-make_combined_plot <- function(model1, model2 = NULL, 
-                               title = "Estimated Marginal Means") {
-
-  df1 <- modelbased::estimate_means(
-    model1, by = c("Gender", "Relevance", "Condition", "ConditionBelief"),backend = "emmeans") |>
-    dplyr::mutate(Sample = "Study 1") |>
-    as.data.frame()
-
-  # Study 2: only Relevant
-  if (!is.null(model2)) {
-    df2 <- modelbased::estimate_means(
-      model2, by = c("Gender", "Condition", "ConditionBelief"), backend = "emmeans") |>
-      dplyr::mutate(Relevance = "Relevant", Sample = "Study 2") |>
-      as.data.frame()
-    pred_df <- rbind(df1, df2)
-  } else {
-    pred_df <- df1
-  }
-
-  plt <- pred_df |>
-    ggplot(aes(x = ConditionBelief, y = Proportion,color = Condition, linetype = Sample, group = interaction(Sample, Condition)
-    )) +
-    geom_hline(yintercept = 0, color = "darkgrey") +
-    geom_line(size = 1) +
-    geom_point(size = 2) +
-    geom_errorbar(aes(ymin = CI_low, ymax = CI_high), width = 0.1) +
-    facet_grid(Relevance ~ Gender, switch = "y") +
-    scale_color_manual(values = c("AI-Generated" = "#2196F3","Photograph" = "#F44336")) +
-    theme_minimal(base_size = 14) +
-    labs(title = title, x= "Whether the original labels were believed to be true",color = "Images presented as:", linetype = "Sample"
-    ) +
-    theme(
-      axis.title.y = element_blank(),
-      axis.text.y = element_text(size = 8),
-      strip.placement = "outside",
-      strip.background.x = element_rect(fill = "lightgrey", color = NA),
-      strip.text.x = element_text(size = 10),
-      strip.text.y = element_text(size = 10),
-      axis.text.x = element_text(face = "bold", size = 9, color = "black"),
-      legend.text = element_text(size = 10),
-      legend.position = "bottom"
-    )
-
-  plt
-}
-
 ```
@@
 arousal2 <- readRDS("models/ModelArousal_2.rds")
-
-tbl_a1 <- tbl_results(arousal1, title = "Fixed Effects: Arousal Study 1")
-tbl_a1
 ```
@@
 ```{r}
-tbl_a2 <- tbl_results(arousal2, title = "Fixed Effects: Arousal Study 2")
-tbl_a2
+results_table(arousal1)
 ```
@@
 ```{r}
+results_table(arousal2)
+
+```
+
+```{r}
+#| fig-height: 8
+#| fig-width: 8
+
+make_combined_plot <- function(model1, model2 = NULL, 
+                               title = "Estimated Marginal Means") {
+
+  df1 <- modelbased::estimate_means(
+    model1, by = c("Gender", "Relevance", "Condition", "ConditionBelief"),backend = "emmeans") |>
+    dplyr::mutate(Sample = "Study 1") |>
+    as.data.frame()
+
+  # Study 2: only Relevant
+  if (!is.null(model2)) {
+    df2 <- modelbased::estimate_means(
+      model2, by = c("Gender", "Condition", "ConditionBelief"), backend = "emmeans") |>
+      dplyr::mutate(Relevance = "Relevant", Sample = "Study 2") |>
+      as.data.frame()
+    pred_df <- rbind(df1, df2)
+  } else {
+    pred_df <- df1
+  }
+
+  plt <- pred_df |>
+    ggplot(aes(x = ConditionBelief, y = Proportion,color = Condition, linetype = Sample, group = interaction(Sample, Condition)
+    )) +
+    geom_hline(yintercept = 0, color = "darkgrey") +
+    geom_line(linewidth = 1) +
+    geom_point(size = 2) +
+    geom_errorbar(aes(ymin = CI_low, ymax = CI_high), width = 0.1) +
+    facet_grid(Relevance ~ Gender, switch = "y") +
+    scale_color_manual(values = c("AI-Generated" = "#2196F3","Photograph" = "#F44336")) +
+    theme_minimal(base_size = 14) +
+    labs(title = title, x= "Whether the original labels were believed to be true",color = "Images presented as:", linetype = "Sample"
+    ) +
+    theme(
+      axis.title.y = element_blank(),
+      axis.text.y = element_text(size = 8),
+      strip.placement = "outside",
+      strip.background.x = element_rect(fill = "lightgrey", color = NA),
+      strip.text.x = element_text(size = 10),
+      strip.text.y = element_text(size = 10),
+      axis.text.x = element_text(face = "bold", size = 9, color = "black"),
+      legend.text = element_text(size = 10),
+      legend.position = "bottom")
+
+  plt
+}
+
 plta <- make_combined_plot(arousal1, arousal2, title = "Arousal Estimates for All Stimuli")
+
+plta
 ```
@@
 enticement2 <- readRDS("models/ModelEnticement_2.rds")
-
-tbl_e1 <- tbl_results(enticement1, title = "Fixed Effects: Enticement Study 1")
-tbl_e1
 ```
@@
 ```{r}
-tbl_e2 <- tbl_results(enticement2, title = "Fixed Effects: Enticement Study 2")
-tbl_e2
+results_table(enticement1)
 ```
@@
 ```{r}
+results_table(enticement2)
+```
+
+```{r}
+#| fig-height: 8
+#| fig-width: 8
+
 plt_e <- make_combined_plot(enticement1, enticement2, title = "Enticement Estimates for All Stimuli")
@@
 valence2 <- readRDS("models/ModelValence_2.rds")
-
-tbl_v1 <- tbl_results(valence1, title = "Fixed Effects: Valence Study 1")
-tbl_v1
 ```
@@
 ```{r}
-tbl_v2 <- tbl_results(valence2, title = "Fixed Effects: Valence Study 2")
-tbl_v2
+results_table(valence1)
 ```
@@
 ```{r}
+results_table(valence2)
+```
+
+```{r}
+#| fig-height: 8
+#| fig-width: 8
+
 plt_v <- make_combined_plot(valence1, valence2, title = "Valence Estimates for All Stimuli")
@@
 
+::: {.panel-tabset}
+
 ### Random Effects
 
+```{r}
+
+table_dvour <- function(g) {
+  performance::performance_dvour(g) |> 
+    arrange(desc(D_vour)) |> 
+    gt::gt() |> 
+    gt::data_color("D_vour", palette = "green", domain = c(0, 1)) |> 
+    gt::fmt_auto()
+}
+
+g1 <- modelbased::estimate_grouplevel(arousal1)
+table_dvour(g1)
+
+```
+
+```{r}
+g2 <- modelbased::estimate_grouplevel(arousal2)
+table_dvour(g2)
+```
+
 ### Participant effects
+
+:::

### 2025-09-02 paper/manuscript.qmd
started fiction ero manuscript

@@
 ---
-title: ""
+title: "The Effect of Fictional Reappraisal on Subjective Ratings Toward Images"
 shorttitle: "FicitionEro"
@@
     roles:
+      - Project administration
+      - Data curation
+      - Formal Analysis
+      - Investigation
+      - Visualization
+      - Writing – original draft
+      - Writing – review & editing
     affiliations:
@@
     roles:
-      - Project administration
       - Data curation
@@
         department: "School of Psychology"
-        city: "Brighton"
-        country: "UK"
-        postal-code: "BN1 9RH"
 # author-note:
@@
     # Can be jou (journal), man (manuscript), stu (student), or doc (document)
-    documentmode: man
+    documentmode: jou
     include-in-header:
@@
 ```{r}
-#| message: false
 #| warning: false
+#| label: "fig-paradigm1"
+#| apa-twocolumn: true  # A Figure Spanning Two Columns When in Journal Mode
+#| out-width: "100%"
+#| fig-cap: "Paradigm 2"
 
@@
 Importantly, they were informed that all images were real photographs, and that the “AI-generated” label was used solely to test the effect of belief on affective reactions.
-A shareable link to the experiment was also provided.
+A shareable link to the experiment was also provided [see @fig-paradigm1].
 
@@
 ```{r}
-#| message: false
 #| warning: false
+#| label: "fig-paradigm2"
+#| apa-twocolumn: true  # A Figure Spanning Two Columns When in Journal Mode
+#| out-width: "100%"
+#| fig-cap: "Paradigm 2"
 
-knitr::include_graphics("images/Paradigm1.png")
+knitr::include_graphics("images/Paradigm2.png")
 ```
 
+see @fig-paradigm2
+
 ### Data Analysis
+
+# References
+
+<!-- References will auto-populate in the refs div below -->
+
+::: {#refs}
+:::

### 2025-09-02 paper/manuscript.qmd
updated manuscript
participants,  materials and procedure for study 1 and study 2 completed

@@
 
-The final sample consisted of 705 participants (Mean = 30.2 years $\pm$ 11.8, 35.7% Female).
+The final sample consisted of 705 participants (Mean age = 30.2 years $\pm$ 11.8; 35.7% female).
 Participants were primarily from the United Kingdom (28.23%), Italy (18.72%), the United States (14.33%), and Colombia (11.06%), with the remaining 27.66% distributed across other countries.
-
 Ethical approval for this study was obtained from the School of Psychology Ethics Committee at the University of Sussex (ER/MHHE20/1).
@@
 
-All written materials in this study were translated into the participants native tongue languages: English, Italian, French, Spanish.
+All written materials in this study were translated into the participants’ native languages: English, Italian, French, and Spanish.
 
@@
 
-The Beliefs about Artificial Image Technology (BAIT) assesses general attitudes toward artificial intelligence (AI) and beliefs about AI-generated media.
-It includes six items adapted from the General Attitudes towards Artificial Intelligence Scale [GAAIS, @schepman2020initial; @schepman2023general] comprising three positively valenced (e.g., “Artificial Intelligence is exciting”) and three negatively valenced items (e.g., “Artificial Intelligence might take control of people”).
+The Beliefs about Artificial Image Technology (BAIT) scale assesses general attitudes toward artificial intelligence (AI) and beliefs about AI-generated media.
+It includes six items adapted from the General Attitudes towards Artificial Intelligence Scale [GAAIS, @schepman2020initial; @schepman2023general], comprising three positively valenced (e.g., “Artificial Intelligence is exciting”) and three negatively valenced items (e.g., “Artificial Intelligence might take control of people”).
 In addition, several items were developed to evaluate beliefs about computer-generated imagery, such as “Current Artificial Intelligence algorithms can generate very realistic images” and “Images of faces or people generated by Artificial Intelligence always contain errors and artifacts.” All items were rated on a continuous scale from strongly disagree (0) to strongly agree (1).
@@
 
-Consumption of Pornography Scale – General [COPS; @hatch2023consumption] is a 34-item measure of pornography use across four dimensions: frequency, duration, accidental exposure, and deliberate exposure.
-In the current study, a subset of items from the frequency and duration subscales was used.
-Participants reported how often they had viewed pornography in the past 30 days (e.g., not at all, once or twice, weekly, daily, multiple times per day), and the typical duration of viewing sessions (less than 5 minutes to 46+ minutes).
+The Consumption of Pornography Scale – General [COPS, @hatch2023consumption] is a 34-itemmeasure assessing pornography use across multiple dimensions, including frequency, duration and recency of sexual activity.
+Participants reported how often they had viewed pornography in the past 30 days (e.g., not at all, once or twice, weekly, daily, multiple times per day) and the typical duration of viewing sessions (less than 5 minutes to 46+ minutes).
 An additional item assessed the recency of any sexual activity, with response options ranging from within the past 24 hours to more than a year ago.
@@
 
-**Arousal**.
+#### Arousal
+
 Subjective sexual arousal was assessed following each image with the question, “How much did you feel sexually aroused?” Responses were recorded on a continuous scale from Not at all (0) to Very much (1).
 
-**Enticement**. Perceived enticement was measured after each image using the question, “How enticing would you rate this image to be?” with the same scale ranging from Not at all (0) to Very much (1).
+#### Enticement
 
-**Valence**. Emotional valence was evaluated by asking, “The feeling evoked by the image was...” rated on a scale from Unpleasant (-1) to Pleasant (1).
+Perceived enticement was measured after each image using the question, “How enticing would you rate this image to be?” with the same scale ranging from Not at all (0) to Very much (1).
 
-**Perceived Realism**.
+#### Valence
+
+Emotional valence was evaluated by asking, “The feeling evoked by the image was...” rated on a scale from Unpleasant (-1) to Pleasant (1).
+
+#### Realism
+
 In a final stage of the experiment, each image was shown again, and participants rated its perceived realism with the question, “How realistic was this image?” using a continuous scale anchored at AI-generated (0) and Photograph (1).
+
+#### Feedback
 
@@
 Anonymized data, together with all preprocessing and analysis scripts, will be openly released on GitHub to facilitate complete reproducibility.
-
 Participants first provided informed consent before completing a short demographic questionnaire covering gender, age, ethnicity, country of residence, education, and English proficiency.
@@
 
+<!-- EYE-tracking data? -->
+
 In the first phase, participants were told that the study aimed to validate a new image-generation algorithm.
-They were informed that they would see images allegedly produced by this algorithm intermixed with real photographs, each preceded by a cue indicating whether the upcoming image was of an “AI-generated” or “Photograph" origin.
+They were informed that they would see images allegedly produced by this algorithm intermixed with real photographs, each preceded by a cue indicating whether the upcoming image was of an “AI-generated” or “Photograph” origin.
 Their task was to rate each image on arousal, enticement, and valence.
-
-Each participant viewed 60 images in total: 40 erotic images (20 male and 20 female) from the Erotic subset of the Nencki Affective Picture System [NAPS ERO; @wierzba2015erotic], and 20 additional images (10 neutral, 10 positively arousing) from the original NAPS database [@marchewka2014nencki].
+Each participant viewed 60 images in total: 40 erotic images (20 male and 20 female) from the Erotic subset of the Nencki Affective Picture System [NAPS ERO, @wierzba2015erotic], and 20 additional images (10 neutral, 10 positively arousing) from the original NAPS database [@marchewka2014nencki].
 Each trial followed a fixed timing sequence: a fixation cross (750 ms), a color-coded textual cue (1,250 ms), another fixation cross (500 ms), then the image (2,500 ms).
@@
 This phase was self-paced, with responses required before continuing.
-
 After completing the image-rating phase, participants filled out two self-report questionnaires: first the BAIT scale, followed by the COPS questionnaire.
-
-<!-- Thanks a lot. In the next phase, we would like to see if you found our <b>image generation algorithm convincing</b> and error-free. -->
-
-<!-- We will briefly present you <b>all the images</b> one last time (the AI-generated ones, as well as the photos), and you will have to rate them on how <b>real</b> (how realistic, photography-like) the image is.
--->
 
@@
 They were asked whether they could distinguish AI-generated from real images, whether AI images appeared more or less arousing, whether cue labels seemed accurate or reversed, and whether specific images stood out as particularly arousing or unarousing.
-
 Finally, participants were debriefed on the true purpose of the study: to examine how image labels (AI-generated vs.
@@
 Importantly, they were informed that all images were real photographs, and that the “AI-generated” label was used solely to test the effect of belief on affective reactions.
-A shareable link to the experiment was also provided [see @fig-paradigm1].
+A shareable link to the experiment was also provided.
 
@@
 
-The initial sample comprised of 279 participants recruited via Prolific\textcopyright.
+The initial sample comprised 279 participants recruited via Prolific\textcopyright.
+Inclusion criteria required participants to be native English speakers or residents of countries with high levels of English proficiency.
 Participant exclusions were applied as follows: five participants were removed for showing no variability in arousal ratings (i.e., they did not move the response scales).
@@
 The final sample consisted of 261 participants (Mean = 37.4 $\pm$ 12.7, 48.7% Female).
-%4.12% of participants were from the United Kingdom, 26.52% from South Africa, 11.47% from the United States and the remaining 7.89% distributed across other countries.
+56.32% of participants were from the United Kingdom, 26.82% from South Africa, 10.34% from the United States, and the remaining 6.51% were from other countries.
 
@@
 ### Materials
+
+#### Questionnaires
+
+The questionnaires used in Study 2 were largely the same as those in Study 1, with minor modifications.
+In the BAIT, two items, assessing beliefs that AI might take control of people and interest in using AI systems in daily life, were removed.
+Additionally, the wording was streamlined by replacing “Artificial Intelligence” with “AI” throughout the scale.
+In the COPS, the item assessing the typical duration of pornography viewing sessions was omitted, retaining only items measuring frequency of pornography viewing and recency of sexual activity.
+
+#### Affective Measures
+
+#### Arousal
+Subjective sexual arousal was assessed following each image with the question, “How much did you feel sexually aroused?” Responses were recorded on 6-point Likert scale from Not at all (0) to Very much (6).
+
+#### Enticement
+Perceived enticement was measured after each image using the question, “How enticing would you rate this image to be?” with the same scale ranging from 6-point Likert scale from Not at all (0) to Very much (6).
+
+#### Valence
+Emotional valence was evaluated by asking, “The feeling evoked by the image was...” rated on a scale from Unpleasant (0) to Pleasant (6).
+
+#### Reality
+In a final stage of the experiment, each image was shown again, and participants rated on the images authenticity with the question, “I think this face is...Indicate your confidence that the image is fake or real” using a continuous scale anchored at AI-generated (-3) and Photograph (3).
+
+#### Feedback
 
@@
 
-see @fig-paradigm2
+Consistent with Study 1, Study 2 was conducted in jsPsych following born-open principles [@de2024datapipe; @de2015jspsych].Participants first provided informed consent, being informed that they could withdraw at any time; however, once the experiment was completed, withdrawal was not possible because the data were anonymized prior to storage.
+They then completed the same demographic questions as in Study 1, with the exception of items regarding birth control use.
+
+<!-- EYE-tracking data? -->
+
+In the first phase, participants were informed that the researchers were collaborating with a young AI start-up based in Brighton, intended to enhance the believability of the study.
+Participants were told that they would view images generated by this algorithm intermixed with “real” photographs, each preceded by a label indicating whether the image was AI-generated or a photograph.
+They were asked to rate each image on sexual arousal, enticement, and valence.
+A total of 50 images were presented, drawn from two categories of the NAPS-ERO database (25 images of couples and 25 images of individuals).
+
+Images were assigned to be relevant to participants’ self-reported gender and sexual orientation; for example, male participants identifying as homosexual viewed male individuals and male couples.
+Each trial followed a fixed timing sequence: a fixation cross (500 ms), a color-coded textual cue displayed for 1,000 ms, a second fixation cross (500 ms), and then the image presented for 2,000 ms.
+Cue colors were the same as in Study 1 and were randomly assigned across trials.
+Participants identifying as other in gender or bisexual/other in sexual orientation were asked which type of images they preferred, with options including “Women (and heterosexual couples),” “Men (and heterosexual couples),” “Only women (and lesbian couples),” and “Only men (and gay couples).”
+
+Midway through the 50 images, participants were provided with a break and instructed to continue when ready.
+At this point, they completed a brief feedback survey assessing their subjective impressions of the images and AI-generation labels.
+This survey asked whether certain images were particularly arousing, whether AI-generated images were more or less arousing than the photographs, and participants’ perceptions of the AI-generation algorithm.
+Specifically, they indicated whether differences between AI-generated and real images were obvious or subtle, whether they perceived inconsistencies or reversals in labeling (“Photograph” vs.
+“AI-Generated”), and whether they believed all images were either photos or AI-generated.
+If participants indicated that all images were real or AI-generated, they rated their confidence on a scale from “Not at all” to “Completely certain.” This feedback captured participants’ explicit beliefs and subjective reactions regarding both the content and labeling of the images.Following the first phase, participants completed the BAIT and COPS questionnaires.
+
+In the second phase, participants were informed that some images had been intentionally mislabeled and were asked to judge whether each image was AI-generated or a real photograph, expressing their confidence at the extremes of the scale.
+The timing procedure in this phase was identical to Study 1.
+After each image, participants provided general feedback regarding their experience and any additional comments.
+Finally, participants were presented with a debrief page informing them that all images were, in fact, real photographs (see @fig-paradigm2).
 

### 2025-09-02 paper/manuscript.tex
updated manuscript
participants,  materials and procedure for study 1 and study 2 completed

\documentclass[
  jou,
  floatsintext,
  longtable,
  nolmodern,
  notxfonts,
  notimes,
  colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{apa7}

\usepackage{amsmath}
\usepackage{amssymb}

\usepackage[bidi=default]{babel}
\babelprovide[main,import]{english}

% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}

\RequirePackage{longtable}
\RequirePackage{threeparttablex}

\makeatletter
\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
	{0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
	{-.5em}%
	{\normalfont\normalsize\bfseries\typesectitle}}

\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{0.5em}%
	{0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
	{-\z@\relax}%
	{\normalfont\normalsize\bfseries\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
\makeatother

\usepackage{longtable, booktabs, multirow, multicol, colortbl, hhline, caption, array, float, xpatch}
\setcounter{topnumber}{2}
\setcounter{bottomnumber}{2}
\setcounter{totalnumber}{4}
\renewcommand{\topfraction}{0.85}
\renewcommand{\bottomfraction}{0.85}
\renewcommand{\textfraction}{0.15}
\renewcommand{\floatpagefraction}{0.7}

\usepackage{tcolorbox}
\tcbuselibrary{listings,theorems, breakable, skins}
\usepackage{fontawesome5}

\definecolor{quarto-callout-color}{HTML}{909090}
\definecolor{quarto-callout-note-color}{HTML}{0758E5}
\definecolor{quarto-callout-important-color}{HTML}{CC1914}
\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
\definecolor{quarto-callout-tip-color}{HTML}{00A047}
\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
\definecolor{quarto-callout-color-frame}{HTML}{ACACAC}
\definecolor{quarto-callout-note-color-frame}{HTML}{4582EC}
\definecolor{quarto-callout-important-color-frame}{HTML}{D9534F}
\definecolor{quarto-callout-warning-color-frame}{HTML}{F0AD4E}
\definecolor{quarto-callout-tip-color-frame}{HTML}{02B875}
\definecolor{quarto-callout-caution-color-frame}{HTML}{FD7E14}

%\newlength\Oldarrayrulewidth
%\newlength\Oldtabcolsep

\usepackage{hyperref}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}

\usepackage{graphicx}
\makeatletter
\newsavebox\pandoc@box
\newcommand*\pandocbounded[1]{% scales image to fit in text height/width
  \sbox\pandoc@box{#1}%
  \Gscale@div\@tempa{\textheight}{\dimexpr\ht\pandoc@box+\dp\pandoc@box\relax}%
  \Gscale@div\@tempb{\linewidth}{\wd\pandoc@box}%
  \ifdim\@tempb\p@<\@tempa\p@\let\@tempa\@tempb\fi% select the smaller of both
  \ifdim\@tempa\p@<\p@\scalebox{\@tempa}{\usebox\pandoc@box}%
  \else\usebox{\pandoc@box}%
  \fi%
}
% Set default figure placement to htbp
\def\fps@figure{htbp}
\makeatother

% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
\makeatletter
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}
  \fi
  % set entry spacing
  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{\hfill\break\parbox[t]{\linewidth}{\strut\ignorespaces#1\strut}}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage[nolongtablepatch]{lineno}
\linenumbers

\usepackage{newtx}

\defaultfontfeatures{Scale=MatchLowercase}
\defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}

\title{The Effect of Fictional Reappraisal on Subjective Ratings Toward
Images}

\shorttitle{FicitionEro}

\usepackage{etoolbox}

\authorsnames[{2,1},{2}]{Dominique Makowski,Ana Neves}

\authorsaffiliations{
{Sussex Centre for Consciousness Science, University of Sussex},{School
of Psychology, University of Sussex}}

\leftheader{Makowski and Neves}

\abstract{Blabla the abstract blabla.}

\keywords{keyword1, keyword2, keyword3}

\authornote{\par{\addORCIDlink{Dominique
Makowski}{0000-0001-5375-9967}}\par{\addORCIDlink{Ana
Neves}{0009-0006-0020-7599}}

\par{     \begin{tcolorbox}[enhanced jigsaw, arc=.35mm, opacityback=0, colback=white, breakable, left=2mm, leftrule=.75mm, rightrule=.15mm, colframe=quarto-callout-note-color-frame, toprule=.15mm, bottomrule=.15mm]

\end{tcolorbox}

This preprint is a non-peer-reviewed work from the
\href{https://realitybending.github.io/}{\textbf{Reality Bending Lab}}.
\begin{center}
\includegraphics[width=0.2\linewidth,height=\textheight,keepaspectratio]{manuscript_files/mediabag/ReBeL_LogoOnly_hu114.png}
\end{center}  Author roles were classified using the Contributor Role Taxonomy (CRediT; https://credit.niso.org/) as follows: Dominique
Makowski:   Project administration, Data curation, Formal
Analysis, Investigation, Visualization, Writing -- original
draft, Writing -- review \& editing; Ana Neves:   Data curation, Formal
Analysis, Investigation, Visualization, Writing -- original
draft, Writing -- review \& editing}
\par{Correspondence concerning this article should be addressed
to Dominique Makowski, Email: D.Makowski@sussex.ac.uk}
}

\usepackage{pbalance} 
\usepackage{float}
\makeatletter
\let\oldtpt\ThreePartTable
\let\endoldtpt\endThreePartTable
\def\ThreePartTable{\@ifnextchar[\ThreePartTable@i \ThreePartTable@ii}
\def\ThreePartTable@i[#1]{\begin{figure}[!htbp]
\onecolumn
\begin{minipage}{0.5\textwidth}
\oldtpt[#1]
}
\def\ThreePartTable@ii{\begin{figure}[!htbp]
\onecolumn
\begin{minipage}{0.5\textwidth}
\oldtpt
}
\def\endThreePartTable{
\endoldtpt
\end{minipage}
\twocolumn
\end{figure}}
\makeatother

\makeatletter
\let\endoldlt\endlongtable		
\def\endlongtable{
\hline
\endoldlt}
\makeatother

\newenvironment{twocolumntable}% environment name
{% begin code
\begin{table*}[!htbp]%
\onecolumn%
}%
{%
\twocolumn%
\end{table*}%
}% end code

\urlstyle{same}

\usepackage{lscape}
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\@ifpackageloaded{fontawesome5}{}{\usepackage{fontawesome5}}
\definecolor{quarto-callout-color}{HTML}{909090}
\definecolor{quarto-callout-note-color}{HTML}{0758E5}
\definecolor{quarto-callout-important-color}{HTML}{CC1914}
\definecolor{quarto-callout-warning-color}{HTML}{EB9113}
\definecolor{quarto-callout-tip-color}{HTML}{00A047}
\definecolor{quarto-callout-caution-color}{HTML}{FC5300}
\definecolor{quarto-callout-color-frame}{HTML}{acacac}
\definecolor{quarto-callout-note-color-frame}{HTML}{4582ec}
\definecolor{quarto-callout-important-color-frame}{HTML}{d9534f}
\definecolor{quarto-callout-warning-color-frame}{HTML}{f0ad4e}
\definecolor{quarto-callout-tip-color-frame}{HTML}{02b875}
\definecolor{quarto-callout-caution-color-frame}{HTML}{fd7e14}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother

% From https://tex.stackexchange.com/a/645996/211326
%%% apa7 doesn't want to add appendix section titles in the toc
%%% let's make it do it
\makeatletter
\xpatchcmd{\appendix}
  {\par}
  {\addcontentsline{toc}{section}{\@currentlabelname}\par}
  {}{}
\makeatother

%% Disable longtable counter
%% https://tex.stackexchange.com/a/248395/211326

\usepackage{etoolbox}

\makeatletter
\patchcmd{\LT@caption}
  {\bgroup}
  {\bgroup\global\LTpatch@captiontrue}
  {}{}
\patchcmd{\longtable}
  {\par}
  {\par\global\LTpatch@captionfalse}
  {}{}
\apptocmd{\endlongtable}
  {\ifLTpatch@caption\else\addtocounter{table}{-1}\fi}
  {}{}
\newif\ifLTpatch@caption
\makeatother

\begin{document}

\maketitle

\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\setlength\LTleft{0pt}

\resetlinenumber[1]

\section{Study 1}\label{study-1}

\subsection{Methods}\label{methods}

\textbf{Participants}

The initial sample comprised 1,067 participants recruited via multiple
channels, including Prolific\textcopyright, Sona (ref), social media
platforms, university classrooms, and snowball sampling. This strategy
yielded a heterogeneous pool of both incentivised and non-incentivised
individuals, including students and members of the general population
from England, France, Italy, Colombia, and Spain.

To ensure data quality, several exclusion criteria were applied.
Participants were removed if they (a) showed no variation in arousal
ratings across trials (N = 8), (b) displayed a negative correlation
between arousal and enticement alongside lower arousal ratings for
erotic compared to neutral stimuli, suggesting a possible
misunderstanding of scale direction (N = 4), or (c) self-identified with
a gender or sexual orientation incompatible with the aims of the
analysis (N = 350). For the latter, only self-reported heterosexual
individuals were retained.

The final sample consisted of 705 participants (Mean age = 30.2 years
\(\pm\) 11.8; 35.7\% female). Participants were primarily from the
United Kingdom (28.23\%), Italy (18.72\%), the United States (14.33\%),
and Colombia (11.06\%), with the remaining 27.66\% distributed across
other countries. Ethical approval for this study was obtained from the
School of Psychology Ethics Committee at the University of Sussex
(ER/MHHE20/1).

\subsubsection{Materials}\label{materials}

All written materials in this study were translated into the
participants' native languages: English, Italian, French, and Spanish.

\paragraph{Questionnaires.}\label{questionnaires}

The Beliefs about Artificial Image Technology (BAIT) scale assesses
general attitudes toward artificial intelligence (AI) and beliefs about
AI-generated media. It includes six items adapted from the General
Attitudes towards Artificial Intelligence Scale (GAAIS,
\citeproc{ref-schepman2020initial}{Schepman \& Rodway, 2020},
\citeproc{ref-schepman2023general}{2023}), comprising three positively
valenced (e.g., ``Artificial Intelligence is exciting'') and three
negatively valenced items (e.g., ``Artificial Intelligence might take
control of people''). In addition, several items were developed to
evaluate beliefs about computer-generated imagery, such as ``Current
Artificial Intelligence algorithms can generate very realistic images''
and ``Images of faces or people generated by Artificial Intelligence
always contain errors and artifacts.'' All items were rated on a
continuous scale from strongly disagree (0) to strongly agree (1). One
item was included to assess self-reported AI knowledge, with anchors
ranging from Not at all (0) to Expert (6).

The Consumption of Pornography Scale -- General (COPS,
\citeproc{ref-hatch2023consumption}{Hatch et al., 2023}) is a
34-itemmeasure assessing pornography use across multiple dimensions,
including frequency, duration and recency of sexual activity.
Participants reported how often they had viewed pornography in the past
30 days (e.g., not at all, once or twice, weekly, daily, multiple times
per day) and the typical duration of viewing sessions (less than 5
minutes to 46+ minutes). An additional item assessed the recency of any
sexual activity, with response options ranging from within the past 24
hours to more than a year ago.

\paragraph{Affective Measures.}\label{affective-measures}

\paragraph{Arousal.}\label{arousal}

Subjective sexual arousal was assessed following each image with the
question, ``How much did you feel sexually aroused?'' Responses were
recorded on a continuous scale from Not at all (0) to Very much (1).

\paragraph{Enticement.}\label{enticement}

Perceived enticement was measured after each image using the question,
``How enticing would you rate this image to be?'' with the same scale
ranging from Not at all (0) to Very much (1).

\paragraph{Valence.}\label{valence}

Emotional valence was evaluated by asking, ``The feeling evoked by the
image was\ldots{}'' rated on a scale from Unpleasant (-1) to Pleasant
(1).

\paragraph{Realism.}\label{realism}

In a final stage of the experiment, each image was shown again, and
participants rated its perceived realism with the question, ``How
realistic was this image?'' using a continuous scale anchored at
AI-generated (0) and Photograph (1).

\paragraph{Feedback.}\label{feedback}

\textbf{Procedure}

\begin{figure*}[!htbp]

{\caption{{Paradigm 2}{\label{fig-paradigm1}}}}

\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{images/Paradigm1.png}

\end{figure*}

The study was conducted in line with the born-open principle
(\citeproc{ref-de2024datapipe}{Leeuw, 2024}), ensuring transparency and
reproducibility at every stage. The experiment was implemented entirely
in jsPsych (\citeproc{ref-de2015jspsych}{De Leeuw, 2015}), with the full
code hosted publicly on GitHub, which also served as the platform for
running the online study. Raw data were automatically stored in a
private Open Science Framework (OSF) repository. Anonymized data,
together with all preprocessing and analysis scripts, will be openly
released on GitHub to facilitate complete reproducibility. Participants
first provided informed consent before completing a short demographic
questionnaire covering gender, age, ethnicity, country of residence,
education, and English proficiency. Optional questions on birth control
use were also included. They then proceeded to the experimental tasks.

In the first phase, participants were told that the study aimed to
validate a new image-generation algorithm. They were informed that they
would see images allegedly produced by this algorithm intermixed with
real photographs, each preceded by a cue indicating whether the upcoming
image was of an ``AI-generated'' or ``Photograph'' origin. Their task
was to rate each image on arousal, enticement, and valence. Each
participant viewed 60 images in total: 40 erotic images (20 male and 20
female) from the Erotic subset of the Nencki Affective Picture System
(NAPS ERO, \citeproc{ref-wierzba2015erotic}{Wierzba et al., 2015}), and
20 additional images (10 neutral, 10 positively arousing) from the
original NAPS database (\citeproc{ref-marchewka2014nencki}{Marchewka et
al., 2014}). Each trial followed a fixed timing sequence: a fixation
cross (750 ms), a color-coded textual cue (1,250 ms), another fixation
cross (500 ms), then the image (2,500 ms). Cues were presented in red,
green, or blue, with colors randomly assigned across participants.

Following each image, participants rated their emotional response using
three continuous sliders assessing sexual arousal, enticement, and
valence. This phase was self-paced, with responses required before
continuing. After completing the image-rating phase, participants filled
out two self-report questionnaires: first the BAIT scale, followed by
the COPS questionnaire.

In the final phase, participants viewed the same 60 images, presented in
a new randomized order. Each was preceded by a 500 ms fixation cross and
displayed for 1,000 ms. This time, participants rated each image on
perceived realism---how photographic or lifelike it appeared.

At the end of the experiment, participants completed a feedback form.
They were asked whether they could distinguish AI-generated from real
images, whether AI images appeared more or less arousing, whether cue
labels seemed accurate or reversed, and whether specific images stood
out as particularly arousing or unarousing. Finally, participants were
debriefed on the true purpose of the study: to examine how image labels
(AI-generated vs.~real photograph) influence emotional responses.
Importantly, they were informed that all images were real photographs,
and that the ``AI-generated'' label was used solely to test the effect
of belief on affective reactions. A shareable link to the experiment was
also provided.

\textbf{Data Analysis}

\section{Study 2}\label{study-2}

\subsection{Methods}\label{methods-1}

\subsubsection{Participants}\label{participants}

The initial sample comprised 279 participants recruited via
Prolific\textcopyright. Inclusion criteria required participants to be
native English speakers or residents of countries with high levels of
English proficiency. Participant exclusions were applied as follows:
five participants were removed for showing no variability in arousal
ratings (i.e., they did not move the response scales). An additional
five participants were excluded for completing the study on a mobile
device. One participant was excluded due to displaying negative
correlations between arousal and both enticement and valence.
Furthermore, five participants who self-identified as neither female nor
male, and two participants who reported a sexual orientation other than
heterosexual, homosexual, or bisexual, were excluded from further
analyses. Finally, one participant was removed because the stimuli
presented were not relevant to their gender and sexual orientation.

The final sample consisted of 261 participants (Mean = 37.4 \(\pm\)
12.7, 48.7\% Female). 56.32\% of participants were from the United
Kingdom, 26.82\% from South Africa, 10.34\% from the United States, and
the remaining 6.51\% were from other countries.

Ethical approval for this study was obtained from the School of
Psychology Ethics Committee at the University of Sussex (ER/EB672/2).

\subsubsection{Materials}\label{materials-1}

\paragraph{Questionnaires.}\label{questionnaires-1}

The questionnaires used in Study 2 were largely the same as those in
Study 1, with minor modifications. In the BAIT, two items, assessing
beliefs that AI might take control of people and interest in using AI
systems in daily life, were removed. Additionally, the wording was
streamlined by replacing ``Artificial Intelligence'' with ``AI''
throughout the scale. In the COPS, the item assessing the typical
duration of pornography viewing sessions was omitted, retaining only
items measuring frequency of pornography viewing and recency of sexual
activity.

\paragraph{Affective Measures.}\label{affective-measures-1}

\paragraph{Arousal.}\label{arousal-1}

Subjective sexual arousal was assessed following each image with the
question, ``How much did you feel sexually aroused?'' Responses were
recorded on 6-point Likert scale from Not at all (0) to Very much (6).

\paragraph{Enticement.}\label{enticement-1}

Perceived enticement was measured after each image using the question,
``How enticing would you rate this image to be?'' with the same scale
ranging from 6-point Likert scale from Not at all (0) to Very much (6).

\paragraph{Valence.}\label{valence-1}

Emotional valence was evaluated by asking, ``The feeling evoked by the
image was\ldots{}'' rated on a scale from Unpleasant (0) to Pleasant
(6).

\paragraph{Reality.}\label{reality}

In a final stage of the experiment, each image was shown again, and
participants rated on the images authenticity with the question, ``I
think this face is\ldots Indicate your confidence that the image is fake
or real'' using a continuous scale anchored at AI-generated (-3) and
Photograph (3).

\paragraph{Feedback.}\label{feedback-1}

\subsubsection{Procedure}\label{procedure}

\begin{figure*}[!htbp]

{\caption{{Paradigm 2}{\label{fig-paradigm2}}}}

\includegraphics[width=1\linewidth,height=\textheight,keepaspectratio]{images/Paradigm2.png}

\end{figure*}

Consistent with Study 1, Study 2 was conducted in jsPsych following
born-open principles (\citeproc{ref-de2015jspsych}{De Leeuw, 2015};
\citeproc{ref-de2024datapipe}{Leeuw, 2024}).Participants first provided
informed consent, being informed that they could withdraw at any time;
however, once the experiment was completed, withdrawal was not possible
because the data were anonymized prior to storage. They then completed
the same demographic questions as in Study 1, with the exception of
items regarding birth control use.

In the first phase, participants were informed that the researchers were
collaborating with a young AI start-up based in Brighton, intended to
enhance the believability of the study. Participants were told that they
would view images generated by this algorithm intermixed with ``real''
photographs, each preceded by a label indicating whether the image was
AI-generated or a photograph. They were asked to rate each image on
sexual arousal, enticement, and valence. A total of 50 images were
presented, drawn from two categories of the NAPS-ERO database (25 images
of couples and 25 images of individuals).

Images were assigned to be relevant to participants' self-reported
gender and sexual orientation; for example, male participants
identifying as homosexual viewed male individuals and male couples. Each
trial followed a fixed timing sequence: a fixation cross (500 ms), a
color-coded textual cue displayed for 1,000 ms, a second fixation cross
(500 ms), and then the image presented for 2,000 ms. Cue colors were the
same as in Study 1 and were randomly assigned across trials.
Participants identifying as other in gender or bisexual/other in sexual
orientation were asked which type of images they preferred, with options
including ``Women (and heterosexual couples),'' ``Men (and heterosexual
couples),'' ``Only women (and lesbian couples),'' and ``Only men (and
gay couples).''

Midway through the 50 images, participants were provided with a break
and instructed to continue when ready. At this point, they completed a
brief feedback survey assessing their subjective impressions of the
images and AI-generation labels. This survey asked whether certain
images were particularly arousing, whether AI-generated images were more
or less arousing than the photographs, and participants' perceptions of
the AI-generation algorithm. Specifically, they indicated whether
differences between AI-generated and real images were obvious or subtle,
whether they perceived inconsistencies or reversals in labeling
(``Photograph'' vs.~``AI-Generated''), and whether they believed all
images were either photos or AI-generated. If participants indicated
that all images were real or AI-generated, they rated their confidence
on a scale from ``Not at all'' to ``Completely certain.'' This feedback
captured participants' explicit beliefs and subjective reactions
regarding both the content and labeling of the images.Following the
first phase, participants completed the BAIT and COPS questionnaires.

In the second phase, participants were informed that some images had
been intentionally mislabeled and were asked to judge whether each image
was AI-generated or a real photograph, expressing their confidence at
the extremes of the scale. The timing procedure in this phase was
identical to Study 1. After each image, participants provided general
feedback regarding their experience and any additional comments.
Finally, participants were presented with a debrief page informing them
that all images were, in fact, real photographs (see
Figure~\ref{fig-paradigm2}).

\subsubsection{Data Analysis}\label{data-analysis}

\section{References}\label{references}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-de2015jspsych}
De Leeuw, J. R. (2015). jsPsych: A JavaScript library for creating
behavioral experiments in a web browser. \emph{Behavior Research
Methods}, \emph{47}(1), 1--12.

\bibitem[\citeproctext]{ref-hatch2023consumption}
Hatch, S. G., Esplin, C. R., Hatch, H. D., Halstead, A., Olsen, J., \&
Braithwaite, S. R. (2023). The consumption of pornography scale--general
(COPS--g). \emph{Sexual and Relationship Therapy}, \emph{38}(2),
194--218.

\bibitem[\citeproctext]{ref-de2024datapipe}
Leeuw, J. R. de. (2024). DataPipe: Born-open data collection for online
experiments. \emph{Behavior Research Methods}, \emph{56}(3), 2499--2506.

\bibitem[\citeproctext]{ref-marchewka2014nencki}
Marchewka, A., Żurawski, Ł., Jednoróg, K., \& Grabowska, A. (2014). The
nencki affective picture system (NAPS): Introduction to a novel,
standardized, wide-range, high-quality, realistic picture database.
\emph{Behavior Research Methods}, \emph{46}(2), 596--610.

\bibitem[\citeproctext]{ref-schepman2020initial}
Schepman, A., \& Rodway, P. (2020). Initial validation of the general
attitudes towards artificial intelligence scale. \emph{Computers in
Human Behavior Reports}, \emph{1}, 100014.

\bibitem[\citeproctext]{ref-schepman2023general}
Schepman, A., \& Rodway, P. (2023). The general attitudes towards
artificial intelligence scale (GAAIS): Confirmatory validation and
associations with personality, corporate distrust, and general trust.
\emph{International Journal of Human--Computer Interaction},
\emph{39}(13), 2724--2741.

\bibitem[\citeproctext]{ref-wierzba2015erotic}
Wierzba, M., Riegel, M., Pucz, A., Leśniewska, Z., Dragan, W. Ł., Gola,
M., Jednoróg, K., \& Marchewka, A. (2015). Erotic subset for the nencki
affective picture system (NAPS ERO): Cross-sexual comparison study.
\emph{Frontiers in Psychology}, \emph{6}, 1336.

\end{CSLReferences}

\end{document}

### 2025-09-02 paper/manuscript.qmd
started intro

@@
 ```
+
+<!-- AI and Reality distinction
+  - rise of AI
+  - societal consequences
+  - indistinguishable nature of artificial vs real content -->
+
+Recent advances in artificial intelligence (AI) have introduced new challenges for human cognition, particularly regarding the ability to distinguish between authentic and fabricated experiences [@miller2023ai].
+The stakes of such perceptual uncertainty are considerable, with misinformation representing one of the most pressing societal consequences [@kreps2022all].
+For instance, deepfakes (face-swapping technologies that enable the creation of realistic fake images and videos) have already been employed to fabricate convincing political speeches that appear genuine [@meskys2020regulating].
+When deployed in electoral contexts, such content has the potential to distort public opinion and undermine democratic processes by rendering the truth unclear [@graber2021artificial]. 
+Yet political disinformation is only one domain in which synthetic media exerts influence. 
+The increased accessibility of generative technologies means that manipulated or entirely artificial content now permeates social media, entertainment, immersive environments, and interpersonal communication [@nightingale2022ai].
+In these settings, the boundaries between the “real” and the “artificial” are becoming progressively less discernible, raising fundamental questions about how individuals perceive and evaluate reality.
+
+<!-- Reality Perception
+  - ambiguous stimuli
+  - perceptual cues, emotional influence, reality monitoring
+  - AI getting better at producing realistic content -->
+
+A key challenge lies in the prevalence of ambiguous stimuli, that is images, texts, videos, or environments whose authenticity cannot be easily established. 
+While artificial stimuli once carried perceptual markers that betrayed their inauthenticity, such as distortions in early computer-generated imagery [@corvi2023detection; @mcdonnell2010face], these limitations are rapidly disappearing.
+In the domain of face generation especially, current algorithms now produce synthetic images that are virtually indistinguishable from genuine photographs [@moshel2022you; @nightingale2022ai]. 
+As these technologies approach perfect realism, the study of reality perception becomes not only a theoretical concern but also a practical imperative, with direct implications for information security, social trust, and the ethical deployment of AI.
+
+<!-- Affective Responses and Reality Judgments
+  - Link perception of realism with emotional engagement: arousal, valence, enticement.
+  - Mention theories such as Affective Reality Theory (Makowski, 2023) if relevant, or more general emotion–cognition links.
+  - Emotions may not just follow perception, but also shape how we judge what is real. -->
+
+<!-- Sexual Stimuli and Pornography Consumption
+  - Motivation behind inclusion of sexual/non-sexual content (e.g., sexual images are affectively intense, highly relevant for arousal/enticement measures).
+  - Bring in literature on pornography consumption and attitudes toward AI in intimate contexts (questionnaires)
+  - Highlight that this domain is both theoretically interesting (strong affective reactions) and socially relevant (AI-generated sexual content already exists, raising ethical debates). -->
 

### 2025-09-02 paper/manuscript.tex
started intro

@@
 
-\par{     \begin{tcolorbox}[enhanced jigsaw, arc=.35mm, opacityback=0, colback=white, breakable, left=2mm, leftrule=.75mm, rightrule=.15mm, colframe=quarto-callout-note-color-frame, toprule=.15mm, bottomrule=.15mm]
+\par{     \begin{tcolorbox}[enhanced jigsaw, bottomrule=.15mm, colframe=quarto-callout-note-color-frame, left=2mm, breakable, colback=white, opacityback=0, rightrule=.15mm, toprule=.15mm, leftrule=.75mm, arc=.35mm]
 
@@
 \resetlinenumber[1]
+
+Recent advances in artificial intelligence (AI) have introduced new
+challenges for human cognition, particularly regarding the ability to
+distinguish between authentic and fabricated experiences
+(\citeproc{ref-miller2023ai}{Miller et al., 2023}). The stakes of such
+perceptual uncertainty are considerable, with misinformation
+representing one of the most pressing societal consequences
+(\citeproc{ref-kreps2022all}{Kreps et al., 2022}). For instance,
+deepfakes (face-swapping technologies that enable the creation of
+realistic fake images and videos) have already been employed to
+fabricate convincing political speeches that appear genuine
+(\citeproc{ref-meskys2020regulating}{Meskys et al., 2020}). When
+deployed in electoral contexts, such content has the potential to
+distort public opinion and undermine democratic processes by rendering
+the truth unclear (\citeproc{ref-graber2021artificial}{Graber-Mitchell,
+2021}). Yet political disinformation is only one domain in which
+synthetic media exerts influence. The increased accessibility of
+generative technologies means that manipulated or entirely artificial
+content now permeates social media, entertainment, immersive
+environments, and interpersonal communication
+(\citeproc{ref-nightingale2022ai}{Nightingale \& Farid, 2022}).\\
+In these settings, the boundaries between the ``real'' and the
+``artificial'' are becoming progressively less discernible, raising
+fundamental questions about how individuals perceive and evaluate
+reality.
+
+A key challenge lies in the prevalence of ambiguous stimuli, that is
+images, texts, videos, or environments whose authenticity cannot be
+easily established. While artificial stimuli once carried perceptual
+markers that betrayed their inauthenticity, such as distortions in early
+computer-generated imagery (\citeproc{ref-corvi2023detection}{Corvi et
+al., 2023}; \citeproc{ref-mcdonnell2010face}{McDonnell \& Breidt,
+2010}), these limitations are rapidly disappearing. In the domain of
+face generation especially, current algorithms now produce synthetic
+images that are virtually indistinguishable from genuine photographs
+(\citeproc{ref-nightingale2022ai}{Nightingale \& Farid, 2022};
+\citeproc{ref-moshel2022you}{\textbf{moshel2022you?}}). As these
+technologies approach perfect realism, the study of reality perception
+becomes not only a theoretical concern but also a practical imperative,
+with direct implications for information security, social trust, and the
+ethical deployment of AI.
 
@@
 \begin{CSLReferences}{1}{0}
+\bibitem[\citeproctext]{ref-corvi2023detection}
+Corvi, R., Cozzolino, D., Zingarini, G., Poggi, G., Nagano, K., \&
+Verdoliva, L. (2023). On the detection of synthetic images generated by
+diffusion models. \emph{ICASSP 2023-2023 IEEE International Conference
+on Acoustics, Speech and Signal Processing (ICASSP)}, 1--5.
+
 \bibitem[\citeproctext]{ref-de2015jspsych}
@@
 Methods}, \emph{47}(1), 1--12.
+
+\bibitem[\citeproctext]{ref-graber2021artificial}
+Graber-Mitchell, N. (2021). \emph{Artificial illusions: Deepfakes as
+speech}.
 
@@
 194--218.
+
+\bibitem[\citeproctext]{ref-kreps2022all}
+Kreps, S., McCain, R. M., \& Brundage, M. (2022). All the news that's
+fit to fabricate: AI-generated text as a tool of media misinformation.
+\emph{Journal of Experimental Political Science}, \emph{9}(1), 104--117.
 
@@
 \emph{Behavior Research Methods}, \emph{46}(2), 596--610.
+
+\bibitem[\citeproctext]{ref-mcdonnell2010face}
+McDonnell, R., \& Breidt, M. (2010). Face reality: Investigating the
+uncanny valley for virtual faces. In \emph{ACM SIGGRAPH ASIA 2010
+sketches} (pp. 1--2).
+
+\bibitem[\citeproctext]{ref-meskys2020regulating}
+Meskys, E., Kalpokiene, J., Jurcys, P., \& Liaudanskas, A. (2020).
+Regulating deep fakes: Legal and ethical considerations. \emph{Journal
+of Intellectual Property Law \& Practice}, \emph{15}(1), 24--31.
+
+\bibitem[\citeproctext]{ref-miller2023ai}
+Miller, E. J., Steward, B. A., Witkower, Z., Sutherland, C. A.,
+Krumhuber, E. G., \& Dawel, A. (2023). AI hyperrealism: Why AI faces are
+perceived as more real than human ones. \emph{Psychological Science},
+\emph{34}(12), 1390--1403.
+
+\bibitem[\citeproctext]{ref-nightingale2022ai}
+Nightingale, S. J., \& Farid, H. (2022). AI-synthesized faces are
+indistinguishable from real faces and more trustworthy.
+\emph{Proceedings of the National Academy of Sciences}, \emph{119}(8),
+e2120481119.
 

### 2025-09-15 analysis/analysis.qmd
minor

@@
 
+- Reliability
+
 ```{r}
-
 table_dvour <- function(g) {
@@
 
-g1 <- modelbased::estimate_grouplevel(arousal1)
+g1 <- modelbased::estimate_grouplevel(m_a2, type = "total")
 table_dvour(g1)
 
+```
+
+```{r}
+
+colors <- c("p" = "#9C27B0", "confright" = "#795548", "confleft" = "#795548",
+            "precright" = "#607D8B","precleft" = "#607D8B", "pex" = "#FF9800", "bex" = "#F44336")
+
+p2_dvour <- g1_choco |> 
+  mutate(Component = ifelse(Component == "conditional", "p",  Component),
+         Component = fct_relevel(Component, "p", "confright", "confleft", "precright", "precleft", "pex", "bex"),
+         Group = fct_relevel(Group, "Participant", "Item"),
+         .group = paste0(Group, " (", Component, ")")) |>
+  ggplot(aes(x = Median, y = Level)) +
+  geom_pointrange(aes(xmin = CI_low, xmax = CI_high, color= Component), linewidth = 0.3, size = 0.05) +
+  facet_grid(Group~Component, scales = "free", switch="both") +
+  ggside::geom_xsidedensity(aes(group = .group, fill = Component), color = NA) +
+  ggside::ggside(scales  = "free") +
+  scale_color_manual(values = colors) +
+  scale_fill_manual(values = colors) +
+  theme_minimal() +
+  theme(axis.text.y = element_blank(),
+        axis.ticks.y = element_blank(),
+        strip.placement.x = "outside",
+        strip.background = element_rect(fill = NA, color = NA),
+        axis.title.x = element_blank(),
+        axis.title.y = element_blank(),
+        panel.grid.minor = element_blank(),
+        panel.grid.major.y = element_blank(),
+        legend.position = "none")
+p2_dvour
 ```
@@
 
+```{r}
+
+```
+
 :::

### 2025-09-15 analysis/server/make_model.R

@@ -42,6 +42,10 @@ df1 <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/ref
 # MODELS --------
 
 # Arousal
+
+# random slopes that did not converge: (Condition:Relevance/ Participant) + 
+
+
 m_a1 <-  glmmTMB::glmmTMB(Arousal ~ Gender / Relevance/ Condition*ConditionBelief + (1|Participant) + (1|Item),
                           data=df1,
                           family=glmmTMB::ordbeta(),
@@ -107,7 +111,7 @@ df2 <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/ref
 # MODELS --------
 
 # Arousal
-m_a2<-  glmmTMB::glmmTMB(Arousal ~ Gender / Condition*ConditionBelief + (1|Participant) + (1|Item),
+m_a2<-  glmmTMB::glmmTMB(Arousal ~ Gender / Condition*ConditionBelief + (Condition|Participant) + (1|Item),
                           data=df2,
                           family=glmmTMB::ordbeta(),
                           control = glmmTMB::glmmTMBControl(parallel = 8))

### 2025-09-29 analysis/analysis.qmd
started change to brms

--- 2025-09-02 analysis/analysis.qmd
@@
 
-::: {.panel-tabset}
-
 ### Random Effects
@@
 
+model_draft <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition + (Condition|Participant) + (1|Item),
+                          data=df2,
+                          family=glmmTMB::ordbeta(),
+                          control = glmmTMB::glmmTMBControl(parallel = 8))
+
+```
+### Reliability
+
+```{r}
 table_dvour <- function(g) {
@@
     gt::gt() |> 
-    gt::data_color("D_vour", palette = "green", domain = c(0, 1)) |> 
+    gt::data_color("D_vour", palette = c("red","green"), domain = c(0, 1)) |> 
     gt::fmt_auto()
@@
 
-g1 <- modelbased::estimate_grouplevel(arousal1)
+g1 <- modelbased::estimate_grouplevel(model_draft)
 table_dvour(g1)
@@
 
+#### Participant effects
+
 ```{r}
-g2 <- modelbased::estimate_grouplevel(arousal2)
-table_dvour(g2)
+colors <- c("(Intercept)" = "#9C27B0","ConditionAI-Generated" = "#FF9800")
+
+p2_dvour <- g1 |> 
+  ggplot(aes(x = Coefficient, y = Level)) +
+  geom_pointrange(aes(xmin = CI_low, xmax = CI_high, color = Parameter), linewidth = 0.3, size = 0.05) +
+  facet_grid(Group~Parameter, scales = "free", switch="both") +
+  ggside::ggside(scales  = "free") +
+  ggside::geom_xsidedensity(aes(group = Parameter, fill = Parameter), color = NA) +
+  ggside::ggside(scales  = "free") +
+  scale_color_manual(values = colors) +
+  scale_fill_manual(values = colors) +
+  theme_minimal() +
+  theme(axis.text.y = element_blank(),
+        axis.ticks.y = element_blank(),
+        strip.placement.x = "outside",
+        strip.background = element_rect(fill = NA, color = NA),
+        axis.title.x = element_blank(),
+        axis.title.y = element_blank(),
+        panel.grid.minor = element_blank(),
+        panel.grid.major.y = element_blank(),
+        legend.position = "none")
+p2_dvour
 ```
 
-### Participant effects
-
-:::
+### Correlation

### 2025-09-29 analysis/server/make_model.R

@@ -38,6 +38,7 @@ df1 <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/ref
          ConditionBelief = fct_relevel(ConditionBelief, "True", "False")) |> 
   mutate(across(starts_with("Feedback_"), function(x) {fct_relevel(x, "False", "True")}))
 
+df1[1:2,] # keep only 2 participants to test locally 
 
 # MODELS --------
 
@@ -46,20 +47,20 @@ df1 <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/ref
 # random slopes that did not converge: (Condition:Relevance/ Participant) + 
 
 
-m_a1 <-  glmmTMB::glmmTMB(Arousal ~ Gender / Relevance/ Condition*ConditionBelief + (1|Participant) + (1|Item),
+m_a1 <-  brms::brm(Arousal ~ Gender / Relevance/ Condition*ConditionBelief + (1|Participant) + (1|Item),
                           data=df1,
                           family=glmmTMB::ordbeta(),
                           control = glmmTMB::glmmTMBControl(parallel = 8))
 
 # Enticement
-m_e1 <-  glmmTMB::glmmTMB(Enticement ~ Gender /Relevance/Condition*ConditionBelief + (1|Participant) + (1|Item),
+m_e1 <-  brms::brm(Enticement ~ Gender /Relevance/Condition*ConditionBelief + (1|Participant) + (1|Item),
                           data=df1,
                           family=glmmTMB::ordbeta(),
                           control = glmmTMB::glmmTMBControl(parallel = 8))
 
 
 # Valence
-m_v1 <-  glmmTMB::glmmTMB(Valence ~ Gender / Relevance/ Condition*ConditionBelief + (1|Participant) + (1|Item),
+m_v1 <-  brms::brm(Valence ~ Gender / Relevance/ Condition*ConditionBelief + (1|Participant) + (1|Item),
                           data=df1,
                           family=glmmTMB::ordbeta(),
                           control = glmmTMB::glmmTMBControl(parallel = 8))
@@ -107,21 +108,22 @@ df2 <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/ref
     TRUE ~ "Individual")) |>
   mutate(StimuliType = fct_relevel(StimuliType, "Individual", "Couple"))
 
+df2[1:2,] # keep only 2 participants to test locally 
+
 
 # MODELS --------
-
 # Arousal
[…]

### 2025-09-29 analysis/analysis.qmd
minor

@@
 ## Data Preparation
+
+```{r}
+
+m_a1 <-  brms::brm(Arousal ~ Gender / Relevance/ Condition*ConditionBelief + (Relevance / Condition|Participant) + (1|Item),
+                          data=df1, family=zero_one_inflated_beta())
+
+# Enticement
+m_e1 <-  brms::brm(Enticement ~ Gender /Relevance/Condition*ConditionBelief + (1|Participant) + (1|Item),
+                          data=df1, family=zero_one_inflated_beta())
+
+# Valence
+m_v1 <-  brms::brm(Valence ~ Gender / Relevance/ Condition*ConditionBelief + (1|Participant) + (1|Item),
+                          data=df1, family=zero_one_inflated_beta())
+```
+
+```{r}
+
+m_a2<-  brms::brm(Arousal ~ Gender / Condition*ConditionBelief + (Condition|Participant) + (1|Item),
+                          data=df2, family=zero_one_inflated_beta())
+# Enticement
+m_e2 <-  brms::brm(Enticing ~ Gender / Condition*ConditionBelief + (1|Participant) + (1|Item),
+                          data=df2,family=zero_one_inflated_beta())
+# Valence
+m_v2 <-  brms::brm(Valence ~ Gender / Condition*ConditionBelief + (1|Participant) + (1|Item),
+                          data=df2,family=zero_one_inflated_beta())
+```
 

### 2025-09-29 analysis/server/make_model.R

@@ -5,6 +5,7 @@ library(easystats)
 library(patchwork)
 library(ggside)
 library(glmmTMB)
+library(brms)
 
 options(mc.cores = parallel::detectCores(),
         brms.backend = "cmdstanr",
@@ -47,23 +48,17 @@ df1[1:2,] # keep only 2 participants to test locally
 # random slopes that did not converge: (Condition:Relevance/ Participant) + 
 
 
-m_a1 <-  brms::brm(Arousal ~ Gender / Relevance/ Condition*ConditionBelief + (1|Participant) + (1|Item),
-                          data=df1,
-                          family=glmmTMB::ordbeta(),
-                          control = glmmTMB::glmmTMBControl(parallel = 8))
+m_a1 <-  brms::brm(Arousal ~ Gender / Relevance/ Condition*ConditionBelief + (Relevance / Condition|Participant) + (1|Item),
+                          data=df1, family=zero_one_inflated_beta())
 
 # Enticement
 m_e1 <-  brms::brm(Enticement ~ Gender /Relevance/Condition*ConditionBelief + (1|Participant) + (1|Item),
-                          data=df1,
-                          family=glmmTMB::ordbeta(),
-                          control = glmmTMB::glmmTMBControl(parallel = 8))
+                          data=df1, family=zero_one_inflated_beta())
 
 
 # Valence
 m_v1 <-  brms::brm(Valence ~ Gender / Relevance/ Condition*ConditionBelief + (1|Participant) + (1|Item),
-                          data=df1,
-                          family=glmmTMB::ordbeta(),
-                          control = glmmTMB::glmmTMBControl(parallel = 8))
+                          data=df1, family=zero_one_inflated_beta())
 
 # Save models
 saveRDS(m_a1, file = "../models/ModelArousal_1.rds")
@@ -114,19 +109,13 @@ df2[1:2,] # keep only 2 participants to test locally
 # MODELS --------
 # Arousal
 m_a2<-  brms::brm(Arousal ~ Gender / Condition*ConditionBelief + (Condition|Participant) + (1|Item),
-                          data=df2,
-                          family=glmmTMB::ordbeta(),
-                          control = glmmTMB::glmmTMBControl(parallel = 8))
+                          data=df2, family=zero_one_inflated_beta())
 # Enticement
 m_e2 <-  brms::brm(Enticing ~ Gender / Condition*ConditionBelief + (1|Participant) + (1|Item),
-                          data=df2,
[…]

### 2025-10-09 analysis/analysis.qmd
Update analysis.qmd

--- 2025-09-29 analysis/analysis.qmd
@@
   ggplot(aes(x=Arousal, fill = Condition)) +
-  geom_histogram(position = "identity", alpha = 0.4, colour = "black", bins = 20) +
+  geom_histogram(position = "identity", alpha = 0.5, colour = "black", bins = 30) +
   scale_x_continuous(breaks = c(0, 1)) +
@@
 arousal_dist2
+```
+
+### Arousal Distributions
+
+```{r Arousal1}
+#| fig-width: 12
+arousal_dist1 <- df1 |>
+  ggplot(aes(x=Arousal, fill = Condition)) +
+  geom_histogram(position = "identity", alpha = 0.5, colour = "black", bins = 30) +
+  scale_x_continuous(breaks = c(0, 1)) +
+  labs(title = "Arousal Study 1", ) +
+  facet_wrap(~Gender) +
+  scale_fill_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5, face="bold"))
+
+arousal_dist1
+```
+
+```{r Arousal2}
+#| fig-width: 12
+arousal_dist2 <- df2 |>
+  ggplot(aes(x=Arousal, fill = Condition)) +
+  geom_bar(position = "identity", alpha = 0.5, line = "black") +
+  scale_y_sqrt(expand = c(0, 0)) +
+  scale_x_continuous(breaks = c(0, 1)) +
+  labs(title = "Arousal Study 2", ) +
+  facet_wrap(~Gender) +
+  scale_fill_manual(values=c("Photograph"="#F44336", "AI-Generated"="#2196F3")) +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5, face="bold"))
+
+arousal_dist2
+```
+
+### Enticment Distributions
+
+```{r Arousal1}
+#| fig-width: 12
+enticement_dist1 <- df1 |>
+  ggplot(aes(x=Enticement, fill = Condition)) +
+  geom_histogram(position = "identity", alpha = 0.5, colour = "black", bins = 30) +
+  scale_x_continuous(breaks = c(0, 1)) +
+  labs(title = "Enticement Study 1", ) +
+  facet_wrap(~Gender) +
+  scale_fill_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5, face="bold"))
+
+enticement_dist1
+```
+
+```{r Arousal2}
+#| fig-width: 12
+enticement_dist2 <- df2 |>
+  ggplot(aes(x=Enticing, fill = Condition)) +
+  geom_bar(position = "identity", alpha = 0.5, line = "black") +
+  scale_y_sqrt(expand = c(0, 0)) +
+  scale_x_continuous(breaks = c(0, 1)) +
+  labs(title = "Enticment Study 2", ) +
+  facet_wrap(~Gender) +
+  scale_fill_manual(values=c("Photograph"="#F44336", "AI-Generated"="#2196F3")) +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5, face="bold"))
+
+enticement_dist2
+```
+
+### Valence Distributions
+
+```{r Arousal1}
+#| fig-width: 12
+valence_dist1 <- df1 |>
+  ggplot(aes(x=Valence, fill = Condition)) +
+  geom_histogram(position = "identity", alpha = 0.5, colour = "black", bins = 30) +
+  scale_x_continuous(breaks = c(0, 1)) +
+  labs(title = "Valence Study 1", ) +
+  facet_wrap(~Gender) +
+  scale_fill_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5, face="bold"))
+
+valence_dist1
+```
+
+```{r Arousal2}
+#| fig-width: 12
+valence_dist2 <- df2 |>
+  ggplot(aes(x=Valence, fill = Condition)) +
+  geom_bar(position = "identity", alpha = 0.5, line = "black") +
+  scale_y_sqrt(expand = c(0, 0)) +
+  scale_x_continuous(breaks = c(0, 1)) +
+  labs(title = "Valence Study 2", ) +
+  facet_wrap(~Gender) +
+  scale_fill_manual(values=c("Photograph"="#F44336", "AI-Generated"="#2196F3")) +
+  theme_minimal() +
+  theme(plot.title = element_text(hjust = 0.5, face="bold"))
+
+valence_dist2
 ```
@@
 ```{r}
+params_table <- function(m) {
+  d <- as.data.frame(m, variable = insight::find_parameters(m, effects = "fixed", flatten  = TRUE))
+  t <- bayestestR::describe_posterior(d, effects = "fixed", component = "all", ci_method = "hdi", test = "p_direction")
+  out <- insight::format_table(t)
+  out |> 
+    mutate(col = t$pd) |> 
+    gt::gt() |> 
+    gt::data_color(columns = "col", method = "numeric", target_columns = "pd", 
+                   row = col > 0.95, palette = "yellow") |> 
+    gt::data_color(columns = "col", method = "numeric", target_columns = "pd", 
+                   row = col > 0.97, palette = "green") |> 
+    gt::cols_hide("col")
+ }
+```
+
+```{r}
 arousal1 <- readRDS("models/ModelArousal_1.rds")
@@
 ```{r}
-results_table(arousal1)
+params_table(arousal1)
+summary(arousal1, robust = TRUE)
 ```
@@
 ```{r}
-results_table(arousal2)
+params_table(arousal2)
+summary(arousal2, robust = TRUE)
 
@@
   plt <- pred_df |>
-    ggplot(aes(x = ConditionBelief, y = Proportion,color = Condition, linetype = Sample, group = interaction(Sample, Condition)
+    ggplot(aes(x = ConditionBelief, y = Estimate,color = Condition, linetype = Sample, group = interaction(Sample, Condition)
     )) +
@@
 ```{r}
-results_table(enticement1)
+params_table(enticement1)
+summary(enticement1, robust = TRUE)
 ```
@@
 ```{r}
-results_table(enticement2)
+params_table(enticement2)
+summary(enticement2, robust = TRUE)
+
 ```
@@
 ```{r}
-results_table(valence1)
+params_table(valence1)
+summary(valence1, robust = TRUE)
 ```
@@
 ```{r}
-results_table(valence2)
+params_table(valence2)
+summary(valence2, robust = TRUE)
+
 ```
@@
 
-```{r}
-
-model_draft <- glmmTMB::glmmTMB(Arousal ~ Gender / Condition + (Condition|Participant) + (1|Item),
-                          data=df2,
-                          family=glmmTMB::ordbeta(),
-                          control = glmmTMB::glmmTMBControl(parallel = 8))
-
-```
 ### Reliability

### 2025-10-09 analysis/server/make_model.R
Update make_model.R

@@ -32,14 +32,14 @@ df1 <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/ref
   ) |>
   rename(Gender = Sex) |>
   datawizard::rescale(select=c("Valence"), range=c(-1, 1), to=c(0, 1)) |>
-  mutate(Condition = fct_relevel(Condition, "Photograph", "AI-Generated"),
-         Relevance =  fct_relevel(Relevance, "Relevant", "Irrelevant", "Non-erotic"),
+  mutate(Condition = fct_relevel(Condition, "Photograph", "AIGenerated"),
+         Relevance =  fct_relevel(Relevance, "Relevant", "Irrelevant", "NonErotic"),
          Gender =  fct_relevel(Gender, "Male", "Female"),
          PornFrequency = as.numeric(as.factor(COPS_Frequency_2)),
          SexualActivity_num = as.numeric(as.factor(SexualActivity)),
          ConditionBelief = case_when(
            Condition == "Photograph" & Realness > 0.5 ~ "True",
-           Condition == "AI-Generated" & Realness < 0.5 ~ "True",
+           Condition == "AIGenerated" & Realness < 0.5 ~ "True",
            .default = "False"
          ),
          ConditionBelief = as.factor(ConditionBelief),
@@ -114,14 +114,14 @@ df2 <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/ref
     Condition == "Fiction" ~ "AI-Generated",
     Condition == "Reality" ~ "Photograph"
   )) |>
-  mutate(Condition = fct_relevel(Condition, "Photograph", "AI-Generated"),
+  mutate(Condition = fct_relevel(Condition, "Photograph", "AIGenerated"),
          Gender =  fct_relevel(Gender, "Male", "Female"),
          SexualOrientation = fct_relevel(SexualOrientation, "Heterosexual", "Homosexual", "Bisexual"),
          PornFrequency = as.numeric(as.factor(COPS_Frequency)),
          SexualActivity_num = as.numeric(as.factor(SexualActivity)),
          ConditionBelief = case_when(
            Condition == "Photograph" & Realness > 0.5 ~ "True",
-           Condition == "AI-Generated" & Realness < 0.5 ~ "True",
+           Condition == "AIGenerated" & Realness < 0.5 ~ "True",
            .default = "False"),
          ConditionBelief = as.factor(ConditionBelief),
          ConditionBelief = fct_relevel(ConditionBelief, "True", "False")) |>

### 2025-11-10 analysis/analysis.qmd
Update analysis.qmd

@@
   ggplot(aes(x=Arousal, fill = Condition)) +
-  geom_bar(position = "identity", alpha = 0.5, line = "black") +
-  scale_y_sqrt(expand = c(0, 0)) +
-  scale_x_continuous(breaks = c(0, 1)) +
-  labs(title = "Arousal Study 2", ) +
-  facet_wrap(~Gender) +
-  scale_fill_manual(values=c("Photograph"="#F44336", "AI-Generated"="#2196F3")) +
-  theme_minimal() +
-  theme(plot.title = element_text(hjust = 0.5, face="bold"))
-
-arousal_dist2
-```
-
-### Arousal Distributions
-
-```{r Arousal1}
-#| fig-width: 12
-arousal_dist1 <- df1 |>
-  ggplot(aes(x=Arousal, fill = Condition)) +
-  geom_histogram(position = "identity", alpha = 0.5, colour = "black", bins = 30) +
-  scale_x_continuous(breaks = c(0, 1)) +
-  labs(title = "Arousal Study 1", ) +
-  facet_wrap(~Gender) +
-  scale_fill_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
-  theme_minimal() +
-  theme(plot.title = element_text(hjust = 0.5, face="bold"))
-
-arousal_dist1
-```
-
-```{r Arousal2}
-#| fig-width: 12
-arousal_dist2 <- df2 |>
-  ggplot(aes(x=Arousal, fill = Condition)) +
-  geom_bar(position = "identity", alpha = 0.5, line = "black") +
+  geom_bar(position = "identity", alpha = 0.5, colour = "black") +
   scale_y_sqrt(expand = c(0, 0)) +
@@
   ggplot(aes(x=Enticing, fill = Condition)) +
-  geom_bar(position = "identity", alpha = 0.5, line = "black") +
+  geom_bar(position = "identity", alpha = 0.5, colour = "black") +
   scale_y_sqrt(expand = c(0, 0)) +
@@
   ggplot(aes(x=Valence, fill = Condition)) +
-  geom_bar(position = "identity", alpha = 0.5, line = "black") +
+  geom_bar(position = "identity", alpha = 0.5, colour = "black") +
   scale_y_sqrt(expand = c(0, 0)) +
@@
 ```
+:::
 
-### Average Arousal
+## Average Arousal
+
+::: {.panel-tabset}
+
+### Study 1
 
@@
 ```
+
+### Study 2
 
@@
 
+<!-- Study 2 Arousal:  Draws: 96 chains, each with iter = 2000; warmup = 1000; thin = 1; total post-warmup draws = 96000 -->
+
+<!-- Study 2 Arousal: Draws: 80 chains, each with iter=2000; warmup=1000; thin=1; post-warmup draws per chain=1000, total post-warmup draws=80000. -->
 ```{r}
@@
 ```
+
+#### Posterior Description
+
+<!-- Sampling Diagnostics -->
+
+<!-- - ESS should be at least 1000 (the effective sample size - ESS - is an estimation of the number of independent samples) -->
+
+<!-- - R^(“R-hat”) Should be lower than 1.01 (R-hat is a measure of convergence) -->
 
@@
 summary(arousal2, robust = TRUE)
+```
 
+#### Model Performance
+
+```{r}
+performance::performance(arousal1)
 ```
@@
 ```{r}
-#| fig-height: 8
-#| fig-width: 8
-
-make_combined_plot <- function(model1, model2 = NULL, 
-                               title = "Estimated Marginal Means") {
-
-  df1 <- modelbased::estimate_means(
-    model1, by = c("Gender", "Relevance", "Condition", "ConditionBelief"),backend = "emmeans") |>
-    dplyr::mutate(Sample = "Study 1") |>
-    as.data.frame()
-
-  # Study 2: only Relevant
-  if (!is.null(model2)) {
-    df2 <- modelbased::estimate_means(
-      model2, by = c("Gender", "Condition", "ConditionBelief"), backend = "emmeans") |>
-      dplyr::mutate(Relevance = "Relevant", Sample = "Study 2") |>
-      as.data.frame()
-    pred_df <- rbind(df1, df2)
-  } else {
-    pred_df <- df1
-  }
-
-  plt <- pred_df |>
-    ggplot(aes(x = ConditionBelief, y = Estimate,color = Condition, linetype = Sample, group = interaction(Sample, Condition)
-    )) +
-    geom_hline(yintercept = 0, color = "darkgrey") +
-    geom_line(linewidth = 1) +
-    geom_point(size = 2) +
-    geom_errorbar(aes(ymin = CI_low, ymax = CI_high), width = 0.1) +
-    facet_grid(Relevance ~ Gender, switch = "y") +
-    scale_color_manual(values = c("AI-Generated" = "#2196F3","Photograph" = "#F44336")) +
-    theme_minimal(base_size = 14) +
-    labs(title = title, x= "Whether the original labels were believed to be true",color = "Images presented as:", linetype = "Sample"
-    ) +
-    theme(
-      axis.title.y = element_blank(),
-      axis.text.y = element_text(size = 8),
-      strip.placement = "outside",
-      strip.background.x = element_rect(fill = "lightgrey", color = NA),
-      strip.text.x = element_text(size = 10),
-      strip.text.y = element_text(size = 10),
-      axis.text.x = element_text(face = "bold", size = 9, color = "black"),
-      legend.text = element_text(size = 10),
-      legend.position = "bottom")
-
-  plt
-}
-
-plta <- make_combined_plot(arousal1, arousal2, title = "Arousal Estimates for All Stimuli")
-
-plta
-```
-
-### Enticement
-
-```{r}
-enticement1 <- readRDS("models/ModelEnticement_1.rds")
-enticement2 <- readRDS("models/ModelEnticement_2.rds")
-```
-
-```{r}
-params_table(enticement1)
-summary(enticement1, robust = TRUE)
-```
-
-```{r}
-params_table(enticement2)
-summary(enticement2, robust = TRUE)
-
-```
-
-```{r}
-#| fig-height: 8
-#| fig-width: 8
-
-plt_e <- make_combined_plot(enticement1, enticement2, title = "Enticement Estimates for All Stimuli")
-plt_e
-```
-
-### Valence
-
-```{r}
-valence1 <- readRDS("models/ModelValence_1.rds")
-valence2 <- readRDS("models/ModelValence_2.rds")
-```
-
-```{r}
-params_table(valence1)
-summary(valence1, robust = TRUE)
-```
-
-```{r}
-params_table(valence2)
-summary(valence2, robust = TRUE)
-
-```
-
-```{r}
-#| fig-height: 8
-#| fig-width: 8
-
-plt_v <- make_combined_plot(valence1, valence2, title = "Valence Estimates for All Stimuli")
-plt_v
+performance::performance(arousal2)
 ```

### 2025-11-10 analysis/server/make_model.R
Update make_model.R

@@ -27,7 +27,7 @@ df1 <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/ref
 # ----------------------------
 
 # Arousal
-f_a1 <- brms::brmsformula(Arousal ~ Gender/Relevance/Condition * ConditionBelief + ((Relevance / Condition * ConditionBelief) | Participant) + (1 | Item))
+f_a1 <- brms::brmsformula(Arousal ~ Gender / Relevance / (Condition * ConditionBelief) + (1  + Relevance / Condition  | Participant) + (1|Item))
 m_a1 <-  brms::brm(
   formula = f_a1,
   data = df1,
@@ -42,36 +42,36 @@ m_a1 <-  brms::brm(
 )
 
 # Enticement (FIXED: use f_e1 and set chains)
-f_e1 <- brms::brmsformula(Enticement ~ Gender/Relevance/Condition * ConditionBelief + ((Relevance / Condition * ConditionBelief) | Participant) + (1 | Item))
+# f_e1 <- brms::brmsformula(Enticement ~ Gender/Relevance/Condition * ConditionBelief + ((Relevance / Condition * ConditionBelief) | Participant) + (1 | Item))
 
-m_e1 <-  brms::brm(
-  formula = f_e1,
-  data = df1,
-  family = zero_one_inflated_beta(),
-  chains = chains_per_task,
-  cores = chains_per_task,
-  iter = iter,
-  warmup = warmup,
-  seed = 1234 + start_chain,
-  backend = "cmdstanr",
-  file = file.path(models_dir, paste0("ModelEnticement_1_task_", task_id))
-)
+# m_e1 <-  brms::brm(
+#   formula = f_e1,
+#   data = df1,
+#   family = zero_one_inflated_beta(),
+#   chains = chains_per_task,
+#   cores = chains_per_task,
+#   iter = iter,
+#   warmup = warmup,
+#   seed = 1234 + start_chain,
+#   backend = "cmdstanr",
+#   file = file.path(models_dir, paste0("ModelEnticement_1_task_", task_id))
+# )
 
 # Valence
-f_v1 <- brms::brmsformula(Valence ~ Gender/Relevance/Condition * ConditionBelief + ((Relevance / Condition * ConditionBelief) | Participant) + (1 | Item))
[…]

### 2025-11-11 paper/manuscript.qmd
minor

@@
 
-The initial sample comprised 1,067 participants recruited via multiple channels, including Prolific\textcopyright, Sona (ref), social media platforms, university classrooms, and snowball sampling.
+The initial sample comprised 1,067 participants recruited via multiple channels, including Prolific\textcopyright, Sona Systems, social media platforms, university classrooms, and snowball sampling.
 This strategy yielded a heterogeneous pool of both incentivised and non-incentivised individuals, including students and members of the general population from England, France, Italy, Colombia, and Spain.
@@
 
-The Consumption of Pornography Scale – General [COPS, @hatch2023consumption] is a 34-itemmeasure assessing pornography use across multiple dimensions, including frequency, duration and recency of sexual activity.
+The Consumption of Pornography Scale – General [COPS, @hatch2023consumption] is a 34-item measure assessing pornography use across multiple dimensions, including frequency, duration and recency of sexual activity.
 Participants reported how often they had viewed pornography in the past 30 days (e.g., not at all, once or twice, weekly, daily, multiple times per day) and the typical duration of viewing sessions (less than 5 minutes to 46+ minutes).
@@
 Their task was to rate each image on arousal, enticement, and valence.
-Each participant viewed 60 images in total: 40 erotic images (20 male and 20 female) from the Erotic subset of the Nencki Affective Picture System [NAPS ERO, @wierzba2015erotic], and 20 additional images (10 neutral, 10 positively arousing) from the original NAPS database [@marchewka2014nencki].
+Each participant viewed, in a randomised order, 60 images in total: 40 erotic images (20 male and 20 female) from the Erotic subset of the Nencki Affective Picture System [NAPS ERO, @wierzba2015erotic], and 20 additional images (10 neutral, 10 positively arousing) from the original NAPS database [@marchewka2014nencki].
 Each trial followed a fixed timing sequence: a fixation cross (750 ms), a color-coded textual cue (1,250 ms), another fixation cross (500 ms), then the image (2,500 ms).
@@
 
-In the final phase, participants viewed the same 60 images, presented in a new randomized order.
+In the final phase, participants viewed the same 60 images, presented in a new randomised order.
 Each was preceded by a 500 ms fixation cross and displayed for 1,000 ms.

### 2025-11-11 analysis/analysis.qmd
minor

@@
 
+<!-- These functions provide information about the reliability of group-level estimates (i.e., random effects) in mixed models.
+They are useful to assess whether the predictors yield consistent group-level variability.
+"Group-level" can refer, for instance, to different participants in a study, and the predictors to the effect of some experimental condition.
+-->
+
+<!-- D_vour: corresponds to the normalized ratio of observed variability to uncertainty in random effect estimates -->
+
 ```{r}
@@
 
-g1 <- modelbased::estimate_grouplevel(model_draft)
+draft_model <- brms::brm(
+  formula = Arousal ~ Gender / (Condition * ConditionBelief) + (1  + Condition | Participant) + (1|Item),
+  data = df2,
+  family = brms::zero_one_inflated_beta())
+
+g1 <- modelbased::estimate_grouplevel(arousal2)
 table_dvour(g1)
@@
 p2_dvour <- g1 |> 
-  ggplot(aes(x = Coefficient, y = Level)) +
+  ggplot(aes(x = Estimate, y = Level)) +
   geom_pointrange(aes(xmin = CI_low, xmax = CI_high, color = Parameter), linewidth = 0.3, size = 0.05) +

### 2025-11-13 analysis/analysis.qmd
minor

@@
 
-<!-- Study 2 Arousal:  Draws: 96 chains, each with iter = 2000; warmup = 1000; thin = 1; total post-warmup draws = 96000 -->
-
-<!-- Study 2 Arousal: Draws: 80 chains, each with iter=2000; warmup=1000; thin=1; post-warmup draws per chain=1000, total post-warmup draws=80000. -->
 ```{r}
-arousal1 <- readRDS("models/ModelArousal_1.rds")
+# arousal1 <- readRDS("models/ModelArousal_1.rds")
 arousal2 <- readRDS("models/ModelArousal_2.rds")
@@
 }
+```
 
-draft_model <- brms::brm(
-  formula = Arousal ~ Gender / (Condition * ConditionBelief) + (1  + Condition | Participant) + (1|Item),
-  data = df2,
-  family = brms::zero_one_inflated_beta())
+```{r}
+# draft_model <- brms::brm(
+#   formula = Arousal ~ Gender / (Condition * ConditionBelief) + (1  + Condition | Participant) + (1|Item),
+#   data = df2,
+#   family = brms::zero_one_inflated_beta())
 
-g1 <- modelbased::estimate_grouplevel(arousal2)
+# g1 <- modelbased::estimate_grouplevel(arousal2)
+
+# saveRDS(g1, file = "draft_model_estimates.rds")
+
+```
+
+```{r}
+g1 <- readRDS("draft_model_estimates.rds")
+
 table_dvour(g1)
@@
 
+<!-- The random intercepts for participants showed moderate variability around the grand mean, suggesting that some participants tended to report consistently higher or lower arousal regardless of condition or belief.
+-->
+
+<!-- The item-level intercepts exhibited similar variability, indicating that certain stimuli were intrinsically more arousing than others across participants. -->
+
 ```{r}
-colors <- c("(Intercept)" = "#9C27B0","ConditionAI-Generated" = "#FF9800")
+colors <- c("Intercept" = "#9C27B0")
 
 p2_dvour <- g1 |> 
-  ggplot(aes(x = Estimate, y = Level)) +
+   mutate(Group = fct_relevel(Group, "Participant", "Item")) |>
+  ggplot(aes(x = Median , y = Level)) +
   geom_pointrange(aes(xmin = CI_low, xmax = CI_high, color = Parameter), linewidth = 0.3, size = 0.05) +

### 2025-11-13 analysis/analysis.qmd
updated analysis
rest of analysis done with draft model

@@
 ```{r}
-# draft_model <- brms::brm(
-#   formula = Arousal ~ Gender / (Condition * ConditionBelief) + (1  + Condition | Participant) + (1|Item),
-#   data = df2,
-#   family = brms::zero_one_inflated_beta())
+draft_model <- brms::brm(
+  formula = Arousal ~ Gender / (Condition * ConditionBelief) + (1  + Condition | Participant) + (1|Item),
+  data = df2,
+  algorithm = "meanfield",
+  family = brms::zero_one_inflated_beta())
 
-# g1 <- modelbased::estimate_grouplevel(arousal2)
+g1 <- modelbased::estimate_grouplevel(draft_model)
 
@@
 ```{r}
-g1 <- readRDS("draft_model_estimates.rds")
+# g1 <- readRDS("draft_model_estimates.rds")
 
@@
 
+##### Study 1
+
 ```{r}
-colors <- c("Intercept" = "#9C27B0")
+colors <- c("Intercept" = "#9C27B0", "ConditionAIMGenerated" = "#FF9800")
 
 p2_dvour <- g1 |> 
-   mutate(Group = fct_relevel(Group, "Participant", "Item")) |>
+   mutate(Group = fct_relevel(Group, "Participant", "Item"),
+          Parameter = fct_relevel(Parameter, "Intercept", "ConditionAIMGenerated")) |>
+  ggplot(aes(x = Median , y = Level)) +
+  geom_pointrange(aes(xmin = CI_low, xmax = CI_high, color = Parameter), linewidth = 0.3, size = 0.05) +
+  facet_grid(Group~Parameter, scales = "free", switch="both") +
+  ggside::ggside(scales  = "free") +
+  ggside::geom_xsidedensity(aes(group = Parameter, fill = Parameter), color = NA) +
+  ggside::ggside(scales  = "free") +
+  scale_color_manual(values = colors) +
+  scale_fill_manual(values = colors) +
+  theme_minimal() +
+  theme(axis.text.y = element_blank(),
+        axis.ticks.y = element_blank(),
+        strip.placement.x = "outside",
+        strip.background = element_rect(fill = NA, color = NA),
+        axis.title.x = element_blank(),
+        axis.title.y = element_blank(),
+        panel.grid.minor = element_blank(),
+        panel.grid.major.y = element_blank(),
+        legend.position = "none")
+p2_dvour
+```
+
+##### Study 2
+
+```{r}
+colors <- c("Intercept" = "#9C27B0", "ConditionAIMGenerated" = "#FF9800")
+
+p2_dvour <- g1 |> 
+   mutate(Group = fct_relevel(Group, "Participant", "Item"),
+          Parameter = fct_relevel(Parameter, "Intercept", "ConditionAIMGenerated")) |>
   ggplot(aes(x = Median , y = Level)) +
@@
 ### Correlation
+
+- between random-slopes (effect of condition) and dispositional traits 
+<!-- - look at mint and fiction choco analysis for correlation matrix -->
+
+#### Study 1
+
+```{r}
+
+df_phase <- as.data.frame(g1) |>
+  filter(Group == "Participant") |>
+  mutate(Parameter = as.factor(Parameter)) |>
+   pivot_wider(id_cols = Level, names_from = Parameter, values_from = c(Median, MAD, CI_low, CI_high),names_glue = "{Parameter}_{.value}"
+  ) |>
+  rename(Participant= Level)
+
+head(g2_phase)
+
+df_dispositional <- dfsub1 |>
+  select(Participant, 
+           BAIT_Videos, BAIT_Visual, BAIT_Text, AI_Knowledge, SexualActivity, 
+           GAAIS_Negative, GAAIS_Positive, Porn) |>
+  rename(Porn_factor = Porn)
+
+head(g3_dispositional)
+
+```
+
+```{r}
+make_cor <- function(df_phase, df_dispositional = NULL, 
+                     qname_x = TRUE, qname_y = TRUE, 
+                     textsize = 3, xcol = "#424242", ycol = "#424242") {
+
+  # Identify common participants (if df_dispositional provided)
+  if (!is.null(df_dispositional)) {
+    common_ids <- intersect(df_phase$Participant, df_dispositional$Participant)
+    df_phase <- df_phase |> filter(Participant %in% common_ids) |> arrange(Participant)
+    df_dispositional <- df_dispositional |> filter(Participant %in% common_ids) |> arrange(Participant)
+  }
+
+  # Compute correlations
+  # r <- df_phase |>
+  #   select(ConditionAIMGenerated_Median, Intercept_Median) |>
+  #   correlation::correlation(
+  #     data2 = if (!is.null(df_dispositional)) df_dispositional |> select(-Participant) else NULL,
+  #     p_adjust = "none",
+  #     redundant = ifelse(is.null(df_dispositional), TRUE, FALSE)
+  #   ) |>
+  #   correlation::cor_sort() |>
+  #   mutate(
+  #     label = ifelse(p < .05, paste0(insight::format_value(r, lead_zero = FALSE, zap_small = TRUE)), ""),
+  #     Parameter1 = as.factor(Parameter1),
+  #     Parameter2 = as.factor(Parameter2)
+  #   )
+
+  r <- df_phase |>
+  select(ConditionAIMGenerated_Median, Intercept_Median) |>
+  correlation::correlation(
+    data2 = if (!is.null(df_dispositional)) df_dispositional |> select(-Participant) else NULL,
+    p_adjust = "none",
+    redundant = ifelse(is.null(df_dispositional), TRUE, FALSE)
+  ) |>
+  correlation::cor_sort() |>
+  mutate(
+    # always show r, add '*' if p < .05
+    label = paste0(
+      insight::format_value(r, lead_zero = FALSE, zap_small = TRUE),
+      ifelse(p < .05, "*", "")
+    ),
+    Parameter1 = as.factor(Parameter1),
+    Parameter2 = as.factor(Parameter2)
+  )
+
+  # Clear diagonal labels
+  r[as.character(r$Parameter1) == as.character(r$Parameter2), "label"] <- ""
+
+  # Axis names
+  xnames <- levels(r$Parameter1)
+  ynames <- levels(r$Parameter2)
+
+  # xcol <- case_when(
+  #   str_detect(xnames, "Condition") ~ "#1565C0",
+  #   str_detect(xnames, "Intercept") ~ "#6A1B9A",
+  #   .default = xcol
+  # )
+  # ycol <- case_when(
+  #   str_detect(ynames, "BAIT") ~ "#00838F",
+  #   str_detect(ynames, "GAAIS") ~ "#C62828",
+  #   str_detect(ynames, "AI_Knowledge") ~ "#EF6C00",
+  #   .default = ycol
+  # )
+
+  # Bold emphasis (optional, minimal)
+  xbold <- case_when(
+    str_detect(xnames, "Condition") ~ "bold",
+    str_detect(xnames, "Intercept") ~ "bold",
+    .default = "plain"
+  )
+  ybold <- case_when(
+    str_detect(ynames, "BAIT") ~ "bold",
+    str_detect(ynames, "GAAIS") ~ "bold",
+    str_detect(ynames, "Porn") ~ "bold",
+    str_detect(ynames, "AI") ~ "bold",
+    .default = "plain"
+  )
+
+  # Plot
+  r |>
+    ggplot(aes(x = Parameter1, y = Parameter2, fill = r)) +
+    geom_tile() +
+    geom_text(aes(label = label), size = textsize, lineheight = 0.9) +
+    scale_fill_gradient2(low = "blue", high = "red", mid = "white", midpoint = 0) +
+    theme_minimal() +
+    theme(
+      axis.text.x = element_text(color = xcol, face = xbold),
+      axis.text.y = element_text(color = ycol, face = ybold),
+      legend.position = "none",
+      axis.title = element_blank()
+    )
+}
+
+p_corAI <- make_cor(df_phase, df_dispositional, qname_x = FALSE, qname_y = FALSE, textsize = 3)  +
+  labs(title="Correlations between the effect of condition and dispositional traits") +
+  theme(axis.title = element_blank())
+
+p_corAI 
+```
+
+#### Study 2

### 2025-11-13 paper/manuscript.qmd
minor

@@
 
+<!-- Duffy et al., 2024:  when image sare controlled for types of artifacts participants show no ability in distinguishing real vs fake faces.
+Altough, they did rate faces with higher intensity smiles as more real.
+-->
+
 Recent advances in artificial intelligence (AI) have introduced new challenges for human cognition, particularly regarding the ability to distinguish between authentic and fabricated experiences [@miller2023ai].
-The stakes of such perceptual uncertainty are considerable, with misinformation representing one of the most pressing societal consequences [@kreps2022all].
+
+The consequences of such perceptual uncertainty are considerable, with misinformation representing one of the most pressing societal consequences [@kreps2022all].
 For instance, deepfakes (face-swapping technologies that enable the creation of realistic fake images and videos) have already been employed to fabricate convincing political speeches that appear genuine [@meskys2020regulating].
@@
 A key challenge lies in the prevalence of ambiguous stimuli, that is images, texts, videos, or environments whose authenticity cannot be easily established. 
-While artificial stimuli once carried perceptual markers that betrayed their inauthenticity, such as distortions in early computer-generated imagery [@corvi2023detection; @mcdonnell2010face], these limitations are rapidly disappearing.
+While artificial stimuli once carried perceptual markers that made their inauthenticity easier to spot, such as distortions in early computer-generated imagery [@corvi2023detection; @mcdonnell2010face], these limitations are rapidly disappearing.
 In the domain of face generation especially, current algorithms now produce synthetic images that are virtually indistinguishable from genuine photographs [@moshel2022you; @nightingale2022ai]. 
@@
   - Mention theories such as Affective Reality Theory (Makowski, 2023) if relevant, or more general emotion–cognition links.
-  - Emotions may not just follow perception, but also shape how we judge what is real. -->
+  - Emotions may not just follow perception, but also shape how we judge what is real -PP. -->
 

### 2025-11-24 analysis/analysis.qmd
updated scripts

@@
 }
+
+results_table <- function(model, effects="fixed", filter=NULL) {
+  if("marginaleffects" %in% class(model)) {
+    model |> 
+      parameters::parameters() |> 
+      as.data.frame() |> 
+      select(-Parameter, -SE, -S, z=Statistic) |> 
+      insight::format_table() |> 
+      parameters::display()
+  } else {
+    display(parameters::parameters(model, effects=effects, keep=filter))
+  }
+}
 ```
 
+<!-- - condition as random intercept for participant converged but not sure whether we should keep intercepts different or the same for the models? -->
+
+<!-- ```{r} -->
+
+<!-- m_arousal1 <- glmmTMB::glmmTMB(Arousal ~ Gender / Relevance / Condition + (Relevance | Participant) + (Relevance|Item), data=df1, family=glmmTMB::ordbeta(), control = glmmTMB::glmmTMBControl(parallel = 8)) -->
+
+<!-- m_arousal2 <- glmmTMB::glmmTMB(Arousal ~ Gender/ Condition + (1| Participant) + (1|Item), family=glmmTMB::ordbeta(), data=df2, control = glmmTMB::glmmTMBControl(parallel = 8)) -->
+<!-- ``` -->
+
 ```{r}
-# arousal1 <- readRDS("models/ModelArousal_1.rds")
+arousal1 <- readRDS("models/ModelArousal_1.rds")
 arousal2 <- readRDS("models/ModelArousal_2.rds")
@@
 
+<!-- ```{r} -->
+<!-- results_table(m_arousal1) -->
+<!-- results_table(m_arousal2) -->
+<!-- ``` -->
+
 ```{r}
-params_table(arousal1)
+params_table(m_arousal1)
 summary(arousal1, robust = TRUE)

### 2025-11-24 analysis/server/make_model.R

@@ -27,11 +27,11 @@ df1 <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/ref
 # ----------------------------
 
 # Arousal
-f_a1 <- brms::brmsformula(Arousal ~ Gender / Relevance / (Condition * ConditionBelief) + (1  + Relevance / Condition  | Participant) + (1|Item))
+f_a1 <- brms::brmsformula(Arousal ~ Gender / Relevance / (Condition * ConditionBelief) + (1  + Relevance / Condition | Participant) + (Relevance|Item))
 m_a1 <-  brms::brm(
   formula = f_a1,
   data = df1,
-  family = zero_one_inflated_beta(),
+  family = gaussian(),
   chains = chains_per_task,
   cores = chains_per_task,
   iter = iter,
@@ -42,12 +42,12 @@ m_a1 <-  brms::brm(
 )
 
 # Enticement (FIXED: use f_e1 and set chains)
-# f_e1 <- brms::brmsformula(Enticement ~ Gender / Relevance / (Condition * ConditionBelief) + (1  + Relevance / Condition  | Participant) + (1|Item))
+# f_e1 <- brms::brmsformula(Enticement ~ Gender / Relevance / (Condition * ConditionBelief) + (1  + Relevance / (Condition * ConditionBelief) | Participant) + (Relevance|Item))
 
 # m_e1 <-  brms::brm(
 #   formula = f_e1,
 #   data = df1,
-#   family = zero_one_inflated_beta(),
+#   family = gaussian(),
 #   chains = chains_per_task,
 #   cores = chains_per_task,
 #   iter = iter,
@@ -58,12 +58,12 @@ m_a1 <-  brms::brm(
 # )
 
 # Valence
-# f_v1 <- brms::brmsformula(Valence ~ Gender / Relevance / (Condition * ConditionBelief) + (1  + Relevance / Condition  | Participant) + (1|Item))
+# f_v1 <- brms::brmsformula(Valence ~ Gender / Relevance / (Condition * ConditionBelief) + (1  + Relevance / (Condition * ConditionBelief) | Participant) + (Relevance|Item))
 
 # m_v1 <-  brms::brm(
 #   formula = f_v1,
 #   data = df1,
-#   family = zero_one_inflated_beta(),
+#   family = gaussian(),
 #   chains = chains_per_task,
 #   cores = chains_per_task,
 #   iter = iter,
[…]

### 2025-11-27 analysis/analysis.qmd
updated model scripts

@@
 library(gt)
+library(ggdist)
 
@@
 
+params_table <- function(m) {
+  d <- as.data.frame(m, variable = insight::find_parameters(m, effects = "fixed", flatten  = TRUE))
+  t <- bayestestR::describe_posterior(d, effects = "fixed", component = "all", ci_method = "hdi", test = "p_direction")
+  out <- insight::format_table(t)
+  out |> 
+    mutate(col = t$pd) |> 
+    gt::gt() |> 
+    gt::data_color(columns = "col", method = "numeric", target_columns = "pd", 
+                   row = col > 0.95, palette = "yellow") |> 
+    gt::data_color(columns = "col", method = "numeric", target_columns = "pd", 
+                   row = col > 0.97, palette = "green") |> 
+    gt::cols_hide("col")
+}
 ```
@@
 
-```{r}
-params_table <- function(m) {
-  d <- as.data.frame(m, variable = insight::find_parameters(m, effects = "fixed", flatten  = TRUE))
-  t <- bayestestR::describe_posterior(d, effects = "fixed", component = "all", ci_method = "hdi", test = "p_direction")
-  out <- insight::format_table(t)
-  out |> 
-    mutate(col = t$pd) |> 
-    gt::gt() |> 
-    gt::data_color(columns = "col", method = "numeric", target_columns = "pd", 
-                   row = col > 0.95, palette = "yellow") |> 
-    gt::data_color(columns = "col", method = "numeric", target_columns = "pd", 
-                   row = col > 0.97, palette = "green") |> 
-    gt::cols_hide("col")
-}
-
-results_table <- function(model, effects="fixed", filter=NULL) {
-  if("marginaleffects" %in% class(model)) {
-    model |> 
-      parameters::parameters() |> 
-      as.data.frame() |> 
-      select(-Parameter, -SE, -S, z=Statistic) |> 
-      insight::format_table() |> 
-      parameters::display()
-  } else {
-    display(parameters::parameters(model, effects=effects, keep=filter))
-  }
-}
-```
+#### Distributions
 
@@
 ```{r}
+df1 |> 
+  ggplot(aes(x = Gender, y = Arousal, fill = ConditionBelief)) +
+  geom_violin(position = position_dodge(width = 1), alpha = 0.6, trim = FALSE) +
+  stat_pointinterval(
+    position = position_dodge(width = 1),
+    .width = c(.66, .95),
+    point_size = 1.5) +
+  facet_grid(Relevance ~ Condition) +
+  theme_minimal(base_size = 14) +
+  labs(
+    title = "Arousal by Gender × Belief × Relevance × Condition",
+    x = "Gender",
+    y = "Arousal",
+    fill = " Condition Belief"
+  )
+
+df2 |> 
+  ggplot(aes(x = Gender, y = Arousal, fill = ConditionBelief)) +
+  geom_violin(position = position_dodge(width = 1), alpha = 0.6, trim = FALSE) +
+  stat_pointinterval(
+    position = position_dodge(width = 1),
+    .width = c(.66, .95),
+    point_size = 1.5) +
+  facet_grid( ~ Condition) +
+  theme_minimal(base_size = 14) +
+  labs(
+    title = "Arousal by Gender × Belief × Relevance × Condition",
+    x = "Gender",
+    y = "Arousal",
+    fill = " Condition Belief"
+  )
+
+```
+
+```{r}
 arousal1 <- readRDS("models/ModelArousal_1.rds")
 arousal2 <- readRDS("models/ModelArousal_2.rds")
+
 ```

### 2025-11-27 analysis/server/make_model.R

@@ -27,7 +27,7 @@ df1 <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/ref
 # ----------------------------
 
 # Arousal
-f_a1 <- brms::brmsformula(Arousal ~ Gender / Relevance / (Condition * ConditionBelief) + (1  + Relevance / Condition | Participant) + (Relevance|Item))
+f_a1 <- brms::brmsformula(Arousal ~ Gender / Relevance / (Condition * ConditionBelief) + (1  + Condition  | Participant) + (1|Item))
 m_a1 <-  brms::brm(
   formula = f_a1,
   data = df1,

### 2025-12-02 analysis/analysis.qmd
analysis script

@@
 
+#Individual models
+
+m <- readRDS("models/individual_models/ModelArousal_1_task_1.rds")
+m <- readRDS("models/individual_models/ModelArousal_1_task_2.rds")
+m <- readRDS("models/individual_models/ModelArousal_1_task_3.rds")
+m <- readRDS("models/individual_models/ModelArousal_1_task_4.rds")
+m <- readRDS("models/individual_models/ModelArousal_1_task_5.rds")
+m <- readRDS("models/individual_models/ModelArousal_1_task_6.rds")
+
+m <- readRDS("models/individual_models/ModelArousal_2_task_1.rds")
+m <- readRDS("models/individual_models/ModelArousal_2_task_2.rds")
+m <- readRDS("models/individual_models/ModelArousal_2_task_3.rds")
+m <- readRDS("models/individual_models/ModelArousal_2_task_4.rds")
+m <- readRDS("models/individual_models/ModelArousal_2_task_5.rds")
+m <- readRDS("models/individual_models/ModelArousal_2_task_6.rds")
+
 ```

### 2025-12-03 analysis/server/cleaned_data.R
Update cleaned_data.R

@@ -14,7 +14,23 @@ df1 <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/ref
     by = "Participant"
   ) |>
   rename(Gender = Sex) |>
-  datawizard::rescale(select=c("Valence"), range=c(-1, 1), to=c(0, 1)) 
+  datawizard::rescale(select=c("Valence"), range=c(-1, 1), to=c(0, 1)) |>
+  
+
+# |>
+#   mutate(Condition = fct_relevel(Condition, "Photograph", "AIGenerated"),
+#          Relevance =  fct_relevel(Relevance, "Relevant", "Irrelevant", "NonErotic"),
+#          Gender =  fct_relevel(Gender, "Male", "Female"),
+#          PornFrequency = as.numeric(as.factor(COPS_Frequency_2)),
+#          SexualActivity_num = as.numeric(as.factor(SexualActivity)),
+#          ConditionBelief = case_when(
+#            Condition == "Photograph" & Realness > 0.5 ~ "True",
+#            Condition == "AIGenerated" & Realness < 0.5 ~ "True",
+#            .default = "False"
+#          ),
+#          ConditionBelief = as.factor(ConditionBelief),
+#          ConditionBelief = fct_relevel(ConditionBelief, "True", "False")) |>
+#   mutate(across(starts_with("Feedback_"), function(x) {fct_relevel(x, "False", "True")}))
 
 
 write.csv(df1, "../data/df1.csv", row.names = FALSE)
@@ -33,7 +49,28 @@ df2 <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/ref
   mutate(Condition = case_when(
     Condition == "Fiction" ~ "AIGenerated",
     Condition == "Reality" ~ "Photograph"
-  )) 
+  )) |>
+  mutate(ConditionBelief = case_when(
+               Condition == "Photograph" & Realness > 0.5 ~ "True", Condition
+               == "AIGenerated" & Realness < 0.5 ~ "True", .default =
+               "False"))
+  
+      
+
+# |>
+#   mutate(Condition = fct_relevel(Condition, "Photograph", "AIGenerated"),
+#          Gender =  fct_relevel(Gender, "Male", "Female"),
+#          SexualOrientation = fct_relevel(SexualOrientation, "Heterosexual", "Homosexual", "Bisexual"),
+#          PornFrequency = as.numeric(as.factor(COPS_Frequency)),
[…]

### 2025-12-03 analysis/server/make_model.R
Added relevance as random slope for Participant

@@ -39,7 +39,7 @@ df1 <- read.csv("https://raw.githubusercontent.com/RealityBending/FictionEro/ref
 # ----------------------------
 
 # Arousal
-f_a1 <- brms::brmsformula(Arousal ~ Gender / Relevance / Condition * ConditionBelief + (1  + Condition  | Participant) + (1|Item))
+f_a1 <- brms::brmsformula(Arousal ~ Gender / Relevance / Condition * ConditionBelief + (Relevance/Condition  | Participant) + (1|Item))
 
 # brms::get_prior(f_a1, data=df1)
 

### 2025-12-03 analysis/server/combine_models.R
Models running with relevance as random slope

@@ -14,7 +14,10 @@ setwd("/mnt/lustre/users/psych/asf25/fictionero/models/")
 # model_names <- c("ModelArousal_1", "ModelEnticement_1", "ModelValence_1",
 #                  "ModelArousal_2", "ModelEnticement_2", "ModelValence_2")
 
-model_names <- c("ModelArousal_1","ModelArousal_2")
+# model_names <- c("ModelArousal_1","ModelArousal_2")
+
+model_names <- c("ModelArousal_1")
+
 
 # Pick model based on array ID
 model_name <- model_names[task_id]

### 2025-12-03 analysis/analysis.qmd
Updated analysis
@DominiqueMakowski  good Rhat and ESS for individual and combined models with specified priors . Have added Relevance as slope for participants and started running them to see if they come back with reliable estimates

@@
 
-m <- readRDS("models/individual_models/ModelArousal_2_task_1.rds")
-m <- readRDS("models/individual_models/ModelArousal_2_task_2.rds")
-m <- readRDS("models/individual_models/ModelArousal_2_task_3.rds")
-m <- readRDS("models/individual_models/ModelArousal_2_task_4.rds")
-m <- readRDS("models/individual_models/ModelArousal_2_task_5.rds")
-m <- readRDS("models/individual_models/ModelArousal_2_task_6.rds")
+# 
+# m <- readRDS("models/individual_models/ModelArousal_2_task_1.rds")
+# m <- readRDS("models/individual_models/ModelArousal_2_task_2.rds")
+# m <- readRDS("models/individual_models/ModelArousal_2_task_3.rds")
+# m <- readRDS("models/individual_models/ModelArousal_2_task_4.rds")
+# m <- readRDS("models/individual_models/ModelArousal_2_task_5.rds")
+# m <- readRDS("models/individual_models/ModelArousal_2_task_6.rds")
 

### 2025-12-09 analysis/analysis.qmd
Update analysis.qmd

--- 2025-11-27 analysis/analysis.qmd
@@
   datawizard::rescale(select=c("Valence"), range=c(-1, 1), to=c(0, 1)) |> 
-  mutate(Condition = fct_relevel(Condition, "Photograph", "AI-Generated"),
-         Relevance =  fct_relevel(Relevance, "Relevant", "Irrelevant", "Non-erotic"),
+  mutate(Condition = fct_recode(Condition, "Photograph" = "Photograph", "AIGenerated" = "AI-Generated"),
+         Condition = fct_relevel(Condition, "Photograph", "AIGenerated"),
+         Relevance = fct_recode(Relevance,  "Relevant" = "Relevant",  "Irrelevant"= "Irrelevant", "NonErotic" = "Non-erotic"),
+         Relevance =  fct_relevel(Relevance, "Relevant", "Irrelevant", "NonErotic"),
          Gender =  fct_relevel(Gender, "Male", "Female"),
+         ConditionBelief = case_when(
+           Condition == "Photograph" & Realness > 0.5 ~ "True",
+           Condition == "AIGenerated" & Realness < 0.5 ~ "True",
+           .default = "False"),
+         ConditionBelief = as.factor(ConditionBelief),
+         ConditionBelief = fct_relevel(ConditionBelief, "True", "False"),
          PornFrequency = as.numeric(as.factor(COPS_Frequency_2)),
          SexualActivity_num = as.numeric(as.factor(SexualActivity)),
-         ConditionBelief = case_when(
-           Condition == "Photograph" & Realness > 0.5 ~ "True",
-           Condition == "AI-Generated" & Realness < 0.5 ~ "True",
-           .default = "False"
-         )) |> 
-  mutate(across(starts_with("Feedback_"), function(x) {fct_relevel(x, "False", "True")}))
+         across(starts_with("Feedback_"), function(x) {fct_relevel(x, "False", "True")}))
 ```
@@
   datawizard::rescale(select= c("Realness"), range=c(-3,3), to=c(0,1)) |>
-  mutate(Condition = case_when(
-    Condition == "Fiction" ~ "AI-Generated",
-    Condition == "Reality" ~ "Photograph"
-  )) |>
-  mutate(Condition = fct_relevel(Condition, "Photograph", "AI-Generated"),
-         Gender =  fct_relevel(Gender, "Male", "Female"),
-         SexualOrientation = fct_relevel(SexualOrientation, "Heterosexual", "Homosexual", "Bisexual"),
+  filter(SexualOrientation == "Heterosexual") |> # Keep only heterosexuals
+  mutate(Gender =  fct_relevel(Gender, "Male", "Female"),
+         Condition = case_when(
+           Condition == "Fiction" ~ "AIGenerated",
+           Condition == "Reality" ~ "Photograph"), 
+         Condition = fct_relevel(Condition, "Photograph", "AIGenerated"),
+         ConditionBelief = case_when(
+           Condition == "Photograph" & Realness > 0.5 ~ "True",
+           Condition == "AIGenerated" & Realness < 0.5 ~ "True",
+           .default = "False"),
+         ConditionBelief = as.factor(ConditionBelief),
+         ConditionBelief = fct_relevel(ConditionBelief, "True", "False"),
          PornFrequency = as.numeric(as.factor(COPS_Frequency)),
          SexualActivity_num = as.numeric(as.factor(SexualActivity)),
-         ConditionBelief = case_when(
-           Condition == "Photograph" & Realness > 0.5 ~ "True",
-           Condition == "AI-Generated" & Realness < 0.5 ~ "True",
-           .default = "False",
-         )) |>
-  rename(AllRealConfidence = "Feedback_AllRealConfidence",
+         across(starts_with("Feedback_"), as.factor), 
+         across(starts_with("Feedback_"), function(x) {fct_relevel(x, "False", "True")})) |>
+    rename(Item = Stimulus,
+           Enticement = Enticing,
+           AllRealConfidence = "Feedback_AllRealConfidence",
            AllFakeConfidence = "Feedback_AllFakeConfidence",
-         Enjoyment = "Feedback_Enjoyment",
-         Item = Stimulus
-  )|>
-  mutate(across(starts_with("Feedback_"), as.factor)) |>
-  mutate(ConditionBelief = as.factor(ConditionBelief)) |>
-  mutate(StimuliType = case_when(
-    grepl("couple", Item, ignore.case = TRUE) ~ "Couple",
-    TRUE ~ "Individual")) |>
-  mutate(StimuliType = fct_relevel(StimuliType, "Individual", "Couple"))
+           Enjoyment = "Feedback_Enjoyment") 
 ```
@@
   facet_wrap(~Gender) +
-  scale_fill_manual(values=c("AI-Generated"="#2196F3", "Photograph"="#F44336")) +
+  scale_fill_manual(values=c("AIGenerated"="#2196F3", "Photograph"="#F44336")) +
   theme_minimal() +
@@
   facet_wrap(~Gender) +
-  scale_fill_manual(values=c("Photograph"="#F44336", "AI-Generated"="#2196F3")) +
+  scale_fill_manual(values=c("AIGenerated"="#2196F3", "Photograph"="#F44336")) +
   theme_minimal() +
@@
 enticement_dist2 <- df2 |>
-  ggplot(aes(x=Enticing, fill = Condition)) +
+  ggplot(aes(x=Enticement, fill = Condition)) +
   geom_bar(position = "identity", alpha = 0.5, colour = "black") +
@@
   facet_wrap(~Gender) +
-  scale_fill_manual(values=c("Photograph"="#F44336", "AI-Generated"="#2196F3")) +
+  scale_fill_manual(values=c("Photograph"="#F44336", "AIGenerated"="#2196F3")) +
   theme_minimal() +
@@
       ) |>
-      mutate(diff_arousal = `mean_Arousal_AI-Generated` - mean_Arousal_Photograph)
+      mutate(diff_arousal = `mean_Arousal_AIGenerated` - mean_Arousal_Photograph)
   )
@@
   ggplot(aes(x = Feedback_AILessArousing, y = diff_arousal, fill = Feedback_AILessArousing)) +
-  geom_boxplot(width = 0.4,alpha = 0.6) +
+  geom_boxplot(width = 0.4,alpha = 0.7) +
   geom_jitter(width = 0.2, alpha = 0.1, size = 1) +
@@
   ) +
-  scale_fill_manual(values = c("True" = "#FF9800", "False" = "#E91E63")) +
+  scale_fill_manual(values = c("True" = "#E66100", "False" = "#5D3A9B")) +
   theme_minimal() +
@@
                   values_from = mean_arousal) |>
-      mutate(diff_arousal = `mean_Arousal_AI-Generated` - mean_Arousal_Photograph)
+      mutate(diff_arousal = `mean_Arousal_AIGenerated` - mean_Arousal_Photograph)
   )
@@
   ggplot(aes(x = Feedback_AILessArousing, y = diff_arousal, fill = Feedback_AILessArousing)) +
-  geom_boxplot(width = 0.4, alpha = 0.6) +
+  geom_boxplot(width = 0.4, alpha = 0.7) +
   geom_jitter(width = 0.2, alpha = 0.1, size = 1) +
@@
 
-<!-- - condition as random intercept for participant converged but not sure whether we should keep intercepts different or the same for the models? -->
-
-<!-- ```{r} -->
-
-<!-- m_arousal1 <- glmmTMB::glmmTMB(Arousal ~ Gender / Relevance / Condition + (Relevance | Participant) + (Relevance|Item), data=df1, family=glmmTMB::ordbeta(), control = glmmTMB::glmmTMBControl(parallel = 8)) -->
-
-<!-- m_arousal2 <- glmmTMB::glmmTMB(Arousal ~ Gender/ Condition + (1| Participant) + (1|Item), family=glmmTMB::ordbeta(), data=df2, control = glmmTMB::glmmTMBControl(parallel = 8)) -->
-<!-- ``` -->
-
 ```{r}
@@
   ggplot(aes(x = Gender, y = Arousal, fill = ConditionBelief)) +
-  geom_violin(position = position_dodge(width = 1), alpha = 0.6, trim = FALSE) +
-  stat_pointinterval(
-    position = position_dodge(width = 1),
-    .width = c(.66, .95),
-    point_size = 1.5) +
+  geom_violin(position = position_dodge(width = 1), alpha = 0.7, trim = FALSE) +
+  stat_pointinterval(position = position_dodge(width = 1),point_size = 1.5) +
   facet_grid(Relevance ~ Condition) +
+  scale_fill_manual(values = c("True" = "#E66100", "False" = "#5D3A9B")) +
   theme_minimal(base_size = 14) +
-  labs(
-    title = "Arousal by Gender × Belief × Relevance × Condition",
-    x = "Gender",
-    y = "Arousal",
-    fill = " Condition Belief"
-  )
+  labs(title = "Arousal by Gender × Belief × Relevance × Condition", subtitle ="Study 1", x = "Gender",y = "Arousal",fill = " Condition Belief")
 
@@
   ggplot(aes(x = Gender, y = Arousal, fill = ConditionBelief)) +
-  geom_violin(position = position_dodge(width = 1), alpha = 0.6, trim = FALSE) +
-  stat_pointinterval(
-    position = position_dodge(width = 1),
-    .width = c(.66, .95),
-    point_size = 1.5) +
+  geom_violin(position = position_dodge(width = 1), alpha = 0.7, trim = FALSE) +
+  stat_pointinterval(position = position_dodge(width = 1),point_size = 1.5) +
   facet_grid( ~ Condition) +
+  scale_fill_manual(values = c("True" = "#E66100", "False" = "#5D3A9B")) +
   theme_minimal(base_size = 14) +
-  labs(
-    title = "Arousal by Gender × Belief × Relevance × Condition",
-    x = "Gender",
-    y = "Arousal",
-    fill = " Condition Belief"
-  )
+  labs(title = "Arousal by Gender × Belief × Relevance × Condition", subtitle ="Study 2", x = "Gender", y = "Arousal",fill = " Condition Belief")
 
@@
 arousal2 <- readRDS("models/ModelArousal_2.rds")
-
 ```
@@
 ```{r}
-params_table(m_arousal1)
+params_table(arousal1)
 summary(arousal1, robust = TRUE)

### 2025-12-12 analysis/server/combine_models.R
Update combine_models.R
Running Zoib models

@@ -11,8 +11,10 @@ task_id <- as.numeric(Sys.getenv("SLURM_ARRAY_TASK_ID"))
 setwd("/mnt/lustre/users/psych/asf25/fictionero/models/")
 
 # List of models
-model_names <- c("ModelEnticement_1", "ModelValence_1",
-                 "ModelEnticement_2", "ModelValence_2")
+# model_names <- c("ModelEnticement_1", "ModelValence_1",
+#                  "ModelEnticement_2", "ModelValence_2")
+
+model_names <- c("ModelArousal_1", "ModelArousal_2")
 
 # Pick model based on array ID
 model_name <- model_names[task_id]

### 2025-12-12 analysis/analysis.qmd
Update analysis.qmd
Added ZOIB arousal models (combined mdoels)

@@
 ```{r}
-arousal1 <- readRDS("models/ModelArousal_1.rds")
-arousal2 <- readRDS("models/ModelArousal_2.rds")
+arousal1_GAU <- readRDS("models/Gaussian/ModelArousal_1.rds")
+arousal2_GAU <- readRDS("models/Gaussian/ModelArousal_2.rds")
+
+arousal1_ZOIB <- readRDS("models/ZOIB/ModelArousal_1_ZOIB.rds")
+arousal2_ZOIB <- readRDS("models/ZOIB/ModelArousal_2_ZOIB.rds")
 ```
@@
 summary(arousal2, robust = TRUE)
+```
+
+```{r}
+params_table(arousal1_ZOIB)
+summary(arousal1_ZOIB, robust = TRUE)
+```
+
+```{r}
+params_table(arousal2_ZOIB) 
+summary(arousal2_ZOIB, robust = TRUE)
 ```
@@
 ```{r}
-draft_model <- brms::brm(
-  formula = Arousal ~ Gender / (Condition * ConditionBelief) + (1  + Condition | Participant) + (1|Item),
-  data = df2,
-  algorithm = "meanfield",
-  family = brms::zero_one_inflated_beta())
-
-g1 <- modelbased::estimate_grouplevel(draft_model)
-
-# saveRDS(g1, file = "draft_model_estimates.rds")
+a1 <- modelbased::estimate_grouplevel(arousal1)
+a2 <- modelbased::estimate_grouplevel(arousal2)
 
@@
 ```{r}
-# g1 <- readRDS("draft_model_estimates.rds")
-
-table_dvour(g1)
-
+table_dvour(a2)
 ```
